### 2023-03-11 paper/main.tex
first commit: already written intro and method

\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{enumerate}
\usepackage{amsmath}
\usepackage{bm}
\usepackage[ruled,linesnumbered]{algorithm2e}

\def\T{\mathrm{T}}

\title{Greedy-based RBS maximum allowable current calculation method}
\author{3057761608 }
\date{March 2023}

\begin{document}

\maketitle

\section{Introduction}

% Battery energy storage systems(BESS) 被用在新能源汽车、风力发电站等场景中，为设备提供高品位电能的保存和释放。
Battery Energy Storage Systems (BESSs) are used to store and release high quality electrical energy in a timely manner in scenarios such as electric vehicles and wind power turbines.
A large number of individual battery cells are interconnected in groups by circuitry to form the main body of BESSs and achieve the required capacity and voltage for the application. 
However, the large number of cells also poses a challenge to the reliability of BESS: capacity and lifetime of the system depends mainly on the least healthy battery cells, known as the cask effect. 
As the multiple charge/discharge cycles of BESSs exacerbate the inconsistency of individual cells, the unhealthy batteries will appear early in operation.

% 【RBS的先进性、现状】
% Reconfigurable battery system(RBS) 解决固定电路电池组的 cask effect：系统的容量和寿命取决于状态最差的某些电池。
% 此外，不一致性也在系统运行中加剧恶化。
% 通过动态改变电路，调控或隔离不良电池，有助于提升系统整体可靠性。
% 但是，重构也增加了设计、分析和控制的难度。
% 当前，系统有成百上千的电池，平均每个电池由3~5个开关控制，形成了庞大的状态空间。
Reconfigurable Battery System (RBS), which can dynamically change the connections between batteries and switch between different circuit configurations as required, is expected to solve the above problem. 
Unlike fixed configurations, reconfigurable circuits have additional switches connected to battery cells in specific topological patterns. 
Series/parallel switching relationships and even the isolation of unhealthy batteries can be achieved by controlling the states of these switches (open or closed). 
From the point of view of the battery cells, RBS has a higher reliability than conventional configurable battery systems. 
However, it also increases the complexity of design and control.
Each battery in RBS is controlled by an average of 3 to 5 switches. When the system has hundreds or thousands of cells, there is a huge state space waits to solve.

% 【快速评估系统最大电流的作用和意义、文献现状】
% （一些典型结构、控制策略、评估）
% 快速评估系统最大允许电流在设计、分析和控制中起到重要作用。
% 对设计，系统的最大输出电流
% 对控制，应对故障，静态结构破坏
% 但是没有严谨研究最大电流。（直接说没有）
% del: 一些研究使用了过度的简化，不准；（具体文献？）:led
% del: 只针对小数量的电池和特定的结构，不普适（具体文献，容易找到）:led
The importance of the Maximum Allowable Current (MAC), defined as the maximum current that the system can output to external electrical equipment when the currents of all the batteries in the system do not exceed the specified value, is beginning to be recognised in RBS research. 
From the definition it can be seen that MAC determines the maximum output current of the RBS during normal operation at the design stage and of the reconfigured system when the failed batteries are isolated during the run-in phase. 
MAC is therefore one of the key indicators used in the study for the design and evaluation of RBSs.
% (#TODO: 一些考虑最大许用电流的构建结构的策略)
(TODO: Some literature on strategies for RBS that take MAC into account)
However, none of the existing literature on RBS provides a method for calculating the MAC.

% 【本文的主要内容和结构】
% 我们提出了快速估计RBS的算法，基于贪婪策略。填补了这一空白。
The purpose of this paper is to propose an effective and efficient algorithm based on the greedy search strategy to solve the MAC of RBSs. 
A mathematical model of MAC is constructed and the optimal solution is searched in the state space of switches using maximising the number of cells directly connected in parallel as the strategy.

% 文章组织：section 2，算法的框架和细节；section 3，案例，讨论和验证；section 4 总结。
This paper is organized as follows. 
Section II presents the mathematical model and the algorithm in detail.
Section III solves an example proposed in \cite{kimDESADependableEfficient2012}and discusses the results. 
Finally, Section IV provides concluding remarks and directions forjk future work.

\section{Method}
% \subsection{model building}

% Graph model has been uesd in the past to represent the connectivity of batteries in the RBS.
% In the study by He et al. \cite{heExploringAdaptiveReconfiguration2013} the batteries in system are represented as the vertices in the graph, and the connectivity between them are expressed as the edges.
% \begin{figure}[htbp]
%     \centering
%     \includegraphics[width=\textwidth]{../attachments/graph_model.png} % #TODO: redraw figure c
%     \caption{A typical RBS architecture and its two common graph models. 
%             (a) RBS architecture \cite{kimDESADependableEfficient2012}, (b) graph model focused on connectivity \cite{heExploringAdaptiveReconfiguration2013}, (c) graph model used in this paper.}
%     \label{fig:graph_model}
% \end{figure}
% Figure \ref{fig:graph_model}(b) illustrates one example of the connectiviy model of a typical RBS architecture(Figure \ref{fig:graph_model}(a)).
% The additional vertices + and - in the figure represent the cathode and anode of the RBS, respectively, and the directed edges between the neighboring nodes represent the possible flows of current.
% However, this graph model % 写不下去了，我们的图模型能做的，He 的图模型基本也能做，甚至还要清晰

\subsection{circuit model}

A typical RBS circuit consists of battery cells and switches.
We first transform them into ideal components under reasonable assumptions to establish a processable circuit.
Then the circuit structure is described in matrix form and the related equations are given.

% 【电路，有向图，规定，假设】
% node，连接battery和switch，编号顺序
% edge，battery 或 switch，编号顺序
% 电池等效为恒压ub串内阻rb
% Ro，外电阻
% 关联矩阵
% x，开关状态，01变量
% 【模型，求解方法】
% 假设均一化，矩阵分块
% 在导纳矩阵非奇异的条件下
% 推导出输出电流Io和电池电流Ib
The normal equivalent circuit of a battery consists of a voltage source in series with a resistor, and a capacitor in parallel with another resistor to simulate the polarisation in batteries.
As the main aim of this research is to calculate the stable MAC offered by a given RBS architecture, only the steady-state behaviour of the circuit is taken into account, while transient effects are ignored in this research.
Thus, we equate the battery $i$ as a constant voltage source $u_{b,i}$ in series with a resistor $r_{b,i}$.
A binary variable $x_j$ is used to represent the state of the switch $j$: 0 and 1 mean open and closed respectively.
To simplify the calculation, the closed switch is considered as a resistor with a very small resistance value $r_s$, which will be treated as zero in the final result.
In the following derivation, the product of the conductance $1/r_s$ and the variable $x_j$ is used to characterize the state of the switch $j$.

Before obtaining the incidence matrix representing the structure of the circuit, a directed graph model $G(V,E)$ for the RBS is constructed in such a way that
\begin{enumerate}[(1)]
    \item the vertex set $V={v_1,v_2,\cdots,v_N}$ represents the nodes connecting batteries and/or switches, where $v_1$ and $v_N$ represent the anode and cathode of the RBS respectively;
    \item the directed edge set $E$ represents the output circuit, $N_b$ batteries and $N_s$ switches, corresponding set $E_o$, $E_b$ and $E_s$. The external electrical equipment in the output circuit is treated as one directed edge $v_n \to v_1$. The direction of the edge representing a battery is set to be from the anode to the cathode. For the edges representing switches, their directions are marked from the low node to the the high node. A negative value for the voltage drop or current solved on the edge means that the actual direction is opposite to that initially specified.
\end{enumerate}

Based on the above directed graph which has $N$ nodes and $1+N_b+N_s$ directed edges (1 refers to the output circuit), its incidence matrix $\bm{A}_{N\times (1+N_b+N_s)}$ is defined as
\begin{align}\label{eq:A}
    a_{ij}=
    \begin{cases}
        1,  & \text{edge  $j$ leaves vertex $i$},\\
        -1, & \text{edge $j$ enters vertex $i$},\\
        0,  & \text{otherwise}.
    \end{cases}
\end{align}
Since each column of $\bm{A}$ sums to zero, we delete the last line and use the reduced incidence matrix $\bm{A}_{(N-1)\times(1+N_b+N_s)}$ in the following calculation.
y splitting $E$ into $\{E_o, E_b, E_s\}$, $A$ is rewritten as follows
\begin{equation}
    \bm{A} = 
    \begin{bmatrix}
        \bm{A}_o & \bm{A}_b & \bm{A}_s
    \end{bmatrix}.
\end{equation}

$1+N_b+N_s$ edges' currents $\bm{I}_{(1+N_b+N_s)\times 1}$ and voltages $\bm{U}_{(1+N_b+N_s)\times 1}$, and $N-1$ nodes' voltages $\bm{U}_{n, (N-1)\times 1}$ have following relationships from Kirchhoffs law
\begin{align}\label{eq:Kirchhoffs_law}
    \begin{cases}
    \bm{A} \bm{I} = \bm{0}, \\
    \bm{U}        = \bm{A}^\T \bm{U}_n.
    \end{cases}
\end{align}
These directed edges are treated as generalized branches and expressed in matrix form as follows
\begin{equation}\label{eq:generalized_branches}
    \bm{I} = \bm{Y}\bm{X} \bm{U} - \bm{Y}\bm{X} \bm{U}_s +\bm{I}_s,
\end{equation}
where $\bm{I}$ and $\bm{U}$ are the column vectors about $1+N_b+N_s$ edges' current and voltage, respectively; 
$\bm{U}_s$ and $\bm{I}_s$ denote the source voltage and source current of the generalized branches, respectively;
$\bm{Y}$ is the admittance matrix of the circuit, and $\bm{X}$ is the state matrix defined as
\begin{equation}\label{eq:X}
    \bm{X} = diag(
        1,  
        \underbrace{1, \cdots, 1}_{N_b~\text{of}~1}, 
        \underbrace{1, 0 \cdots, 1}_{N_s~\text{of}~0/1}
    ).
\end{equation}

In addition to the equivalent circuit assumptions, we also assume that all batteries have the same internal resistance value $r_b$ and supply the same electric potential $u_s$ to simplify the model.
Then the output current $I_o$ and each battery's current $\bm{I}_b$ can be given by solving the simultaneous Equations \ref{eq:Kirchhoffs_law} and \ref{eq:generalized_branches} eventually.
Let
\begin{equation}\label{eq:Yn}
    \bm{Y}_n (\bm{X}) = \frac{1}{R_o} \bm{A}_o\bm{A}_o^\T + \frac{1}{r_b} \bm{A}_b\bm{A}_b^\T + \frac{1}{r_s}\bm{A}_s\bm{X}\bm{A}_s^\T,
\end{equation}
where $R_o$ is the equivalent resistance of the external circuit.
Then, if $\bm{Y}_n$ is an invertible matrix, 
\begin{align}
    I_o(\bm{X})      & = \frac{u_b}{R_o r_b} \bm{A}_o^\T \bm{Y}_n^{-1}(\bm{X}) \bm{A}_b \bm{I}_{N_b\times 1};\label{eq:I_o}\\
    \bm{I}_b(\bm{X}) & = \frac{u_b}{r_b^2}[\bm{A}_b^\T \bm{Y}_n^{-1}(\bm{X}) \bm{A}_b\bm{I}_{N_b \times 1}  -r_b \bm{I}_{N_b \times 1}],\label{eq:I_b}
\end{align}
where $\bm{I}_{N_b\times 1}$ is a column vector with all terms being one.

% 用外电流Ib比所有电池中最大电流max（Ib）之比，表征电路的最大许用输出。是电路结构本身的性质，与电池无关。电路的线性保证了。
% 目标问题转化为【数学形式】
% Max rate
% s.t.
We use the ratio of $I_o$ and $\max (\bm{I}_b)$ to characterize the allowable current for a given RBS architecture, denoted as $\eta$.
The $\eta$ reflects the ability of the RBS architecture itself to deliver current, regardliess of the battery cells used by the RBS.
Due to the linearity of the above circuit model, the output current will vary by the same multiple if the allowable current of all batteries varies by a certain multiple.
Our problem in RBS can be formulated as
\begin{align}
        & \max \eta \label{eq:max_eta}\\
    \mathrm{s.t.}\,\, & \eta = \frac{I_o}{\max (\bm{I}_b)}, \\
        & \max (\bm{I}_b) \leq I_m,
\end{align}
where $I_m$ is the maximum allowable current of the battery; $I_o$ and $\bm{I}_b$ can be calculated by Equations \ref{eq:I_o} and \ref{eq:I_b}.
The presence of the inverse matrix $\bm{Y}_n^{-1}$ prevents us from solving \ref{eq:max_eta} directly, especially when a large number of battery cells and switches are present in the system.
We therefore propose a greedy algorithm to solve this model.

\subsection{greedy solution}
% 使用贪心算法策略求解
% 【贪心策略】
% 电池i的最短路径，短指的是路径上电池数量最少
% 贪心策略，当系统中越多的电池被以最短路径联入电路，外电路电流越大。
% 短路，检查
% 组合，逐一
If the battery $i$ is connected to the anode $v_1$ and the cathode $v_N$ of the RBS by a certain line with the minimum number of battery cells on the path,
we call this path the shortest path ($SP_i$) for the battery $i$.
Since batteries can provide more total current when connected in parallel than in series, $SP_i$ is the path where battery $i$ contributes the most current to the system output.
Our solution greedily addresses the issue mentioned in the previous subsection: we greedily allow as many cells as possible to be connected to the overall circuit via $SP$.
We cannot guarantee that all cells will be connected into the circuit via their $SP$s at the same time, so we ues the following strategies to select $SP$s:
\begin{enumerate}[(1)]
    \item Recude the total number of $SP$s selected, when none of the valid circuits can be formed under the current number of $SP$s. 
    \item Calculate each combination on $SP$s one by one to obtain the $\eta$ under the given number of $SP$s. 
\end{enumerate}
We recommend using the dichotomy method to find the right number of selected $SP$s faster in our experience.

% 【总体流程（二分查找）】
% 对于给定结构和最大许用电流通过如下步骤得到：
% （伪代码开始）
% 通过图查找，深度优先，对每个电池找最短路径
% 以二分策略选择考察电池数量N_{select}
% 通过组合，形成C^{N_select}_{N_total}种方式，对于每种方式
% 	仅将选中的电池最短路径上的开关状态设置为1
% 	求解电流，公式
%	检查各电池电流，是否短路或超过电池的最大许用电流（否，break）
% 	给出外电路电流和所有电池电流的最大值，计算比率
% （伪代码结束）
% 电池电流Ib不超过ub/rb，未短路，合法（电池电流Ib受外电路Ro影响，考虑设一个固定值Ibmax，表示电池最大许用电流）
(TODO: this part is rubbish and wait to be revised)
The specific steps for calculating $\max \eta$ of a given RBS architecture $G(V,E)$ are described below:
\begin{enumerate}[\textbf{Step} 1:]
    \item Get $SP_i$(s) for each battery $i\in E_b$ using Depth-First Search.
    \item Get $\bm{A}$ of $G(V,E)$ by Equation \ref{eq:A}.
    \item Determine the number $N_{sel}$ of selected $SP$s: the initial value is $N_b$, after which the value is calculated by dichotomy.
    When $N_{sel}$ is no longer changing, go to \textbf{Step }8.
    \item Select $N_{sel}$ batteries from total $N_b$ for combination, and select the $SP$s of the selected cells for further combination. 
    The set of combinations about $SP_i$s of $N_{sel}$ batteries is denoted as $C_p(N_{sel})$. 
    For all $c_p$s in $C_p(N_{sel})$, determine whether the corresponding circuits meet the requirements and calculate the $\eta$s by the following \textbf{Step }5,6 and 7.
    \item For a $c_p\in C_p(N_{sel})$, let the switch $j$'s state variable be 1 if $j$ in the $c_p$; 0 otherwise. The $\bm{X}$ for the $c_p$ is further obtained by Equation \ref{eq:X}.
    If all $c_p$s in $C_p(N_{sel})$ have been selected, return to \textbf{Step }3.
    \item Calculate $\bm{Y}_n$ by \ref{eq:Yn} and determine whether the $Y_n$ is invertible.
    If so, perform the next step; otherwise, return to \textbf{Step }5 and select another $c_p$.
    \item Calculate output current $I_o$ and batteries's currents $\bm{I}_b$ by Equations \ref{eq:I_o} and \ref{eq:I_b}.
    Check if the max current of batteries $\max(\bm{I}_b)$ exceeds the permissible value $I_m$.
    If it does not exceed, calculate the ratio $I_o/\max(\bm{I}_b)$, i.e. $\eta$; otherwise, return to \textbf{Step }5 and select another $c_p$.
    \item Choose the largest one from all the calculated $\eta$s as the output.
\end{enumerate}

The pseudo-code of the algorithm is as follows:
\begin{algorithm}
    \caption{Get the max currents ratio of a certain RBS}\label{alg:eta_RBS}
    \KwData{Directed graph model $G(V,E)$ of the RBS}
    \KwResult{$\max \eta$}
    \For{$i \in E_b$}{$P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \wedge \text{has the fewest edges $\in E_b$}\}$.}
    get $\bm{A}$ by Equation \ref{eq:A}\;
    \While{not yet determine $\max \eta$ }
        {
            $N_{sel} \leftarrow \text{number of selected $SP$s calculated by dichotomy}$\;
            $C_b    \leftarrow \text{set of all combinations of $N_{sel} $~batteries from $N_b$}$\;
            \For{$c_b \in C_b$}{
                $C_p  \leftarrow \text{set of all combinations of $p_{ij}\in P_i$ from $\{P_i|i\in c_b\}$} $\;
                \For{$c_p \in C_p$}{
                    $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in c_p$ else 0}$\;
                    $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
                    get $\bm{Y}_n$ by Equation \ref{eq:Yn}\;
                    \eIf{$\bm{Y}_n$ is invertible}{
                        get $I_o$ by Equation \ref{eq:I_o}\;
                        get $\bm{I}_b$ by Equation \ref{eq:I_b}\;
                        \eIf{$\max(\bm{I}_b)\leq I_m$}{
                            $\eta \leftarrow I_o/\max(\bm{I}_b)$\;
                        }{break}
                    }{break}
                }
            }
        }
\end{algorithm}

\section{An example and discussions}
% 经典结构
% 建模
% 求解
% 正确性

\section{Conclusion}

\bibliographystyle{ieeetr}
\bibliography{../attachments/my_ref}

\end{document}

### 2023-03-11 max_allowable_current.m

@@ -1,0 +1,56 @@
+function [is_battery_short_circuit, out_current_ideal] = max_allowable_current(switch_state,Ao,Ab,As)
+% function out_current_ideal = max_allowable_current(switch_state,Ao,Ab,As)
+%MAX_ALLOWABLE_CURRENT 此处显示有关此函数的摘要
+% Ao=sparse([1],[1],[-1],7,1);
+% Ab=sparse([3,4,5,6],[1,2,1,2],[1,1,-1,-1],7,2);
+% As=sparse([1,2,2,2,3,3,4,5,6,6,7,7,7],[1,1,2,3,2,4,3,5,4,6,5,6,7],[1,-1,1,1,-1,1,-1,1,-1,1,-1,-1,1]);
+
+Nb=size(Ab,2); % batterys number
+Ns=size(As,2); % switches number
+x=diag([1,ones(1,Nb),switch_state]); % state
+
+% define resistance
+Ro=sym('Ro','positive'); % for out
+rb=sym('rb','positive'); % battery internal resistance
+rs=sym('rs','positive'); % switch resistance
+ub=sym('ub','positive'); % battery electric potential
+% define A
+A=[Ao,Ab,As];
+% define Y and Yn
+yo=1/Ro;
+yb=ones(1,Nb)/rb;
+ys=ones(1,Ns)/rs;
+Y=diag([yo,yb,ys]);
+Y=Y*x; % refine Y by x
+Yn=A*Y*A';
+% define Us
+Us=[0;-ones(Nb,1)*ub;zeros(Ns,1)];
+% define Is and Isn
+Is=zeros(1+Nb+Ns,1);
+Isn=A*Y*Us-A*Is;
+
+% Yn
+% det(Yn)
+Un=Yn\Isn;
+U=A'*Un;
+I=Y*U-Y*Us+Is;
+
+Io=simplify(I(1));
+Ib=simplify(I(2:1+Nb));
+Ib_ideal=subs(Ib,rs,0);
+% whether battery short circuit
+is_battery_short_circuit=0;
+for ib_ideal = Ib_ideal
+    if ib_ideal == ub/rb
+        is_battery_short_circuit=1;
+    end
+end
+% out current
+if Ib_max == 0
+    out_current=0;
+else
+    out_current=simplify(Io/max(Ib));
+end
+out_current_ideal=subs(out_current,rs,0);
+end
+

### 2023-03-11 solve_max_allowable_current.m

@@ -1,0 +1,35 @@
+Ao=sparse([1],[1],[-1],7,1);
+Ab=sparse([3,4,5,6],[1,2,1,2],[1,1,-1,-1],7,2);
+As=sparse([1,2,2,2,3,3,4,5,6,6,7,7,7],[1,1,2,3,2,4,3,5,4,6,5,6,7],[1,-1,1,1,-1,1,-1,1,-1,1,-1,-1,1]);
+A=[Ao Ab As];
+Nb=size(Ab,2); % batterys number
+Ns=size(As,2); % switches number
+Ro=sym('Ro','positive'); % for out
+rb=sym('rb','positive'); % battery internal resistance
+rs=sym('rs','positive'); % switch resistance
+ub=sym('ub','positive'); % battery electric potential
+switch_state=[0,1,1,1,1,1,0];
+x=diag(switch_state);
+Us=[0,-ub*ones(1,Nb),zeros(1,Ns)]';
+Y=diag([1/Ro,ones(1,Nb)/rb,switch_state/rs]);
+Yn=A*Y*A';
+% det(Yn)
+Isn=A*Y*Us;
+Un=Yn\Isn;
+U=A'*Un;
+I=Y*U-Y*Us;
+Io=simplify(I(1));
+Ib=simplify(I(2:Nb+1));
+Io_ideal=subs(Io,rs,0)
+Ib_ideal=subs(Ib,rs,0)
+rate=Io_ideal/my_max(Ib_ideal)
+
+function m=my_max(list)
+    m=list(1);
+    for v = list(2:end)
+        if isAlways(m<v)
+            m=v;
+        end
+    end
+end
+

### 2023-03-11 test.m

@@ -1,0 +1,30 @@
+Ao=sparse([1],[1],[-1],8,1);
+Ab=sparse([3,4,5,6,6,7],[1,2,1,2,3,3],[1,1,-1,-1,1,-1],8,3);
+As=sparse([1,2,2,2,3,4,5,7,8,8,8],[1,1,2,3,2,3,4,5,4,5,6],[1,-1,1,1,-1,-1,1,1,-1,-1,1]);
+A=[Ao Ab As];
+Ro=sym('Ro','positive'); % for out
+rb=sym('rb','positive'); % battery internal resistance
+rs=sym('rs','positive'); % switch resistance
+ub=sym('ub','positive'); % battery electric potential
+% rb=0.1; % battery internal resistance
+% Ro=10; % for out
+% rs=rb*1e-6; % switch resistance
+% ub=3; % battery electric potential
+
+switch_state=[1,1,1,1,1,1];
+x=diag(switch_state);
+Us=[0,-ub*ones(1,3),zeros(1,6)]';
+Ub=[-ub;-ub;-ub];
+Yo=diag(1/Ro);
+Yb=diag([1,1,1]/rb);
+Ys=diag(ones(1,6)/rs)*x;
+Y=diag([1/Ro,ones(1,3)/rb,switch_state/rs]);
+Yn=A*Y*A';
+Isn=A*Y*Us;
+Un=Yn\Isn;
+U=A'*Un;
+I=Y*U-Y*Us;
+Io=simplify(I(1));
+Ib=simplify(I(2:4));
+Io_ideal=subs(Io,rs,0)
+Ib_ideal=subs(Ib,rs,0)

### 2023-03-21 paper/main.tex
modified first two prg in intro and greedy solution; add fig1

@@
 % Battery energy storage systems(BESS) 被用在新能源汽车、风力发电站等场景中，为设备提供高品位电能的保存和释放。
-Battery Energy Storage Systems (BESSs) are used to store and release high quality electrical energy in a timely manner in scenarios such as electric vehicles and wind power turbines.
-A large number of individual battery cells are interconnected in groups by circuitry to form the main body of BESSs and achieve the required capacity and voltage for the application. 
-However, the large number of cells also poses a challenge to the reliability of BESS: capacity and lifetime of the system depends mainly on the least healthy battery cells, known as the cask effect. 
-As the multiple charge/discharge cycles of BESSs exacerbate the inconsistency of individual cells, the unhealthy batteries will appear early in operation.
+Battery Energy Storage Systems (BESSs) are used to store and release high quality electrical energy  in scenarios such as electric vehicles and wind power turbines.
+The main body of BESSs consists of a large number of individual battery cells which are interconnected by series-parallel circuitry to provide the required charge storage capacity and output voltage for application.
+However, the increasing number of cells also poses a challenge to the reliability of BESSs: the system's capacity of energy storage and operation safety mainly  depend on the least healthy battery cells in the body, known as the cask effect.
+In addition, the unhealthy batteries will appear early in operation because the multiple charge/discharge cycles may exacerbate further deterioration of  cells in poor condition.
+For traditional BESSs with fixed circuitry, these limitations and issues cannot be aovided and restrict their practical applications.
 
@@
 % 当前，系统有成百上千的电池，平均每个电池由3~5个开关控制，形成了庞大的状态空间。
-Reconfigurable Battery System (RBS), which can dynamically change the connections between batteries and switch between different circuit configurations as required, is expected to solve the above problem.
-Unlike fixed configurations, reconfigurable circuits have additional switches connected to battery cells in specific topological patterns. 
-Series/parallel switching relationships and even the isolation of unhealthy batteries can be achieved by controlling the states of these switches (open or closed). 
-From the point of view of the battery cells, RBS has a higher reliability than conventional configurable battery systems. 
-However, it also increases the complexity of design and control.
-Each battery in RBS is controlled by an average of 3 to 5 switches. When the system has hundreds or thousands of cells, there is a huge state space waits to solve.
+Reconfigurable Battery System (RBS), which can dynamically  switch between different circuit configurations as required, is expected to solve the above problem. 
+Unlike fixed BESSs, reconfigurable circuits use additional switches to change the series/parallel relationship between batteries.
+Figure 1 illustrates one of the classic architecture proposed by Visairo et al.(ref:18). % #TODO : ref check
+When the longitudinal switches are cloesd and the diagonal switches are open, the batteries are connected in parallel; conversely, they are connected in series.
+And any battery in the Figure can be disconnected to isolated the unhealthy one or to provide redundancy.
+Based on the reconfiguration, RBSs are available to isolated the unhealthy batteries timely and balance the degradation differents between individual cells as required.
+However, the reconfiguration also increases the complexity of system design and control.
+Each battery in RBSs is controlled by an average of 3 to 5 switches according to reported architectures(ref:13-20).
+When the system has hundreds or thousands of cells, there is a huge state space waits to solve.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{../attachments/fig1.png}
+    \caption{The physical model (a), circuit model (b) and figure model(c) of the classic architecture reported by ref. (d) The overall framework of our method.}
+\end{figure}
 
@@
 \section{Method}
-% \subsection{model building}
-
-% Graph model has been uesd in the past to represent the connectivity of batteries in the RBS.
-% In the study by He et al.
-\cite{heExploringAdaptiveReconfiguration2013} the batteries in system are represented as the vertices in the graph, and the connectivity between them are expressed as the edges.
-% \begin{figure}[htbp]
-%     \centering
-%     \includegraphics[width=\textwidth]{../attachments/graph_model.png} % #TODO: redraw figure c
-%     \caption{A typical RBS architecture and its two common graph models. 
-%             (a) RBS architecture \cite{kimDESADependableEfficient2012}, (b) graph model focused on connectivity \cite{heExploringAdaptiveReconfiguration2013}, (c) graph model used in this paper.}
-%     \label{fig:graph_model}
-% \end{figure}
-% Figure \ref{fig:graph_model}(b) illustrates one example of the connectiviy model of a typical RBS architecture(Figure \ref{fig:graph_model}(a)).
-% The additional vertices + and - in the figure represent the cathode and anode of the RBS, respectively, and the directed edges between the neighboring nodes represent the possible flows of current.
-% However, this graph model % 写不下去了，我们的图模型能做的，He 的图模型基本也能做，甚至还要清晰
 
@@
 % 组合，逐一
-If the battery $i$ is connected to the anode $v_1$ and the cathode $v_N$ of the RBS by a certain line with the minimum number of battery cells on the path,
-we call this path the shortest path ($SP_i$) for the battery $i$.
-Since batteries can provide more total current when connected in parallel than in series, $SP_i$ is the path where battery $i$ contributes the most current to the system output.
-Our solution greedily addresses the issue mentioned in the previous subsection: we greedily allow as many cells as possible to be connected to the overall circuit via $SP$.
-We cannot guarantee that all cells will be connected into the circuit via their $SP$s at the same time, so we ues the following strategies to select $SP$s:
-\begin{enumerate}[(1)]
-    \item Recude the total number of $SP$s selected, when none of the valid circuits can be formed under the current number of $SP$s. 
-    \item Calculate each combination on $SP$s one by one to obtain the $\eta$ under the given number of $SP$s. 
-\end{enumerate}
-We recommend using the dichotomy method to find the right number of selected $SP$s faster in our experience.
+First, we define the battery $i$'s shortest path ($SP_i$).
+When the battery $i$ is connected to the anode $v_1$ and the cathode $v_N$ of the RBS by the path $p$ in the graph model, the distance $\omega$ of $p$ is defined by the following equation:
+\begin{equation}
+    \omega(p) = N_s \cdot n_b (p) + n_s (p),
+\end{equation}
+where $N_s$ is the total number of switches in the system; $n_b(p)$ and $n_s(p)$ are number of batteries and switches in the path $p$ respectively.
+$SP_i$ is defined as the path with the minimum $\omega$ for battery $i$.
+According to the definition, $SP_i$ gives the simplest strategy by which the control of battery $i$ is achieved with a minimum of switches while minimising the influence of other batteries.
+From the perspective of series/parallel, the more batteries are connected into circuit via their $SP$s, the more batteries are connected in parallel.
+Since batteries can provide more total output current when connected in parallel than in series, we greedily allow as many cells as possible to be connected into to the overall circuit via their $SP$s to obtain the MAC.
+The dichotomy method is also performed to faster find the right number of $SP$s.
 
@@
 % 电池电流Ib不超过ub/rb，未短路，合法（电池电流Ib受外电路Ro影响，考虑设一个固定值Ibmax，表示电池最大许用电流）
-(TODO: this part is rubbish and wait to be revised)
-The specific steps for calculating $\max \eta$ of a given RBS architecture $G(V,E)$ are described below:
-\begin{enumerate}[\textbf{Step} 1:]
-    \item Get $SP_i$(s) for each battery $i\in E_b$ using Depth-First Search.
-    \item Get $\bm{A}$ of $G(V,E)$ by Equation \ref{eq:A}.
-    \item Determine the number $N_{sel}$ of selected $SP$s: the initial value is $N_b$, after which the value is calculated by dichotomy.
-    When $N_{sel}$ is no longer changing, go to \textbf{Step }8.
-    \item Select $N_{sel}$ batteries from total $N_b$ for combination, and select the $SP$s of the selected cells for further combination. 
-    The set of combinations about $SP_i$s of $N_{sel}$ batteries is denoted as $C_p(N_{sel})$. 
-    For all $c_p$s in $C_p(N_{sel})$, determine whether the corresponding circuits meet the requirements and calculate the $\eta$s by the following \textbf{Step }5,6 and 7.
-    \item For a $c_p\in C_p(N_{sel})$, let the switch $j$'s state variable be 1 if $j$ in the $c_p$; 0 otherwise. The $\bm{X}$ for the $c_p$ is further obtained by Equation \ref{eq:X}.
-    If all $c_p$s in $C_p(N_{sel})$ have been selected, return to \textbf{Step }3.
-    \item Calculate $\bm{Y}_n$ by \ref{eq:Yn} and determine whether the $Y_n$ is invertible.
-    If so, perform the next step; otherwise, return to \textbf{Step }5 and select another $c_p$.
-    \item Calculate output current $I_o$ and batteries's currents $\bm{I}_b$ by Equations \ref{eq:I_o} and \ref{eq:I_b}.
-    Check if the max current of batteries $\max(\bm{I}_b)$ exceeds the permissible value $I_m$.
-    If it does not exceed, calculate the ratio $I_o/\max(\bm{I}_b)$, i.e. $\eta$; otherwise, return to \textbf{Step }5 and select another $c_p$.
-    \item Choose the largest one from all the calculated $\eta$s as the output.
-\end{enumerate}
-
 The pseudo-code of the algorithm is as follows:
 \begin{algorithm}
-    \caption{Get the max currents ratio of a certain RBS}\label{alg:eta_RBS}
+    \caption{Get the max available currents of a certain RBS}\label{alg:eta_RBS}
     \KwData{Directed graph model $G(V,E)$ of the RBS}
     \KwResult{$\max \eta$}
-    \For{$i \in E_b$}{$P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \wedge \text{has the fewest edges $\in E_b$}\}$.}
+    \For{$i \in E_b$}{
+        $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
+        $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
+        }
     get $\bm{A}$ by Equation \ref{eq:A}\;
@@
             \For{$c_b \in C_b$}{
-                $C_p  \leftarrow \text{set of all combinations of $p_{ij}\in P_i$ from $\{P_i|i\in c_b\}$} $\;
-                \For{$c_p \in C_p$}{
-                    $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in c_p$ else 0}$\;
+                % $P_{selected} \leftarrow \bigcup_{i\in c_b}SP_i$\;
+                $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
                 $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
@@
                 }{break}
-                }
             }

### 2023-03-24 paper/main.tex
0324:paper-example, code in my.ipynb

@@
+% 从现在起，你将扮演一位科研工作者，有着丰富的论文写作经验。现在有学生向你请教论文写作的问题。可能会给你一段话，你将这段话用英文润色；也可能是直接请教你一些表达或科技论文的框架。你的最终目的是，指导该学生写出一篇优秀的、可发表的科技论文。
+
 \documentclass{article}
@@
 % Battery energy storage systems(BESS) 被用在新能源汽车、风力发电站等场景中，为设备提供高品位电能的保存和释放。
-Battery Energy Storage Systems (BESSs) are used to store and release high quality electrical energy  in scenarios such as electric vehicles and wind power turbines.
-The main body of BESSs consists of a large number of individual battery cells which are interconnected by series-parallel circuitry to provide the required charge storage capacity and output voltage for application.
-However, the increasing number of cells also poses a challenge to the reliability of BESSs: the system's capacity of energy storage and operation safety mainly  depend on the least healthy battery cells in the body, known as the cask effect.
-In addition, the unhealthy batteries will appear early in operation because the multiple charge/discharge cycles may exacerbate further deterioration of  cells in poor condition.
-For traditional BESSs with fixed circuitry, these limitations and issues cannot be aovided and restrict their practical applications.
+Battery Energy Storage Systems (BESSs) are widely used to store and supply high-quality electrical energy in various applications, including electric vehicles and wind power turbines. 
+Typically, a BESS consists of a large number of battery cells that are interconnected by series-parallel circuitry to provide the required charge storage capacity and output voltage. 
+However, as the number of cells increases, the reliability of the system becomes a major concern. 
+The capacity and safety of the BESS are mainly determined by the least healthy battery cells, a phenomenon known as the cask effect. 
+Furthermore, the degradation of cells in poor condition is accelerated by multiple charge/discharge cycles, which can lead to early failure of the unhealthy cells. 
+These limitations and issues are particularly problematic for traditional BESSs with fixed circuitry, which hinder their practical applications.
 
@@
 Unlike fixed BESSs, reconfigurable circuits use additional switches to change the series/parallel relationship between batteries.
-Figure 1 illustrates one of the classic architecture proposed by Visairo et al.(ref:18). % #TODO : ref check
+Figure 1 illustrates one of the classic architecture proposed by Visairo et al.\cite{visairoReconfigurableBatteryPack2008}.
 When the longitudinal switches are cloesd and the diagonal switches are open, the batteries are connected in parallel; conversely, they are connected in series.
@@
     \caption{The physical model (a), circuit model (b) and figure model(c) of the classic architecture reported by ref. (d) The overall framework of our method.}
+    \label{fig:1}
 \end{figure}
@@
 
-\subsection{circuit model}
+\subsection{graph model and circuit model}
 
@@
         \underbrace{1, 0 \cdots, 1}_{N_s~\text{of}~0/1}
-    ).
+    )
+    =\begin{bmatrix}
+        \bm{I} &\\
+         & \bm{X}_s
+    \end{bmatrix}.
 \end{equation}
@@
 \begin{equation}\label{eq:Yn}
-    \bm{Y}_n (\bm{X}) = \frac{1}{R_o} \bm{A}_o\bm{A}_o^\T + \frac{1}{r_b} \bm{A}_b\bm{A}_b^\T + \frac{1}{r_s}\bm{A}_s\bm{X}\bm{A}_s^\T,
+    \bm{Y}_n (\bm{X}) = \frac{1}{R_o} \bm{A}_o\bm{A}_o^\T + \frac{1}{r_b} \bm{A}_b\bm{A}_b^\T + \frac{1}{r_s}\bm{A}_s\bm{X}_s\bm{A}_s^\T,
 \end{equation}
+% \begin{equation}\label{eq:Yn}
+%     \bm{Y}_n (\bm{X}_s) = \frac{1}{R_o} \bm{A}_o\bm{A}_o^\T + \bm{A}_b \bm{Y}_b \bm{A}_b^\T + \bm{A}_s \bm{Y}_s \bm{X}_s \bm{A}_s^\T
+% \end{equation}
 where $R_o$ is the equivalent resistance of the external circuit.
@@
 \end{align}
+% \begin{align}
+%     I_o(\bm{X}_s)      & = \frac{1}{R_o}\bm{A}_o^\T\bm{Y}_n^{-1}(\bm{X}_s)\bm{A}_b\bm{Y}_b\bm{U}_b;\label{eq:I_o}\\
+%     \bm{I}_b(\bm{X}_s) & = \bm{Y}_b\bm{A}_b^\T\bm{Y}_n^{-1}(\bm{X}_s)\bm{A}_b\bm{Y}_b\bm{U}_b-\bm{Y}_b\bm{U}_b,\label{eq:I_b}
+% \end{align}
 where $\bm{I}_{N_b\times 1}$ is a column vector with all terms being one.
@@
 \section{An example and discussions}
-% 经典结构
-% 建模
-% 求解
-% 正确性
+% 经典结构  visairoReconfigurableBatteryPack2008 验证我们方法的有效性，这个结构的设计目的和应用，我们的验证基于不同规模
+% 建模：物理结构，图模型，电路模型
+% 求解及讨论：模型的正确性，不同规模的效率
+In this section, we evaluate the propoesd algorithm of MAC based on a reconfigurable structure \cite{visairoReconfigurableBatteryPack2008} that has been applied.
+We first build the graph model and equivalent circuit model based on the structure's physical model, as mentioned in section II.
+Then, the accuracy of the result and the efficiency of the algorithm at different scales are discussed.
+
+\subsection{Module building}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{../attachments/fig2.png}
+    \caption{The physical model (a), circuit model (b) and figure model(c) of the reconfigurable architecture propoesd by Visairo \cite{visairoReconfigurableBatteryPack2008}}
+    \label{fig:2}
+\end{figure}
+
+\subsubsection{physical model}
+
+The reconfigurable architecture proposed by Visairo et al.\cite{visairoReconfigurableBatteryPack2008} is shown in Figure \ref{fig:2}(a).
+In this architecture, each cell is controlled by about 3 switches on average.
+Excepted for two switches ($S_1$ and $S_10$ in Figure \ref{fig:2}(a)) controlling the total circuit, the vertical switches (e.g.
+$S_2$ and $S_7$ in Figure \ref{fig:2}(a)) allow the batteries to be directly connected to the main circuit, and the switches($S_5$ for example) in the diagonal direction can realize connecting the batteries in series.
+Thus, it can dynamically change the output voltage and current as needed.
+The architecture in Figure \ref{fig:2}(a) only has 3 batteries, but in practice it can add new branches containing batteries and switches to deal with large-scale batteries.
+
+\subsection{graph model}
+
+Figure \ref{fig:2}(b) shows the graph model based on the physical model, as shown in Figure \ref{fig:2}(a), with rules mentioned in section II.
+This model captures the connection relationship between the batteries and switches, where vertex 1 and 10 represent the anode and cathode of the RBS respectively, and other vertexes represent the nodes connecting batteries and/or switches.
+The directed edges marked 1, 2 and 3 refer to the corresponding batteries.
+And the edges with two opposite directions represent switches.
+Taking the external electrical equipment in the output circuit as a whole, a directed edge segment from $v_1$ to $v_{10}$ can be obtained.
+
+\subsection{circuit model}
+
+According to the assumptions about batteries and switches in section II, an equivalent circuit model can be obtained, as shown in Figure \ref{fig:2}(c).
+Based on Equation \ref{eq:A}, we can get its incidence matrix $\bm{A}$:\
+{\setlength{\arraycolsep}{4pt}
+\begin{equation}
+\begin{array}{cc}
+    &  \begin{array}{c c ccc cccccccccc} & e_o &e_{b1}  &e_{b2} & e_{b3} & e_{s1} & e_{s2} & e_{s3} & e_{s4} & e_{s5} & e_{s6} & e_{s7} & e_{s8} & e_{s9} & e_{s10} \end{array}\\
+        \begin{array}{c} v_1\\v_2\\v_3\\v_4\\v_5\\v_6\\v_7\\v_8\\v_9\end{array} & \left[
+    \begin{array}{c|ccc|cccccccccc}
+        -1  &0 &0 &0   &1 &0 &0 &0 &0 &0 &0 &0 &0 &0\\
+        0   &0 &0 &0   &-1&1 &1 &1 &0 &0 &0 &0 &0 &0\\
+        0   &1 &0 &0   &0 &-1&0 &0 &1 &0 &0 &0 &0 &0\\
+        0   &0 &1 &0   &0 &0 &-1&0 &0 &1 &0 &0 &0 &0\\
+        0   &0 &0 &1   &0 &0 &0 &-1&0 &0 &0 &0 &0 &0\\
+        0   &-1&0 &0   &0 &0 &0 &0 &0 &0 &1 &0 &0 &0\\
+        0   &0 &-1&0   &0 &0 &0 &0 &-1&0 &0 &1 &0 &0\\
+        0   &0 &0 &-1  &0 &0 &0 &0 &0 &-1&0 &0 &1 &0\\
+        0   &0 &0 &0   &0 &0 &0 &0 &0 &0 &-1&-1&-1&1\\
+    \end{array} \right]
+\end{array},
+\end{equation}
+}
+where the rows correspond to vertexes in the graph model, and the first column, second to fourth columns, and last ten columns correspond to external electrical equipment, 3 batteries, and 10 switches, respectively.
+According to the above classification of the columns, the matrix $\bm{A}$ can be divided into $\bm{A}_o$, $\bm{A}_b$, and $\bm{A}_s$.
+
+The state matrix $\bm{X}$ is determined by the switches' state, that is, the specific configuration of the RBS.
+For example, when switch $S_1$, $S_2$, $S_3$, $S_4$ , $S_7$, $S_8$, $S_9$ and $S_{10}$ are closed, and switch $S_5$ and $S_6$ are open, that is , battery $B_1$, $B_2$ and $B_3$ are connected in parallel to supply power to the external circuit, the state matrix $\bm{X}$ is given by
+\begin{equation}
+    \bm{X} = diag(
+        1,  
+        \underbrace{1,1,1}_{\text{batteries}}, 
+        \underbrace{1,1,1,1,0,0,1,1,1,1}_{\text{switches}}
+    ).
+\end{equation}
+
+For the rest of the parameters, such as $R_o$, $r_b$ and $u_b$, this subsection still uses symbols for calculations.
+Their specific value will be explained and discussed at the end of the solution.
+
+\subsection{Module solving and discussing}
 

### 2023-03-25 my_total_MAC.m
matlab for MAC code

@@ -1,0 +1,105 @@
+%% basic setting
+% take care : num_b, s_s, t_s
+
+num_b = 3;
+num_s = 3*num_b+1;
+num_n = 2*num_b+4;
+
+% edge: out
+s_o = num_n;
+t_o = 1;
+weight_o = 10;
+
+% edge: battery
+s_b = 3:(3+num_b-1);
+t_b = (3+num_b):(3+2*num_b-1);
+weight_b = num_s*ones(1,num_b);
+
+% edge: switch TODO:rewrite s_s and t_s
+s_s = [1,2,2,2,3,4,6,7,8,9];
+t_s = [2,3,4,5,7,8,9,9,9,10];
+weight_s = ones(1,num_s);
+
+%% graph model
+
+% edge: total
+s_total = [s_o, s_b, s_s, t_s];
+t_total = [t_o, t_b, t_s, s_s];
+weight_total = [weight_o, weight_b, weight_s, weight_s];
+% G: total
+G_total = digraph(s_total,t_total,weight_total);
+node_pos=[0,0;1,0;1,1;2,1;3,1;1,2;2,2;3,2;1,3;0,3];
+plot(G_total, ...
+    'XData',node_pos(:,1), 'YData',node_pos(:,2), ...
+    'EdgeLabel',G_total.Edges.Weight);
+% get x_s
+x_s = zeros(1,num_s);
+list_of_s = [s_s', t_s'];
+for i=1:num_b
+    % get sp
+    path1 = shortestpath(G_total,1,s_b(i));
+    path2 = shortestpath(G_total,t_b(i),num_n);
+    sp = [path1, path2];
+    % set x_s
+    for j=1:size(list_of_s,1)
+        s = list_of_s(j,:);
+        idx = ismember(sp,s);
+        if any(idx) && any(abs(diff(find(idx))) == 1)
+            x_s(j) = 1;
+        end
+    end
+end
+
+%% circuit model
+
+% edge: degenerate
+s_dege = [s_o, s_b, s_s];
+t_dege = [t_o, t_b, t_s];
+weight_dege = [weight_o, weight_b, weight_s];
+% G and incidence: degenerate
+G_dege = digraph(s_dege,t_dege,weight_dege);
+node_pos=[0,0;1,0;1,1;2,1;3,1;1,2;2,2;3,2;1,3;0,3];
+plot(G_dege, ...
[…]

### 2023-03-26 RBSClass.m
add class (matlab)

@@ -1,0 +1,150 @@
+classdef RBSClass
+    properties
+        num_b
+        num_s
+        num_n
+        node_pos_x
+        node_pos_y
+        s_o
+        t_o
+        weight_o
+        s_b
+        t_b
+        weight_b
+        s_s
+        t_s
+        weight_s
+        G_total
+        SPs
+        G_dege
+        A
+    end
+    methods
+        function rbs = RBSClass(num_b)
+            rbs.num_b = num_b;
+            rbs.num_s = 3*num_b+1;
+            rbs.num_n = 2*num_b+4;
+            % node: positon
+            rbs.node_pos_x = [0,1,1:num_b,1:num_b,1,0];
+            rbs.node_pos_y = [0,0,ones(1,num_b),2*ones(1,num_b),3,3];
+            % edge: out
+            rbs.s_o = rbs.num_n;
+            rbs.t_o = 1;
+            rbs.weight_o= 1+num_b*rbs.num_s+rbs.num_s;
+            % edge: battery
+            rbs.s_b = 3:(3+num_b-1);
+            rbs.t_b = (3+num_b):(3+2*num_b-1);
+            rbs.weight_b = rbs.num_s*ones(1,num_b);
+            % edge: switch 
+            rbs.s_s = [1, 2*ones(1,num_b), ...
+                3:1+num_b, ...
+                3+num_b:2+2*num_b, ...
+                rbs.num_n-1];
+            rbs.t_s = [2, 3:2+num_b, ...
+                4+num_b:2+2*num_b, ...
+                (3+2*num_b)*ones(1,num_b), ...
+                rbs.num_n];
+            rbs.weight_s = ones(1,rbs.num_s);
+            % G for graph
+            rbs.G_total = rbs.get_G_total();
+            % SPs
+            rbs.SPs = rbs.get_SPs();
+            % G for circuit
+            rbs.G_dege = rbs.get_G_dege();
+            % A
+            rbs.A = rbs.get_A();
+        end
+        function G_total = get_G_total(rbs)
+            s_total = [rbs.s_o, rbs.s_b, rbs.s_s, rbs.t_s];
+            t_total = [rbs.t_o, rbs.t_b, rbs.t_s, rbs.s_s];
+            weight_total = [rbs.weight_o, ...
+                rbs.weight_b, ...
+                rbs.weight_s, ...
+                rbs.weight_s];
+            G_total = digraph(s_total,t_total,weight_total);
[…]

### 2023-03-26 my_total_MAC.m

@@ -1,23 +1,27 @@
 %% basic setting
-% take care : num_b, s_s, t_s
+% take care : num_b, s_s, t_s, node_pos_x/y
 
-num_b = 3;
+num_b = 5;
 num_s = 3*num_b+1;
 num_n = 2*num_b+4;
+
+% node: positon
+node_pos_x=[0,1,1:num_b,1:num_b,1,0];
+node_pos_y=[0,0,ones(1,num_b),2*ones(1,num_b),3,3];
 
 % edge: out
 s_o = num_n;
 t_o = 1;
-weight_o = 10;
+weight_o = 1+num_b*num_s+num_s;
 
 % edge: battery
 s_b = 3:(3+num_b-1);
 t_b = (3+num_b):(3+2*num_b-1);
 weight_b = num_s*ones(1,num_b);
 
-% edge: switch TODO:rewrite s_s and t_s
-s_s = [1,2,2,2,3,4,6,7,8,9];
-t_s = [2,3,4,5,7,8,9,9,9,10];
+% edge: switch 
+s_s = [1, 2*ones(1,num_b), 3:1+num_b, 3+num_b:2+2*num_b,num_n-1];
+t_s = [2, 3:2+num_b, 4+num_b:2+2*num_b, (3+2*num_b)*ones(1,num_b), num_n];
 weight_s = ones(1,num_s);
 
 %% graph model
@@ -28,9 +32,9 @@ t_total = [t_o, t_b, t_s, s_s];
 weight_total = [weight_o, weight_b, weight_s, weight_s];
 % G: total
 G_total = digraph(s_total,t_total,weight_total);
-node_pos=[0,0;1,0;1,1;2,1;3,1;1,2;2,2;3,2;1,3;0,3];
+
 plot(G_total, ...
-    'XData',node_pos(:,1), 'YData',node_pos(:,2), ...
+    'XData',node_pos_x, 'YData',node_pos_y, ...
     'EdgeLabel',G_total.Edges.Weight);
 % get x_s
 x_s = zeros(1,num_s);
@@ -58,9 +62,8 @@ t_dege = [t_o, t_b, t_s];
 weight_dege = [weight_o, weight_b, weight_s];
 % G and incidence: degenerate
 G_dege = digraph(s_dege,t_dege,weight_dege);
-node_pos=[0,0;1,0;1,1;2,1;3,1;1,2;2,2;3,2;1,3;0,3];
 plot(G_dege, ...
[…]

### 2023-03-26 solve_max_allowable_current.m

@@ -1,35 +1,0 @@
-Ao=sparse([1],[1],[-1],7,1);
-Ab=sparse([3,4,5,6],[1,2,1,2],[1,1,-1,-1],7,2);
-As=sparse([1,2,2,2,3,3,4,5,6,6,7,7,7],[1,1,2,3,2,4,3,5,4,6,5,6,7],[1,-1,1,1,-1,1,-1,1,-1,1,-1,-1,1]);
-A=[Ao Ab As];
-Nb=size(Ab,2); % batterys number
-Ns=size(As,2); % switches number
-Ro=sym('Ro','positive'); % for out
-rb=sym('rb','positive'); % battery internal resistance
-rs=sym('rs','positive'); % switch resistance
-ub=sym('ub','positive'); % battery electric potential
-switch_state=[0,1,1,1,1,1,0];
-x=diag(switch_state);
-Us=[0,-ub*ones(1,Nb),zeros(1,Ns)]';
-Y=diag([1/Ro,ones(1,Nb)/rb,switch_state/rs]);
-Yn=A*Y*A';
-% det(Yn)
-Isn=A*Y*Us;
-Un=Yn\Isn;
-U=A'*Un;
-I=Y*U-Y*Us;
-Io=simplify(I(1));
-Ib=simplify(I(2:Nb+1));
-Io_ideal=subs(Io,rs,0)
-Ib_ideal=subs(Ib,rs,0)
-rate=Io_ideal/my_max(Ib_ideal)
-
-function m=my_max(list)
-    m=list(1);
-    for v = list(2:end)
-        if isAlways(m<v)
-            m=v;
-        end
-    end
-end
-

### 2023-03-28 paper/main.tex
0329: ,ainbody

@@
 \documentclass{article}
-\usepackage{graphicx} % Required for inserting images
+\usepackage{graphicx}
+\usepackage{subcaption}
 \usepackage{enumerate}
 \usepackage{amsmath}
+\usepackage{multirow}
 \usepackage{bm}
@@
 When the battery $i$ is connected to the anode $v_1$ and the cathode $v_N$ of the RBS by the path $p$ in the graph model, the distance $\omega$ of $p$ is defined by the following equation:
-\begin{equation}
+\begin{equation}\label{eq:weight}
     \omega(p) = N_s \cdot n_b (p) + n_s (p),
@@
                 \eIf{$\bm{Y}_n$ is invertible}{
+                }{construct an effective solution}
                 get $I_o$ by Equation \ref{eq:I_o}\;
@@
                 }{break}
-                }{break}
             }
@@
 
-\section{An example and discussions}
+\section{Examples and discussions}
 % 经典结构  visairoReconfigurableBatteryPack2008 验证我们方法的有效性，这个结构的设计目的和应用，我们的验证基于不同规模
@@
 % 求解及讨论：模型的正确性，不同规模的效率
-In this section, we evaluate the propoesd algorithm of MAC based on a reconfigurable structure \cite{visairoReconfigurableBatteryPack2008} that has been applied.
-We first build the graph model and equivalent circuit model based on the structure's physical model, as mentioned in section II.
-Then, the accuracy of the result and the efficiency of the algorithm at different scales are discussed.
 
-\subsection{Module building}
+% 1. 以f4结构为例，example
+% 描述试验过程，包括物理模型（结构）、图模型（有向图、SP）、电路模型（关联矩阵和状态向量）
+% 描述试验结果，根据求解算法，当SPs取xxx时，电路输出电流达到MAC（图，红色表示开关闭合），各电池电流、输出电流的符号运算结果
+% 讨论结果，关联矩阵A的可逆性讨论；影响输出电流的因素，对MAC定义的讨论，对“许用”的说明；
+% 2. 为进一步说明模型和算法的有效性，我们对不同结构、不同电池规模进行求解
+% a). 在e4、f4、e2f2结构上验证算法有效性
+% b). 在f2、f4、f6、f12 上验证有效性
+% （图）物理模型、求解后模型、求解结果：红色表示开关闭合
+% （图）说明电池数量增加的示意图
+% （表）结构、求解结果（Io，Ibmax，MAC）
+% （表）电池数量、求解结果（Io，Ibmax，MAC）
+% 准确性：算法MAC求解结果与电路定律符合
+% 正确性：模型将电池的物理模型等效为恒压源和电阻，外电路等效为电阻，验证该假设的合理性——分析ub、rb等对结果的影响
+% 3. 该方法的优点和未来改进方向：
+% a) 可以获得电路的所有信息，用于其他可重构电路指标的计算，如输出电压等
+% b) 可对电池等效模型进行修改，如引入电容，分析暂态
 
-\begin{figure}
+In this section, we evaluate the algorithm and models for MAC mentioned earlier, based on some previously reported structures. 
+Firstly, we provide a specific example for the algorithm and models proposed in Section II using the structure proposed by Visairo and discuss the model and computation process.
+Next, we further verify the applicability of our method on RBSs with different structures and sizes. 
+Finally, we highlight the advantages of our method and suggest directions for future improvements.
+
+\subsection{An specific example}
+
+\begin{figure}[htbp]
   \centering
-    \includegraphics[width=\textwidth]{../attachments/fig2.png}
-    \caption{The physical model (a), circuit model (b) and figure model(c) of the reconfigurable architecture propoesd by Visairo \cite{visairoReconfigurableBatteryPack2008}}
-    \label{fig:2}
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{../attachments/f4-phy.png}
+    \caption{}
+    \label{fig:f4-phy}
+  \end{subfigure}
+  \hspace{0.05\textwidth}
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{../attachments/f4-gra.png}
+    \caption{}
+    \label{fig:f4-gra}
+  \end{subfigure}
+  \\
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{../attachments/f-dege-4-modify.png}
+    \caption{}
+    \label{fig:f4-circ}
+  \end{subfigure}
+  \hspace{0.05\textwidth}
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{../attachments/f-dege-mac-4.png}
+    \caption{}
+    \label{fig:f4-mac}
+  \end{subfigure}
+
+  \caption{the physical model (a), circuit model (b) and figure model(c) of the reconfigurable architecture propoesd by visairo \cite{visairoReconfigurableBatteryPack2008}(d) is the result}
+  \label{fig:f4-all}
 \end{figure}
 
-\subsubsection{physical model}
+The reconfigurable architecture proposed by Visairo et al.\cite{visairoReconfigurableBatteryPack2008} is shown in Figure \ref{fig:f4-phy}.
+In this architecture, each cell is controlled by about 3 switches on average.
+Excepted for two switches ($S_1$ and $S_{13}$ in Figure \ref{fig:f4-phy}) controlling the total circuit, the vertical switches (e.g.
+$S_2$ and $S_9$ in Figure \ref{fig:f4-phy}) allow the batteries to be directly connected to the main circuit, and the switches($S_6$ for example) in the diagonal direction can realize connecting the batteries in series.
+Thus, it can dynamically change the output voltage and current as needed.
+The architecture in Figure \ref{fig:f4-phy} only has 4 batteries, but in practice it can add new branches containing batteries and switches to deal with large-scale batteries\cite{kimDependableEfficientScalable2010}.
 
-The reconfigurable architecture proposed by Visairo et al.\cite{visairoReconfigurableBatteryPack2008} is shown in Figure \ref{fig:2}(a).
-In this architecture, each cell is controlled by about 3 switches on average.
-Excepted for two switches ($S_1$ and $S_10$ in Figure \ref{fig:2}(a)) controlling the total circuit, the vertical switches (e.g.
-$S_2$ and $S_7$ in Figure \ref{fig:2}(a)) allow the batteries to be directly connected to the main circuit, and the switches($S_5$ for example) in the diagonal direction can realize connecting the batteries in series.
-Thus, it can dynamically change the output voltage and current as needed.
-The architecture in Figure \ref{fig:2}(a) only has 3 batteries, but in practice it can add new branches containing batteries and switches to deal with large-scale batteries.
+The graph in Figure \ref{fig:f4-gra} represents a graphical model based on the physical model(Figure \ref{fig:f4-phy}). 
+The model is presented in the form of a directed graph, capturing the connection relationship between the battery and switch in the circuit. 
+Vertex 1 and 12 represent the ancode and cathode of the RBS, respectively; 
+the remaining vertices represent the connection nodes between the batteries and switches. 
+Battery 1, 2, 3, and 4 are represented by green directed edges in the graph, while switches are represented by gray directed edges with opposite directions. 
+The external electrical appliance is considered as a directed edge from node 12 to node 1. 
+In the graph model, the directionality of the edges is strictly specified to ensure that there is no reverse flow of current in the battery and external electrical appliance, which could damage the appliance.
 
-\subsection{graph model}
+According to Equation \ref{eq:weight}, the weight of the edge corresponding to the battery is the total number of switches, which is 13; 
+the weight of the edge corresponding to the switch is 1. 
+By setting the weight in this way, on the one hand, it avoids the simultaneous occurrence of multiple batteries in a single SP, weakening the influence between different batteries; 
+on the other hand, it minimizes the number of switches on the path, which means that only a few switches (i.e., the switches on the SP) need to be closed to connect the battery to the main circuit. 
+By using the depth-first search algorithm, the SP of battery 1 can be calculated as the node list $[1, 2, 3, 7, 11, 12]$, and the SPs of the other batteries are shown in Figure \ref{fig:f4-gra}. 
+The SPs provide a basis for selecting variables when solving the MAC through the circuit model in the future.
 
-Figure \ref{fig:2}(b) shows the graph model based on the physical model, as shown in Figure \ref{fig:2}(a), with rules mentioned in section II.
-This model captures the connection relationship between the batteries and switches, where vertex 1 and 10 represent the anode and cathode of the RBS respectively, and other vertexes represent the nodes connecting batteries and/or switches.
-The directed edges marked 1, 2 and 3 refer to the corresponding batteries.
-And the edges with two opposite directions represent switches.
-Taking the external electrical equipment in the output circuit as a whole, a directed edge segment from $v_1$ to $v_{10}$ can be obtained.
-
-\subsection{circuit model}
-
-According to the assumptions about batteries and switches in section II, an equivalent circuit model can be obtained, as shown in Figure \ref{fig:2}(c).
-Based on Equation \ref{eq:A}, we can get its incidence matrix $\bm{A}$:\
-{\setlength{\arraycolsep}{4pt}
+The equivalent circuit model, as shows in Figure \ref{fig:f4-circ}, can be obtained based on the assumptions in Section II. 
+In this model, the batteries and switches are treated as branches, where the battery is regarded as a branch consisting of a voltage source $u_b$ in series with a resistor $r_b$, and the switch is regarded as a branch controlled by a state variable $x_s$ to short or open the circuit.
+Difference from the directed graph model, only one directed edge is used to represent the branch in the circuit, regardless of whether it represents a battery or a switch. 
+The direction of the edge is defined as pointing from the node with the smaller number to the  larger . 
+The direction of the edge is only a preset direction used to calculate the current and voltage. 
+When the computed current or voltage value is negative, it indicates that the direction of the battery or potential difference is opposite to the preset direction. 
+Based on the node-edge relationship in Figure \ref{fig:f4-circ}, the incidence matrix $\bm{A}$: can be obtained according to Equation \ref{eq:A}:
+% {\setlength{\arraycolsep}{4pt}
+% \begin{equation}
+% \begin{array}{cc}
+%     &  \begin{array}{c c ccc cccccccccc} & e_o &e_{b1}  &e_{b2} & e_{b3} & e_{s1} & e_{s2} & e_{s3} & e_{s4} & e_{s5} & e_{s6} & e_{s7} & e_{s8} & e_{s9} & e_{s10} \end{array}\\
+%         \begin{array}{c} v_1\\v_2\\v_3\\v_4\\v_5\\v_6\\v_7\\v_8\\v_9\end{array} & \left[
+%     \begin{array}{c|ccc|cccccccccc}
+%         -1  &0 &0 &0   &1 &0 &0 &0 &0 &0 &0 &0 &0 &0\\
+%         0   &0 &0 &0   &-1&1 &1 &1 &0 &0 &0 &0 &0 &0\\
+%         0   &1 &0 &0   &0 &-1&0 &0 &1 &0 &0 &0 &0 &0\\
+%         0   &0 &1 &0   &0 &0 &-1&0 &0 &1 &0 &0 &0 &0\\
+%         0   &0 &0 &1   &0 &0 &0 &-1&0 &0 &0 &0 &0 &0\\
+%         0   &-1&0 &0   &0 &0 &0 &0 &0 &0 &1 &0 &0 &0\\
+%         0   &0 &-1&0   &0 &0 &0 &0 &-1&0 &0 &1 &0 &0\\
+%         0   &0 &0 &-1  &0 &0 &0 &0 &0 &-1&0 &0 &1 &0\\
+%         0   &0 &0 &0   &0 &0 &0 &0 &0 &0 &-1&-1&-1&1\\
+%     \end{array} \right]
+% \end{array},
+% \end{equation}
+% }
+{\setlength{\arraycolsep}{2pt}
 \begin{equation}
 \begin{array}{cc}
-    &  \begin{array}{c c ccc cccccccccc} & e_o &e_{b1}  &e_{b2} & e_{b3} & e_{s1} & e_{s2} & e_{s3} & e_{s4} & e_{s5} & e_{s6} & e_{s7} & e_{s8} & e_{s9} & e_{s10} \end{array}\\
-        \begin{array}{c} v_1\\v_2\\v_3\\v_4\\v_5\\v_6\\v_7\\v_8\\v_9\end{array} & \left[
-    \begin{array}{c|ccc|cccccccccc}
-        -1  &0 &0 &0   &1 &0 &0 &0 &0 &0 &0 &0 &0 &0\\
-        0   &0 &0 &0   &-1&1 &1 &1 &0 &0 &0 &0 &0 &0\\
-        0   &1 &0 &0   &0 &-1&0 &0 &1 &0 &0 &0 &0 &0\\
-        0   &0 &1 &0   &0 &0 &-1&0 &0 &1 &0 &0 &0 &0\\
-        0   &0 &0 &1   &0 &0 &0 &-1&0 &0 &0 &0 &0 &0\\
-        0   &-1&0 &0   &0 &0 &0 &0 &0 &0 &1 &0 &0 &0\\
-        0   &0 &-1&0   &0 &0 &0 &0 &-1&0 &0 &1 &0 &0\\
-        0   &0 &0 &-1  &0 &0 &0 &0 &0 &-1&0 &0 &1 &0\\
-        0   &0 &0 &0   &0 &0 &0 &0 &0 &0 &-1&-1&-1&1\\
+    &  \begin{array}{c c cccc ccccccccccccc} & e_o &e_{b1}  &e_{b2} & e_{b3} & e_{b4} & e_{s1} & e_{s2} & e_{s3} & e_{s4} & e_{s5} & e_{s6} & e_{s7} & e_{s8} & e_{s9} & e_{s10} & e_{s11} & e_{s12} & e_{s13} \end{array}\\
+        \begin{array}{c} v_1\\v_2\\v_3\\v_4\\v_5\\v_6\\v_7\\v_8\\v_9\\v_{10}\\v_{11}\\v_{12}\end{array} & \left[
+    \begin{array}{c|cccc|ccccccccccccc}
+    -1  &  0  &  0  &  0  &  0  &  1  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0\\
+     0  &  0  &  0  &  0  &  0  & -1  &  1  &  1  &  1  &  1  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0\\
+     0  &  1  &  0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  1  &  0  &  0  &  0  &  0  &  0  &  0  &  0\\
+     0  &  0  &  1  &  0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  1  &  0  &  0  &  0  &  0  &  0  &  0\\
+     0  &  0  &  0  &  1  &  0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  1  &  0  &  0  &  0  &  0  &  0\\
+     0  &  0  &  0  &  0  &  1  &  0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0\\
+     0  & -1  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  1  &  0  &  0  &  0  &  0\\
+     0  &  0  & -1  &  0  &  0  &  0  &  0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  1  &  0  &  0  &  0\\
+     0  &  0  &  0  & -1  &  0  &  0  &  0  &  0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  1  &  0  &  0\\
+     0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  1  &  0\\
+     0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  & -1  & -1  & -1  & -1  &  1\\
     \end{array} \right]
@@
 }
-where the rows correspond to vertexes in the graph model, and the first column, second to fourth columns, and last ten columns correspond to external electrical equipment, 3 batteries, and 10 switches, respectively.
+where the rows correspond to vertexes in the graph model, and the first column, second to fourth columns, and last ten columns correspond to external electrical equipment, 4 batteries, and 13 switches, respectively.
 According to the above classification of the columns, the matrix $\bm{A}$ can be divided into $\bm{A}_o$, $\bm{A}_b$, and $\bm{A}_s$.
@@
 The state matrix $\bm{X}$ is determined by the switches' state, that is, the specific configuration of the RBS.
-For example, when switch $S_1$, $S_2$, $S_3$, $S_4$ , $S_7$, $S_8$, $S_9$ and $S_{10}$ are closed, and switch $S_5$ and $S_6$ are open, that is , battery $B_1$, $B_2$ and $B_3$ are connected in parallel to supply power to the external circuit, the state matrix $\bm{X}$ is given by
+For example, when switch
+% $S_1$, $S_2$, $S_3$, $S_4$ , $S_7$, $S_8$, $S_9$ and $S_{10}$  % for f3
+$S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$ and $S_{13}$ 
+are closed, and switch $S_6$, $S_7$ and $S_8$ are open, that is , battery $B_1$, $B_2$, $B_3$ and $_4$ are connected in parallel to supply power to the external circuit, the state matrix $\bm{X}$ is given by
 \begin{equation}
+%     \bm{X} = diag(
+%         1,  
+%         \underbrace{1,1,1}_{\text{batteries}}, 
+%         \underbrace{1,1,1,1,0,0,1,1,1,1}_{\text{switches}}
+%     ).
     \bm{X} = diag(
         1,  
-        \underbrace{1,1,1}_{\text{batteries}}, 
-        \underbrace{1,1,1,1,0,0,1,1,1,1}_{\text{switches}}
+        \underbrace{1,1,1,1}_{\text{batteries}}, 
+        \underbrace{1,1,1,1,1,0,0,0,1,1,1,1,1}_{\text{switches}}
     ).
@@
 
-For the rest of the parameters, such as $R_o$, $r_b$ and $u_b$, this subsection still uses symbols for calculations.
-Their specific value will be explained and discussed at the end of the solution.
+When using Algorithm 1 to solve the MAC, we may encounter the situation where the matrix $\bm{Y}_n$ is not full rank, and we cannot directly obtain its inverse matrix. 
+This is because some switches are open, causing some branches with voltage sources to be independent of the main circuit and form new circuits. 
+These circuits have infinite possible values for potential difference between them, since they are not connected to each other. 
+In other words, there are theoretically infinite solutions for potential. 
+However, all of these solutions will satisfy the voltage and current laws required by the equation. 
+On the one hand, for the main circuit, since the model specifies node 12 as the reference point for potential at the beginning (i.e., the associated matrix $\bm{A}$ is reduced by one row corresponding to node 12), the submatrix of $\bm{Y}_n$ formed by the edges on the main circuit path must be full rank, so there is no problem as described above.
+On the other hand, since the new circuit is independent of the main circuit, it will not affect the output currents of the main circuit and the battery currents. 
+Therefore, any solution can be used for subsequent calculations.
+Here, we can choose the solution where the potential at the node with the smallest number in the independent branch is 0.
 
-\subsection{Module solving and discussing}
+% MAC of RBS_f(4): 4.00
+% Io_ideal: (4*ub)/(4*Ro + rb)
+% Ib_ideal(1): ub/(4*Ro + rb)
+% Ib_ideal(2): ub/(4*Ro + rb)
+% Ib_ideal(3): ub/(4*Ro + rb)
+% Ib_ideal(4): ub/(4*Ro + rb)
+% those switches are close: 1 2 3 4 5 9 10 11 12 13 
+The final calculation result of $\eta$ for the structure in Figure \ref{fig:f4-phy} is 4. 
+The corresponding currents of output and each battery are shown in Table \ref{tab:1}. 
+The red edges in Figure \ref{fig:f4-mac} represent the closed switches.
+\begin{table}[h]
+    \caption{TODO}
+    \label{tab:1}
+    \begin{tabular}{ccc}
+        \hline
+        output current $I_o$       & battery current $\bm{I}_b$       & $\eta$        \\ 
+        \hline\\
+        $\displaystyle\frac{4u_b}{4R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b}\right]$   & $4.00$ \\ 
+        \\
+        \hline
+    \end{tabular}
+\end{table}
+For this structure, when all batteries are connected to the main circuit through the switches in the vertical direction in Figure \ref{fig:f4-phy} and the batteries are connected in parallel, the output current is maximum, which is the sum of the currents of the four batteries.
+From the specific results of the output current $I_o$ and battery currents $\bm{I}_b$, both are related to the battery voltage $u_b$, internal resistance $r_b$, and external circuit resistance $R_o$. 
+This means that even for the same structure, the output current will change when the external circuit  or the battery specifications  change. 
+By dividing the output current by the sum of the battery currents, we obtain $\eta$, in which the effects of these variables cancel out.
+Thanks to the linearity of the studied structure, when the battery specifications change, the output current also changes proportionally, such as doubling the battery voltage would also double the output current.
+This variable can reflect the characteristics of the structure itself, regardless of the batteries used. 
+Therefore, using $\eta$ as the metric for the MAC is better than using the output current directly.
+
+\subsection{Difference structures and sizes}
+
+To further demonstrate the effectiveness of the model and algorithm, we solve for different structures and RBSs of different sizes.
+
+TODO: 
+% 贪婪算法
+
+\begin{figure}[htbp]
+  \centering
+  \begin{subfigure}[b]{0.3\textwidth}
+    \includegraphics[width=\textwidth]{../attachments/f-dege-mac-4.png}
+    \caption{}
+    \label{fig:f4-mac}
+  \end{subfigure}
+  \hspace{0.05\textwidth}
+  \begin{subfigure}[b]{0.3\textwidth}
+    \includegraphics[width=\textwidth]{../attachments/e-dege-mac-4.png}
+    \caption{}
+    \label{fig:e4-mac}
+  \end{subfigure}
+  \hspace{0.05\textwidth}
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{../attachments/e2f2-dege-mac.png}
+    \caption{}
+    \label{fig:e2f2-mac}
+  \end{subfigure}
+
+  \caption{TODO}
+  \label{fig:d-structure}
+\end{figure}
+
+\begin{table}[h]
+    \caption{TODO}
+    \label{tab:d-structure}
+    \begin{tabular}{cccc}
+        \hline
+        structure &  output current $I_o$       & battery current $\bm{I}_b$       & $\eta$        \\ 
+        \hline\\
+        f &  $\displaystyle\frac{4u_b}{4R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b}\right]$   & $2.00$ \\ 
+        \\
+        e &  $\displaystyle\frac{u_b}{R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{R_o + r_b},0,0,0\right]$   & $4.00$ \\ 
+        \\ 
+        e2f2 &  $\displaystyle\frac{2u_b}{2R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{2R_o + r_b},\frac{u_b}{2R_o + r_b},0,0\right]$   & $6.00$ \\ 
+        \\
+        \hline
+    \end{tabular}
+\end{table}
+
+\begin{figure}[htbp]
+  \centering
+  \begin{subfigure}[b]{0.3\textwidth}
+    \includegraphics[width=\textwidth]{../attachments/f-dege-mac-2.png}
+    \caption{}
+    \label{fig:f2-mac}
+  \end{subfigure}
+  \hspace{0.05\textwidth}
+  \begin{subfigure}[b]{0.3\textwidth}
+    \includegraphics[width=\textwidth]{../attachments/f-dege-mac-4.png}
+    \caption{}
+    \label{fig:f4-mac}
+  \end{subfigure}
+  \hspace{0.05\textwidth}
+  \begin{subfigure}[b]{0.45\textwidth}
+    \includegraphics[width=\textwidth]{../attachments/f-dege-mac-6.png}
+    \caption{}
+    \label{fig:f6-mac}
+  \end{subfigure}
+
+  \caption{TODO}
+  \label{fig:d-sizes}
+\end{figure}
+
+\begin{table}[h]
+    \caption{TODO}
+    \label{tab:d-structure}
+    \begin{tabular}{cccc}
+        \hline
+        size &  output current $I_o$       & battery current $\bm{I}_b$       & $\eta$        \\ 
+        \hline\\
+        2 &  $\displaystyle\frac{2u_b}{2R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{2R_o + r_b},\frac{u_b}{2R_o + r_b},\frac{u_b}{2R_o + r_b},\frac{u_b}{2R_o + r_b}\right]$   & $4.00$ \\ 
+        \\
+        4 &  $\displaystyle\frac{4u_b}{4R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b}\right]$   & $4.00$ \\ 
+        \\
+        6 &  $\displaystyle\frac{6u_b}{6R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{6R_o + r_b},\frac{u_b}{6R_o + r_b},\frac{u_b}{6R_o + r_b},\frac{u_b}{6R_o + r_b}\right]$   & $4.00$ \\ 
+        \\
+        \hline
+    \end{tabular}
+\end{table}
+
+\subsection{Advantages and future improvements}
+
+Our proposed method can obtain comprehensive information about the battery system, including the voltage, current, power, and energy of each battery, as well as the output voltage and current of the system.
+This information can be used for various reconfigurable circuit metrics, such as output voltage regulation, power balancing, and fault diagnosis. 
+By using this method, engineers and researchers can obtain a better understanding of the behavior and performance of battery systems, and optimize their designs and operations accordingly.
+
+To further enhance the usefulness of our method, we can modify the equivalent battery model by introducing capacitance to analyze the transient behavior of the battery system. 
+This modification can capture the dynamic response of the battery system to sudden changes in load or input voltage, and enable more accurate simulations of battery systems under transient conditions.
+By incorporating these models and techniques, we can achieve more accurate and realistic simulations of battery systems, and enable more advanced analysis and design of battery systems.
 
 \section{Conclusion}
+
+In conclusion, we have successfully addressed the problem of estimating the maximum allowable current (MAC) for RBS.
+First, we established a directed graph model to describe the connection relationship between the battery and the switch based on the physical model and solved the shortest path (SP) for the battery to connect to the main circuit.
+Then, we established a circuit model by equivalently representing the battery as a series voltage source and resistance and used switch state variables (X_s) to describe RBS reconstruction.
+Based on a greedy algorithm, we used SP to provide a search strategy for X_s and proposed using the ratio of output current to maximum battery current to describe MAC.
+The effectiveness of this method has been verified on RBS with different structures and scales.
+Our model can provide information on current and voltage in each branch of the circuit and is expandable.
 

### 2023-03-28 RBSClass.m

@@ -14,6 +14,10 @@ classdef RBSClass
         s_s
         t_s
         weight_s
+        Ro=sym('Ro','positive'); % for out
+        rb=sym('rb','positive'); % battery internal resistance
+        rs=sym('rs','positive'); % switch resistance
+        ub=sym('ub','positive'); % battery electric potential
         G_total
         SPs
         G_dege
@@ -63,10 +67,17 @@ classdef RBSClass
                 rbs.weight_s];
             G_total = digraph(s_total,t_total,weight_total);
         end
-        function plot_G_total(rbs)
-            plot(rbs.G_total, ...
+        function p=plot_G_total(rbs)
+            p=plot(rbs.G_total, ...
                 'XData',rbs.node_pos_x, 'YData',rbs.node_pos_y, ...
-                'EdgeLabel',rbs.G_total.Edges.Weight);
+                'LineWidth',2,'EdgeColor','#666666', ...
+                'MarkerSize',5);
+            highlight(p,[rbs.num_n 1],'LineStyle','--')
+            for node=1:length(rbs.s_b)
+                highlight(p,[rbs.s_b(node),rbs.t_b(node)], ...
+                    'EdgeColor','#006837','LineWidth',2);
+            end
+            axis off;
         end
         function SPs = get_SPs(rbs)
             SPs = cell(rbs.num_b,1);
@@ -98,11 +109,31 @@ classdef RBSClass
             weight_dege = [rbs.weight_o, rbs.weight_b, rbs.weight_s];
             G_dege = digraph(s_dege,t_dege,weight_dege);
         end
-        function plot_G_dege(rbs)
-            plot(rbs.G_dege, ...
+        function p=plot_G_dege(rbs)
+            p=plot(rbs.G_dege, ...
                 'XData',rbs.node_pos_x, 'YData',rbs.node_pos_y, ...
-                'EdgeLabel',rbs.G_dege.Edges.Weight);
+                'LineWidth',2,'EdgeColor','#666666', ...
+                'MarkerSize',5);
+            highlight(p,[rbs.num_n 1],'LineStyle','--')
+            for node=1:length(rbs.s_b)
+                highlight(p,[rbs.s_b(node),rbs.t_b(node)], ...
+                    'EdgeColor','#006837','LineWidth',2);
+            end
+            axis off;
         end
+        function p=plot_G_dege_hl_swithch(rbs,x_s)
+            p=rbs.plot_G_dege;
+            for i=1:length(x_s)
+                if x_s(i)
[…]

### 2023-03-28 RBSClass_e.m

@@ -1,0 +1,41 @@
+classdef RBSClass_e < RBSClass
+    properties
+    end
+    methods
+        function rbs = RBSClass_e(num_b)
+            rbs = rbs@RBSClass(num_b);
+            rbs.num_b = num_b;
+            rbs.num_s = 3*num_b+3;
+            rbs.num_n = 3*num_b+4;
+            % node: positon
+            rbs.node_pos_x = [0,repmat([1,2,1],1,num_b),1,2,0];
+            i = 1:num_b;
+            temp = reshape([2*i-2; 2*i-2; 2*i-1], 1, []);
+            rbs.node_pos_y = [0,temp,temp(end)+1,temp(end)+1,temp(end)+1];
+  
+            % edge: out
+            rbs.s_o = rbs.num_n;
+            rbs.t_o = 1;
+            rbs.weight_o= 1+num_b*rbs.num_s+rbs.num_s;
+            % edge: battery
+            rbs.s_b = 4:3:(3*num_b+1);
+            rbs.t_b = 5:3:(3*num_b+2);
+            rbs.weight_b = rbs.num_s*ones(1,num_b);
+            % edge: switch 
+            i = 1:num_b;
+            temp = reshape([3*i-1; 3*i-1; 3*i], 1, []);
+            rbs.s_s = [1, temp, temp(end)+2, temp(end)+2];
+            temp = reshape([3*i; 3*i+1; 3*i+3], 1, []);
+            rbs.t_s = [2, temp, temp(end), temp(end)+1];
+            rbs.weight_s = ones(1,rbs.num_s);
+            % G for graph
+            rbs.G_total = rbs.get_G_total();
+            % SPs
+            rbs.SPs = rbs.get_SPs();
+            % G for circuit
+            rbs.G_dege = rbs.get_G_dege();
+            % A
+            rbs.A = rbs.get_A();
+        end
+    end
+end

### 2023-03-28 RBSClass_e2f2.m

@@ -1,0 +1,37 @@
+classdef RBSClass_e2f2 < RBSClass
+    properties
+    end
+    methods
+        function rbs = RBSClass_e2f2()
+            rbs = rbs@RBSClass(4);
+            num_b = 4;
+            rbs.num_b = num_b;
+            rbs.num_s = 19;
+            rbs.num_n = 18;
+            % node: positon
+            rbs.node_pos_x = [0,2,4,2,1,3,1,3,2,4,2,1,3,1,3,2,4,0];
+            rbs.node_pos_y = [0,0,0,1,2,2,3,3,4,4,5,6,6,7,7,8,8,8];
+  
+            % edge: out
+            rbs.s_o = rbs.num_n;
+            rbs.t_o = 1;
+            rbs.weight_o= 1+num_b*rbs.num_s+rbs.num_s;
+            % edge: battery
+            rbs.s_b = [5,6,12,13];
+            rbs.t_b = [7,8,14,15];
+            rbs.weight_b = rbs.num_s*ones(1,num_b);
+            % edge: switch 
+            rbs.s_s = [1,2,2,3,4,4,5,7,8,9,9,10,11,11,12,14,15,16,16];
+            rbs.t_s = [2,3,4,10,5,6,8,9,9,10,11,17,12,13,15,16,16,17,18];
+            rbs.weight_s = ones(1,rbs.num_s);
+            % G for graph
+            rbs.G_total = rbs.get_G_total();
+            % SPs
+            rbs.SPs = rbs.get_SPs();
+            % G for circuit
+            rbs.G_dege = rbs.get_G_dege();
+            % A
+            rbs.A = rbs.get_A();
+        end
+    end
+end

### 2023-03-28 RBSClass_f.m

@@ -1,0 +1,41 @@
+classdef RBSClass_f < RBSClass
+    properties
+    end
+    methods
+        function rbs = RBSClass_f(num_b)
+            rbs = rbs@RBSClass(num_b);
+            rbs.num_b = num_b;
+            rbs.num_s = 3*num_b+1;
+            rbs.num_n = 2*num_b+4;
+            % node: positon
+            rbs.node_pos_x = [0,1,1:num_b,1:num_b,1,0];
+            rbs.node_pos_y = [0,0,ones(1,num_b),2*ones(1,num_b),3,3];
+            % edge: out
+            rbs.s_o = rbs.num_n;
+            rbs.t_o = 1;
+            rbs.weight_o= 1+num_b*rbs.num_s+rbs.num_s;
+            % edge: battery
+            rbs.s_b = 3:(3+num_b-1);
+            rbs.t_b = (3+num_b):(3+2*num_b-1);
+            rbs.weight_b = rbs.num_s*ones(1,num_b);
+            % edge: switch 
+            rbs.s_s = [1, 2*ones(1,num_b), ...
+                3:1+num_b, ...
+                3+num_b:2+2*num_b, ...
+                rbs.num_n-1];
+            rbs.t_s = [2, 3:2+num_b, ...
+                4+num_b:2+2*num_b, ...
+                (3+2*num_b)*ones(1,num_b), ...
+                rbs.num_n];
+            rbs.weight_s = ones(1,rbs.num_s);
+            % G for graph
+            rbs.G_total = rbs.get_G_total();
+            % SPs
+            rbs.SPs = rbs.get_SPs();
+            % G for circuit
+            rbs.G_dege = rbs.get_G_dege();
+            % A
+            rbs.A = rbs.get_A();
+        end
+    end
+end

### 2023-03-28 main.m

@@ -1,0 +1,78 @@
+delete main.out
+diary('main.out');
+%% RBS-f
+for i = [2,4,6,8]
+    % 创建RBSClass_f对象
+    rbs_f = RBSClass_f(i);
+    % 绘制并保存对象结构
+    path_file = sprintf('.\\attachments\\f-dege-%d.png',i);
+    rbs_f.save_plot(rbs_f.plot_G_dege(),path_file)
+    % 获取MAC和x_s并打印相关信息
+    [mac, x_s] = rbs_f.get_mac();
+    fprintf('MAC of RBS_f(%d): %.2f\n', i, mac)
+    [~,~,Io_ideal,Ib_ideal] = rbs_f.get_current(x_s);
+    fprintf('Io_ideal: %s\n', Io_ideal)
+    for battery=1:i
+        fprintf('Ib_ideal(%d): %s\n',battery, Ib_ideal(battery))
+    end
+    fprintf('those switches are close: ')
+    for j = 1:length(x_s)
+        if (x_s(j)==1)
+            fprintf('%d ',j)
+        end
+    end
+    fprintf('\n\n');
+    % 绘制并保存结果
+    path_file = sprintf('.\\attachments\\f-dege-mac-%d.png',i);
+    rbs_f.save_plot(rbs_f.plot_G_dege_hl_swithch(x_s),path_file)
+end
+
+%% RBS-e
+for i = 2:4
+    % 创建RBSClass_e对象
+    rbs_e = RBSClass_e(i);
+    % 绘制并保存对象结构
+    path_file = sprintf('.\\attachments\\e-dege-%d.png',i);
+    rbs_e.save_plot(rbs_e.plot_G_dege(),path_file)
+    % 获取MAC和x_s并打印相关信息
+    [mac, x_s] = rbs_e.get_mac();
+    fprintf('MAC of RBS_e(%d): %.2f\n', i, mac)
+    [~,~,Io_ideal,Ib_ideal] = rbs_e.get_current(x_s);
+    fprintf('Io_ideal: %s\n', Io_ideal)
+    for battery=1:i
+        fprintf('Ib_ideal(%d): %s\n',battery, Ib_ideal(battery))
+    end
+    fprintf('those switches are close: ')
+    for j = 1:length(x_s)
+        if (x_s(j)==1)
+            fprintf('%d ',j)
+        end
+    end
+    fprintf('\n\n');
[…]

### 2023-03-28 test.m

@@ -1,30 +1,0 @@
-Ao=sparse([1],[1],[-1],8,1);
-Ab=sparse([3,4,5,6,6,7],[1,2,1,2,3,3],[1,1,-1,-1,1,-1],8,3);
-As=sparse([1,2,2,2,3,4,5,7,8,8,8],[1,1,2,3,2,3,4,5,4,5,6],[1,-1,1,1,-1,-1,1,1,-1,-1,1]);
-A=[Ao Ab As];
-Ro=sym('Ro','positive'); % for out
-rb=sym('rb','positive'); % battery internal resistance
-rs=sym('rs','positive'); % switch resistance
-ub=sym('ub','positive'); % battery electric potential
-% rb=0.1; % battery internal resistance
-% Ro=10; % for out
-% rs=rb*1e-6; % switch resistance
-% ub=3; % battery electric potential
-
-switch_state=[1,1,1,1,1,1];
-x=diag(switch_state);
-Us=[0,-ub*ones(1,3),zeros(1,6)]';
-Ub=[-ub;-ub;-ub];
-Yo=diag(1/Ro);
-Yb=diag([1,1,1]/rb);
-Ys=diag(ones(1,6)/rs)*x;
-Y=diag([1/Ro,ones(1,3)/rb,switch_state/rs]);
-Yn=A*Y*A';
-Isn=A*Y*Us;
-Un=Yn\Isn;
-U=A'*Un;
-I=Y*U-Y*Us;
-Io=simplify(I(1));
-Ib=simplify(I(2:4));
-Io_ideal=subs(Io,rs,0)
-Ib_ideal=subs(Ib,rs,0)

### 2023-03-29 paper/main.tex
0329: paper version 2

@@
-% 从现在起，你将扮演一位科研工作者，有着丰富的论文写作经验。现在有学生向你请教论文写作的问题。可能会给你一段话，你将这段话用英文润色；也可能是直接请教你一些表达或科技论文的框架。你的最终目的是，指导该学生写出一篇优秀的、可发表的科技论文。
+% 从现在起，你将扮演一位科研工作者，有着丰富的论文写作经验。现在有学生向你请教论文写作的问题。可能会给你一段话，你将这段话用英文润色；也可能是直接请教你一些表达或科技论文的框架。你的最终目的是，指导该学生写出一篇优秀的、可发表的科技论文。其中一些内容以latex格式存在，你可以选择忽视。
 
@@
 
+\begin{abstract}
+    Traditional battery systems are limited by their dependence on the worst-performing battery cell, which negatively impacts their performance and lifespan.
+    To overcome this limitation, Reconfigurable Battery Systems (RBSs) have emerged as a promising alternative, with the ability to dynamically adjust the circuit configuration to optimize the charging and discharging strategies of battery cells.
+    However, due to their reconfigurability, RBSs require new performance indicators to evaluate their performance.
+    This paper proposes an approach to estimate the Maximum Allowable Current (MAC), which is a crucial indicator for evaluating or optimizing the performance of RBSs.
+    The proposed method utilizes a greedy algorithm based on a graph model and an equivalent circuit model. 
+    By searching for the shortest path for battery cells to connect to the main circuit in the graph model, a greedy search strategy is provided for the equivalent circuit model to describe the switch state variables.
+    We validate the effectiveness of the proposed method on RBS structures of different sizes and configurations. 
+    Our results also show that the ratio of the output current to the maximum battery current could better reflect the structural performance of RBS than the output current alone. 
+\end{abstract}
+
 \section{Introduction}
@@
 % Battery energy storage systems(BESS) 被用在新能源汽车、风力发电站等场景中，为设备提供高品位电能的保存和释放。
-Battery Energy Storage Systems (BESSs) are widely used to store and supply high-quality electrical energy in various applications, including electric vehicles and wind power turbines. 
+Battery Energy Storage Systems (BESSs) are widely used to store and supply high-quality electrical energy in various applications, including electric vehicles and wind power turbines\cite{desiqueiraControlStrategySmooth2021,karandehTwoStageAlgorithmOptimal2019,yangBatteryEnergyStorage2018,choCommercialResearchBattery2015}.
 Typically, a BESS consists of a large number of battery cells that are interconnected by series-parallel circuitry to provide the required charge storage capacity and output voltage. 
@@
 The capacity and safety of the BESS are mainly determined by the least healthy battery cells, a phenomenon known as the cask effect. 
-Furthermore, the degradation of cells in poor condition is accelerated by multiple charge/discharge cycles, which can lead to early failure of the unhealthy cells. 
+Furthermore, the degradation of cells in poor condition is accelerated by multiple charge/discharge cycles, which can lead to early failure of the unhealthy cells\cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019}.
 These limitations and issues are particularly problematic for traditional BESSs with fixed circuitry, which hinder their practical applications.
@@
 % 当前，系统有成百上千的电池，平均每个电池由3~5个开关控制，形成了庞大的状态空间。
-Reconfigurable Battery System (RBS), which can dynamically  switch between different circuit configurations as required, is expected to solve the above problem. 
+Reconfigurable Battery System (RBS), which can dynamically  switch between different circuit configurations as required, is expected to solve the above problem\cite{hanNextGenerationBatteryManagement2020a}.
 Unlike fixed BESSs, reconfigurable circuits use additional switches to change the series/parallel relationship between batteries.
-Figure 1 illustrates one of the classic architecture proposed by Visairo et al.\cite{visairoReconfigurableBatteryPack2008}.
+Figure \ref{fig:1} illustrates one of the classic architecture proposed by Visairo et al.\cite{visairoReconfigurableBatteryPack2008}.
 When the longitudinal switches are cloesd and the diagonal switches are open, the batteries are connected in parallel; conversely, they are connected in series.
 And any battery in the Figure can be disconnected to isolated the unhealthy one or to provide redundancy.
-Based on the reconfiguration, RBSs are available to isolated the unhealthy batteries timely and balance the degradation differents between individual cells as required.
+Based on the reconfiguration, RBSs are available to isolated the unhealthy batteries timely and balance the degradation differences between individual cells as required.
 However, the reconfiguration also increases the complexity of system design and control.
-Each battery in RBSs is controlled by an average of 3 to 5 switches according to reported architectures(ref:13-20).
-When the system has hundreds or thousands of cells, there is a huge state space waits to solve.
+Each battery in RBSs is controlled by an average of 3 to 5 switches according to reported architectures\cite{taesickimSeriesconnectedSelfreconfigurableMulticell2012,heReconfigurationassistedChargingLargescale2014,lawsonSoftwareConfigurableBattery2012,kimBalancedReconfigurationStorage2011,kimDependableEfficientScalable2010}visairoReconfigurableBatteryPack2008.
+When the system has hundreds or thousands of cells, there is a huge value range waits to be solve.
 
@@
     \centering
-    \includegraphics[width=\textwidth]{../attachments/fig1.png}
-    \caption{The physical model (a), circuit model (b) and figure model(c) of the classic architecture reported by ref. (d) The overall framework of our method.}
+    \includegraphics[width=\textwidth]{../attachments/fig1-v2.png}
+    \caption{Diagram of our proposed method.
+It includes a graph model and an equivalent circuit model based on the physical model, and the maximum allowable current is obtained by using a greedy algorithm.}
     \label{fig:1}
@@
 % del: 只针对小数量的电池和特定的结构，不普适（具体文献，容易找到）:led
-The importance of the Maximum Allowable Current (MAC), defined as the maximum current that the system can output to external electrical equipment when the currents of all the batteries in the system do not exceed the specified value, is beginning to be recognised in RBS research.
-From the definition it can be seen that MAC determines the maximum output current of the RBS during normal operation at the design stage and of the reconfigured system when the failed batteries are isolated during the run-in phase.
-MAC is therefore one of the key indicators used in the study for the design and evaluation of RBSs.
-% (#TODO: 一些考虑最大许用电流的构建结构的策略)
-(TODO: Some literature on strategies for RBS that take MAC into account)
-However, none of the existing literature on RBS provides a method for calculating the MAC.
+Maximum Allowable Current (MAC) is a critical parameter in the design and evaluation of reconfigurable battery systems (RBSs). 
+MAC determines the maximum current that the RBS can output to external electrical equipment without exceeding a specified current limit for batteries.
+This parameter is important for ensuring the safe and reliable operation of RBSs during normal operation and when failed batteries are isolated. 
+Despite its importance, existing literature on RBSs does not provide a method for calculating MAC, which poses a challenge for the design and evaluation of these systems.
 
@@
 
+Our main contribution is the development of a mathematical model that describes the problem of calculating the Maximum Allowable Current (MAC) in reconfigurable battery systems (RBSs). 
+As shown in Figure \ref{fig:1}, the graph model is used to describe the structure of the RBS and determine the shortest paths (SPs) of battery connections to the main circuit with minimal cost;
+the circuit model represents the batteries and switches in an actual RBS as equivalent circuit branches that can be processed;
+based on a greedy strategy that selects the SPs to determine the switch state $X_s$, we can solve for the optimal MAC. 
+Our proposed method provides an efficient and effective way to calculate MAC, which can help to improve the design and evaluation of RBSs and ensure their safe and reliable operation in various applications.
+
 % 文章组织：section 2，算法的框架和细节；section 3，案例，讨论和验证；section 4 总结。
 This paper is organized as follows. 
-Section II presents the mathematical model and the algorithm in detail.
-Section III solves an example proposed in \cite{kimDESADependableEfficient2012}and discusses the results. 
-Finally, Section IV provides concluding remarks and directions forjk future work.
+Section II presents the graph model and circuit model, and the algorithm in detail.
+In Section III, we apply the proposed method to solves an example proposed in \cite{kimDESADependableEfficient2012} and further validated its on RBSs of different structures and scales.
+Finally, we provides concluding remarks and discuss potential directions for future work.
 
@@
 
-A typical RBS circuit consists of battery cells and switches.
-We first transform them into ideal components under reasonable assumptions to establish a processable circuit.
-Then the circuit structure is described in matrix form and the related equations are given.
+A typical RBS circuit is composed of battery cells and switches. 
+To establish a processable circuit, we transform these components into ideal elements under reasonable assumptions. 
+The resulting circuit structure is then described in matrix form, and the related equations are provided.
 
@@
 % 推导出输出电流Io和电池电流Ib
-The normal equivalent circuit of a battery consists of a voltage source in series with a resistor, and a capacitor in parallel with another resistor to simulate the polarisation in batteries.
-As the main aim of this research is to calculate the stable MAC offered by a given RBS architecture, only the steady-state behaviour of the circuit is taken into account, while transient effects are ignored in this research.
-Thus, we equate the battery $i$ as a constant voltage source $u_{b,i}$ in series with a resistor $r_{b,i}$.
-A binary variable $x_j$ is used to represent the state of the switch $j$: 0 and 1 mean open and closed respectively.
-To simplify the calculation, the closed switch is considered as a resistor with a very small resistance value $r_s$, which will be treated as zero in the final result.
-In the following derivation, the product of the conductance $1/r_s$ and the variable $x_j$ is used to characterize the state of the switch $j$.
+
+The normal equivalent circuit for a battery consists of a voltage source in series with a resistor, and a capacitor in parallel with another resistor to simulate the polarization in batteries. 
+Since our main objective is to calculate the stable MAC offered by a given RBS architecture, we only consider the steady-state behavior of the circuit, ignoring transient effects. 
+Therefore, we model the battery $i$ as a constant voltage source $u_{b,i}$ in series with a resistor $r_{b,i}$. 
+And we use a binary variable $x_j$ to represent the state of switch $j$, where 0 and 1 indicate open and closed, respectively. 
+To simplify the calculation, we consider a closed switch as a resistor with a very small resistance value $r_s$, which we treat as zero in the final result. 
+In the following derivation, we use the product of the conductance $1/r_s$ and the variable $x_j$ to characterize the state of switch $j$.
 
@@
   \end{subfigure}
-
-  \caption{the physical model (a), circuit model (b) and figure model(c) of the reconfigurable architecture propoesd by visairo \cite{visairoReconfigurableBatteryPack2008}(d) is the result}
+  \caption{ RBS structure proposed by Visairo\cite{visairoReconfigurableBatteryPack2008} with 4 batteries.
+(a) Physical model, (b) graph model, (c) equivalent circuit model, and (d) results obtained by using the proposed method.
+The red highlighted lines indicate the open/close states of switches.}
   \label{fig:f4-all}
@@
 \begin{table}[h]
-    \caption{TODO}
+    \caption{Detailed results of the proposed method for the RBS structure proposed by Visairo\cite{visairoReconfigurableBatteryPack2008} with 4 batteries, including the output current, current of each battery, and $\eta$.}
     \label{tab:1}
@@
 For this structure, when all batteries are connected to the main circuit through the switches in the vertical direction in Figure \ref{fig:f4-phy} and the batteries are connected in parallel, the output current is maximum, which is the sum of the currents of the four batteries.
+The MAC of this structure is correctly estimated by our greedy algorithm.
 From the specific results of the output current $I_o$ and battery currents $\bm{I}_b$, both are related to the battery voltage $u_b$, internal resistance $r_b$, and external circuit resistance $R_o$. 
@@
 
-TODO: 
-% 贪婪算法
-
+Figure \ref{fig:d-structure} illustrates three architectures, each consisting of four batteries with different interconnections.
+Architecture \ref{fig:d-structure-f4}, previously described in the subsection, was proposed by Visairo\cite{visairoReconfigurableBatteryPack2008}. 
+Architecture \ref{fig:d-structure-e4}, proposed by Lawson \cite{lawsonSoftwareConfigurableBattery2012}, allows for the disconnection of any battery to isolate a faulty one or to provide redundancy, and requires significantly fewer switches than \ref{fig:d-structure-e4}.
+Architecture \ref{fig:d-structure-e2f2} is a novel structure obtained by combining the features of both \ref{fig:d-structure-f4} and \ref{fig:d-structure-e4}. 
+The final solution obtained by the greedy algorithm is shown in Figure \ref{fig:d-structure} and summarized in Table \ref{tab:d-structure}.
 \begin{figure}[htbp]
@@
     \caption{}
-    \label{fig:f4-mac}
+    \label{fig:d-structure-f4}
   \end{subfigure}
@@
     \caption{}
-    \label{fig:e4-mac}
+    \label{fig:d-structure-e4}
   \end{subfigure}
@@
     \caption{}
-    \label{fig:e2f2-mac}
+    \label{fig:d-structure-e2f2}
   \end{subfigure}
-
-  \caption{TODO}
+  \caption{Results obstained by our method on (a) structure proposed by Visairo\cite{visairoReconfigurableBatteryPack2008}, (b) structure proposed by Lawson\cite{lawsonSoftwareConfigurableBattery2012}, and (c) structure combining Visairo's and Lawson's structure.
+The red highlighted lines indicate the open/close states of switches.}
   \label{fig:d-structure}
@@
 \begin{table}[h]
-    \caption{TODO}
+    \centering
+    \caption{detailed results of the proposed method for the rbs structure with 4 batteries (a) proposed by visairo\cite{visairoReconfigurableBatteryPack2008}, (b) proposed by lawson\cite{lawsonSoftwareConfigurableBattery2012} and (c) combining both  , including the output current, current of each battery, and $\eta$.}
     \label{tab:d-structure}
@@
         \hline\\
-        f &  $\displaystyle\frac{4u_b}{4R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b}\right]$   & $2.00$ \\ 
+        Visairo\cite{visairoReconfigurableBatteryPack2008} &  $\displaystyle\frac{4u_b}{4R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b}\right]$   & $2.00$ \\
         \\
-        e &  $\displaystyle\frac{u_b}{R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{R_o + r_b},0,0,0\right]$   & $4.00$ \\ 
+        Lawson\cite{lawsonSoftwareConfigurableBattery2012} &  $\displaystyle\frac{u_b}{R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{R_o + r_b},0,0,0\right]$   & $4.00$ \\ 
         \\ 
-        e2f2 &  $\displaystyle\frac{2u_b}{2R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{2R_o + r_b},\frac{u_b}{2R_o + r_b},0,0\right]$   & $6.00$ \\ 
+        combining both &  $\displaystyle\frac{2u_b}{2R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{2R_o + r_b},\frac{u_b}{2R_o + r_b},0,0\right]$   & $6.00$ \\ 
         \\
@@
 \end{table}
+
+Figure \ref{fig:d-size} presents the structures proposed by Visairo \cite{visairoReconfigurableBatteryPack2008} with varying numbers of batteries. 
+We applied our method to solve structures with 2, 4, and 6 batteries, and the results are shown in Figure \ref{fig:d-size} and summarized in Table \ref{tab:d-size}.
 
@@
     \caption{}
-    \label{fig:f2-mac}
+    \label{fig:d-size-2}
   \end{subfigure}
@@
     \caption{}
-    \label{fig:f4-mac}
+    \label{fig:d-size-4}
   \end{subfigure}
@@
     \caption{}
-    \label{fig:f6-mac}
+    \label{fig:d-size-6}
   \end{subfigure}
 
-  \caption{TODO}
-  \label{fig:d-sizes}
+  \caption{Results obstained by our method on structure proposed by Visairo\cite{visairoReconfigurableBatteryPack2008} with (a)2, (b)4 and (c) 6 batteries.
+The red highlighted lines indicate the open/close states of switches.}
+  \label{fig:d-size}
 \end{figure}
@@
 \begin{table}[h]
-    \caption{TODO}
-    \label{tab:d-structure}
+    \caption{detailed results of the proposed method for the rbs structure  proposed by visairo\cite{visairoReconfigurableBatteryPack2008} with (a)2, (b)4 and (c) 6 batteries , including the output current, current of each battery, and $\eta$.}
+    \label{tab:d-size}
     \begin{tabular}{cccc}
@@
         \hline\\
-        2 &  $\displaystyle\frac{2u_b}{2R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{2R_o + r_b},\frac{u_b}{2R_o + r_b},\frac{u_b}{2R_o + r_b},\frac{u_b}{2R_o + r_b}\right]$   & $4.00$ \\ 
+        2 &  $\displaystyle\frac{2u_b}{2R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{2R_o + r_b},\frac{u_b}{2R_o + r_b},\frac{u_b}{2R_o + r_b},\frac{u_b}{2R_o + r_b}\right]$   & $2.00$ \\ 
         \\
@@
         \\
-        6 &  $\displaystyle\frac{6u_b}{6R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{6R_o + r_b},\frac{u_b}{6R_o + r_b},\frac{u_b}{6R_o + r_b},\frac{u_b}{6R_o + r_b}\right]$   & $4.00$ \\ 
+        6 &  $\displaystyle\frac{6u_b}{6R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{6R_o + r_b},\frac{u_b}{6R_o + r_b},\frac{u_b}{6R_o + r_b},\frac{u_b}{6R_o + r_b}\right]$   & $6.00$ \\ 
         \\
@@
 \end{table}
+
+Our greedy algorithm provided accurate estimates of the structure MAC and generated safe and effective switch control strategies, as indicated by the results shown in Figure \ref{fig:d-structure} and \ref{fig:d-size}, where the highlighted red switches denote the closed positions.
+Furthermore, the current solutions obtained from the control strategies in Table \ref{tab:d-structure} and \ref{tab:d-size} show that the output current is influenced by the external circuit resistance, battery potential, and internal resistance, but is linearly related to the battery current, consistent with the conclusion about $\eta$ in the previous subsection.
 
@@
 
-In conclusion, we have successfully addressed the problem of estimating the maximum allowable current (MAC) for RBS.
-First, we established a directed graph model to describe the connection relationship between the battery and the switch based on the physical model and solved the shortest path (SP) for the battery to connect to the main circuit.
-Then, we established a circuit model by equivalently representing the battery as a series voltage source and resistance and used switch state variables (X_s) to describe RBS reconstruction.
-Based on a greedy algorithm, we used SP to provide a search strategy for X_s and proposed using the ratio of output current to maximum battery current to describe MAC.
-The effectiveness of this method has been verified on RBS with different structures and scales.
-Our model can provide information on current and voltage in each branch of the circuit and is expandable.
+In conclusion, we successfully estimated the Maximum Allowable Current (MAC) of the Rechargeable Battery Systems (RBSs), which is an important performance indicator for evaluating the RBSs. 
+We developed both a graph model and a circuit model and used a greedy strategy to solve the MAC. 
+Our method was validated for RBS structures of different sizes and configurations, demonstrating its effectiveness for handling complex models in practice. 
+This work provides an effective approach for designing and evaluating the output current performance of RBS. 
+Our model can be used to obtain current and voltage information for different nodes and branches, and is scalable for larger systems.
+Future work could focus on : 
+a) using current and voltage information to construct new performance indicators for evaluating RBS performance, and 
+b) modifying the equivalent model of the battery for circuit model applications, such as transient analysis.
 

### 2023-03-30 RBSClass.m
fix pic dpi=300

@@ -221,7 +221,9 @@ classdef RBSClass
     end
     methods (Static)
         function save_plot(p, file_name)
-            saveas(p,file_name)
+            % saveas(p,file_name)
+            
+            print(file_name, '-dpng', '-r300')
         end
         function save_fig(p, file_name)
             show(p);

### 2023-03-30 main.m

@@ -1,7 +1,7 @@
 delete main.out
 diary('main.out');
 %% RBS-f
-for i = [2,4,6,8]
+for i = [2,4,6]
     % 创建RBSClass_f对象
     rbs_f = RBSClass_f(i);
     % 绘制并保存对象结构

### 2023-04-12 RBSClass.m
modify fig-main

@@ -70,12 +70,12 @@ classdef RBSClass
         function p=plot_G_total(rbs)
             p=plot(rbs.G_total, ...
                 'XData',rbs.node_pos_x, 'YData',rbs.node_pos_y, ...
-                'LineWidth',2,'EdgeColor','#666666', ...
-                'MarkerSize',5);
+                'LineWidth',2.5,'EdgeColor','#000000', ...
+                'MarkerSize',6);
             highlight(p,[rbs.num_n 1],'LineStyle','--')
             for node=1:length(rbs.s_b)
                 highlight(p,[rbs.s_b(node),rbs.t_b(node)], ...
-                    'EdgeColor','#006837','LineWidth',2);
+                    'EdgeColor','#00a300','LineWidth',3);
             end
             axis off;
         end
@@ -112,12 +112,12 @@ classdef RBSClass
         function p=plot_G_dege(rbs)
             p=plot(rbs.G_dege, ...
                 'XData',rbs.node_pos_x, 'YData',rbs.node_pos_y, ...
-                'LineWidth',2,'EdgeColor','#666666', ...
-                'MarkerSize',5);
+                'LineWidth',3,'EdgeColor','#000000', ...
+                'MarkerSize',6);
             highlight(p,[rbs.num_n 1],'LineStyle','--')
             for node=1:length(rbs.s_b)
                 highlight(p,[rbs.s_b(node),rbs.t_b(node)], ...
-                    'EdgeColor','#006837','LineWidth',2);
+                    'EdgeColor','#00a300','LineWidth',3);
             end
             axis off;
         end
@@ -126,7 +126,7 @@ classdef RBSClass
             for i=1:length(x_s)
                 if x_s(i)
                     highlight(p,[rbs.s_s(i),rbs.t_s(i)], ...
-                        'EdgeColor','#e41a1c','LineWidth',2);
+                        'EdgeColor','#c00000','LineWidth',3);
                 end
             end
             axis off;

### 2023-04-12 main_plot.m

@@ -1,0 +1,8 @@
+rbs = RBSClass_f(4);
+rbs.plot_G_total
+export_fig 'attachments\new-main-2.png' -transparent -m2
+rbs.plot_G_dege
+export_fig 'attachments\new-main-3.png' -transparent -m2
+[mac, x_s] = rbs.get_mac();
+rbs.plot_G_dege_hl_swithch(x_s)
+export_fig 'attachments\new-main-4.png' -transparent -m2

### 2023-04-13 paper/main.tex
plan of modify
modify fig-main
0413: modify based on 0403-discuss

--- 2023-03-24 paper/main.tex
@@
-% 从现在起，你将扮演一位科研工作者，有着丰富的论文写作经验。现在有学生向你请教论文写作的问题。可能会给你一段话，你将这段话用英文润色；也可能是直接请教你一些表达或科技论文的框架。你的最终目的是，指导该学生写出一篇优秀的、可发表的科技论文。
+% 0403 修改要点
+% 1.(need more detail) 原图1 更换实物图、更换风格、对比度，放到method部分
+% 2.(done)新的图1，典型结构的电路图
+% 3.(done)introduction 第二段 RBS 修改（增加的典型结构），列点的形式说明亮点，其余以删除为主
+% 4.(done) method 部分，最开始添一小段，结合原图1介绍流程
+% 5.(done) 第3 section 标题直接改为 examples，只包含：一个详细的结构、不同规模的对比、不同结构的对比，删去展望部分；修改图例，改善图的表示
+% 6.(done) conclusion 重写，包含展望
+% 7.(done)全文主语的修改，逐段润色，caption的修改
+% 8.(done)abstract 修改
+% 9. 转为 word（proref 更新）
+
+% figure 要点
+% (done) fig-arch: e 橙色标记不健康电池，三个闭合的开关
+% (done)f4-gra 标记SP
 
 \documentclass{article}
-\usepackage{graphicx} % Required for inserting images
+\usepackage{graphicx}
+\usepackage{subcaption}
 \usepackage{enumerate}
 \usepackage{amsmath}
+\usepackage{multirow}
 \usepackage{bm}
@@
 
-\title{Greedy-based RBS maximum allowable current calculation method}
+\title{Greedy-based RBS maximum allowable current calculation method} % #TODO: 修改标题
 \author{3057761608 }
@@
 
+\begin{abstract}
+    Reconfigurable Battery Systems (RBSs) offer a promising alternative to traditional battery systems, which are limited by their reliance on the worst-performing cell. 
+    RBSs can dynamically adjust the circuit configuration to optimize battery cell charging and discharging strategies. 
+    However, due to their reconfigurability, RBSs require new performance indicators to evaluate their performance.
+    This paper proposes a method to estimate the Maximum Allowable Current (MAC), a crucial indicator to evaluate RBS performance. 
+    The method employs a greedy algorithm based on a graph model and an equivalent circuit model. 
+    By searching for the shortest path for battery cells to connect to the main circuit in the graph model, a greedy search strategy is provided for the equivalent circuit model to describe the switch state variables.
+    The effectiveness of this method is validated on RBS structures of different sizes and configurations.
+    The results also show that the ratio of the output current to the maximum battery current could better reflect the structural performance of RBS than the output current alone.
+\end{abstract}
+
 \section{Introduction}
 
-% Battery energy storage systems(BESS) 被用在新能源汽车、风力发电站等场景中，为设备提供高品位电能的保存和释放。
-Battery Energy Storage Systems (BESSs) are widely used to store and supply high-quality electrical energy in various applications, including electric vehicles and wind power turbines. 
-Typically, a BESS consists of a large number of battery cells that are interconnected by series-parallel circuitry to provide the required charge storage capacity and output voltage. 
+Battery Energy Storage Systems (BESSs) are widely used to store and supply high-quality electrical energy in various applications, such as electric vehicles and wind power turbines\cite{desiqueiraControlStrategySmooth2021,karandehTwoStageAlgorithmOptimal2019,yangBatteryEnergyStorage2018,choCommercialResearchBattery2015}.
+Typically, a BESS consists of numerous battery cells that are interconnected by series-parallel circuitry to provide the required charge storage capacity and output voltage.
 However, as the number of cells increases, the reliability of the system becomes a major concern.
 The capacity and safety of the BESS are mainly determined by the least healthy battery cells, a phenomenon known as the cask effect.
-Furthermore, the degradation of cells in poor condition is accelerated by multiple charge/discharge cycles, which can lead to early failure of the unhealthy cells. 
-These limitations and issues are particularly problematic for traditional BESSs with fixed circuitry, which hinder their practical applications.
+Furthermore, the degradation of cells in poor condition is accelerated by multiple charge/discharge cycles, which can lead to early failure of the unhealthy cells\cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019}.
+These concerns are particularly problematic for traditional BESSs with fixed circuitry, which limit their practicality.
 
-% 【RBS的先进性、现状】
-% Reconfigurable battery system(RBS) 解决固定电路电池组的 cask effect：系统的容量和寿命取决于状态最差的某些电池。
-% 此外，不一致性也在系统运行中加剧恶化。
-% 通过动态改变电路，调控或隔离不良电池，有助于提升系统整体可靠性。
-% 但是，重构也增加了设计、分析和控制的难度。
-% 当前，系统有成百上千的电池，平均每个电池由3~5个开关控制，形成了庞大的状态空间。
-Reconfigurable Battery System (RBS), which can dynamically  switch between different circuit configurations as required, is expected to solve the above problem. 
+\begin{figure}[htbp]
+    \centering
+    \begin{subfigure}[b]{0.15\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/arch-e.png}
+        \caption{}
+        \label{fig:arch-f}
+    \end{subfigure}
+    \hspace{0.05\textwidth}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/arch-f.png}
+        \caption{}
+        \label{fig:arch-e}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/arch-fe.png}
+        \caption{}
+        \label{fig:arch-ef}
+    \end{subfigure}
+    \caption{The RBS structure proposed by (a)Lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b)Visairo\cite{visairoReconfigurableBatteryPack2008} and (c) synthesized from (a) and (b).}
+    \label{fig:arch}
+\end{figure}
+
+Reconfigurable Battery System (RBS), which can dynamically switch between different circuit configurations as required, is expected to solve the above problem\cite{hanNextGenerationBatteryManagement2020a}.
 Unlike fixed BESSs, reconfigurable circuits use additional switches to change the series/parallel relationship between batteries.
-Figure 1 illustrates one of the classic architecture proposed by Visairo et al.\cite{visairoReconfigurableBatteryPack2008}.
-When the longitudinal switches are cloesd and the diagonal switches are open, the batteries are connected in parallel; conversely, they are connected in series.
-And any battery in the Figure can be disconnected to isolated the unhealthy one or to provide redundancy.
-Based on the reconfiguration, RBSs are available to isolated the unhealthy batteries timely and balance the degradation differents between individual cells as required.
-However, the reconfiguration also increases the complexity of system design and control.
-Each battery in RBSs is controlled by an average of 3 to 5 switches according to reported architectures(ref:13-20).
-When the system has hundreds or thousands of cells, there is a huge state space waits to solve.
+Figure \ref{fig:arch} shows two proposed RBS structures (Figure \ref{fig:arch-e} and Figure \ref{fig:arch-f}), as well as a new structure (Figure \ref{fig:arch-ef}) synthesized from these two structures, all of which can dynamically adjust the connection of the battery as required.
+For instance, in the structure shown in Figure \ref{fig:arch-e} when an unhealthy battery (the orange battery in the figure) exists in the system, the isolation of the battery can be achieved by closing the three adjacent switches marked in the figure and opening the switch below the battery to ensure the reliable operation of the system.
+The structure in Figure \ref{fig:arch-f} is more flexible in terms of controlling system output.
+Its switches can be used to connect the batteries in parallel or in series, thereby enabling the system to vary the system's output current or power.
+By combining those two structures, cell isolation and output control can be easily achieved, as shown in Figure \ref{fig:arch-ef}. 
+Therefore, compared with traditional fixed-structure battery systems, RBS has higher reliability and flexibility. 
+However, due to the existence of more switches and more complex connection methods in RBS, there are more challenges in design, analysis, and control.
+
+Maximum Allowable Current (MAC) is a critical parameter in the design and evaluation of reconfigurable battery systems (RBSs).
+MAC specifies the maximum current that the RBS can output to external electrical equipment without exceeding a specified current limit for batteries.
+This parameter is important for ensuring the safe and reliable operation of RBSs during normal operation and when failed batteries are isolated.
+Despite its importance, there is currently no method in the literature on RBSs for calculating MAC, which poses a challenge for the design and evaluation of these systems.
+
+The purpose of this paper is to propose a universal and effective method for calculating the Maximum Allowable Current (MAC) of RBS. 
+To achieve this, models with RBS connection relationships and component status information are established, and then a greedy algorithm is used to search for MAC.
+This method has the following advantages:
+1. It can effectively calculate MAC for RBSs with different sizes and structures.
+2. A structural indicator is given to characterize the MAC of the structure, which is not affected by batteries and external circuits.
+The paper is structured as follows: 
+Section II presents the framework and details of the algorithm. 
+In Section III, using a specific structure as an example, the application of the method is demonstrated, and the effectiveness of the method on RBS with different structures and sizes is verified. 
+Finally, concluding remarks and future research directions are provided.
+
+\section{Method}
 
@@
     \centering
-    \includegraphics[width=\textwidth]{../attachments/fig1.png}
-    \caption{The physical model (a), circuit model (b) and figure model(c) of the classic architecture reported by ref. (d) The overall framework of our method.}
-    \label{fig:1}
+    \includegraphics[width=\textwidth]{../attachments/main-v4.png}
+    \caption{Diagram of this method. 
+        It includes a graph model and an equivalent circuit model based on the actual RBS.
+        The shortest path of each battery is obstained from the graph model, and the voltage and current of the equivalent circuit model are calculated.
+        By greedily searching for the combination of the shortest path, the MAC is calculated in the equivalent circuit model.
+        } 
+    \label{fig:main}
 \end{figure}
 
-% 【快速评估系统最大电流的作用和意义、文献现状】
-% （一些典型结构、控制策略、评估）
-% 快速评估系统最大允许电流在设计、分析和控制中起到重要作用。
-% 对设计，系统的最大输出电流
-% 对控制，应对故障，静态结构破坏
-% 但是没有严谨研究最大电流。（直接说没有）
-% del: 一些研究使用了过度的简化，不准；（具体文献？）:led
-% del: 只针对小数量的电池和特定的结构，不普适（具体文献，容易找到）:led
-The importance of the Maximum Allowable Current (MAC), defined as the maximum current that the system can output to external electrical equipment when the currents of all the batteries in the system do not exceed the specified value, is beginning to be recognised in RBS research.
-From the definition it can be seen that MAC determines the maximum output current of the RBS during normal operation at the design stage and of the reconfigured system when the failed batteries are isolated during the run-in phase.
-MAC is therefore one of the key indicators used in the study for the design and evaluation of RBSs.
-% (#TODO: 一些考虑最大许用电流的构建结构的策略)
-(TODO: Some literature on strategies for RBS that take MAC into account)
-However, none of the existing literature on RBS provides a method for calculating the MAC.
-
-% 【本文的主要内容和结构】
-% 我们提出了快速估计RBS的算法，基于贪婪策略。填补了这一空白。
-The purpose of this paper is to propose an effective and efficient algorithm based on the greedy search strategy to solve the MAC of RBSs. 
-A mathematical model of MAC is constructed and the optimal solution is searched in the state space of switches using maximising the number of cells directly connected in parallel as the strategy.
-
-% 文章组织：section 2，算法的框架和细节；section 3，案例，讨论和验证；section 4 总结。
-This paper is organized as follows. 
-Section II presents the mathematical model and the algorithm in detail.
-Section III solves an example proposed in \cite{kimDESADependableEfficient2012}and discusses the results. 
-Finally, Section IV provides concluding remarks and directions forjk future work.
-
-\section{Method}
-
+Figure \ref{fig:main} shows the flowchart of our method.
+Firstly, a graph model is abstracted from the actual RBS for finding the shortest path.
+Then, an equivalent circuit model is established based on the graph model for solving the voltage and current in the circuit.
+Finally, by greedily searching for the combination of the shortest path, the MAC is calculated in the equivalent circuit model.
 \subsection{graph model and circuit model}
 
-A typical RBS circuit consists of battery cells and switches.
-We first transform them into ideal components under reasonable assumptions to establish a processable circuit.
-Then the circuit structure is described in matrix form and the related equations are given.
+A typical RBS circuit is composed of battery cells and switches.
+To establish a processable circuit, these components are transformed into ideal elements under reasonable assumptions.
+The resulting circuit structure is then described in matrix form, and the related equations are provided.
 
-% 【电路，有向图，规定，假设】
-% node，连接battery和switch，编号顺序
-% edge，battery 或 switch，编号顺序
-% 电池等效为恒压ub串内阻rb
-% Ro，外电阻
-% 关联矩阵
-% x，开关状态，01变量
-% 【模型，求解方法】
-% 假设均一化，矩阵分块
-% 在导纳矩阵非奇异的条件下
-% 推导出输出电流Io和电池电流Ib
-The normal equivalent circuit of a battery consists of a voltage source in series with a resistor, and a capacitor in parallel with another resistor to simulate the polarisation in batteries.
-As the main aim of this research is to calculate the stable MAC offered by a given RBS architecture, only the steady-state behaviour of the circuit is taken into account, while transient effects are ignored in this research.
-Thus, we equate the battery $i$ as a constant voltage source $u_{b,i}$ in series with a resistor $r_{b,i}$.
-A binary variable $x_j$ is used to represent the state of the switch $j$: 0 and 1 mean open and closed respectively.
-To simplify the calculation, the closed switch is considered as a resistor with a very small resistance value $r_s$, which will be treated as zero in the final result.
-In the following derivation, the product of the conductance $1/r_s$ and the variable $x_j$ is used to characterize the state of the switch $j$.
+The normal equivalent circuit for a battery consists of a voltage source in series with a resistor, and a capacitor in parallel with another resistor to simulate the polarization in batteries.
+To calculate the MAC that can be stablely provided by RBS, only the steady-state behavior of the battery is considered in the model, and transient behavior is ignored.
+Therefore, the battery $i$ is modeled as a constant voltage source $u_{b,i}$ in series with a resistor $r_{b,i}$.
+And a binary variable $x_j$ is used to represent the state of switch $j$, where 0 and 1 indicate open and closed, respectively.
+To simplify the calculation, a closed switch is considered as a resistor with a very small resistance value $r_s$, which are treated as zero in the final result.
+In the following derivation, the product of the conductance $1/r_s$ and the variable $x_j$ is used to characterize the state of switch $j$.
 
-Before obtaining the incidence matrix representing the structure of the circuit, a directed graph model $G(V,E)$ for the RBS is constructed in such a way that
+A directed graph model $G(V,E)$ for the RBS is constructed in such a way that
 \begin{enumerate}[(1)]
-    \item the vertex set $V={v_1,v_2,\cdots,v_N}$ represents the nodes connecting batteries and/or switches, where $v_1$ and $v_N$ represent the anode and cathode of the RBS respectively;
-    \item the directed edge set $E$ represents the output circuit, $N_b$ batteries and $N_s$ switches, corresponding set $E_o$, $E_b$ and $E_s$.
+    \item Nodes: the vertex set $V={v_1,v_2,\cdots,v_N}$ represents the nodes connecting batteries and/or switches, where $v_1$ and $v_N$ represent the anode and cathode of the RBS respectively;
+    \item Edges: the directed edge set $E$ represents the output circuit, $N_b$ batteries and $N_s$ switches, corresponding set $E_o$, $E_b$ and $E_s$.
 The external electrical equipment in the output circuit is treated as one directed edge $v_n \to v_1$.
@@
 \end{align}
-Since each column of $\bm{A}$ sums to zero, we delete the last line and use the reduced incidence matrix $\bm{A}_{(N-1)\times(1+N_b+N_s)}$ in the following calculation.
-y splitting $E$ into $\{E_o, E_b, E_s\}$, $A$ is rewritten as follows
+Since each column of $\bm{A}$ sums to zero, the last line are deleted and the reduced incidence matrix $\bm{A}_{(N-1)\times(1+N_b+N_s)}$ are used in the following calculation.
+By splitting $E$ into $\{E_o, E_b, E_s\}$, $A$ is rewritten as follows
 \begin{equation}
@@
 \end{equation}
-% \begin{equation}\label{eq:Yn}
-%     \bm{Y}_n (\bm{X}_s) = \frac{1}{R_o} \bm{A}_o\bm{A}_o^\T + \bm{A}_b \bm{Y}_b \bm{A}_b^\T + \bm{A}_s \bm{Y}_s \bm{X}_s \bm{A}_s^\T
-% \end{equation}
 where $R_o$ is the equivalent resistance of the external circuit.
@@
 \end{align}
-% \begin{align}
-%     I_o(\bm{X}_s)      & = \frac{1}{R_o}\bm{A}_o^\T\bm{Y}_n^{-1}(\bm{X}_s)\bm{A}_b\bm{Y}_b\bm{U}_b;\label{eq:I_o}\\
-%     \bm{I}_b(\bm{X}_s) & = \bm{Y}_b\bm{A}_b^\T\bm{Y}_n^{-1}(\bm{X}_s)\bm{A}_b\bm{Y}_b\bm{U}_b-\bm{Y}_b\bm{U}_b,\label{eq:I_b}
-% \end{align}
 where $\bm{I}_{N_b\times 1}$ is a column vector with all terms being one.
 
-% 用外电流Ib比所有电池中最大电流max（Ib）之比，表征电路的最大许用输出。是电路结构本身的性质，与电池无关。电路的线性保证了。
-% 目标问题转化为【数学形式】
-% Max rate
-% s.t.
-We use the ratio of $I_o$ and $\max (\bm{I}_b)$ to characterize the allowable current for a given RBS architecture, denoted as $\eta$.
-The $\eta$ reflects the ability of the RBS architecture itself to deliver current, regardliess of the battery cells used by the RBS.
-Due to the linearity of the above circuit model, the output current will vary by the same multiple if the allowable current of all batteries varies by a certain multiple.
-Our problem in RBS can be formulated as
+Here, the ratio of $I_o$ and $\max (\bm{I}_b)$ is used to characterize the maximum allowable current for a given RBS architecture, denoted as $\eta$.
+The discussion in the next section will show that the $\eta$ reflects the ability of the RBS architecture itself to deliver current, regardliess of the battery cells used by the RBS.
+Finally the problem in RBS can be formulated as
 \begin{align}
@@
 where $I_m$ is the maximum allowable current of the battery; $I_o$ and $\bm{I}_b$ can be calculated by Equations \ref{eq:I_o} and \ref{eq:I_b}.
-The presence of the inverse matrix $\bm{Y}_n^{-1}$ prevents us from solving \ref{eq:max_eta} directly, especially when a large number of battery cells and switches are present in the system.
-We therefore propose a greedy algorithm to solve this model.
+However, it is difficult to solve \ref{eq:max_eta} directly because of the presence of matrix $\bm{Y}_n^{-1}$.
+A greedy algorithm is proposed to solve this problem in the next subsection.
 
 \subsection{greedy solution}
-% 使用贪心算法策略求解
-% 【贪心策略】
-% 电池i的最短路径，短指的是路径上电池数量最少
-% 贪心策略，当系统中越多的电池被以最短路径联入电路，外电路电流越大。
-% 短路，检查
-% 组合，逐一
-First, we define the battery $i$'s shortest path ($SP_i$).
+
+First, the battery $i$'s shortest path ($SP_i$) is given here.
 When the battery $i$ is connected to the anode $v_1$ and the cathode $v_N$ of the RBS by the path $p$ in the graph model, the distance $\omega$ of $p$ is defined by the following equation:
-\begin{equation}
+\begin{equation}\label{eq:weight}
     \omega(p) = N_s \cdot n_b (p) + n_s (p),
@@
 From the perspective of series/parallel, the more batteries are connected into circuit via their $SP$s, the more batteries are connected in parallel.
-Since batteries can provide more total output current when connected in parallel than in series, we greedily allow as many cells as possible to be connected into to the overall circuit via their $SP$s to obtain the MAC.
+Since batteries can provide more total output current when connected in parallel than in series, the algorithm greedily selects as many cells as possible to be connected into to the overall circuit via their $SP$s to obtain the MAC.
 The dichotomy method is also performed to faster find the right number of $SP$s.
 
-% 【总体流程（二分查找）】
-% 对于给定结构和最大许用电流通过如下步骤得到：
-% （伪代码开始）
-% 通过图查找，深度优先，对每个电池找最短路径
-% 以二分策略选择考察电池数量N_{select}
-% 通过组合，形成C^{N_select}_{N_total}种方式，对于每种方式
-% 	仅将选中的电池最短路径上的开关状态设置为1
-% 	求解电流，公式
-%	检查各电池电流，是否短路或超过电池的最大许用电流（否，break）
-% 	给出外电路电流和所有电池电流的最大值，计算比率
-% （伪代码结束）
-% 电池电流Ib不超过ub/rb，未短路，合法（电池电流Ib受外电路Ro影响，考虑设一个固定值Ibmax，表示电池最大许用电流）
 The pseudo-code of the algorithm is as follows:
@@
         \For{$c_b \in C_b$}{
-                % $P_{selected} \leftarrow \bigcup_{i\in c_b}SP_i$\;
             $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
@@
             \eIf{$\bm{Y}_n$ is invertible}{
+            }{construct an effective solution}
             get $I_o$ by Equation \ref{eq:I_o}\;
@@
             }{break}
-                }{break}
         }
@@
 
-\section{An example and discussions}
-% 经典结构  visairoReconfigurableBatteryPack2008 验证我们方法的有效性，这个结构的设计目的和应用，我们的验证基于不同规模
-% 建模：物理结构，图模型，电路模型
-% 求解及讨论：模型的正确性，不同规模的效率
-In this section, we evaluate the propoesd algorithm of MAC based on a reconfigurable structure \cite{visairoReconfigurableBatteryPack2008} that has been applied.
-We first build the graph model and equivalent circuit model based on the structure's physical model, as mentioned in section II.
-Then, the accuracy of the result and the efficiency of the algorithm at different scales are discussed.
+\section{Examples}
 
-\subsection{Module building}
+This section verifies the effectiveness of the above model and algorithm on several structures.
+Firstly, the detailed modeling and solving process of a specific RBS structure (proposed by \cite{visairoReconfigurableBatteryPack2008}) with four battery cells is given.
+Then, the effectiveness is verified on RBSs with different structures and sizes.
+This section also explains the advantages of using $\eta$ to characterize MAC.
 
-\begin{figure}
+\subsection{An specific example}
+
+\begin{figure}[htbp]
     \centering
-    \includegraphics[width=\textwidth]{../attachments/fig2.png}
-    \caption{The physical model (a), circuit model (b) and figure model(c) of the reconfigurable architecture propoesd by Visairo \cite{visairoReconfigurableBatteryPack2008}}
-    \label{fig:2}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/f4-phy.png}
+        \caption{}
+        \label{fig:f4-phy}
+    \end{subfigure}
+    \hspace{0.05\textwidth}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/v3-new-main-2.png}
+        \caption{}
+        \label{fig:f4-gra}
+    \end{subfigure}
+    \\
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/f-dege-4-modify.png}
+        \caption{}
+        \label{fig:f4-circ}
+    \end{subfigure}
+    \hspace{0.05\textwidth}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/f-dege-mac-4.png}
+        \caption{}
+        \label{fig:f4-mac}
+    \end{subfigure}
+    \caption{ 
+        RBS structure proposed by Visairo\cite{visairoReconfigurableBatteryPack2008} with 4 batteries. 
+        (a) Physical model, (b) graph model, (c) equivalent circuit model, and (d) results obtained by using the proposed method.
+        The blue highlighted lines indicate the SPs. 
+        The red highlighted lines indicate the open/close states of switches.
+        }
+    \label{fig:f4-all}
 \end{figure}
 
-\subsubsection{physical model}
+The reconfigurable architecture proposed by Visairo et al.\cite{visairoReconfigurableBatteryPack2008} is shown in Figure \ref{fig:f4-phy}.
+In this architecture, each cell is controlled by about 3 switches on average.
+Excepted for two switches ($S_1$ and $S_{13}$ in Figure \ref{fig:f4-phy}) controlling the total circuit, the vertical switches (e.g.
+$S_2$ and $S_9$ in Figure \ref{fig:f4-phy}) allow the batteries to be directly connected to the main circuit, and the switches($S_6$ for example) in the diagonal direction can realize connecting the batteries in series.
+Thus, it can dynamically change the output voltage and current as needed.
+The architecture in Figure \ref{fig:f4-phy} only has 4 batteries, but in practice it can add new branches containing batteries and switches to deal with large-scale batteries\cite{kimDependableEfficientScalable2010}.
 
-The reconfigurable architecture proposed by Visairo et al.\cite{visairoReconfigurableBatteryPack2008} is shown in Figure \ref{fig:2}(a).
-In this architecture, each cell is controlled by about 3 switches on average.
-Excepted for two switches ($S_1$ and $S_10$ in Figure \ref{fig:2}(a)) controlling the total circuit, the vertical switches (e.g.
-$S_2$ and $S_7$ in Figure \ref{fig:2}(a)) allow the batteries to be directly connected to the main circuit, and the switches($S_5$ for example) in the diagonal direction can realize connecting the batteries in series.
-Thus, it can dynamically change the output voltage and current as needed.
-The architecture in Figure \ref{fig:2}(a) only has 3 batteries, but in practice it can add new branches containing batteries and switches to deal with large-scale batteries.
+The graph in Figure \ref{fig:f4-gra} represents a graphical model based on the physical model(Figure \ref{fig:f4-phy}).
+The model is presented in the form of a directed graph, capturing the connection relationship between the battery and switch in the circuit.
+Vertex 1 and 12 represent the ancode and cathode of the RBS, respectively;
+the remaining vertices represent the connection nodes between the batteries and switches.
+Battery 1, 2, 3, and 4 are represented by green directed edges in the graph, while switches are represented by gray directed edges with opposite directions.
+The external electrical appliance is considered as a directed edge from node 12 to node 1.
+In the graph model, the directionality of the edges is strictly specified to ensure that there is no reverse flow of current in the battery and external electrical appliance.
 
-\subsection{graph model}
+According to Equation \ref{eq:weight}, the weight of the edge corresponding to the battery is the total number of switches, which is 13;
+the weight of the edge corresponding to the switch is 1.
+By setting the weight in this way, on the one hand, it avoids the simultaneous occurrence of multiple batteries in a single SP, weakening the influence between different batteries;
+on the other hand, it minimizes the number of switches on the path, which means that only a few switches (i.e., the switches on the SP) need to be closed to connect the battery to the main circuit.
+By using the depth-first search algorithm, the SP of battery 1 can be calculated as the node list $[1, 2, 3, 7, 11, 12]$, and the SPs of the other batteries are shown in Figure \ref{fig:f4-gra}.
 
-Figure \ref{fig:2}(b) shows the graph model based on the physical model, as shown in Figure \ref{fig:2}(a), with rules mentioned in section II.
-This model captures the connection relationship between the batteries and switches, where vertex 1 and 10 represent the anode and cathode of the RBS respectively, and other vertexes represent the nodes connecting batteries and/or switches.
-The directed edges marked 1, 2 and 3 refer to the corresponding batteries.
-And the edges with two opposite directions represent switches.
-Taking the external electrical equipment in the output circuit as a whole, a directed edge segment from $v_1$ to $v_{10}$ can be obtained.
-
-\subsection{circuit model}
-
-According to the assumptions about batteries and switches in section II, an equivalent circuit model can be obtained, as shown in Figure \ref{fig:2}(c).
-Based on Equation \ref{eq:A}, we can get its incidence matrix $\bm{A}$:\
-{\setlength{\arraycolsep}{4pt}
+The equivalent circuit model, as shows in Figure \ref{fig:f4-circ}, can be obtained based on the assumptions in Section II.
+In this model, the batteries and switches are treated as branches, where the battery is regarded as a branch consisting of a voltage source $u_b$ in series with a resistor $r_b$, and the switch is regarded as a branch controlled by a state variable $x_s$ to short or open the circuit.
+The branches are represented as direction edges, whose direction is from the node with the smaller number to the larger. 
+When the computed current or voltage value is negative, it indicates that the direction of the battery or potential difference is opposite to the preset direction.
+Based on the node-edge relationship in Figure \ref{fig:f4-circ}, the incidence matrix $\bm{A}$: can be obtained according to Equation \ref{eq:A}:
+{\setlength{\arraycolsep}{2pt}
 \begin{equation}
     \begin{array}{cc}
-    &  \begin{array}{c c ccc cccccccccc} & e_o &e_{b1}  &e_{b2} & e_{b3} & e_{s1} & e_{s2} & e_{s3} & e_{s4} & e_{s5} & e_{s6} & e_{s7} & e_{s8} & e_{s9} & e_{s10} \end{array}\\
-        \begin{array}{c} v_1\\v_2\\v_3\\v_4\\v_5\\v_6\\v_7\\v_8\\v_9\end{array} & \left[
-    \begin{array}{c|ccc|cccccccccc}
-        -1  &0 &0 &0   &1 &0 &0 &0 &0 &0 &0 &0 &0 &0\\
-        0   &0 &0 &0   &-1&1 &1 &1 &0 &0 &0 &0 &0 &0\\
-        0   &1 &0 &0   &0 &-1&0 &0 &1 &0 &0 &0 &0 &0\\
-        0   &0 &1 &0   &0 &0 &-1&0 &0 &1 &0 &0 &0 &0\\
-        0   &0 &0 &1   &0 &0 &0 &-1&0 &0 &0 &0 &0 &0\\
-        0   &-1&0 &0   &0 &0 &0 &0 &0 &0 &1 &0 &0 &0\\
-        0   &0 &-1&0   &0 &0 &0 &0 &-1&0 &0 &1 &0 &0\\
-        0   &0 &0 &-1  &0 &0 &0 &0 &0 &-1&0 &0 &1 &0\\
-        0   &0 &0 &0   &0 &0 &0 &0 &0 &0 &-1&-1&-1&1\\
+        &  \begin{array}{c c cccc ccccccccccccc} & e_o &e_{b1}  &e_{b2} & e_{b3} & e_{b4} & e_{s1} & e_{s2} & e_{s3} & e_{s4} & e_{s5} & e_{s6} & e_{s7} & e_{s8} & e_{s9} & e_{s10} & e_{s11} & e_{s12} & e_{s13} \end{array}\\
+            \begin{array}{c} v_1\\v_2\\v_3\\v_4\\v_5\\v_6\\v_7\\v_8\\v_9\\v_{10}\\v_{11}\\v_{12}\end{array} & \left[
+                    \begin{array}{c|cccc|ccccccccccccc}
+                        -1  &  0  &  0  &  0  &  0  &  1  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0\\
+                        0  &  0  &  0  &  0  &  0  & -1  &  1  &  1  &  1  &  1  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0\\
+                        0  &  1  &  0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  1  &  0  &  0  &  0  &  0  &  0  &  0  &  0\\
+                        0  &  0  &  1  &  0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  1  &  0  &  0  &  0  &  0  &  0  &  0\\
+                        0  &  0  &  0  &  1  &  0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  1  &  0  &  0  &  0  &  0  &  0\\
+                        0  &  0  &  0  &  0  &  1  &  0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0\\
+                        0  & -1  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  1  &  0  &  0  &  0  &  0\\
+                        0  &  0  & -1  &  0  &  0  &  0  &  0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  1  &  0  &  0  &  0\\
+                        0  &  0  &  0  & -1  &  0  &  0  &  0  &  0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  1  &  0  &  0\\
+                        0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  1  &  0\\
+                        0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  & -1  & -1  & -1  & -1  &  1\\
                     \end{array} \right]
@@
 The state matrix $\bm{X}$ is determined by the switches' state, that is, the specific configuration of the RBS.
-For example, when switch $S_1$, $S_2$, $S_3$, $S_4$ , $S_7$, $S_8$, $S_9$ and $S_{10}$ are closed, and switch $S_5$ and $S_6$ are open, that is , battery $B_1$, $B_2$ and $B_3$ are connected in parallel to supply power to the external circuit, the state matrix $\bm{X}$ is given by
+For example, when switch
+$S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$ and $S_{13}$
+are closed, and switch $S_6$, $S_7$ and $S_8$ are open, that is , battery $B_1$, $B_2$, $B_3$ and $_4$ are connected in parallel to supply power to the external circuit, the state matrix $\bm{X}$ is given by
 \begin{equation}
@@
     1,
-        \underbrace{1,1,1}_{\text{batteries}}, 
-        \underbrace{1,1,1,1,0,0,1,1,1,1}_{\text{switches}}
+    \underbrace{1,1,1,1}_{\text{batteries}},
+    \underbrace{1,1,1,1,1,0,0,0,1,1,1,1,1}_{\text{switches}}
     ).
@@
 
-For the rest of the parameters, such as $R_o$, $r_b$ and $u_b$, this subsection still uses symbols for calculations.
-Their specific value will be explained and discussed at the end of the solution.
+When using the algorithm to solve the MAC, one may encounter the situation where the matrix $\bm{Y}_n$ is not full rank, and its inverse matrix cannot directly be obtained.
+This is because so many switches are open that some branches with voltage sources are independent of the main circuit and form new circuits.
+These circuits have infinite possible values for potential difference between them, since they are not connected to each other.
+But the potential of the main circuit, which connects from node 1 to node 12 and completely determines the output, is certain and unique.
+Therefore, the non-invertibility of $\bm{Y}_n$ will not affect the final solution.
+Here, one can choose the solution where the potential at the node with the smallest number in the independent branch is 0.
 
-\subsection{Module solving and discussing}
+\begin{table}[h]
+    \caption{Detailed results of the proposed method for the RBS structure proposed by Visairo\cite{visairoReconfigurableBatteryPack2008} with 4 batteries, including the output current, current of each battery, and $\eta$.}
+    \label{tab:1}
+    \begin{tabular}{ccc}
+        \hline
+        output current $I_o$       & battery current $\bm{I}_b$       & $\eta$        \\
+        \hline\\
+        $\displaystyle\frac{4u_b}{4R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b}\right]$   & $4.00$ \\
+        \\
+        \hline
+    \end{tabular}
+\end{table}
+The final calculation result of $\eta$ for the structure in Figure \ref{fig:f4-phy} is 4.
+The corresponding currents of output and each battery are shown in Table \ref{tab:1}.
+The corresponding switch control strategy is: $S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$ and $S_{13}$ are closed (highlighted in red in Figure \ref{fig:f4-mac}), and $S_6$, $S_7$ and $S_8$ are open.
+For this structure, when all batteries are connected to the main circuit through the switches in the vertical direction in Figure \ref{fig:f4-phy} and the batteries are connected in parallel, the output current is maximum, which is the sum of the currents of the four batteries.
+The MAC of this structure is correctly estimated by our greedy algorithm.
+
+From the specific results of the output current $I_o$ and battery currents $\bm{I}_b$, both are related to the battery voltage $u_b$, internal resistance $r_b$, and external circuit resistance $R_o$.
+This means that even for the same structure, the output current will change when the external circuit  or the battery specifications  change.
+By dividing the output current by the sum of the battery currents, the obtained $\eta$ does not include items affected by external circuit and batteries.
+This characteristic is guaranteed by the linear nature of the RBS circuit.
+
+\subsection{Different structures and sizes}
+
+To further demonstrate the effectiveness of the models and algorithm, RBSs with different structures and sizes are considered.
+On the one hand, the modeling and solving of the three battery structures in Figure \ref{fig:arch} are carried out, where the structure in Figure \ref{fig:arch-e} is proposed by Visairo\cite{visairoReconfigurableBatteryPack2008}, the structure in Figure \ref{fig:arch-f} is proposed by Lawson\cite{lawsonSoftwareConfigurableBattery2012}, and the structure in Figure \ref{fig:arch-ef} is a combination of the two.
+All three structures have 4 battery cells.
+On the other hand, the modeling and solving of the battery structures proposed by Visairo\cite{visairoReconfigurableBatteryPack2008} with different numbers of battery cells (2, 4, and 6 cells) are also carried out.
+
+The greedy algorithm provided accurate estimates of the structure MAC and generated safe and effective switch control strategies, as indicated by the results shown in Figure \ref{fig:d-structure} and \ref{fig:d-size}, where the highlighted red switches denote the closed positions.
+Furthermore, the results about currents in Table \ref{tab:d-structure} and \ref{tab:d-size} show that the output currents are influenced by the external circuit resistance, battery potential, and internal resistance, but are linearly related to the battery currents, consistent with the conclusion about $\eta$ in the previous subsection.
+
+\begin{figure}[htbp]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/e-dege-mac-4.png}
+        \caption{}
+        \label{fig:d-structure-f4}
+    \end{subfigure}
+    \hspace{0.05\textwidth}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/f-dege-mac-4.png}
+        \caption{}
+        \label{fig:d-structure-e4}
+    \end{subfigure}
+    \hspace{0.05\textwidth}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/e2f2-dege-mac.png}
+        \caption{}
+        \label{fig:d-structure-e2f2}
+    \end{subfigure}
+    \caption{
+        The switches state when the output current is MAC on structure (a) proposed by Lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b) proposed by Visairo\cite{visairoReconfigurableBatteryPack2008}, and (c) combining  Lawson's and Visairo's structure.
+        The red highlighted lines indicate the open/close states of switches.
+        }
+    \label{fig:d-structure}
+\end{figure}
+
+\begin{table}[h]
+    \centering
+    \caption{
+        detailed results of the proposed method for the RBS with 4 batteries (a) proposed by lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b) proposed by  visairo\cite{visairoReconfigurableBatteryPack2008} and (c) combining both  , including the output current, current of each battery, and $\eta$.}
+    \label{tab:d-structure}
+    \begin{tabular}{cccc}
+        \hline
+        structure &  output current $I_o$       & battery current $\bm{I}_b$       & $\eta$        \\
+        \hline\\
+        Lawson\cite{lawsonSoftwareConfigurableBattery2012} &  $\displaystyle\frac{u_b}{R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{R_o + r_b},0,0,0\right]$   & $1.00$ \\
+        \\
+        Visairo\cite{visairoReconfigurableBatteryPack2008} &  $\displaystyle\frac{4u_b}{4R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b}\right]$   & $4.00$ \\
+        \\
+        combining both &  $\displaystyle\frac{2u_b}{2R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{2R_o + r_b},\frac{u_b}{2R_o + r_b},0,0\right]$   & $2.00$ \\
+        \\
+        \hline
+    \end{tabular}
+\end{table}
+
+\begin{figure}[htbp]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/f-dege-mac-2.png}
+        \caption{}
+        \label{fig:d-size-2}
+    \end{subfigure}
+    \hspace{0.05\textwidth}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/f-dege-mac-4.png}
+        \caption{}
+        \label{fig:d-size-4}
+    \end{subfigure}
+    \hspace{0.05\textwidth}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/f-dege-mac-6.png}
+        \caption{}
+        \label{fig:d-size-6}
+    \end{subfigure}
+    \caption{
+        The switches state when the output current is MAC on structure proposed by Visairo\cite{visairoReconfigurableBatteryPack2008} with (a)2, (b)4 and (c) 6 batteries.  
+        The red highlighted lines indicate the open/close states of switches.
+        }
+    \label{fig:d-size}
+\end{figure}
+
+\begin{table}[h]
+    \caption{detailed results of the proposed method for the RBS proposed by visairo\cite{visairoReconfigurableBatteryPack2008} with (a)2, (b)4 and (c) 6 batteries , including the output current, current of each battery, and $\eta$.}
+    \label{tab:d-size}
+    \begin{tabular}{cccc}
+        \hline
+        size &  output current $I_o$       & battery current $\bm{I}_b$       & $\eta$        \\
+        \hline\\
+        2 &  $\displaystyle\frac{2u_b}{2R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{2R_o + r_b},\frac{u_b}{2R_o + r_b},\frac{u_b}{2R_o + r_b},\frac{u_b}{2R_o + r_b}\right]$   & $2.00$ \\
+        \\
+        4 &  $\displaystyle\frac{4u_b}{4R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b}\right]$   & $4.00$ \\
+        \\
+        6 &  $\displaystyle\frac{6u_b}{6R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{6R_o + r_b},\frac{u_b}{6R_o + r_b},\frac{u_b}{6R_o + r_b},\frac{u_b}{6R_o + r_b}\right]$   & $6.00$ \\
+        \\
+        \hline
+    \end{tabular}
+\end{table}
 
 \section{Conclusion}
+
+A graph model and a circuit model were developed, and a greedy strategy was employed to solve the MAC. 
+The proposed method was tested on RBSs of varying structures and sizes. 
+Additionally, an indicator, denoted by $\eta$ , was introduced to evaluate the performance of the RBS's output current. 
+This work presents an effective approach for designing and evaluating the output current performance of RBS. 
+Future research could focus on developing new performance indicators for evaluating RBS performance using the currents and voltages obtained by this method, as well as modifying the equivalent model of the battery to enable more accurate simulations of RBS, including transient analysis.
 

### 2023-04-13 RBSClass.m

@@ -223,7 +223,9 @@ classdef RBSClass
         function save_plot(p, file_name)
             % saveas(p,file_name)
             
-            print(file_name, '-dpng', '-r300')
+            % print(file_name, '-dpng', '-r300')
+            cmd = sprintf('export_fig %s -transparent -m2',file_name);
+            eval(cmd);
         end
         function save_fig(p, file_name)
             show(p);

### 2023-04-13 main_plot.m

@@ -1,8 +1,8 @@
 rbs = RBSClass_f(4);
 rbs.plot_G_total
-export_fig 'attachments\new-main-2.png' -transparent -m2
+export_fig 'attachments\f4-gra.png' -transparent -m2
 rbs.plot_G_dege
-export_fig 'attachments\new-main-3.png' -transparent -m2
+export_fig 'attachments\f4-dege.png' -transparent -m2
 [mac, x_s] = rbs.get_mac();
 rbs.plot_G_dege_hl_swithch(x_s)
-export_fig 'attachments\new-main-4.png' -transparent -m2
+export_fig 'attachments\f4-dege-mac.png' -transparent -m2

### 2023-05-20 paper/main.tex
add 0519 讨论结果
modify intro, method

@@
-% 0403 修改要点
-% 1.(need more detail) 原图1 更换实物图、更换风格、对比度，放到method部分
-% 2.(done)新的图1，典型结构的电路图
-% 3.(done)introduction 第二段 RBS 修改（增加的典型结构），列点的形式说明亮点，其余以删除为主
-% 4.(done) method 部分，最开始添一小段，结合原图1介绍流程
-% 5.(done) 第3 section 标题直接改为 examples，只包含：一个详细的结构、不同规模的对比、不同结构的对比，删去展望部分；修改图例，改善图的表示
-% 6.(done) conclusion 重写，包含展望
-% 7.(done)全文主语的修改，逐段润色，caption的修改
-% 8.(done)abstract 修改
-% 9. 转为 word（proref 更新）
-
-% figure 要点
-% (done) fig-arch: e 橙色标记不健康电池，三个闭合的开关
-% (done)f4-gra 标记SP
+% 0519 修改
+% 背景介绍：随着RBS的结构复杂度的增长，特别是当有电池隔离的情况出现，人工MAC判断越来也困难，需要具有普适性的算法
+% 模型：保留电路模型的相关推导；旧版两个图统一为一个拓扑模型图 topologic model
+% 讨论：电池组拓扑设计新思路，新的复杂结构（仅作验证）；电池隔离（尽量写）
+% 保留电路模型的相关推导
+% 图片：重画所有图，用ppt，注意字体大小、元素含义统一
+% 专有名词的统一：structure, external electrical appliance, components
+% 伪代码：修改后放附录
 
@@
 
-\title{Greedy-based RBS maximum allowable current calculation method} % #TODO: 修改标题
+\title{A Greedy-based calculation method of RBS maximum allowable current}
 \author{3057761608 }
-\date{March 2023}
 
@@
 \begin{abstract}
-    Reconfigurable Battery Systems (RBSs) offer a promising alternative to traditional battery systems, which are limited by their reliance on the worst-performing cell. 
-    RBSs can dynamically adjust the circuit configuration to optimize battery cell charging and discharging strategies. 
-    However, due to their reconfigurability, RBSs require new performance indicators to evaluate their performance.
-    This paper proposes a method to estimate the Maximum Allowable Current (MAC), a crucial indicator to evaluate RBS performance. 
-    The method employs a greedy algorithm based on a graph model and an equivalent circuit model. 
-    By searching for the shortest path for battery cells to connect to the main circuit in the graph model, a greedy search strategy is provided for the equivalent circuit model to describe the switch state variables.
-    The effectiveness of this method is validated on RBS structures of different sizes and configurations.
-    The results also show that the ratio of the output current to the maximum battery current could better reflect the structural performance of RBS than the output current alone.
+    Reconfigurable Battery Systems (RBSs) offer a promising alternative to traditional battery systems owing to their dynamical topologic structure for the optimization of battery cell charging and discharging stragegies.
+    During the operation of the RBS, the Maximum Allowable Current (MAC) is a critical indicator to guide the reconfiguring control of the system in terms of safety and reliability.
+    In this paper, the MAC of the RBS is calculated by using a greedy algorithm based on the topologic model of the RBS.
+    The effectiveness of this method is validated on the RBSs with different structures.
+    % #TODO
+
+    keywords: Reconfigurable Battery System, Maximum Allowable Current, Greedy Algorithm
 \end{abstract}
@@
 
-Battery Energy Storage Systems (BESSs) are widely used to store and supply high-quality electrical energy in various applications, such as electric vehicles and wind power turbines\cite{desiqueiraControlStrategySmooth2021,karandehTwoStageAlgorithmOptimal2019,yangBatteryEnergyStorage2018,choCommercialResearchBattery2015}.
+Battery Energy Storage Systems (BESSs) are widely used to store and supply high-quality electrical energy in various applications, such as smart grids and wind power plants \cite{desiqueiraControlStrategySmooth2021,karandehTwoStageAlgorithmOptimal2019,yangBatteryEnergyStorage2018,choCommercialResearchBattery2015}.
 Typically, a BESS consists of numerous battery cells that are interconnected by series-parallel circuitry to provide the required charge storage capacity and output voltage.
-However, as the number of cells increases, the reliability of the system becomes a major concern.
-The capacity and safety of the BESS are mainly determined by the least healthy battery cells, a phenomenon known as the cask effect.
-Furthermore, the degradation of cells in poor condition is accelerated by multiple charge/discharge cycles, which can lead to early failure of the unhealthy cells\cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019}.
-These concerns are particularly problematic for traditional BESSs with fixed circuitry, which limit their practicality.
+For the traditional BESS, the connections between batteries are fixed and the performance of system is limited by the worst cell, as the result of the cask effect.
+Furthermore, reliability and even safety issues will alse be aroused since the failed battery cannot be promptly isolated to exacerbate the degradation of the other batteries during the operational process \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019}.
+Undoubtedly theses issues hinder the practical application of traditional BESSs.
+
+Reconfigurable Battery System (RBS), which can dynamically switch to arbitrary circuit configurations as required, is expected to solve the above problem\cite{hanNextGenerationBatteryManagement2020a}.
+The ability to switches circuit helps to isolate unhealthy batteries from the circuit in a timely manner, thereby improving the safety and reliability of the battery system.
+Fig. \ref{fig:arch} shows two popular typologies of the RBSs developed by Lawson\cite{lawsonSoftwareConfigurableBattery2012} and Visairo \cite{visairoReconfigurableBatteryPack2008} respectively. 
+Taking the RBS shown in Fig.
+\ref{fig:arch-e} as example, the batteries in the RBS can beare connected not only in series when the switches $S_1$, $S_5$, $S_6$, $S_7$, $S_8$, $S_9$, and $S_{13}$ are closed, but also in parallel when $S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$, and $S_{13}$ are closed.
+Furthermore, when an unhealthy battery, for instance the orange one in Fig.
+\ref{fig:arch-f}, exits in the RBS, it can be isolated by closing its three adjacent switches (i.e.
+$S_5$, $S_7$ and $S_8$) and opening the switch below that battery (i.e.
+$S_6$) to ensure the system still remains a reliable working mode.
 
@@
     \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.3\textwidth}
+    \begin{subfigure}[b]{0.45\textwidth}
         \includegraphics[width=\textwidth]{../attachments/arch-f.png}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/arch-fe.png}
-        \caption{}
-        \label{fig:arch-ef}
-    \end{subfigure}
-    \caption{The RBS structure proposed by (a)Lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b)Visairo\cite{visairoReconfigurableBatteryPack2008} and (c) synthesized from (a) and (b).}
+    \caption{The RBS structure proposed by (a)Lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b)Visairo\cite{visairoReconfigurableBatteryPack2008}.}
     \label{fig:arch}
@@
 
-Reconfigurable Battery System (RBS), which can dynamically switch between different circuit configurations as required, is expected to solve the above problem\cite{hanNextGenerationBatteryManagement2020a}.
-Unlike fixed BESSs, reconfigurable circuits use additional switches to change the series/parallel relationship between batteries.
-Figure \ref{fig:arch} shows two proposed RBS structures (Figure \ref{fig:arch-e} and Figure \ref{fig:arch-f}), as well as a new structure (Figure \ref{fig:arch-ef}) synthesized from these two structures, all of which can dynamically adjust the connection of the battery as required.
-For instance, in the structure shown in Figure \ref{fig:arch-e} when an unhealthy battery (the orange battery in the figure) exists in the system, the isolation of the battery can be achieved by closing the three adjacent switches marked in the figure and opening the switch below the battery to ensure the reliable operation of the system.
-The structure in Figure \ref{fig:arch-f} is more flexible in terms of controlling system output.
-Its switches can be used to connect the batteries in parallel or in series, thereby enabling the system to vary the system's output current or power.
-By combining those two structures, cell isolation and output control can be easily achieved, as shown in Figure \ref{fig:arch-ef}. 
-Therefore, compared with traditional fixed-structure battery systems, RBS has higher reliability and flexibility. 
-However, due to the existence of more switches and more complex connection methods in RBS, there are more challenges in design, analysis, and control.
+The complex connecting structure between batteries and switches enables the flexibility of the RBS, but also brings the challenges in design and control cost.
+The Maximum Allowable Current (MAC) of the RBS system is defined as the maximum current that is allowed for each individual battery of the system, and is a critical indictor to be evaluate the RBS output current to the electronic appliances.
+It helps the designer to assess whether the RBS meets the output current requirements, and contributes to the formulation of appropriate and safe management stragegies for the battery management system (BMS).
+As the complexity of RBS increases, especially when the certain battery needs to be isolated, it becomes difficult to visually obtain the MAC, and a universal algorithm is needed to solve the MAC.
+Despite its importance, there is currently no method available to evaluate MAC for RBSs.
+Therefore, the purpose of this paper is to propose a universal and effective method for calculating the MAC of the RBS.
+To achieve this, a topologic model that builds the relationship between RBS circuit topology and internal resistance and voltage of its batteries are established.
+Then, a greedy algorithm is employed to search the available circuit of the RBS for reaching the MAC.
+With the developed method, MAC of RBSs with different structures can be calculated effectively.
 
-Maximum Allowable Current (MAC) is a critical parameter in the design and evaluation of reconfigurable battery systems (RBSs).
-MAC specifies the maximum current that the RBS can output to external electrical equipment without exceeding a specified current limit for batteries.
-This parameter is important for ensuring the safe and reliable operation of RBSs during normal operation and when failed batteries are isolated.
-Despite its importance, there is currently no method in the literature on RBSs for calculating MAC, which poses a challenge for the design and evaluation of these systems.
+The remainder of this paper is organized as follows:
+Section II presents the framework and details of the proposed topologic model and the greedy algorithm.
+In Section III, a case study of using the proposed model and algorithm to enumerate the MAC of a specific structure is demonstrated.
+Finally, the concluding remarks are drawn in Section IV.
 
-The purpose of this paper is to propose a universal and effective method for calculating the Maximum Allowable Current (MAC) of RBS. 
-To achieve this, models with RBS connection relationships and component status information are established, and then a greedy algorithm is used to search for MAC.
-This method has the following advantages:
-1. It can effectively calculate MAC for RBSs with different sizes and structures.
-2. A structural indicator is given to characterize the MAC of the structure, which is not affected by batteries and external circuits.
-The paper is structured as follows: 
-Section II presents the framework and details of the algorithm. 
-In Section III, using a specific structure as an example, the application of the method is demonstrated, and the effectiveness of the method on RBS with different structures and sizes is verified. 
-Finally, concluding remarks and future research directions are provided.
+\section{Methodology}
 
-\section{Method}
+The overall MAC modeling process from an RBS structure is shown in Fig. \ref{fig:main}, which can be divided into four main steps.
+In the first place, the actual RBS structure is converted to a topologic model, in which the connected relationships between batteries and switches are abstracted and the performance parameters of the batteries are retained.
+Subsequently, constraints and objective function, i.e. MAC, are obtained based on the previous connected relationships and parameters.
+Then, the shortest path (SP) of each battery in the RBS is obtained by Dijkstra algorithm.
+In the end, the open/close strategy of the RBS is implemented by greedily selecting the SPs to achieve MAC and quantitatively calculated in the equivalent circuit.
+% 只有一个 topologic model，建模；先根据连接关系和物理参数建立目标函数和约束；再找SP；最后根据贪婪算法求解MAC。
 
+% TODO: fig 整体框图
 \begin{figure}
@@
 
-Figure \ref{fig:main} shows the flowchart of our method.
-Firstly, a graph model is abstracted from the actual RBS for finding the shortest path.
-Then, an equivalent circuit model is established based on the graph model for solving the voltage and current in the circuit.
-Finally, by greedily searching for the combination of the shortest path, the MAC is calculated in the equivalent circuit model.
-\subsection{graph model and circuit model}
+\subsection{Topologic Model}
 
-A typical RBS circuit is composed of battery cells and switches.
-To establish a processable circuit, these components are transformed into ideal elements under reasonable assumptions.
+As demonstrated in Fig. \ref{fig:arch}, a typical RBS is made up of a number of battery cells and switches in a dynamically adjustable connection.
+To establish a processable circuit, these batteries and switches are transformed into ideal elements under reasonable assumptions.
 The resulting circuit structure is then described in matrix form, and the related equations are provided.
@@
 The normal equivalent circuit for a battery consists of a voltage source in series with a resistor, and a capacitor in parallel with another resistor to simulate the polarization in batteries.
-To calculate the MAC that can be stablely provided by RBS, only the steady-state behavior of the battery is considered in the model, and transient behavior is ignored.
-Therefore, the battery $i$ is modeled as a constant voltage source $u_{b,i}$ in series with a resistor $r_{b,i}$.
-And a binary variable $x_j$ is used to represent the state of switch $j$, where 0 and 1 indicate open and closed, respectively.
-To simplify the calculation, a closed switch is considered as a resistor with a very small resistance value $r_s$, which are treated as zero in the final result.
-In the following derivation, the product of the conductance $1/r_s$ and the variable $x_j$ is used to characterize the state of switch $j$.
+To simplify the model, the transient characteristics of the circuit are not considered, so the capacitor mentioned above is ignored.
+In this way, the battery $i$ in the RBS is modeled by the series connection in between a constant voltage source $u_{b,i}$ and a resistor $r_{b,i}$,  as shown in Fig. %TODO 电池模型有电阻电容简化为电阻的示意图。
+And a binary variable $x_j$ is used to represent the state of switch $j$, where 0 for ON and 1 for OFF, respectively.
+To simplify the calculation, a closed switch is considered as a resistor with a very small resistance value $r_s$.
 
-A directed graph model $G(V,E)$ for the RBS is constructed in such a way that
-\begin{enumerate}[(1)]
-    \item Nodes: the vertex set $V={v_1,v_2,\cdots,v_N}$ represents the nodes connecting batteries and/or switches, where $v_1$ and $v_N$ represent the anode and cathode of the RBS respectively;
-    \item Edges: the directed edge set $E$ represents the output circuit, $N_b$ batteries and $N_s$ switches, corresponding set $E_o$, $E_b$ and $E_s$.
-The external electrical equipment in the output circuit is treated as one directed edge $v_n \to v_1$.
-The direction of the edge representing a battery is set to be from the anode to the cathode.
-For the edges representing switches, their directions are marked from the low node to the the high node.
-A negative value for the voltage drop or current solved on the edge means that the actual direction is opposite to that initially specified.
+For a given RBS structure, the topologic model for the RBS is constructed as a directed graph $G(V,E)$ in such a way that:
+\begin{enumerate}
+    \item Nodes: node $v_1$ and $v_N$ represent the anode and cathode of the RBS respectively, and the other nodes $v_2,\cdots , v_{N-1}$ represent the points connecting batteries and/or switches, where $N$ is the total number of nodes.
+    \item Edges: the directed edges represent batteries, switches and the external electrical appliance in the output circuit based on whether the current direction is constrainted or not. 
+        When the battery is in operation, the internal current direction must be from the negative electrode to the positive electrode, so it is represented by a directed edge from the negative to the positive ; this edge has attributes $(u_b, r_b)$, where $u_b$ and $r_b$ represent battery $b$'s electromotive force and internal resistance.
+        Switches have no constraints on the current direction, so they are represented by a pair of directed edges with opposite directions; these edges both have attribute $(0, r_s)$, where $r_s$ represents the resistance of switch as mentioned above.
+        To fully solve for the current and voltage, an external electrical appliance equivalent as a resistor $R_0$ is connected to the anode and cathode of the RBS and represented by a directed edge from the anode $v_N$  to the cathode $v_1$ of the RBS.
+        Similarly, this edge has attribute $(0, R_0)$.
+        If a given RBS structure has $N_b$ batteries and $N_s$ switches in total, then the number of edges is $N_b+2N_s+1$, where 1 refers to the external electrical appliance.
 \end{enumerate}
 
-Based on the above directed graph which has $N$ nodes and $1+N_b+N_s$ directed edges (1 refers to the output circuit), its incidence matrix $\bm{A}_{N\times (1+N_b+N_s)}$ is defined as
+\subsection{Constraints and Objective Function}
+
+The constraints and objective function are obtained by analyzing the currents of batteries and external electrical appliance, as following.
+Based on the above directed graph which has $N$ nodes and $N_b+2N_s+1$ directed edges, its incidence matrix $\bm{A}$ is defined as
 \begin{align}\label{eq:A}
-    a_{ij}=
+    $a_{ij}$=
     \begin{cases}
@@
 \end{align}
-Since each column of $\bm{A}$ sums to zero, the last line are deleted and the reduced incidence matrix $\bm{A}_{(N-1)\times(1+N_b+N_s)}$ are used in the following calculation.
-By splitting $E$ into $\{E_o, E_b, E_s\}$, $A$ is rewritten as follows
+Since each column of $\bm{A}$ sums to zero, the last line are deleted.
+Furthermore, because of a couple of opposite directed edges for each switch, the $N_s$ columns corresponding to the switches are also deleted.
+Finally, the reduced incidence matrix $\bm{A}_{(N-1)\times(N_b+N_s+1)}$ are used in the following calculation.
+By divided as batteries, switches and external electrical appliance, $A$ is rewritten as follows
 \begin{equation}
@@
     \begin{bmatrix}
-        \bm{A}_o & \bm{A}_b & \bm{A}_s
+        \bm{A}_b & \bm{A}_s & \bm{A}_o
     \end{bmatrix}.
@@
 
-$1+N_b+N_s$ edges' currents $\bm{I}_{(1+N_b+N_s)\times 1}$ and voltages $\bm{U}_{(1+N_b+N_s)\times 1}$, and $N-1$ nodes' voltages $\bm{U}_{n, (N-1)\times 1}$ have following relationships from Kirchhoffs law
+$N_b+N_s+1$ edges' currents $\bm{I}_{(N_b+N_s+1)\times 1}$ and voltages $\bm{U}_{(N_b+N_s+1)\times 1}$, and $N-1$ nodes' voltages $\bm{U}_{n, (N-1)\times 1}$ have following relationships from Kirchhoffs law
 \begin{align}\label{eq:Kirchhoffs_law}
     \begin{cases}
-        \bm{A} \bm{I} = \bm{0}, \\
-        \bm{U}        = \bm{A}^\T \bm{U}_n.
+        $\bm{A} \bm{I} = \bm{0}$, \\
+        $\bm{U}        = \bm{A}^\T \bm{U}_n.$
     \end{cases}
@@
 \begin{equation}\label{eq:X}
-    \bm{X} = diag(
-    1,
+    \bm{X} = \diag(
     \underbrace{1, \cdots, 1}_{N_b~\text{of}~1},
-    \underbrace{1, 0 \cdots, 1}_{N_s~\text{of}~0/1}
-    )
+    \underbrace{1, 0 \cdots, 1}_{N_s~\text{of}~0/1},
+    1)
     =\begin{bmatrix}
-        \bm{I} &\\
-        & \bm{X}_s
+        \bm{X}_s &\\
+        & \bm{I}
     \end{bmatrix}.
@@
 In addition to the equivalent circuit assumptions, we also assume that all batteries have the same internal resistance value $r_b$ and supply the same electric potential $u_s$ to simplify the model.
-Then the output current $I_o$ and each battery's current $\bm{I}_b$ can be given by solving the simultaneous Equations \ref{eq:Kirchhoffs_law} and \ref{eq:generalized_branches} eventually.
+Then the output current $I_o$ and each battery's current $\bm{I}_b$ can be given by solving the simultaneous Eq. \ref{eq:Kirchhoffs_law} and \ref{eq:generalized_branches} eventually.
 Let
@@
 \end{align}
-where $\bm{I}_{N_b\times 1}$ is a column vector with all terms being one.
+where $\bm{I}_{N_b\times 1}$ is a column vector with all equal to 1.
 
-Here, the ratio of $I_o$ and $\max (\bm{I}_b)$ is used to characterize the maximum allowable current for a given RBS architecture, denoted as $\eta$.
+In this study, the ratio of $I_o$ and $\max (\bm{I}_b)$ is used to characterize the maximum allowable current for a given RBS architecture, denoted as $\eta$:
+\begin{equation}\label{eq:eta}
+    \eta = \frac{I_o}{\max (\bm{I}_b)}.
+\end{equation}
 The discussion in the next section will show that the $\eta$ reflects the ability of the RBS architecture itself to deliver current, regardliess of the battery cells used by the RBS.
 Finally the problem in RBS can be formulated as
-\begin{align}
+\begin{align}\label{eq:max_eta}
     & \max \eta \label{eq:max_eta}\\
-    \mathrm{s.t.}\,\, & \eta = \frac{I_o}{\max (\bm{I}_b)}, \\
     & \max (\bm{I}_b) \leq I_m,
 \end{align}
-where $I_m$ is the maximum allowable current of the battery; $I_o$ and $\bm{I}_b$ can be calculated by Equations \ref{eq:I_o} and \ref{eq:I_b}.
-However, it is difficult to solve \ref{eq:max_eta} directly because of the presence of matrix $\bm{Y}_n^{-1}$.
+where $I_m$ is the maximum allowable current of the battery; $\eta$ can be calculated by Eq. \ref{eq:eta}; $I_o$ and $\bm{I}_b$ can be calculated by Eq. \ref{eq:I_o} and \ref{eq:I_b}.
+However, it is computationally difficult to solve \ref{eq:max_eta} directly because of the presence of matrix $\bm{Y}_n^{-1}$.
+As the number of batteries and switches in the RBS increase, the order of the matrix increases, and the time costed to compute increases sharply.
 A greedy algorithm is proposed to solve this problem in the next subsection.
 
-\subsection{greedy solution}
+\subsection{Greedy Solution}
 
-First, the battery $i$'s shortest path ($SP_i$) is given here.
+In this subsection, a greedy algorithm is proposed based on shortest paths ($SP$s), which is given here firstly.
 When the battery $i$ is connected to the anode $v_1$ and the cathode $v_N$ of the RBS by the path $p$ in the graph model, the distance $\omega$ of $p$ is defined by the following equation:
@@
 $SP_i$ is defined as the path with the minimum $\omega$ for battery $i$.
-According to the definition, $SP_i$ gives the simplest strategy by which the control of battery $i$ is achieved with a minimum of switches while minimising the influence of other batteries.
+\begin{equation}
+    SP_i = \argmin_{p \in P_i} \omega(p),
+\end{equation}
+where $P_i$ is the set of all paths from $v_1$ to $v_N$ and passed through the directed edge $i$ in the direction of it.
+Specifically, the Dijkstra algorithm can be used to implement the $SP_i$.
+According to the definition, $SP_i$ gives the simplest strategy by which the control of battery $i$ is achieved with a minimum of switches while minimizing the influence of other batteries.
 From the perspective of series/parallel, the more batteries are connected into circuit via their $SP$s, the more batteries are connected in parallel.
@@
 
-The pseudo-code of the algorithm is as follows:
-\begin{algorithm}
-    \caption{Get the max available currents of a certain RBS}\label{alg:eta_RBS}
-    \KwData{Directed graph model $G(V,E)$ of the RBS}
-    \KwResult{$\max \eta$}
-    \For{$i \in E_b$}{
-        $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
-        $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
-    }
-    get $\bm{A}$ by Equation \ref{eq:A}\;
-    \While{not yet determine $\max \eta$ }
-    {
-        $N_{sel} \leftarrow \text{number of selected $SP$s calculated by dichotomy}$\;
-        $C_b    \leftarrow \text{set of all combinations of $N_{sel} $~batteries from $N_b$}$\;
-        \For{$c_b \in C_b$}{
-            $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
-            $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
-            get $\bm{Y}_n$ by Equation \ref{eq:Yn}\;
-            \eIf{$\bm{Y}_n$ is invertible}{
-            }{construct an effective solution}
-            get $I_o$ by Equation \ref{eq:I_o}\;
-            get $\bm{I}_b$ by Equation \ref{eq:I_b}\;
-            \eIf{$\max(\bm{I}_b)\leq I_m$}{
-                $\eta \leftarrow I_o/\max(\bm{I}_b)$\;
-            }{break}
-        }
-    }
-\end{algorithm}
+After finding the potential SPs combinations about the MAC, the state variable $\bm{X}_s$ of the switches can be determined, and the optimization problem \ref{eq:max_eta} can be solved using Eq.
+\ref{eq:eta}, \ref{eq:I_o} and \ref{eq:I_b}.
+The overall flowchart is shown in Fig. \ref{fig:flowchart}, and the corresponding pseudo-code of the algorithm is shown in Algorithm \ref{alg:eta_RBS}.
+% TODO 算法流程图
 
-\section{Examples}
+\section{Case Study}
 
@@
 
+\section{Appendix}
+\begin{algorithm}
+    \caption{Get the max available currents of a certain RBS}\label{alg:eta_RBS}
+    \KwData{Directed graph model $G(V,E)$ of the RBS}
+    \KwResult{$\max \eta$}
+    \For{$i \in E_b$}{
+        $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
+        $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
+    }
+    get $\bm{A}$ by Equation \ref{eq:A}\;
+    \While{not yet determine $\max \eta$ }
+    {
+        $N_{sel} \leftarrow \text{number of selected $SP$s calculated by dichotomy}$\;
+        $C_b    \leftarrow \text{set of all combinations of $N_{sel} $~batteries from $N_b$}$\;
+        \For{$c_b \in C_b$}{
+            $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
+            $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
+            get $\bm{Y}_n$ by Equation \ref{eq:Yn}\;
+            \eIf{$\bm{Y}_n$ is invertible}{
+            }{construct an effective solution}
+            get $I_o$ by Equation \ref{eq:I_o}\;
+            get $\bm{I}_b$ by Equation \ref{eq:I_b}\;
+            \eIf{$\max(\bm{I}_b)\leq I_m$}{
+                $\eta \leftarrow I_o/\max(\bm{I}_b)$\;
+            }{break}
+        }
+    }
+\end{algorithm}
+
 \bibliographystyle{ieeetr}

### 2023-05-21 paper/main.tex
modify case study 1/2

@@
 \usepackage{amsmath}
+\DeclareMathOperator{\diag}{diag}
 \usepackage{multirow}
+\usepackage{booktabs}
 \usepackage{bm}
 \usepackage[ruled,linesnumbered]{algorithm2e}
+\setcounter{MaxMatrixCols}{20}
 
@@
 \begin{align}\label{eq:A}
-    $a_{ij}$=
+    a_{ij}=
     \begin{cases}
@@
     \begin{cases}
-        $\bm{A} \bm{I} = \bm{0}$, \\
-        $\bm{U}        = \bm{A}^\T \bm{U}_n.$
+        \bm{A} \bm{I} = \bm{0}, \\
+        \bm{U}        = \bm{A}^\T \bm{U}_n.
     \end{cases}
@@
     =\begin{bmatrix}
-        \bm{X}_s &\\
-        & \bm{I}
+        \bm{I} & & \\
+        & \bm{X}_s &\\
+        & &\bm{I}
     \end{bmatrix}.
@@
 \begin{equation}\label{eq:Yn}
-    \bm{Y}_n (\bm{X}) = \frac{1}{R_o} \bm{A}_o\bm{A}_o^\T + \frac{1}{r_b} \bm{A}_b\bm{A}_b^\T + \frac{1}{r_s}\bm{A}_s\bm{X}_s\bm{A}_s^\T,
+    \bm{Y}_n (\bm{X}_s) = \frac{1}{R_o} \bm{A}_o\bm{A}_o^\T + \frac{1}{r_b} \bm{A}_b\bm{A}_b^\T + \frac{1}{r_s}\bm{A}_s\bm{X}_s\bm{A}_s^\T,
 \end{equation}
@@
 \begin{align}
-    I_o(\bm{X})      & = \frac{u_b}{R_o r_b} \bm{A}_o^\T \bm{Y}_n^{-1}(\bm{X}) \bm{A}_b \bm{I}_{N_b\times 1};\label{eq:I_o}\\
-    \bm{I}_b(\bm{X}) & = \frac{u_b}{r_b^2}[\bm{A}_b^\T \bm{Y}_n^{-1}(\bm{X}) \bm{A}_b\bm{I}_{N_b \times 1}  -r_b \bm{I}_{N_b \times 1}],\label{eq:I_b}
+    I_o(\bm{X}_s)      & = \frac{u_b}{R_o r_b} \bm{A}_o^\T \bm{Y}_n^{-1}(\bm{X}) \bm{A}_b \bm{I}_{N_b\times 1};\label{eq:I_o}\\
+    \bm{I}_b(\bm{X}_s) & = \frac{u_b}{r_b^2}[\bm{A}_b^\T \bm{Y}_n^{-1}(\bm{X}) \bm{A}_b\bm{I}_{N_b \times 1}  -r_b \bm{I}_{N_b \times 1}],\label{eq:I_b}
 \end{align}
@@
 Finally the problem in RBS can be formulated as
-\begin{align}\label{eq:max_eta}
+\begin{align}
     & \max \eta \label{eq:max_eta}\\
-    & \max (\bm{I}_b) \leq I_m,
+    \text{s.t.} & \max (\bm{I}_b) \leq I_m, \label{eq:Ib_leq_Im}
 \end{align}
@@
 As the number of batteries and switches in the RBS increase, the order of the matrix increases, and the time costed to compute increases sharply.
-A greedy algorithm is proposed to solve this problem in the next subsection.
+A greedy algorithm will be proposed to solve this problem in the next subsection.
 
-\subsection{Greedy Solution}
+The integrability of the matrix $\bm{Y}_n$ is explained here.
+Although the above solution procedure requires the matrix $\bm{Y}_n$ to be invertible, it is still possible to encounter integrable $\bm{Y}_n$ in the calculation.
+The physical meaning of this case corresponds to the fact that due to the excessive number of switches in OFF, the solved circuit structure forms circuit branches independent of the main circuit, i.e., the circuit connected to the anode and cathode of the RBS.
+Since these independent branches are not connected to the main circuit, the voltage potentials of these branches cannot be determined and theoretically an infinite number of sets of solutions exist. 
+Benfit from the independence, these solutions have no influence on the results of the main circuit. 
+Since only the currents and voltages of the main circuit are of interest, only one of these solutions needs to be chosen for subsequent calculation.
+
+\subsection{Greedy Solution}\label{subsec:greedy_solution}
 
@@
 \begin{equation}
-    SP_i = \argmin_{p \in P_i} \omega(p),
+    SP_i = \mathop{\arg\min}_{p \in P_i} \omega(p),
 \end{equation}
@@
 
-This section verifies the effectiveness of the above model and algorithm on several structures.
-Firstly, the detailed modeling and solving process of a specific RBS structure (proposed by \cite{visairoReconfigurableBatteryPack2008}) with four battery cells is given.
-Then, the effectiveness is verified on RBSs with different structures and sizes.
-This section also explains the advantages of using $\eta$ to characterize MAC.
+This section presents a case study to demonstrate the effectiveness of the proposed method.
+A more intricate structure, which integrates the two previously proposed structures, is proposed.
+The effectiveness of the aforementioned algorithm is substantiated on this structure to confirm its applicability in practical scenarios.
+Moreover, the algorithm's versatility is also established through its application in complex cases such as the presence of isolated battery cell.
 
-\subsection{An specific example}
+\subsection{Determination of a new RBS structure}
 
-\begin{figure}[htbp]
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/f4-phy.png}
-        \caption{}
-        \label{fig:f4-phy}
-    \end{subfigure}
-    \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/v3-new-main-2.png}
-        \caption{}
-        \label{fig:f4-gra}
-    \end{subfigure}
-    \\
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/f-dege-4-modify.png}
-        \caption{}
-        \label{fig:f4-circ}
-    \end{subfigure}
-    \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/f-dege-mac-4.png}
-        \caption{}
-        \label{fig:f4-mac}
-    \end{subfigure}
-    \caption{ 
-        RBS structure proposed by Visairo\cite{visairoReconfigurableBatteryPack2008} with 4 batteries. 
-        (a) Physical model, (b) graph model, (c) equivalent circuit model, and (d) results obtained by using the proposed method.
-        The blue highlighted lines indicate the SPs. 
-        The red highlighted lines indicate the open/close states of switches.
-        }
-    \label{fig:f4-all}
-\end{figure}
+% TODO: 图，我们的结构；以及与之前两种结构的关系
+% fig:arch-ef
 
-The reconfigurable architecture proposed by Visairo et al.\cite{visairoReconfigurableBatteryPack2008} is shown in Figure \ref{fig:f4-phy}.
-In this architecture, each cell is controlled by about 3 switches on average.
-Excepted for two switches ($S_1$ and $S_{13}$ in Figure \ref{fig:f4-phy}) controlling the total circuit, the vertical switches (e.g.
-$S_2$ and $S_9$ in Figure \ref{fig:f4-phy}) allow the batteries to be directly connected to the main circuit, and the switches($S_6$ for example) in the diagonal direction can realize connecting the batteries in series.
-Thus, it can dynamically change the output voltage and current as needed.
-The architecture in Figure \ref{fig:f4-phy} only has 4 batteries, but in practice it can add new branches containing batteries and switches to deal with large-scale batteries\cite{kimDependableEfficientScalable2010}.
+The RBS structure proposed by Lawson et al\cite{lawsonSoftwareConfigurableBattery2012}, shown in Fig.
+\ref{fig:arch-e}, easily enables the isolation of arbitrary cells or the addition of redundant cells to the system, but these cells are limited to being connected in series only and the switch between cells connection modes is not flexible.
+In contrast, the structure proposed by Visairo et al\cite{visairoReconfigurableBatteryPack2008}, shown in Fig.
+\ref{fig:arch-f}, allows the flexibility to switch the cells between series, parallel and mixed series-parallel modes, thus allowing dynamic voltage adjustment according to the external load and improving energy conversion efficiency, but is not as simple as the structure by Lawson et al in terms of isolating cells or adding redundancy.
+In order to combine the advantages of both structures, a new structure is obtained by replacing the batteries in Fig.
+\ref{fig:arch-e} with the structure in Fig.
+\ref{fig:arch-f}, as shown in Fig.
+\ref{fig:arch-ef}.
+This more complex structure has the structure of Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} as the main frame and the structure of Visairo et al.\cite{visairoReconfigurableBatteryPack2008} as the substructure.
+In this way, the circuit topology of the substructure (i.e.
+the structure in the box in Fig.
+\ref{fig:arch-ef}) can be changed to enable dynamic and flexible voltage adjustment according to the load, while at the same time taking advantage of the ease of battery isolation and increased redundancy of the main frame.
+The next subsections will use this structure with 4 battery cells and 19 switches as an example to demonstrate the effectiveness of the proposed algorithm.
 
-The graph in Figure \ref{fig:f4-gra} represents a graphical model based on the physical model(Figure \ref{fig:f4-phy}).
+\subsection{Calculation details and result}
+
+% TODO: 图，结构的有向图，注意颜色，绿色、灰色、蓝色
+% fig:ef-topo
+
+The graph in Fig. \ref{fig:ef-topo} represents the topologic model based on the new RBS structure mentioned in the last subsection (Fig. \ref{fig:arch-ef}).
 The model is presented in the form of a directed graph, capturing the connection relationship between the battery and switch in the circuit.
-Vertex 1 and 12 represent the ancode and cathode of the RBS, respectively;
-the remaining vertices represent the connection nodes between the batteries and switches.
-Battery 1, 2, 3, and 4 are represented by green directed edges in the graph, while switches are represented by gray directed edges with opposite directions.
-The external electrical appliance is considered as a directed edge from node 12 to node 1.
-In the graph model, the directionality of the edges is strictly specified to ensure that there is no reverse flow of current in the battery and external electrical appliance.
+Battery cell 1, 2, 3, and 4 are represented by green directed edges in the graph, while nineteen switches are represented by gray directed edges with opposite directions.
+The external electrical appliance is considered as a directed edge from the cathode of the RBS ( node $18$ in the graph) to the anode ( node $1$ in the graph), represented as the blue directed edge in the graph.
+Totally, there are 19 nodes and 43 edges in the graph.
 
-According to Equation \ref{eq:weight}, the weight of the edge corresponding to the battery is the total number of switches, which is 13;
-the weight of the edge corresponding to the switch is 1.
-By setting the weight in this way, on the one hand, it avoids the simultaneous occurrence of multiple batteries in a single SP, weakening the influence between different batteries;
-on the other hand, it minimizes the number of switches on the path, which means that only a few switches (i.e., the switches on the SP) need to be closed to connect the battery to the main circuit.
-By using the depth-first search algorithm, the SP of battery 1 can be calculated as the node list $[1, 2, 3, 7, 11, 12]$, and the SPs of the other batteries are shown in Figure \ref{fig:f4-gra}.
+Based on the node-edge relationship given in Fig. \ref{fig:ef-topo}, the incidence matrix $\bm{A}$ can be obtained according to Eq. \ref{eq:A}:
+\begin{equation}
+    \bm{A} = 
+    \begin{bmatrix}
+        \bm{A}_b & \bm{A}_s & \bm{A}_o
+    \end{bmatrix},
+\end{equation}
 
-The equivalent circuit model, as shows in Figure \ref{fig:f4-circ}, can be obtained based on the assumptions in Section II.
-In this model, the batteries and switches are treated as branches, where the battery is regarded as a branch consisting of a voltage source $u_b$ in series with a resistor $r_b$, and the switch is regarded as a branch controlled by a state variable $x_s$ to short or open the circuit.
-The branches are represented as direction edges, whose direction is from the node with the smaller number to the larger. 
-When the computed current or voltage value is negative, it indicates that the direction of the battery or potential difference is opposite to the preset direction.
-Based on the node-edge relationship in Figure \ref{fig:f4-circ}, the incidence matrix $\bm{A}$: can be obtained according to Equation \ref{eq:A}:
-{\setlength{\arraycolsep}{2pt}
 \begin{equation}
-    \begin{array}{cc}
-        &  \begin{array}{c c cccc ccccccccccccc} & e_o &e_{b1}  &e_{b2} & e_{b3} & e_{b4} & e_{s1} & e_{s2} & e_{s3} & e_{s4} & e_{s5} & e_{s6} & e_{s7} & e_{s8} & e_{s9} & e_{s10} & e_{s11} & e_{s12} & e_{s13} \end{array}\\
-            \begin{array}{c} v_1\\v_2\\v_3\\v_4\\v_5\\v_6\\v_7\\v_8\\v_9\\v_{10}\\v_{11}\\v_{12}\end{array} & \left[
-                    \begin{array}{c|cccc|ccccccccccccc}
-                        -1  &  0  &  0  &  0  &  0  &  1  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0\\
-                        0  &  0  &  0  &  0  &  0  & -1  &  1  &  1  &  1  &  1  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0\\
-                        0  &  1  &  0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  1  &  0  &  0  &  0  &  0  &  0  &  0  &  0\\
-                        0  &  0  &  1  &  0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  1  &  0  &  0  &  0  &  0  &  0  &  0\\
-                        0  &  0  &  0  &  1  &  0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  1  &  0  &  0  &  0  &  0  &  0\\
-                        0  &  0  &  0  &  0  &  1  &  0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0\\
-                        0  & -1  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  1  &  0  &  0  &  0  &  0\\
-                        0  &  0  & -1  &  0  &  0  &  0  &  0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  1  &  0  &  0  &  0\\
-                        0  &  0  &  0  & -1  &  0  &  0  &  0  &  0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  1  &  0  &  0\\
-                        0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  0  &  0  &  0  &  0  & -1  &  0  &  0  &  0  &  1  &  0\\
-                        0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  &  0  & -1  & -1  & -1  & -1  &  1\\
-                    \end{array} \right]
-    \end{array},
+    \bm{A}_b^\T = 
+    \begin{bmatrix}
+        0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+        0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 \\
+        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 \\
+    \end{bmatrix},
 \end{equation}
-}
-where the rows correspond to vertexes in the graph model, and the first column, second to fourth columns, and last ten columns correspond to external electrical equipment, 4 batteries, and 13 switches, respectively.
-According to the above classification of the columns, the matrix $\bm{A}$ can be divided into $\bm{A}_o$, $\bm{A}_b$, and $\bm{A}_s$.
 
+\begin{equation}
+    \bm{A}_s^\T = 
+    \begin{bmatrix}
+        1 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+        0 & 1 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+        0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+        0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+        0 & 0 & 0 & 1 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+        0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+        0 & 0 & 0 & 0 & 1 & 0 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+        0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+        0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 \\
+        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 &-1 \\
+        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 &-1 & 0 & 0 & 0 & 0 & 0 \\
+        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 \\
+        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 &-1 & 0 & 0 \\
+        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 \\
+        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 &-1 & 0 \\
+        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 &-1 \\
+        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 \\
+    \end{bmatrix},
+\end{equation}
+
+\begin{equation}
+    \bm{A}_o^\T = 
+    \begin{bmatrix}
+       -1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+    \end{bmatrix}.
+\end{equation}
 The state matrix $\bm{X}$ is determined by the switches' state, that is, the specific configuration of the RBS.
-For example, when switch
-$S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$ and $S_{13}$
-are closed, and switch $S_6$, $S_7$ and $S_8$ are open, that is , battery $B_1$, $B_2$, $B_3$ and $_4$ are connected in parallel to supply power to the external circuit, the state matrix $\bm{X}$ is given by
+For example, when switch $S_1$, $S_3$, $S_5$, $S_6$, $S_8$, $S_9$, $S_{11}$, $S_{13}$, $S_{14}$, $S_{16}$, $S_{17}$ and $S_{19}$ are ON, and the rest of the switches are OFF, the state matrix $\bm{X}$ is given by
 \begin{equation}
     \bm{X} = diag(
-    1,
+    \underbrace{1,0,1,0,1,1,0,1,1,0,1,0,1,1,0,1,1,0,1}_{\text{switches}},
     \underbrace{1,1,1,1}_{\text{batteries}},
-    \underbrace{1,1,1,1,1,0,0,0,1,1,1,1,1}_{\text{switches}}
+    1
     ).
 \end{equation}
+By substituting the above specific values of $\bm{A}$ and $\bm{X}$ above into Eqs.
+\ref{eq:Yn}, \ref{eq:I_o}, \ref{eq:I_b} and \ref{eq:eta} in turn, the $\eta$ at the current situation, i.e.
+battery cell $B_1$ and $B_2$, $B_3$ and $B_4$ are connected in parallel with each other, and then connected in series to supply the external electrical appliance, can be obtained after the sequential calculation.
+The results are shown in Tab. \ref{tab:given_x}.
 
-When using the algorithm to solve the MAC, one may encounter the situation where the matrix $\bm{Y}_n$ is not full rank, and its inverse matrix cannot directly be obtained.
-This is because so many switches are open that some branches with voltage sources are independent of the main circuit and form new circuits.
-These circuits have infinite possible values for potential difference between them, since they are not connected to each other.
-But the potential of the main circuit, which connects from node 1 to node 12 and completely determines the output, is certain and unique.
-Therefore, the non-invertibility of $\bm{Y}_n$ will not affect the final solution.
-Here, one can choose the solution where the potential at the node with the smallest number in the independent branch is 0.
+\begin{table}[htbp]
+  \centering
+    \caption{Calculating result of the output current $I_o$, battery current $\bm{I}_b$ and ratio $\eta$ for a specificed switches state $\bm{X}_m$ in the structure combining Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} and Visairo et al.\cite{visairoReconfigurableBatteryPack2008} with 4 battery cells and 19 switches.}
+    \begin{tabular}{cc}
+    \toprule
+        Structure & 4 battery cells and 19 switches  \\
+        % Structure & combining Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} and Visairo et al.\cite{visairoReconfigurableBatteryPack2008} with 4 battery cells and 19 switches  \\
+    \midrule
+    Switch ON & 1,3,5,6,8,9,11,13,14,16,17,19 \\
+        $\bm{X}_s$ & $\diag(1,0,1,0,1,1,0,1,1,0,1,0,1,1,0,1,1,0,1)$ \\
+    \midrule
+        $I_o$ & $2u_b/(R_o+r_b)$ \\
+        $\bm{I}_b$ & $[u_b/(R_o+r_b),u_b/(R_o+r_b),u_b/(R_o+r_b),u_b/(R_o+r_b)]$ \\
+        $\eta$     & 2 \\
+    \bottomrule
+    \end{tabular}%
+  \label{tab:given_x}%
+\end{table}%
 
-\begin{table}[h]
-    \caption{Detailed results of the proposed method for the RBS structure proposed by Visairo\cite{visairoReconfigurableBatteryPack2008} with 4 batteries, including the output current, current of each battery, and $\eta$.}
-    \label{tab:1}
-    \begin{tabular}{ccc}
-        \hline
-        output current $I_o$       & battery current $\bm{I}_b$       & $\eta$        \\
-        \hline\\
-        $\displaystyle\frac{4u_b}{4R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b}\right]$   & $4.00$ \\
-        \\
-        \hline
-    \end{tabular}
-\end{table}
-The final calculation result of $\eta$ for the structure in Figure \ref{fig:f4-phy} is 4.
-The corresponding currents of output and each battery are shown in Table \ref{tab:1}.
-The corresponding switch control strategy is: $S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$ and $S_{13}$ are closed (highlighted in red in Figure \ref{fig:f4-mac}), and $S_6$, $S_7$ and $S_8$ are open.
-For this structure, when all batteries are connected to the main circuit through the switches in the vertical direction in Figure \ref{fig:f4-phy} and the batteries are connected in parallel, the output current is maximum, which is the sum of the currents of the four batteries.
-The MAC of this structure is correctly estimated by our greedy algorithm.
+The above gives the procedure for calculating the current and $\eta$ when the specified switches are given ON or OFF.
+However, in order to calculate the MAC of the structure, i.e.
+the maximum $\eta$, it is necessary to find the corresponding switch state using a greedy strategy, as mentioned in subsection \ref{subsec:greedy_solution}.
+
+Firstly, the weight $N_s$ in Eq. \ref{eq:weight} represents the total number of switches in the system, which is 19. 
+By using this formula and the Dijkstra search strategy, the $SP$s of each cell can be obtained, as shown in Fig 1.  % TODO: fig 4 个cell的SP
+According to the greedy strategy, as many $SP$s as possible should be selected to get the MAC. 
+In the first iteration, the $SP$s of all four batteries are selected, and the switch states on the paths are set to ON. 
+The corresponding $\bm{X}_s$ are calculated using the previous method, and the currents of the batteries are obtained as $u_b/r_b$, $u_b/r_b$, $u_b/r_b$, and $u_b/r_b$. 
+Since all batteries are short-circuited and the current of the battery exceeds the maximum allowed current $I_m$, this solution does not satisfy constraint \ref{eq:Ib_leq_Im} and is discarded. 
+The second iteration is carried out using the dichotomy method, and two batteries are selected for the combination. 
+Assuming that the selected combinations are $(B1, B2)$, the $\bm{X}_s$ obtained according to the $SP$s are substituted into the previous calculation, and the current of each battery is $u_b/r_b$, $u_b/r_b$, $0$, and $0$.
+This solution meets the condition. 
+After that, the case of selecting three cells is considered. 
+By similar calculations, it is determined that all solutions do not satisfy the constraint when three cells are selected. 
+Finally, the MAC of this structure is $\eta=2$, and the related results are shown in Tab. \ref{tab:find_mac}.
+
+\begin{table}[htbp]
+  \centering
+    \caption{MAC Calculating result of the output current $I_o$, battery current $\bm{I}_b$ and ratio $\eta$ in the structure combining Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} and Visairo et al.\cite{visairoReconfigurableBatteryPack2008} with 4 battery cells and 19 switches.}
+    \begin{tabular}{cc}
+    \toprule
+        % Structure & combining Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} and Visairo et al.\cite{visairoReconfigurableBatteryPack2008} with 4 battery cells and 19 switches  \\
+        Structure & 4 battery cells and 19 switches  \\
+    \midrule
+    Switch ON & 1,3,5,6,8,9,10,12,18,19 \\
+    $\bm{X}_s$ & $\diag(1,0,1,0,1,1,0,1,1,1,0,1,0,0,0,0,0,1,1)$ \\
+    \midrule
+        $I_o$ & $2u_b/(2R_o+r_b)$ \\
+        $\bm{I}_b$ & $[u_b/(2R_o+r_b),u_b/(2R_o+r_b),0,0]$ \\
+        $\eta$     & 2 \\
+    \bottomrule
+    \end{tabular}%
+  \label{tab:find_mac}%
+\end{table}%
+
+\subsection{Discussion}
 
@@
 \bibliographystyle{ieeetr}
-\bibliography{../attachments/my_ref}
+% \bibliography{../attachments/my_ref}
+\bibliography{my_ref}
 

### 2023-05-21 paper/main.tex
modify case discussion

@@
 Firstly, the weight $N_s$ in Eq. \ref{eq:weight} represents the total number of switches in the system, which is 19. 
-By using this formula and the Dijkstra search strategy, the $SP$s of each cell can be obtained, as shown in Fig 1.  % TODO: fig 4 个cell的SP
+By using this formula and the Dijkstra search strategy, the $SP$s of each cell can be obtained, as shown in Figs.
+\ref{fig:sp1} to \ref{fig:sp4}.
+% TODO: fig 4 个cell的SP（fig:sp1,2,3,4），最终求解结果 fig:ef-mac
 According to the greedy strategy, as many $SP$s as possible should be selected to get the MAC. 
@@
 By similar calculations, it is determined that all solutions do not satisfy the constraint when three cells are selected. 
-Finally, the MAC of this structure is $\eta=2$, and the related results are shown in Tab. \ref{tab:find_mac}.
+Finally, the MAC of this structure is $\eta=2$, and the related result is shown in Fig. \ref{fig:ef-mac} and Tab. \ref{tab:find_mac}.
 
@@
 
-From the specific results of the output current $I_o$ and battery currents $\bm{I}_b$, both are related to the battery voltage $u_b$, internal resistance $r_b$, and external circuit resistance $R_o$.
-This means that even for the same structure, the output current will change when the external circuit  or the battery specifications  change.
-By dividing the output current by the sum of the battery currents, the obtained $\eta$ does not include items affected by external circuit and batteries.
-This characteristic is guaranteed by the linear nature of the RBS circuit.
+The correctness of the results shown in Fig. \ref{fig:ef-mac} is obvious. 
+When B1 and B2 or B3 and B4 are connected in parallel, the RBS can output the maximum current, which is $\eta=2$, i.e. twice the current output of a single battery in RBS.
+While adding more batteries to the main circuit can only form a series structure and will not improve the MAC.
+It is worth noting that when solving for MAC, $\eta$ is used as the objective function instead of $I_o$, which makes the result of MAC more reasonable. 
+According to the results shown in Tab.
+\ref{tab:find_mac}, $I_o$ and $\bm{I}_b$ are affected by the equivalent resistance $R_o$ of external electrical appliance, the battery's electromotive force $u_b$, and internal resistance $r_b$.
+This means that if $I_o$ is used as the objective function, even for the same RBS structure, the MAC result and corresponding switch state could be changed due to different external electrical appliances.
+This increases the difficulty and uncertainty in RBS structure design. 
+On the contrary, by using $\eta$ as the objective function, which dividing $I_o$ and $\max\bm{I}_b$, the influence of these factors on the results is eliminated, as shown in Tabs.
+\ref{tab:given_x} and \ref{tab:find_mac}.
+$\eta$ only reflects the maximum output current capability of the RBS structure.
+Assuming that the maximum allowed current of battery cells in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by calculating the $\eta$ of the structure.
+Therefore, compared to $I_o$, $\eta$ is more suitable for structure design. 
+Most of the currently proposed RBS structures have simple topological characteristics, and the calculation of MACs are relatively simple, even intuitive. 
+However, when complex and flexible structures need to be designed for application scenarios such as equalization or isolation of specific battery cells, the estimation of MAC will become complex and complicated.
+The method proposed in this paper can effectively solve any RBS structure and estimate MAC universally, paving the way for the structure design of more complex and flexible RBSs.
 
-\subsection{Different structures and sizes}
+% 对比Tab. 1和 Tab. 2，可以发现，对于这两种开关状态 $\bm{X}_s$，在电阻和电动势相同的情况下，前者的Io更大。
+% 这主要是由于在Tab. 1的情形下，四个电池以两并两串的形式接入主电路，提供了更多的电动势。
+% 相应的，每个电池的电流也更大。
+% 此时，如果仅使用 Io 作为目标函数，则  （） TODO：讨论怎么说
 
-To further demonstrate the effectiveness of the models and algorithm, RBSs with different structures and sizes are considered.
-On the one hand, the modeling and solving of the three battery structures in Figure \ref{fig:arch} are carried out, where the structure in Figure \ref{fig:arch-e} is proposed by Visairo\cite{visairoReconfigurableBatteryPack2008}, the structure in Figure \ref{fig:arch-f} is proposed by Lawson\cite{lawsonSoftwareConfigurableBattery2012}, and the structure in Figure \ref{fig:arch-ef} is a combination of the two.
-All three structures have 4 battery cells.
-On the other hand, the modeling and solving of the battery structures proposed by Visairo\cite{visairoReconfigurableBatteryPack2008} with different numbers of battery cells (2, 4, and 6 cells) are also carried out.
+% 对电池隔离场景的讨论
+% 当系统中存在被隔离的电池时，该方法可用于判断RBS的输出能否依然满足要求。
+% 对隔离电池后形成的新结构按前文算法进行计算即可得到隔离操作后的MAC。
+% 对L的结构、V的结构和我们的结构，不同隔离电池数下的MAC进行计算
+% L：1~3，eta=1；4，eta=0
+% V：1~4，eta=4~0
+% new：1~4，eta=2，2，1，0
+% 画个图，new（最好情况，最坏情况），L，V
+% 说明最好情况、最坏情况。
+% L的结构，在电池全被隔离前都能提供eta=1的MAC；V的结构，MAC随电池隔离数增加而迅速下降；new的结构，MAC的减少情况介于两者之间。
 
-The greedy algorithm provided accurate estimates of the structure MAC and generated safe and effective switch control strategies, as indicated by the results shown in Figure \ref{fig:d-structure} and \ref{fig:d-size}, where the highlighted red switches denote the closed positions.
-Furthermore, the results about currents in Table \ref{tab:d-structure} and \ref{tab:d-size} show that the output currents are influenced by the external circuit resistance, battery potential, and internal resistance, but are linearly related to the battery currents, consistent with the conclusion about $\eta$ in the previous subsection.
-
-\begin{figure}[htbp]
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/e-dege-mac-4.png}
-        \caption{}
-        \label{fig:d-structure-f4}
-    \end{subfigure}
-    \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/f-dege-mac-4.png}
-        \caption{}
-        \label{fig:d-structure-e4}
-    \end{subfigure}
-    \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/e2f2-dege-mac.png}
-        \caption{}
-        \label{fig:d-structure-e2f2}
-    \end{subfigure}
-    \caption{
-        The switches state when the output current is MAC on structure (a) proposed by Lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b) proposed by Visairo\cite{visairoReconfigurableBatteryPack2008}, and (c) combining  Lawson's and Visairo's structure.
-        The red highlighted lines indicate the open/close states of switches.
-        }
-    \label{fig:d-structure}
-\end{figure}
-
-\begin{table}[h]
-    \centering
-    \caption{
-        detailed results of the proposed method for the RBS with 4 batteries (a) proposed by lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b) proposed by  visairo\cite{visairoReconfigurableBatteryPack2008} and (c) combining both  , including the output current, current of each battery, and $\eta$.}
-    \label{tab:d-structure}
-    \begin{tabular}{cccc}
-        \hline
-        structure &  output current $I_o$       & battery current $\bm{I}_b$       & $\eta$        \\
-        \hline\\
-        Lawson\cite{lawsonSoftwareConfigurableBattery2012} &  $\displaystyle\frac{u_b}{R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{R_o + r_b},0,0,0\right]$   & $1.00$ \\
-        \\
-        Visairo\cite{visairoReconfigurableBatteryPack2008} &  $\displaystyle\frac{4u_b}{4R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b}\right]$   & $4.00$ \\
-        \\
-        combining both &  $\displaystyle\frac{2u_b}{2R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{2R_o + r_b},\frac{u_b}{2R_o + r_b},0,0\right]$   & $2.00$ \\
-        \\
-        \hline
-    \end{tabular}
-\end{table}
-
-\begin{figure}[htbp]
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/f-dege-mac-2.png}
-        \caption{}
-        \label{fig:d-size-2}
-    \end{subfigure}
-    \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/f-dege-mac-4.png}
-        \caption{}
-        \label{fig:d-size-4}
-    \end{subfigure}
-    \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/f-dege-mac-6.png}
-        \caption{}
-        \label{fig:d-size-6}
-    \end{subfigure}
-    \caption{
-        The switches state when the output current is MAC on structure proposed by Visairo\cite{visairoReconfigurableBatteryPack2008} with (a)2, (b)4 and (c) 6 batteries.  
-        The red highlighted lines indicate the open/close states of switches.
-        }
-    \label{fig:d-size}
-\end{figure}
-
-\begin{table}[h]
-    \caption{detailed results of the proposed method for the RBS proposed by visairo\cite{visairoReconfigurableBatteryPack2008} with (a)2, (b)4 and (c) 6 batteries , including the output current, current of each battery, and $\eta$.}
-    \label{tab:d-size}
-    \begin{tabular}{cccc}
-        \hline
-        size &  output current $I_o$       & battery current $\bm{I}_b$       & $\eta$        \\
-        \hline\\
-        2 &  $\displaystyle\frac{2u_b}{2R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{2R_o + r_b},\frac{u_b}{2R_o + r_b},\frac{u_b}{2R_o + r_b},\frac{u_b}{2R_o + r_b}\right]$   & $2.00$ \\
-        \\
-        4 &  $\displaystyle\frac{4u_b}{4R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b},\frac{u_b}{4R_o + r_b}\right]$   & $4.00$ \\
-        \\
-        6 &  $\displaystyle\frac{6u_b}{6R_o + r_b}$ &  $\displaystyle\left[\frac{u_b}{6R_o + r_b},\frac{u_b}{6R_o + r_b},\frac{u_b}{6R_o + r_b},\frac{u_b}{6R_o + r_b}\right]$   & $6.00$ \\
-        \\
-        \hline
-    \end{tabular}
-\end{table}
+% 对于
 

### 2023-05-21 paper/main.tex
modify case study 2/2 and conclustion

@@
 % 0519 修改
-% 背景介绍：随着RBS的结构复杂度的增长，特别是当有电池隔离的情况出现，人工MAC判断越来也困难，需要具有普适性的算法
-% 模型：保留电路模型的相关推导；旧版两个图统一为一个拓扑模型图 topologic model
-% 讨论：电池组拓扑设计新思路，新的复杂结构（仅作验证）；电池隔离（尽量写）
-% 保留电路模型的相关推导
 % 图片：重画所有图，用ppt，注意字体大小、元素含义统一
-% 专有名词的统一：structure, external electrical appliance, components
+% 专有名词的统一：structure, external electrical appliance
 % 伪代码：修改后放附录
@@
 \section{Introduction}
+
+% TODO 提到后面讨论部分的场景
 
@@
 
+% TODO 添加文献，各种结构的
+
 The correctness of the results shown in Fig. \ref{fig:ef-mac} is obvious. 
@@
 
-% 对电池隔离场景的讨论
-% 当系统中存在被隔离的电池时，该方法可用于判断RBS的输出能否依然满足要求。
-% 对隔离电池后形成的新结构按前文算法进行计算即可得到隔离操作后的MAC。
-% 对L的结构、V的结构和我们的结构，不同隔离电池数下的MAC进行计算
-% L：1~3，eta=1；4，eta=0
-% V：1~4，eta=4~0
-% new：1~4，eta=2，2，1，0
-% 画个图，new（最好情况，最坏情况），L，V
-% 说明最好情况、最坏情况。
-% L的结构，在电池全被隔离前都能提供eta=1的MAC；V的结构，MAC随电池隔离数增加而迅速下降；new的结构，MAC的减少情况介于两者之间。
-
-% 对于
+When the RBS has isolated battery cells, the original topology of the structure is altered. 
+However, the method proposed in this paper can still be used to calculate the MAC of the new structure. 
+The MAC after the isolation operation can be obtained by calculating the new structure following the procedures described in the previous subsection.
+During the calculation process, the isolated battery cell(s) do not participate in the calculation, i.e., their nodes, edges, and $SP$s are not considered. 
+The MACs under various isolated battery cell(s) are calculated on the structures proposed by Lawson et al.
+(Fig.
+\ref{fig:arch-e}), Visairo et al.
+(Fig.
+\ref{fig:arch-f}), and the new structure that integrates the previous two structures (Fig.
+\ref{fig:ef-topo}), as shown in Fig.
+\ref{fig:isolated_mac}.
+%TODO: 不同隔离电池数，三种结构，MAC
+For the structure proposed by Lawson et al., the MAC remains the same as that without isolated battery cells, i.e., $\eta=1$, when the number of isolated battery cells increases, until all the cells in the RBS are isolated.
+For the structure proposed by Visairo et al., the MAC decreases as the number of isolated battery cells increases, until $\eta=0$.
+While the new structure has two cases of isolating two cells, one is to isolate two cells within the same substructure, in which case $\eta=2$; the other is to isolate one cell in each of the two substructures, in which case $\eta=1$.
+Overall, the MAC of the new structure is positioned between the structures proposed by Lawson et al. and Visairo et al..
+It can be seen that the MAC of the structure in Fig. \ref{fig:arch-e} is the most stable, and the structure has advantages in isolation and redundancy backup, but its MAC is the smallest. 
+The structure proposed shown by Fig. \ref{fig:arch-f} can output the largest MAC but is susceptible to the number of isolated battery cells. 
+However, the structure proposed by this paper has certain advantages in both aspects, being insensitive to the number of isolated battery cells while simultaneously achieving a larger MAC.
 
@@
 
-A graph model and a circuit model were developed, and a greedy strategy was employed to solve the MAC. 
-The proposed method was tested on RBSs of varying structures and sizes. 
-Additionally, an indicator, denoted by $\eta$ , was introduced to evaluate the performance of the RBS's output current. 
-This work presents an effective approach for designing and evaluating the output current performance of RBS. 
+This paper firstly proposes a method to calculation the MAC of RBS according to its architecture. 
+To find the circuit in RBS that enable the MAC, a greedy strategy incorporate with the topologic model is developed to. 
+The effectiveness of proposed method is tested on a more complex RBS structure based on two proposed structure.
+This work presents an effective approach to evaluate the MAC of RBS, which is essential for design and management of the RBS. 
 Future research could focus on developing new performance indicators for evaluating RBS performance using the currents and voltages obtained by this method, as well as modifying the equivalent model of the battery to enable more accurate simulations of RBS, including transient analysis.
 
-\section{Appendix}
+\section{Appendix} %TODO 待修改
 \begin{algorithm}

### 2023-05-22 paper/main.tex
modify contains and figures

@@
-% 0519 修改
-% 图片：重画所有图，用ppt，注意字体大小、元素含义统一
-% 专有名词的统一：structure, external electrical appliance
-% 伪代码：修改后放附录
-
 \documentclass{article}
@@
 \setcounter{MaxMatrixCols}{20}
-
+\usepackage{tikz}
+\usetikzlibrary{
+  arrows.meta,
+  calc,
+  fit,
+  positioning,
+  quotes,
+  graphs,
+  shapes.geometric
+}
 \def\T{\mathrm{T}}
@@
     In this paper, the MAC of the RBS is calculated by using a greedy algorithm based on the topologic model of the RBS.
-    The effectiveness of this method is validated on the RBSs with different structures.
-    % #TODO
+    The effectiveness of this method is validated on a more complex RBS structure based on two proposed structure.
+    The MAC and the computational method proposed in this article pave the way for more flexible design and more complex application scenarios, such as battery cell isolation, for RBS.
 
@@
 \section{Introduction}
-
-% TODO 提到后面讨论部分的场景
 
@@
     \centering
-    \begin{subfigure}[b]{0.15\textwidth}
+    \begin{subfigure}[b]{0.2\textwidth}
         \includegraphics[width=\textwidth]{../attachments/arch-e.png}
@@
 Then, a greedy algorithm is employed to search the available circuit of the RBS for reaching the MAC.
-With the developed method, MAC of RBSs with different structures can be calculated effectively.
+With the developed method, MAC of RBSs with different structures can be calculated effectively, including application scenarios with isolated battery cells.
 
@@
 Section II presents the framework and details of the proposed topologic model and the greedy algorithm.
-In Section III, a case study of using the proposed model and algorithm to enumerate the MAC of a specific structure is demonstrated.
+In Section III, a case study of using the proposed model and algorithm to enumerate the MAC of a new and complex structure is demonstrated.
+The calculation results and scenarios such as battery cells isolation also are discussed
 Finally, the concluding remarks are drawn in Section IV.
@@
 In the end, the open/close strategy of the RBS is implemented by greedily selecting the SPs to achieve MAC and quantitatively calculated in the equivalent circuit.
-% 只有一个 topologic model，建模；先根据连接关系和物理参数建立目标函数和约束；再找SP；最后根据贪婪算法求解MAC。
 
-% TODO: fig 整体框图
-\begin{figure}
+\begin{figure}[htbp]
     \centering
-    \includegraphics[width=\textwidth]{../attachments/main-v4.png}
-    \caption{Diagram of this method. 
-        It includes a graph model and an equivalent circuit model based on the actual RBS.
-        The shortest path of each battery is obstained from the graph model, and the voltage and current of the equivalent circuit model are calculated.
-        By greedily searching for the combination of the shortest path, the MAC is calculated in the equivalent circuit model.
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/main.png}
+        \caption{}
+        \label{fig:main}
+    \end{subfigure}
+    \\ 
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/battery_simple.png}
+        \caption{}
+        \label{fig:battery_simple}
+    \end{subfigure}
+    \caption{(a)Diagram of this method, which contains four main steps.
+    Step 1: The RBS structure is converted to a topologic model.
+    Step 2: Constraints and objective function are obtained based on the previous topologic model.
+    Step 3: The shortest path of each battery in the RBS is obtained by Dijkstra algorithm.
+    Step 4: The MAC is achieved by greedily selecting the shortest paths to open/close switches.
+    (b) The equivalent circuit of a battery in this method, with $u_{b,i}$ and $r_{b,i}$ representing the voltage and internal resistance of the battery $i$ respectively.
+    The capacitor in Thevenin model is ignored.
     }
-    \label{fig:main}
 \end{figure}
@@
 
-The normal equivalent circuit for a battery consists of a voltage source in series with a resistor, and a capacitor in parallel with another resistor to simulate the polarization in batteries.
+The normal equivalent circuit for a battery consists of a voltage source in series with a resistor, and a capacitor in parallel with another resistor to simulate the polarization in batteries, kwon as Thevenin model\cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
 To simplify the model, the transient characteristics of the circuit are not considered, so the capacitor mentioned above is ignored.
-In this way, the battery $i$ in the RBS is modeled by the series connection in between a constant voltage source $u_{b,i}$ and a resistor $r_{b,i}$,  as shown in Fig. %TODO 电池模型有电阻电容简化为电阻的示意图。
+In this way, the battery $i$ in the RBS is modeled by the series connection in between a constant voltage source $u_{b,i}$ and a resistor $r_{b,i}$,  as shown in Fig. \ref{fig:battery_simple}
 And a binary variable $x_j$ is used to represent the state of switch $j$, where 0 for ON and 1 for OFF, respectively.
@@
 $SP_i$ is defined as the path with the minimum $\omega$ for battery $i$.
-\begin{equation}
+\begin{equation}\label{eq:def_sp}
     SP_i = \mathop{\arg\min}_{p \in P_i} \omega(p),
@@
 The overall flowchart is shown in Fig. \ref{fig:flowchart}, and the corresponding pseudo-code of the algorithm is shown in Algorithm \ref{alg:eta_RBS}.
-% TODO 算法流程图
 
+\tikzset{
+  meta box/.style={
+    draw,
+    black,
+    very thick,
+    text centered,
+  },
+  punkt/.style={
+    meta box,
+    rectangle,
+    rounded corners,
+    inner sep=.25em,
+    minimum height=2em,
+    minimum width=4em,
+    align=center,
+    text width=10em
+  },
+  round/.style={
+    meta box,
+    circle,
+    minimum size=0,
+    inner sep=0pt, 
+    outer sep=0pt
+  },
+  every fit/.style={
+    draw,
+    thick,
+    dashed,
+    gray,
+    inner xsep=.5em,
+    inner ysep=.75em
+  }
+}
+\begin{figure}
+\begin{tikzpicture}[font=\small, node font=\small, node distance=1.5em]
+    \node[punkt]     (input) {Input: RBS structure};
+    \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Eqs. \ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
+    \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Eq. \ref{eq:A}};
+    \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{set}=N_b$ };
+    \node[punkt, below=0.3of get_Nset] (get_cb) {get $c_b$s by combinating $N_{set}$ batteries from $N_b$};
+    \node[draw, diamond, aspect=2, below=0.3of get_cb] (is_check_all_cb) {are all $c_b$s checked?};
+    \node[draw, diamond, aspect=2, right=1of is_check_all_cb] (is_Nset_converged) {is $N_{set}$ converged?};
+    \node[punkt, above=of is_Nset_converged] (reset_Nset) {reset $N_{set}$ by dichotomy};
+    \node[punkt, text width=15em, below=0.3of is_check_all_cb] (get_Xs) {
+        select an unchecked $c_b$, and get its $\bm{X}_m$ by \\ 
+        if switch $j$ $\in \bigcup_{i\in c_b}SP_i$:\\
+        $\bm{X}[j]=1$ else $0$};
+    \node[punkt, below=0.3of get_Xs] (get_Yn) {get $\bm{Y}_n$ by Eq.\ref{eq:Yn}};
+    \node[draw, diamond, aspect=2, below=0.3of get_Yn] (is_Yn_invertible) {is $\bm{Y}_n$ invertible?};
+    \node[punkt, right=1.3of is_Yn_invertible] (construct) {construct an effective solution};
+    \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Eqs. \ref{eq:I_o} and \ref{eq:I_b}};
+    \node[draw, diamond, aspect=2, below=0.3of get_I] (is_leq_Im) {is $\max \bm{I}_b \leq I_m$?};
+    \node[punkt, right=1.3of is_leq_Im] (drop_eta) {drop this $\eta$};
+    \node[punkt, below=0.3of is_leq_Im] (get_eta) {get $\eta$ by Eq.\ref{eq:eta}};
+    \node[punkt, below=0.3of get_eta] (update_max_eta) {update $\max \eta$};
+    \node[punkt, right=1of is_Nset_converged] (output) {Output: $\max \eta$};
+    \node[round,left=1.5of update_max_eta](point1){};
+
+    \graph{
+      (input) -> (get_SP) -> (get_A) -> (get_Nset) -> (get_cb) -> (is_check_all_cb) ->["No"] (get_Xs) -> (get_Yn) -> (is_Yn_invertible) ->["Yes"] (get_I) -> (is_leq_Im) ->["Yes"] (get_eta) -> (update_max_eta);
+      (is_check_all_cb) ->["Yes"] (is_Nset_converged) ->["No"] (reset_Nset) -> (get_cb);
+      (is_Yn_invertible) ->["No"] (construct) ->[to path={|- (\tikztotarget)}] (get_I);
+      (is_leq_Im) ->["No"] (drop_eta) ->[to path={|- (\tikztotarget)}] (update_max_eta);
+      (is_Nset_converged) ->["Yes"] (output);
+      (update_max_eta) -- (point1) ->[to path={|- (\tikztotarget)}] (is_check_all_cb);
+    };
+\end{tikzpicture}
+\caption{The computational flowchart of the proposed method in this paper.}\label{fig:flowchart}
+\end{figure}
 \section{Case Study}
@@
 
-% TODO: 图，我们的结构；以及与之前两种结构的关系
-% fig:arch-ef
+\begin{figure}[htbp]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/arch-ef.png}
+        \caption{}
+        \label{fig:arch-ef}
+    \end{subfigure}
+    \hspace{0.05\textwidth}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/ef-topo.png}
+        \caption{}
+        \label{fig:ef-topo}
+    \end{subfigure}
+    \caption{
+        (a) The new RBS structure proposed in this paper, which is obtained by replacing the batteries in Fig.
+\ref{fig:arch-e} with the structure in Fig.
+\ref{fig:arch-f}, as shown in the dashed boxes in the figure.
+        (b) The corresponding topologic model of the new RBS structure, which is a directed graph.
+        The nodes represent the connection points of the battery cells and/or the switches.
+        The green,gray and blue directed edges represent the battery cells, the switches and the external electrical appliance, respectively.
+    }
+\end{figure}
 
@@
 \subsection{Calculation details and result}
-
-% TODO: 图，结构的有向图，注意颜色，绿色、灰色、蓝色
-% fig:ef-topo
 
@@
 
+\begin{figure}[htbp]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/ef-sp1.png}
+        \caption{}
+        \label{fig:sp1}
+    \end{subfigure}
+    \hspace{0.05\textwidth}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/ef-sp2.png}
+        \caption{}
+        \label{fig:sp2}
+    \end{subfigure}
+    \\
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/ef-sp3.png}
+        \caption{}
+        \label{fig:sp3}
+    \end{subfigure}
+    \hspace{0.05\textwidth}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/ef-sp4.png}
+        \caption{}
+        \label{fig:sp4}
+    \end{subfigure}
+    \caption{
+        The $SP$s of battery cell (a)$B_1$ (b)$B_2$ (c)$B_3$ (d)$B_4$ in the new structure's topological model, which is highlighted in red.
+        }
+\end{figure}
+
 \begin{table}[htbp]
@@
 
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.5\textwidth]{../attachments/ef-mac.png}
+    \caption{
+        The finally calculation result of MAC for the new structure with four battery cells and 19 switches.
+        The red lines represent the branches through which the current flows, and the switches on these branches are ON. 
+        In this situation, the RBS outputs MAC to the outside, which is $\eta=2$.
+    }\label{fig:ef-mac}
+\end{figure}
+
 \subsection{Discussion}
-
-% TODO 添加文献，各种结构的
 
@@
 Therefore, compared to $I_o$, $\eta$ is more suitable for structure design. 
-Most of the currently proposed RBS structures have simple topological characteristics, and the calculation of MACs are relatively simple, even intuitive. 
+Most of the currently proposed RBS structures have simple topological characteristics, and the calculation of MACs are relatively simple, even intuitive. % #TODO 添加cite
 However, when complex and flexible structures need to be designed for application scenarios such as equalization or isolation of specific battery cells, the estimation of MAC will become complex and complicated.
@@
 % 相应的，每个电池的电流也更大。
-% 此时，如果仅使用 Io 作为目标函数，则  （） TODO：讨论怎么说
+% 此时，如果仅使用 Io 作为目标函数，则  （） #TODO：讨论怎么说
 
@@
 \ref{fig:isolated_mac}.
-%TODO: 不同隔离电池数，三种结构，MAC
 For the structure proposed by Lawson et al., the MAC remains the same as that without isolated battery cells, i.e., $\eta=1$, when the number of isolated battery cells increases, until all the cells in the RBS are isolated.
@@
 However, the structure proposed by this paper has certain advantages in both aspects, being insensitive to the number of isolated battery cells while simultaneously achieving a larger MAC.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.8\textwidth]{../attachments/isolated_mac.png}
+    \caption{
+        The variation of MAC with the number of isolated battery cells for different RBS structures, including the structure proposed by Lawson et al., Visairo et al.
+, and the new structure in this paper.
+    }\label{fig:isolated_mac}
+\end{figure}
 

### 2023-05-22 paper/my_flowchat.tex
modify contains and figures

--- 2023-05-21 paper/main.tex
@@
-% 0519 修改
-% 背景介绍：随着RBS的结构复杂度的增长，特别是当有电池隔离的情况出现，人工MAC判断越来也困难，需要具有普适性的算法
-% 模型：保留电路模型的相关推导；旧版两个图统一为一个拓扑模型图 topologic model
-% 讨论：电池组拓扑设计新思路，新的复杂结构（仅作验证）；电池隔离（尽量写）
-% 保留电路模型的相关推导
-% 图片：重画所有图，用ppt，注意字体大小、元素含义统一
-% 专有名词的统一：structure, external electrical appliance, components
-% 伪代码：修改后放附录
-
 \documentclass{article}
-\usepackage{graphicx}
-\usepackage{subcaption}
-\usepackage{enumerate}
-\usepackage{amsmath}
-\DeclareMathOperator{\diag}{diag}
-\usepackage{multirow}
-\usepackage{booktabs}
+\usepackage[showframe]{geometry}
+\usepackage{tikz}
 \usepackage{bm}
-\usepackage[ruled,linesnumbered]{algorithm2e}
-\setcounter{MaxMatrixCols}{20}
-
-\def\T{\mathrm{T}}
-
-\title{A Greedy-based calculation method of RBS maximum allowable current}
-\author{3057761608 }
-
+\usetikzlibrary{
+  arrows.meta,
+  calc,
+  fit,
+  positioning,
+  quotes,
+  graphs,
+  shapes.geometric
+}
 \begin{document}
-
-\maketitle
-
-\begin{abstract}
-    Reconfigurable Battery Systems (RBSs) offer a promising alternative to traditional battery systems owing to their dynamical topologic structure for the optimization of battery cell charging and discharging stragegies.
-    During the operation of the RBS, the Maximum Allowable Current (MAC) is a critical indicator to guide the reconfiguring control of the system in terms of safety and reliability.
-    In this paper, the MAC of the RBS is calculated by using a greedy algorithm based on the topologic model of the RBS.
-    The effectiveness of this method is validated on the RBSs with different structures.
-    % #TODO
-
-    keywords: Reconfigurable Battery System, Maximum Allowable Current, Greedy Algorithm
-\end{abstract}
-
-\section{Introduction}
-
-Battery Energy Storage Systems (BESSs) are widely used to store and supply high-quality electrical energy in various applications, such as smart grids and wind power plants \cite{desiqueiraControlStrategySmooth2021,karandehTwoStageAlgorithmOptimal2019,yangBatteryEnergyStorage2018,choCommercialResearchBattery2015}.
-Typically, a BESS consists of numerous battery cells that are interconnected by series-parallel circuitry to provide the required charge storage capacity and output voltage.
-For the traditional BESS, the connections between batteries are fixed and the performance of system is limited by the worst cell, as the result of the cask effect.
-Furthermore, reliability and even safety issues will alse be aroused since the failed battery cannot be promptly isolated to exacerbate the degradation of the other batteries during the operational process \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019}.
-Undoubtedly theses issues hinder the practical application of traditional BESSs.
-
-Reconfigurable Battery System (RBS), which can dynamically switch to arbitrary circuit configurations as required, is expected to solve the above problem\cite{hanNextGenerationBatteryManagement2020a}.
-The ability to switches circuit helps to isolate unhealthy batteries from the circuit in a timely manner, thereby improving the safety and reliability of the battery system.
-Fig. \ref{fig:arch} shows two popular typologies of the RBSs developed by Lawson\cite{lawsonSoftwareConfigurableBattery2012} and Visairo \cite{visairoReconfigurableBatteryPack2008} respectively. 
-Taking the RBS shown in Fig.
-\ref{fig:arch-e} as example, the batteries in the RBS can beare connected not only in series when the switches $S_1$, $S_5$, $S_6$, $S_7$, $S_8$, $S_9$, and $S_{13}$ are closed, but also in parallel when $S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$, and $S_{13}$ are closed.
-Furthermore, when an unhealthy battery, for instance the orange one in Fig.
-\ref{fig:arch-f}, exits in the RBS, it can be isolated by closing its three adjacent switches (i.e.
-$S_5$, $S_7$ and $S_8$) and opening the switch below that battery (i.e.
-$S_6$) to ensure the system still remains a reliable working mode.
-
-\begin{figure}[htbp]
-    \centering
-    \begin{subfigure}[b]{0.15\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/arch-e.png}
-        \caption{}
-        \label{fig:arch-f}
-    \end{subfigure}
-    \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/arch-f.png}
-        \caption{}
-        \label{fig:arch-e}
-    \end{subfigure}
-    \caption{The RBS structure proposed by (a)Lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b)Visairo\cite{visairoReconfigurableBatteryPack2008}.}
-    \label{fig:arch}
-\end{figure}
-
-The complex connecting structure between batteries and switches enables the flexibility of the RBS, but also brings the challenges in design and control cost.
-The Maximum Allowable Current (MAC) of the RBS system is defined as the maximum current that is allowed for each individual battery of the system, and is a critical indictor to be evaluate the RBS output current to the electronic appliances.
-It helps the designer to assess whether the RBS meets the output current requirements, and contributes to the formulation of appropriate and safe management stragegies for the battery management system (BMS).
-As the complexity of RBS increases, especially when the certain battery needs to be isolated, it becomes difficult to visually obtain the MAC, and a universal algorithm is needed to solve the MAC.
-Despite its importance, there is currently no method available to evaluate MAC for RBSs.
-Therefore, the purpose of this paper is to propose a universal and effective method for calculating the MAC of the RBS.
-To achieve this, a topologic model that builds the relationship between RBS circuit topology and internal resistance and voltage of its batteries are established.
-Then, a greedy algorithm is employed to search the available circuit of the RBS for reaching the MAC.
-With the developed method, MAC of RBSs with different structures can be calculated effectively.
-
-The remainder of this paper is organized as follows:
-Section II presents the framework and details of the proposed topologic model and the greedy algorithm.
-In Section III, a case study of using the proposed model and algorithm to enumerate the MAC of a specific structure is demonstrated.
-Finally, the concluding remarks are drawn in Section IV.
-
-\section{Methodology}
-
-The overall MAC modeling process from an RBS structure is shown in Fig. \ref{fig:main}, which can be divided into four main steps.
-In the first place, the actual RBS structure is converted to a topologic model, in which the connected relationships between batteries and switches are abstracted and the performance parameters of the batteries are retained.
-Subsequently, constraints and objective function, i.e. MAC, are obtained based on the previous connected relationships and parameters.
-Then, the shortest path (SP) of each battery in the RBS is obtained by Dijkstra algorithm.
-In the end, the open/close strategy of the RBS is implemented by greedily selecting the SPs to achieve MAC and quantitatively calculated in the equivalent circuit.
-% 只有一个 topologic model，建模；先根据连接关系和物理参数建立目标函数和约束；再找SP；最后根据贪婪算法求解MAC。
-
-% TODO: fig 整体框图
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{../attachments/main-v4.png}
-    \caption{Diagram of this method. 
-        It includes a graph model and an equivalent circuit model based on the actual RBS.
-        The shortest path of each battery is obstained from the graph model, and the voltage and current of the equivalent circuit model are calculated.
-        By greedily searching for the combination of the shortest path, the MAC is calculated in the equivalent circuit model.
-        } 
-    \label{fig:main}
-\end{figure}
-
-\subsection{Topologic Model}
-
-As demonstrated in Fig. \ref{fig:arch}, a typical RBS is made up of a number of battery cells and switches in a dynamically adjustable connection.
-To establish a processable circuit, these batteries and switches are transformed into ideal elements under reasonable assumptions.
-The resulting circuit structure is then described in matrix form, and the related equations are provided.
-
-The normal equivalent circuit for a battery consists of a voltage source in series with a resistor, and a capacitor in parallel with another resistor to simulate the polarization in batteries.
-To simplify the model, the transient characteristics of the circuit are not considered, so the capacitor mentioned above is ignored.
-In this way, the battery $i$ in the RBS is modeled by the series connection in between a constant voltage source $u_{b,i}$ and a resistor $r_{b,i}$,  as shown in Fig. %TODO 电池模型有电阻电容简化为电阻的示意图。
-And a binary variable $x_j$ is used to represent the state of switch $j$, where 0 for ON and 1 for OFF, respectively.
-To simplify the calculation, a closed switch is considered as a resistor with a very small resistance value $r_s$.
-
-For a given RBS structure, the topologic model for the RBS is constructed as a directed graph $G(V,E)$ in such a way that:
-\begin{enumerate}
-    \item Nodes: node $v_1$ and $v_N$ represent the anode and cathode of the RBS respectively, and the other nodes $v_2,\cdots , v_{N-1}$ represent the points connecting batteries and/or switches, where $N$ is the total number of nodes.
-    \item Edges: the directed edges represent batteries, switches and the external electrical appliance in the output circuit based on whether the current direction is constrainted or not. 
-        When the battery is in operation, the internal current direction must be from the negative electrode to the positive electrode, so it is represented by a directed edge from the negative to the positive ; this edge has attributes $(u_b, r_b)$, where $u_b$ and $r_b$ represent battery $b$'s electromotive force and internal resistance.
-        Switches have no constraints on the current direction, so they are represented by a pair of directed edges with opposite directions; these edges both have attribute $(0, r_s)$, where $r_s$ represents the resistance of switch as mentioned above.
-        To fully solve for the current and voltage, an external electrical appliance equivalent as a resistor $R_0$ is connected to the anode and cathode of the RBS and represented by a directed edge from the anode $v_N$  to the cathode $v_1$ of the RBS.
-        Similarly, this edge has attribute $(0, R_0)$.
-        If a given RBS structure has $N_b$ batteries and $N_s$ switches in total, then the number of edges is $N_b+2N_s+1$, where 1 refers to the external electrical appliance.
-\end{enumerate}
-
-\subsection{Constraints and Objective Function}
-
-The constraints and objective function are obtained by analyzing the currents of batteries and external electrical appliance, as following.
-Based on the above directed graph which has $N$ nodes and $N_b+2N_s+1$ directed edges, its incidence matrix $\bm{A}$ is defined as
-\begin{align}\label{eq:A}
-    a_{ij}=
-    \begin{cases}
-        1,  & \text{edge  $j$ leaves vertex $i$},\\
-        -1, & \text{edge $j$ enters vertex $i$},\\
-        0,  & \text{otherwise}.
-    \end{cases}
-\end{align}
-Since each column of $\bm{A}$ sums to zero, the last line are deleted.
-Furthermore, because of a couple of opposite directed edges for each switch, the $N_s$ columns corresponding to the switches are also deleted.
-Finally, the reduced incidence matrix $\bm{A}_{(N-1)\times(N_b+N_s+1)}$ are used in the following calculation.
-By divided as batteries, switches and external electrical appliance, $A$ is rewritten as follows
-\begin{equation}
-    \bm{A} =
-    \begin{bmatrix}
-        \bm{A}_b & \bm{A}_s & \bm{A}_o
-    \end{bmatrix}.
-\end{equation}
-
-$N_b+N_s+1$ edges' currents $\bm{I}_{(N_b+N_s+1)\times 1}$ and voltages $\bm{U}_{(N_b+N_s+1)\times 1}$, and $N-1$ nodes' voltages $\bm{U}_{n, (N-1)\times 1}$ have following relationships from Kirchhoffs law
-\begin{align}\label{eq:Kirchhoffs_law}
-    \begin{cases}
-        \bm{A} \bm{I} = \bm{0}, \\
-        \bm{U}        = \bm{A}^\T \bm{U}_n.
-    \end{cases}
-\end{align}
-These directed edges are treated as generalized branches and expressed in matrix form as follows
-\begin{equation}\label{eq:generalized_branches}
-    \bm{I} = \bm{Y}\bm{X} \bm{U} - \bm{Y}\bm{X} \bm{U}_s +\bm{I}_s,
-\end{equation}
-where $\bm{I}$ and $\bm{U}$ are the column vectors about $1+N_b+N_s$ edges' current and voltage, respectively;
-$\bm{U}_s$ and $\bm{I}_s$ denote the source voltage and source current of the generalized branches, respectively;
-$\bm{Y}$ is the admittance matrix of the circuit, and $\bm{X}$ is the state matrix defined as
-\begin{equation}\label{eq:X}
-    \bm{X} = \diag(
-    \underbrace{1, \cdots, 1}_{N_b~\text{of}~1},
-    \underbrace{1, 0 \cdots, 1}_{N_s~\text{of}~0/1},
-    1)
-    =\begin{bmatrix}
-        \bm{I} & & \\
-        & \bm{X}_s &\\
-        & &\bm{I}
-    \end{bmatrix}.
-\end{equation}
-
-In addition to the equivalent circuit assumptions, we also assume that all batteries have the same internal resistance value $r_b$ and supply the same electric potential $u_s$ to simplify the model.
-Then the output current $I_o$ and each battery's current $\bm{I}_b$ can be given by solving the simultaneous Eq. \ref{eq:Kirchhoffs_law} and \ref{eq:generalized_branches} eventually.
-Let
-\begin{equation}\label{eq:Yn}
-    \bm{Y}_n (\bm{X}_s) = \frac{1}{R_o} \bm{A}_o\bm{A}_o^\T + \frac{1}{r_b} \bm{A}_b\bm{A}_b^\T + \frac{1}{r_s}\bm{A}_s\bm{X}_s\bm{A}_s^\T,
-\end{equation}
-where $R_o$ is the equivalent resistance of the external circuit.
-Then, if $\bm{Y}_n$ is an invertible matrix,
-\begin{align}
-    I_o(\bm{X}_s)      & = \frac{u_b}{R_o r_b} \bm{A}_o^\T \bm{Y}_n^{-1}(\bm{X}) \bm{A}_b \bm{I}_{N_b\times 1};\label{eq:I_o}\\
-    \bm{I}_b(\bm{X}_s) & = \frac{u_b}{r_b^2}[\bm{A}_b^\T \bm{Y}_n^{-1}(\bm{X}) \bm{A}_b\bm{I}_{N_b \times 1}  -r_b \bm{I}_{N_b \times 1}],\label{eq:I_b}
-\end{align}
-where $\bm{I}_{N_b\times 1}$ is a column vector with all equal to 1.
-
-In this study, the ratio of $I_o$ and $\max (\bm{I}_b)$ is used to characterize the maximum allowable current for a given RBS architecture, denoted as $\eta$:
-\begin{equation}\label{eq:eta}
-    \eta = \frac{I_o}{\max (\bm{I}_b)}.
-\end{equation}
-The discussion in the next section will show that the $\eta$ reflects the ability of the RBS architecture itself to deliver current, regardliess of the battery cells used by the RBS.
-Finally the problem in RBS can be formulated as
-\begin{align}
-    & \max \eta \label{eq:max_eta}\\
-    \text{s.t.} & \max (\bm{I}_b) \leq I_m, \label{eq:Ib_leq_Im}
-\end{align}
-where $I_m$ is the maximum allowable current of the battery; $\eta$ can be calculated by Eq. \ref{eq:eta}; $I_o$ and $\bm{I}_b$ can be calculated by Eq. \ref{eq:I_o} and \ref{eq:I_b}.
-However, it is computationally difficult to solve \ref{eq:max_eta} directly because of the presence of matrix $\bm{Y}_n^{-1}$.
-As the number of batteries and switches in the RBS increase, the order of the matrix increases, and the time costed to compute increases sharply.
-A greedy algorithm will be proposed to solve this problem in the next subsection.
-
-The integrability of the matrix $\bm{Y}_n$ is explained here.
-Although the above solution procedure requires the matrix $\bm{Y}_n$ to be invertible, it is still possible to encounter integrable $\bm{Y}_n$ in the calculation.
-The physical meaning of this case corresponds to the fact that due to the excessive number of switches in OFF, the solved circuit structure forms circuit branches independent of the main circuit, i.e., the circuit connected to the anode and cathode of the RBS.
-Since these independent branches are not connected to the main circuit, the voltage potentials of these branches cannot be determined and theoretically an infinite number of sets of solutions exist. 
-Benfit from the independence, these solutions have no influence on the results of the main circuit. 
-Since only the currents and voltages of the main circuit are of interest, only one of these solutions needs to be chosen for subsequent calculation.
-
-\subsection{Greedy Solution}\label{subsec:greedy_solution}
-
-In this subsection, a greedy algorithm is proposed based on shortest paths ($SP$s), which is given here firstly.
-When the battery $i$ is connected to the anode $v_1$ and the cathode $v_N$ of the RBS by the path $p$ in the graph model, the distance $\omega$ of $p$ is defined by the following equation:
-\begin{equation}\label{eq:weight}
-    \omega(p) = N_s \cdot n_b (p) + n_s (p),
-\end{equation}
-where $N_s$ is the total number of switches in the system; $n_b(p)$ and $n_s(p)$ are number of batteries and switches in the path $p$ respectively.
-$SP_i$ is defined as the path with the minimum $\omega$ for battery $i$.
-\begin{equation}
-    SP_i = \mathop{\arg\min}_{p \in P_i} \omega(p),
-\end{equation}
-where $P_i$ is the set of all paths from $v_1$ to $v_N$ and passed through the directed edge $i$ in the direction of it.
-Specifically, the Dijkstra algorithm can be used to implement the $SP_i$.
-According to the definition, $SP_i$ gives the simplest strategy by which the control of battery $i$ is achieved with a minimum of switches while minimizing the influence of other batteries.
-From the perspective of series/parallel, the more batteries are connected into circuit via their $SP$s, the more batteries are connected in parallel.
-Since batteries can provide more total output current when connected in parallel than in series, the algorithm greedily selects as many cells as possible to be connected into to the overall circuit via their $SP$s to obtain the MAC.
-The dichotomy method is also performed to faster find the right number of $SP$s.
-
-After finding the potential SPs combinations about the MAC, the state variable $\bm{X}_s$ of the switches can be determined, and the optimization problem \ref{eq:max_eta} can be solved using Eq.
-\ref{eq:eta}, \ref{eq:I_o} and \ref{eq:I_b}.
-The overall flowchart is shown in Fig. \ref{fig:flowchart}, and the corresponding pseudo-code of the algorithm is shown in Algorithm \ref{alg:eta_RBS}.
-% TODO 算法流程图
-
-\section{Case Study}
-
-This section presents a case study to demonstrate the effectiveness of the proposed method.
-A more intricate structure, which integrates the two previously proposed structures, is proposed.
-The effectiveness of the aforementioned algorithm is substantiated on this structure to confirm its applicability in practical scenarios.
-Moreover, the algorithm's versatility is also established through its application in complex cases such as the presence of isolated battery cell.
-
-\subsection{Determination of a new RBS structure}
-
-% TODO: 图，我们的结构；以及与之前两种结构的关系
-% fig:arch-ef
-
-The RBS structure proposed by Lawson et al\cite{lawsonSoftwareConfigurableBattery2012}, shown in Fig.
-\ref{fig:arch-e}, easily enables the isolation of arbitrary cells or the addition of redundant cells to the system, but these cells are limited to being connected in series only and the switch between cells connection modes is not flexible.
-In contrast, the structure proposed by Visairo et al\cite{visairoReconfigurableBatteryPack2008}, shown in Fig.
-\ref{fig:arch-f}, allows the flexibility to switch the cells between series, parallel and mixed series-parallel modes, thus allowing dynamic voltage adjustment according to the external load and improving energy conversion efficiency, but is not as simple as the structure by Lawson et al in terms of isolating cells or adding redundancy.
-In order to combine the advantages of both structures, a new structure is obtained by replacing the batteries in Fig.
-\ref{fig:arch-e} with the structure in Fig.
-\ref{fig:arch-f}, as shown in Fig.
-\ref{fig:arch-ef}.
-This more complex structure has the structure of Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} as the main frame and the structure of Visairo et al.\cite{visairoReconfigurableBatteryPack2008} as the substructure.
-In this way, the circuit topology of the substructure (i.e.
-the structure in the box in Fig.
-\ref{fig:arch-ef}) can be changed to enable dynamic and flexible voltage adjustment according to the load, while at the same time taking advantage of the ease of battery isolation and increased redundancy of the main frame.
-The next subsections will use this structure with 4 battery cells and 19 switches as an example to demonstrate the effectiveness of the proposed algorithm.
-
-\subsection{Calculation details and result}
-
-% TODO: 图，结构的有向图，注意颜色，绿色、灰色、蓝色
-% fig:ef-topo
-
-The graph in Fig. \ref{fig:ef-topo} represents the topologic model based on the new RBS structure mentioned in the last subsection (Fig. \ref{fig:arch-ef}).
-The model is presented in the form of a directed graph, capturing the connection relationship between the battery and switch in the circuit.
-Battery cell 1, 2, 3, and 4 are represented by green directed edges in the graph, while nineteen switches are represented by gray directed edges with opposite directions.
-The external electrical appliance is considered as a directed edge from the cathode of the RBS ( node $18$ in the graph) to the anode ( node $1$ in the graph), represented as the blue directed edge in the graph.
-Totally, there are 19 nodes and 43 edges in the graph.
-
-Based on the node-edge relationship given in Fig. \ref{fig:ef-topo}, the incidence matrix $\bm{A}$ can be obtained according to Eq. \ref{eq:A}:
-\begin{equation}
-    \bm{A} = 
-    \begin{bmatrix}
-        \bm{A}_b & \bm{A}_s & \bm{A}_o
-    \end{bmatrix},
-\end{equation}
-
-\begin{equation}
-    \bm{A}_b^\T = 
-    \begin{bmatrix}
-        0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 \\
-    \end{bmatrix},
-\end{equation}
-
-\begin{equation}
-    \bm{A}_s^\T = 
-    \begin{bmatrix}
-        1 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 1 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 1 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 1 & 0 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 &-1 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 &-1 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 &-1 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 &-1 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 &-1 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 \\
-    \end{bmatrix},
-\end{equation}
-
-\begin{equation}
-    \bm{A}_o^\T = 
-    \begin{bmatrix}
-       -1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-    \end{bmatrix}.
-\end{equation}
-The state matrix $\bm{X}$ is determined by the switches' state, that is, the specific configuration of the RBS.
-For example, when switch $S_1$, $S_3$, $S_5$, $S_6$, $S_8$, $S_9$, $S_{11}$, $S_{13}$, $S_{14}$, $S_{16}$, $S_{17}$ and $S_{19}$ are ON, and the rest of the switches are OFF, the state matrix $\bm{X}$ is given by
-\begin{equation}
-    \bm{X} = diag(
-    \underbrace{1,0,1,0,1,1,0,1,1,0,1,0,1,1,0,1,1,0,1}_{\text{switches}},
-    \underbrace{1,1,1,1}_{\text{batteries}},
-    1
-    ).
-\end{equation}
-By substituting the above specific values of $\bm{A}$ and $\bm{X}$ above into Eqs.
-\ref{eq:Yn}, \ref{eq:I_o}, \ref{eq:I_b} and \ref{eq:eta} in turn, the $\eta$ at the current situation, i.e.
-battery cell $B_1$ and $B_2$, $B_3$ and $B_4$ are connected in parallel with each other, and then connected in series to supply the external electrical appliance, can be obtained after the sequential calculation.
-The results are shown in Tab. \ref{tab:given_x}.
-
-\begin{table}[htbp]
-  \centering
-    \caption{Calculating result of the output current $I_o$, battery current $\bm{I}_b$ and ratio $\eta$ for a specificed switches state $\bm{X}_m$ in the structure combining Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} and Visairo et al.\cite{visairoReconfigurableBatteryPack2008} with 4 battery cells and 19 switches.}
-    \begin{tabular}{cc}
-    \toprule
-        Structure & 4 battery cells and 19 switches  \\
-        % Structure & combining Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} and Visairo et al.\cite{visairoReconfigurableBatteryPack2008} with 4 battery cells and 19 switches  \\
-    \midrule
-    Switch ON & 1,3,5,6,8,9,11,13,14,16,17,19 \\
-        $\bm{X}_s$ & $\diag(1,0,1,0,1,1,0,1,1,0,1,0,1,1,0,1,1,0,1)$ \\
-    \midrule
-        $I_o$ & $2u_b/(R_o+r_b)$ \\
-        $\bm{I}_b$ & $[u_b/(R_o+r_b),u_b/(R_o+r_b),u_b/(R_o+r_b),u_b/(R_o+r_b)]$ \\
-        $\eta$     & 2 \\
-    \bottomrule
-    \end{tabular}%
-  \label{tab:given_x}%
-\end{table}%
-
-The above gives the procedure for calculating the current and $\eta$ when the specified switches are given ON or OFF.
-However, in order to calculate the MAC of the structure, i.e.
-the maximum $\eta$, it is necessary to find the corresponding switch state using a greedy strategy, as mentioned in subsection \ref{subsec:greedy_solution}.
-
-Firstly, the weight $N_s$ in Eq. \ref{eq:weight} represents the total number of switches in the system, which is 19. 
-By using this formula and the Dijkstra search strategy, the $SP$s of each cell can be obtained, as shown in Figs.
-\ref{fig:sp1} to \ref{fig:sp4}.
-% TODO: fig 4 个cell的SP（fig:sp1,2,3,4），最终求解结果 fig:ef-mac
-According to the greedy strategy, as many $SP$s as possible should be selected to get the MAC. 
-In the first iteration, the $SP$s of all four batteries are selected, and the switch states on the paths are set to ON. 
-The corresponding $\bm{X}_s$ are calculated using the previous method, and the currents of the batteries are obtained as $u_b/r_b$, $u_b/r_b$, $u_b/r_b$, and $u_b/r_b$. 
-Since all batteries are short-circuited and the current of the battery exceeds the maximum allowed current $I_m$, this solution does not satisfy constraint \ref{eq:Ib_leq_Im} and is discarded. 
-The second iteration is carried out using the dichotomy method, and two batteries are selected for the combination. 
-Assuming that the selected combinations are $(B1, B2)$, the $\bm{X}_s$ obtained according to the $SP$s are substituted into the previous calculation, and the current of each battery is $u_b/r_b$, $u_b/r_b$, $0$, and $0$.
-This solution meets the condition. 
-After that, the case of selecting three cells is considered. 
-By similar calculations, it is determined that all solutions do not satisfy the constraint when three cells are selected. 
-Finally, the MAC of this structure is $\eta=2$, and the related result is shown in Fig. \ref{fig:ef-mac} and Tab. \ref{tab:find_mac}.
-
-\begin{table}[htbp]
-  \centering
-    \caption{MAC Calculating result of the output current $I_o$, battery current $\bm{I}_b$ and ratio $\eta$ in the structure combining Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} and Visairo et al.\cite{visairoReconfigurableBatteryPack2008} with 4 battery cells and 19 switches.}
-    \begin{tabular}{cc}
-    \toprule
-        % Structure & combining Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} and Visairo et al.\cite{visairoReconfigurableBatteryPack2008} with 4 battery cells and 19 switches  \\
-        Structure & 4 battery cells and 19 switches  \\
-    \midrule
-    Switch ON & 1,3,5,6,8,9,10,12,18,19 \\
-    $\bm{X}_s$ & $\diag(1,0,1,0,1,1,0,1,1,1,0,1,0,0,0,0,0,1,1)$ \\
-    \midrule
-        $I_o$ & $2u_b/(2R_o+r_b)$ \\
-        $\bm{I}_b$ & $[u_b/(2R_o+r_b),u_b/(2R_o+r_b),0,0]$ \\
-        $\eta$     & 2 \\
-    \bottomrule
-    \end{tabular}%
-  \label{tab:find_mac}%
-\end{table}%
-
-\subsection{Discussion}
-
-The correctness of the results shown in Fig. \ref{fig:ef-mac} is obvious. 
-When B1 and B2 or B3 and B4 are connected in parallel, the RBS can output the maximum current, which is $\eta=2$, i.e. twice the current output of a single battery in RBS.
-While adding more batteries to the main circuit can only form a series structure and will not improve the MAC.
-It is worth noting that when solving for MAC, $\eta$ is used as the objective function instead of $I_o$, which makes the result of MAC more reasonable. 
-According to the results shown in Tab.
-\ref{tab:find_mac}, $I_o$ and $\bm{I}_b$ are affected by the equivalent resistance $R_o$ of external electrical appliance, the battery's electromotive force $u_b$, and internal resistance $r_b$.
-This means that if $I_o$ is used as the objective function, even for the same RBS structure, the MAC result and corresponding switch state could be changed due to different external electrical appliances.
-This increases the difficulty and uncertainty in RBS structure design. 
-On the contrary, by using $\eta$ as the objective function, which dividing $I_o$ and $\max\bm{I}_b$, the influence of these factors on the results is eliminated, as shown in Tabs.
-\ref{tab:given_x} and \ref{tab:find_mac}.
-$\eta$ only reflects the maximum output current capability of the RBS structure.
-Assuming that the maximum allowed current of battery cells in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by calculating the $\eta$ of the structure.
-Therefore, compared to $I_o$, $\eta$ is more suitable for structure design. 
-Most of the currently proposed RBS structures have simple topological characteristics, and the calculation of MACs are relatively simple, even intuitive. 
-However, when complex and flexible structures need to be designed for application scenarios such as equalization or isolation of specific battery cells, the estimation of MAC will become complex and complicated.
-The method proposed in this paper can effectively solve any RBS structure and estimate MAC universally, paving the way for the structure design of more complex and flexible RBSs.
-
-% 对比Tab. 1和 Tab. 2，可以发现，对于这两种开关状态 $\bm{X}_s$，在电阻和电动势相同的情况下，前者的Io更大。
-% 这主要是由于在Tab. 1的情形下，四个电池以两并两串的形式接入主电路，提供了更多的电动势。
-% 相应的，每个电池的电流也更大。
-% 此时，如果仅使用 Io 作为目标函数，则  （） TODO：讨论怎么说
-
-% 对电池隔离场景的讨论
-% 当系统中存在被隔离的电池时，该方法可用于判断RBS的输出能否依然满足要求。
-% 对隔离电池后形成的新结构按前文算法进行计算即可得到隔离操作后的MAC。
-% 对L的结构、V的结构和我们的结构，不同隔离电池数下的MAC进行计算
-% L：1~3，eta=1；4，eta=0
-% V：1~4，eta=4~0
-% new：1~4，eta=2，2，1，0
-% 画个图，new（最好情况，最坏情况），L，V
-% 说明最好情况、最坏情况。
-% L的结构，在电池全被隔离前都能提供eta=1的MAC；V的结构，MAC随电池隔离数增加而迅速下降；new的结构，MAC的减少情况介于两者之间。
-
-% 对于
-
-\section{Conclusion}
-
-A graph model and a circuit model were developed, and a greedy strategy was employed to solve the MAC. 
-The proposed method was tested on RBSs of varying structures and sizes. 
-Additionally, an indicator, denoted by $\eta$ , was introduced to evaluate the performance of the RBS's output current. 
-This work presents an effective approach for designing and evaluating the output current performance of RBS. 
-Future research could focus on developing new performance indicators for evaluating RBS performance using the currents and voltages obtained by this method, as well as modifying the equivalent model of the battery to enable more accurate simulations of RBS, including transient analysis.
-
-\section{Appendix}
-\begin{algorithm}
-    \caption{Get the max available currents of a certain RBS}\label{alg:eta_RBS}
-    \KwData{Directed graph model $G(V,E)$ of the RBS}
-    \KwResult{$\max \eta$}
-    \For{$i \in E_b$}{
-        $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
-        $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
-    }
-    get $\bm{A}$ by Equation \ref{eq:A}\;
-    \While{not yet determine $\max \eta$ }
-    {
-        $N_{sel} \leftarrow \text{number of selected $SP$s calculated by dichotomy}$\;
-        $C_b    \leftarrow \text{set of all combinations of $N_{sel} $~batteries from $N_b$}$\;
-        \For{$c_b \in C_b$}{
-            $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
-            $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
-            get $\bm{Y}_n$ by Equation \ref{eq:Yn}\;
-            \eIf{$\bm{Y}_n$ is invertible}{
-            }{construct an effective solution}
-            get $I_o$ by Equation \ref{eq:I_o}\;
-            get $\bm{I}_b$ by Equation \ref{eq:I_b}\;
-            \eIf{$\max(\bm{I}_b)\leq I_m$}{
-                $\eta \leftarrow I_o/\max(\bm{I}_b)$\;
-            }{break}
+% \makeatletter
+\tikzset{
+  meta box/.style={
+    draw,
+    black,
+    very thick,
+    text centered,
+  },
+  punkt/.style={
+    meta box,
+    rectangle,
+    rounded corners,
+    inner sep=.25em,
+    minimum height=2em,
+    minimum width=4em,
+    align=center,
+    text width=10em
+  },
+  round/.style={
+    meta box,
+    circle,
+    minimum size=0,
+    inner sep=0pt, 
+    outer sep=0pt
+  },
+  every fit/.style={
+    draw,
+    thick,
+    dashed,
+    gray,
+    inner xsep=.5em,
+    inner ysep=.75em
   }
 }
-\end{algorithm}
+% helper macro
+% \newcommand\tikz@expand@dimen[2]{\tikzset{minimum #2={#1/4}}}
+% tikz styles: adjust min width/height of nodes
+\tikzset{
+  add dimen/.code 2 args={%
+    \pgfkeysgetvalue{/pgf/minimum #1}\tikz@dimen@min
+    \expandafter\tikz@expand@dimen\expandafter{\tikz@dimen@min + #2 * 2em}{#1}%
+  },
+  wider/.style={add dimen={width}{#1}},
+  higher/.style={add dimen={height}{#1}},
+}
+% \makeatother
 
-\bibliographystyle{ieeetr}
-% \bibliography{../attachments/my_ref}
-\bibliography{my_ref}
+\begin{tikzpicture}[font=\small, node font=\small, node distance=1.5em]
+    \node[punkt]     (input) {Input: RBS structure};
+    \node[punkt, below=0.3of input] (get_SP) {
+      get $SP$s by Eqs. 1 and 2 and Dijkstra Search
+      };
 
+    \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Eq.1};
+    \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{set}=N_b$ };
+    \node[punkt, below=0.3of get_Nset] (get_cb) {get $c_b$s by combinating $N_{set}$ batteries from $N_b$};
+    \node[draw, diamond, aspect=2, below=0.3of get_cb] (is_check_all_cb) {are all $c_b$s checked?};
+    \node[draw, diamond, aspect=2, right=1of is_check_all_cb] (is_Nset_converged) {is $N_{set}$ converged?};
+    \node[punkt, above=of is_Nset_converged] (reset_Nset) {reset $N_{set}$ by dichotomy};
+    \node[punkt, text width=15em, below=0.3of is_check_all_cb] (get_Xs) {
+      select an unchecked $c_b$, and get its $\bm{X}_m$ by \\ 
+      if switch $j$ $\in \bigcup_{i\in c_b}SP_i$:\\
+             $\bm{X}[j]=1$ else $0$};
+    \node[punkt, below=0.3of get_Xs] (get_Yn) {get $\bm{Y}_n$ by Eq.3};
+    \node[draw, diamond, aspect=2, below=0.3of get_Yn] (is_Yn_invertible) {is $\bm{Y}_n$ invertible?};
+    \node[punkt, right=1.3of is_Yn_invertible] (construct) {construct an effective solution};
+    \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Eq.4 and 5};
+
+    \node[draw, diamond, aspect=2, below=0.3of get_I] (is_leq_Im) {is $\max \bm{I}_b \leq I_m$?};
+    \node[punkt, right=1.3of is_leq_Im] (drop_eta) {drop this $\eta$};
+    \node[punkt, below=0.3of is_leq_Im] (get_eta) {get $\eta$ by Eq.6};
+    \node[punkt, below=0.3of get_eta] (update_max_eta) {update $\max \eta$};
+    \node[punkt, right=1of is_Nset_converged] (output) {Output: $\max \eta$};
+
+    \node[round,left=1.5of update_max_eta](point1){};
+
+    \graph{
+      (input) -> (get_SP) -> (get_A) -> (get_Nset) -> (get_cb) -> (is_check_all_cb) ->["No"] (get_Xs) -> (get_Yn) -> (is_Yn_invertible) ->["Yes"] (get_I) -> (is_leq_Im) ->["Yes"] (get_eta) -> (update_max_eta);
+      (is_check_all_cb) ->["Yes"] (is_Nset_converged) ->["No"] (reset_Nset) -> (get_cb);
+      (is_Yn_invertible) ->["No"] (construct) ->[to path={|- (\tikztotarget)}] (get_I);
+      (is_leq_Im) ->["No"] (drop_eta) ->[to path={|- (\tikztotarget)}] (update_max_eta);
+      (is_Nset_converged) ->["Yes"] (output);
+      (update_max_eta) -- (point1) ->[to path={|- (\tikztotarget)}] (is_check_all_cb);
+    };
+
+\end{tikzpicture}
 \end{document}

### 2023-05-22 paper/main.tex
add some cites, fix arrows in figures

@@
 Firstly, the weight $N_s$ in Eq. \ref{eq:weight} represents the total number of switches in the system, which is 19. 
-By using this formula and the Dijkstra search strategy, the $SP$s of each cell can be obtained, as shown in Figs.
-\ref{fig:sp1} to \ref{fig:sp4}.
-% TODO: fig 4 个cell的SP（fig:sp1,2,3,4），最终求解结果 fig:ef-mac
+By using this formula and the Dijkstra search strategy, the $SP$s of each cell can be obtained, as shown in Figs. \ref{fig:sp1} to \ref{fig:sp4}.
 According to the greedy strategy, as many $SP$s as possible should be selected to get the MAC. 
@@
 Therefore, compared to $I_o$, $\eta$ is more suitable for structure design. 
-Most of the currently proposed RBS structures have simple topological characteristics, and the calculation of MACs are relatively simple, even intuitive. % #TODO 添加cite
+Most of the currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} have simple topological characteristics, and the calculation of MACs are relatively simple, even intuitive.
+% #TODO 添加cite
 However, when complex and flexible structures need to be designed for application scenarios such as equalization or isolation of specific battery cells, the estimation of MAC will become complex and complicated.

### 2023-05-23 paper/simple_for_2docx.tex
优化latex2word的效果

--- 2023-05-22 paper/main.tex
@@
 Then, if $\bm{Y}_n$ is an invertible matrix,
-\begin{align}
-    I_o(\bm{X}_s)      & = \frac{u_b}{R_o r_b} \bm{A}_o^\T \bm{Y}_n^{-1}(\bm{X}) \bm{A}_b \bm{I}_{N_b\times 1};\label{eq:I_o}\\
-    \bm{I}_b(\bm{X}_s) & = \frac{u_b}{r_b^2}[\bm{A}_b^\T \bm{Y}_n^{-1}(\bm{X}) \bm{A}_b\bm{I}_{N_b \times 1}  -r_b \bm{I}_{N_b \times 1}],\label{eq:I_b}
-\end{align}
+\begin{equation}
+    I_o(\bm{X}_s)       = \frac{u_b}{R_o r_b} \bm{A}_o^\T \bm{Y}_n^{-1}(\bm{X}) \bm{A}_b \bm{I}_{N_b\times 1};\label{eq:I_o}
+\end{equation}
+\begin{equation}
+    \bm{I}_b(\bm{X}_s)  = \frac{u_b}{r_b^2}[\bm{A}_b^\T \bm{Y}_n^{-1}(\bm{X}) \bm{A}_b\bm{I}_{N_b \times 1}  -r_b \bm{I}_{N_b \times 1}],\label{eq:I_b}
+\end{equation}
 where $\bm{I}_{N_b\times 1}$ is a column vector with all equal to 1.
@@
 where $I_m$ is the maximum allowable current of the battery; $\eta$ can be calculated by Eq. \ref{eq:eta}; $I_o$ and $\bm{I}_b$ can be calculated by Eq. \ref{eq:I_o} and \ref{eq:I_b}.
-However, it is computationally difficult to solve \ref{eq:max_eta} directly because of the presence of matrix $\bm{Y}_n^{-1}$.
+However, it is computationally difficult to solve Eq. \ref{eq:max_eta} directly because of the presence of matrix $\bm{Y}_n^{-1}$.
 As the number of batteries and switches in the RBS increase, the order of the matrix increases, and the time costed to compute increases sharply.
@@
 \begin{figure}
-\begin{tikzpicture}[font=\small, node font=\small, node distance=1.5em]
-    \node[punkt]     (input) {Input: RBS structure};
-    \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Eqs. \ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
-    \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Eq. \ref{eq:A}};
-    \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{set}=N_b$ };
-    \node[punkt, below=0.3of get_Nset] (get_cb) {get $c_b$s by combinating $N_{set}$ batteries from $N_b$};
-    \node[draw, diamond, aspect=2, below=0.3of get_cb] (is_check_all_cb) {are all $c_b$s checked?};
-    \node[draw, diamond, aspect=2, right=1of is_check_all_cb] (is_Nset_converged) {is $N_{set}$ converged?};
-    \node[punkt, above=of is_Nset_converged] (reset_Nset) {reset $N_{set}$ by dichotomy};
-    \node[punkt, text width=15em, below=0.3of is_check_all_cb] (get_Xs) {
-        select an unchecked $c_b$, and get its $\bm{X}_m$ by \\ 
-        if switch $j$ $\in \bigcup_{i\in c_b}SP_i$:\\
-        $\bm{X}[j]=1$ else $0$};
-    \node[punkt, below=0.3of get_Xs] (get_Yn) {get $\bm{Y}_n$ by Eq.\ref{eq:Yn}};
-    \node[draw, diamond, aspect=2, below=0.3of get_Yn] (is_Yn_invertible) {is $\bm{Y}_n$ invertible?};
-    \node[punkt, right=1.3of is_Yn_invertible] (construct) {construct an effective solution};
-    \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Eqs. \ref{eq:I_o} and \ref{eq:I_b}};
-    \node[draw, diamond, aspect=2, below=0.3of get_I] (is_leq_Im) {is $\max \bm{I}_b \leq I_m$?};
-    \node[punkt, right=1.3of is_leq_Im] (drop_eta) {drop this $\eta$};
-    \node[punkt, below=0.3of is_leq_Im] (get_eta) {get $\eta$ by Eq.\ref{eq:eta}};
-    \node[punkt, below=0.3of get_eta] (update_max_eta) {update $\max \eta$};
-    \node[punkt, right=1of is_Nset_converged] (output) {Output: $\max \eta$};
-    \node[round,left=1.5of update_max_eta](point1){};
-
-    \graph{
-      (input) -> (get_SP) -> (get_A) -> (get_Nset) -> (get_cb) -> (is_check_all_cb) ->["No"] (get_Xs) -> (get_Yn) -> (is_Yn_invertible) ->["Yes"] (get_I) -> (is_leq_Im) ->["Yes"] (get_eta) -> (update_max_eta);
-      (is_check_all_cb) ->["Yes"] (is_Nset_converged) ->["No"] (reset_Nset) -> (get_cb);
-      (is_Yn_invertible) ->["No"] (construct) ->[to path={|- (\tikztotarget)}] (get_I);
-      (is_leq_Im) ->["No"] (drop_eta) ->[to path={|- (\tikztotarget)}] (update_max_eta);
-      (is_Nset_converged) ->["Yes"] (output);
-      (update_max_eta) -- (point1) ->[to path={|- (\tikztotarget)}] (is_check_all_cb);
-    };
-\end{tikzpicture}
+% \begin{tikzpicture}[font=\small, node font=\small, node distance=1.5em]
+%     \node[punkt]     (input) {Input: RBS structure};
+%     \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Eqs. \ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
+%     \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Eq. \ref{eq:A}};
+%     \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{set}=N_b$ };
+%     \node[punkt, below=0.3of get_Nset] (get_cb) {get $c_b$s by combinating $N_{set}$ batteries from $N_b$};
+%     \node[draw, diamond, aspect=2, below=0.3of get_cb] (is_check_all_cb) {are all $c_b$s checked?};
+%     \node[draw, diamond, aspect=2, right=1of is_check_all_cb] (is_Nset_converged) {is $N_{set}$ converged?};
+%     \node[punkt, above=of is_Nset_converged] (reset_Nset) {reset $N_{set}$ by dichotomy};
+%     \node[punkt, text width=15em, below=0.3of is_check_all_cb] (get_Xs) {
+%         select an unchecked $c_b$, and get its $\bm{X}_m$ by \\ 
+%         if switch $j$ $\in \bigcup_{i\in c_b}SP_i$:\\
+%         $\bm{X}[j]=1$ else $0$};
+%     \node[punkt, below=0.3of get_Xs] (get_Yn) {get $\bm{Y}_n$ by Eq.\ref{eq:Yn}};
+%     \node[draw, diamond, aspect=2, below=0.3of get_Yn] (is_Yn_invertible) {is $\bm{Y}_n$ invertible?};
+%     \node[punkt, right=1.3of is_Yn_invertible] (construct) {construct an effective solution};
+%     \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Eqs. \ref{eq:I_o} and \ref{eq:I_b}};
+%     \node[draw, diamond, aspect=2, below=0.3of get_I] (is_leq_Im) {is $\max \bm{I}_b \leq I_m$?};
+%     \node[punkt, right=1.3of is_leq_Im] (drop_eta) {drop this $\eta$};
+%     \node[punkt, below=0.3of is_leq_Im] (get_eta) {get $\eta$ by Eq.\ref{eq:eta}};
+%     \node[punkt, below=0.3of get_eta] (update_max_eta) {update $\max \eta$};
+%     \node[punkt, right=1of is_Nset_converged] (output) {Output: $\max \eta$};
+%     \node[round,left=1.5of update_max_eta](point1){};
+% 
+%     \graph{
+%       (input) -> (get_SP) -> (get_A) -> (get_Nset) -> (get_cb) -> (is_check_all_cb) ->["No"] (get_Xs) -> (get_Yn) -> (is_Yn_invertible) ->["Yes"] (get_I) -> (is_leq_Im) ->["Yes"] (get_eta) -> (update_max_eta);
+%       (is_check_all_cb) ->["Yes"] (is_Nset_converged) ->["No"] (reset_Nset) -> (get_cb);
+%       (is_Yn_invertible) ->["No"] (construct) ->[to path={|- (\tikztotarget)}] (get_I);
+%       (is_leq_Im) ->["No"] (drop_eta) ->[to path={|- (\tikztotarget)}] (update_max_eta);
+%       (is_Nset_converged) ->["Yes"] (output);
+%       (update_max_eta) -- (point1) ->[to path={|- (\tikztotarget)}] (is_check_all_cb);
+%     };
+% \end{tikzpicture}
+    \centering
+    \includegraphics[width=\textwidth]{../attachments/IMG_20230411_225909.jpg}
 \caption{The computational flowchart of the proposed method in this paper.}\label{fig:flowchart}
@@
 Most of the currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} have simple topological characteristics, and the calculation of MACs are relatively simple, even intuitive.
-% #TODO 添加cite
 However, when complex and flexible structures need to be designed for application scenarios such as equalization or isolation of specific battery cells, the estimation of MAC will become complex and complicated.
@@
 
-\section{Appendix} %TODO 待修改
-\begin{algorithm}
-    \caption{Get the max available currents of a certain RBS}\label{alg:eta_RBS}
-    \KwData{Directed graph model $G(V,E)$ of the RBS}
-    \KwResult{$\max \eta$}
-    \For{$i \in E_b$}{
-        $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
-        $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
-    }
-    get $\bm{A}$ by Equation \ref{eq:A}\;
-    \While{not yet determine $\max \eta$ }
-    {
-        $N_{sel} \leftarrow \text{number of selected $SP$s calculated by dichotomy}$\;
-        $C_b    \leftarrow \text{set of all combinations of $N_{sel} $~batteries from $N_b$}$\;
-        \For{$c_b \in C_b$}{
-            $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
-            $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
-            get $\bm{Y}_n$ by Equation \ref{eq:Yn}\;
-            \eIf{$\bm{Y}_n$ is invertible}{
-            }{construct an effective solution}
-            get $I_o$ by Equation \ref{eq:I_o}\;
-            get $\bm{I}_b$ by Equation \ref{eq:I_b}\;
-            \eIf{$\max(\bm{I}_b)\leq I_m$}{
-                $\eta \leftarrow I_o/\max(\bm{I}_b)$\;
-            }{break}
-        }
-    }
-\end{algorithm}
+% \section{Appendix}
+% \begin{algorithm}
+%     \caption{Get the max available currents of a certain RBS}\label{alg:eta_RBS}
+%     \KwData{Directed graph model $G(V,E)$ of the RBS}
+%     \KwResult{$\max \eta$}
+%     \For{$i \in E_b$}{
+%         $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
+%         $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
+%     }
+%     get $\bm{A}$ by Equation \ref{eq:A}\;
+%     \While{not yet determine $\max \eta$ }
+%     {
+%         $N_{sel} \leftarrow \text{number of selected $SP$s calculated by dichotomy}$\;
+%         $C_b    \leftarrow \text{set of all combinations of $N_{sel} $~batteries from $N_b$}$\;
+%         \For{$c_b \in C_b$}{
+%             $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
+%             $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
+%             get $\bm{Y}_n$ by Equation \ref{eq:Yn}\;
+%             \eIf{$\bm{Y}_n$ is invertible}{
+%             }{construct an effective solution}
+%             get $I_o$ by Equation \ref{eq:I_o}\;
+%             get $\bm{I}_b$ by Equation \ref{eq:I_b}\;
+%             \eIf{$\max(\bm{I}_b)\leq I_m$}{
+%                 $\eta \leftarrow I_o/\max(\bm{I}_b)$\;
+%             }{break}
+%         }
+%     }
+% \end{algorithm}
 
 \bibliographystyle{ieeetr}
-% \bibliography{../attachments/my_ref}
 \bibliography{my_ref}

### 2023-06-22 paper/main.tex
将 v2.1 介绍和方法部分：将v2.1讨论后的修改意见转移到tex中

@@
+% 0622 v3.0 plan
+% -[ ] 将 word 批注和修改内容整理到 tex 中
+% -[ ] 确定修改要点，批注和obsidian记录
+% -[ ] 添加参考文献，期刊的
+
+% mark
+% 统一为 directed graph model
+% 统一用 electrical load 而非 electrical appliance (泛指家电)
+
 \documentclass{article}
@@
 
-\title{A Greedy-based calculation method of RBS maximum allowable current}
+\title{Maximum Allowable Current Determination of Arbitrary Reconfigurable Battery Systems By Using a Directed Graph Model Combined with Greedy Algorithm}
 \author{3057761608 }
@@
 
-\begin{abstract}
-    Reconfigurable Battery Systems (RBSs) offer a promising alternative to traditional battery systems owing to their dynamical topologic structure for the optimization of battery cell charging and discharging stragegies.
-    During the operation of the RBS, the Maximum Allowable Current (MAC) is a critical indicator to guide the reconfiguring control of the system in terms of safety and reliability.
-    In this paper, the MAC of the RBS is calculated by using a greedy algorithm based on the topologic model of the RBS.
+\begin{abstract} % #TODO: rewrite
+    Reconfigurable Battery Systems (RBSs) offer a promising alternative to traditional battery systems owing to their flexible and dynamic changeable topologic structure subjected to battery cell charging and discharging strategies.
+    During the operation of the RBS, Maximum Allowable Current (MAC) is a critical indicator to guide the reconfiguring control of the system in terms of safety and reliability. 
+    In this paper, the MAC of the RBS is calculated by using a greedy algorithm based on the directed graph model of the RBS. % 这句话展开讲， Greedy algorithm方法被用于…/与…方法相结合，实现了对任意RBS结构的MAC提取，
+    % The greedy algorithm method has been used to solve a model based on topology structure, achieving MAC estimation for any RBS structure.
     The effectiveness of this method is validated on a more complex RBS structure based on two proposed structure. 
-    The MAC and the computational method proposed in this article pave the way for more flexible design and more complex application scenarios, such as battery cell isolation, for RBS.
+    This proposed Greedy-based method paves the way for more flexible design and more complex application scenarios, such as battery cell isolation, for RBS.
 
@@
 \section{Introduction}
+% 不放案例
+% 重构灵活性的文献
+% 有向图的文献
 
-Battery Energy Storage Systems (BESSs) are widely used to store and supply high-quality electrical energy in various applications, such as smart grids and wind power plants \cite{desiqueiraControlStrategySmooth2021,karandehTwoStageAlgorithmOptimal2019,yangBatteryEnergyStorage2018,choCommercialResearchBattery2015}.
-Typically, a BESS consists of numerous battery cells that are interconnected by series-parallel circuitry to provide the required charge storage capacity and output voltage.
-For the traditional BESS, the connections between batteries are fixed and the performance of system is limited by the worst cell, as the result of the cask effect.
-Furthermore, reliability and even safety issues will alse be aroused since the failed battery cannot be promptly isolated to exacerbate the degradation of the other batteries during the operational process \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019}.
-Undoubtedly theses issues hinder the practical application of traditional BESSs.
+Battery Energy Storage Systems (BESSs) are widely used to store and release high-quality electrical energy in various applications, such as smart grids and wind power plants \cite{desiqueiraControlStrategySmooth2021,karandehTwoStageAlgorithmOptimal2019,yangBatteryEnergyStorage2018,choCommercialResearchBattery2015}.
+Typically, a BESS consists of numerous battery cells that are interconnected by series-parallel circuitry to provide the required capacity storage.
+The traditional BESS, in which the batteries are connected in a fixed topology, has a significant weakness on its worst battery, caused by the so-called cask effect.
+Furthermore, if this worst battery is failed during the operation process, it will exacerbate the degradation of the other batteries with a high possibility, and arouse reliability and even safety issues \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019}.
 
-Reconfigurable Battery System (RBS), which can dynamically switch to arbitrary circuit configurations as required, is expected to solve the above problem\cite{hanNextGenerationBatteryManagement2020a}.
-The ability to switches circuit helps to isolate unhealthy batteries from the circuit in a timely manner, thereby improving the safety and reliability of the battery system.
+Reconfigurable Battery System (RBS), which can dynamically switch to different circuit topology configurations as required, is expected to solve the above problem\cite{hanNextGenerationBatteryManagement2020a}.
+The ability of switching circuit helps to isolate unhealthy batteries, and thereby improve the safety and reliability of the battery system.
 Fig. \ref{fig:arch} shows two popular typologies of the RBSs developed by Lawson\cite{lawsonSoftwareConfigurableBattery2012} and Visairo \cite{visairoReconfigurableBatteryPack2008} respectively. 
 Taking the RBS shown in Fig.
-\ref{fig:arch-e} as example, the batteries in the RBS can beare connected not only in series when the switches $S_1$, $S_5$, $S_6$, $S_7$, $S_8$, $S_9$, and $S_{13}$ are closed, but also in parallel when $S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$, and $S_{13}$ are closed.
+\ref{fig:arch-e} as example, the batteries in the RBS can be connected not only in series when the switches $S_1$, $S_5$, $S_6$, $S_7$, $S_8$, $S_9$, and $S_{13}$ are closed, but also in parallel when $S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$, and $S_{13}$ are closed.
 Furthermore, when an unhealthy battery, for instance the orange one in Fig.
@@
 $S_6$) to ensure the system still remains a reliable working mode.
+% 补充一句话总结，visairo的网络与固定串并联结构相比具有哪些优点，更适合使用在什么场合
 
@@
 
-The complex connecting structure between batteries and switches enables the flexibility of the RBS, but also brings the challenges in design and control cost.
-The Maximum Allowable Current (MAC) of the RBS system is defined as the maximum current that is allowed for each individual battery of the system, and is a critical indictor to be evaluate the RBS output current to the electronic appliances.
+The complex connecting structure between batteries and switches enables the flexibility of the RBS, but on the other hand brings the challenges in desgin and control cost as well.
+All switches of the RBS need to be controlled to output currents and powers that match the external load in read-time while avoiding batteries short-circuit.
+The Maximum Allowable Current (MAC) of the RBS system is defined as the maximum current that is allowed for each individual battery of the system, and is a critical indictor to be evaluate the RBS output current to the electronic appliances.% 这里缺少过渡，MAC和设计与控制成本有什么关系？
 It helps the designer to assess whether the RBS meets the output current requirements, and contributes to the formulation of appropriate and safe management stragegies for the battery management system (BMS).
-As the complexity of RBS increases, especially when the certain battery needs to be isolated, it becomes difficult to visually obtain the MAC, and a universal algorithm is needed to solve the MAC.
-Despite its importance, there is currently no method available to evaluate MAC for RBSs.
-Therefore, the purpose of this paper is to propose a universal and effective method for calculating the MAC of the RBS.
-To achieve this, a topologic model that builds the relationship between RBS circuit topology and internal resistance and voltage of its batteries are established.
+Despite its importance, there is currently no way to automatically evaluate MAC for RBSs. 
+Especially when one (or more) stochastic battery is isolated, it is not possible to simultaneously determine the MAC of the rest of the RBS to assist the BMS to provide a timely adjustment of the control strategy.
+Under such circumstance, a universal and effective method for calculating the MAC of the RBS is urgently needed for the practical application of RBSs. 
+To achieve this, a directed graph model that builds the relationship between RBS circuit topology and internal resistance and voltage of its batteries are established. 
 Then, a greedy algorithm is employed to search the available circuit of the RBS for reaching the MAC.
-With the developed method, MAC of RBSs with different structures can be calculated effectively, including application scenarios with isolated battery cells.
+% 以上两句话争取合并成一句话，提出的方法应该紧扣标题（即与标题的方法一致）
+With this proposed method, the MAC of RBSs with arbitrary structures can be calculated effectively, including application scenarios with isolated battery cells.
 
@@
 In Section III, a case study of using the proposed model and algorithm to enumerate the MAC of a new and complex structure is demonstrated. 
-The calculation results and scenarios such as battery cells isolation also are discussed
+The calculation results and scenarios such as battery cells isolation also are discussed. 
 Finally, the concluding remarks are drawn in Section IV.
@@
 
-The overall MAC modeling process from an RBS structure is shown in Fig. \ref{fig:main}, which can be divided into four main steps.
-In the first place, the actual RBS structure is converted to a topologic model, in which the connected relationships between batteries and switches are abstracted and the performance parameters of the batteries are retained.
-Subsequently, constraints and objective function, i.e. MAC, are obtained based on the previous connected relationships and parameters.
+The overall MAC modeling process based on an RBS is shown in Fig. \ref{fig:main}, which can be divided into four main steps.
+In the first place, the actual switching circuit typology of the RBS is converted to a directed graph model, in which the connected relationships between batteries and switches are described by nodes and the performance parameters of the batteries are retained.
+Subsequently, the allowable current of the RBS is regarded as an objective function to be obtained based on the previous connected relationships and parameters.
 Then, the shortest path (SP) of each battery in the RBS is obtained by Dijkstra algorithm.
-In the end, the open/close strategy of the RBS is implemented by greedily selecting the SPs to achieve MAC and quantitatively calculated in the equivalent circuit.
+In the end, an optimized switching circuit strategy of the RBS is implemented by greedily selecting the SPs to achieve MAC and quantitatively calculated in the equivalent circuit.
+% 问题出在 要用最简短、读者能接受的话描述清楚方法
+% 重写上面一段，注意描述方法时的逻辑性
+
+% main 主图只保留文字
 
@@
     \end{subfigure}
-    \caption{(a)Diagram of this method, which contains four main steps.
+    % caption 简写
+    \caption{ (a)Diagram of this method, which contains four main steps.
         Step 1: The RBS structure is converted to a topologic model.
@@
 
-\subsection{Topologic Model}
+\subsection{Directed graph Model}
 
-As demonstrated in Fig. \ref{fig:arch}, a typical RBS is made up of a number of battery cells and switches in a dynamically adjustable connection.
+% 以下内容删去，改为对三层关系的说明
+% 说清三层关系：传统有向图（电池做结点）、Xu的有向图、本文包含物理信息的有向图
+As demonstrated in Figs. \ref{fig:arch-f} and \ref{fig:arch-e}, RBS is constructed by a number of batteries and switches in a dynamically adjustable connection.
 To establish a processable circuit, these batteries and switches are transformed into ideal elements under reasonable assumptions.
@@
 
-The normal equivalent circuit for a battery consists of a voltage source in series with a resistor, and a capacitor in parallel with another resistor to simulate the polarization in batteries, kwon as Thevenin model\cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
-To simplify the model, the transient characteristics of the circuit are not considered, so the capacitor mentioned above is ignored.
-In this way, the battery $i$ in the RBS is modeled by the series connection in between a constant voltage source $u_{b,i}$ and a resistor $r_{b,i}$,  as shown in Fig. \ref{fig:battery_simple}
-And a binary variable $x_j$ is used to represent the state of switch $j$, where 0 for ON and 1 for OFF, respectively.
-To simplify the calculation, a closed switch is considered as a resistor with a very small resistance value $r_s$.
+% 说明电池的等效电路化处理
+% 等效成电路，用电路方法处理；借助等效电路方法
+As shown in Fig.
+\ref{fig:battery_simple}, the battery in the RBS can be equivalent to a black-box circuit consisting of two resistors (i.e.
+$r_1$ and $r_2$), and a capacitor (i.e.
+$C$), kwon as Thevenin model\cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
+% 电路相关写法参考 https://eng.libretexts.org/Bookshelves/Electrical_Engineering/Introductory_Electrical_Engineering/Electrical_Engineering_(Johnson)/03%3A_Analog_Signal_Processing/3.07%3A_Equivalent_Circuits_-_Resistors_and_Sources
+% Under ... situations, ... , therefore, such a model can be simplified by ...
+% 说明为什么要简化，在说明怎么简化 
+% 稳态瞬态，整体结构的特征，而非局部
+In this way, the battery $i$ in the RBS is modeled by the series connection in between a constant voltage source $u_{i}$ and a resistor $r_{i}$,  as shown in Fig. \ref{fig:battery_simple}
+Furthermore, the state of switch $j$ in the RBS is represented by a binary variable $x_j$, where 0 for ON and 1 for OFF, respectively.
+When the switch is closed, it can be regarded as a resistor with a very small resistance value $r_s$.
 
-For a given RBS structure, the topologic model for the RBS is constructed as a directed graph $G(V,E)$ in such a way that:
+For a given RBS structure, the directed graph model for the RBS is constructed as a directed graph $G(V,E)$ in such a way that:
 \begin{enumerate}
-    \item Nodes: node $v_1$ and $v_N$ represent the anode and cathode of the RBS respectively, and the other nodes $v_2,\cdots , v_{N-1}$ represent the points connecting batteries and/or switches, where $N$ is the total number of nodes.
-    \item Edges: the directed edges represent batteries, switches and the external electrical appliance in the output circuit based on whether the current direction is constrainted or not. 
-        When the battery is in operation, the internal current direction must be from the negative electrode to the positive electrode, so it is represented by a directed edge from the negative to the positive ; this edge has attributes $(u_b, r_b)$, where $u_b$ and $r_b$ represent battery $b$'s electromotive force and internal resistance.
-        Switches have no constraints on the current direction, so they are represented by a pair of directed edges with opposite directions; these edges both have attribute $(0, r_s)$, where $r_s$ represents the resistance of switch as mentioned above.
-        To fully solve for the current and voltage, an external electrical appliance equivalent as a resistor $R_0$ is connected to the anode and cathode of the RBS and represented by a directed edge from the anode $v_N$  to the cathode $v_1$ of the RBS.
-        Similarly, this edge has attribute $(0, R_0)$.
-        If a given RBS structure has $N_b$ batteries and $N_s$ switches in total, then the number of edges is $N_b+2N_s+1$, where 1 refers to the external electrical appliance.
+    \item Nodes: % 重写，node represent the connection with 3种情况；for a RBS with N nodes ...
+        Among them, the nodes $v_1$ and $v_N$ represent the anode and cathode of the RBS respectively, whereas the other nodes $v_2,\cdots,v_{N-1}$ represent the points connecting batteries and/or switches.
+    \item Edges: % 重写，边的方向由电流确定；边的属性三个分别说
+        the directed edges represent batteries, switches and the external electrical load in the output circuit based on whether the current direction is constrained or not. 
+        For instance, the battery is represented by a directed edge from its one electrode to the other to describe the current direction through that battery.
+        This directed edge is draw from the cathode to anode when the battery is in the discarded mode, and on the other way around when the battery is in the charging mode.
+        The directed edge has two attributes $(u_i, r_i)$, where $u_i$ and $r_i$ represent battery $i$'s electromotive force and internal resistance, respectively.
+        On the other hand, switches are allowed to work under bi-directional currents, so they are represented by a pair of directed edges with two-way directions.
+        % ...
+        As a conclude, for a given RBS structure has $N_b$ batteries and $N_s$ switches, the total number of directed edges is $N_b+2N_s+1$, where 1 refers to the external electrical load.
+
+        % When the battery is in operation, the internal current direction must be from the negative electrode to the positive electrode, so it is represented by a directed edge from the negative to the positive ; this edge has attributes $(u_b, r_b)$, where $u_b$ and $r_b$ represent battery $b$'s electromotive force and internal resistance.
+        % Switches have no constraints on the current direction, so they are represented by a pair of directed edges with opposite directions; these edges both have attribute $(0, r_s)$, where $r_s$ represents the resistance of switch as mentioned above.
+        % To fully solve for the current and voltage, an external electrical appliance equivalent as a resistor $R_0$ is connected to the anode and cathode of the RBS and represented by a directed edge from the anode $v_N$  to the cathode $v_1$ of the RBS.
+        % Similarly, this edge has attribute $(0, R_0)$.
 \end{enumerate}
@@
 
-The constraints and objective function are obtained by analyzing the currents of batteries and external electrical appliance, as following.
-Based on the above directed graph which has $N$ nodes and $N_b+2N_s+1$ directed edges, its incidence matrix $\bm{A}$ is defined as
+% hat
+% 约束和目标函数-在hat部分说
+% 提前说下约束和目标函数是啥
+The constraints and objective function are obtained by analyzing the currents of batteries and external electrical load.
+% 添加过渡句
+% 文献或教科书上导纳矩阵的定义式
+For a directed graph with $N$ nodes and $N_b+2N_s+1$ directed edges, an incidence matrix $\bm{A}$, as shown in Eq. \ref{eq:A}, is defined to ... % 定义导纳矩阵的作用
+% 更换 a_ij 的下角标ij，这个已经被电池和开关用了
 \begin{align}\label{eq:A}
@@
 \end{align}
+% 矩阵A的处理，要写得流畅
+% According to the XX (连通关系？) principle, the sum of currents at each node is zero.
+% 为保证后续矩阵计算满秩，不失一般性地将最后一行删除
 Since each column of $\bm{A}$ sums to zero, the last line are deleted.
-Furthermore, because of a couple of opposite directed edges for each switch, the $N_s$ columns corresponding to the switches are also deleted.
+Furthermore, because of a couple of two-way directed edges for each switch, the $N_s$ columns corresponding to the switches are also deleted.
+% 好好写这句话，开关j在矩阵A中对应两列，且两列互为相反数，删除其中一列可以在不丢失信息的条件下降低矩阵维数，进而降低计算量
 Finally, the reduced incidence matrix $\bm{A}_{(N-1)\times(N_b+N_s+1)}$ are used in the following calculation.
-By divided as batteries, switches and external electrical appliance, $A$ is rewritten as follows
+As a result, $\bm{A}$ can be reduced to a $(N-1)\times(N_b+N_s+1)$ matrix for further calculation of ... % 补全
+By distinguishing the components of the batteries, switches and external electrical load, $\bm{A}$ is rewritten as:
 \begin{equation}
@@
 
-$N_b+N_s+1$ edges' currents $\bm{I}_{(N_b+N_s+1)\times 1}$ and voltages $\bm{U}_{(N_b+N_s+1)\times 1}$, and $N-1$ nodes' voltages $\bm{U}_{n, (N-1)\times 1}$ have following relationships from Kirchhoffs law
+According to Kirchhoffs law, we have
 \begin{align}\label{eq:Kirchhoffs_law}
@@
         \bm{A} \bm{I} = \bm{0}, \\
-        \bm{U}        = \bm{A}^\T \bm{U}_n.
+        \bm{U}        = \bm{A}^\T \bm{U}_n,
     \end{cases}
 \end{align}
+where $\bm{I}$ and $\bm{U}$ indicate the current and voltage arrays of the $N_b+N_s+1$ edges, respectively;
+$\bm{U}_n$ is the voltage array of the $N-1$ nodes.
 These directed edges are treated as generalized branches and expressed in matrix form as follows
@@
     =\begin{bmatrix}
-        \bm{I} & & \\
+        \bm{E} & & \\
         & \bm{X}_s &\\
-        & &\bm{I}
+        & &\bm{E}
     \end{bmatrix}.
 \end{equation}
+where $\bm{E}$ is the identity matrix, and $\bm{X}_s$ is a diagonal matrix with $N_s$ elements of 0 or 1.
 
-In addition to the equivalent circuit assumptions, we also assume that all batteries have the same internal resistance value $r_b$ and supply the same electric potential $u_s$ to simplify the model.
-Then the output current $I_o$ and each battery's current $\bm{I}_b$ can be given by solving the simultaneous Eq. \ref{eq:Kirchhoffs_law} and \ref{eq:generalized_branches} eventually.
+Furtherly, by assuming that the electromotive force and internal resistance of all batteries in the RBS are identical, denoted as $u_b$ and $r_b$ respectively, the output current $I_o$ and each battery's current $\bm{I}_b$ can be calculated by solving the Eqs.
+\ref{eq:Kirchhoffs_law} and \ref{eq:generalized_branches} eventually.
 Let
@@
 \end{equation}
-where $R_o$ is the equivalent resistance of the external circuit.
+where $R_o$ is the equivalent resistance of the external electrical load.
 Then, if $\bm{Y}_n$ is an invertible matrix,
-\begin{align}
+\begin{align} % 统一下角标，不用在公式中表示矩阵形状；单位矩阵的符号
     I_o(\bm{X}_s)      & = \frac{u_b}{R_o r_b} \bm{A}_o^\T \bm{Y}_n^{-1}(\bm{X}) \bm{A}_b \bm{I}_{N_b\times 1};\label{eq:I_o}\\
@@
 \end{align}
-where $\bm{I}_{N_b\times 1}$ is a column vector with all equal to 1.
+where $\bm{I}_{N_b\times 1}$ is an array with all elements equaling to 1.
 
-In this study, the ratio of $I_o$ and $\max (\bm{I}_b)$ is used to characterize the maximum allowable current for a given RBS architecture, denoted as $\eta$:
+Then an indicator $\eta$ is defined by the ratio of $I_o$ and $\max (\bm{I}_b)$ shown in Eq.
+\ref{eq:eta}, to characterize the current output capacity of the RBS structure under different switching states:
 \begin{equation}\label{eq:eta}
@@
 \end{equation}
-The discussion in the next section will show that the $\eta$ reflects the ability of the RBS architecture itself to deliver current, regardliess of the battery cells used by the RBS.
-Finally the problem in RBS can be formulated as
+Finally the problem of solving MAC can be formulated as
 \begin{align}
@@
 \end{align}
-where $I_m$ is the maximum allowable current of the battery; $\eta$ can be calculated by Eq. \ref{eq:eta}; $I_o$ and $\bm{I}_b$ can be calculated by Eq. \ref{eq:I_o} and \ref{eq:I_b}.
-However, it is computationally difficult to solve \ref{eq:max_eta} directly because of the presence of matrix $\bm{Y}_n^{-1}$.
+where $I_m$ is the maximum allowable current of the battery.
+However, it is computationally difficult to solve \ref{eq:max_eta} because of the presence of matrix $\bm{Y}_n^{-1}$. % 在此处说明 Yn-1的难求解，也是由于这一非线性项的存在，传统的优化方法无法求解
 As the number of batteries and switches in the RBS increase, the order of the matrix increases, and the time costed to compute increases sharply.
-A greedy algorithm will be proposed to solve this problem in the next subsection.
+A greedy algorithm will be proposed to solve this problem in the next subsection. % 扩写：为解决这个问题，需要从xx入手，采用greedy algorithm 代替xx，greedy algorithm 具体的实现过程如下节所示。
 
-The integrability of the matrix $\bm{Y}_n$ is explained here.
-Although the above solution procedure requires the matrix $\bm{Y}_n$ to be invertible, it is still possible to encounter integrable $\bm{Y}_n$ in the calculation.
-The physical meaning of this case corresponds to the fact that due to the excessive number of switches in OFF, the solved circuit structure forms circuit branches independent of the main circuit, i.e., the circuit connected to the anode and cathode of the RBS.
-Since these independent branches are not connected to the main circuit, the voltage potentials of these branches cannot be determined and theoretically an infinite number of sets of solutions exist. 
-Benfit from the independence, these solutions have no influence on the results of the main circuit. 
-Since only the currents and voltages of the main circuit are of interest, only one of these solutions needs to be chosen for subsequent calculation.
+% Herein provides the solution procedure of …: 1. 2.
+% 考虑这部分怎么写，想不出就直接删了吧。
+% The integrability of the matrix $\bm{Y}_n$ is explained here.
+% Although the above solution procedure requires the matrix $\bm{Y}_n$ to be invertible, it is still possible to encounter integrable $\bm{Y}_n$ in the calculation.
+% The physical meaning of this case corresponds to the fact that due to the excessive number of switches in OFF, the solved circuit structure forms circuit branches independent of the main circuit, i.e., the circuit connected to the anode and cathode of the RBS.
+% Since these independent branches are not connected to the main circuit, the voltage potentials of these branches cannot be determined and theoretically an infinite number of sets of solutions exist.
+% Benfit from the independence, these solutions have no influence on the results of the main circuit. 
+% Since only the currents and voltages of the main circuit are of interest, only one of these solutions needs to be chosen for subsequent calculation.
 
-\subsection{Greedy Solution}\label{subsec:greedy_solution}
-
-In this subsection, a greedy algorithm is proposed based on shortest paths ($SP$s), which is given here firstly.
-When the battery $i$ is connected to the anode $v_1$ and the cathode $v_N$ of the RBS by the path $p$ in the graph model, the distance $\omega$ of $p$ is defined by the following equation:
+\subsection{Shortest Path}
+% 计算SP的部分单独一个 subsection
+% 添点内容，修改下面两句话
+A path is defined by the complete route passing through one battery (or a consecutive series of batteries) and closed switches from the anode $v_1$ to cathode $v_N$ of the RBS.
+Assuming a situation that battery $i$ is connected to the anode $v_1$ and the cathode $v_N$ of the RBS by a path $p$ in the graph model.
+Then the distance $\omega$ of the path $p$ is defined by the following equation: % 给出使用 Ns的原因，在这句开头，利用RBS的灵活性，通过额外的开关实现一条path上的电池数尽可能少，因此对路径p上的电池数量进行惩罚，设其权重为Ns，而路径p上的开关数量的权重设为1，从而使得最短路径表示的是电池数量最少的情况。 #TODO: 好好想这句话怎么写清楚
 \begin{equation}\label{eq:weight}
@@
 \end{equation}
-where $P_i$ is the set of all paths from $v_1$ to $v_N$ and passed through the directed edge $i$ in the direction of it.
-Specifically, the Dijkstra algorithm can be used to implement the $SP_i$.
+where $P_i$ is the set of all paths from $v_1$ to $v_N$ which pass through the directed edge $i$.
+The Dijkstra algorithm can be used to implement the $SP_i$. % 简短说下过程，给参考文献
+
+% SP 的作用，好好解释，下段重写(是不是该挪到下一subsection)
 According to the definition, $SP_i$ gives the simplest strategy by which the control of battery $i$ is achieved with a minimum of switches while minimizing the influence of other batteries.
@@
 Since batteries can provide more total output current when connected in parallel than in series, the algorithm greedily selects as many cells as possible to be connected into to the overall circuit via their $SP$s to obtain the MAC.
-The dichotomy method is also performed to faster find the right number of $SP$s.
+The dichotomy method is also performed to faster find the right number of $SP$s. % 添加对贪心算法的步骤介绍，具体某一步说明采用了二分法…
 
-After finding the potential SPs combinations about the MAC, the state variable $\bm{X}_s$ of the switches can be determined, and the optimization problem \ref{eq:max_eta} can be solved using Eq.
+\subsection{Greedy Algorithm}\label{subsec:greedy_solution}
+
+In this subsection, a greedy algorithm is proposed based on shortest paths ($SP$s), which is given here firstly. % 这句话改成 greedy algorithm 在整个 MAC 计算中的作用
+
+After finding the potential SPs combinations in correspondence MAC, the state variable $\bm{X}_s$ of the switches can be determined, and the optimization problem \ref{eq:max_eta} can be solved using Eq.
 \ref{eq:eta}, \ref{eq:I_o} and \ref{eq:I_b}.
-The overall flowchart is shown in Fig. \ref{fig:flowchart}, and the corresponding pseudo-code of the algorithm is shown in Algorithm \ref{alg:eta_RBS}.
+The overall flowchart is shown in Fig.
+\ref{fig:flowchart}, and the corresponding pseudo-code of the algorithm is shown in Appendix \ref{alg:eta_RBS}.
+% 这句话应该放前面说，采用“总-分”架构，先给出流程图，然后再结合流程各步骤介绍每类具体算法的应用过程
 
@@
 \end{tikzpicture}
-\caption{The computational flowchart of the proposed method in this paper.}\label{fig:flowchart}
+\caption{The computational flowchart of the MAC if an RBS.}\label{fig:flowchart}
 \end{figure}
+
 \section{Case Study}

### 2023-06-23 paper/main.tex
添加了具体修改计划

@@
 % 0622 v3.0 plan
-% -[ ] 将 word 批注和修改内容整理到 tex 中
-% -[ ] 确定修改要点，批注和obsidian记录
-% -[ ] 添加参考文献，期刊的
+% -[x] 将 word 批注和修改内容整理到 tex 中
+% -[x] 确定修改要点，批注和obsidian记录
+
+% 0623 v3.0 plan 具体修改计划
+% !!!!!! 先改方法、后改案例、最后改介绍和其他
+% -[ ] 题目 点明我们的普适性、自动化？
+% -[ ] 摘要 中间段重写；点明普适性、自动化
+% -[ ] introduction 
+%      -[ ] 不放案例；
+%      -[ ] 增加重构灵活性的文献；
+%      -[ ] 有向图的文献；
+%      -[ ] 点明普适性、自动化
+% -[ ] methodology 
+%      -[ ] main 图重画，只保留文字；
+%      -[ ] 有向图模型，说清三层关系，更规矩地写建模过程；
+%      -[ ] 优化目标和约束；
+%      -[ ] 最短路径，逐句逐字去捋顺；
+%      -[ ] 贪心算法，结合流程图说明算法过程，把二分法融进去；
+%      -[ ] 增加隔离的处理，如约束、算法的改动
+% -[ ] case study 
+%      -[ ] 考虑新结构（MAC=4，想不到就算了，仍用ef结构）；
+%      -[ ] results 直接给出结果，略去计算细节；
+%      -[ ] discussion 说明eta的合理性；
+%      -[ ] 什么样的结构能获得更大的MAC（易隔离性和输出性能的冲突）（想不出来就算了）；
+%      -[ ] 电池隔离场景下的MAC变化(比较不同结构)
+
+% keep in mind
+% 1. 用最简洁、读者最能接受的话说明清楚自己想表达的内容
 
@@
 \usepackage{tikz}
-\usetikzlibrary{
-  arrows.meta,
-  calc,
-  fit,
-  positioning,
-  quotes,
-  graphs,
-  shapes.geometric
-}
+\usetikzlibrary{arrows.meta, calc, fit, positioning, quotes, graphs, shapes.geometric}
 \def\T{\mathrm{T}}
@@
 
+% SP 的控制角度意义
+% 在下一章节详细说明，如何利用SP求解MAC
 % SP 的作用，好好解释，下段重写(是不是该挪到下一subsection)
@@
 From the perspective of series/parallel, the more batteries are connected into circuit via their $SP$s, the more batteries are connected in parallel.
-Since batteries can provide more total output current when connected in parallel than in series, the algorithm greedily selects as many cells as possible to be connected into to the overall circuit via their $SP$s to obtain the MAC.
-The dichotomy method is also performed to faster find the right number of $SP$s. % 添加对贪心算法的步骤介绍，具体某一步说明采用了二分法…
 
@@
 
+% 说明 利用 SP 求解 MAC 的原理
+Since batteries can provide more total output current when connected in parallel than in series, the algorithm greedily selects as many cells as possible to be connected into to the overall circuit via their $SP$s to obtain the MAC.
+% the maximu....SP.....I(两句话合到一起); 这种并联结构可以通过贪心算法得到;
+
+% 贪心算法的具体步骤
+The dichotomy method is also performed to faster find the right number of $SP$s. % 添加对贪心算法的步骤介绍，具体某一步说明采用了二分法…
+% 二分法融入贪心算法，添加贪心算法步骤
 After finding the potential SPs combinations in correspondence MAC, the state variable $\bm{X}_s$ of the switches can be determined, and the optimization problem \ref{eq:max_eta} can be solved using Eq.
@@
 \tikzset{
-  meta box/.style={
-    draw,
-    black,
-    very thick,
-    text centered,
-  },
-  punkt/.style={
-    meta box,
-    rectangle,
-    rounded corners,
-    inner sep=.25em,
-    minimum height=2em,
-    minimum width=4em,
-    align=center,
-    text width=10em
-  },
-  round/.style={
-    meta box,
-    circle,
-    minimum size=0,
-    inner sep=0pt, 
-    outer sep=0pt
-  },
-  every fit/.style={
-    draw,
-    thick,
-    dashed,
-    gray,
-    inner xsep=.5em,
-    inner ysep=.75em
-  }
+  meta box/.style={draw, black, very thick, text centered, },
+  punkt/.style={meta box, rectangle, rounded corners, inner sep=.25em, minimum height=2em, minimum width=4em, align=center, text width=10em },
+  round/.style={meta box, circle, minimum size=0, inner sep=0pt, outer sep=0pt },
+  every fit/.style={draw, thick, dashed, gray, inner xsep=.5em, inner ysep=.75em }
 }
@@
 
-This section presents a case study to demonstrate the effectiveness of the proposed method.
-A more intricate structure, which integrates the two previously proposed structures, is proposed.
-The effectiveness of the aforementioned algorithm is substantiated on this structure to confirm its applicability in practical scenarios.
-Moreover, the algorithm's versatility is also established through its application in complex cases such as the presence of isolated battery cell.
+% 案例分析部分要点
+% - 考虑给个新结构，让MAC=4
+% - 直接给出结构的结果（一个我们提出的，模型的边和结点、SP结果示意图、结果表格；其余结构的结果表格）（注意一些表格的caption）
+%   - It is composed of a total of 19 nodes and 43 edges. 再分别给出哪些节点、边代表什么
+% - eta 反映了结构本身输出电流的能力，与 Io相比
+% - MAC 越高越好 （MAC 是一个结构的输出电流上限，越大意味着可输出的范围越大）
+% - 电池隔离后 MAC 的变化，评判结构的优劣(多放一些结构)
+
+In this section, an intricate structure shown in Fig. 4 is constructed based on the combination of two RBS structures, which are plotted in Fig. (a) and (b) respectively. 
+… % 介绍组成RBS结构的优缺点
+The new proposed RBS structure integrates the advantages of these two traditional RBS structures, and is particularly used to demonstrate the use of the proposed MAC determination method.
 
@@
     \caption{
-        (a) The new RBS structure proposed in this paper, which is obtained by replacing the batteries in Fig.
-\ref{fig:arch-e} with the structure in Fig.
-\ref{fig:arch-f}, as shown in the dashed boxes in the figure.
+        (a) The new RBS structure proposed  by ... % 参考正文修改这里
         (b) The corresponding topologic model of the new RBS structure, which is a directed graph.
+        % 以下句子放正文
         The nodes represent the connection points of the battery cells and/or the switches.
-        The green,gray and blue directed edges represent the battery cells, the switches and the external electrical appliance, respectively.
+        The green,gray and blue directed edges represent the battery cells, the switches and the external electrical load, respectively.
     }
@@
 
+% 以下这段话融入到前一句，分别介绍新建 RBS 结构的两个组成怎么来的， 有什么优点
 The RBS structure proposed by Lawson et al\cite{lawsonSoftwareConfigurableBattery2012}, shown in Fig.
-\ref{fig:arch-e}, easily enables the isolation of arbitrary cells or the addition of redundant cells to the system, but these cells are limited to being connected in series only and the switch between cells connection modes is not flexible.
+\ref{fig:arch-e}, easily enables the isolation of the highly degraded battery ( or a series connection of batteries) from the battery module.
 In contrast, the structure proposed by Visairo et al\cite{visairoReconfigurableBatteryPack2008}, shown in Fig.
 \ref{fig:arch-f}, allows the flexibility to switch the cells between series, parallel and mixed series-parallel modes, thus allowing dynamic voltage adjustment according to the external load and improving energy conversion efficiency, but is not as simple as the structure by Lawson et al in terms of isolating cells or adding redundancy.
-In order to combine the advantages of both structures, a new structure is obtained by replacing the batteries in Fig.
-\ref{fig:arch-e} with the structure in Fig.
-\ref{fig:arch-f}, as shown in Fig.
-\ref{fig:arch-ef}.
-This more complex structure has the structure of Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} as the main frame and the structure of Visairo et al.\cite{visairoReconfigurableBatteryPack2008} as the substructure.
-In this way, the circuit topology of the substructure (i.e.
-the structure in the box in Fig.
-\ref{fig:arch-ef}) can be changed to enable dynamic and flexible voltage adjustment according to the load, while at the same time taking advantage of the ease of battery isolation and increased redundancy of the main frame.
-The next subsections will use this structure with 4 battery cells and 19 switches as an example to demonstrate the effectiveness of the proposed algorithm.
+% 这句话太长了
+In order to combine the advantages of both above RBS structures, a new structure is obtained by integrating the Visairo RBS structure into Lawson RBS structure as shown in Fig. \ref{fig:arch-ef}.
+In this way, the circuit topology of the substructure (for instance the batteries B1, B2 and their related switches) can be changed to enable dynamic and flexible voltage tuning in terms of the external load, as well as taking advantage of the ease of battery isolation and increased redundancy of the main frame.
 
-\subsection{Calculation details and result}
+\subsection{Result}
+% 删去太细节的计算
 
-The graph in Fig. \ref{fig:ef-topo} represents the topologic model based on the new RBS structure mentioned in the last subsection (Fig. \ref{fig:arch-ef}).
-The model is presented in the form of a directed graph, capturing the connection relationship between the battery and switch in the circuit.
-Battery cell 1, 2, 3, and 4 are represented by green directed edges in the graph, while nineteen switches are represented by gray directed edges with opposite directions.
-The external electrical appliance is considered as a directed edge from the cathode of the RBS ( node $18$ in the graph) to the anode ( node $1$ in the graph), represented as the blue directed edge in the graph.
-Totally, there are 19 nodes and 43 edges in the graph.
+The directed graph in Fig. \ref{fig:ef-topo} represents the topology of the new RBS structure proposed in this study (Fig. \ref{fig:arch-ef}). 
+% 下面这句 It is composed of a total of 19 nodes and 43 edges. 先总体介绍模型包括多少个节点和边，再分别给出哪些节点/边代表哪些东西 
+In this model, batteries $B_1$, $B_2$, $B_3$, and $B_4$ are represented by green directed edges in the graph, while 19 switches are represented by gray directed edges with two-way directions. 
+The external electrical load is considered as a directed edge from the cathode of the RBS (i.e. node 18 ) to the anode (i.e. node 1 ), represented as the blue directed edge in the graph.
 
@@
   \centering
-    \caption{Calculating result of the output current $I_o$, battery current $\bm{I}_b$ and ratio $\eta$ for a specificed switches state $\bm{X}_m$ in the structure combining Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} and Visairo et al.\cite{visairoReconfigurableBatteryPack2008} with 4 battery cells and 19 switches.}
+    \caption{Calculating result of the output current $I_o$, battery current $\bm{I}_b$ and ratio $\eta$ for a specificed switches state $\bm{X}_m$ in the structure combining Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} and Visairo et al.\cite{visairoReconfigurableBatteryPack2008} with 4 battery cells and 19 switches.} % 修改该caption
     \begin{tabular}{cc}
@@
 the maximum $\eta$, it is necessary to find the corresponding switch state using a greedy strategy, as mentioned in subsection \ref{subsec:greedy_solution}.
+% 重写这句话，有误解
 
+% 删减以下这段话，不需要单纯描述过程，直接给出结果
 Firstly, the weight $N_s$ in Eq. \ref{eq:weight} represents the total number of switches in the system, which is 19. 
@@
     \caption{
-        The $SP$s of battery cell (a)$B_1$ (b)$B_2$ (c)$B_3$ (d)$B_4$ in the new structure's topological model, which is highlighted in red.
+        The $SP$s (highlighted in red) of battery (a)$B_1$ (b)$B_2$ (c)$B_3$ (d)$B_4$ in the complex RBS structure 
         }
@@
   \centering
-    \caption{MAC Calculating result of the output current $I_o$, battery current $\bm{I}_b$ and ratio $\eta$ in the structure combining Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} and Visairo et al.\cite{visairoReconfigurableBatteryPack2008} with 4 battery cells and 19 switches.}
+    \caption{MAC Calculating result of the output current $I_o$, battery current $\bm{I}_b$ and ratio $\eta$ in the structure combining Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} and Visairo et al.\cite{visairoReconfigurableBatteryPack2008} with 4 battery cells and 19 switches.} % 修改该caption
     \begin{tabular}{cc}
@@
 
-The correctness of the results shown in Fig. \ref{fig:ef-mac} is obvious. 
-When B1 and B2 or B3 and B4 are connected in parallel, the RBS can output the maximum current, which is $\eta=2$, i.e. twice the current output of a single battery in RBS.
+First, the correctness of the results in Fig. ref{fig:ef-mac} is discussed here.
+When $B_1$ and $B_2$ or $B_3$ and $B_4$ are connected in parallel, the RBS can output the maximum current, which is $\eta=2$, i.e. twice the current output of a single battery in RBS.
 While adding more batteries to the main circuit can only form a series structure and will not improve the MAC.
@@
 \ref{tab:find_mac}, $I_o$ and $\bm{I}_b$ are affected by the equivalent resistance $R_o$ of external electrical appliance, the battery's electromotive force $u_b$, and internal resistance $r_b$.
+% Io 和 Ib 是 xxx的函数
 This means that if $I_o$ is used as the objective function, even for the same RBS structure, the MAC result and corresponding switch state could be changed due to different external electrical appliances.
@@
 The method proposed in this paper can effectively solve any RBS structure and estimate MAC universally, paving the way for the structure design of more complex and flexible RBSs.
-
-% 对比Tab. 1和 Tab. 2，可以发现，对于这两种开关状态 $\bm{X}_s$，在电阻和电动势相同的情况下，前者的Io更大。
-% 这主要是由于在Tab. 1的情形下，四个电池以两并两串的形式接入主电路，提供了更多的电动势。
-% 相应的，每个电池的电流也更大。
-% 此时，如果仅使用 Io 作为目标函数，则  （） #TODO：讨论怎么说
 
@@
 
-\section{Appendix} %TODO 待修改
-\begin{algorithm}
+\section{Appendix} 
+\begin{algorithm}% #TODO 待修改
     \caption{Get the max available currents of a certain RBS}\label{alg:eta_RBS}
@@
 
+\section{Acknowledgement}
+This work was supported by the National Natural Science Foundation of China (NSFC, No.52075028).
+
 \bibliographystyle{ieeetr}
-% \bibliography{../attachments/my_ref}
 \bibliography{my_ref}

### 2023-06-24 paper/main.tex
add magic
修改了方法部分的hat和main.png

@@
 % 统一用 electrical load 而非 electrical appliance (泛指家电)
+
+% magic
+% 你将扮演一位英文学术写作经验丰富的大学老师，指导一位非英文母语的学生完成并改进他的论文。 你的目标是帮助他写出一篇流畅、清晰、易读、符合规范的英文学术论文。 他会向你用中文说明自己想表达的内容，有时还会给你一些不完整的英文句子让你补充完整。你不应该逐字翻译他的内容，你需要和他经过多次的沟通，以确定最好的表达。 注意，你们交流的内容可能包含latex语法，你需要理解并使用；当你形成完整的句子或段落时，你要将这些句子或段落放在```和```之间，即 ```some sentence ```，其中每写完一句话都要换行。
 
@@
 
-The overall MAC modeling process based on an RBS is shown in Fig. \ref{fig:main}, which can be divided into four main steps.
-In the first place, the actual switching circuit typology of the RBS is converted to a directed graph model, in which the connected relationships between batteries and switches are described by nodes and the performance parameters of the batteries are retained.
-Subsequently, the allowable current of the RBS is regarded as an objective function to be obtained based on the previous connected relationships and parameters.
-Then, the shortest path (SP) of each battery in the RBS is obtained by Dijkstra algorithm.
-In the end, an optimized switching circuit strategy of the RBS is implemented by greedily selecting the SPs to achieve MAC and quantitatively calculated in the equivalent circuit.
-% 问题出在 要用最简短、读者能接受的话描述清楚方法
-% 重写上面一段，注意描述方法时的逻辑性
-
-% main 主图只保留文字
+The central principle of this method is to make the batteries in RBS connected in series as much as possible, thereby maximizing the output current of the RBS.
+To universally and automatically achieve this, the overall process is divided into four steps, as shown in Fig. \ref{fig:main}.
+Firstly, a directed graph model is established for subsequent computing, which not only contains the connected relationships between batteries and switches, but also retains the performance parameters of the batteries.
+Subsequently, based on the equivalent circuit, the MAC problem is transformed into specific objective functions and constraints.
+Then, the shortest paths (SPs, where additional batteries and switches on the path are penalized as distance) for the batteries are obtained using the Dijkstra algorithm to guide the batteries in the RBS connect in series.
+Finally, a greedy algorithm is employed to organize the switches, allowing the batteries to connect via their SPs while satisfying the constraints, resulting in the MAC of the RBS.
 
@@
     % caption 简写
-    \caption{ (a)Diagram of this method, which contains four main steps.
-        Step 1: The RBS structure is converted to a topologic model.
-        Step 2: Constraints and objective function are obtained based on the previous topologic model.
-        Step 3: The shortest path of each battery in the RBS is obtained by Dijkstra algorithm.
-        Step 4: The MAC is achieved by greedily selecting the shortest paths to open/close switches.
-        (b) The equivalent circuit of a battery in this method, with $u_{b,i}$ and $r_{b,i}$ representing the voltage and internal resistance of the battery $i$ respectively.
-        The capacitor in Thevenin model is ignored.
+    \caption{ 
+        (a)Diagram of this method, which contains four main steps.
+        (b) The equivalent circuit of a battery in this method.
     }

### 2023-06-25 paper/main.tex
修改了 directed graph model

@@
 % -[ ] methodology 
-%      -[ ] main 图重画，只保留文字；
+%      -[x] main 图重画，只保留文字；
 %      -[ ] 有向图模型，说清三层关系，更规矩地写建模过程；
@@
     \centering
-    \begin{subfigure}[b]{\textwidth}
+    \begin{subfigure}[b]{0.8\textwidth}
         \includegraphics[width=\textwidth]{../attachments/main.png}
@@
     \end{subfigure}
-    \\ 
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/battery_simple.png}
-        \caption{}
-        \label{fig:battery_simple}
-    \end{subfigure}
-    % caption 简写
     \caption{ 
-        (a)Diagram of this method, which contains four main steps.
-        (b) The equivalent circuit of a battery in this method.
+        Diagram of this method, which contains four main steps.
     }
@@
 
-% 以下内容删去，改为对三层关系的说明
-% 说清三层关系：传统有向图（电池做结点）、Xu的有向图、本文包含物理信息的有向图
-As demonstrated in Figs. \ref{fig:arch-f} and \ref{fig:arch-e}, RBS is constructed by a number of batteries and switches in a dynamically adjustable connection.
-To establish a processable circuit, these batteries and switches are transformed into ideal elements under reasonable assumptions.
-The resulting circuit structure is then described in matrix form, and the related equations are provided.
+\begin{figure}[htbp]
+    \centering
+    \begin{subfigure}[b]{0.31\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/direct-graph-he.png}
+        \caption{}
+        \label{fig:direct-graph-he}
+    \end{subfigure}
+    \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/direct-graph-xu.png}
+        \caption{}
+        \label{fig:direct-graph-xu}
+    \end{subfigure}
+    \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.24\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/direct-graph-my.png}
+        \caption{}
+        \label{fig:direct-graph-my}
+    \end{subfigure}
+    \\
+    \begin{subfigure}[b]{0.8\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/battery_simple.png}
+        \caption{}
+        \label{fig:batter_simple}
+    \end{subfigure}
+    \caption{ 
+        Directed graph models used in (a) He's work \cite{heExploringAdaptiveReconfiguration2013}, (b) our previous work , and (c) this paper.
+        (d) The equivalent circuit of a battery in this method.
+    }
+\end{figure}
 
-% 说明电池的等效电路化处理
-% 等效成电路，用电路方法处理；借助等效电路方法
+He et al.
+\cite{heExploringAdaptiveReconfiguration2013} once proposed an abstracted directed graph model for RBS, where the nodes represented the batteries, the edges represented the configuration flexibility, and the weight of each vertex corresponded to the battery voltage ( Fig.
+\ref{fig:direct-graph-he}).
+The model effectively captured all potential system configurations and offered a direct metric for configuration flexibility, but it did not specify the physical implementation of the connectivity between batteries, meaning one graph might have had multiple RBS structures.
+We previously proposed a novel directed graph model that, in contrast to He's model, used nodes to represent the connections between batteries and switches, and directed edges to represent batteries and switches (Fig.
+\ref{fig:direct-graph-xu}), allowing for a one-to-one correspondence between the RBS structure and the directed graph model.
+This model was able to accurately and comprehensively represent the RBS topological structure but could not be used for quantitative MAC calculations due to the lack of consideration for battery and switch performance parameters.
+To address this, an improved directed graph model is used here based on our original model, adding electromotive force and resistance attributes on the edges based to equivalent circuits (Fig.
+\ref{fig:direct-graph-my}).
+The model also considers the external load as an equivalent resistance and integrate it into the analysis, making it a complete circuit model for later circuit analysis.
+The following will provide a detailed explanation of the method for equating the components in RBS and constructing the directed graph model.
+
+In order to use circuit analysis methods to solve the MAC of the RBS, the components in the RBS are equated to ideal circuit elements.
 As shown in Fig.
-\ref{fig:battery_simple}, the battery in the RBS can be equivalent to a black-box circuit consisting of two resistors (i.e.
-$r_1$ and $r_2$), and a capacitor (i.e.
-$C$), kwon as Thevenin model\cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
-% 电路相关写法参考 https://eng.libretexts.org/Bookshelves/Electrical_Engineering/Introductory_Electrical_Engineering/Electrical_Engineering_(Johnson)/03%3A_Analog_Signal_Processing/3.07%3A_Equivalent_Circuits_-_Resistors_and_Sources
-% Under ... situations, ... , therefore, such a model can be simplified by ...
-% 说明为什么要简化，在说明怎么简化 
-% 稳态瞬态，整体结构的特征，而非局部
-In this way, the battery $i$ in the RBS is modeled by the series connection in between a constant voltage source $u_{i}$ and a resistor $r_{i}$,  as shown in Fig. \ref{fig:battery_simple}
-Furthermore, the state of switch $j$ in the RBS is represented by a binary variable $x_j$, where 0 for ON and 1 for OFF, respectively.
-When the switch is closed, it can be regarded as a resistor with a very small resistance value $r_s$.
+\ref{fig:battery_simple}, the battery in the RBS can be represented as a black-box circuit consisting of two resistors (i.e., $r_1$ and $r_2$) and a capacitor (i.e., $C$), known as the Thevenin model\cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
+With an emphasis on the stable output of the RBS, the capacitor in the Thevenin model can be considered as an open circuit without affecting the steady-state current.
+Therefore, the battery $i$ in the RBS can be simplified as the series connection between a constant voltage source $u_{i}$ and a resistor $r_{i}$.
+Furthermore, the state of switch $j$ in the RBS is represented by a binary variable $x_j$, where 0 is for ON and 1 is for OFF, respectively.
+When the switch is closed, it can be regarded as a resistor with a very small resistance value $r_{j}$.
+Lastly, the external load is considered as a resistor with a value of $r_o$.
 
@@
 \begin{enumerate}
-    \item Nodes: % 重写，node represent the connection with 3种情况；for a RBS with N nodes ...
-        Among them, the nodes $v_1$ and $v_N$ represent the anode and cathode of the RBS respectively, whereas the other nodes $v_2,\cdots,v_{N-1}$ represent the points connecting batteries and/or switches.
-    \item Edges: % 重写，边的方向由电流确定；边的属性三个分别说
-        the directed edges represent batteries, switches and the external electrical load in the output circuit based on whether the current direction is constrained or not. 
-        For instance, the battery is represented by a directed edge from its one electrode to the other to describe the current direction through that battery.
-        This directed edge is draw from the cathode to anode when the battery is in the discarded mode, and on the other way around when the battery is in the charging mode.
-        The directed edge has two attributes $(u_i, r_i)$, where $u_i$ and $r_i$ represent battery $i$'s electromotive force and internal resistance, respectively.
-        On the other hand, switches are allowed to work under bi-directional currents, so they are represented by a pair of directed edges with two-way directions.
-        % ...
-        As a conclude, for a given RBS structure has $N_b$ batteries and $N_s$ switches, the total number of directed edges is $N_b+2N_s+1$, where 1 refers to the external electrical load.
-
-        % When the battery is in operation, the internal current direction must be from the negative electrode to the positive electrode, so it is represented by a directed edge from the negative to the positive ; this edge has attributes $(u_b, r_b)$, where $u_b$ and $r_b$ represent battery $b$'s electromotive force and internal resistance.
-        % Switches have no constraints on the current direction, so they are represented by a pair of directed edges with opposite directions; these edges both have attribute $(0, r_s)$, where $r_s$ represents the resistance of switch as mentioned above.
-        % To fully solve for the current and voltage, an external electrical appliance equivalent as a resistor $R_0$ is connected to the anode and cathode of the RBS and represented by a directed edge from the anode $v_N$  to the cathode $v_1$ of the RBS.
-        % Similarly, this edge has attribute $(0, R_0)$.
+    \item Nodes:
+        The nodes in the directed graph correspond to the connection points of components in the actual RBS. 
+        Assuming there are a total of $N$ nodes in the RBS, for the sake of convenience, the anode of the RBS is denoted as $v_1$ and the cathode as $v_N$.
+    \item Edges:
+        The edges in the directed graph correspond to the batteries, switches, and external electrical loads in the actual RBS.
+        Therefore, there are three types of directed edges. 
+        For a battery $B_i$, its directed edge $e_i$ is drawn from the cathode to the anode, as the battery only allows current to flow in one direction when in operation.
+        For a switch $S_j$, since it is allowed to work under bi-directional currents, it is represented by a pair of directed edges with two-way directions. 
+        Regarding the external electronic load, as it is connected to the anode and cathode of the RBS, a directed edge from $v_N$ to $v_1$ is used to represent it. 
+        In conclusion, for a given RBS structure with $N_b$ batteries and $N_s$ switches, the total number of directed edges is $N_b+2N_s+1$, where 1 refers to the external electrical load.
+    \item Edges' attributes:
+        Each edge is assigned two attributes, voltage difference and resistance, based on the equivalent method mentioned above.
+        The values for the battery $B_i$, switch $S_j$, and external loads correspond to $(u_i, r_i)$, $(0, r_j)$, and $(0, r_o)$, respectively.
 \end{enumerate}

### 2023-06-25 paper/main.tex
标记
修改了约束条件和目标函数部分

@@
 %      -[x] main 图重画，只保留文字；
-%      -[ ] 有向图模型，说清三层关系，更规矩地写建模过程；
+%      -[x] 有向图模型，说清三层关系，更规矩地写建模过程；
 %      -[ ] 优化目标和约束；
@@
 % magic
-% 你将扮演一位英文学术写作经验丰富的大学老师，指导一位非英文母语的学生完成并改进他的论文。 你的目标是帮助他写出一篇流畅、清晰、易读、符合规范的英文学术论文。 他会向你用中文说明自己想表达的内容，有时还会给你一些不完整的英文句子让你补充完整。你不应该逐字翻译他的内容，你需要和他经过多次的沟通，以确定最好的表达。 注意，你们交流的内容可能包含latex语法，你需要理解并使用；当你形成完整的句子或段落时，你要将这些句子或段落放在```和```之间，即 ```some sentence ```，其中每写完一句话都要换行。
+% 你将扮演一位英文学术写作经验丰富的大学老师，指导一位非英文母语的学生完成并改进他的论文。 你的目标是帮助他写出一篇流畅、清晰、易读、符合规范的英文学术论文。 他会向你用中文说明自己想表达的内容，有时还会给你一些不完整的英文句子让你补充完整。你不应该逐字翻译他的内容，你需要和他经过多次的沟通，以确定最好的表达。 注意，你们交流的内容可能包含latex语法，你需要理解并使用；当你形成完整的句子或段落时，你要将这些句子或段落放在```\n 和\n ```之间，即 ```\n some sentence\n ```，其中每写完一句话都要换行。
 
@@
         \caption{}
-        \label{fig:batter_simple}
+        \label{fig:battery_simple}
     \end{subfigure}
@@
 When the switch is closed, it can be regarded as a resistor with a very small resistance value $r_{j}$.
-Lastly, the external load is considered as a resistor with a value of $r_o$.
+Lastly, the external load is considered as a resistor with a value of $R_o$.
 
@@
         Each edge is assigned two attributes, voltage difference and resistance, based on the equivalent method mentioned above.
-        The values for the battery $B_i$, switch $S_j$, and external loads correspond to $(u_i, r_i)$, $(0, r_j)$, and $(0, r_o)$, respectively.
+        The values for the battery $B_i$, switch $S_j$, and external loads correspond to $(u_i, r_i)$, $(0, r_j)$, and $(0, R_o)$, respectively.
 \end{enumerate}
@@
 
-% hat
-% 约束和目标函数-在hat部分说
-% 提前说下约束和目标函数是啥
-The constraints and objective function are obtained by analyzing the currents of batteries and external electrical load.
-% 添加过渡句
-% 文献或教科书上导纳矩阵的定义式
-For a directed graph with $N$ nodes and $N_b+2N_s+1$ directed edges, an incidence matrix $\bm{A}$, as shown in Eq. \ref{eq:A}, is defined to ... % 定义导纳矩阵的作用
-% 更换 a_ij 的下角标ij，这个已经被电池和开关用了
+Based on the definition of MAC, determining the MAC of RBS involves maximizing the RBS output current while ensuring that the currents of all batteries do not exceed the batteries' maximum allowable current.
+In this subsection, the constraints and objective function to solve the RBS's MAC will be established through circuit analysis, based on the previously constructed directed graph model.
+
+First, the topology in the directed graph model is represented in matrix form $\bm{A}$, known as the incidence matrix , to facilitate circuit analysis.
+The specific definition of the incidence matrix is shown in Eq. \ref{eq:A}.
 \begin{align}\label{eq:A}
-    a_{ij}=
+    a_{kl}=
     \begin{cases}
-        1,  & \text{edge $j$ leaves vertex $i$},\\
-        -1, & \text{edge $j$ enters vertex $i$},\\
+        1,  & \text{edge $l$ leaves node $k$},\\
+        -1, & \text{edge $l$ enters node $k$},\\
         0,  & \text{otherwise}.
@@
 \end{align}
-% 矩阵A的处理，要写得流畅
-% According to the XX (连通关系？) principle, the sum of currents at each node is zero.
-% 为保证后续矩阵计算满秩，不失一般性地将最后一行删除
-Since each column of $\bm{A}$ sums to zero, the last line are deleted.
-Furthermore, because of a couple of two-way directed edges for each switch, the $N_s$ columns corresponding to the switches are also deleted.
-% 好好写这句话，开关j在矩阵A中对应两列，且两列互为相反数，删除其中一列可以在不丢失信息的条件下降低矩阵维数，进而降低计算量
-Finally, the reduced incidence matrix $\bm{A}_{(N-1)\times(N_b+N_s+1)}$ are used in the following calculation.
-As a result, $\bm{A}$ can be reduced to a $(N-1)\times(N_b+N_s+1)$ matrix for further calculation of ... % 补全
-By distinguishing the components of the batteries, switches and external electrical load, $\bm{A}$ is rewritten as:
-\begin{equation}
+For a directed graph consisting of $N$ nodes and $N_b+2N_s+1$ directed edges, its incidence matrix $\bm{A}$ is an $N\times(N_b+2N_s+1)$ matrix. 
+In this matrix, the rows and columns represent the nodes and edges of the directed graph, respectively.
+By distinguishing the components in the RBS corresponding to each column , $\bm{A}$ can be rewritten as:
+\begin{equation}\label{eq:A_bso}
     \bm{A} =
@@
         \bm{A}_b & \bm{A}_s & \bm{A}_o
+    \end{bmatrix},
+\end{equation}
+where $\bm{A}_b$, $\bm{A}_s$ and $\bm{A}_o$ are the sub-matrices corresponding to the batteries, switches and external electrical load, respectively.
+To alleviate computational complexity, matrix $\bm{A}$ undergoes dimensionality reduction.
+Since each directed edge has one node to leave and one to enter, the sum of the values in every column of $\bm{A}$ is zero.
+Therefore removing any single one row will not result in a loss of information. 
+Without loss of generality, the last row is removed here.
+On the other hand, since each switch in the RBS is represented by a pair of directed edges with two-way directions, the two columns corresponding to the switch are mutually opposite.
+Thus, for the sub-matrix $\bm{A}_s$, only one column is retained for each pair of columns representing the same switch.
+As a result, $\bm{A}$ can be reduced to a $(N-1)\times(N_b+N_s+1)$ matrix, denoted as $\bm{\tilde{A}}$, for further calculation of current and voltage.
+Similar to Eq. \ref{eq:A_bso}, $\bm{\tilde{A}}$ can be rewritten as:
+\begin{equation}\label{eq:A_bso_tilde}
+    \bm{\tilde{A}} =
+    \begin{bmatrix}
+        \bm{\tilde{A}}_b & \bm{\tilde{A}}_s & \bm{\tilde{A}}_o
     \end{bmatrix}.
@@
 
+After obtaining the incidence matrix, the currents of all batteries and output in RBS are determined by solving the circuit equations.
 According to Kirchhoffs law, we have
@@
     \begin{cases}
-        \bm{A} \bm{I} = \bm{0}, \\
-        \bm{U}        = \bm{A}^\T \bm{U}_n,
+        \bm{\tilde{A}} \bm{I} = \bm{0}, \\
+        \bm{U}        = \bm{\tilde{A}}^\T \bm{U}_n,
     \end{cases}
 \end{align}
-where $\bm{I}$ and $\bm{U}$ indicate the current and voltage arrays of the $N_b+N_s+1$ edges, respectively;
+where $\bm{I}$ and $\bm{U}$ indicate the current and voltage difference arrays of the $N_b+N_s+1$ edges, respectively;
 $\bm{U}_n$ is the voltage array of the $N-1$ nodes.
@@
 \end{equation}
-where $\bm{I}$ and $\bm{U}$ are the column vectors about $1+N_b+N_s$ edges' current and voltage, respectively;
-$\bm{U}_s$ and $\bm{I}_s$ denote the source voltage and source current of the generalized branches, respectively;
-$\bm{Y}$ is the admittance matrix of the circuit, and $\bm{X}$ is the state matrix defined as
+where $\bm{U}_s$ and $\bm{I}_s$ denote the source voltage and source current of the generalized branches, respectively.
+Because all batteries have been equivalent to voltage sources rather than current sources in the previous subsection, all elements of the array $\bm{I}_s$ are 0, 
+while the elements of the array $\bm{U}_s$ are equal to the first attribute of the corresponding edges in the directed graph.
+The $\bm{Y}$ in \ref{eq:generalized_branches} is the admittance matrix of the circuit, defined as the inverse of the impedance matrix.
+That is the elements of the diagonal matrix $\bm{Y}$ are equal to the reciprocal of the second attribute of the corresponding edges in the directed graph, and the off-diagonal elements are 0.
+The $\bm{X}$ is the state matrix, which describes whether the RBS batteries and switches are allowed to pass current.
+It is defined as
 \begin{equation}\label{eq:X}
     \bm{X} = \diag(
-    \underbrace{1, \cdots, 1}_{N_b~\text{of}~1},
+    \underbrace{1, 0 \cdots, 1}_{N_b~\text{of}~0/1},
     \underbrace{1, 0 \cdots, 1}_{N_s~\text{of}~0/1},
@@
     =\begin{bmatrix}
-        \bm{E} & & \\
+        \bm{X}_b & & \\
         & \bm{X}_s &\\
-        & &\bm{E}
+        & & 1
     \end{bmatrix}.
 \end{equation}
-where $\bm{E}$ is the identity matrix, and $\bm{X}_s$ is a diagonal matrix with $N_s$ elements of 0 or 1.
+Where the elements $x_i$ of the matrix $\bm{X}_b$ represent whether the battery $i$ has been removed from the circuit, with $x_i=1$ indicating removal and $x_i=0$ indicating that it is still available to supply power.
+When all batteries are health and capable of providing current to the external load, $\bm{X}_b$ is an identity matrix. 
+The elements $x_j$ of the matrix $\bm{X}_s$ represent whether the switch $j$ is closed, with $x_j=1$ indicating closure and $x_j=0$ indicating disconnection, which is consistent with the previous subsection.
 
-Furtherly, by assuming that the electromotive force and internal resistance of all batteries in the RBS are identical, denoted as $u_b$ and $r_b$ respectively, the output current $I_o$ and each battery's current $\bm{I}_b$ can be calculated by solving the Eqs.
-\ref{eq:Kirchhoffs_law} and \ref{eq:generalized_branches} eventually.
-Let
+Theoretically, the output current $I_o$ and the currents of each battery $\bm{I}_b$ in the RBS  can be determined by solving Eqs.
+\ref{eq:Kirchhoffs_law}, \ref{eq:generalized_branches}, and \ref{eq:X} under any given state $\bm{X}$.
+In order to obtain specific constraint conditions and objective functions, it is further assumed that all batteries have the same electromotive force and internal resistance, denoted as $u_b$ and $r_b$, respectively.
+This allows for the derivation of explicit expressions for $I_o$ and $\bm{I}_b$.
+After derivation and simplification, the output current $I_o$ and the currents of each battery $\bm{I}_b$ are ultimately represented as Eqs. \ref{eq:I_o} and \ref{eq:I_b}, respectively.
+\begin{equation}\label{eq:I_o}
+    I_o = \frac{1}{R_o r_b} \bm{\tilde{A}}_o^\T \bm{Y}_n^{-1}(\bm{X}) \bm{\tilde{A}}_b \bm{U}_b,
+\end{equation}
+\begin{equation}\label{eq:I_b}
+    \bm{I}_b = \frac{1}{r_b^2}[\bm{\tilde{A}}_b^\T \bm{Y}_n^{-1}(\bm{X}) \bm{\tilde{A}}_b\bm{U}_b -r_b \bm{U}_b],
+\end{equation}
+where $\bm{U}_b$ is a $N_b\times 1$ array with all elements equaling to $u_b$;
+$\bm{Y}_n$ is the equivalent admittance matrix of the circuit, defined as
 \begin{equation}\label{eq:Yn}
-    \bm{Y}_n (\bm{X}_s) = \frac{1}{R_o} \bm{A}_o\bm{A}_o^\T + \frac{1}{r_b} \bm{A}_b\bm{A}_b^\T + \frac{1}{r_s}\bm{A}_s\bm{X}_s\bm{A}_s^\T,
+    \bm{Y}_n (\bm{X}) = \frac{1}{R_o} \bm{\tilde{A}}_o\bm{\tilde{A}}_o^\T + \frac{1}{r_b} \bm{\tilde{A}}_b\bm{X}_b\bm{\tilde{A}}_b^\T + \frac{1}{r_s}\bm{\tilde{A}}_s\bm{X}_s\bm{\tilde{A}}_s^\T.
 \end{equation}
-where $R_o$ is the equivalent resistance of the external electrical load.
-Then, if $\bm{Y}_n$ is an invertible matrix,
-\begin{align} % 统一下角标，不用在公式中表示矩阵形状；单位矩阵的符号
-    I_o(\bm{X}_s)      & = \frac{u_b}{R_o r_b} \bm{A}_o^\T \bm{Y}_n^{-1}(\bm{X}) \bm{A}_b \bm{I}_{N_b\times 1};\label{eq:I_o}\\
-    \bm{I}_b(\bm{X}_s) & = \frac{u_b}{r_b^2}[\bm{A}_b^\T \bm{Y}_n^{-1}(\bm{X}) \bm{A}_b\bm{I}_{N_b \times 1}  -r_b \bm{I}_{N_b \times 1}],\label{eq:I_b}
-\end{align}
-where $\bm{I}_{N_b\times 1}$ is an array with all elements equaling to 1.
 
-Then an indicator $\eta$ is defined by the ratio of $I_o$ and $\max (\bm{I}_b)$ shown in Eq.
-\ref{eq:eta}, to characterize the current output capacity of the RBS structure under different switching states:
+To characterize the current output capacity of the RBS structure under different switching states, an indicator $\eta$ is defined by the ratio of $I_o$ and $\max (\bm{I}_b)$ shown in Eq. \ref{eq:eta}:
 \begin{equation}\label{eq:eta}
@@
 \begin{align}
-    & \max \eta \label{eq:max_eta}\\
+    & \max \eta(\bm{X}_s) \label{eq:max_eta}\\
     \text{s.t.} & \max (\bm{I}_b) \leq I_m, \label{eq:Ib_leq_Im}
@@
 where $I_m$ is the maximum allowable current of the battery.
-However, it is computationally difficult to solve \ref{eq:max_eta} because of the presence of matrix $\bm{Y}_n^{-1}$. % 在此处说明 Yn-1的难求解，也是由于这一非线性项的存在，传统的优化方法无法求解
-As the number of batteries and switches in the RBS increase, the order of the matrix increases, and the time costed to compute increases sharply.
-A greedy algorithm will be proposed to solve this problem in the next subsection. % 扩写：为解决这个问题，需要从xx入手，采用greedy algorithm 代替xx，greedy algorithm 具体的实现过程如下节所示。
+
+However, it is computationally difficult to solve \ref{eq:max_eta} because of the $\bm{Y}_n^{-1}$.
+On one hand, due to the introduction of nonlinear terms by $\bm{Y}_n^{-1}$, many effective methods in linear optimization are not suitable for this problem.
+On the other hand, the rank of $Y_{n}$ is proportional to the number of batteries and switches, which can be very large for a large RBS system, leading to significant computational burden.
+Therefore, intelligent algorithms that rely on evolving by iteration may face efficiency issues when dealing with large RBS system.
+In order to address this issue, the problem should be considered from the perspective of guiding the RBS to reconstruct as many parallel structures as possible.
+Consequently, a greedy algorithm based on the shortest path is proposed. 
+The detailed implementation process is presented in the following two subsections.
 

### 2023-06-26 paper/main.tex
修改了 SP 部分

@@
 %      -[x] 有向图模型，说清三层关系，更规矩地写建模过程；
-%      -[ ] 优化目标和约束；
+%      -[x] 优化目标和约束；
 %      -[ ] 最短路径，逐句逐字去捋顺；
@@
 Therefore, intelligent algorithms that rely on evolving by iteration may face efficiency issues when dealing with large RBS system.
+% 如果有时间，可以在案例部分做个对比，看看智能算法和本文算法的效率差距有多大。
 In order to address this issue, the problem should be considered from the perspective of guiding the RBS to reconstruct as many parallel structures as possible.
@@
 \subsection{Shortest Path}
-% 计算SP的部分单独一个 subsection
-% 添点内容，修改下面两句话
-A path is defined by the complete route passing through one battery (or a consecutive series of batteries) and closed switches from the anode $v_1$ to cathode $v_N$ of the RBS.
-Assuming a situation that battery $i$ is connected to the anode $v_1$ and the cathode $v_N$ of the RBS by a path $p$ in the graph model.
-Then the distance $\omega$ of the path $p$ is defined by the following equation: % 给出使用 Ns的原因，在这句开头，利用RBS的灵活性，通过额外的开关实现一条path上的电池数尽可能少，因此对路径p上的电池数量进行惩罚，设其权重为Ns，而路径p上的开关数量的权重设为1，从而使得最短路径表示的是电池数量最少的情况。 #TODO: 好好想这句话怎么写清楚
+
+The path $p$ used in this method is defined as the complete route that passes through one battery (or a consecutive series of batteries) and closed switches, connecting the anode $v_1$ to the cathode $v_N$ of the RBS.
+By applying a penalty to the series-connected batteries on the path, where additional batteries imply a longer distance, the algorithm encourages the RBS to form parallel structures as much as possible.
+Meanwhile, to reduce the number of switches controlled during the reconstruction process, a penalty is also applied to the total number of switches on the path, while ensuring the minimum number of batteries.
+Therefore, the distance $\omega$ of the path $p$ is defined by the following equation: 
 \begin{equation}\label{eq:weight}
@@
 \end{equation}
-where $N_s$ is the total number of switches in the system; $n_b(p)$ and $n_s(p)$ are number of batteries and switches in the path $p$ respectively. 
-$SP_i$ is defined as the path with the minimum $\omega$ for battery $i$.
+where $N_s$ is the total number of switches in the system; 
+$n_b(p)$ and $n_s(p)$ are number of batteries and switches in the path $p$ respectively. 
+Moreover, the shortest path $SP_i$ is defined as the path with the minimum $\omega$ for battery $i$, as shown in the following equation:
 \begin{equation}\label{eq:def_sp}
@@
 where $P_i$ is the set of all paths from $v_1$ to $v_N$ which pass through the directed edge $i$.
-The Dijkstra algorithm can be used to implement the $SP_i$. % 简短说下过程，给参考文献
 
-% SP 的控制角度意义
-% 在下一章节详细说明，如何利用SP求解MAC
-% SP 的作用，好好解释，下段重写(是不是该挪到下一subsection)
-According to the definition, $SP_i$ gives the simplest strategy by which the control of battery $i$ is achieved with a minimum of switches while minimizing the influence of other batteries.
-From the perspective of series/parallel, the more batteries are connected into circuit via their $SP$s, the more batteries are connected in parallel.
+The $SP_i$ can be solved by the Dijkstra algorithm.
+The Dijkstra algorithm is a graph search method that finds the shortest path between two given nodes in a weighted graph, efficiently solving the single-source shortest path problem.
+Assuming that the cathode and anode of battery $i$ are denoted as $v_i^-$ and $v_i^+$ respectively, the path $p$ of battery $i$  can be divided into three segments : $v_1 \rightarrow v_i^-$, $v_i^+ \rightarrow v_N$, and $v_i^- \rightarrow v_i^+$.
+The $v_i^- \rightarrow v_i^+$ is the directed edge corresponding to battery $i$. 
+With the Dijkstra algorithm, shortest paths for the $v_1 \rightarrow v_i^-$ and $v_i^+ \rightarrow v_N$ can be calculated under the weights given in Eq.
+\ref{eq:weight}, denoted as $SP(v_i^- \rightarrow v_i^+)$ and $SP(v_i^+ \rightarrow v_N)$, respectively.
+Finally, the $SP_i$ for battery $i$ is formed by the complete path with $SP(v_1 \rightarrow v_i^-)$, $v_i^- \rightarrow v_i^+$, and $SP(v_i^+ \rightarrow v_N)$.
 
 \subsection{Greedy Algorithm}\label{subsec:greedy_solution}
+
+From the perspective of series/parallel, the more batteries are connected into circuit via their $SP$s, the more batteries are connected in parallel.
 

### 2023-06-26 paper/main.tex
修改了 贪心算法 部分

@@
 %      -[ ] 点明普适性、自动化
-% -[ ] methodology 
+% -[x] methodology 
 %      -[x] main 图重画，只保留文字；
@@
 %      -[x] 优化目标和约束；
-%      -[ ] 最短路径，逐句逐字去捋顺；
-%      -[ ] 贪心算法，结合流程图说明算法过程，把二分法融进去；
-%      -[ ] 增加隔离的处理，如约束、算法的改动
+%      -[x] 最短路径，逐句逐字去捋顺；
+%      -[x] 贪心算法，结合流程图说明算法过程，把二分法融进去；
+%      -[x] 增加隔离的处理，如约束、算法的改动
 % -[ ] case study 
-%      -[ ] 考虑新结构（MAC=4，想不到就算了，仍用ef结构）；
+%      -[ ] 考虑新结构（MAC=4，想不到就算了，仍用ef结构）(0626: 想不到)；
 %      -[ ] results 直接给出结果，略去计算细节；
@@
 
-From the perspective of series/parallel, the more batteries are connected into circuit via their $SP$s, the more batteries are connected in parallel.
+From the perspective of series/parallel connections, integrating more batteries into the circuit through their shortest paths ($SP$s) results in a larger number of batteries connected in parallel, thereby increasing the total output current of the RBS.
+However, conflicts may arise between the $SP$s of different batteries. 
+For instance, the $SP$s of two batteries might form a short-circuited RBS structure, which is not allowed. 
+To address this issue, a greedy algorithm is employed to incorporate as many $SP$s as possible while satisfying the reconstruction requirements.
 
-In this subsection, a greedy algorithm is proposed based on shortest paths ($SP$s), which is given here firstly. % 这句话改成 greedy algorithm 在整个 MAC 计算中的作用
-
-% 说明 利用 SP 求解 MAC 的原理
-Since batteries can provide more total output current when connected in parallel than in series, the algorithm greedily selects as many cells as possible to be connected into to the overall circuit via their $SP$s to obtain the MAC.
-% the maximu....SP.....I(两句话合到一起); 这种并联结构可以通过贪心算法得到;
-
-% 贪心算法的具体步骤
-The dichotomy method is also performed to faster find the right number of $SP$s. % 添加对贪心算法的步骤介绍，具体某一步说明采用了二分法…
-% 二分法融入贪心算法，添加贪心算法步骤
-After finding the potential SPs combinations in correspondence MAC, the state variable $\bm{X}_s$ of the switches can be determined, and the optimization problem \ref{eq:max_eta} can be solved using Eq.
-\ref{eq:eta}, \ref{eq:I_o} and \ref{eq:I_b}.
-The overall flowchart is shown in Fig.
-\ref{fig:flowchart}, and the corresponding pseudo-code of the algorithm is shown in Appendix \ref{alg:eta_RBS}.
-% 这句话应该放前面说，采用“总-分”架构，先给出流程图，然后再结合流程各步骤介绍每类具体算法的应用过程
+The algorithm, as illustrated in Fig. \ref{fig:flowchart}, can be summarized as follows, with the corresponding pseudo-code presented in Algorithm \ref{alg:eta_RBS}.
+First, the shortest paths ($SP$s) are obtained using Eqs. \ref{eq:weight} and \ref{eq:def_sp} in conjunction with Dijkstra Search. 
+Next, the matrix $\bm{A}$ is calculated using Eq. \ref{eq:A}, and the initial $N_{set}$ is set to $N_b$. 
+The algorithm iteratively checks different combinations of $c_b$ batteries from $N_b$ and updates $N_{set}$ using a dichotomy method until convergence is reached. 
+For each combination, the algorithm constructs an effective solution if possible, and calculates the currents $I_o$ and $\bm{I}_b$ using Eqs. \ref{eq:I_o} and \ref{eq:I_b}. 
+If the maximum current $\bm{I}_b$ is less than or equal to $I_m$, the $\eta$ is calculated using Eq. \ref{eq:eta}, and the maximum $\eta$ is updated accordingly. 
+Finally, the algorithm outputs the maximum $\eta$ once $N_{set}$ converges.
 
@@
 \section{Appendix} 
-\begin{algorithm}% #TODO 待修改
+\begin{algorithm}
     \caption{Get the max available currents of a certain RBS}\label{alg:eta_RBS}
@@
     {
-        $N_{sel} \leftarrow \text{number of selected $SP$s calculated by dichotomy}$\;
-        $C_b    \leftarrow \text{set of all combinations of $N_{sel} $~batteries from $N_b$}$\;
+        $N_{set} \leftarrow \text{number of setected $SP$s calculated by dichotomy}$\;
+        $C_b    \leftarrow \text{set of all combinations of $N_{set} $~batteries from $N_b$}$\;
         \For{$c_b \in C_b$}{

### 2023-06-26 paper/main.tex
修改了case study部分

@@
 % -[ ] introduction 
-%      -[ ] 不放案例；
+%      -[ ] 只放 V的结构，并展示串联、并联和隔离；
 %      -[ ] 增加重构灵活性的文献；
@@
 % -[ ] case study 
-%      -[ ] 考虑新结构（MAC=4，想不到就算了，仍用ef结构）(0626: 想不到)；
-%      -[ ] results 直接给出结果，略去计算细节；
+%      -[-] 考虑新结构（MAC=4，想不到就算了，仍用ef结构）(0626: 想不到)；
+%      -[x] results 直接给出结果，略去计算细节；
 %      -[ ] discussion 说明eta的合理性；
-%      -[ ] 什么样的结构能获得更大的MAC（易隔离性和输出性能的冲突）（想不出来就算了）；
+%      -[-] 什么样的结构能获得更大的MAC（易隔离性和输出性能的冲突）（想不出来就算了）(0626:有想法，但是要引入互斥片段的概念)；
 %      -[ ] 电池隔离场景下的MAC变化(比较不同结构)
@@
 \begin{abstract} % #TODO: rewrite
-    Reconfigurable Battery Systems (RBSs) offer a promising alternative to traditional battery systems owing to their flexible and dynamic changeable topologic structure subjected to battery cell charging and discharging strategies.
+    Reconfigurable Battery Systems (RBSs) offer a promising alternative to traditional battery systems owing to their flexible and dynamic changeable topologic structure subjected to battery charging and discharging strategies.
     During the operation of the RBS, Maximum Allowable Current (MAC) is a critical indicator to guide the reconfiguring control of the system in terms of safety and reliability. 
@@
     The effectiveness of this method is validated on a more complex RBS structure based on two proposed structure. 
-    This proposed Greedy-based method paves the way for more flexible design and more complex application scenarios, such as battery cell isolation, for RBS.
+    This proposed Greedy-based method paves the way for more flexible design and more complex application scenarios, such as battery isolation, for RBS.
 
@@
 Battery Energy Storage Systems (BESSs) are widely used to store and release high-quality electrical energy in various applications, such as smart grids and wind power plants \cite{desiqueiraControlStrategySmooth2021,karandehTwoStageAlgorithmOptimal2019,yangBatteryEnergyStorage2018,choCommercialResearchBattery2015}.
-Typically, a BESS consists of numerous battery cells that are interconnected by series-parallel circuitry to provide the required capacity storage.
+Typically, a BESS consists of numerous batteries that are interconnected by series-parallel circuitry to provide the required capacity storage.
 The traditional BESS, in which the batteries are connected in a fixed topology, has a significant weakness on its worst battery, caused by the so-called cask effect.
@@
 The ability of switching circuit helps to isolate unhealthy batteries, and thereby improve the safety and reliability of the battery system.
-Fig. \ref{fig:arch} shows two popular typologies of the RBSs developed by Lawson\cite{lawsonSoftwareConfigurableBattery2012} and Visairo \cite{visairoReconfigurableBatteryPack2008} respectively. 
-Taking the RBS shown in Fig.
-\ref{fig:arch-e} as example, the batteries in the RBS can be connected not only in series when the switches $S_1$, $S_5$, $S_6$, $S_7$, $S_8$, $S_9$, and $S_{13}$ are closed, but also in parallel when $S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$, and $S_{13}$ are closed.
-Furthermore, when an unhealthy battery, for instance the orange one in Fig.
-\ref{fig:arch-f}, exits in the RBS, it can be isolated by closing its three adjacent switches (i.e.
+Fig.\ref{fig:arch} shows two popular typologies of the RBSs developed by Lawson\cite{lawsonSoftwareConfigurableBattery2012} and Visairo \cite{visairoReconfigurableBatteryPack2008} respectively. 
+Taking the RBS shown in Fig.\ref{fig:stru-Visairo} as example, the batteries in the RBS can be connected not only in series when the switches $S_1$, $S_5$, $S_6$, $S_7$, $S_8$, $S_9$, and $S_{13}$ are closed, but also in parallel when $S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$, and $S_{13}$ are closed.
+Furthermore, when an unhealthy battery, for instance the orange one in Fig.\ref{fig:stru-Lawson}, exits in the RBS, it can be isolated by closing its three adjacent switches (i.e.
 $S_5$, $S_7$ and $S_8$) and opening the switch below that battery (i.e.
@@
         \caption{}
-        \label{fig:arch-f}
+        \label{fig:stru-Lawson}
     \end{subfigure}
@@
         \caption{}
-        \label{fig:arch-e}
+        \label{fig:stru-Visairo}
     \end{subfigure}
@@
 % 以上两句话争取合并成一句话，提出的方法应该紧扣标题（即与标题的方法一致）
-With this proposed method, the MAC of RBSs with arbitrary structures can be calculated effectively, including application scenarios with isolated battery cells.
+With this proposed method, the MAC of RBSs with arbitrary structures can be calculated effectively, including application scenarios with isolated batteries.
 
@@
 In Section III, a case study of using the proposed model and algorithm to enumerate the MAC of a new and complex structure is demonstrated. 
-The calculation results and scenarios such as battery cells isolation also are discussed. 
+The calculation results and scenarios such as batteries isolation also are discussed. 
 Finally, the concluding remarks are drawn in Section IV.
@@
 The central principle of this method is to make the batteries in RBS connected in series as much as possible, thereby maximizing the output current of the RBS.
-To universally and automatically achieve this, the overall process is divided into four steps, as shown in Fig. \ref{fig:main}.
+To universally and automatically achieve this, the overall process is divided into four steps, as shown in Fig.\ref{fig:main}.
 Firstly, a directed graph model is established for subsequent computing, which not only contains the connected relationships between batteries and switches, but also retains the performance parameters of the batteries.
@@
     \begin{subfigure}[b]{0.8\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/main.png}
+        \includegraphics[width=\textwidth]{../attachments/main.png} % #TODO: 修改step2中的公式
         \caption{}
@@
 He et al.
-\cite{heExploringAdaptiveReconfiguration2013} once proposed an abstracted directed graph model for RBS, where the nodes represented the batteries, the edges represented the configuration flexibility, and the weight of each vertex corresponded to the battery voltage ( Fig.
-\ref{fig:direct-graph-he}).
+\cite{heExploringAdaptiveReconfiguration2013} once proposed an abstracted directed graph model for RBS, where the nodes represented the batteries, the edges represented the configuration flexibility, and the weight of each vertex corresponded to the battery voltage ( Fig.\ref{fig:direct-graph-he}).
 The model effectively captured all potential system configurations and offered a direct metric for configuration flexibility, but it did not specify the physical implementation of the connectivity between batteries, meaning one graph might have had multiple RBS structures.
-We previously proposed a novel directed graph model that, in contrast to He's model, used nodes to represent the connections between batteries and switches, and directed edges to represent batteries and switches (Fig.
-\ref{fig:direct-graph-xu}), allowing for a one-to-one correspondence between the RBS structure and the directed graph model.
+We previously proposed a novel directed graph model that, in contrast to He's model, used nodes to represent the connections between batteries and switches, and directed edges to represent batteries and switches (Fig.\ref{fig:direct-graph-xu}), allowing for a one-to-one correspondence between the RBS structure and the directed graph model.
 This model was able to accurately and comprehensively represent the RBS topological structure but could not be used for quantitative MAC calculations due to the lack of consideration for battery and switch performance parameters.
-To address this, an improved directed graph model is used here based on our original model, adding electromotive force and resistance attributes on the edges based to equivalent circuits (Fig.
-\ref{fig:direct-graph-my}).
+To address this, an improved directed graph model is used here based on our original model, adding electromotive force and resistance attributes on the edges based to equivalent circuits (Fig.\ref{fig:direct-graph-my}).
 The model also considers the external load as an equivalent resistance and integrate it into the analysis, making it a complete circuit model for later circuit analysis.
@@
 In order to use circuit analysis methods to solve the MAC of the RBS, the components in the RBS are equated to ideal circuit elements.
-As shown in Fig.
-\ref{fig:battery_simple}, the battery in the RBS can be represented as a black-box circuit consisting of two resistors (i.e., $r_1$ and $r_2$) and a capacitor (i.e., $C$), known as the Thevenin model\cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
+As shown in Fig.\ref{fig:battery_simple}, the battery in the RBS can be represented as a black-box circuit consisting of two resistors (i.e., $r_1$ and $r_2$) and a capacitor (i.e., $C$), known as the Thevenin model\cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
 With an emphasis on the stable output of the RBS, the capacitor in the Thevenin model can be considered as an open circuit without affecting the steady-state current.
@@
 First, the topology in the directed graph model is represented in matrix form $\bm{A}$, known as the incidence matrix , to facilitate circuit analysis.
-The specific definition of the incidence matrix is shown in Eq. \ref{eq:A}.
+The specific definition of the incidence matrix is shown in Eq.\ref{eq:A}.
 \begin{align}\label{eq:A}
@@
 As a result, $\bm{A}$ can be reduced to a $(N-1)\times(N_b+N_s+1)$ matrix, denoted as $\bm{\tilde{A}}$, for further calculation of current and voltage.
-Similar to Eq. \ref{eq:A_bso}, $\bm{\tilde{A}}$ can be rewritten as:
+Similar to Eq.\ref{eq:A_bso}, $\bm{\tilde{A}}$ can be rewritten as:
 \begin{equation}\label{eq:A_bso_tilde}
@@
 
-Theoretically, the output current $I_o$ and the currents of each battery $\bm{I}_b$ in the RBS  can be determined by solving Eqs.
-\ref{eq:Kirchhoffs_law}, \ref{eq:generalized_branches}, and \ref{eq:X} under any given state $\bm{X}$.
+Theoretically, the output current $I_o$ and the currents of each battery $\bm{I}_b$ in the RBS  can be determined by solving Eqs.\ref{eq:Kirchhoffs_law}, \ref{eq:generalized_branches}, and \ref{eq:X} under any given state $\bm{X}$.
 In order to obtain specific constraint conditions and objective functions, it is further assumed that all batteries have the same electromotive force and internal resistance, denoted as $u_b$ and $r_b$, respectively.
 This allows for the derivation of explicit expressions for $I_o$ and $\bm{I}_b$.
-After derivation and simplification, the output current $I_o$ and the currents of each battery $\bm{I}_b$ are ultimately represented as Eqs. \ref{eq:I_o} and \ref{eq:I_b}, respectively.
+After derivation and simplification, the output current $I_o$ and the currents of each battery $\bm{I}_b$ are ultimately represented as Eqs.\ref{eq:I_o} and \ref{eq:I_b}, respectively.
 \begin{equation}\label{eq:I_o}
@@
 
-To characterize the current output capacity of the RBS structure under different switching states, an indicator $\eta$ is defined by the ratio of $I_o$ and $\max (\bm{I}_b)$ shown in Eq. \ref{eq:eta}:
+To characterize the current output capacity of the RBS structure under different switching states, an indicator $\eta$ is defined by the ratio of $I_o$ and $\max (\bm{I}_b)$ shown in Eq.\ref{eq:eta}:
 \begin{equation}\label{eq:eta}
@@
 The $v_i^- \rightarrow v_i^+$ is the directed edge corresponding to battery $i$. 
-With the Dijkstra algorithm, shortest paths for the $v_1 \rightarrow v_i^-$ and $v_i^+ \rightarrow v_N$ can be calculated under the weights given in Eq.
-\ref{eq:weight}, denoted as $SP(v_i^- \rightarrow v_i^+)$ and $SP(v_i^+ \rightarrow v_N)$, respectively.
+With the Dijkstra algorithm, shortest paths for the $v_1 \rightarrow v_i^-$ and $v_i^+ \rightarrow v_N$ can be calculated under the weights given in Eq.\ref{eq:weight}, denoted as $SP(v_i^- \rightarrow v_i^+)$ and $SP(v_i^+ \rightarrow v_N)$, respectively.
 Finally, the $SP_i$ for battery $i$ is formed by the complete path with $SP(v_1 \rightarrow v_i^-)$, $v_i^- \rightarrow v_i^+$, and $SP(v_i^+ \rightarrow v_N)$.
@@
 
-The algorithm, as illustrated in Fig. \ref{fig:flowchart}, can be summarized as follows, with the corresponding pseudo-code presented in Algorithm \ref{alg:eta_RBS}.
-First, the shortest paths ($SP$s) are obtained using Eqs. \ref{eq:weight} and \ref{eq:def_sp} in conjunction with Dijkstra Search. 
-Next, the matrix $\bm{A}$ is calculated using Eq. \ref{eq:A}, and the initial $N_{set}$ is set to $N_b$. 
+The algorithm, as illustrated in Fig.\ref{fig:flowchart}, can be summarized as follows, with the corresponding pseudo-code presented in Algorithm \ref{alg:greedy}.
+First, the shortest paths ($SP$s) are obtained using Eqs.\ref{eq:weight} and \ref{eq:def_sp} in conjunction with Dijkstra Search. 
+Next, the matrix $\bm{A}$ is calculated using Eq.\ref{eq:A}, and the initial $N_{set}$ is set to $N_b$. 
 The algorithm iteratively checks different combinations of $c_b$ batteries from $N_b$ and updates $N_{set}$ using a dichotomy method until convergence is reached. 
-For each combination, the algorithm constructs an effective solution if possible, and calculates the currents $I_o$ and $\bm{I}_b$ using Eqs. \ref{eq:I_o} and \ref{eq:I_b}. 
-If the maximum current $\bm{I}_b$ is less than or equal to $I_m$, the $\eta$ is calculated using Eq. \ref{eq:eta}, and the maximum $\eta$ is updated accordingly. 
+For each combination, the algorithm constructs an effective solution if possible, and calculates the currents $I_o$ and $\bm{I}_b$ using Eqs.\ref{eq:I_o} and \ref{eq:I_b}. 
+If the maximum current $\bm{I}_b$ is less than or equal to $I_m$, the $\eta$ is calculated using Eq.\ref{eq:eta}, and the maximum $\eta$ is updated accordingly. 
 Finally, the algorithm outputs the maximum $\eta$ once $N_{set}$ converges.
@@
     \node[punkt]     (input) {Input: RBS structure};
-    \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Eqs. \ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
-    \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Eq. \ref{eq:A}};
+    \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Eqs.\ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
+    \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Eq.\ref{eq:A}};
     \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{set}=N_b$ };
@@
     \node[punkt, right=1.3of is_Yn_invertible] (construct) {construct an effective solution};
-    \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Eqs. \ref{eq:I_o} and \ref{eq:I_b}};
+    \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Eqs.\ref{eq:I_o} and \ref{eq:I_b}};
     \node[draw, diamond, aspect=2, below=0.3of get_I] (is_leq_Im) {is $\max \bm{I}_b \leq I_m$?};
@@
 \end{tikzpicture}
-\caption{The computational flowchart of the MAC if an RBS.}\label{fig:flowchart}
+\caption{The computational flowchart of the MAC for a given RBS.}\label{fig:flowchart}
 \end{figure}
@@
 
-% 案例分析部分要点
-% - 考虑给个新结构，让MAC=4
-% - 直接给出结构的结果（一个我们提出的，模型的边和结点、SP结果示意图、结果表格；其余结构的结果表格）（注意一些表格的caption）
-%   - It is composed of a total of 19 nodes and 43 edges. 再分别给出哪些节点、边代表什么
-% - eta 反映了结构本身输出电流的能力，与 Io相比
-% - MAC 越高越好 （MAC 是一个结构的输出电流上限，越大意味着可输出的范围越大）
-% - 电池隔离后 MAC 的变化，评判结构的优劣(多放一些结构)
-
-In this section, an intricate structure shown in Fig. 4 is constructed based on the combination of two RBS structures, which are plotted in Fig. (a) and (b) respectively. 
-… % 介绍组成RBS结构的优缺点
-The new proposed RBS structure integrates the advantages of these two traditional RBS structures, and is particularly used to demonstrate the use of the proposed MAC determination method.
-
-\subsection{Determination of a new RBS structure}
+\subsection{Structures}
 
@@
     \centering
-    \begin{subfigure}[b]{0.45\textwidth}
+    \begin{subfigure}[b]{0.2\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/arch-e.png} % #TODO: 把不健康电池改为健康
+        \caption{}
+        \label{fig:study-stru-Lawson}
+    \end{subfigure}
+    \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.4\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/arch-f.png}
+        \caption{}
+        \label{fig:study-stru-Visairo}
+    \end{subfigure}
+    \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.31\textwidth}
         \includegraphics[width=\textwidth]{../attachments/arch-ef.png}
         \caption{}
-        \label{fig:arch-ef}
+        \label{fig:study-stru-my}
+    \end{subfigure}
+    \caption{The 4-battery RBS structures proposed by (a)Lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b)Visairo\cite{visairoReconfigurableBatteryPack2008} and (c)this paper.}
+\end{figure}
+
+Currently, two types of RBS structures have been proposed by Visairo et al.
+\cite{visairoReconfigurableBatteryPack2008} and Lawson et al.
+\cite{lawsonSoftwareConfigurableBattery2012}, both of which have been applied in practice.
+The primary goal of Visairo's structure (Fig.\ref{fig:study-stru-Visairo}) was to achieve dynamic adjustment of RBS output; however, the isolation of unhealthy batteries was not sufficiently addressed.
+When batteries need to be isolated in the RBS of Visairo's structure, the methods for isolating them and the subsequent changes in RBS output warrant further investigation.
+Lawson et al. conducted research on battery isolation in RBS and specifically designed the structure shown in Fig.\ref{fig:study-stru-Lawson}. 
+This structure has the advantage of easily isolating batteries, but it cannot dynamically adjust the output current of RBS. 
+Based on the structures of Visairo and Lawson, this paper presents a new structure, as shown in Fig.\ref{fig:study-stru-my}, which combines the advantages of both.
+By integrating the Visairo RBS structure into the Lawson RBS structure, the new structure not only allows the flexibility to switch the batteries between series, parallel, and mixed series-parallel modes, but also easily enables the isolation of highly degraded batteries from the RBS.
+These three structures will be employed to validate the effectiveness of this paper's proposed method for calculating the MAC. 
+And their variations in output current under battery isolation conditions will be studied.
+
+\subsection{Result}
+
+As shown in Fig.\ref{fig:study-stru-my}, the new RBS structure consists of 4 batteries and 19 switches. 
+The corresponding directed graph is depicted in Fig.\ref{fig:study-dirgraph-my}, which is composed of of a total of 18 nodes and 43 edges. 
+Batteries $B_1$, $B_2$, $B_3$, and $B_4$ are denoted by green directed edges in the graph, while the 19 switches are represented by gray directed edges with bi-directional arrows. 
+The external electrical load is treated as a directed edge from the cathode of the RBS (i.e., node 18) to the anode (i.e., node 1), as indicated by the blue directed edge in the graph.
+Utilizing Eq.\ref{eq:weight} and the Dijkstra algorithm, the $SP$s of the four batteries in the RBS structure of Fig.\ref{fig:study-stru-my} are shown in Figs.\ref{fig:sp1}-\ref{fig:sp4}, highlighted in red.
+Finally, the MAC calculation results of the structure in Fig.\ref{fig:study-stru-my} are shown as Tab.\ref{tab:study-results-my} and Fig.\ref{fig:study-results-my}, obtained by the greedy algorithm \ref{alg:greedy}.
+Tab.\ref{tab:study-results-my} contains the switches states, the output current $I_o$, battery current $\bm{I}_b$ and ratio $\eta$ of the RBS structure with all batteries in good health when the RBS output reaches the MAC.
+Fig.\ref{fig:study-results-my} presents the corresponding circuit, with the red highlight indicating that current is flowing through the respective branches.
+
+\begin{figure}[htbp] % #TODO：补上两个开关
+    \centering
+    \begin{subfigure}[b]{0.28\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/ef-topo.png} % #TODO：补上两个开关
+        \caption{}
+        \label{fig:study-dirgraph-my}
     \end{subfigure}
     \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/ef-topo.png}
-        \caption{}
-        \label{fig:ef-topo}
-    \end{subfigure}
-    \caption{
-        (a) The new RBS structure proposed  by ... % 参考正文修改这里
-        (b) The corresponding topologic model of the new RBS structure, which is a directed graph.
-        % 以下句子放正文
-        The nodes represent the connection points of the battery cells and/or the switches.
-        The green,gray and blue directed edges represent the battery cells, the switches and the external electrical load, respectively.
-    }
-\end{figure}
-
-% 以下这段话融入到前一句，分别介绍新建 RBS 结构的两个组成怎么来的， 有什么优点
-The RBS structure proposed by Lawson et al\cite{lawsonSoftwareConfigurableBattery2012}, shown in Fig.
-\ref{fig:arch-e}, easily enables the isolation of the highly degraded battery ( or a series connection of batteries) from the battery module.
-In contrast, the structure proposed by Visairo et al\cite{visairoReconfigurableBatteryPack2008}, shown in Fig.
-\ref{fig:arch-f}, allows the flexibility to switch the cells between series, parallel and mixed series-parallel modes, thus allowing dynamic voltage adjustment according to the external load and improving energy conversion efficiency, but is not as simple as the structure by Lawson et al in terms of isolating cells or adding redundancy.
-% 这句话太长了
-In order to combine the advantages of both above RBS structures, a new structure is obtained by integrating the Visairo RBS structure into Lawson RBS structure as shown in Fig. \ref{fig:arch-ef}.
-In this way, the circuit topology of the substructure (for instance the batteries B1, B2 and their related switches) can be changed to enable dynamic and flexible voltage tuning in terms of the external load, as well as taking advantage of the ease of battery isolation and increased redundancy of the main frame.
-
-\subsection{Result}
-% 删去太细节的计算
-
-The directed graph in Fig. \ref{fig:ef-topo} represents the topology of the new RBS structure proposed in this study (Fig. \ref{fig:arch-ef}). 
-% 下面这句 It is composed of a total of 19 nodes and 43 edges. 先总体介绍模型包括多少个节点和边，再分别给出哪些节点/边代表哪些东西 
-In this model, batteries $B_1$, $B_2$, $B_3$, and $B_4$ are represented by green directed edges in the graph, while 19 switches are represented by gray directed edges with two-way directions. 
-The external electrical load is considered as a directed edge from the cathode of the RBS (i.e. node 18 ) to the anode (i.e. node 1 ), represented as the blue directed edge in the graph.
-
-Based on the node-edge relationship given in Fig. \ref{fig:ef-topo}, the incidence matrix $\bm{A}$ can be obtained according to Eq. \ref{eq:A}:
-\begin{equation}
-    \bm{A} = 
-    \begin{bmatrix}
-        \bm{A}_b & \bm{A}_s & \bm{A}_o
-    \end{bmatrix},
-\end{equation}
-
-\begin{equation}
-    \bm{A}_b^\T = 
-    \begin{bmatrix}
-        0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 \\
-    \end{bmatrix},
-\end{equation}
-
-\begin{equation}
-    \bm{A}_s^\T = 
-    \begin{bmatrix}
-        1 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 1 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 1 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 1 & 0 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 &-1 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 &-1 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 &-1 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 &-1 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 &-1 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 \\
-    \end{bmatrix},
-\end{equation}
-
-\begin{equation}
-    \bm{A}_o^\T = 
-    \begin{bmatrix}
-       -1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-    \end{bmatrix}.
-\end{equation}
-The state matrix $\bm{X}$ is determined by the switches' state, that is, the specific configuration of the RBS.
-For example, when switch $S_1$, $S_3$, $S_5$, $S_6$, $S_8$, $S_9$, $S_{11}$, $S_{13}$, $S_{14}$, $S_{16}$, $S_{17}$ and $S_{19}$ are ON, and the rest of the switches are OFF, the state matrix $\bm{X}$ is given by
-\begin{equation}
-    \bm{X} = diag(
-    \underbrace{1,0,1,0,1,1,0,1,1,0,1,0,1,1,0,1,1,0,1}_{\text{switches}},
-    \underbrace{1,1,1,1}_{\text{batteries}},
-    1
-    ).
-\end{equation}
-By substituting the above specific values of $\bm{A}$ and $\bm{X}$ above into Eqs.
-\ref{eq:Yn}, \ref{eq:I_o}, \ref{eq:I_b} and \ref{eq:eta} in turn, the $\eta$ at the current situation, i.e.
-battery cell $B_1$ and $B_2$, $B_3$ and $B_4$ are connected in parallel with each other, and then connected in series to supply the external electrical appliance, can be obtained after the sequential calculation.
-The results are shown in Tab. \ref{tab:given_x}.
-
-\begin{table}[htbp]
-  \centering
-    \caption{Calculating result of the output current $I_o$, battery current $\bm{I}_b$ and ratio $\eta$ for a specificed switches state $\bm{X}_m$ in the structure combining Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} and Visairo et al.\cite{visairoReconfigurableBatteryPack2008} with 4 battery cells and 19 switches.} % 修改该caption
-    \begin{tabular}{cc}
-    \toprule
-        Structure & 4 battery cells and 19 switches  \\
-        % Structure & combining Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} and Visairo et al.\cite{visairoReconfigurableBatteryPack2008} with 4 battery cells and 19 switches  \\
-    \midrule
-    Switch ON & 1,3,5,6,8,9,11,13,14,16,17,19 \\
-        $\bm{X}_s$ & $\diag(1,0,1,0,1,1,0,1,1,0,1,0,1,1,0,1,1,0,1)$ \\
-    \midrule
-        $I_o$ & $2u_b/(R_o+r_b)$ \\
-        $\bm{I}_b$ & $[u_b/(R_o+r_b),u_b/(R_o+r_b),u_b/(R_o+r_b),u_b/(R_o+r_b)]$ \\
-        $\eta$     & 2 \\
-    \bottomrule
-    \end{tabular}%
-  \label{tab:given_x}%
-\end{table}%
-
-The above gives the procedure for calculating the current and $\eta$ when the specified switches are given ON or OFF.
-However, in order to calculate the MAC of the structure, i.e.
-the maximum $\eta$, it is necessary to find the corresponding switch state using a greedy strategy, as mentioned in subsection \ref{subsec:greedy_solution}.
-% 重写这句话，有误解
-
-% 删减以下这段话，不需要单纯描述过程，直接给出结果
-Firstly, the weight $N_s$ in Eq. \ref{eq:weight} represents the total number of switches in the system, which is 19. 
-By using this formula and the Dijkstra search strategy, the $SP$s of each cell can be obtained, as shown in Figs. \ref{fig:sp1} to \ref{fig:sp4}.
-According to the greedy strategy, as many $SP$s as possible should be selected to get the MAC. 
-In the first iteration, the $SP$s of all four batteries are selected, and the switch states on the paths are set to ON. 
-The corresponding $\bm{X}_s$ are calculated using the previous method, and the currents of the batteries are obtained as $u_b/r_b$, $u_b/r_b$, $u_b/r_b$, and $u_b/r_b$. 
-Since all batteries are short-circuited and the current of the battery exceeds the maximum allowed current $I_m$, this solution does not satisfy constraint \ref{eq:Ib_leq_Im} and is discarded. 
-The second iteration is carried out using the dichotomy method, and two batteries are selected for the combination. 
-Assuming that the selected combinations are $(B1, B2)$, the $\bm{X}_s$ obtained according to the $SP$s are substituted into the previous calculation, and the current of each battery is $u_b/r_b$, $u_b/r_b$, $0$, and $0$.
-This solution meets the condition. 
-After that, the case of selecting three cells is considered. 
-By similar calculations, it is determined that all solutions do not satisfy the constraint when three cells are selected. 
-Finally, the MAC of this structure is $\eta=2$, and the related result is shown in Fig. \ref{fig:ef-mac} and Tab. \ref{tab:find_mac}.
-
-\begin{figure}[htbp]
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
+    \begin{subfigure}[b]{0.28\textwidth}
         \includegraphics[width=\textwidth]{../attachments/ef-sp1.png}
@@
     \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.45\textwidth}
+    \begin{subfigure}[b]{0.28\textwidth}
         \includegraphics[width=\textwidth]{../attachments/ef-sp2.png}
@@
     \\
-    \begin{subfigure}[b]{0.45\textwidth}
+    \begin{subfigure}[b]{0.28\textwidth}
         \includegraphics[width=\textwidth]{../attachments/ef-sp3.png}
@@
     \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.45\textwidth}
+    \begin{subfigure}[b]{0.28\textwidth}
         \includegraphics[width=\textwidth]{../attachments/ef-sp4.png}
@@
     \end{subfigure}
+    \hspace{0.05\textwidth}
+    \begin{subfigure}[b]{0.28\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/ef-mac.png} % #TODO: 闭合开关。移除开关，直接连上
+        \caption{}
+        \label{fig:study-results-my}
+    \end{subfigure}
     \caption{
-        The $SP$s (highlighted in red) of battery (a)$B_1$ (b)$B_2$ (c)$B_3$ (d)$B_4$ in the complex RBS structure 
+        For the RBS structure in Fig.\ref{fig:study-stru-my}, 
+        (a)its directed graph 
+        and the $SP$s (highlighted in red) of battery (b)$B_1$, (c)$B_2$, (d)$B_3$, (e)$B_4$.
+        (f)The circuit of the RBS with its output reaching the MAC.
         }
+    \label{fig:all-results-my}
 \end{figure}
@@
   \centering
-    \caption{MAC Calculating result of the output current $I_o$, battery current $\bm{I}_b$ and ratio $\eta$ in the structure combining Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} and Visairo et al.\cite{visairoReconfigurableBatteryPack2008} with 4 battery cells and 19 switches.} % 修改该caption
+    \caption{MAC Calculating result of the 4-battery RBS structure in Fig.\ref{fig:study-stru-my}.}
     \begin{tabular}{cc}
     \toprule
-        % Structure & combining Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} and Visairo et al.\cite{visairoReconfigurableBatteryPack2008} with 4 battery cells and 19 switches  \\
-        Structure & 4 battery cells and 19 switches  \\
+        Structure & Fig.\ref{fig:study-stru-my} with 4 batteries and 19 switches  \\
+        % Battery isolated & None \\
     \midrule
-    Switch ON & 1,3,5,6,8,9,10,12,18,19 \\
-    $\bm{X}_s$ & $\diag(1,0,1,0,1,1,0,1,1,1,0,1,0,0,0,0,0,1,1)$ \\
-    \midrule
+    Switch ON & $S_1$,$S_3$,$S_5$,$S_6$,$S_8$,$S_9$,$S_{10}$,$S_{12}$,$S_{18}$,$S_{19}$ \\
     $I_o$ & $2u_b/(2R_o+r_b)$ \\
@@
     \bottomrule
-    \end{tabular}%
-  \label{tab:find_mac}%
-\end{table}%
+    \end{tabular}
+  \label{tab:study-results-my}
+\end{table}
+
+Similarly, the MAC calculation results of the structures in Figs.\ref{fig:study-stru-Lawson} and \ref{fig:study-stru-Visairo} are shown as Tab.\ref{tab:study-results-Lawson} and Tab.\ref{tab:study-results-Visairo}, respectively.
+
+\begin{table}[htbp]
+  \centering
+    \caption{MAC Calculating result of the 4-battery RBS structure in Fig.\ref{fig:study-stru-Lawson}.}
+    \begin{tabular}{cc}
+    \toprule
+        Structure & Fig.\ref{fig:study-stru-Lawson} with 4 batteries and 15 switches  \\
+        % Battery isolated & None \\
+    \midrule
+    Switch ON & $S_1$,$S_3$,$S_5$,$S_7$,$S_{10}$,$S_{13}$,$S_{14}$,$S_{15}$ \\
+    $I_o$ & $u_b/(R_o+r_b)$ \\
+    $\bm{I}_b$ & $[u_b/(R_o+r_b),0,0,0]$ \\
+    $\eta$     & 1 \\
+    \bottomrule
+    \end{tabular}
+  \label{tab:study-results-Lawson}
+\end{table}
+
+\begin{table}[htbp]
+  \centering
+    \caption{MAC Calculating result of the 4-battery RBS structure in Fig.\ref{fig:study-stru-Visairo}.}
+    \begin{tabular}{cc}
+    \toprule
+        Structure & Fig.\ref{fig:study-stru-Visairo} with 4 batteries and 13 switches  \\
+        % Battery isolated & None \\
+    \midrule
+    Switch ON & $S_1$,$S_2$,$S_3$,$S_4$,$S_5$,$S_9$,$S_{10}$,$S_{11}$,$S_{12}$,$S_{13}$ \\
+    $I_o$ & $4u_b/(4R_o+r_b)$ \\
+    $\bm{I}_b$ & $[u_b/(4R_o+r_b),u_b/(4R_o+r_b),u_b/(4R_o+r_b),u_b/(4R_o+r_b)]$ \\
+    $\eta$     & 4 \\
+    \bottomrule
+    \end{tabular}
+  \label{tab:study-results-Visairo}
+\end{table}
+
+\subsection{Discussion}
+
+In this subsection, we firstly discuss the correctness of the results presented in Fig.\ref{fig:all-results-my} and Tab.\ref{tab:study-results-my}. 
+When $B_1$ and $B_2$ or $B_3$ and $B_4$ are connected in parallel, the RBS can output the maximum current, which is $\eta=2$, i.e., twice the current output of a single battery in RBS. 
+Adding more batteries to the main circuit can only form a series structure and will not improve the MAC. 
+Therefore, the switches state given in Tab.\ref{tab:study-results-my} can make the RBS output current reach the maximum.
+
+It is important to note that when solving for MAC, $\eta$ is used as the objective function instead of $I_o$. 
+This choice makes the result of MAC more reasonable. 
+As shown in Tab.\ref{tab:study-results-my}, $I_o$ and $\bm{I}_b$ are functions of $R_o$, $u_b$, and $r_b$. 
+If $I_o$ were used as the objective function, even for the same RBS structure, the MAC result and corresponding switches state could change due to different external electrical appliances.
+It would increase the difficulty and uncertainty in RBS structure design. 
+In contrast, by using $\eta$ as the objective function, which is defined as the ratio of $I_o$ and $\max\bm{I}_b$, the influence of these factors on the results can be eliminated. 
+$\eta$ solely reflects the maximum output current capability of the RBS structure. 
+Assuming that the maximum allowed current of batteries in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by determining the $\eta$ of the structure. 
+Therefore, compared to $I_o$, $\eta$ is more suitable for structure design.
+
+Furthermore, the significance of the method proposed in this paper is discussed from the perspective of next-generation RBS design.
+Most of the currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} exhibit simple topological characteristics, and the calculation of MACs is relatively straightforward, even intuitive.
+However, these simple structures do not always fully satisfy the requirements of complex applications, such as dynamically adapting the circuit to variable and random operating conditions, and actively equalizing differences among the batteries in the RBS.
+Moreover, isolating the batteries disrupts the original regularity and symmetry of the topology, which complicates the otherwise simple structure, and the maximum output current of the system becomes more challenging to obtain.
+Owing to the advantages of pervasiveness and automation, the proposed method can be employed to calculate the MAC of arbitrary RBS structures, which helps to address the aforementioned issues and paves the way for more complex and flexible RBS structure design.
+
+To illustrate this point, the MACs of the three RBS structures mentioned above are calculated after the batteries are isolated, as shown in Fig.\ref{fig:isolated_mac}. 
+Specifically, for the structure presented in Fig.\ref{fig:study-stru-my}, the corresponding circuit states of MACs when isolating different numbers of batteries are depicted in Figs.\ref{fig:my-isolated-1}-\ref{fig:my-isolated-3}.
+This structure has two cases of isolating two batteries: 
+one is to isolate two batteries within the same substructure (Fig.\ref{fig:my-isolated-2b}), in which case $\eta=2$; the other is to isolate one battery in each of the two substructures (Fig.\ref{fig:my-isolated-2w}), in which case $\eta=1$.
+From the results, it can be observed that the proposed method provides reasonable outcomes for isolating batteries with any number and position.
+
+Furthermore, the performance of output current for the three RBS when isolating batteries is also illustrated in Fig. \ref{fig:isolated_mac}. 
+For the structure proposed by Lawson et al., the MAC remains the same as that without isolated battery cells, i.e., $\eta=1$, when the number of isolated battery cells increases, until all the cells in the RBS are isolated.
+For Visairo's structure, the MAC decreases as the number of isolated battery cells increases, until $\eta=0$. 
+In contrast, the MAC of the structure proposed in this work is positioned between the two structures. 
+This indicates that the structure proposed in this paper, compared to Lawson's structure, has a larger MAC under the same number of batteries, which means a wider output current regulation range. 
+On the other hand, by simply changing the states of $S_2$, $S_4$, $S_{11}$, and $S_{12}$ in the conversion structure, this structure can address the majority of battery isolation scenarios, whereas Visairo's structure requires specific battery targeting and switch control.
+In summary, the structure proposed in this paper has the advantages of both Lawson's and Visairo's structures.
 
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../attachments/ef-mac.png}
+    \includegraphics[width=0.65\textwidth]{../attachments/isolated_mac.png}
     \caption{
-        The finally calculation result of MAC for the new structure with four battery cells and 19 switches.
-        The red lines represent the branches through which the current flows, and the switches on these branches are ON. 
-        In this situation, the RBS outputs MAC to the outside, which is $\eta=2$.
-    }\label{fig:ef-mac}
+        The variation of MAC with the number of isolated batteries for different RBS structures, including the structure proposed by Lawson et al., Visairo et al.
+, and the structure proposed in this paper.
+    }\label{fig:isolated_mac}
 \end{figure}
 
-\subsection{Discussion}
-
-First, the correctness of the results in Fig. ref{fig:ef-mac} is discussed here.
-When $B_1$ and $B_2$ or $B_3$ and $B_4$ are connected in parallel, the RBS can output the maximum current, which is $\eta=2$, i.e. twice the current output of a single battery in RBS.
-While adding more batteries to the main circuit can only form a series structure and will not improve the MAC.
-It is worth noting that when solving for MAC, $\eta$ is used as the objective function instead of $I_o$, which makes the result of MAC more reasonable. 
-According to the results shown in Tab.
-\ref{tab:find_mac}, $I_o$ and $\bm{I}_b$ are affected by the equivalent resistance $R_o$ of external electrical appliance, the battery's electromotive force $u_b$, and internal resistance $r_b$.
-% Io 和 Ib 是 xxx的函数
-This means that if $I_o$ is used as the objective function, even for the same RBS structure, the MAC result and corresponding switch state could be changed due to different external electrical appliances.
-This increases the difficulty and uncertainty in RBS structure design. 
-On the contrary, by using $\eta$ as the objective function, which dividing $I_o$ and $\max\bm{I}_b$, the influence of these factors on the results is eliminated, as shown in Tabs.
-\ref{tab:given_x} and \ref{tab:find_mac}.
-$\eta$ only reflects the maximum output current capability of the RBS structure.
-Assuming that the maximum allowed current of battery cells in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by calculating the $\eta$ of the structure.
-Therefore, compared to $I_o$, $\eta$ is more suitable for structure design. 
-Most of the currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} have simple topological characteristics, and the calculation of MACs are relatively simple, even intuitive.
-% #TODO 添加cite
-However, when complex and flexible structures need to be designed for application scenarios such as equalization or isolation of specific battery cells, the estimation of MAC will become complex and complicated.
-The method proposed in this paper can effectively solve any RBS structure and estimate MAC universally, paving the way for the structure design of more complex and flexible RBSs.
-
-When the RBS has isolated battery cells, the original topology of the structure is altered. 
-However, the method proposed in this paper can still be used to calculate the MAC of the new structure. 
-The MAC after the isolation operation can be obtained by calculating the new structure following the procedures described in the previous subsection.
-During the calculation process, the isolated battery cell(s) do not participate in the calculation, i.e., their nodes, edges, and $SP$s are not considered. 
-The MACs under various isolated battery cell(s) are calculated on the structures proposed by Lawson et al.
-(Fig.
-\ref{fig:arch-e}), Visairo et al.
-(Fig.
-\ref{fig:arch-f}), and the new structure that integrates the previous two structures (Fig.
-\ref{fig:ef-topo}), as shown in Fig.
-\ref{fig:isolated_mac}.
-For the structure proposed by Lawson et al., the MAC remains the same as that without isolated battery cells, i.e., $\eta=1$, when the number of isolated battery cells increases, until all the cells in the RBS are isolated.
-For the structure proposed by Visairo et al., the MAC decreases as the number of isolated battery cells increases, until $\eta=0$.
-While the new structure has two cases of isolating two cells, one is to isolate two cells within the same substructure, in which case $\eta=2$; the other is to isolate one cell in each of the two substructures, in which case $\eta=1$.
-Overall, the MAC of the new structure is positioned between the structures proposed by Lawson et al. and Visairo et al..
-It can be seen that the MAC of the structure in Fig. \ref{fig:arch-e} is the most stable, and the structure has advantages in isolation and redundancy backup, but its MAC is the smallest. 
-The structure proposed shown by Fig. \ref{fig:arch-f} can output the largest MAC but is susceptible to the number of isolated battery cells. 
-However, the structure proposed by this paper has certain advantages in both aspects, being insensitive to the number of isolated battery cells while simultaneously achieving a larger MAC.
-
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=0.8\textwidth]{../attachments/isolated_mac.png}
-    \caption{
-        The variation of MAC with the number of isolated battery cells for different RBS structures, including the structure proposed by Lawson et al., Visairo et al.
-, and the new structure in this paper.
-    }\label{fig:isolated_mac}
-\end{figure}
+% 对 my 结构的具体示意图 #TODO
+% 隔离1个 fig:my-isolated-1
+% 隔离2个，最好的情况 fig:my-isolated-2b
+% 隔离2个，最差的情况 fig:my-isolated-2w
+% 隔离3个 fig:my-isolated-3
 
@@
 
+\newpage
 \section{Appendix}
+
 \begin{algorithm}
-    \caption{Get the max available currents of a certain RBS}\label{alg:eta_RBS}
+    \caption{Get the max available currents of a certain RBS}\label{alg:greedy}
     \KwData{Directed graph model $G(V,E)$ of the RBS}

### 2023-06-26 paper/main.tex
修改了 conclusion

@@
 %      -[x] 增加隔离的处理，如约束、算法的改动
-% -[ ] case study 
+% -[x] case study 
 %      -[-] 考虑新结构（MAC=4，想不到就算了，仍用ef结构）(0626: 想不到)；
 %      -[x] results 直接给出结果，略去计算细节；
-%      -[ ] discussion 说明eta的合理性；
+%      -[x] discussion 说明eta的合理性；
 %      -[-] 什么样的结构能获得更大的MAC（易隔离性和输出性能的冲突）（想不出来就算了）(0626:有想法，但是要引入互斥片段的概念)；
-%      -[ ] 电池隔离场景下的MAC变化(比较不同结构)
+%      -[x] 电池隔离场景下的MAC变化(比较不同结构)
 
@@
 
-This paper firstly proposes a method to calculation the MAC of RBS according to its architecture. 
-To find the circuit in RBS that enable the MAC, a greedy strategy incorporate with the topologic model is developed to. 
-The effectiveness of proposed method is tested on a more complex RBS structure based on two proposed structure.
-This work presents an effective approach to evaluate the MAC of RBS, which is essential for design and management of the RBS. 
-Future research could focus on developing new performance indicators for evaluating RBS performance using the currents and voltages obtained by this method, as well as modifying the equivalent model of the battery to enable more accurate simulations of RBS, including transient analysis.
+This paper proposes a method for computing the MAC of an RBS pervasively and automatically based on its structure.
+To identify the circuit within the RBS that enables the MAC, a greedy strategy combined with a directed graph model is developed.
+The effectiveness of the proposed method is tested on a more complex RBS structure, which is based on two proposed structures.
+The method remains effective for the application scenario of battery isolation in RBS and demonstrates that the new structure has the advantage of both output current flexibility and easy battery isolation.
+Future research could focus on developing new performance metrics to evaluate the performance of the RBS using the currents and voltages obtained by the method, as well as modifying the equivalent model of the battery to allow for more accurate simulations of the RBS, including transient analysis.
 

### 2023-06-27 paper/main.tex
修改了 conclusion introduction 和 摘要

@@
 % -[ ] 题目 点明我们的普适性、自动化？
-% -[ ] 摘要 中间段重写；点明普适性、自动化
-% -[ ] introduction 
-%      -[ ] 只放 V的结构，并展示串联、并联和隔离；
-%      -[ ] 增加重构灵活性的文献；
-%      -[ ] 有向图的文献；
-%      -[ ] 点明普适性、自动化
+% -[x] 摘要 中间段重写；点明普适性、自动化
+% -[x] introduction 
+%      -[x] 只放 V的结构，并展示串联、并联和隔离；
+%      -[-] 增加重构灵活性的文献；
+%      -[-] 有向图的文献；
+%      -[x] 点明普适性、自动化
 % -[x] methodology 
@@
 \title{Maximum Allowable Current Determination of Arbitrary Reconfigurable Battery Systems By Using a Directed Graph Model Combined with Greedy Algorithm}
+
 \author{3057761608 }
@@
 
-\begin{abstract} % #TODO: rewrite
+\begin{abstract} % # TODO: check
     Reconfigurable Battery Systems (RBSs) offer a promising alternative to traditional battery systems owing to their flexible and dynamic changeable topologic structure subjected to battery charging and discharging strategies.
     During the operation of the RBS, Maximum Allowable Current (MAC) is a critical indicator to guide the reconfiguring control of the system in terms of safety and reliability. 
-    In this paper, the MAC of the RBS is calculated by using a greedy algorithm based on the directed graph model of the RBS. % 这句话展开讲， Greedy algorithm方法被用于…/与…方法相结合，实现了对任意RBS结构的MAC提取，
-    % The greedy algorithm method has been used to solve a model based on topology structure, achieving MAC estimation for any RBS structure.
-    The effectiveness of this method is validated on a more complex RBS structure based on two proposed structure. 
-    This proposed Greedy-based method paves the way for more flexible design and more complex application scenarios, such as battery isolation, for RBS.
+    In this paper, the MAC of the RBS is calculated using a greedy algorithm combined with the directed graph model of the RBS.
+    Based on the directed graph model, the algorithm guides the RBS to allow as many batteries to be connected in parallel as possible, thus maximizing the output current of the system while ensuring proper battery operation.
+    The effectiveness of this method is validated on a novel and complex RBS structure.
+    This method paves the way for next-generation RBS design and application, such as battery isolation.
 
-    keywords:  Reconfigurable Battery System, Maximum Allowable Current, Greedy Algorithm
+    keywords:  Reconfigurable Battery System, Maximum Allowable Current, Directed Graph Model , Greedy Algorithm
 \end{abstract}
@@
 \section{Introduction}
-% 不放案例
-% 重构灵活性的文献
-% 有向图的文献
 
@@
 Furthermore, if this worst battery is failed during the operation process, it will exacerbate the degradation of the other batteries with a high possibility, and arouse reliability and even safety issues \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019}.
+% #TODO: 放些 space 电池组的文献
 
@@
 The ability of switching circuit helps to isolate unhealthy batteries, and thereby improve the safety and reliability of the battery system.
-Fig.\ref{fig:arch} shows two popular typologies of the RBSs developed by Lawson\cite{lawsonSoftwareConfigurableBattery2012} and Visairo \cite{visairoReconfigurableBatteryPack2008} respectively. 
-Taking the RBS shown in Fig.\ref{fig:stru-Visairo} as example, the batteries in the RBS can be connected not only in series when the switches $S_1$, $S_5$, $S_6$, $S_7$, $S_8$, $S_9$, and $S_{13}$ are closed, but also in parallel when $S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$, and $S_{13}$ are closed.
-Furthermore, when an unhealthy battery, for instance the orange one in Fig.\ref{fig:stru-Lawson}, exits in the RBS, it can be isolated by closing its three adjacent switches (i.e.
-$S_5$, $S_7$ and $S_8$) and opening the switch below that battery (i.e.
-$S_6$) to ensure the system still remains a reliable working mode.
-% 补充一句话总结，visairo的网络与固定串并联结构相比具有哪些优点，更适合使用在什么场合
+Fig.\ref{fig:stru-Visairo} shows a typical RBS structure developed by Visairo \cite{visairoReconfigurableBatteryPack2008} for dynamically adjusting the output voltage and current.
+In this structure, the batteries can be connected not only in series when the switches $S_1$, $S_5$, $S_6$, $S_7$, $S_8$, $S_9$, and $S_{13}$ are closed (Fig.\ref{fig:stru-Visairo-serial}), but also in parallel when $S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$, and $S_{13}$ are closed (Fig.\ref{fig:stru-Visairo-parallel}).
+Furthermore, when an unhealthy battery, for instance the orange one $B_3$ in Fig.\ref{fig:stru-Visairo-isolate}, appears in the RBS, it can be isolated by opening its two adjacent switches (i.e.
+$S_4$ and $S_{11}$), ensuring the system still remains a reliable working mode.
 
-\begin{figure}[htbp]
+\begin{figure}[htbp] % #TODO: V 的结构示意图
     \centering
-    \begin{subfigure}[b]{0.2\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/arch-e.png}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/arch-f.png} % 完整结构
         \caption{}
-        \label{fig:stru-Lawson}
+        \label{fig:stru-Visairo}
     \end{subfigure}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/arch-f.png}
+        \includegraphics[width=\textwidth]{../attachments/arch-f.png} % 全串联
         \caption{}
-        \label{fig:stru-Visairo}
+        \label{fig:stru-Visairo-serial}
     \end{subfigure}
-    \caption{The RBS structure proposed by (a)Lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b)Visairo\cite{visairoReconfigurableBatteryPack2008}.}
+    \\
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/arch-f.png} % 全并联
+        \caption{}
+        \label{fig:stru-Visairo-parallel}
+    \end{subfigure}
+    \hspace{0.05\textwidth}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/arch-f.png} % 电池隔离 右二 B3 全并联
+        \caption{}
+        \label{fig:stru-Visairo-isolate}
+    \end{subfigure}
+    \caption{
+        (a) The RBS structure proposed by Visairo\cite{visairoReconfigurableBatteryPack2008}, with
+        all batteries in (b) series connection, (c) parallel connection, and
+        (d) battery $B_3$ isolated.
+        }
     \label{fig:arch}
@@
 
-The complex connecting structure between batteries and switches enables the flexibility of the RBS, but on the other hand brings the challenges in desgin and control cost as well.
-All switches of the RBS need to be controlled to output currents and powers that match the external load in read-time while avoiding batteries short-circuit.
-The Maximum Allowable Current (MAC) of the RBS system is defined as the maximum current that is allowed for each individual battery of the system, and is a critical indictor to be evaluate the RBS output current to the electronic appliances.% 这里缺少过渡，MAC和设计与控制成本有什么关系？
-It helps the designer to assess whether the RBS meets the output current requirements, and contributes to the formulation of appropriate and safe management stragegies for the battery management system (BMS).
-Despite its importance, there is currently no way to automatically evaluate MAC for RBSs. 
-Especially when one (or more) stochastic battery is isolated, it is not possible to simultaneously determine the MAC of the rest of the RBS to assist the BMS to provide a timely adjustment of the control strategy.
-Under such circumstance, a universal and effective method for calculating the MAC of the RBS is urgently needed for the practical application of RBSs. 
-To achieve this, a directed graph model that builds the relationship between RBS circuit topology and internal resistance and voltage of its batteries are established. 
-Then, a greedy algorithm is employed to search the available circuit of the RBS for reaching the MAC.
-% 以上两句话争取合并成一句话，提出的方法应该紧扣标题（即与标题的方法一致）
-With this proposed method, the MAC of RBSs with arbitrary structures can be calculated effectively, including application scenarios with isolated batteries.
+The complex connection structure between batteries and switches in the RBS provides flexibility but also introduces challenges in design and operational control. 
+Unlike traditional BESSs with fixed outputs, the RBS output must be dynamically adjusted by controlling switch states to meet external load requirements. 
+This necessitates additional, time-consuming output performance analysis during design and corresponding control strategies. 
+An incorrect switch control strategy may cause battery short-circuiting or overload, risking the entire system. 
+The Maximum Allowable Current (MAC), an RBS performance indicator, can guide designers in addressing this issue. 
+MAC is defined as the maximum RBS output current that ensures each battery's current remains within a safe range.
+Therefore, it provides a benchmark for RBS output current, protecting individual batteries and identifying overall system output limits during operation. 
+Despite its importance, no method currently exists for automatically evaluating MAC for RBSs.
+In particular, when one or more random cells are isolated, there is still no method to determine the MAC of the remaining RBS in time to assist the system in adjusting the control strategy timely. 
+A universal and automatical method for calculating RBS MAC is urgently needed for practical applications. 
+In this study, a directed graph model and greedy algorithm are employed to determine the MAC of RBS and the corresponding control strategy, effectively calculating the MAC for RBSs with arbitrary structures, including scenarios with isolated batteries.
 
 The remainder of this paper is organized as follows: 
-Section II presents the framework and details of the proposed topologic model and the greedy algorithm. 
-In Section III, a case study of using the proposed model and algorithm to enumerate the MAC of a new and complex structure is demonstrated. 
+Section II presents the framework and details of the proposed directed graph model and the greedy algorithm. 
+Section III demonstrated a case study of using the proposed method to determine the MAC of a novel and complex structure. 
 The calculation results and scenarios such as batteries isolation also are discussed. 
@@
     \begin{subfigure}[b]{0.24\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/direct-graph-my.png}
+        \includegraphics[width=\textwidth]{../attachments/direct-graph-my.png} % #TODO: 蓝色线段由实变虚
         \caption{}
@@
     \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/arch-ef.png}
+        \includegraphics[width=\textwidth]{../attachments/arch-ef.png} % #TODO: 去掉虚线框
         \caption{}
@@
 By integrating the Visairo RBS structure into the Lawson RBS structure, the new structure not only allows the flexibility to switch the batteries between series, parallel, and mixed series-parallel modes, but also easily enables the isolation of highly degraded batteries from the RBS.
-These three structures will be employed to validate the effectiveness of this paper's proposed method for calculating the MAC. 
 And their variations in output current under battery isolation conditions will be studied.
+This RBS structure will be used to validate the effectiveness of the proposed method for calculating the MAC, and be compared with the Lawson's and Visairo's structure to illustrate its advantage on battery isolation.
 
@@
 The external electrical load is treated as a directed edge from the cathode of the RBS (i.e., node 18) to the anode (i.e., node 1), as indicated by the blue directed edge in the graph.
-Utilizing Eq.\ref{eq:weight} and the Dijkstra algorithm, the $SP$s of the four batteries in the RBS structure of Fig.\ref{fig:study-stru-my} are shown in Figs.\ref{fig:sp1}-\ref{fig:sp4}, highlighted in red.
+Utilizing Eq.\ref{eq:weight} and the Dijkstra algorithm, the $SP$s of the four batteries in the RBS structure of Fig.\ref{fig:study-stru-my} are highlighted by red in Figs.\ref{fig:sp1}-\ref{fig:sp4}.
 Finally, the MAC calculation results of the structure in Fig.\ref{fig:study-stru-my} are shown as Tab.\ref{tab:study-results-my} and Fig.\ref{fig:study-results-my}, obtained by the greedy algorithm \ref{alg:greedy}.
@@
         Structure & Fig.\ref{fig:study-stru-my} with 4 batteries and 19 switches  \\
-        % Battery isolated & None \\
     \midrule
@@
         Structure & Fig.\ref{fig:study-stru-Lawson} with 4 batteries and 15 switches  \\
-        % Battery isolated & None \\
     \midrule
@@
         Structure & Fig.\ref{fig:study-stru-Visairo} with 4 batteries and 13 switches  \\
-        % Battery isolated & None \\
     \midrule
@@
 
-Furthermore, the significance of the method proposed in this paper is discussed from the perspective of next-generation RBS design.
+The method proposed in this paper is significant for the design of next-generation RBSs in the following aspects.
 Most of the currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} exhibit simple topological characteristics, and the calculation of MACs is relatively straightforward, even intuitive.
@@
 
-Furthermore, the performance of output current for the three RBS when isolating batteries is also illustrated in Fig. \ref{fig:isolated_mac}. 
+Furthermore, the performance of output current for the three RBS when isolating batteries is also illustrated in Fig.\ref{fig:isolated_mac}. 
 For the structure proposed by Lawson et al., the MAC remains the same as that without isolated battery cells, i.e., $\eta=1$, when the number of isolated battery cells increases, until all the cells in the RBS are isolated.
@@
 
-This paper proposes a method for computing the MAC of an RBS pervasively and automatically based on its structure.
-To identify the circuit within the RBS that enables the MAC, a greedy strategy combined with a directed graph model is developed.
-The effectiveness of the proposed method is tested on a more complex RBS structure, which is based on two proposed structures.
-The method remains effective for the application scenario of battery isolation in RBS and demonstrates that the new structure has the advantage of both output current flexibility and easy battery isolation.
-Future research could focus on developing new performance metrics to evaluate the performance of the RBS using the currents and voltages obtained by the method, as well as modifying the equivalent model of the battery to allow for more accurate simulations of the RBS, including transient analysis.
+This paper proposes a pervasive and automatical method for computing the MAC of the given RBS.
+The method is  implemented by a greedy algorithm combined with a directed graph model, whose effectiveness is tested on a novel and complex RBS structure.
+The method remains effective for the application scenario of RBS battery isolation and demonstrates that the novel structure has the advantage on flexible output current and convenient battery isolation.
+Future research could focus on developing new indictors to evaluate the performance of the RBS with the currents and voltages obtained by the method, as well as modifying the equivalent model of the battery to allow for more accurate simulations of the RBS, including transient analysis.
 
 \newpage
+
 \section{Appendix}

### 2023-06-27 paper/main.tex
再次修改了摘要

@@
 % !!!!!! 先改方法、后改案例、最后改介绍和其他
-% -[ ] 题目 点明我们的普适性、自动化？
+% -[x] 题目 点明我们的普适性、自动化？
 % -[x] 摘要 中间段重写；点明普适性、自动化
@@
 
-% keep in mind
-% 1. 用最简洁、读者最能接受的话说明清楚自己想表达的内容
-
 % mark
@@
 % 统一用 electrical load 而非 electrical appliance (泛指家电)
-
-% magic
-% 你将扮演一位英文学术写作经验丰富的大学老师，指导一位非英文母语的学生完成并改进他的论文。 你的目标是帮助他写出一篇流畅、清晰、易读、符合规范的英文学术论文。 他会向你用中文说明自己想表达的内容，有时还会给你一些不完整的英文句子让你补充完整。你不应该逐字翻译他的内容，你需要和他经过多次的沟通，以确定最好的表达。 注意，你们交流的内容可能包含latex语法，你需要理解并使用；当你形成完整的句子或段落时，你要将这些句子或段落放在```\n 和\n ```之间，即 ```\n some sentence\n ```，其中每写完一句话都要换行。
 
@@
 
-\begin{abstract} % # TODO: check
-    Reconfigurable Battery Systems (RBSs) offer a promising alternative to traditional battery systems owing to their flexible and dynamic changeable topologic structure subjected to battery charging and discharging strategies.
-    During the operation of the RBS, Maximum Allowable Current (MAC) is a critical indicator to guide the reconfiguring control of the system in terms of safety and reliability. 
-    In this paper, the MAC of the RBS is calculated using a greedy algorithm combined with the directed graph model of the RBS.
-    Based on the directed graph model, the algorithm guides the RBS to allow as many batteries to be connected in parallel as possible, thus maximizing the output current of the system while ensuring proper battery operation.
+\begin{abstract}
+    Reconfigurable Battery Systems (RBSs) present a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structure subjected to battery charging and discharging strategies.
+    During the operation of the RBS, the Maximum Allowable Current (MAC) is a critical indicator to guide the system's reconfiguring control, ensuring safety and reliability.
+    In this paper, we propose a calculation method for the MAC of an RBS using a greedy algorithm in conjunction with a directed graph model of the RBS.
+    By employing the directed graph model, the greedy algorithm guides the RBS to establish parallel connections among batteries, aiming to maximize the system's output current while ensuring that none of the batteries are overloaded or short-circuited.
     The effectiveness of this method is validated on a novel and complex RBS structure.
-    This method paves the way for next-generation RBS design and application, such as battery isolation.
+    The results demonstrate the viability of this method and its potential in facilitating next-generation RBS designs and applications, including battery isolation.
 

### 2023-06-27 paper/main.tex
修改了图片

@@
 
+% #TODO: 根据 space 的背景进行修改，放点它们的文献
 Battery Energy Storage Systems (BESSs) are widely used to store and release high-quality electrical energy in various applications, such as smart grids and wind power plants \cite{desiqueiraControlStrategySmooth2021,karandehTwoStageAlgorithmOptimal2019,yangBatteryEnergyStorage2018,choCommercialResearchBattery2015}.
@@
 Furthermore, if this worst battery is failed during the operation process, it will exacerbate the degradation of the other batteries with a high possibility, and arouse reliability and even safety issues \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019}.
-% #TODO: 放些 space 电池组的文献
 
@@
 
-\begin{figure}[htbp] % #TODO: V 的结构示意图
+\begin{figure}[htbp]
     \centering
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/arch-f.png} % 完整结构
+        \includegraphics[width=\textwidth]{../attachments/stru-V-origin.png} % 完整结构
         \caption{}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/arch-f.png} % 全串联
+        \includegraphics[width=\textwidth]{../attachments/stru-V-serial.png} % 全串联
         \caption{}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/arch-f.png} % 全并联
+        \includegraphics[width=\textwidth]{../attachments/stru-V-parallel.png} % 全并联
         \caption{}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/arch-f.png} % 电池隔离 右二 B3 全并联
+        \includegraphics[width=\textwidth]{../attachments/stru-V-isolate} % 电池隔离 右二 B3 全并联
         \caption{}
@@
     \begin{subfigure}[b]{0.8\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/main.png} % #TODO: 修改step2中的公式
+        \includegraphics[width=\textwidth]{../attachments/main.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.24\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/direct-graph-my.png} % #TODO: 蓝色线段由实变虚
+        \includegraphics[width=\textwidth]{../attachments/direct-graph-my.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.2\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/arch-e.png} % #TODO: 把不健康电池改为健康
+        \includegraphics[width=\textwidth]{../attachments/stru-L-origin.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.4\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/arch-f.png}
+        \includegraphics[width=\textwidth]{../attachments/stru-V-origin.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/arch-ef.png} % #TODO: 去掉虚线框
+        \includegraphics[width=\textwidth]{../attachments/stru-my-origin.png}
         \caption{}
@@
 
-\begin{figure}[htbp] % #TODO：补上两个开关
+\begin{figure}[htbp]
     \centering
     \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/ef-topo.png} % #TODO：补上两个开关
+        \includegraphics[width=\textwidth]{../attachments/ef-topo.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/ef-mac.png} % #TODO: 闭合开关。移除开关，直接连上
+        \includegraphics[width=\textwidth]{../attachments/ef-mac.png}
         \caption{}
@@
     \centering
-    \includegraphics[width=0.65\textwidth]{../attachments/isolated_mac.png}
+    \includegraphics[width=0.5\textwidth]{../attachments/isolated_mac.png}
     \caption{
@@
 
-% 对 my 结构的具体示意图 #TODO
-% 隔离1个 fig:my-isolated-1
-% 隔离2个，最好的情况 fig:my-isolated-2b
-% 隔离2个，最差的情况 fig:my-isolated-2w
-% 隔离3个 fig:my-isolated-3
+\begin{figure}[htbp]
+    \centering
+    \begin{subfigure}[b]{0.31\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/my-isolated-1.png}
+        \caption{}
+        \label{fig:my-isolated-1}
+    \end{subfigure}
+    \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.31\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/my-isolated-2b.png}
+        \caption{}
+        \label{fig:my-isolated-2b}
+    \end{subfigure}
+    \\
+    \begin{subfigure}[b]{0.31\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/my-isolated-2w.png}
+        \caption{}
+        \label{fig:my-isolated-2w}
+    \end{subfigure}
+    \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.31\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/my-isolated-3.png}
+        \caption{}
+        \label{fig:my-isolated-3}
+    \end{subfigure}
+    \caption{
+        The circuit states of MACs when isolating (a)one, (b)two(best case), (c)two(worst case) and (d)three batteries for the structure in Fig.\ref{fig:study-stru-my}.
+        }
+\end{figure}
 

### 2023-06-27 paper/main.tex
space相关：添加文献、修改introduction

@@
 
-% #TODO: 根据 space 的背景进行修改，放点它们的文献
-Battery Energy Storage Systems (BESSs) are widely used to store and release high-quality electrical energy in various applications, such as smart grids and wind power plants \cite{desiqueiraControlStrategySmooth2021,karandehTwoStageAlgorithmOptimal2019,yangBatteryEnergyStorage2018,choCommercialResearchBattery2015}.
-Typically, a BESS consists of numerous batteries that are interconnected by series-parallel circuitry to provide the required capacity storage.
-The traditional BESS, in which the batteries are connected in a fixed topology, has a significant weakness on its worst battery, caused by the so-called cask effect.
-Furthermore, if this worst battery is failed during the operation process, it will exacerbate the degradation of the other batteries with a high possibility, and arouse reliability and even safety issues \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019}.
+Battery Energy Storage Systems (BESSs) are extensively employed in various applications, such as wind power plants and space power systems, to store and release high-quality electrical energy \cite{desiqueiraControlStrategySmooth2021,yangBatteryEnergyStorage2018,choCommercialResearchBattery2015,zhangDevelopmentProspectChinese2021,schwanbeckInternationalSpaceStation2019}.
+Typically, a BESS consists of numerous batteries interconnected by series-parallel circuitry to provide the required capacity storage.
+However, traditional BESSs, in which the batteries are connected in a fixed topology, exhibit a significant weakness in their worst battery due to the so-called cask effect.
+Moreover, if this worst battery fails during operation, it can exacerbate the degradation of other batteries with a high possibility, leading to reliability and safety issues \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019,jeevarajanBatterySafetyQualifications2012}.
+These problems have become significant technical barriers in the development of new-generation space vehicles and urgently need to be addressed \cite{pomboHybridPowerSystem2021}.
 
-Reconfigurable Battery System (RBS), which can dynamically switch to different circuit topology configurations as required, is expected to solve the above problem\cite{hanNextGenerationBatteryManagement2020a}.
+Reconfigurable Battery System (RBS), which can dynamically switch to different circuit topology configurations as required, is expected to solve the above problems\cite{hanNextGenerationBatteryManagement2020a}.
 The ability of switching circuit helps to isolate unhealthy batteries, and thereby improve the safety and reliability of the battery system.

### 2023-06-27 paper/simple_for_2docx.tex
转换为 docx 格式并调整 （V3）

@@
+% 0622 v3.0 plan
+% -[x] 将 word 批注和修改内容整理到 tex 中
+% -[x] 确定修改要点，批注和obsidian记录
+
+% 0623 v3.0 plan 具体修改计划
+% !!!!!! 先改方法、后改案例、最后改介绍和其他
+% -[x] 题目 点明我们的普适性、自动化？
+% -[x] 摘要 中间段重写；点明普适性、自动化
+% -[x] introduction 
+%      -[x] 只放 V的结构，并展示串联、并联和隔离；
+%      -[-] 增加重构灵活性的文献；
+%      -[-] 有向图的文献；
+%      -[x] 点明普适性、自动化
+% -[x] methodology 
+%      -[x] main 图重画，只保留文字；
+%      -[x] 有向图模型，说清三层关系，更规矩地写建模过程；
+%      -[x] 优化目标和约束；
+%      -[x] 最短路径，逐句逐字去捋顺；
+%      -[x] 贪心算法，结合流程图说明算法过程，把二分法融进去；
+%      -[x] 增加隔离的处理，如约束、算法的改动
+% -[x] case study 
+%      -[-] 考虑新结构（MAC=4，想不到就算了，仍用ef结构）(0626: 想不到)；
+%      -[x] results 直接给出结果，略去计算细节；
+%      -[x] discussion 说明eta的合理性；
+%      -[-] 什么样的结构能获得更大的MAC（易隔离性和输出性能的冲突）（想不出来就算了）(0626:有想法，但是要引入互斥片段的概念)；
+%      -[x] 电池隔离场景下的MAC变化(比较不同结构)
+
+% mark
+% 统一为 directed graph model
+% 统一用 electrical load 而非 electrical appliance (泛指家电)
+
 \documentclass{article}
@@
 \usepackage{tikz}
-\usetikzlibrary{
-  arrows.meta,
-  calc,
-  fit,
-  positioning,
-  quotes,
-  graphs,
-  shapes.geometric
-}
+\usetikzlibrary{arrows.meta, calc, fit, positioning, quotes, graphs, shapes.geometric}
 \def\T{\mathrm{T}}
 
-\title{A Greedy-based calculation method of RBS maximum allowable current}
+\title{Maximum Allowable Current Determination of Arbitrary Reconfigurable Battery Systems By Using a Directed Graph Model Combined with Greedy Algorithm}
+
 \author{3057761608 }
@@
 \begin{abstract}
-    Reconfigurable Battery Systems (RBSs) offer a promising alternative to traditional battery systems owing to their dynamical topologic structure for the optimization of battery cell charging and discharging stragegies.
-    During the operation of the RBS, the Maximum Allowable Current (MAC) is a critical indicator to guide the reconfiguring control of the system in terms of safety and reliability.
-    In this paper, the MAC of the RBS is calculated by using a greedy algorithm based on the topologic model of the RBS.
-    The effectiveness of this method is validated on a more complex RBS structure based on two proposed structure.
-    The MAC and the computational method proposed in this article pave the way for more flexible design and more complex application scenarios, such as battery cell isolation, for RBS.
+    Reconfigurable Battery Systems (RBSs) present a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structure subjected to battery charging and discharging strategies.
+    During the operation of the RBS, the Maximum Allowable Current (MAC) is a critical indicator to guide the system's reconfiguring control, ensuring safety and reliability.
+    In this paper, we propose a calculation method for the MAC of an RBS using a greedy algorithm in conjunction with a directed graph model of the RBS.
+    By employing the directed graph model, the greedy algorithm guides the RBS to establish parallel connections among batteries, aiming to maximize the system's output current while ensuring that none of the batteries are overloaded or short-circuited.
+    The effectiveness of this method is validated on a novel and complex RBS structure.
+    The results demonstrate the viability of this method and its potential in facilitating next-generation RBS designs and applications, including battery isolation.
 
-    keywords: Reconfigurable Battery System, Maximum Allowable Current, Greedy Algorithm
+    keywords:  Reconfigurable Battery System, Maximum Allowable Current, Directed Graph Model , Greedy Algorithm
 \end{abstract}
@@
 
-Battery Energy Storage Systems (BESSs) are widely used to store and supply high-quality electrical energy in various applications, such as smart grids and wind power plants \cite{desiqueiraControlStrategySmooth2021,karandehTwoStageAlgorithmOptimal2019,yangBatteryEnergyStorage2018,choCommercialResearchBattery2015}.
-Typically, a BESS consists of numerous battery cells that are interconnected by series-parallel circuitry to provide the required charge storage capacity and output voltage.
-For the traditional BESS, the connections between batteries are fixed and the performance of system is limited by the worst cell, as the result of the cask effect.
-Furthermore, reliability and even safety issues will alse be aroused since the failed battery cannot be promptly isolated to exacerbate the degradation of the other batteries during the operational process \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019}.
-Undoubtedly theses issues hinder the practical application of traditional BESSs.
+Battery Energy Storage Systems (BESSs) are extensively employed in various applications, such as wind power plants and space power systems, to store and release high-quality electrical energy \cite{desiqueiraControlStrategySmooth2021,yangBatteryEnergyStorage2018,choCommercialResearchBattery2015,zhangDevelopmentProspectChinese2021,schwanbeckInternationalSpaceStation2019}.
+Typically, a BESS consists of numerous batteries interconnected by series-parallel circuitry to provide the required capacity storage.
+However, traditional BESSs, in which the batteries are connected in a fixed topology, exhibit a significant weakness in their worst battery due to the so-called cask effect.
+Moreover, if this worst battery fails during operation, it can exacerbate the degradation of other batteries with a high possibility, leading to reliability and safety issues \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019,jeevarajanBatterySafetyQualifications2012}.
+These problems have become significant technical barriers in the development of new-generation space vehicles and urgently need to be addressed \cite{pomboHybridPowerSystem2021}.
 
-Reconfigurable Battery System (RBS), which can dynamically switch to arbitrary circuit configurations as required, is expected to solve the above problem\cite{hanNextGenerationBatteryManagement2020a}.
-The ability to switches circuit helps to isolate unhealthy batteries from the circuit in a timely manner, thereby improving the safety and reliability of the battery system.
-Fig. \ref{fig:arch} shows two popular typologies of the RBSs developed by Lawson\cite{lawsonSoftwareConfigurableBattery2012} and Visairo \cite{visairoReconfigurableBatteryPack2008} respectively. 
-Taking the RBS shown in Fig.
-\ref{fig:arch-e} as example, the batteries in the RBS can beare connected not only in series when the switches $S_1$, $S_5$, $S_6$, $S_7$, $S_8$, $S_9$, and $S_{13}$ are closed, but also in parallel when $S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$, and $S_{13}$ are closed.
-Furthermore, when an unhealthy battery, for instance the orange one in Fig.
-\ref{fig:arch-f}, exits in the RBS, it can be isolated by closing its three adjacent switches (i.e.
-$S_5$, $S_7$ and $S_8$) and opening the switch below that battery (i.e.
-$S_6$) to ensure the system still remains a reliable working mode.
+Reconfigurable Battery System (RBS), which can dynamically switch to different circuit topology configurations as required, is expected to solve the above problems\cite{hanNextGenerationBatteryManagement2020a}.
+The ability of switching circuit helps to isolate unhealthy batteries, and thereby improve the safety and reliability of the battery system.
+Fig.\ref{fig:stru-Visairo} shows a typical RBS structure developed by Visairo \cite{visairoReconfigurableBatteryPack2008} for dynamically adjusting the output voltage and current.
+In this structure, the batteries can be connected not only in series when the switches $S_1$, $S_5$, $S_6$, $S_7$, $S_8$, $S_9$, and $S_{13}$ are closed (Fig.\ref{fig:stru-Visairo-serial}), but also in parallel when $S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$, and $S_{13}$ are closed (Fig.\ref{fig:stru-Visairo-parallel}).
+Furthermore, when an unhealthy battery, for instance the orange one $B_3$ in Fig.\ref{fig:stru-Visairo-isolate}, appears in the RBS, it can be isolated by opening its two adjacent switches (i.e.
+$S_4$ and $S_{11}$), ensuring the system still remains a reliable working mode.
 
@@
     \centering
-   \begin{subfigure}[b]{0.2\textwidth}
-       \includegraphics[width=\textwidth]{../attachments/arch-e.png}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/stru-V-origin.png} % 完整结构
         \caption{}
-       \label{fig:arch-f}
+        \label{fig:stru-Visairo}
     \end{subfigure}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-       \includegraphics[width=\textwidth]{../attachments/arch-f.png}
+        \includegraphics[width=\textwidth]{../attachments/stru-V-serial.png} % 全串联
         \caption{}
-       \label{fig:arch-e}
+        \label{fig:stru-Visairo-serial}
     \end{subfigure}
-    \caption{The RBS structure proposed by (a)Lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b)Visairo\cite{visairoReconfigurableBatteryPack2008}.}
+    \\
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/stru-V-parallel.png} % 全并联
+        \caption{}
+        \label{fig:stru-Visairo-parallel}
+    \end{subfigure}
+    \hspace{0.05\textwidth}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/stru-V-isolate} % 电池隔离 右二 B3 全并联
+        \caption{}
+        \label{fig:stru-Visairo-isolate}
+    \end{subfigure}
+    \caption{
+        (a) The RBS structure proposed by Visairo\cite{visairoReconfigurableBatteryPack2008}, with
+        all batteries in (b) series connection, (c) parallel connection, and
+        (d) battery $B_3$ isolated.
+        }
     \label{fig:arch}
@@
 
-The complex connecting structure between batteries and switches enables the flexibility of the RBS, but also brings the challenges in design and control cost.
-The Maximum Allowable Current (MAC) of the RBS system is defined as the maximum current that is allowed for each individual battery of the system, and is a critical indictor to be evaluate the RBS output current to the electronic appliances.
-It helps the designer to assess whether the RBS meets the output current requirements, and contributes to the formulation of appropriate and safe management stragegies for the battery management system (BMS).
-As the complexity of RBS increases, especially when the certain battery needs to be isolated, it becomes difficult to visually obtain the MAC, and a universal algorithm is needed to solve the MAC.
-Despite its importance, there is currently no method available to evaluate MAC for RBSs.
-Therefore, the purpose of this paper is to propose a universal and effective method for calculating the MAC of the RBS.
-To achieve this, a topologic model that builds the relationship between RBS circuit topology and internal resistance and voltage of its batteries are established.
-Then, a greedy algorithm is employed to search the available circuit of the RBS for reaching the MAC.
-With the developed method, MAC of RBSs with different structures can be calculated effectively, including application scenarios with isolated battery cells.
+The complex connection structure between batteries and switches in the RBS provides flexibility but also introduces challenges in design and operational control. 
+Unlike traditional BESSs with fixed outputs, the RBS output must be dynamically adjusted by controlling switch states to meet external load requirements. 
+This necessitates additional, time-consuming output performance analysis during design and corresponding control strategies. 
+An incorrect switch control strategy may cause battery short-circuiting or overload, risking the entire system. 
+The Maximum Allowable Current (MAC), an RBS performance indicator, can guide designers in addressing this issue. 
+MAC is defined as the maximum RBS output current that ensures each battery's current remains within a safe range.
+Therefore, it provides a benchmark for RBS output current, protecting individual batteries and identifying overall system output limits during operation. 
+Despite its importance, no method currently exists for automatically evaluating MAC for RBSs.
+In particular, when one or more random cells are isolated, there is still no method to determine the MAC of the remaining RBS in time to assist the system in adjusting the control strategy timely. 
+A universal and automatical method for calculating RBS MAC is urgently needed for practical applications. 
+In this study, a directed graph model and greedy algorithm are employed to determine the MAC of RBS and the corresponding control strategy, effectively calculating the MAC for RBSs with arbitrary structures, including scenarios with isolated batteries.
 
 The remainder of this paper is organized as follows: 
-Section II presents the framework and details of the proposed topologic model and the greedy algorithm.
-In Section III, a case study of using the proposed model and algorithm to enumerate the MAC of a new and complex structure is demonstrated.
-The calculation results and scenarios such as battery cells isolation also are discussed
+Section II presents the framework and details of the proposed directed graph model and the greedy algorithm. 
+Section III demonstrated a case study of using the proposed method to determine the MAC of a novel and complex structure. 
+The calculation results and scenarios such as batteries isolation also are discussed. 
 Finally, the concluding remarks are drawn in Section IV.
@@
 
-The overall MAC modeling process from an RBS structure is shown in Fig. \ref{fig:main}, which can be divided into four main steps.
-In the first place, the actual RBS structure is converted to a topologic model, in which the connected relationships between batteries and switches are abstracted and the performance parameters of the batteries are retained.
-Subsequently, constraints and objective function, i.e. MAC, are obtained based on the previous connected relationships and parameters.
-Then, the shortest path (SP) of each battery in the RBS is obtained by Dijkstra algorithm.
-In the end, the open/close strategy of the RBS is implemented by greedily selecting the SPs to achieve MAC and quantitatively calculated in the equivalent circuit.
+The central principle of this method is to make the batteries in RBS connected in series as much as possible, thereby maximizing the output current of the RBS.
+To universally and automatically achieve this, the overall process is divided into four steps, as shown in Fig.\ref{fig:main}.
+Firstly, a directed graph model is established for subsequent computing, which not only contains the connected relationships between batteries and switches, but also retains the performance parameters of the batteries.
+Subsequently, based on the equivalent circuit, the MAC problem is transformed into specific objective functions and constraints.
+Then, the shortest paths (SPs, where additional batteries and switches on the path are penalized as distance) for the batteries are obtained using the Dijkstra algorithm to guide the batteries in the RBS connect in series.
+Finally, a greedy algorithm is employed to organize the switches, allowing the batteries to connect via their SPs while satisfying the constraints, resulting in the MAC of the RBS.
 
@@
     \end{subfigure}
+    \caption{ 
+        Diagram of this method, which contains four main steps.
+    }
+\end{figure}
+
+\subsection{Directed graph Model}
+
+\begin{figure}[htbp]
+    \centering
+    \begin{subfigure}[b]{0.31\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/direct-graph-he.png}
+        \caption{}
+        \label{fig:direct-graph-he}
+    \end{subfigure}
+    \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.23\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/direct-graph-xu.png}
+        \caption{}
+        \label{fig:direct-graph-xu}
+    \end{subfigure}
+    \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.24\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/direct-graph-my.png}
+        \caption{}
+        \label{fig:direct-graph-my}
+    \end{subfigure}
     \\
-    \begin{subfigure}[b]{\textwidth}
+    \begin{subfigure}[b]{0.8\textwidth}
         \includegraphics[width=\textwidth]{../attachments/battery_simple.png}
@@
     \end{subfigure}
-    \caption{(a)Diagram of this method, which contains four main steps.
-    Step 1: The RBS structure is converted to a topologic model.
-    Step 2: Constraints and objective function are obtained based on the previous topologic model.
-    Step 3: The shortest path of each battery in the RBS is obtained by Dijkstra algorithm.
-    Step 4: The MAC is achieved by greedily selecting the shortest paths to open/close switches.
-    (b) The equivalent circuit of a battery in this method, with $u_{b,i}$ and $r_{b,i}$ representing the voltage and internal resistance of the battery $i$ respectively.
-    The capacitor in Thevenin model is ignored.
+    \caption{ 
+        Directed graph models used in (a) He's work \cite{heExploringAdaptiveReconfiguration2013}, (b) our previous work , and (c) this paper.
+        (d) The equivalent circuit of a battery in this method.
     }
@@
 
-\subsection{Topologic Model}
+He et al.
+\cite{heExploringAdaptiveReconfiguration2013} once proposed an abstracted directed graph model for RBS, where the nodes represented the batteries, the edges represented the configuration flexibility, and the weight of each vertex corresponded to the battery voltage ( Fig.\ref{fig:direct-graph-he}).
+The model effectively captured all potential system configurations and offered a direct metric for configuration flexibility, but it did not specify the physical implementation of the connectivity between batteries, meaning one graph might have had multiple RBS structures.
+We previously proposed a novel directed graph model that, in contrast to He's model, used nodes to represent the connections between batteries and switches, and directed edges to represent batteries and switches (Fig.\ref{fig:direct-graph-xu}), allowing for a one-to-one correspondence between the RBS structure and the directed graph model.
+This model was able to accurately and comprehensively represent the RBS topological structure but could not be used for quantitative MAC calculations due to the lack of consideration for battery and switch performance parameters.
+To address this, an improved directed graph model is used here based on our original model, adding electromotive force and resistance attributes on the edges based to equivalent circuits (Fig.\ref{fig:direct-graph-my}).
+The model also considers the external load as an equivalent resistance and integrate it into the analysis, making it a complete circuit model for later circuit analysis.
+The following will provide a detailed explanation of the method for equating the components in RBS and constructing the directed graph model.
 
-As demonstrated in Fig. \ref{fig:arch}, a typical RBS is made up of a number of battery cells and switches in a dynamically adjustable connection.
-To establish a processable circuit, these batteries and switches are transformed into ideal elements under reasonable assumptions.
-The resulting circuit structure is then described in matrix form, and the related equations are provided.
+In order to use circuit analysis methods to solve the MAC of the RBS, the components in the RBS are equated to ideal circuit elements.
+As shown in Fig.\ref{fig:battery_simple}, the battery in the RBS can be represented as a black-box circuit consisting of two resistors (i.e., $r_1$ and $r_2$) and a capacitor (i.e., $C$), known as the Thevenin model\cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
+With an emphasis on the stable output of the RBS, the capacitor in the Thevenin model can be considered as an open circuit without affecting the steady-state current.
+Therefore, the battery $i$ in the RBS can be simplified as the series connection between a constant voltage source $u_{i}$ and a resistor $r_{i}$.
+Furthermore, the state of switch $j$ in the RBS is represented by a binary variable $x_j$, where 0 is for ON and 1 is for OFF, respectively.
+When the switch is closed, it can be regarded as a resistor with a very small resistance value $r_{j}$.
+Lastly, the external load is considered as a resistor with a value of $R_o$.
 
-The normal equivalent circuit for a battery consists of a voltage source in series with a resistor, and a capacitor in parallel with another resistor to simulate the polarization in batteries, kwon as Thevenin model\cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
-To simplify the model, the transient characteristics of the circuit are not considered, so the capacitor mentioned above is ignored.
-In this way, the battery $i$ in the RBS is modeled by the series connection in between a constant voltage source $u_{b,i}$ and a resistor $r_{b,i}$,  as shown in Fig. \ref{fig:battery_simple}
-And a binary variable $x_j$ is used to represent the state of switch $j$, where 0 for ON and 1 for OFF, respectively.
-To simplify the calculation, a closed switch is considered as a resistor with a very small resistance value $r_s$.
-
-For a given RBS structure, the topologic model for the RBS is constructed as a directed graph $G(V,E)$ in such a way that:
+For a given RBS structure, the directed graph model for the RBS is constructed as a directed graph $G(V,E)$ in such a way that:
 \begin{enumerate}
-    \item Nodes: node $v_1$ and $v_N$ represent the anode and cathode of the RBS respectively, and the other nodes $v_2,\cdots , v_{N-1}$ represent the points connecting batteries and/or switches, where $N$ is the total number of nodes.
-    \item Edges: the directed edges represent batteries, switches and the external electrical appliance in the output circuit based on whether the current direction is constrainted or not. 
-        When the battery is in operation, the internal current direction must be from the negative electrode to the positive electrode, so it is represented by a directed edge from the negative to the positive ; this edge has attributes $(u_b, r_b)$, where $u_b$ and $r_b$ represent battery $b$'s electromotive force and internal resistance.
-        Switches have no constraints on the current direction, so they are represented by a pair of directed edges with opposite directions; these edges both have attribute $(0, r_s)$, where $r_s$ represents the resistance of switch as mentioned above.
-        To fully solve for the current and voltage, an external electrical appliance equivalent as a resistor $R_0$ is connected to the anode and cathode of the RBS and represented by a directed edge from the anode $v_N$  to the cathode $v_1$ of the RBS.
-        Similarly, this edge has attribute $(0, R_0)$.
-        If a given RBS structure has $N_b$ batteries and $N_s$ switches in total, then the number of edges is $N_b+2N_s+1$, where 1 refers to the external electrical appliance.
+    \item Nodes:
+        The nodes in the directed graph correspond to the connection points of components in the actual RBS. 
+        Assuming there are a total of $N$ nodes in the RBS, for the sake of convenience, the anode of the RBS is denoted as $v_1$ and the cathode as $v_N$.
+    \item Edges:
+        The edges in the directed graph correspond to the batteries, switches, and external electrical loads in the actual RBS.
+        Therefore, there are three types of directed edges. 
+        For a battery $B_i$, its directed edge $e_i$ is drawn from the cathode to the anode, as the battery only allows current to flow in one direction when in operation.
+        For a switch $S_j$, since it is allowed to work under bi-directional currents, it is represented by a pair of directed edges with two-way directions. 
+        Regarding the external electronic load, as it is connected to the anode and cathode of the RBS, a directed edge from $v_N$ to $v_1$ is used to represent it. 
+        In conclusion, for a given RBS structure with $N_b$ batteries and $N_s$ switches, the total number of directed edges is $N_b+2N_s+1$, where 1 refers to the external electrical load.
+    \item Edges' attributes:
+        Each edge is assigned two attributes, voltage difference and resistance, based on the equivalent method mentioned above.
+        The values for the battery $B_i$, switch $S_j$, and external loads correspond to $(u_i, r_i)$, $(0, r_j)$, and $(0, R_o)$, respectively.
 \end{enumerate}
@@
 
-The constraints and objective function are obtained by analyzing the currents of batteries and external electrical appliance, as following.
-Based on the above directed graph which has $N$ nodes and $N_b+2N_s+1$ directed edges, its incidence matrix $\bm{A}$ is defined as
+Based on the definition of MAC, determining the MAC of RBS involves maximizing the RBS output current while ensuring that the currents of all batteries do not exceed the batteries' maximum allowable current.
+In this subsection, the constraints and objective function to solve the RBS's MAC will be established through circuit analysis, based on the previously constructed directed graph model.
+
+First, the topology in the directed graph model is represented in matrix form $\bm{A}$, known as the incidence matrix , to facilitate circuit analysis.
+The specific definition of the incidence matrix is shown in Eq.\ref{eq:A}.
 \begin{align}\label{eq:A}
-    a_{ij}=
+    a_{kl}=
     \begin{cases}
-        1,  & \text{edge  $j$ leaves vertex $i$},\\
-        -1, & \text{edge $j$ enters vertex $i$},\\
+        1,  & \text{edge $l$ leaves node $k$},\\
+        -1, & \text{edge $l$ enters node $k$},\\
         0,  & \text{otherwise}.
@@
 \end{align}
-Since each column of $\bm{A}$ sums to zero, the last line are deleted.
-Furthermore, because of a couple of opposite directed edges for each switch, the $N_s$ columns corresponding to the switches are also deleted.
-Finally, the reduced incidence matrix $\bm{A}_{(N-1)\times(N_b+N_s+1)}$ are used in the following calculation.
-By divided as batteries, switches and external electrical appliance, $A$ is rewritten as follows
-\begin{equation}
+For a directed graph consisting of $N$ nodes and $N_b+2N_s+1$ directed edges, its incidence matrix $\bm{A}$ is an $N\times(N_b+2N_s+1)$ matrix. 
+In this matrix, the rows and columns represent the nodes and edges of the directed graph, respectively.
+By distinguishing the components in the RBS corresponding to each column , $\bm{A}$ can be rewritten as:
+\begin{equation}\label{eq:A_bso}
     \bm{A} =
@@
         \bm{A}_b & \bm{A}_s & \bm{A}_o
+    \end{bmatrix},
+\end{equation}
+where $\bm{A}_b$, $\bm{A}_s$ and $\bm{A}_o$ are the sub-matrices corresponding to the batteries, switches and external electrical load, respectively.
+To alleviate computational complexity, matrix $\bm{A}$ undergoes dimensionality reduction.
+Since each directed edge has one node to leave and one to enter, the sum of the values in every column of $\bm{A}$ is zero.
+Therefore removing any single one row will not result in a loss of information. 
+Without loss of generality, the last row is removed here.
+On the other hand, since each switch in the RBS is represented by a pair of directed edges with two-way directions, the two columns corresponding to the switch are mutually opposite.
+Thus, for the sub-matrix $\bm{A}_s$, only one column is retained for each pair of columns representing the same switch.
+As a result, $\bm{A}$ can be reduced to a $(N-1)\times(N_b+N_s+1)$ matrix, denoted as $\bm{\tilde{A}}$, for further calculation of current and voltage.
+Similar to Eq.\ref{eq:A_bso}, $\bm{\tilde{A}}$ can be rewritten as:
+\begin{equation}\label{eq:A_bso_tilde}
+    \bm{\tilde{A}} =
+    \begin{bmatrix}
+        \bm{\tilde{A}}_b & \bm{\tilde{A}}_s & \bm{\tilde{A}}_o
     \end{bmatrix}.
@@
 
-$N_b+N_s+1$ edges' currents $\bm{I}_{(N_b+N_s+1)\times 1}$ and voltages $\bm{U}_{(N_b+N_s+1)\times 1}$, and $N-1$ nodes' voltages $\bm{U}_{n, (N-1)\times 1}$ have following relationships from Kirchhoffs law
+After obtaining the incidence matrix, the currents of all batteries and output in RBS are determined by solving the circuit equations.
+According to Kirchhoffs law, we have
 \begin{align}\label{eq:Kirchhoffs_law}
     \begin{cases}
-        \bm{A} \bm{I} = \bm{0}, \\
-        \bm{U}        = \bm{A}^\T \bm{U}_n.
+        \bm{\tilde{A}} \bm{I} = \bm{0}, \\
+        \bm{U}        = \bm{\tilde{A}}^\T \bm{U}_n,
     \end{cases}
 \end{align}
+where $\bm{I}$ and $\bm{U}$ indicate the current and voltage difference arrays of the $N_b+N_s+1$ edges, respectively;
+$\bm{U}_n$ is the voltage array of the $N-1$ nodes.
 These directed edges are treated as generalized branches and expressed in matrix form as follows
@@
     =\begin{bmatrix}
-        \bm{I} & & \\
+        \bm{X}_b & & \\
         & \bm{X}_s &\\
-        & &\bm{I}
+        & & 1
     \end{bmatrix}.
 \end{equation}
+Where the elements $x_i$ of the matrix $\bm{X}_b$ represent whether the battery $i$ has been removed from the circuit, with $x_i=1$ indicating removal and $x_i=0$ indicating that it is still available to supply power.
+When all batteries are health and capable of providing current to the external load, $\bm{X}_b$ is an identity matrix. 
+The elements $x_j$ of the matrix $\bm{X}_s$ represent whether the switch $j$ is closed, with $x_j=1$ indicating closure and $x_j=0$ indicating disconnection, which is consistent with the previous subsection.
 
-In addition to the equivalent circuit assumptions, we also assume that all batteries have the same internal resistance value $r_b$ and supply the same electric potential $u_s$ to simplify the model.
-Then the output current $I_o$ and each battery's current $\bm{I}_b$ can be given by solving the simultaneous Eq. \ref{eq:Kirchhoffs_law} and \ref{eq:generalized_branches} eventually.
-Let
+Theoretically, the output current $I_o$ and the currents of each battery $\bm{I}_b$ in the RBS  can be determined by solving Eqs.\ref{eq:Kirchhoffs_law}, \ref{eq:generalized_branches}, and \ref{eq:X} under any given state $\bm{X}$.
+In order to obtain specific constraint conditions and objective functions, it is further assumed that all batteries have the same electromotive force and internal resistance, denoted as $u_b$ and $r_b$, respectively.
+This allows for the derivation of explicit expressions for $I_o$ and $\bm{I}_b$.
+After derivation and simplification, the output current $I_o$ and the currents of each battery $\bm{I}_b$ are ultimately represented as Eqs.\ref{eq:I_o} and \ref{eq:I_b}, respectively.
+\begin{equation}\label{eq:I_o}
+    I_o = \frac{1}{R_o r_b} \bm{\tilde{A}}_o^\T \bm{Y}_n^{-1}(\bm{X}) \bm{\tilde{A}}_b \bm{U}_b,
+\end{equation}
+\begin{equation}\label{eq:I_b}
+    \bm{I}_b = \frac{1}{r_b^2}[\bm{\tilde{A}}_b^\T \bm{Y}_n^{-1}(\bm{X}) \bm{\tilde{A}}_b\bm{U}_b -r_b \bm{U}_b],
+\end{equation}
+where $\bm{U}_b$ is a $N_b\times 1$ array with all elements equaling to $u_b$;
+$\bm{Y}_n$ is the equivalent admittance matrix of the circuit, defined as
 \begin{equation}\label{eq:Yn}
-    \bm{Y}_n (\bm{X}_s) = \frac{1}{R_o} \bm{A}_o\bm{A}_o^\T + \frac{1}{r_b} \bm{A}_b\bm{A}_b^\T + \frac{1}{r_s}\bm{A}_s\bm{X}_s\bm{A}_s^\T,
+    \bm{Y}_n (\bm{X}) = \frac{1}{R_o} \bm{\tilde{A}}_o\bm{\tilde{A}}_o^\T + \frac{1}{r_b} \bm{\tilde{A}}_b\bm{X}_b\bm{\tilde{A}}_b^\T + \frac{1}{r_s}\bm{\tilde{A}}_s\bm{X}_s\bm{\tilde{A}}_s^\T.
 \end{equation}
-where $R_o$ is the equivalent resistance of the external circuit.
-Then, if $\bm{Y}_n$ is an invertible matrix,
-\begin{equation}
-    I_o(\bm{X}_s)       = \frac{u_b}{R_o r_b} \bm{A}_o^\T \bm{Y}_n^{-1}(\bm{X}) \bm{A}_b \bm{I}_{N_b\times 1};\label{eq:I_o}
-\end{equation}
-\begin{equation}
-    \bm{I}_b(\bm{X}_s)  = \frac{u_b}{r_b^2}[\bm{A}_b^\T \bm{Y}_n^{-1}(\bm{X}) \bm{A}_b\bm{I}_{N_b \times 1}  -r_b \bm{I}_{N_b \times 1}],\label{eq:I_b}
-\end{equation}
-where $\bm{I}_{N_b\times 1}$ is a column vector with all equal to 1.
 
-In this study, the ratio of $I_o$ and $\max (\bm{I}_b)$ is used to characterize the maximum allowable current for a given RBS architecture, denoted as $\eta$:
+To characterize the current output capacity of the RBS structure under different switching states, an indicator $\eta$ is defined by the ratio of $I_o$ and $\max (\bm{I}_b)$ shown in Eq.\ref{eq:eta}:
 \begin{equation}\label{eq:eta}
@@
 \end{equation}
-The discussion in the next section will show that the $\eta$ reflects the ability of the RBS architecture itself to deliver current, regardliess of the battery cells used by the RBS.
-Finally the problem in RBS can be formulated as
+Finally the problem of solving MAC can be formulated as
 \begin{align}
-    & \max \eta \label{eq:max_eta}\\
+    & \max \eta(\bm{X}_s) \label{eq:max_eta}\\
     \text{s.t.} & \max (\bm{I}_b) \leq I_m, \label{eq:Ib_leq_Im}
 \end{align}
-where $I_m$ is the maximum allowable current of the battery; $\eta$ can be calculated by Eq. \ref{eq:eta}; $I_o$ and $\bm{I}_b$ can be calculated by Eq. \ref{eq:I_o} and \ref{eq:I_b}.
-However, it is computationally difficult to solve Eq. \ref{eq:max_eta} directly because of the presence of matrix $\bm{Y}_n^{-1}$.
-As the number of batteries and switches in the RBS increase, the order of the matrix increases, and the time costed to compute increases sharply.
-A greedy algorithm will be proposed to solve this problem in the next subsection.
+where $I_m$ is the maximum allowable current of the battery.
 
-The integrability of the matrix $\bm{Y}_n$ is explained here.
-Although the above solution procedure requires the matrix $\bm{Y}_n$ to be invertible, it is still possible to encounter integrable $\bm{Y}_n$ in the calculation.
-The physical meaning of this case corresponds to the fact that due to the excessive number of switches in OFF, the solved circuit structure forms circuit branches independent of the main circuit, i.e., the circuit connected to the anode and cathode of the RBS.
-Since these independent branches are not connected to the main circuit, the voltage potentials of these branches cannot be determined and theoretically an infinite number of sets of solutions exist. 
-Benfit from the independence, these solutions have no influence on the results of the main circuit. 
-Since only the currents and voltages of the main circuit are of interest, only one of these solutions needs to be chosen for subsequent calculation.
+However, it is computationally difficult to solve \ref{eq:max_eta} because of the $\bm{Y}_n^{-1}$.
+On one hand, due to the introduction of nonlinear terms by $\bm{Y}_n^{-1}$, many effective methods in linear optimization are not suitable for this problem.
+On the other hand, the rank of $Y_{n}$ is proportional to the number of batteries and switches, which can be very large for a large RBS system, leading to significant computational burden.
+Therefore, intelligent algorithms that rely on evolving by iteration may face efficiency issues when dealing with large RBS system.
+% 如果有时间，可以在案例部分做个对比，看看智能算法和本文算法的效率差距有多大。
+In order to address this issue, the problem should be considered from the perspective of guiding the RBS to reconstruct as many parallel structures as possible.
+Consequently, a greedy algorithm based on the shortest path is proposed. 
+The detailed implementation process is presented in the following two subsections.
 
-\subsection{Greedy Solution}\label{subsec:greedy_solution}
+% Herein provides the solution procedure of …: 1. 2.
+% 考虑这部分怎么写，想不出就直接删了吧。
+% The integrability of the matrix $\bm{Y}_n$ is explained here.
+% Although the above solution procedure requires the matrix $\bm{Y}_n$ to be invertible, it is still possible to encounter integrable $\bm{Y}_n$ in the calculation.
+% The physical meaning of this case corresponds to the fact that due to the excessive number of switches in OFF, the solved circuit structure forms circuit branches independent of the main circuit, i.e., the circuit connected to the anode and cathode of the RBS.
+% Since these independent branches are not connected to the main circuit, the voltage potentials of these branches cannot be determined and theoretically an infinite number of sets of solutions exist.
+% Benfit from the independence, these solutions have no influence on the results of the main circuit. 
+% Since only the currents and voltages of the main circuit are of interest, only one of these solutions needs to be chosen for subsequent calculation.
 
-In this subsection, a greedy algorithm is proposed based on shortest paths ($SP$s), which is given here firstly.
-When the battery $i$ is connected to the anode $v_1$ and the cathode $v_N$ of the RBS by the path $p$ in the graph model, the distance $\omega$ of $p$ is defined by the following equation:
+\subsection{Shortest Path}
+
+The path $p$ used in this method is defined as the complete route that passes through one battery (or a consecutive series of batteries) and closed switches, connecting the anode $v_1$ to the cathode $v_N$ of the RBS.
+By applying a penalty to the series-connected batteries on the path, where additional batteries imply a longer distance, the algorithm encourages the RBS to form parallel structures as much as possible.
+Meanwhile, to reduce the number of switches controlled during the reconstruction process, a penalty is also applied to the total number of switches on the path, while ensuring the minimum number of batteries.
+Therefore, the distance $\omega$ of the path $p$ is defined by the following equation: 
 \begin{equation}\label{eq:weight}
@@
 \end{equation}
-where $N_s$ is the total number of switches in the system; $n_b(p)$ and $n_s(p)$ are number of batteries and switches in the path $p$ respectively.
-$SP_i$ is defined as the path with the minimum $\omega$ for battery $i$.
+where $N_s$ is the total number of switches in the system; 
+$n_b(p)$ and $n_s(p)$ are number of batteries and switches in the path $p$ respectively. 
+Moreover, the shortest path $SP_i$ is defined as the path with the minimum $\omega$ for battery $i$, as shown in the following equation:
 \begin{equation}\label{eq:def_sp}
@@
 \end{equation}
-where $P_i$ is the set of all paths from $v_1$ to $v_N$ and passed through the directed edge $i$ in the direction of it.
-Specifically, the Dijkstra algorithm can be used to implement the $SP_i$.
-According to the definition, $SP_i$ gives the simplest strategy by which the control of battery $i$ is achieved with a minimum of switches while minimizing the influence of other batteries.
-From the perspective of series/parallel, the more batteries are connected into circuit via their $SP$s, the more batteries are connected in parallel.
-Since batteries can provide more total output current when connected in parallel than in series, the algorithm greedily selects as many cells as possible to be connected into to the overall circuit via their $SP$s to obtain the MAC.
-The dichotomy method is also performed to faster find the right number of $SP$s.
+where $P_i$ is the set of all paths from $v_1$ to $v_N$ which pass through the directed edge $i$.
 
-After finding the potential SPs combinations about the MAC, the state variable $\bm{X}_s$ of the switches can be determined, and the optimization problem \ref{eq:max_eta} can be solved using Eq.
-\ref{eq:eta}, \ref{eq:I_o} and \ref{eq:I_b}.
-The overall flowchart is shown in Fig. \ref{fig:flowchart}, and the corresponding pseudo-code of the algorithm is shown in Algorithm \ref{alg:eta_RBS}.
+The $SP_i$ can be solved by the Dijkstra algorithm.
+The Dijkstra algorithm is a graph search method that finds the shortest path between two given nodes in a weighted graph, efficiently solving the single-source shortest path problem.
+Assuming that the cathode and anode of battery $i$ are denoted as $v_i^-$ and $v_i^+$ respectively, the path $p$ of battery $i$  can be divided into three segments : $v_1 \rightarrow v_i^-$, $v_i^+ \rightarrow v_N$, and $v_i^- \rightarrow v_i^+$.
+The $v_i^- \rightarrow v_i^+$ is the directed edge corresponding to battery $i$. 
+With the Dijkstra algorithm, shortest paths for the $v_1 \rightarrow v_i^-$ and $v_i^+ \rightarrow v_N$ can be calculated under the weights given in Eq.\ref{eq:weight}, denoted as $SP(v_i^- \rightarrow v_i^+)$ and $SP(v_i^+ \rightarrow v_N)$, respectively.
+Finally, the $SP_i$ for battery $i$ is formed by the complete path with $SP(v_1 \rightarrow v_i^-)$, $v_i^- \rightarrow v_i^+$, and $SP(v_i^+ \rightarrow v_N)$.
 
-\tikzset{
-  meta box/.style={
-    draw,
-    black,
-    very thick,
-    text centered,
-  },
-  punkt/.style={
-    meta box,
-    rectangle,
-    rounded corners,
-    inner sep=.25em,
-    minimum height=2em,
-    minimum width=4em,
-    align=center,
-    text width=10em
-  },
-  round/.style={
-    meta box,
-    circle,
-    minimum size=0,
-    inner sep=0pt, 
-    outer sep=0pt
-  },
-  every fit/.style={
-    draw,
-    thick,
-    dashed,
-    gray,
-    inner xsep=.5em,
-    inner ysep=.75em
-  }
-}
+\subsection{Greedy Algorithm}\label{subsec:greedy_solution}
+
+From the perspective of series/parallel connections, integrating more batteries into the circuit through their shortest paths ($SP$s) results in a larger number of batteries connected in parallel, thereby increasing the total output current of the RBS.
+However, conflicts may arise between the $SP$s of different batteries. 
+For instance, the $SP$s of two batteries might form a short-circuited RBS structure, which is not allowed. 
+To address this issue, a greedy algorithm is employed to incorporate as many $SP$s as possible while satisfying the reconstruction requirements.
+
+The algorithm, as illustrated in Fig.\ref{fig:flowchart}, can be summarized as follows, with the corresponding pseudo-code presented in Algorithm \ref{alg:greedy}.
+First, the shortest paths ($SP$s) are obtained using Eqs.\ref{eq:weight} and \ref{eq:def_sp} in conjunction with Dijkstra Search. 
+Next, the matrix $\bm{A}$ is calculated using Eq.\ref{eq:A}, and the initial $N_{set}$ is set to $N_b$. 
+The algorithm iteratively checks different combinations of $c_b$ batteries from $N_b$ and updates $N_{set}$ using a dichotomy method until convergence is reached. 
+For each combination, the algorithm constructs an effective solution if possible, and calculates the currents $I_o$ and $\bm{I}_b$ using Eqs.\ref{eq:I_o} and \ref{eq:I_b}. 
+If the maximum current $\bm{I}_b$ is less than or equal to $I_m$, the $\eta$ is calculated using Eq.\ref{eq:eta}, and the maximum $\eta$ is updated accordingly. 
+Finally, the algorithm outputs the maximum $\eta$ once $N_{set}$ converges.
+
+% \tikzset{
+%   meta box/.style={draw, black, very thick, text centered, },
+%   punkt/.style={meta box, rectangle, rounded corners, inner sep=.25em, minimum height=2em, minimum width=4em, align=center, text width=10em },
+%   round/.style={meta box, circle, minimum size=0, inner sep=0pt, outer sep=0pt },
+%   every fit/.style={draw, thick, dashed, gray, inner xsep=.5em, inner ysep=.75em }
+% }
 \begin{figure}
@@
 %     \node[punkt]     (input) {Input: RBS structure};
-%     \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Eqs. \ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
-%     \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Eq. \ref{eq:A}};
+%     \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Eqs.\ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
+%     \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Eq.\ref{eq:A}};
 %     \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{set}=N_b$ };
@@
 %     \node[punkt, right=1.3of is_Yn_invertible] (construct) {construct an effective solution};
-%     \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Eqs. \ref{eq:I_o} and \ref{eq:I_b}};
+%     \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Eqs.\ref{eq:I_o} and \ref{eq:I_b}};
 %     \node[draw, diamond, aspect=2, below=0.3of get_I] (is_leq_Im) {is $\max \bm{I}_b \leq I_m$?};
@@
     \centering
-    \includegraphics[width=\textwidth]{../attachments/IMG_20230411_225909.jpg}
-\caption{The computational flowchart of the proposed method in this paper.}\label{fig:flowchart}
+    \begin{subfigure}[b]{0.8\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/main.png} % 替换用
+        \caption{}
+        \label{fig:main}
+    \end{subfigure}
+\caption{The computational flowchart of the MAC for a given RBS.}\label{fig:flowchart}
 \end{figure}
+
 \section{Case Study}
 
-This section presents a case study to demonstrate the effectiveness of the proposed method.
-A more intricate structure, which integrates the two previously proposed structures, is proposed.
-The effectiveness of the aforementioned algorithm is substantiated on this structure to confirm its applicability in practical scenarios.
-Moreover, the algorithm's versatility is also established through its application in complex cases such as the presence of isolated battery cell.
-
-\subsection{Determination of a new RBS structure}
+\subsection{Structures}
 
@@
     \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/arch-ef.png}
+    \begin{subfigure}[b]{0.2\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/stru-L-origin.png}
         \caption{}
-        \label{fig:arch-ef}
+        \label{fig:study-stru-Lawson}
     \end{subfigure}
-    \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/ef-topo.png}
+    \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.4\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/stru-V-origin.png}
         \caption{}
-        \label{fig:ef-topo}
+        \label{fig:study-stru-Visairo}
     \end{subfigure}
-    \caption{
-        (a) The new RBS structure proposed in this paper, which is obtained by replacing the batteries in Fig.
-\ref{fig:arch-e} with the structure in Fig.
-\ref{fig:arch-f}, as shown in the dashed boxes in the figure.
-        (b) The corresponding topologic model of the new RBS structure, which is a directed graph.
-        The nodes represent the connection points of the battery cells and/or the switches.
-        The green,gray and blue directed edges represent the battery cells, the switches and the external electrical appliance, respectively.
-    }
+    \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.31\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/stru-my-origin.png}
+        \caption{}
+        \label{fig:study-stru-my}
+    \end{subfigure}
+    \caption{The 4-battery RBS structures proposed by (a)Lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b)Visairo\cite{visairoReconfigurableBatteryPack2008} and (c)this paper.}
 \end{figure}
 
-The RBS structure proposed by Lawson et al\cite{lawsonSoftwareConfigurableBattery2012}, shown in Fig.
-\ref{fig:arch-e}, easily enables the isolation of arbitrary cells or the addition of redundant cells to the system, but these cells are limited to being connected in series only and the switch between cells connection modes is not flexible.
-In contrast, the structure proposed by Visairo et al\cite{visairoReconfigurableBatteryPack2008}, shown in Fig.
-\ref{fig:arch-f}, allows the flexibility to switch the cells between series, parallel and mixed series-parallel modes, thus allowing dynamic voltage adjustment according to the external load and improving energy conversion efficiency, but is not as simple as the structure by Lawson et al in terms of isolating cells or adding redundancy.
-In order to combine the advantages of both structures, a new structure is obtained by replacing the batteries in Fig.
-\ref{fig:arch-e} with the structure in Fig.
-\ref{fig:arch-f}, as shown in Fig.
-\ref{fig:arch-ef}.
-This more complex structure has the structure of Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} as the main frame and the structure of Visairo et al.\cite{visairoReconfigurableBatteryPack2008} as the substructure.
-In this way, the circuit topology of the substructure (i.e.
-the structure in the box in Fig.
-\ref{fig:arch-ef}) can be changed to enable dynamic and flexible voltage adjustment according to the load, while at the same time taking advantage of the ease of battery isolation and increased redundancy of the main frame.
-The next subsections will use this structure with 4 battery cells and 19 switches as an example to demonstrate the effectiveness of the proposed algorithm.
+Currently, two types of RBS structures have been proposed by Visairo et al.
+\cite{visairoReconfigurableBatteryPack2008} and Lawson et al.
+\cite{lawsonSoftwareConfigurableBattery2012}, both of which have been applied in practice.
+The primary goal of Visairo's structure (Fig.\ref{fig:study-stru-Visairo}) was to achieve dynamic adjustment of RBS output; however, the isolation of unhealthy batteries was not sufficiently addressed.
+When batteries need to be isolated in the RBS of Visairo's structure, the methods for isolating them and the subsequent changes in RBS output warrant further investigation.
+Lawson et al. conducted research on battery isolation in RBS and specifically designed the structure shown in Fig.\ref{fig:study-stru-Lawson}. 
+This structure has the advantage of easily isolating batteries, but it cannot dynamically adjust the output current of RBS. 
+Based on the structures of Visairo and Lawson, this paper presents a new structure, as shown in Fig.\ref{fig:study-stru-my}, which combines the advantages of both.
+By integrating the Visairo RBS structure into the Lawson RBS structure, the new structure not only allows the flexibility to switch the batteries between series, parallel, and mixed series-parallel modes, but also easily enables the isolation of highly degraded batteries from the RBS.
+And their variations in output current under battery isolation conditions will be studied.
+This RBS structure will be used to validate the effectiveness of the proposed method for calculating the MAC, and be compared with the Lawson's and Visairo's structure to illustrate its advantage on battery isolation.
 
-\subsection{Calculation details and result}
+\subsection{Result}
 
-The graph in Fig. \ref{fig:ef-topo} represents the topologic model based on the new RBS structure mentioned in the last subsection (Fig. \ref{fig:arch-ef}).
-The model is presented in the form of a directed graph, capturing the connection relationship between the battery and switch in the circuit.
-Battery cell 1, 2, 3, and 4 are represented by green directed edges in the graph, while nineteen switches are represented by gray directed edges with opposite directions.
-The external electrical appliance is considered as a directed edge from the cathode of the RBS ( node $18$ in the graph) to the anode ( node $1$ in the graph), represented as the blue directed edge in the graph.
-Totally, there are 19 nodes and 43 edges in the graph.
-
-Based on the node-edge relationship given in Fig. \ref{fig:ef-topo}, the incidence matrix $\bm{A}$ can be obtained according to Eq. \ref{eq:A}:
-\begin{equation}
-    \bm{A} = 
-    \begin{bmatrix}
-        \bm{A}_b & \bm{A}_s & \bm{A}_o
-    \end{bmatrix},
-\end{equation}
-
-\begin{equation}
-    \bm{A}_b^\T = 
-    \begin{bmatrix}
-        0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 \\
-    \end{bmatrix},
-\end{equation}
-
-\begin{equation}
-    \bm{A}_s^\T = 
-    \begin{bmatrix}
-        1 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 1 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 1 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 1 & 0 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 &-1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 &-1 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 &-1 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 &-1 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 &-1 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 &-1 \\
-        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 \\
-    \end{bmatrix},
-\end{equation}
-
-\begin{equation}
-    \bm{A}_o^\T = 
-    \begin{bmatrix}
-       -1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-    \end{bmatrix}.
-\end{equation}
-The state matrix $\bm{X}$ is determined by the switches' state, that is, the specific configuration of the RBS.
-For example, when switch $S_1$, $S_3$, $S_5$, $S_6$, $S_8$, $S_9$, $S_{11}$, $S_{13}$, $S_{14}$, $S_{16}$, $S_{17}$ and $S_{19}$ are ON, and the rest of the switches are OFF, the state matrix $\bm{X}$ is given by
-\begin{equation}
-    \bm{X} = diag(
-    \underbrace{1,0,1,0,1,1,0,1,1,0,1,0,1,1,0,1,1,0,1}_{\text{switches}},
-    \underbrace{1,1,1,1}_{\text{batteries}},
-    1
-    ).
-\end{equation}
-By substituting the above specific values of $\bm{A}$ and $\bm{X}$ above into Eqs.
-\ref{eq:Yn}, \ref{eq:I_o}, \ref{eq:I_b} and \ref{eq:eta} in turn, the $\eta$ at the current situation, i.e.
-battery cell $B_1$ and $B_2$, $B_3$ and $B_4$ are connected in parallel with each other, and then connected in series to supply the external electrical appliance, can be obtained after the sequential calculation.
-The results are shown in Tab. \ref{tab:given_x}.
-
-\begin{table}[htbp]
-  \centering
-    \caption{Calculating result of the output current $I_o$, battery current $\bm{I}_b$ and ratio $\eta$ for a specificed switches state $\bm{X}_m$ in the structure combining Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} and Visairo et al.\cite{visairoReconfigurableBatteryPack2008} with 4 battery cells and 19 switches.}
-    \begin{tabular}{cc}
-    \toprule
-        Structure & 4 battery cells and 19 switches  \\
-        % Structure & combining Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} and Visairo et al.\cite{visairoReconfigurableBatteryPack2008} with 4 battery cells and 19 switches  \\
-    \midrule
-    Switch ON & 1,3,5,6,8,9,11,13,14,16,17,19 \\
-        $\bm{X}_s$ & $\diag(1,0,1,0,1,1,0,1,1,0,1,0,1,1,0,1,1,0,1)$ \\
-    \midrule
-        $I_o$ & $2u_b/(R_o+r_b)$ \\
-        $\bm{I}_b$ & $[u_b/(R_o+r_b),u_b/(R_o+r_b),u_b/(R_o+r_b),u_b/(R_o+r_b)]$ \\
-        $\eta$     & 2 \\
-    \bottomrule
-    \end{tabular}%
-  \label{tab:given_x}%
-\end{table}%
-
-The above gives the procedure for calculating the current and $\eta$ when the specified switches are given ON or OFF.
-However, in order to calculate the MAC of the structure, i.e.
-the maximum $\eta$, it is necessary to find the corresponding switch state using a greedy strategy, as mentioned in subsection \ref{subsec:greedy_solution}.
-
-Firstly, the weight $N_s$ in Eq. \ref{eq:weight} represents the total number of switches in the system, which is 19. 
-By using this formula and the Dijkstra search strategy, the $SP$s of each cell can be obtained, as shown in Figs. \ref{fig:sp1} to \ref{fig:sp4}.
-According to the greedy strategy, as many $SP$s as possible should be selected to get the MAC. 
-In the first iteration, the $SP$s of all four batteries are selected, and the switch states on the paths are set to ON. 
-The corresponding $\bm{X}_s$ are calculated using the previous method, and the currents of the batteries are obtained as $u_b/r_b$, $u_b/r_b$, $u_b/r_b$, and $u_b/r_b$. 
-Since all batteries are short-circuited and the current of the battery exceeds the maximum allowed current $I_m$, this solution does not satisfy constraint \ref{eq:Ib_leq_Im} and is discarded. 
-The second iteration is carried out using the dichotomy method, and two batteries are selected for the combination. 
-Assuming that the selected combinations are $(B1, B2)$, the $\bm{X}_s$ obtained according to the $SP$s are substituted into the previous calculation, and the current of each battery is $u_b/r_b$, $u_b/r_b$, $0$, and $0$.
-This solution meets the condition. 
-After that, the case of selecting three cells is considered. 
-By similar calculations, it is determined that all solutions do not satisfy the constraint when three cells are selected. 
-Finally, the MAC of this structure is $\eta=2$, and the related result is shown in Fig. \ref{fig:ef-mac} and Tab. \ref{tab:find_mac}.
+As shown in Fig.\ref{fig:study-stru-my}, the new RBS structure consists of 4 batteries and 19 switches. 
+The corresponding directed graph is depicted in Fig.\ref{fig:study-dirgraph-my}, which is composed of of a total of 18 nodes and 43 edges. 
+Batteries $B_1$, $B_2$, $B_3$, and $B_4$ are denoted by green directed edges in the graph, while the 19 switches are represented by gray directed edges with bi-directional arrows. 
+The external electrical load is treated as a directed edge from the cathode of the RBS (i.e., node 18) to the anode (i.e., node 1), as indicated by the blue directed edge in the graph.
+Utilizing Eq.\ref{eq:weight} and the Dijkstra algorithm, the $SP$s of the four batteries in the RBS structure of Fig.\ref{fig:study-stru-my} are highlighted by red in Figs.\ref{fig:sp1}-\ref{fig:sp4}.
+Finally, the MAC calculation results of the structure in Fig.\ref{fig:study-stru-my} are shown as Tab.\ref{tab:study-results-my} and Fig.\ref{fig:study-results-my}, obtained by the greedy algorithm \ref{alg:greedy}.
+Tab.\ref{tab:study-results-my} contains the switches states, the output current $I_o$, battery current $\bm{I}_b$ and ratio $\eta$ of the RBS structure with all batteries in good health when the RBS output reaches the MAC.
+Fig.\ref{fig:study-results-my} presents the corresponding circuit, with the red highlight indicating that current is flowing through the respective branches.
 
@@
     \centering
-    \begin{subfigure}[b]{0.45\textwidth}
+    \begin{subfigure}[b]{0.28\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/ef-topo.png}
+        \caption{}
+        \label{fig:study-dirgraph-my}
+    \end{subfigure}
+    \hspace{0.05\textwidth}
+    \begin{subfigure}[b]{0.28\textwidth}
         \includegraphics[width=\textwidth]{../attachments/ef-sp1.png}
@@
     \end{subfigure}
+    \hspace{0.05\textwidth}
+    \begin{subfigure}[b]{0.28\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/ef-mac.png}
+        \caption{}
+        \label{fig:study-results-my}
+    \end{subfigure}
     \caption{
-        The $SP$s of battery cell (a)$B_1$ (b)$B_2$ (c)$B_3$ (d)$B_4$ in the new structure's topological model, which is highlighted in red.
+        For the RBS structure in Fig.\ref{fig:study-stru-my}, 
+        (a)its directed graph 
+        and the $SP$s (highlighted in red) of battery (b)$B_1$, (c)$B_2$, (d)$B_3$, (e)$B_4$.
+        (f)The circuit of the RBS with its output reaching the MAC.
         }
+    \label{fig:all-results-my}
 \end{figure}
@@
   \centering
-    \caption{MAC Calculating result of the output current $I_o$, battery current $\bm{I}_b$ and ratio $\eta$ in the structure combining Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} and Visairo et al.\cite{visairoReconfigurableBatteryPack2008} with 4 battery cells and 19 switches.}
+    \caption{MAC Calculating result of the 4-battery RBS structure in Fig.\ref{fig:study-stru-my}.}
     \begin{tabular}{cc}
     \toprule
-        % Structure & combining Lawson et al.\cite{lawsonSoftwareConfigurableBattery2012} and Visairo et al.\cite{visairoReconfigurableBatteryPack2008} with 4 battery cells and 19 switches  \\
-        Structure & 4 battery cells and 19 switches  \\
+        Structure & Fig.\ref{fig:study-stru-my} with 4 batteries and 19 switches  \\
     \midrule
-    Switch ON & 1,3,5,6,8,9,10,12,18,19 \\
-    $\bm{X}_s$ & $\diag(1,0,1,0,1,1,0,1,1,1,0,1,0,0,0,0,0,1,1)$ \\
-    \midrule
+    Switch ON & $S_1$,$S_3$,$S_5$,$S_6$,$S_8$,$S_9$,$S_{10}$,$S_{12}$,$S_{18}$,$S_{19}$ \\
     $I_o$ & $2u_b/(2R_o+r_b)$ \\
@@
     \bottomrule
-    \end{tabular}%
-  \label{tab:find_mac}%
-\end{table}%
+    \end{tabular}
+  \label{tab:study-results-my}
+\end{table}
+
+Similarly, the MAC calculation results of the structures in Figs.\ref{fig:study-stru-Lawson} and \ref{fig:study-stru-Visairo} are shown as Tab.\ref{tab:study-results-Lawson} and Tab.\ref{tab:study-results-Visairo}, respectively.
+
+\begin{table}[htbp]
+  \centering
+    \caption{MAC Calculating result of the 4-battery RBS structure in Fig.\ref{fig:study-stru-Lawson}.}
+    \begin{tabular}{cc}
+    \toprule
+        Structure & Fig.\ref{fig:study-stru-Lawson} with 4 batteries and 15 switches  \\
+    \midrule
+    Switch ON & $S_1$,$S_3$,$S_5$,$S_7$,$S_{10}$,$S_{13}$,$S_{14}$,$S_{15}$ \\
+    $I_o$ & $u_b/(R_o+r_b)$ \\
+    $\bm{I}_b$ & $[u_b/(R_o+r_b),0,0,0]$ \\
+    $\eta$     & 1 \\
+    \bottomrule
+    \end{tabular}
+  \label{tab:study-results-Lawson}
+\end{table}
+
+\begin{table}[htbp]
+  \centering
+    \caption{MAC Calculating result of the 4-battery RBS structure in Fig.\ref{fig:study-stru-Visairo}.}
+    \begin{tabular}{cc}
+    \toprule
+        Structure & Fig.\ref{fig:study-stru-Visairo} with 4 batteries and 13 switches  \\
+    \midrule
+    Switch ON & $S_1$,$S_2$,$S_3$,$S_4$,$S_5$,$S_9$,$S_{10}$,$S_{11}$,$S_{12}$,$S_{13}$ \\
+    $I_o$ & $4u_b/(4R_o+r_b)$ \\
+    $\bm{I}_b$ & $[u_b/(4R_o+r_b),u_b/(4R_o+r_b),u_b/(4R_o+r_b),u_b/(4R_o+r_b)]$ \\
+    $\eta$     & 4 \\
+    \bottomrule
+    \end{tabular}
+  \label{tab:study-results-Visairo}
+\end{table}
+
+\subsection{Discussion}
+
+In this subsection, we firstly discuss the correctness of the results presented in Fig.\ref{fig:all-results-my} and Tab.\ref{tab:study-results-my}. 
+When $B_1$ and $B_2$ or $B_3$ and $B_4$ are connected in parallel, the RBS can output the maximum current, which is $\eta=2$, i.e., twice the current output of a single battery in RBS. 
+Adding more batteries to the main circuit can only form a series structure and will not improve the MAC. 
+Therefore, the switches state given in Tab.\ref{tab:study-results-my} can make the RBS output current reach the maximum.
+
+It is important to note that when solving for MAC, $\eta$ is used as the objective function instead of $I_o$. 
+This choice makes the result of MAC more reasonable. 
+As shown in Tab.\ref{tab:study-results-my}, $I_o$ and $\bm{I}_b$ are functions of $R_o$, $u_b$, and $r_b$. 
+If $I_o$ were used as the objective function, even for the same RBS structure, the MAC result and corresponding switches state could change due to different external electrical appliances.
+It would increase the difficulty and uncertainty in RBS structure design. 
+In contrast, by using $\eta$ as the objective function, which is defined as the ratio of $I_o$ and $\max\bm{I}_b$, the influence of these factors on the results can be eliminated. 
+$\eta$ solely reflects the maximum output current capability of the RBS structure. 
+Assuming that the maximum allowed current of batteries in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by determining the $\eta$ of the structure. 
+Therefore, compared to $I_o$, $\eta$ is more suitable for structure design.
+
+The method proposed in this paper is significant for the design of next-generation RBSs in the following aspects.
+Most of the currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} exhibit simple topological characteristics, and the calculation of MACs is relatively straightforward, even intuitive.
+However, these simple structures do not always fully satisfy the requirements of complex applications, such as dynamically adapting the circuit to variable and random operating conditions, and actively equalizing differences among the batteries in the RBS.
+Moreover, isolating the batteries disrupts the original regularity and symmetry of the topology, which complicates the otherwise simple structure, and the maximum output current of the system becomes more challenging to obtain.
+Owing to the advantages of pervasiveness and automation, the proposed method can be employed to calculate the MAC of arbitrary RBS structures, which helps to address the aforementioned issues and paves the way for more complex and flexible RBS structure design.
+
+To illustrate this point, the MACs of the three RBS structures mentioned above are calculated after the batteries are isolated, as shown in Fig.\ref{fig:isolated_mac}. 
+Specifically, for the structure presented in Fig.\ref{fig:study-stru-my}, the corresponding circuit states of MACs when isolating different numbers of batteries are depicted in Figs.\ref{fig:my-isolated-1}-\ref{fig:my-isolated-3}.
+This structure has two cases of isolating two batteries: 
+one is to isolate two batteries within the same substructure (Fig.\ref{fig:my-isolated-2b}), in which case $\eta=2$; the other is to isolate one battery in each of the two substructures (Fig.\ref{fig:my-isolated-2w}), in which case $\eta=1$.
+From the results, it can be observed that the proposed method provides reasonable outcomes for isolating batteries with any number and position.
+
+Furthermore, the performance of output current for the three RBS when isolating batteries is also illustrated in Fig.\ref{fig:isolated_mac}. 
+For the structure proposed by Lawson et al., the MAC remains the same as that without isolated battery cells, i.e., $\eta=1$, when the number of isolated battery cells increases, until all the cells in the RBS are isolated.
+For Visairo's structure, the MAC decreases as the number of isolated battery cells increases, until $\eta=0$. 
+In contrast, the MAC of the structure proposed in this work is positioned between the two structures. 
+This indicates that the structure proposed in this paper, compared to Lawson's structure, has a larger MAC under the same number of batteries, which means a wider output current regulation range. 
+On the other hand, by simply changing the states of $S_2$, $S_4$, $S_{11}$, and $S_{12}$ in the conversion structure, this structure can address the majority of battery isolation scenarios, whereas Visairo's structure requires specific battery targeting and switch control.
+In summary, the structure proposed in this paper has the advantages of both Lawson's and Visairo's structures.
 
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../attachments/ef-mac.png}
+    \includegraphics[width=0.5\textwidth]{../attachments/isolated_mac.png}
     \caption{
-        The finally calculation result of MAC for the new structure with four battery cells and 19 switches.
-        The red lines represent the branches through which the current flows, and the switches on these branches are ON. 
-        In this situation, the RBS outputs MAC to the outside, which is $\eta=2$.
-    }\label{fig:ef-mac}
+        The variation of MAC with the number of isolated batteries for different RBS structures, including the structure proposed by Lawson et al., Visairo et al.
+, and the structure proposed in this paper.
+    }\label{fig:isolated_mac}
 \end{figure}
-
-\subsection{Discussion}
-
-The correctness of the results shown in Fig. \ref{fig:ef-mac} is obvious. 
-When B1 and B2 or B3 and B4 are connected in parallel, the RBS can output the maximum current, which is $\eta=2$, i.e. twice the current output of a single battery in RBS.
-While adding more batteries to the main circuit can only form a series structure and will not improve the MAC.
-It is worth noting that when solving for MAC, $\eta$ is used as the objective function instead of $I_o$, which makes the result of MAC more reasonable. 
-According to the results shown in Tab.
-\ref{tab:find_mac}, $I_o$ and $\bm{I}_b$ are affected by the equivalent resistance $R_o$ of external electrical appliance, the battery's electromotive force $u_b$, and internal resistance $r_b$.
-This means that if $I_o$ is used as the objective function, even for the same RBS structure, the MAC result and corresponding switch state could be changed due to different external electrical appliances.
-This increases the difficulty and uncertainty in RBS structure design. 
-On the contrary, by using $\eta$ as the objective function, which dividing $I_o$ and $\max\bm{I}_b$, the influence of these factors on the results is eliminated, as shown in Tabs.
-\ref{tab:given_x} and \ref{tab:find_mac}.
-$\eta$ only reflects the maximum output current capability of the RBS structure.
-Assuming that the maximum allowed current of battery cells in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by calculating the $\eta$ of the structure.
-Therefore, compared to $I_o$, $\eta$ is more suitable for structure design. 
-Most of the currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} have simple topological characteristics, and the calculation of MACs are relatively simple, even intuitive.
-However, when complex and flexible structures need to be designed for application scenarios such as equalization or isolation of specific battery cells, the estimation of MAC will become complex and complicated.
-The method proposed in this paper can effectively solve any RBS structure and estimate MAC universally, paving the way for the structure design of more complex and flexible RBSs.
-
-% 对比Tab. 1和 Tab. 2，可以发现，对于这两种开关状态 $\bm{X}_s$，在电阻和电动势相同的情况下，前者的Io更大。
-% 这主要是由于在Tab. 1的情形下，四个电池以两并两串的形式接入主电路，提供了更多的电动势。
-% 相应的，每个电池的电流也更大。
-% 此时，如果仅使用 Io 作为目标函数，则  （） #TODO：讨论怎么说
-
-When the RBS has isolated battery cells, the original topology of the structure is altered. 
-However, the method proposed in this paper can still be used to calculate the MAC of the new structure. 
-The MAC after the isolation operation can be obtained by calculating the new structure following the procedures described in the previous subsection.
-During the calculation process, the isolated battery cell(s) do not participate in the calculation, i.e., their nodes, edges, and $SP$s are not considered. 
-The MACs under various isolated battery cell(s) are calculated on the structures proposed by Lawson et al.
-(Fig.
-\ref{fig:arch-e}), Visairo et al.
-(Fig.
-\ref{fig:arch-f}), and the new structure that integrates the previous two structures (Fig.
-\ref{fig:ef-topo}), as shown in Fig.
-\ref{fig:isolated_mac}.
-For the structure proposed by Lawson et al., the MAC remains the same as that without isolated battery cells, i.e., $\eta=1$, when the number of isolated battery cells increases, until all the cells in the RBS are isolated.
-For the structure proposed by Visairo et al., the MAC decreases as the number of isolated battery cells increases, until $\eta=0$.
-While the new structure has two cases of isolating two cells, one is to isolate two cells within the same substructure, in which case $\eta=2$; the other is to isolate one cell in each of the two substructures, in which case $\eta=1$.
-Overall, the MAC of the new structure is positioned between the structures proposed by Lawson et al. and Visairo et al..
-It can be seen that the MAC of the structure in Fig. \ref{fig:arch-e} is the most stable, and the structure has advantages in isolation and redundancy backup, but its MAC is the smallest. 
-The structure proposed shown by Fig. \ref{fig:arch-f} can output the largest MAC but is susceptible to the number of isolated battery cells. 
-However, the structure proposed by this paper has certain advantages in both aspects, being insensitive to the number of isolated battery cells while simultaneously achieving a larger MAC.
 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{../attachments/isolated_mac.png}
+    \begin{subfigure}[b]{0.31\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/my-isolated-1.png}
+        \caption{}
+        \label{fig:my-isolated-1}
+    \end{subfigure}
+    \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.31\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/my-isolated-2b.png}
+        \caption{}
+        \label{fig:my-isolated-2b}
+    \end{subfigure}
+    \\
+    \begin{subfigure}[b]{0.31\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/my-isolated-2w.png}
+        \caption{}
+        \label{fig:my-isolated-2w}
+    \end{subfigure}
+    \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.31\textwidth}
+        \includegraphics[width=\textwidth]{../attachments/my-isolated-3.png}
+        \caption{}
+        \label{fig:my-isolated-3}
+    \end{subfigure}
     \caption{
-        The variation of MAC with the number of isolated battery cells for different RBS structures, including the structure proposed by Lawson et al., Visairo et al.
-, and the new structure in this paper.
-    }\label{fig:isolated_mac}
+        The circuit states of MACs when isolating (a)one, (b)two(best case), (c)two(worst case) and (d)three batteries for the structure in Fig.\ref{fig:study-stru-my}.
+        }
 \end{figure}
@@
 
-This paper firstly proposes a method to calculation the MAC of RBS according to its architecture. 
-To find the circuit in RBS that enable the MAC, a greedy strategy incorporate with the topologic model is developed to. 
-The effectiveness of proposed method is tested on a more complex RBS structure based on two proposed structure.
-This work presents an effective approach to evaluate the MAC of RBS, which is essential for design and management of the RBS. 
-Future research could focus on developing new performance indicators for evaluating RBS performance using the currents and voltages obtained by this method, as well as modifying the equivalent model of the battery to enable more accurate simulations of RBS, including transient analysis.
+This paper proposes a pervasive and automatical method for computing the MAC of the given RBS.
+The method is  implemented by a greedy algorithm combined with a directed graph model, whose effectiveness is tested on a novel and complex RBS structure.
+The method remains effective for the application scenario of RBS battery isolation and demonstrates that the novel structure has the advantage on flexible output current and convenient battery isolation.
+Future research could focus on developing new indictors to evaluate the performance of the RBS with the currents and voltages obtained by the method, as well as modifying the equivalent model of the battery to allow for more accurate simulations of the RBS, including transient analysis.
 
-% \section{Appendix}
-% \begin{algorithm}
-%     \caption{Get the max available currents of a certain RBS}\label{alg:eta_RBS}
-%     \KwData{Directed graph model $G(V,E)$ of the RBS}
-%     \KwResult{$\max \eta$}
-%     \For{$i \in E_b$}{
-%         $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
-%         $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
-%     }
-%     get $\bm{A}$ by Equation \ref{eq:A}\;
-%     \While{not yet determine $\max \eta$ }
-%     {
-%         $N_{sel} \leftarrow \text{number of selected $SP$s calculated by dichotomy}$\;
-%         $C_b    \leftarrow \text{set of all combinations of $N_{sel} $~batteries from $N_b$}$\;
-%         \For{$c_b \in C_b$}{
-%             $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
-%             $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
-%             get $\bm{Y}_n$ by Equation \ref{eq:Yn}\;
-%             \eIf{$\bm{Y}_n$ is invertible}{
-%             }{construct an effective solution}
-%             get $I_o$ by Equation \ref{eq:I_o}\;
-%             get $\bm{I}_b$ by Equation \ref{eq:I_b}\;
-%             \eIf{$\max(\bm{I}_b)\leq I_m$}{
-%                 $\eta \leftarrow I_o/\max(\bm{I}_b)$\;
-%             }{break}
-%         }
-%     }
-% \end{algorithm}
+\newpage
+
+\section{Appendix}
+
+replace !!!
+
+% % \begin{algorithm}
+% %     \caption{Get the max available currents of a certain RBS}\label{alg:greedy}
+% %     \KwData{Directed graph model $G(V,E)$ of the RBS}
+% %     \KwResult{$\max \eta$}
+% %     \For{$i \in E_b$}{
+% %         $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
+% %         $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
+% %     }
+% %     get $\bm{A}$ by Equation \ref{eq:A}\;
+% %     \While{not yet determine $\max \eta$ }
+% %     {
+% %         $N_{set} \leftarrow \text{number of setected $SP$s calculated by dichotomy}$\;
+% %         $C_b    \leftarrow \text{set of all combinations of $N_{set} $~batteries from $N_b$}$\;
+% %         \For{$c_b \in C_b$}{
+% %             $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
+% %             $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
+% %             get $\bm{Y}_n$ by Equation \ref{eq:Yn}\;
+% %             \eIf{$\bm{Y}_n$ is invertible}{
+% %             }{construct an effective solution}
+% %             get $I_o$ by Equation \ref{eq:I_o}\;
+% %             get $\bm{I}_b$ by Equation \ref{eq:I_b}\;
+% %             \eIf{$\max(\bm{I}_b)\leq I_m$}{
+% %                 $\eta \leftarrow I_o/\max(\bm{I}_b)$\;
+% %             }{break}
+% %         }
+% %     }
+% % \end{algorithm}
+
+\section{Acknowledgement}
+This work was supported by the National Natural Science Foundation of China (NSFC, No.52075028).
 

### 2023-06-28 paper/main.tex
添加了师兄的修改意见（v3.1）并修改（v3.2）

@@
 \usepackage{booktabs}
+\usepackage{footnote}
 \usepackage{bm}
@@
     During the operation of the RBS, the Maximum Allowable Current (MAC) is a critical indicator to guide the system's reconfiguring control, ensuring safety and reliability.
-    In this paper, we propose a calculation method for the MAC of an RBS using a greedy algorithm in conjunction with a directed graph model of the RBS.
+    In this paper, we propose a calculation method for the MAC of arbitrary RBS using a greedy algorithm in conjunction with a directed graph model of the RBS.
     By employing the directed graph model, the greedy algorithm guides the RBS to establish parallel connections among batteries, aiming to maximize the system's output current while ensuring that none of the batteries are overloaded or short-circuited.
     The effectiveness of this method is validated on a novel and complex RBS structure.
-    The results demonstrate the viability of this method and its potential in facilitating next-generation RBS designs and applications, including battery isolation.
+    The results demonstrate the effectiveness of this method and its potential in facilitating next-generation RBS designs and applications, including battery isolation.
 
@@
 
-The central principle of this method is to make the batteries in RBS connected in series as much as possible, thereby maximizing the output current of the RBS.
+The central principle of this method is to make the batteries in RBS connected in parallel as much as possible, thereby maximizing the output current of the RBS.
 To universally and automatically achieve this, the overall process is divided into four steps, as shown in Fig.\ref{fig:main}.
@@
 Subsequently, based on the equivalent circuit, the MAC problem is transformed into specific objective functions and constraints.
-Then, the shortest paths (SPs, where additional batteries and switches on the path are penalized as distance) for the batteries are obtained using the Dijkstra algorithm to guide the batteries in the RBS connect in series.
+Then, the shortest paths (SPs, where additional batteries and switches on the path are penalized as distance) for the batteries are obtained using the Dijkstra algorithm to guide the batteries in the RBS connect in parallel.
 Finally, a greedy algorithm is employed to organize the switches, allowing the batteries to connect via their SPs while satisfying the constraints, resulting in the MAC of the RBS.
@@
 
-To illustrate this point, the MACs of the three RBS structures mentioned above are calculated after the batteries are isolated, as shown in Fig.\ref{fig:isolated_mac}. 
+To illustrate this point, the MACs of the three RBS structures mentioned above are calculated after the batteries are isolated, as shown in Tab.\ref{tab:isolated_mac}. 
 Specifically, for the structure presented in Fig.\ref{fig:study-stru-my}, the corresponding circuit states of MACs when isolating different numbers of batteries are depicted in Figs.\ref{fig:my-isolated-1}-\ref{fig:my-isolated-3}.
@@
 
-Furthermore, the performance of output current for the three RBS when isolating batteries is also illustrated in Fig.\ref{fig:isolated_mac}. 
+Furthermore, the performance of output current for the three RBS when isolating batteries is also shown in Tab.\ref{tab:isolated_mac}. 
 For the structure proposed by Lawson et al., the MAC remains the same as that without isolated battery cells, i.e., $\eta=1$, when the number of isolated battery cells increases, until all the cells in the RBS are isolated.
@@
 
-\begin{figure}[htbp]
+\begin{table}[htbp]
   \centering
-    \includegraphics[width=0.5\textwidth]{../attachments/isolated_mac.png}
   \caption{
@@
 , and the structure proposed in this paper.
-    }\label{fig:isolated_mac}
-\end{figure}
+    }
+    \label{tab:isolated_mac}
+    \begin{tabular}{cccc}
+    \toprule
+    \multirow{2}[4]{*}{number of isolated batteries} & \multicolumn{3}{c}{$\eta$ of RBS structure} \\
+\cmidrule{2-4}          & our  & Visairo's  & Lawson's  \\
+    \midrule
+    0     & 2     & 4     & 1 \\
+    1     & 2     & 3     & 1 \\
+    2     & 2$^{\rm a}$ or 1$^{\rm b}$ & 2     & 1 \\
+    3     & 1     & 1     & 1 \\
+    \bottomrule
+    \end{tabular}
+    \\
+    \footnotesize{$^{\rm a}$ isolate two batteries within the same substructure, as shown in Fig.\ref{fig:my-isolated-2b}}\\
+    \footnotesize{$^{\rm b}$ isolate one battery in each of the two substructures, as shown in Fig.\ref{fig:my-isolated-2w}}
+\end{table}
 

### 2023-06-29 paper/SST_main.tex
add SST tex (hasnot finished)

--- 2023-06-28 paper/main.tex
@@
-% 0622 v3.0 plan
-% -[x] 将 word 批注和修改内容整理到 tex 中
-% -[x] 确定修改要点，批注和obsidian记录
+\documentclass{article}
+\usepackage[utf8]{inputenc}
+\usepackage{authblk}
+\usepackage{setspace}
+\usepackage[margin=1.25in]{geometry}
+\usepackage{graphicx}
+\graphicspath{ {./figures/} }
+\usepackage{subcaption}
+\usepackage{amsmath}
+\usepackage{lineno}
+\linenumbers
 
-% 0623 v3.0 plan 具体修改计划
-% !!!!!! 先改方法、后改案例、最后改介绍和其他
-% -[x] 题目 点明我们的普适性、自动化？
-% -[x] 摘要 中间段重写；点明普适性、自动化
-% -[x] introduction 
-%      -[x] 只放 V的结构，并展示串联、并联和隔离；
-%      -[-] 增加重构灵活性的文献；
-%      -[-] 有向图的文献；
-%      -[x] 点明普适性、自动化
-% -[x] methodology 
-%      -[x] main 图重画，只保留文字；
-%      -[x] 有向图模型，说清三层关系，更规矩地写建模过程；
-%      -[x] 优化目标和约束；
-%      -[x] 最短路径，逐句逐字去捋顺；
-%      -[x] 贪心算法，结合流程图说明算法过程，把二分法融进去；
-%      -[x] 增加隔离的处理，如约束、算法的改动
-% -[x] case study 
-%      -[-] 考虑新结构（MAC=4，想不到就算了，仍用ef结构）(0626: 想不到)；
-%      -[x] results 直接给出结果，略去计算细节；
-%      -[x] discussion 说明eta的合理性；
-%      -[-] 什么样的结构能获得更大的MAC（易隔离性和输出性能的冲突）（想不出来就算了）(0626:有想法，但是要引入互斥片段的概念)；
-%      -[x] 电池隔离场景下的MAC变化(比较不同结构)
+%%%%%% Bibliography %%%%%%
+% Replace "sample" in the \addbibresource line below with the name of your .bib file.
+\usepackage[style=nejm, 
+citestyle=numeric-comp,
+sorting=none]{biblatex}
+\addbibresource{my_ref.bib}
 
-% mark
-% 统一为 directed graph model
-% 统一用 electrical load 而非 electrical appliance (泛指家电)
-
-\documentclass{article}
-\usepackage{graphicx}
-\usepackage{subcaption}
-\usepackage{enumerate}
-\usepackage{amsmath}
-\DeclareMathOperator{\diag}{diag}
-\usepackage{multirow}
-\usepackage{booktabs}
-\usepackage{footnote}
-\usepackage{bm}
-\usepackage[ruled,linesnumbered]{algorithm2e}
-\setcounter{MaxMatrixCols}{20}
-\usepackage{tikz}
-\usetikzlibrary{arrows.meta, calc, fit, positioning, quotes, graphs, shapes.geometric}
-\def\T{\mathrm{T}}
-
+%%%%%% Title %%%%%%
+% Full titles can be a maximum of 100 characters, including spaces. 
+% Title Format: Use title case, capitalizing the first letter of each word, except for certain small words, such as articles and short prepositions
 \title{Maximum Allowable Current Determination of Arbitrary Reconfigurable Battery Systems By Using a Directed Graph Model Combined with Greedy Algorithm}
 
-\author{3057761608 }
+%%%%%% Authors %%%%%%
+% Authors should be listed in order of contribution to the paper, by first name, then middle initial (if any), followed by last name.
+% Authors should be listed in the order in which they will appear in the published version if the manuscript is accepted. 
+% Use an asterisk (*) to identify the corresponding author, and be sure to include that person’s e-mail address.
+Use symbols (in this order: †, ‡, §, ||, ¶, #, ††, ‡‡, etc.) for author notes, such as present addresses, “These authors contributed equally to this work” notations, and similar information.
+% You can include group authors, but please include a list of the actual authors (the group members) in the Supplementary Materials.
+\author[1$\dag$]{Binghui Xu}
+\author[1$\dag$]{Guangbin Hua}
+\author[1*]{Cheng Qian}
+\author[1]{Quan Xia}
+\author[1]{Bo Sun}
+\author[1]{Yi Ren}
+\author[1]{Zili Wang}
+
+%%%%%% Affiliations %%%%%%
+\affil[1]{School of Reliability and Systems Engineering, Beihang University, Beijing, 100191, China}
+\affil[*]{Address correspondence to: cqian@buaa.edu.cn}
+\affil[$\dag$]{These authors contributed equally to this work.}
+
+%%%%%% Date %%%%%%
+% Date is optional
+\date{}
+
+%%%%%% Spacing %%%%%%
+% Use paragraph spacing of 1.5 or 2 (for double spacing, use command \doublespacing)
+\onehalfspacing
 
@@
 
+%%%%%% Abstract %%%%%%
 \begin{abstract}
@@
     The results demonstrate the effectiveness of this method and its potential in facilitating next-generation RBS designs and applications, including battery isolation.
+\end{abstract}
 
-    keywords:  Reconfigurable Battery System, Maximum Allowable Current, Directed Graph Model , Greedy Algorithm
-\end{abstract}
+%%%%%% Main Text %%%%%%
 
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/stru-V-origin.png} % 完整结构
+        \includegraphics[width=\textwidth]{stru-V-origin}
         \caption{}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/stru-V-serial.png} % 全串联
+        \includegraphics[width=\textwidth]{stru-V-serial}
         \caption{}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/stru-V-parallel.png} % 全并联
+        \includegraphics[width=\textwidth]{stru-V-parallel}
         \caption{}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/stru-V-isolate} % 电池隔离 右二 B3 全并联
+        \includegraphics[width=\textwidth]{stru-V-isolate}
         \caption{}
@@
 Therefore, intelligent algorithms that rely on evolving by iteration may face efficiency issues when dealing with large RBS system.
-% 如果有时间，可以在案例部分做个对比，看看智能算法和本文算法的效率差距有多大。
 In order to address this issue, the problem should be considered from the perspective of guiding the RBS to reconstruct as many parallel structures as possible.
@@
 The detailed implementation process is presented in the following two subsections.
-
-% Herein provides the solution procedure of …: 1. 2.
-% 考虑这部分怎么写，想不出就直接删了吧。
-% The integrability of the matrix $\bm{Y}_n$ is explained here.
-% Although the above solution procedure requires the matrix $\bm{Y}_n$ to be invertible, it is still possible to encounter integrable $\bm{Y}_n$ in the calculation.
-% The physical meaning of this case corresponds to the fact that due to the excessive number of switches in OFF, the solved circuit structure forms circuit branches independent of the main circuit, i.e., the circuit connected to the anode and cathode of the RBS.
-% Since these independent branches are not connected to the main circuit, the voltage potentials of these branches cannot be determined and theoretically an infinite number of sets of solutions exist.
-% Benfit from the independence, these solutions have no influence on the results of the main circuit. 
-% Since only the currents and voltages of the main circuit are of interest, only one of these solutions needs to be chosen for subsequent calculation.
 
@@
 
-\subsection{Discussion}
-
-In this subsection, we firstly discuss the correctness of the results presented in Fig.\ref{fig:all-results-my} and Tab.\ref{tab:study-results-my}. 
-When $B_1$ and $B_2$ or $B_3$ and $B_4$ are connected in parallel, the RBS can output the maximum current, which is $\eta=2$, i.e., twice the current output of a single battery in RBS. 
-Adding more batteries to the main circuit can only form a series structure and will not improve the MAC. 
-Therefore, the switches state given in Tab.\ref{tab:study-results-my} can make the RBS output current reach the maximum.
-
-It is important to note that when solving for MAC, $\eta$ is used as the objective function instead of $I_o$. 
-This choice makes the result of MAC more reasonable. 
-As shown in Tab.\ref{tab:study-results-my}, $I_o$ and $\bm{I}_b$ are functions of $R_o$, $u_b$, and $r_b$. 
-If $I_o$ were used as the objective function, even for the same RBS structure, the MAC result and corresponding switches state could change due to different external electrical appliances.
-It would increase the difficulty and uncertainty in RBS structure design. 
-In contrast, by using $\eta$ as the objective function, which is defined as the ratio of $I_o$ and $\max\bm{I}_b$, the influence of these factors on the results can be eliminated. 
-$\eta$ solely reflects the maximum output current capability of the RBS structure. 
-Assuming that the maximum allowed current of batteries in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by determining the $\eta$ of the structure. 
-Therefore, compared to $I_o$, $\eta$ is more suitable for structure design.
-
-The method proposed in this paper is significant for the design of next-generation RBSs in the following aspects.
-Most of the currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} exhibit simple topological characteristics, and the calculation of MACs is relatively straightforward, even intuitive.
-However, these simple structures do not always fully satisfy the requirements of complex applications, such as dynamically adapting the circuit to variable and random operating conditions, and actively equalizing differences among the batteries in the RBS.
-Moreover, isolating the batteries disrupts the original regularity and symmetry of the topology, which complicates the otherwise simple structure, and the maximum output current of the system becomes more challenging to obtain.
-Owing to the advantages of pervasiveness and automation, the proposed method can be employed to calculate the MAC of arbitrary RBS structures, which helps to address the aforementioned issues and paves the way for more complex and flexible RBS structure design.
-
-To illustrate this point, the MACs of the three RBS structures mentioned above are calculated after the batteries are isolated, as shown in Tab.\ref{tab:isolated_mac}. 
-Specifically, for the structure presented in Fig.\ref{fig:study-stru-my}, the corresponding circuit states of MACs when isolating different numbers of batteries are depicted in Figs.\ref{fig:my-isolated-1}-\ref{fig:my-isolated-3}.
-This structure has two cases of isolating two batteries: 
-one is to isolate two batteries within the same substructure (Fig.\ref{fig:my-isolated-2b}), in which case $\eta=2$; the other is to isolate one battery in each of the two substructures (Fig.\ref{fig:my-isolated-2w}), in which case $\eta=1$.
-From the results, it can be observed that the proposed method provides reasonable outcomes for isolating batteries with any number and position.
-
-Furthermore, the performance of output current for the three RBS when isolating batteries is also shown in Tab.\ref{tab:isolated_mac}. 
-For the structure proposed by Lawson et al., the MAC remains the same as that without isolated battery cells, i.e., $\eta=1$, when the number of isolated battery cells increases, until all the cells in the RBS are isolated.
-For Visairo's structure, the MAC decreases as the number of isolated battery cells increases, until $\eta=0$. 
-In contrast, the MAC of the structure proposed in this work is positioned between the two structures. 
-This indicates that the structure proposed in this paper, compared to Lawson's structure, has a larger MAC under the same number of batteries, which means a wider output current regulation range. 
-On the other hand, by simply changing the states of $S_2$, $S_4$, $S_{11}$, and $S_{12}$ in the conversion structure, this structure can address the majority of battery isolation scenarios, whereas Visairo's structure requires specific battery targeting and switch control.
-In summary, the structure proposed in this paper has the advantages of both Lawson's and Visairo's structures.
+Furthermore, the RBS under the scenario of isolated batteries is taken into consideration and calculated. 
+The MAC calculation results for the three structures under study, with varying numbers of isolated batteries, are presented in Tab.\ref{tab:isolated_mac}. 
+Figs.\ref{fig:my-isolated-1}-\ref{fig:my-isolated-3} illustrate the corresponding switch control schemes for the new structure proposed in this paper under different isolated battery conditions.
+The characteristics of these three structures in the context of battery isolation will be discussed in the next subsection.
 
@@
 
+\subsection{Discussion}
+
+In this subsection, we firstly discuss the correctness of the results presented in Fig.\ref{fig:all-results-my} and Tab.\ref{tab:study-results-my}. 
+When $B_1$ and $B_2$ or $B_3$ and $B_4$ are connected in parallel, the RBS can output the maximum current, which is $\eta=2$, i.e., twice the current output of a single battery in RBS. 
+Adding more batteries to the main circuit can only form a series structure and will not improve the MAC. 
+Therefore, the switches state given in Tab.\ref{tab:study-results-my} can make the RBS output current reach the maximum.
+
+It is important to note that when solving for MAC, $\eta$ is used as the objective function instead of $I_o$. 
+This choice makes the result of MAC more reasonable. 
+As shown in Tab.\ref{tab:study-results-my}, $I_o$ and $\bm{I}_b$ are functions of $R_o$, $u_b$, and $r_b$. 
+If $I_o$ were used as the objective function, even for the same RBS structure, the MAC result and corresponding switches state could change due to different external electrical appliances.
+It would increase the difficulty and uncertainty in RBS structure design. 
+In contrast, by using $\eta$ as the objective function, which is defined as the ratio of $I_o$ and $\max\bm{I}_b$, the influence of these factors on the results can be eliminated. 
+$\eta$ solely reflects the maximum output current capability of the RBS structure. 
+Assuming that the maximum allowed current of batteries in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by determining the $\eta$ of the structure. 
+Therefore, compared to $I_o$, $\eta$ is more suitable for structure design.
+
+The method proposed in this paper is significant for the design of next-generation RBSs in the following aspects.
+Most of the currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} exhibit simple topological characteristics, and the calculation of MACs is relatively straightforward, even intuitive.
+However, these simple structures do not always fully satisfy the requirements of complex applications, such as dynamically adapting the circuit to variable and random operating conditions, and actively equalizing differences among the batteries in the RBS.
+Moreover, isolating the batteries disrupts the original regularity and symmetry of the topology, which complicates the otherwise simple structure, and the maximum output current of the system becomes more challenging to obtain.
+Owing to the advantages of pervasiveness and automation, the proposed method can be employed to calculate the MAC of arbitrary RBS structures, which helps to address the aforementioned issues and paves the way for more complex and flexible RBS structure design.
+
+To illustrate this point, the MACs of the three RBS structures mentioned above are calculated after the batteries are isolated, as shown in Tab.\ref{tab:isolated_mac}. 
+Specifically, for the structure presented in Fig.\ref{fig:study-stru-my}, the corresponding circuit states of MACs when isolating different numbers of batteries are depicted in Figs.\ref{fig:my-isolated-1}-\ref{fig:my-isolated-3}.
+This structure has two cases of isolating two batteries: 
+one is to isolate two batteries within the same substructure (Fig.\ref{fig:my-isolated-2b}), in which case $\eta=2$; the other is to isolate one battery in each of the two substructures (Fig.\ref{fig:my-isolated-2w}), in which case $\eta=1$.
+From the results, it can be observed that the proposed method provides reasonable outcomes for isolating batteries with any number and position.
+
+Furthermore, the performance of output current for the three RBS when isolating batteries is also shown in Tab.\ref{tab:isolated_mac}. 
+For the structure proposed by Lawson et al., the MAC remains the same as that without isolated battery cells, i.e., $\eta=1$, when the number of isolated battery cells increases, until all the cells in the RBS are isolated.
+For Visairo's structure, the MAC decreases as the number of isolated battery cells increases, until $\eta=0$. 
+In contrast, the MAC of the structure proposed in this work is positioned between the two structures. 
+This indicates that the structure proposed in this paper, compared to Lawson's structure, has a larger MAC under the same number of batteries, which means a wider output current regulation range. 
+On the other hand, by simply changing the states of $S_2$, $S_4$, $S_{11}$, and $S_{12}$ in the conversion structure, this structure can address the majority of battery isolation scenarios, whereas Visairo's structure requires specific battery targeting and switch control.
+In summary, the structure proposed in this paper has the advantages of both Lawson's and Visairo's structures.
+
 \section{Conclusion}
@@
 
-\newpage
+\section*{Acknowledgments}
 
-\section{Appendix}
+\subsection*{Author Contributions}
 
-\begin{algorithm}
-    \caption{Get the max available currents of a certain RBS}\label{alg:greedy}
-    \KwData{Directed graph model $G(V,E)$ of the RBS}
-    \KwResult{$\max \eta$}
-    \For{$i \in E_b$}{
-        $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
-        $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
-    }
-    get $\bm{A}$ by Equation \ref{eq:A}\;
-    \While{not yet determine $\max \eta$ }
-    {
-        $N_{set} \leftarrow \text{number of setected $SP$s calculated by dichotomy}$\;
-        $C_b    \leftarrow \text{set of all combinations of $N_{set} $~batteries from $N_b$}$\;
-        \For{$c_b \in C_b$}{
-            $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
-            $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
-            get $\bm{Y}_n$ by Equation \ref{eq:Yn}\;
-            \eIf{$\bm{Y}_n$ is invertible}{
-            }{construct an effective solution}
-            get $I_o$ by Equation \ref{eq:I_o}\;
-            get $\bm{I}_b$ by Equation \ref{eq:I_b}\;
-            \eIf{$\max(\bm{I}_b)\leq I_m$}{
-                $\eta \leftarrow I_o/\max(\bm{I}_b)$\;
-            }{break}
-        }
-    }
-\end{algorithm}
+% # TODO
 
-\section{Acknowledgement}
+``S. Zhang conceived the idea and designed the experiments.''
+
+``E. F. Mustermann and J. F. Smith conducted the experiments.''
+
+``All authors contributed equally to the writing of the manuscript.''
+
+\subsection*{Funding}
+
 This work was supported by the National Natural Science Foundation of China (NSFC, No.52075028).
 
-\bibliographystyle{ieeetr}
-\bibliography{my_ref}
+\subsection*{Conflicts of Interest}
+
+The authors declare that there is no conflict of interest regarding the publication of this article.
+
+\subsection*{Data Availability}
+% # TODO
+
+\section*{Guidelines for References}
+% #TODO 细看
+Authors are responsible for ensuring that the information in each reference is complete and accurate.
+All data must be cited and references to ``data not shown'' or citations to unpublished results are permitted.
+
+All references should be cited within the text and uncited references will be removed.
+
+There is only one reference list for all sources cited in the main text, figure and table legends, and Supplementary Materials.
+Do not include a second reference list in the Supplementary Materials section.
+References cited only in the Supplementary Materials section are not counted toward length guidelines.
+
+Please do not include any extraneous language such as explanatory notes as part of a reference to a given source.
+The journal prefers that manuscripts do not include end notes; if information is important enough to include, please put into main text.
+If you need to include notes, please explain why they are needed in your cover letter to the editor.
+
+DOIs, if available, should be included for each reference.
+
+% # TODO bib 删去多余的
+\printbibliography
 

### 2023-06-30 paper/SST_main.tex
向 SST 投稿

@@
 
+\usepackage{enumerate}
+\DeclareMathOperator{\diag}{diag}
+\usepackage{multirow}
+\usepackage{booktabs}
+\usepackage{footnote}
+\usepackage{bm}
+\usepackage[ruled,linesnumbered]{algorithm2e}
+\setcounter{MaxMatrixCols}{20}
+\usepackage{tikz}
+\usetikzlibrary{arrows.meta, calc, fit, positioning, quotes, graphs, shapes.geometric}
+\def\T{\mathrm{T}}
+
 %%%%%% Bibliography %%%%%%
@@
 sorting=none]{biblatex}
-\addbibresource{my_ref.bib}
+\addbibresource{main.bib}
 
@@
 % Title Format: Use title case, capitalizing the first letter of each word, except for certain small words, such as articles and short prepositions
-\title{Maximum Allowable Current Determination of Arbitrary Reconfigurable Battery Systems By Using a Directed Graph Model Combined with Greedy Algorithm}
+\title{Maximum Allowable Current Determination of RBS By Using a Directed Graph Model and Greedy Algorithm}
 
@@
 \author[1*]{Cheng Qian}
-\author[1]{Quan Xia}
+\author[1,2]{Quan Xia}
 \author[1]{Bo Sun}
@@
 \affil[1]{School of Reliability and Systems Engineering, Beihang University, Beijing, 100191, China}
+\affil[2]{School of Aeronautic Science and Engineering at Beihang University, Beijing, China}
 \affil[*]{Address correspondence to: cqian@buaa.edu.cn}
@@
 Reconfigurable Battery Systems (RBSs) present a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structure subjected to battery charging and discharging strategies.
-    During the operation of the RBS, the Maximum Allowable Current (MAC) is a critical indicator to guide the system's reconfiguring control, ensuring safety and reliability.
-    In this paper, we propose a calculation method for the MAC of arbitrary RBS using a greedy algorithm in conjunction with a directed graph model of the RBS.
-    By employing the directed graph model, the greedy algorithm guides the RBS to establish parallel connections among batteries, aiming to maximize the system's output current while ensuring that none of the batteries are overloaded or short-circuited.
-    The effectiveness of this method is validated on a novel and complex RBS structure.
-    The results demonstrate the effectiveness of this method and its potential in facilitating next-generation RBS designs and applications, including battery isolation.
+During the operation of the RBS, the Maximum Allowable Current (MAC) of system that ensures each battery’s current remains within a safe range, is a critical indicator to guide the system’s reconfiguring control, ensuring its safety and reliability.
+In this paper, we firstly propose a calculation method for the MAC of arbitrary RBS using a greedy algorithm in conjunction with a directed graph model of the RBS.
+In this method, a new directed graph model is developed to model the structure of RBS, and a greedy algorithm is designed to find the possible circuit that enable MAC.
+Then, the MAC is calculated based on the circuit in-cooperate with the equivalent model of batteries and switches.
+The effectiveness of the proposed method is validated by a novel and complex RBS structure.
+The results show that this method is capable to calculated the MAC of RBSs with different structures or different battery sizes efficiently, which proves the correctness of this method and its potential in facilitating next-generation RBS designs and applications, including battery isolation.
 \end{abstract}
@@
 The ability of switching circuit helps to isolate unhealthy batteries, and thereby improve the safety and reliability of the battery system.
-Fig.\ref{fig:stru-Visairo} shows a typical RBS structure developed by Visairo \cite{visairoReconfigurableBatteryPack2008} for dynamically adjusting the output voltage and current.
-In this structure, the batteries can be connected not only in series when the switches $S_1$, $S_5$, $S_6$, $S_7$, $S_8$, $S_9$, and $S_{13}$ are closed (Fig.\ref{fig:stru-Visairo-serial}), but also in parallel when $S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$, and $S_{13}$ are closed (Fig.\ref{fig:stru-Visairo-parallel}).
-Furthermore, when an unhealthy battery, for instance the orange one $B_3$ in Fig.\ref{fig:stru-Visairo-isolate}, appears in the RBS, it can be isolated by opening its two adjacent switches (i.e.
+Figure \ref{fig:stru-Visairo} shows a typical RBS structure developed by Visairo \cite{visairoReconfigurableBatteryPack2008} for dynamically adjusting the output voltage and current.
+In this structure, the batteries can be connected not only in series when the switches $S_1$, $S_5$, $S_6$, $S_7$, $S_8$, $S_9$, and $S_{13}$ are closed (Figure \ref{fig:stru-Visairo-serial}), but also in parallel when $S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$, and $S_{13}$ are closed (Figure \ref{fig:stru-Visairo-parallel}).
+Furthermore, when an unhealthy battery, for instance the orange one $B_3$ in Figure \ref{fig:stru-Visairo-isolate}, appears in the RBS, it can be isolated by opening its two adjacent switches (i.e.
 $S_4$ and $S_{11}$), ensuring the system still remains a reliable working mode.
@@
 The central principle of this method is to make the batteries in RBS connected in parallel as much as possible, thereby maximizing the output current of the RBS.
-To universally and automatically achieve this, the overall process is divided into four steps, as shown in Fig.\ref{fig:main}.
+To universally and automatically achieve this, the overall process is divided into four steps, as shown in Figure \ref{fig:main}.
 Firstly, a directed graph model is established for subsequent computing, which not only contains the connected relationships between batteries and switches, but also retains the performance parameters of the batteries.
@@
     \begin{subfigure}[b]{0.8\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/main.png}
+        \includegraphics[width=\textwidth]{main}
         \caption{}
@@
     \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/direct-graph-he.png}
+        \includegraphics[width=\textwidth]{direct-graph-he}
         \caption{}
@@
     \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/direct-graph-xu.png}
+        \includegraphics[width=\textwidth]{direct-graph-xu}
         \caption{}
@@
     \begin{subfigure}[b]{0.24\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/direct-graph-my.png}
+        \includegraphics[width=\textwidth]{direct-graph-my}
         \caption{}
@@
     \begin{subfigure}[b]{0.8\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/battery_simple.png}
+        \includegraphics[width=\textwidth]{battery_simple}
         \caption{}
@@
 He et al.
-\cite{heExploringAdaptiveReconfiguration2013} once proposed an abstracted directed graph model for RBS, where the nodes represented the batteries, the edges represented the configuration flexibility, and the weight of each vertex corresponded to the battery voltage ( Fig.\ref{fig:direct-graph-he}).
+\cite{heExploringAdaptiveReconfiguration2013} once proposed an abstracted directed graph model for RBS, where the nodes represented the batteries, the edges represented the configuration flexibility, and the weight of each vertex corresponded to the battery voltage ( Figure \ref{fig:direct-graph-he}).
 The model effectively captured all potential system configurations and offered a direct metric for configuration flexibility, but it did not specify the physical implementation of the connectivity between batteries, meaning one graph might have had multiple RBS structures.
-We previously proposed a novel directed graph model that, in contrast to He's model, used nodes to represent the connections between batteries and switches, and directed edges to represent batteries and switches (Fig.\ref{fig:direct-graph-xu}), allowing for a one-to-one correspondence between the RBS structure and the directed graph model.
+We previously proposed a novel directed graph model that, in contrast to He's model, used nodes to represent the connections between batteries and switches, and directed edges to represent batteries and switches (Figure \ref{fig:direct-graph-xu}), allowing for a one-to-one correspondence between the RBS structure and the directed graph model.
 This model was able to accurately and comprehensively represent the RBS topological structure but could not be used for quantitative MAC calculations due to the lack of consideration for battery and switch performance parameters.
-To address this, an improved directed graph model is used here based on our original model, adding electromotive force and resistance attributes on the edges based to equivalent circuits (Fig.\ref{fig:direct-graph-my}).
+To address this, an improved directed graph model is used here based on our original model, adding electromotive force and resistance attributes on the edges based to equivalent circuits (Figure \ref{fig:direct-graph-my}).
 The model also considers the external load as an equivalent resistance and integrate it into the analysis, making it a complete circuit model for later circuit analysis.
@@
 In order to use circuit analysis methods to solve the MAC of the RBS, the components in the RBS are equated to ideal circuit elements.
-As shown in Fig.\ref{fig:battery_simple}, the battery in the RBS can be represented as a black-box circuit consisting of two resistors (i.e., $r_1$ and $r_2$) and a capacitor (i.e., $C$), known as the Thevenin model\cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
+As shown in Figure \ref{fig:battery_simple}, the battery in the RBS can be represented as a black-box circuit consisting of two resistors (i.e., $r_1$ and $r_2$) and a capacitor (i.e., $C$), known as the Thevenin model\cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
 With an emphasis on the stable output of the RBS, the capacitor in the Thevenin model can be considered as an open circuit without affecting the steady-state current.
@@
 First, the topology in the directed graph model is represented in matrix form $\bm{A}$, known as the incidence matrix , to facilitate circuit analysis.
-The specific definition of the incidence matrix is shown in Eq.\ref{eq:A}.
+The specific definition of the incidence matrix is shown in Equation \ref{eq:A}.
 \begin{align}\label{eq:A}
@@
 As a result, $\bm{A}$ can be reduced to a $(N-1)\times(N_b+N_s+1)$ matrix, denoted as $\bm{\tilde{A}}$, for further calculation of current and voltage.
-Similar to Eq.\ref{eq:A_bso}, $\bm{\tilde{A}}$ can be rewritten as:
+Similar to Equation \ref{eq:A_bso}, $\bm{\tilde{A}}$ can be rewritten as:
 \begin{equation}\label{eq:A_bso_tilde}
@@
 
-Theoretically, the output current $I_o$ and the currents of each battery $\bm{I}_b$ in the RBS  can be determined by solving Eqs.\ref{eq:Kirchhoffs_law}, \ref{eq:generalized_branches}, and \ref{eq:X} under any given state $\bm{X}$.
+Theoretically, the output current $I_o$ and the currents of each battery $\bm{I}_b$ in the RBS  can be determined by solving Equations \ref{eq:Kirchhoffs_law}, \ref{eq:generalized_branches}, and \ref{eq:X} under any given state $\bm{X}$.
 In order to obtain specific constraint conditions and objective functions, it is further assumed that all batteries have the same electromotive force and internal resistance, denoted as $u_b$ and $r_b$, respectively.
 This allows for the derivation of explicit expressions for $I_o$ and $\bm{I}_b$.
-After derivation and simplification, the output current $I_o$ and the currents of each battery $\bm{I}_b$ are ultimately represented as Eqs.\ref{eq:I_o} and \ref{eq:I_b}, respectively.
+After derivation and simplification, the output current $I_o$ and the currents of each battery $\bm{I}_b$ are ultimately represented as Equations \ref{eq:I_o} and \ref{eq:I_b}, respectively.
 \begin{equation}\label{eq:I_o}
@@
 
-To characterize the current output capacity of the RBS structure under different switching states, an indicator $\eta$ is defined by the ratio of $I_o$ and $\max (\bm{I}_b)$ shown in Eq.\ref{eq:eta}:
+To characterize the current output capacity of the RBS structure under different switching states, an indicator $\eta$ is defined by the ratio of $I_o$ and $\max (\bm{I}_b)$ shown in Equation \ref{eq:eta}:
 \begin{equation}\label{eq:eta}
@@
 The $v_i^- \rightarrow v_i^+$ is the directed edge corresponding to battery $i$. 
-With the Dijkstra algorithm, shortest paths for the $v_1 \rightarrow v_i^-$ and $v_i^+ \rightarrow v_N$ can be calculated under the weights given in Eq.\ref{eq:weight}, denoted as $SP(v_i^- \rightarrow v_i^+)$ and $SP(v_i^+ \rightarrow v_N)$, respectively.
+With the Dijkstra algorithm, shortest paths for the $v_1 \rightarrow v_i^-$ and $v_i^+ \rightarrow v_N$ can be calculated under the weights given in Equation \ref{eq:weight}, denoted as $SP(v_i^- \rightarrow v_i^+)$ and $SP(v_i^+ \rightarrow v_N)$, respectively.
 Finally, the $SP_i$ for battery $i$ is formed by the complete path with $SP(v_1 \rightarrow v_i^-)$, $v_i^- \rightarrow v_i^+$, and $SP(v_i^+ \rightarrow v_N)$.
@@
 
-The algorithm, as illustrated in Fig.\ref{fig:flowchart}, can be summarized as follows, with the corresponding pseudo-code presented in Algorithm \ref{alg:greedy}.
-First, the shortest paths ($SP$s) are obtained using Eqs.\ref{eq:weight} and \ref{eq:def_sp} in conjunction with Dijkstra Search. 
-Next, the matrix $\bm{A}$ is calculated using Eq.\ref{eq:A}, and the initial $N_{set}$ is set to $N_b$. 
+The algorithm, as illustrated in Figure \ref{fig:flowchart}, can be summarized as follows, with the corresponding pseudo-code presented in Algorithm \ref{alg:greedy}.
+First, the shortest paths ($SP$s) are obtained using Equations \ref{eq:weight} and \ref{eq:def_sp} in conjunction with Dijkstra Search. 
+Next, the matrix $\bm{A}$ is calculated using Equation \ref{eq:A}, and the initial $N_{set}$ is set to $N_b$. 
 The algorithm iteratively checks different combinations of $c_b$ batteries from $N_b$ and updates $N_{set}$ using a dichotomy method until convergence is reached. 
-For each combination, the algorithm constructs an effective solution if possible, and calculates the currents $I_o$ and $\bm{I}_b$ using Eqs.\ref{eq:I_o} and \ref{eq:I_b}. 
-If the maximum current $\bm{I}_b$ is less than or equal to $I_m$, the $\eta$ is calculated using Eq.\ref{eq:eta}, and the maximum $\eta$ is updated accordingly. 
+For each combination, the algorithm constructs an effective solution if possible, and calculates the currents $I_o$ and $\bm{I}_b$ using Equations \ref{eq:I_o} and \ref{eq:I_b}. 
+If the maximum current $\bm{I}_b$ is less than or equal to $I_m$, the $\eta$ is calculated using Equation \ref{eq:eta}, and the maximum $\eta$ is updated accordingly. 
 Finally, the algorithm outputs the maximum $\eta$ once $N_{set}$ converges.
@@
     \node[punkt]     (input) {Input: RBS structure};
-    \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Eqs.\ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
-    \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Eq.\ref{eq:A}};
+    \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Equations \ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
+    \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Equation \ref{eq:A}};
     \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{set}=N_b$ };
@@
         $\bm{X}[j]=1$ else $0$};
-    \node[punkt, below=0.3of get_Xs] (get_Yn) {get $\bm{Y}_n$ by Eq.\ref{eq:Yn}};
+    \node[punkt, below=0.3of get_Xs] (get_Yn) {get $\bm{Y}_n$ by Equation \ref{eq:Yn}};
     \node[draw, diamond, aspect=2, below=0.3of get_Yn] (is_Yn_invertible) {is $\bm{Y}_n$ invertible?};
     \node[punkt, right=1.3of is_Yn_invertible] (construct) {construct an effective solution};
-    \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Eqs.\ref{eq:I_o} and \ref{eq:I_b}};
+    \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Equations \ref{eq:I_o} and \ref{eq:I_b}};
     \node[draw, diamond, aspect=2, below=0.3of get_I] (is_leq_Im) {is $\max \bm{I}_b \leq I_m$?};
     \node[punkt, right=1.3of is_leq_Im] (drop_eta) {drop this $\eta$};
-    \node[punkt, below=0.3of is_leq_Im] (get_eta) {get $\eta$ by Eq.\ref{eq:eta}};
+    \node[punkt, below=0.3of is_leq_Im] (get_eta) {get $\eta$ by Equation \ref{eq:eta}};
     \node[punkt, below=0.3of get_eta] (update_max_eta) {update $\max \eta$};
@@
     \begin{subfigure}[b]{0.2\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/stru-L-origin.png}
+        \includegraphics[width=\textwidth]{stru-L-origin}
         \caption{}
@@
     \begin{subfigure}[b]{0.4\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/stru-V-origin.png}
+        \includegraphics[width=\textwidth]{stru-V-origin}
         \caption{}
@@
     \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/stru-my-origin.png}
+        \includegraphics[width=\textwidth]{stru-my-origin}
         \caption{}
@@
 \cite{lawsonSoftwareConfigurableBattery2012}, both of which have been applied in practice.
-The primary goal of Visairo's structure (Fig.\ref{fig:study-stru-Visairo}) was to achieve dynamic adjustment of RBS output; however, the isolation of unhealthy batteries was not sufficiently addressed.
+The primary goal of Visairo's structure (Figure \ref{fig:study-stru-Visairo}) was to achieve dynamic adjustment of RBS output; however, the isolation of unhealthy batteries was not sufficiently addressed.
 When batteries need to be isolated in the RBS of Visairo's structure, the methods for isolating them and the subsequent changes in RBS output warrant further investigation.
-Lawson et al. conducted research on battery isolation in RBS and specifically designed the structure shown in Fig.\ref{fig:study-stru-Lawson}. 
+Lawson et al. conducted research on battery isolation in RBS and specifically designed the structure shown in Figure \ref{fig:study-stru-Lawson}. 
 This structure has the advantage of easily isolating batteries, but it cannot dynamically adjust the output current of RBS. 
-Based on the structures of Visairo and Lawson, this paper presents a new structure, as shown in Fig.\ref{fig:study-stru-my}, which combines the advantages of both.
+Based on the structures of Visairo and Lawson, this paper presents a new structure, as shown in Figure \ref{fig:study-stru-my}, which combines the advantages of both.
 By integrating the Visairo RBS structure into the Lawson RBS structure, the new structure not only allows the flexibility to switch the batteries between series, parallel, and mixed series-parallel modes, but also easily enables the isolation of highly degraded batteries from the RBS.
@@
 
-As shown in Fig.\ref{fig:study-stru-my}, the new RBS structure consists of 4 batteries and 19 switches. 
-The corresponding directed graph is depicted in Fig.\ref{fig:study-dirgraph-my}, which is composed of of a total of 18 nodes and 43 edges. 
+As shown in Figure \ref{fig:study-stru-my}, the new RBS structure consists of 4 batteries and 19 switches. 
+The corresponding directed graph is depicted in Figure \ref{fig:study-dirgraph-my}, which is composed of of a total of 18 nodes and 43 edges. 
 Batteries $B_1$, $B_2$, $B_3$, and $B_4$ are denoted by green directed edges in the graph, while the 19 switches are represented by gray directed edges with bi-directional arrows. 
 The external electrical load is treated as a directed edge from the cathode of the RBS (i.e., node 18) to the anode (i.e., node 1), as indicated by the blue directed edge in the graph.
-Utilizing Eq.\ref{eq:weight} and the Dijkstra algorithm, the $SP$s of the four batteries in the RBS structure of Fig.\ref{fig:study-stru-my} are highlighted by red in Figs.\ref{fig:sp1}-\ref{fig:sp4}.
-Finally, the MAC calculation results of the structure in Fig.\ref{fig:study-stru-my} are shown as Tab.\ref{tab:study-results-my} and Fig.\ref{fig:study-results-my}, obtained by the greedy algorithm \ref{alg:greedy}.
-Tab.\ref{tab:study-results-my} contains the switches states, the output current $I_o$, battery current $\bm{I}_b$ and ratio $\eta$ of the RBS structure with all batteries in good health when the RBS output reaches the MAC.
-Fig.\ref{fig:study-results-my} presents the corresponding circuit, with the red highlight indicating that current is flowing through the respective branches.
+Utilizing Equation \ref{eq:weight} and the Dijkstra algorithm, the $SP$s of the four batteries in the RBS structure of Figure \ref{fig:study-stru-my} are highlighted by red in Figures \ref{fig:sp1}-\ref{fig:sp4}.
+Finally, the MAC calculation results of the structure in Figure \ref{fig:study-stru-my} are shown as Table \ref{tab:study-results-my} and Figure \ref{fig:study-results-my}, obtained by the greedy algorithm \ref{alg:greedy}.
+Table \ref{tab:study-results-my} contains the switches states, the output current $I_o$, battery current $\bm{I}_b$ and ratio $\eta$ of the RBS structure with all batteries in good health when the RBS output reaches the MAC.
+Figure \ref{fig:study-results-my} presents the corresponding circuit, with the red highlight indicating that current is flowing through the respective branches.
 
@@
     \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/ef-topo.png}
+        \includegraphics[width=\textwidth]{ef-topo}
         \caption{}
@@
     \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/ef-sp1.png}
+        \includegraphics[width=\textwidth]{ef-sp1}
         \caption{}
@@
     \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/ef-sp2.png}
+        \includegraphics[width=\textwidth]{ef-sp2}
         \caption{}
@@
     \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/ef-sp3.png}
+        \includegraphics[width=\textwidth]{ef-sp3}
         \caption{}
@@
     \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/ef-sp4.png}
+        \includegraphics[width=\textwidth]{ef-sp4}
         \caption{}
@@
     \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/ef-mac.png}
+        \includegraphics[width=\textwidth]{ef-mac}
         \caption{}
@@
     \caption{
-        For the RBS structure in Fig.\ref{fig:study-stru-my}, 
+        For the RBS structure in Figure \ref{fig:study-stru-my}, 
         (a)its directed graph 
@@
   \centering
-    \caption{MAC Calculating result of the 4-battery RBS structure in Fig.\ref{fig:study-stru-my}.}
+    \caption{MAC Calculating result of the 4-battery RBS structure in Figure \ref{fig:study-stru-my}.}
     \begin{tabular}{cc}
     \toprule
-        Structure & Fig.\ref{fig:study-stru-my} with 4 batteries and 19 switches  \\
+        Structure & Figure \ref{fig:study-stru-my} with 4 batteries and 19 switches  \\
     \midrule
@@
 
-Similarly, the MAC calculation results of the structures in Figs.\ref{fig:study-stru-Lawson} and \ref{fig:study-stru-Visairo} are shown as Tab.\ref{tab:study-results-Lawson} and Tab.\ref{tab:study-results-Visairo}, respectively.
+Similarly, the MAC calculation results of the structures in Figures \ref{fig:study-stru-Lawson} and \ref{fig:study-stru-Visairo} are shown as Table \ref{tab:study-results-Lawson} and Table \ref{tab:study-results-Visairo}, respectively.
 
@@
   \centering
-    \caption{MAC Calculating result of the 4-battery RBS structure in Fig.\ref{fig:study-stru-Lawson}.}
+    \caption{MAC Calculating result of the 4-battery RBS structure in Figure \ref{fig:study-stru-Lawson}.}
     \begin{tabular}{cc}
     \toprule
-        Structure & Fig.\ref{fig:study-stru-Lawson} with 4 batteries and 15 switches  \\
+        Structure & Figure \ref{fig:study-stru-Lawson} with 4 batteries and 15 switches  \\
     \midrule
@@
   \centering
-    \caption{MAC Calculating result of the 4-battery RBS structure in Fig.\ref{fig:study-stru-Visairo}.}
+    \caption{MAC Calculating result of the 4-battery RBS structure in Figure \ref{fig:study-stru-Visairo}.}
     \begin{tabular}{cc}
     \toprule
-        Structure & Fig.\ref{fig:study-stru-Visairo} with 4 batteries and 13 switches  \\
+        Structure & Figure \ref{fig:study-stru-Visairo} with 4 batteries and 13 switches  \\
     \midrule
@@
 Furthermore, the RBS under the scenario of isolated batteries is taken into consideration and calculated. 
-The MAC calculation results for the three structures under study, with varying numbers of isolated batteries, are presented in Tab.\ref{tab:isolated_mac}. 
-Figs.\ref{fig:my-isolated-1}-\ref{fig:my-isolated-3} illustrate the corresponding switch control schemes for the new structure proposed in this paper under different isolated battery conditions.
+The MAC calculation results for the three structures under study, with varying numbers of isolated batteries, are presented in Table \ref{tab:isolated_mac}. 
+Figures \ref{fig:my-isolated-1}-\ref{fig:my-isolated-3} illustrate the corresponding switch control schemes for the new structure proposed in this paper under different isolated battery conditions.
 The characteristics of these three structures in the context of battery isolation will be discussed in the next subsection.
@@
       \\
-      \footnotesize{$^{\rm a}$ isolate two batteries within the same substructure, as shown in Fig.\ref{fig:my-isolated-2b}}\\
-      \footnotesize{$^{\rm b}$ isolate one battery in each of the two substructures, as shown in Fig.\ref{fig:my-isolated-2w}}
+      \footnotesize{$^{\rm a}$ isolate two batteries within the same substructure, as shown in Figure \ref{fig:my-isolated-2b}}\\
+      \footnotesize{$^{\rm b}$ isolate one battery in each of the two substructures, as shown in Figure \ref{fig:my-isolated-2w}}
   \end{table}
@@
       \begin{subfigure}[b]{0.31\textwidth}
-          \includegraphics[width=\textwidth]{../attachments/my-isolated-1.png}
+          \includegraphics[width=\textwidth]{my-isolated-1}
           \caption{}
@@
       \begin{subfigure}[b]{0.31\textwidth}
-          \includegraphics[width=\textwidth]{../attachments/my-isolated-2b.png}
+          \includegraphics[width=\textwidth]{my-isolated-2b}
           \caption{}
@@
       \begin{subfigure}[b]{0.31\textwidth}
-          \includegraphics[width=\textwidth]{../attachments/my-isolated-2w.png}
+          \includegraphics[width=\textwidth]{my-isolated-2w}
           \caption{}
@@
       \begin{subfigure}[b]{0.31\textwidth}
-          \includegraphics[width=\textwidth]{../attachments/my-isolated-3.png}
+          \includegraphics[width=\textwidth]{my-isolated-3}
           \caption{}
@@
       \caption{
-          The circuit states of MACs when isolating (a)one, (b)two(best case), (c)two(worst case) and (d)three batteries for the structure in Fig.\ref{fig:study-stru-my}.
+          The circuit states of MACs when isolating (a)one, (b)two(best case), (c)two(worst case) and (d)three batteries for the structure in Figure \ref{fig:study-stru-my}.
           }
@@
 
-In this subsection, we firstly discuss the correctness of the results presented in Fig.\ref{fig:all-results-my} and Tab.\ref{tab:study-results-my}. 
+In this subsection, we firstly discuss the correctness of the results presented in Figure \ref{fig:all-results-my} and Table \ref{tab:study-results-my}. 
 When $B_1$ and $B_2$ or $B_3$ and $B_4$ are connected in parallel, the RBS can output the maximum current, which is $\eta=2$, i.e., twice the current output of a single battery in RBS. 
 Adding more batteries to the main circuit can only form a series structure and will not improve the MAC. 
-Therefore, the switches state given in Tab.\ref{tab:study-results-my} can make the RBS output current reach the maximum.
+Therefore, the switches state given in Table \ref{tab:study-results-my} can make the RBS output current reach the maximum.
 
@@
 This choice makes the result of MAC more reasonable. 
-As shown in Tab.\ref{tab:study-results-my}, $I_o$ and $\bm{I}_b$ are functions of $R_o$, $u_b$, and $r_b$. 
+As shown in Table \ref{tab:study-results-my}, $I_o$ and $\bm{I}_b$ are functions of $R_o$, $u_b$, and $r_b$. 
 If $I_o$ were used as the objective function, even for the same RBS structure, the MAC result and corresponding switches state could change due to different external electrical appliances.
@@
 
-To illustrate this point, the MACs of the three RBS structures mentioned above are calculated after the batteries are isolated, as shown in Tab.\ref{tab:isolated_mac}. 
-Specifically, for the structure presented in Fig.\ref{fig:study-stru-my}, the corresponding circuit states of MACs when isolating different numbers of batteries are depicted in Figs.\ref{fig:my-isolated-1}-\ref{fig:my-isolated-3}.
+To illustrate this point, the MACs of the three RBS structures mentioned above are calculated after the batteries are isolated, as shown in Table \ref{tab:isolated_mac}. 
+Specifically, for the structure presented in Figure \ref{fig:study-stru-my}, the corresponding circuit states of MACs when isolating different numbers of batteries are depicted in Figures \ref{fig:my-isolated-1}-\ref{fig:my-isolated-3}.
 This structure has two cases of isolating two batteries: 
-one is to isolate two batteries within the same substructure (Fig.\ref{fig:my-isolated-2b}), in which case $\eta=2$; the other is to isolate one battery in each of the two substructures (Fig.\ref{fig:my-isolated-2w}), in which case $\eta=1$.
+one is to isolate two batteries within the same substructure (Figure \ref{fig:my-isolated-2b}), in which case $\eta=2$; the other is to isolate one battery in each of the two substructures (Figure \ref{fig:my-isolated-2w}), in which case $\eta=1$.
 From the results, it can be observed that the proposed method provides reasonable outcomes for isolating batteries with any number and position.
 
-Furthermore, the performance of output current for the three RBS when isolating batteries is also shown in Tab.\ref{tab:isolated_mac}. 
+Furthermore, the performance of output current for the three RBS when isolating batteries is also shown in Table \ref{tab:isolated_mac}. 
 For the structure proposed by Lawson et al., the MAC remains the same as that without isolated battery cells, i.e., $\eta=1$, when the number of isolated battery cells increases, until all the cells in the RBS are isolated.
@@
 
+\section{Appendix}
+
+\begin{algorithm}
+    \caption{Get the max available currents of a certain RBS}\label{alg:greedy}
+    \KwData{Directed graph model $G(V,E)$ of the RBS}
+    \KwResult{$\max \eta$}
+    \For{$i \in E_b$}{
+        $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
+        $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
+    }
+    get $\bm{A}$ by Equation \ref{eq:A}\;
+    \While{not yet determine $\max \eta$ }
+    {
+        $N_{set} \leftarrow \text{number of setected $SP$s calculated by dichotomy}$\;
+        $C_b    \leftarrow \text{set of all combinations of $N_{set} $~batteries from $N_b$}$\;
+        \For{$c_b \in C_b$}{
+            $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
+            $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
+            get $\bm{Y}_n$ by Equation \ref{eq:Yn}\;
+            \eIf{$\bm{Y}_n$ is invertible}{
+            }{construct an effective solution}
+            get $I_o$ by Equation \ref{eq:I_o}\;
+            get $\bm{I}_b$ by Equation \ref{eq:I_b}\;
+            \eIf{$\max(\bm{I}_b)\leq I_m$}{
+                $\eta \leftarrow I_o/\max(\bm{I}_b)$\;
+            }{break}
+        }
+    }
+\end{algorithm}
+
 \section*{Acknowledgments}
@@
 
-% # TODO
-
-``S. Zhang conceived the idea and designed the experiments.''
-
-``E. F. Mustermann and J. F. Smith conducted the experiments.''
-
-``All authors contributed equally to the writing of the manuscript.''
+B. Xu conceived the main idea, formulated the overarching research goals and aims, designed the algorithm, and reviewed and revised the manuscript.
+G. Hua developed and analyzed the model, implemented the code and supporting algorithms, and wrote the initial draft.
+C. Qian provided critical review, commentary, and revisions.
+Q. Xia contributed to shaping the research, analysis, and manuscript.
+B. Sun conducted the research and investigation process.
+Y. Ren secured the funding and supervised the project.
+Z. Wang verified the results and provided necessary resources.
 
@@
 \subsection*{Data Availability}
-% # TODO
 
-\section*{Guidelines for References}
-% #TODO 细看
-Authors are responsible for ensuring that the information in each reference is complete and accurate.
-All data must be cited and references to ``data not shown'' or citations to unpublished results are permitted.
+This work does not require any data to be declared or publicly disclosed.
 
-All references should be cited within the text and uncited references will be removed.
-
-There is only one reference list for all sources cited in the main text, figure and table legends, and Supplementary Materials.
-Do not include a second reference list in the Supplementary Materials section.
-References cited only in the Supplementary Materials section are not counted toward length guidelines.
-
-Please do not include any extraneous language such as explanatory notes as part of a reference to a given source.
-The journal prefers that manuscripts do not include end notes; if information is important enough to include, please put into main text.
-If you need to include notes, please explain why they are needed in your cover letter to the editor.
-
-DOIs, if available, should be included for each reference.
-
-% # TODO bib 删去多余的
 \printbibliography

### 2023-06-30 paper/main.tex
向 SST 投稿

@@
 \def\T{\mathrm{T}}
+\graphicspath{ {../attachments/} }
 
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/stru-V-origin.png} % 完整结构
+        \includegraphics[width=\textwidth]{stru-V-origin} % 完整结构
         \caption{}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/stru-V-serial.png} % 全串联
+        \includegraphics[width=\textwidth]{stru-V-serial} % 全串联
         \caption{}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/stru-V-parallel.png} % 全并联
+        \includegraphics[width=\textwidth]{stru-V-parallel} % 全并联
         \caption{}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/stru-V-isolate} % 电池隔离 右二 B3 全并联
+        \includegraphics[width=\textwidth]{stru-V-isolate} % 电池隔离 右二 B3 全并联
         \caption{}
@@
     \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/my-isolated-1.png}
+        \includegraphics[width=\textwidth]{my-isolated-1}
         \caption{}
@@
     \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/my-isolated-2b.png}
+        \includegraphics[width=\textwidth]{my-isolated-2b}
         \caption{}
@@
     \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/my-isolated-2w.png}
+        \includegraphics[width=\textwidth]{my-isolated-2w}
         \caption{}
@@
     \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{../attachments/my-isolated-3.png}
+        \includegraphics[width=\textwidth]{my-isolated-3}
         \caption{}

### 2023-07-09 paper/SST_main.tex
解决了 SST 期刊的参考文献问题

@@
 % Replace "sample" in the \addbibresource line below with the name of your .bib file.
-\usepackage[style=nejm, 
-citestyle=numeric-comp,
-sorting=none]{biblatex}
-\addbibresource{main.bib}
+% \usepackage[style=nejm, 
+% citestyle=numeric-comp,
+% sorting=none]{biblatex}
+% \addbibresource{main.bib}
 
@@
 
-\printbibliography
+\begin{thebibliography}{99}
+
+\bibitem{desiqueiraControlStrategySmooth2021}
+Luanna Maria~Silva {de Siqueira} and Wei Peng.
+\newblock Control strategy to smooth wind power output using battery energy
+  storage system: {{A}} review.
+\newblock {\em Journal of Energy Storage}, 35:102252, March 2021.
+
+\bibitem{yangBatteryEnergyStorage2018}
+Yuqing Yang, Stephen Bremner, Chris Menictas, and Merlinde Kay.
+\newblock Battery energy storage system size determination in renewable energy
+  systems: {{A}} review.
+\newblock {\em Renewable and Sustainable Energy Reviews}, 91:109--125, August
+  2018.
+
+\bibitem{choCommercialResearchBattery2015}
+Jaephil Cho, Sookyung Jeong, and Youngsik Kim.
+\newblock Commercial and research battery technologies for electrical energy
+  storage applications.
+\newblock {\em Progress in Energy and Combustion Science}, 48:84--101, June
+  2015.
+
+\bibitem{zhangDevelopmentProspectChinese2021}
+Lihua Zhang.
+\newblock Development and {{Prospect}} of {{Chinese Lunar Relay Communication
+  Satellite}}.
+\newblock {\em Space: Science \& Technology}, 2021, January 2021.
+
+\bibitem{schwanbeckInternationalSpaceStation2019}
+Eugene Schwanbeck and Penni Dalton.
+\newblock International {{Space Station Lithium-ion Batteries}} for {{Primary
+  Electric Power System}}.
+\newblock In {\em 2019 {{European Space Power Conference}} ({{ESPC}})}, pages
+  1--1. {IEEE}, September 2019.
+
+\bibitem{yangUnbalancedDischargingAging2016}
+Naixing Yang, Xiongwen Zhang, BinBin Shang, and Guojun Li.
+\newblock Unbalanced discharging and aging due to temperature differences among
+  the cells in a lithium-ion battery pack with parallel combination.
+\newblock {\em Journal of Power Sources}, 306:733--741, February 2016.
+
+\bibitem{fengPropagationMechanismsDiagnosis2019}
+Fei Feng, Xiaosong Hu, Lin Hu, Fengling Hu, Yang Li, and Lei Zhang.
+\newblock Propagation mechanisms and diagnosis of parameter inconsistency
+  within {{Li-Ion}} battery packs.
+\newblock {\em Renewable and Sustainable Energy Reviews}, 112:102--113,
+  September 2019.
+
+\bibitem{jeevarajanBatterySafetyQualifications2012}
+J.~A. Jeevarajan and C.~Winchester.
+\newblock Battery {{Safety Qualifications}} for {{Human Ratings}}.
+\newblock {\em Interface magazine}, 21(2):51--55, January 2012.
+
+\bibitem{pomboHybridPowerSystem2021}
+Daniel~V{\'a}zquez Pombo.
+\newblock A {{Hybrid Power System}} for a {{Permanent Colony}} on {{Mars}}.
+\newblock {\em Space: Science \& Technology}, 2021, January 2021.
+
+\bibitem{hanNextGenerationBatteryManagement2020a}
+Weiji Han, Torsten Wik, Anton Kersten, Guangzhong Dong, and Changfu Zou.
+\newblock Next-{{Generation Battery Management Systems}}: {{Dynamic
+  Reconfiguration}}.
+\newblock {\em IEEE Industrial Electronics Magazine}, 14(4):20--31, December
+  2020.
+
+\bibitem{visairoReconfigurableBatteryPack2008}
+H.~Visairo and P.~Kumar.
+\newblock A reconfigurable battery pack for improving power conversion
+  efficiency in portable devices.
+\newblock In {\em 2008 7th {{International Caribbean Conference}} on
+  {{Devices}}, {{Circuits}} and {{Systems}}}, pages 1--6. {IEEE}, April 2008.
+
+\bibitem{heExploringAdaptiveReconfiguration2013}
+Liang He, Lipeng Gu, Linghe Kong, Yu~Gu, Cong Liu, and Tian He.
+\newblock Exploring {{Adaptive Reconfiguration}} to {{Optimize Energy
+  Efficiency}} in {{Large-Scale Battery Systems}}.
+\newblock In {\em 2013 {{IEEE}} 34th {{Real-Time Systems Symposium}}}, pages
+  118--127, December 2013.
+
+\bibitem{hongwenheStateofChargeEstimationLithiumIon2011}
+Hongwen He, Rui Xiong, Xiaowei Zhang, Fengchun Sun, and JinXin Fan.
+\newblock State-of-{{Charge Estimation}} of the {{Lithium-Ion Battery Using}}
+  an {{Adaptive Extended Kalman Filter Based}} on an {{Improved Thevenin
+  Model}}.
+\newblock {\em IEEE Transactions on Vehicular Technology}, 60(4):1461--1469,
+  May 2011.
+
+\bibitem{mousavig.VariousBatteryModels2014}
+S.M. Mousavi~G. and M.~Nikdel.
+\newblock Various battery models for various simulation studies and
+  applications.
+\newblock {\em Renewable and Sustainable Energy Reviews}, 32:477--485, April
+  2014.
+
+\bibitem{lawsonSoftwareConfigurableBattery2012}
+Barrie Lawson.
+\newblock A {{Software Configurable Battery}}.
+\newblock {\em EVS26 International Battery, Hybrid and Fuel Cell Electric
+  Vehicle Symposium}, 2012.
+
+\bibitem{ciNovelDesignAdaptive2007}
+Song Ci, Jiucai Zhang, Hamid Sharif, and Mahmoud Alahmad.
+\newblock A {{Novel Design}} of {{Adaptive Reconfigurable Multicell Battery}}
+  for {{Power-Aware Embedded Networked Sensing Systems}}.
+\newblock In {\em {{IEEE GLOBECOM}} 2007-2007 {{IEEE Global Telecommunications
+  Conference}}}, pages 1043--1047, November 2007.
+
+\bibitem{alahmadBatterySwitchArray2008}
+Mahmoud Alahmad, Herb Hess, Mohammad Mojarradi, William West, and Jay Whitacre.
+\newblock Battery switch array system with application for {{JPL}}'s
+  rechargeable micro-scale batteries.
+\newblock {\em Journal of Power Sources}, 177(2):566--578, March 2008.
+
+\bibitem{kimDependableEfficientScalable2010b}
+Hahnsang Kim and Kang~G. Shin.
+\newblock Dependable, efficient, scalable architecture for management of
+  large-scale batteries.
+\newblock In {\em Proceedings of the 1st {{ACM}}/{{IEEE International
+  Conference}} on {{Cyber-Physical Systems}}}, {{ICCPS}} '10, pages 178--187,
+  {New York, NY, USA}, April 2010. {Association for Computing Machinery}.
+
+\bibitem{kimBalancedReconfigurationStorage2011a}
+Younghyun Kim, Sangyoung Park, Yanzhi Wang, Qing Xie, Naehyuck Chang, Massimo
+  Poncino, and Massoud Pedram.
+\newblock Balanced reconfiguration of storage banks in a hybrid electrical
+  energy storage system.
+\newblock In {\em 2011 {{IEEE}}/{{ACM International Conference}} on
+  {{Computer-Aided Design}} ({{ICCAD}})}, pages 624--631, November 2011.
+
+\bibitem{taesickimSeriesconnectedSelfreconfigurableMulticell2012a}
+Taesic Kim, Wei Qiao, and Liyan Qu.
+\newblock A series-connected self-reconfigurable multicell battery capable of
+  safe and effective charging/discharging and balancing operations.
+\newblock In {\em 2012 {{Twenty-Seventh Annual IEEE Applied Power Electronics
+  Conference}} and {{Exposition}} ({{APEC}})}, pages 2259--2264, February 2012.
+
+\bibitem{6843711}
+Liang He, Linghe Kong, Siyu Lin, Shaodong Ying, Yu~Gu, Tian He, and Cong Liu.
+\newblock Reconfiguration-assisted charging in large-scale {{Lithium-ion}}
+  battery systems.
+\newblock In {\em 2014 {{ACM}}/{{IEEE International Conference}} on
+  {{Cyber-Physical Systems}} ({{ICCPS}})}, pages 60--71, April 2014.
+
+\end{thebibliography}
 

### 2023-07-09 paper/main.tex
解决了 SST 期刊的参考文献问题

@@
 \begin{abstract}
-    Reconfigurable Battery Systems (RBSs) present a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structure subjected to battery charging and discharging strategies.
+    Reconfigurable Battery Systems (RBSs) present a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structure subjected to battery charging and discharging strategies
     During the operation of the RBS, the Maximum Allowable Current (MAC) is a critical indicator to guide the system's reconfiguring control, ensuring safety and reliability.

### 2023-09-01 paper/SST/SST_main.tex
添加了 SST 和 Q 的修改意见文件；添加了修改计划
添加并测试了修改使用的 changes 宏包；修正了 tex2docx 的部分bug
1. changes 在编译时运行正常，但在使用 pandoc 转 word 时无法正常显示。
2. tex2docx 生成的 docx 显示报错时优先删除流程图部分。

--- 2023-07-09 paper/SST_main.tex
@@
 \usepackage{graphicx}
-\graphicspath{ {./figures/} }
+% \graphicspath{ {./figures/} }
+\graphicspath{ {../figures/} }
 \usepackage{subcaption}
@@
 \def\T{\mathrm{T}}
+
+\usepackage[defaultcolor=red]{changes}
+% \added{xxx}
+% \deleted{xxxx}
+% \replaced{a}{b} 原文的b替换成a
+% \usepackage[final]{changes}
+
+% 按 Q 修改意见修改 0901 【优先】
+% 按 SST 修改意见修改 0902 【14号前交给润色机构】
+% 1. 摘要修改，量化我们的成果：explain the most important achievements of the proposed method quantitatively
+% 2. 介绍修改，相关文献：
+%   2.1 RBS 结构分析相关的
+%   2.2 网络流（最大流）相关（但因为问题不同，无法使用，提一句穷举）
+% 3. 介绍修改，逐点列出我们的贡献：state research contribution and achievements as bullet points at the end of the Introduction section
+% 4. 讨论修改，增加算法复杂度，以及和穷举法的比较（该领域尚为空白，没有sota的算法）
+% 5. 讨论修改，增加算法的 limitations（根据复杂度，大规模不好用）
+% 6. 讨论修改，增加结果的准确性介绍（和穷举结果比较）：explain about the accuracy, sufficiency and reliability of their results? How do they verify and validate the results
 
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{stru-V-origin}
+        \includegraphics[width=\textwidth]{stru-V-origin.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{stru-V-serial}
+        \includegraphics[width=\textwidth]{stru-V-serial.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{stru-V-parallel}
+        \includegraphics[width=\textwidth]{stru-V-parallel.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{stru-V-isolate}
+        \includegraphics[width=\textwidth]{stru-V-isolate.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.8\textwidth}
-        \includegraphics[width=\textwidth]{main}
+        \includegraphics[width=\textwidth]{main.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{direct-graph-he}
+        \includegraphics[width=\textwidth]{direct-graph-he.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{direct-graph-xu}
+        \includegraphics[width=\textwidth]{direct-graph-xu.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.24\textwidth}
-        \includegraphics[width=\textwidth]{direct-graph-my}
+        \includegraphics[width=\textwidth]{direct-graph-my.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.8\textwidth}
-        \includegraphics[width=\textwidth]{battery_simple}
+        \includegraphics[width=\textwidth]{battery_simple.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.2\textwidth}
-        \includegraphics[width=\textwidth]{stru-L-origin}
+        \includegraphics[width=\textwidth]{stru-L-origin.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.4\textwidth}
-        \includegraphics[width=\textwidth]{stru-V-origin}
+        \includegraphics[width=\textwidth]{stru-V-origin.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{stru-my-origin}
+        \includegraphics[width=\textwidth]{stru-my-origin.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{ef-topo}
+        \includegraphics[width=\textwidth]{ef-topo.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{ef-sp1}
+        \includegraphics[width=\textwidth]{ef-sp1.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{ef-sp2}
+        \includegraphics[width=\textwidth]{ef-sp2.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{ef-sp3}
+        \includegraphics[width=\textwidth]{ef-sp3.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{ef-sp4}
+        \includegraphics[width=\textwidth]{ef-sp4.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{ef-mac}
+        \includegraphics[width=\textwidth]{ef-mac.png}
         \caption{}
@@
       1     & 2     & 3     & 1 \\
-      2     & 2$^{\rm a}$ or 1$^{\rm b}$ & 2     & 1 \\
+      2     & 2$^{\mathrm{a}}$ or 1$^{\mathrm{b}}$ & 2     & 1 \\
       3     & 1     & 1     & 1 \\
@@
       \\
-      \footnotesize{$^{\rm a}$ isolate two batteries within the same substructure, as shown in Figure \ref{fig:my-isolated-2b}}\\
-      \footnotesize{$^{\rm b}$ isolate one battery in each of the two substructures, as shown in Figure \ref{fig:my-isolated-2w}}
+      \footnotesize{$^{\mathrm{a}}$ isolate two batteries within the same substructure, as shown in Figure \ref{fig:my-isolated-2b}}\\
+      \footnotesize{$^{\mathrm{b}}$ isolate one battery in each of the two substructures, as shown in Figure \ref{fig:my-isolated-2w}}
   \end{table}
@@
       \begin{subfigure}[b]{0.31\textwidth}
-          \includegraphics[width=\textwidth]{my-isolated-1}
+          \includegraphics[width=\textwidth]{my-isolated-1.png}
           \caption{}
@@
       \begin{subfigure}[b]{0.31\textwidth}
-          \includegraphics[width=\textwidth]{my-isolated-2b}
+          \includegraphics[width=\textwidth]{my-isolated-2b.png}
           \caption{}
@@
       \begin{subfigure}[b]{0.31\textwidth}
-          \includegraphics[width=\textwidth]{my-isolated-2w}
+          \includegraphics[width=\textwidth]{my-isolated-2w.png}
           \caption{}
@@
       \begin{subfigure}[b]{0.31\textwidth}
-          \includegraphics[width=\textwidth]{my-isolated-3}
+          \includegraphics[width=\textwidth]{my-isolated-3.png}
           \caption{}

### 2023-09-01 paper/main.tex
添加并测试了修改使用的 changes 宏包；修正了 tex2docx 的部分bug
1. changes 在编译时运行正常，但在使用 pandoc 转 word 时无法正常显示。
2. tex2docx 生成的 docx 显示报错时优先删除流程图部分。

@@
+% tex2docx 报错时优先删除流程图部分图片
+
 % 0622 v3.0 plan
@@
 \def\T{\mathrm{T}}
-\graphicspath{ {../attachments/} }
+\graphicspath{ {./figures/} }
+
+% \usepackage[defaultcolor=red]{changes}
+% \added{xxx}
+% \deleted{xxxx}
+% \replaced{a}{b} 原文的b替换成a
+% \usepackage[final]{changes}
 
@@
 
-\author{3057761608 }
+\author{3057761608}
 
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{stru-V-origin} % 完整结构
+        \includegraphics[width=\textwidth]{stru-V-origin.png} % 完整结构
         \caption{}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{stru-V-serial} % 全串联
+        \includegraphics[width=\textwidth]{stru-V-serial.png} % 全串联
         \caption{}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{stru-V-parallel} % 全并联
+        \includegraphics[width=\textwidth]{stru-V-parallel.png} % 全并联
         \caption{}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{stru-V-isolate} % 电池隔离 右二 B3 全并联
+        \includegraphics[width=\textwidth]{stru-V-isolate.png} % 电池隔离 右二 B3 全并联
         \caption{}
@@
 }
-\begin{figure}
-\begin{tikzpicture}[font=\small, node font=\small, node distance=1.5em]
-    \node[punkt]     (input) {Input: RBS structure};
-    \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Eqs.\ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
-    \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Eq.\ref{eq:A}};
-    \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{set}=N_b$ };
-    \node[punkt, below=0.3of get_Nset] (get_cb) {get $c_b$s by combinating $N_{set}$ batteries from $N_b$};
-    \node[draw, diamond, aspect=2, below=0.3of get_cb] (is_check_all_cb) {are all $c_b$s checked?};
-    \node[draw, diamond, aspect=2, right=1of is_check_all_cb] (is_Nset_converged) {is $N_{set}$ converged?};
-    \node[punkt, above=of is_Nset_converged] (reset_Nset) {reset $N_{set}$ by dichotomy};
-    \node[punkt, text width=15em, below=0.3of is_check_all_cb] (get_Xs) {
-        select an unchecked $c_b$, and get its $\bm{X}_m$ by \\ 
-        if switch $j$ $\in \bigcup_{i\in c_b}SP_i$:\\
-        $\bm{X}[j]=1$ else $0$};
-    \node[punkt, below=0.3of get_Xs] (get_Yn) {get $\bm{Y}_n$ by Eq.\ref{eq:Yn}};
-    \node[draw, diamond, aspect=2, below=0.3of get_Yn] (is_Yn_invertible) {is $\bm{Y}_n$ invertible?};
-    \node[punkt, right=1.3of is_Yn_invertible] (construct) {construct an effective solution};
-    \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Eqs.\ref{eq:I_o} and \ref{eq:I_b}};
-    \node[draw, diamond, aspect=2, below=0.3of get_I] (is_leq_Im) {is $\max \bm{I}_b \leq I_m$?};
-    \node[punkt, right=1.3of is_leq_Im] (drop_eta) {drop this $\eta$};
-    \node[punkt, below=0.3of is_leq_Im] (get_eta) {get $\eta$ by Eq.\ref{eq:eta}};
-    \node[punkt, below=0.3of get_eta] (update_max_eta) {update $\max \eta$};
-    \node[punkt, right=1of is_Nset_converged] (output) {Output: $\max \eta$};
-    \node[round,left=1.5of update_max_eta](point1){};
-
-    \graph{
-      (input) -> (get_SP) -> (get_A) -> (get_Nset) -> (get_cb) -> (is_check_all_cb) ->["No"] (get_Xs) -> (get_Yn) -> (is_Yn_invertible) ->["Yes"] (get_I) -> (is_leq_Im) ->["Yes"] (get_eta) -> (update_max_eta);
-      (is_check_all_cb) ->["Yes"] (is_Nset_converged) ->["No"] (reset_Nset) -> (get_cb);
-      (is_Yn_invertible) ->["No"] (construct) ->[to path={|- (\tikztotarget)}] (get_I);
-      (is_leq_Im) ->["No"] (drop_eta) ->[to path={|- (\tikztotarget)}] (update_max_eta);
-      (is_Nset_converged) ->["Yes"] (output);
-      (update_max_eta) -- (point1) ->[to path={|- (\tikztotarget)}] (is_check_all_cb);
-    };
-\end{tikzpicture}
-\caption{The computational flowchart of the MAC for a given RBS.}\label{fig:flowchart}
-\end{figure}
+% \begin{figure}
+% \begin{tikzpicture}[font=\small, node font=\small, node distance=1.5em]
+%     \node[punkt]     (input) {Input: RBS structure};
+%     \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Eqs.\ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
+%     \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Eq.\ref{eq:A}};
+%     \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{set}=N_b$ };
+%     \node[punkt, below=0.3of get_Nset] (get_cb) {get $c_b$s by combinating $N_{set}$ batteries from $N_b$};
+%     \node[draw, diamond, aspect=2, below=0.3of get_cb] (is_check_all_cb) {are all $c_b$s checked?};
+%     \node[draw, diamond, aspect=2, right=1of is_check_all_cb] (is_Nset_converged) {is $N_{set}$ converged?};
+%     \node[punkt, above=of is_Nset_converged] (reset_Nset) {reset $N_{set}$ by dichotomy};
+%     \node[punkt, text width=15em, below=0.3of is_check_all_cb] (get_Xs) {
+%         select an unchecked $c_b$, and get its $\bm{X}_m$ by \\ 
+%         if switch $j$ $\in \bigcup_{i\in c_b}SP_i$:\\
+%         $\bm{X}[j]=1$ else $0$};
+%     \node[punkt, below=0.3of get_Xs] (get_Yn) {get $\bm{Y}_n$ by Eq.\ref{eq:Yn}};
+%     \node[draw, diamond, aspect=2, below=0.3of get_Yn] (is_Yn_invertible) {is $\bm{Y}_n$ invertible?};
+%     \node[punkt, right=1.3of is_Yn_invertible] (construct) {construct an effective solution};
+%     \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Eqs.\ref{eq:I_o} and \ref{eq:I_b}};
+%     \node[draw, diamond, aspect=2, below=0.3of get_I] (is_leq_Im) {is $\max \bm{I}_b \leq I_m$?};
+%     \node[punkt, right=1.3of is_leq_Im] (drop_eta) {drop this $\eta$};
+%     \node[punkt, below=0.3of is_leq_Im] (get_eta) {get $\eta$ by Eq.\ref{eq:eta}};
+%     \node[punkt, below=0.3of get_eta] (update_max_eta) {update $\max \eta$};
+%     \node[punkt, right=1of is_Nset_converged] (output) {Output: $\max \eta$};
+%     \node[round,left=1.5of update_max_eta](point1){};
+% 
+%     \graph{
+%       (input) -> (get_SP) -> (get_A) -> (get_Nset) -> (get_cb) -> (is_check_all_cb) ->["No"] (get_Xs) -> (get_Yn) -> (is_Yn_invertible) ->["Yes"] (get_I) -> (is_leq_Im) ->["Yes"] (get_eta) -> (update_max_eta);
+%       (is_check_all_cb) ->["Yes"] (is_Nset_converged) ->["No"] (reset_Nset) -> (get_cb);
+%       (is_Yn_invertible) ->["No"] (construct) ->[to path={|- (\tikztotarget)}] (get_I);
+%       (is_leq_Im) ->["No"] (drop_eta) ->[to path={|- (\tikztotarget)}] (update_max_eta);
+%       (is_Nset_converged) ->["Yes"] (output);
+%       (update_max_eta) -- (point1) ->[to path={|- (\tikztotarget)}] (is_check_all_cb);
+%     };
+% \end{tikzpicture}
+% \caption{The computational flowchart of the MAC for a given RBS.}\label{fig:flowchart}
+% \end{figure}
 
@@
     1     & 2     & 3     & 1 \\
-    2     & 2$^{\rm a}$ or 1$^{\rm b}$ & 2     & 1 \\
+    2     & 2$^{\mathrm{a}}$ or 1$^{\mathrm{b}}$ & 2     & 1 \\
     3     & 1     & 1     & 1 \\
@@
     \\
-    \footnotesize{$^{\rm a}$ isolate two batteries within the same substructure, as shown in Fig.\ref{fig:my-isolated-2b}}\\
-    \footnotesize{$^{\rm b}$ isolate one battery in each of the two substructures, as shown in Fig.\ref{fig:my-isolated-2w}}
+    \footnotesize{$^{\mathrm{a}}$ isolate two batteries within the same substructure, as shown in Fig.\ref{fig:my-isolated-2b}}\\
+    \footnotesize{$^{\mathrm{b}}$ isolate one battery in each of the two substructures, as shown in Fig.\ref{fig:my-isolated-2w}}
 \end{table}
@@
     \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{my-isolated-1}
+        \includegraphics[width=\textwidth]{my-isolated-1.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{my-isolated-2b}
+        \includegraphics[width=\textwidth]{my-isolated-2b.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{my-isolated-2w}
+        \includegraphics[width=\textwidth]{my-isolated-2w.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{my-isolated-3}
+        \includegraphics[width=\textwidth]{my-isolated-3.png}
         \caption{}

### 2023-09-10 paper/SST/SST_main.tex
按Q的意见修改了paper正文

@@
+% 【done】 按 Q 修改意见修改 0901 【优先】
+
+% 【done】
+% 2. 介绍修改，相关文献：
+%   2.1 RBS 结构分析相关的
+%   2.2 网络流（最大流）相关（但因为问题不同，无法使用，提一句穷举）
+% 3. 介绍修改，逐点列出我们的贡献：state research contribution and achievements as bullet points at the end of the Introduction section
+
+% 按 SST 修改意见修改 0902 【14号前交给润色机构】
+% 1. 摘要修改，量化我们的成果：explain the most important achievements of the proposed method quantitatively
+% 2. 介绍修改，相关文献：
+%   2.1 RBS 结构分析相关的
+%   2.2 网络流（最大流）相关（但因为问题不同，无法使用，提一句穷举）
+% 3. 介绍修改，逐点列出我们的贡献：state research contribution and achievements as bullet points at the end of the Introduction section
+% 4. 讨论修改，增加算法复杂度，以及和穷举法的比较（该领域尚为空白，没有sota的算法）
+% 5. 讨论修改，增加算法的 limitations（根据复杂度，大规模不好用）
+% 6. 讨论修改，增加结果的准确性介绍（和穷举结果比较）：explain about the accuracy, sufficiency and reliability of their results? How do they verify and validate the results
+% 7. 修改算法的第15步
+
 \documentclass{article}
@@
 % \usepackage[final]{changes}
-
-% 按 Q 修改意见修改 0901 【优先】
-% 按 SST 修改意见修改 0902 【14号前交给润色机构】
-% 1. 摘要修改，量化我们的成果：explain the most important achievements of the proposed method quantitatively
-% 2. 介绍修改，相关文献：
-%   2.1 RBS 结构分析相关的
-%   2.2 网络流（最大流）相关（但因为问题不同，无法使用，提一句穷举）
-% 3. 介绍修改，逐点列出我们的贡献：state research contribution and achievements as bullet points at the end of the Introduction section
-% 4. 讨论修改，增加算法复杂度，以及和穷举法的比较（该领域尚为空白，没有sota的算法）
-% 5. 讨论修改，增加算法的 limitations（根据复杂度，大规模不好用）
-% 6. 讨论修改，增加结果的准确性介绍（和穷举结果比较）：explain about the accuracy, sufficiency and reliability of their results? How do they verify and validate the results
 
@@
 However, traditional BESSs, in which the batteries are connected in a fixed topology, exhibit a significant weakness in their worst battery due to the so-called cask effect.
-Moreover, if this worst battery fails during operation, it can exacerbate the degradation of other batteries with a high possibility, leading to reliability and safety issues \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019,jeevarajanBatterySafetyQualifications2012}.
-These problems have become significant technical barriers in the development of new-generation space vehicles and urgently need to be addressed \cite{pomboHybridPowerSystem2021}.
+Moreover, if this worst battery fails \replaced{from}{during} operation, it can exacerbate the degradation of other batteries with a high possibility, leading to reliability and safety issues \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019,jeevarajanBatterySafetyQualifications2012}.
+These problems have become significant technical barriers in the development of new-generation space vehicles \replaced{unfortunately}{and urgently need to be addressed} \cite{pomboHybridPowerSystem2021}.
 
@@
 The complex connection structure between batteries and switches in the RBS provides flexibility but also introduces challenges in design and operational control. 
-Unlike traditional BESSs with fixed outputs, the RBS output must be dynamically adjusted by controlling switch states to meet external load requirements. 
+Unlike traditional BESSs with fixed outputs, the RBS \replaced{typology}{output} must be dynamically adjusted by controlling switch states to meet external load requirements. 
 This necessitates additional, time-consuming output performance analysis during design and corresponding control strategies. 
@@
 In particular, when one or more random cells are isolated, there is still no method to determine the MAC of the remaining RBS in time to assist the system in adjusting the control strategy timely. 
-A universal and automatical method for calculating RBS MAC is urgently needed for practical applications. 
+A \replaced{automatical and universal}{universal and automatical} method for calculating RBS MAC is \deleted{urgently} needed for practical applications. 
 In this study, a directed graph model and greedy algorithm are employed to determine the MAC of RBS and the corresponding control strategy, effectively calculating the MAC for RBSs with arbitrary structures, including scenarios with isolated batteries.
@@
 To universally and automatically achieve this, the overall process is divided into four steps, as shown in Figure \ref{fig:main}.
-Firstly, a directed graph model is established for subsequent computing, which not only contains the connected relationships between batteries and switches, but also retains the performance parameters of the batteries.
+Firstly, a directed graph model is established for subsequent \replaced{computations.}{computing,} \replaced{The model}{, which} not only contains the connected relationships between batteries and switches, but also retains the performance parameters of the batteries.
 Subsequently, based on the equivalent circuit, the MAC problem is transformed into specific objective functions and constraints.
@@
         \includegraphics[width=\textwidth]{main.png}
-        \caption{}
-        \label{fig:main}
     \end{subfigure}
@@
     }
+    \label{fig:main}
 \end{figure}
@@
     \caption{ 
-        Directed graph models used in (a) He's work \cite{heExploringAdaptiveReconfiguration2013}, (b) our previous work , and (c) this paper.
+        Directed graph models used in (a) He's work \cite{heExploringAdaptiveReconfiguration2013}, (b) our previous work , and (c) \added{the improved model in} this paper.
         (d) The equivalent circuit of a battery in this method.
@@
 \cite{heExploringAdaptiveReconfiguration2013} once proposed an abstracted directed graph model for RBS, where the nodes represented the batteries, the edges represented the configuration flexibility, and the weight of each vertex corresponded to the battery voltage ( Figure \ref{fig:direct-graph-he}).
-The model effectively captured all potential system configurations and offered a direct metric for configuration flexibility, but it did not specify the physical implementation of the connectivity between batteries, meaning one graph might have had multiple RBS structures.
-We previously proposed a novel directed graph model that, in contrast to He's model, used nodes to represent the connections between batteries and switches, and directed edges to represent batteries and switches (Figure \ref{fig:direct-graph-xu}), allowing for a one-to-one correspondence between the RBS structure and the directed graph model.
-This model was able to accurately and comprehensively represent the RBS topological structure but could not be used for quantitative MAC calculations due to the lack of consideration for battery and switch performance parameters.
-To address this, an improved directed graph model is used here based on our original model, adding electromotive force and resistance attributes on the edges based to equivalent circuits (Figure \ref{fig:direct-graph-my}).
+The model effectively captured all potential system configurations and offered a direct metric for configuration flexibility, but it did not specify the physical implementation of the connectivity between batteries, meaning one graph might \replaced{correspond to}{have had} multiple RBS structures.
+We previously proposed a novel directed graph model that, \replaced{completely different from}{in contrast to} He's model, used nodes to represent the connections between batteries and switches, and directed edges to represent batteries and switches (Figure \ref{fig:direct-graph-xu}), allowing for a one-to-one correspondence between the RBS structure and the directed graph model.
+This model was able to accurately and comprehensively represent the RBS topological structure but could not be used for quantitative MAC calculations due to the lack of consideration \replaced{on}{for} \replaced{the voltage, internal resistance and maximum allowable current of the battery}{battery and switch performance parameters}.
+To address this, an \replaced{improvement on our previous model is conducted by}{improved directed graph model is used here based on our original model,} adding electromotive force and resistance attributes on the edges based \replaced{on its}{to} equivalent circuits \deleted{(Figure \ref{fig:direct-graph-my})}.
 The model also considers the external load as an equivalent resistance and integrate it into the analysis, making it a complete circuit model for later circuit analysis.
+\added{Figure \ref{fig:direct-graph-my} shows the improved directed graph model used in this paper.}
 The following will provide a detailed explanation of the method for equating the components in RBS and constructing the directed graph model.
@@
 In order to use circuit analysis methods to solve the MAC of the RBS, the components in the RBS are equated to ideal circuit elements.
-As shown in Figure \ref{fig:battery_simple}, the battery in the RBS can be represented as a black-box circuit consisting of two resistors (i.e., $r_1$ and $r_2$) and a capacitor (i.e., $C$), known as the Thevenin model\cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
+\added{For instance,} \replaced{a}{A}s shown in Figure \ref{fig:battery_simple}, the battery in the RBS can be represented as a black-box circuit consisting of two resistors (i.e., $r_1$ and $r_2$) and a capacitor (i.e., $C$), known as the Thevenin model\cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
 With an emphasis on the stable output of the RBS, the capacitor in the Thevenin model can be considered as an open circuit without affecting the steady-state current.
@@
 
-For a given RBS structure, the directed graph model for the RBS is constructed as a directed graph $G(V,E)$ in such a way that:
+For a given RBS structure, \replaced{its directed graph model $G(V,E)$ is constructed as follows:}{the directed graph model for the RBS is constructed as a directed graph $G(V,E)$ in such a way that:}
 \begin{enumerate}
@@
 
-Based on the definition of MAC, determining the MAC of RBS involves maximizing the RBS output current while ensuring that the currents of all batteries do not exceed the batteries' maximum allowable current.
-In this subsection, the constraints and objective function to solve the RBS's MAC will be established through circuit analysis, based on the previously constructed directed graph model.
+\replaced{For a given RBS, determination of its MAC}{Based on the definition of MAC, determining the MAC of RBS} involves maximizing the RBS output current while ensuring that the currents of all batteries do not exceed the batteries' maximum allowable current.
+In this subsection, the constraints and objective function to solve the RBS's MAC will be established through circuit analysis, based on \replaced{its directed graph model provided in the previous subsection}{the previously constructed directed graph model}.
 
-First, the topology in the directed graph model is represented in matrix form $\bm{A}$, known as the incidence matrix , to facilitate circuit analysis.
-The specific definition of the incidence matrix is shown in Equation \ref{eq:A}.
+First, the topology in the directed graph model is represented in matrix form $\bm{A}$, known as the incidence matrix , \replaced{defined}{to facilitate circuit analysis.
+The specific definition of the incidence matrix is shown} in Equation \ref{eq:A}.
 \begin{align}\label{eq:A}
@@
 Since each directed edge has one node to leave and one to enter, the sum of the values in every column of $\bm{A}$ is zero.
-Therefore removing any single one row will not result in a loss of information. 
-Without loss of generality, the last row is removed here.
+Therefore removing \replaced{the last}{any single one} row will not result in a loss of information. 
+\deleted{Without loss of generality, the last row is removed here.}
 On the other hand, since each switch in the RBS is represented by a pair of directed edges with two-way directions, the two columns corresponding to the switch are mutually opposite.
@@
 while the elements of the array $\bm{U}_s$ are equal to the first attribute of the corresponding edges in the directed graph.
-The $\bm{Y}$ in \ref{eq:generalized_branches} is the admittance matrix of the circuit, defined as the inverse of the impedance matrix.
-That is the elements of the diagonal matrix $\bm{Y}$ are equal to the reciprocal of the second attribute of the corresponding edges in the directed graph, and the off-diagonal elements are 0.
+The $\bm{Y}$ in \added{Equation} \ref{eq:generalized_branches} is the admittance matrix of the circuit, defined as the inverse of the impedance matrix.
+\replaced{The}{That is the} elements \replaced{on}{of} the diagonal \added{of} matrix $\bm{Y}$ are equal to the reciprocal of \added{the resistance, which is} the second attribute of the corresponding edges in the directed graph, and the off-diagonal elements \added{$\bm{Y}$} are 0.
 The $\bm{X}$ is the state matrix, which describes whether the RBS batteries and switches are allowed to pass current.
@@
 
-However, it is computationally difficult to solve \ref{eq:max_eta} because of the $\bm{Y}_n^{-1}$.
-On one hand, due to the introduction of nonlinear terms by $\bm{Y}_n^{-1}$, many effective methods in linear optimization are not suitable for this problem.
+However, it is \added{still} computationally difficult to solve \ref{eq:max_eta} because of the $\bm{Y}_n^{-1}$.
+On one hand, due to the introduction of nonlinear terms by $\bm{Y}_n^{-1}$, many effective methods in linear optimization are not suitable for this \replaced{scenario}{problem}.
 On the other hand, the rank of $Y_{n}$ is proportional to the number of batteries and switches, which can be very large for a large RBS system, leading to significant computational burden.
-Therefore, intelligent algorithms that rely on evolving by iteration may face efficiency issues when dealing with large RBS system.
+Therefore, intelligent algorithms that rely on evolving by iteration may face efficiency \replaced{problem}{issues} when dealing with large RBS system.
 In order to address this issue, the problem should be considered from the perspective of guiding the RBS to reconstruct as many parallel structures as possible.
@@
 \cite{visairoReconfigurableBatteryPack2008} and Lawson et al.
-\cite{lawsonSoftwareConfigurableBattery2012}, both of which have been applied in practice.
-The primary goal of Visairo's structure (Figure \ref{fig:study-stru-Visairo}) was to achieve dynamic adjustment of RBS output; however, the isolation of unhealthy batteries was not sufficiently addressed.
-When batteries need to be isolated in the RBS of Visairo's structure, the methods for isolating them and the subsequent changes in RBS output warrant further investigation.
-Lawson et al. conducted research on battery isolation in RBS and specifically designed the structure shown in Figure \ref{fig:study-stru-Lawson}. 
+\cite{lawsonSoftwareConfigurableBattery2012}, both of which have been \replaced{practically used}{applied in practice}.
+The primary goal of Visairo's structure (Figure \ref{fig:study-stru-Visairo}) was to achieve dynamic adjustment of RBS output \added{power}; however, the isolation of unhealthy batteries was not sufficiently addressed \added{in their work}.
+\deleted{When batteries need to be isolated in the RBS of Visairo's structure, the methods for isolating them and the subsequent changes in RBS output warrant further investigation.}
+Lawson et al.
+\replaced{designed the RBS structure shown in Figure \ref{fig:study-stru-Lawson} for the purpose of battery isolation}{conducted research on battery isolation in RBS and specifically designed the structure shown in Figure \ref{fig:study-stru-Lawson}}.
 This structure has the advantage of easily isolating batteries, but it cannot dynamically adjust the output current of RBS. 
-Based on the structures of Visairo and Lawson, this paper presents a new structure, as shown in Figure \ref{fig:study-stru-my}, which combines the advantages of both.
+Based on the structures of Visairo and Lawson, this paper presents a new structure, as shown in Figure \ref{fig:study-stru-my}\deleted{, which combines the advantages of both}.
 By integrating the Visairo RBS structure into the Lawson RBS structure, the new structure not only allows the flexibility to switch the batteries between series, parallel, and mixed series-parallel modes, but also easily enables the isolation of highly degraded batteries from the RBS.
@@
 
-Furthermore, the RBS under the scenario of isolated batteries is taken into consideration and calculated. 
+Furthermore, the RBS \replaced{with}{under the scenario of} isolated batteries is taken into consideration and calculated. 
 The MAC calculation results for the three structures under study, with varying numbers of isolated batteries, are presented in Table \ref{tab:isolated_mac}. 
 Figures \ref{fig:my-isolated-1}-\ref{fig:my-isolated-3} illustrate the corresponding switch control schemes for the new structure proposed in this paper under different isolated battery conditions.
-The characteristics of these three structures in the context of battery isolation will be discussed in the next subsection.
+\deleted{The characteristics of these three structures in the context of battery isolation will be discussed in the next subsection.}
 
@@
 
-In this subsection, we firstly discuss the correctness of the results presented in Figure \ref{fig:all-results-my} and Table \ref{tab:study-results-my}. 
+\deleted{In this subsection, we firstly discuss the correctness of the results presented in Figure \ref{fig:all-results-my} and Table \ref{tab:study-results-my}.} 
 When $B_1$ and $B_2$ or $B_3$ and $B_4$ are connected in parallel, the RBS can output the maximum current, which is $\eta=2$, i.e., twice the current output of a single battery in RBS. 
@@
 
-It is important to note that when solving for MAC, $\eta$ is used as the objective function instead of $I_o$. 
+It is important to note that \deleted{when solving for MAC,} $\eta$ is used as the objective function instead of $I_o$ \added{in solving MAC}. 
 This choice makes the result of MAC more reasonable. 
 As shown in Table \ref{tab:study-results-my}, $I_o$ and $\bm{I}_b$ are functions of $R_o$, $u_b$, and $r_b$. 
-If $I_o$ were used as the objective function, even for the same RBS structure, the MAC result and corresponding switches state could change due to different external electrical appliances.
+\replaced{However, when}{If} $I_o$ \replaced{was}{were} used as the objective function, even for the same RBS structure, the MAC \replaced{solution}{result} and corresponding switches state could change due to different external electrical appliances.
 It would increase the difficulty and uncertainty in RBS structure design. 
-In contrast, by using $\eta$ as the objective function, which is defined as the ratio of $I_o$ and $\max\bm{I}_b$, the influence of these factors on the results can be eliminated. 
+\replaced{In order to eliminate the influences of such a problem, $\eta$, which is the ratio of $I_o$ and $\max\bm{I}_b$, is adopted as the objective function in our research.}{In contrast, by using $\eta$ as the objective function, which is defined as the ratio of $I_o$ and $\max\bm{I}_b$, the influence of these factors on the results can be eliminated.}
 $\eta$ solely reflects the maximum output current capability of the RBS structure. 
 Assuming that the maximum allowed current of batteries in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by determining the $\eta$ of the structure. 
-Therefore, compared to $I_o$, $\eta$ is more suitable for structure design.
+\deleted{Therefore, compared to $I_o$, $\eta$ is more suitable for structure design.}
 
-The method proposed in this paper is significant for the design of next-generation RBSs in the following aspects.
+The method proposed in this paper is significant for the design of \deleted{next-generation} RBSs in the following aspects.
 Most of the currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} exhibit simple topological characteristics, and the calculation of MACs is relatively straightforward, even intuitive.
 However, these simple structures do not always fully satisfy the requirements of complex applications, such as dynamically adapting the circuit to variable and random operating conditions, and actively equalizing differences among the batteries in the RBS.
-Moreover, isolating the batteries disrupts the original regularity and symmetry of the topology, which complicates the otherwise simple structure, and the maximum output current of the system becomes more challenging to obtain.
-Owing to the advantages of pervasiveness and automation, the proposed method can be employed to calculate the MAC of arbitrary RBS structures, which helps to address the aforementioned issues and paves the way for more complex and flexible RBS structure design.
+Moreover, \replaced{isolation of}{isolating} the batteries disrupts the original regularity and symmetry of the topology, which complicates the otherwise simple structure, and the maximum output current of the system becomes more challenging to obtain.
+\replaced{On the contrary}{Owing to the advantages of pervasiveness and automation}, the proposed method can be employed to calculate the MAC of arbitrary RBS structures, \replaced{especially for these above complex and flexible RBS structures}{which helps to address the aforementioned issues and paves the way for more complex and flexible RBS structure design}.
 
-To illustrate this point, the MACs of the three RBS structures mentioned above are calculated after the batteries are isolated, as shown in Table \ref{tab:isolated_mac}. 
-Specifically, for the structure presented in Figure \ref{fig:study-stru-my}, the corresponding circuit states of MACs when isolating different numbers of batteries are depicted in Figures \ref{fig:my-isolated-1}-\ref{fig:my-isolated-3}.
+To illustrate this point, the MACs of \deleted{the} three RBS structures mentioned above are calculated after \replaced{one and more}{the} batteries are isolated, as shown in Table \ref{tab:isolated_mac}.
+Specifically, for the structure presented in Figure \ref{fig:study-stru-my}, the corresponding circuit states of MACs \replaced{of}{when} isolating \replaced{one to three}{different numbers of} batteries are depicted in Figures \ref{fig:my-isolated-1}-\ref{fig:my-isolated-3}.
 This structure has two cases of isolating two batteries: 
 one is to isolate two batteries within the same substructure (Figure \ref{fig:my-isolated-2b}), in which case $\eta=2$; the other is to isolate one battery in each of the two substructures (Figure \ref{fig:my-isolated-2w}), in which case $\eta=1$.
-From the results, it can be observed that the proposed method provides reasonable outcomes for isolating batteries with any number and position.
+From the results \added{shown in Figure \ref{fig:my-isolated-1}-\ref{fig:my-isolated-3}}, it can be observed that the proposed method provides reasonable outcomes for isolating batteries with any number and position.
 
-Furthermore, the performance of output current for the three RBS when isolating batteries is also shown in Table \ref{tab:isolated_mac}. 
-For the structure proposed by Lawson et al., the MAC remains the same as that without isolated battery cells, i.e., $\eta=1$, when the number of isolated battery cells increases, until all the cells in the RBS are isolated.
-For Visairo's structure, the MAC decreases as the number of isolated battery cells increases, until $\eta=0$. 
-In contrast, the MAC of the structure proposed in this work is positioned between the two structures. 
-This indicates that the structure proposed in this paper, compared to Lawson's structure, has a larger MAC under the same number of batteries, which means a wider output current regulation range. 
-On the other hand, by simply changing the states of $S_2$, $S_4$, $S_{11}$, and $S_{12}$ in the conversion structure, this structure can address the majority of battery isolation scenarios, whereas Visairo's structure requires specific battery targeting and switch control.
-In summary, the structure proposed in this paper has the advantages of both Lawson's and Visairo's structures.
+Furthermore, the \deleted{performance of} output current for the three RBS \replaced{with isolated}{when isolating} batteries is also shown in Table \ref{tab:isolated_mac}. 
+For the structure proposed by Lawson et al., the MAC \replaced{is independent on the number of isolated batteries}{remains the same as that without isolated battery cells, i.e., $\eta=1$, when the number of isolated battery cells increases, until all the cells in the RBS are isolated}.
+\added{However,} \replaced{f}{F}or Visairo's structure, the MAC decreases \replaced{with the increasing number of isolated batteries}{as the number of isolated battery cells increases, until $\eta=0$}.
+\replaced{Nevertherless}{In contrast}, the MAC of the structure proposed in this work is positioned between \replaced{these above}{the} two structures. 
+This indicates that the structure proposed in this paper, compared to Lawson's structure, has a larger MAC under the same number of batteries, \replaced{and exhibits}{which means} a wider output current regulation range.
+\deleted{On the other hand, by simply changing the states of $S_2$, $S_4$, $S_{11}$, and $S_{12}$ in the conversion structure, this structure can address the majority of battery isolation scenarios, whereas Visairo's structure requires specific battery targeting and switch control.}
+\deleted{In summary, the structure proposed in this paper has the advantages of both Lawson's and Visairo's structures.}
 
@@
 
-This paper proposes a pervasive and automatical method for computing the MAC of the given RBS.
-The method is  implemented by a greedy algorithm combined with a directed graph model, whose effectiveness is tested on a novel and complex RBS structure.
-The method remains effective for the application scenario of RBS battery isolation and demonstrates that the novel structure has the advantage on flexible output current and convenient battery isolation.
-Future research could focus on developing new indictors to evaluate the performance of the RBS with the currents and voltages obtained by the method, as well as modifying the equivalent model of the battery to allow for more accurate simulations of the RBS, including transient analysis.
+This paper proposes a pervasive and automatical method for computing the MAC of \replaced{a}{the} given RBS.
+The method is  implemented by a greedy algorithm combined with a directed graph model, \replaced{and}{whose effectiveness is tested on a novel and complex RBS structure.
+The method} remains effective for the application scenario of \replaced{the RBS system with a complex structure and isolated batteries}{RBS battery isolation and demonstrates that the novel structure has the advantage on flexible output current and convenient battery isolation}.
+\deleted{Future research could focus on developing new indictors to evaluate the performance of the RBS with the currents and voltages obtained by the method, as well as modifying the equivalent model of the battery to allow for more accurate simulations of the RBS, including transient analysis.}
+% #TODO 补充我们方法的优势和先进之处；强调可以计算随机隔离电池情况下的RBS结构的MAC
 

### 2023-09-11 paper/SST/simple.tex
完成了正文修改

--- 2023-09-10 paper/SST/SST_main.tex
@@
-% 【done】 按 Q 修改意见修改 0901 【优先】
-
-% 【done】
-% 2. 介绍修改，相关文献：
-%   2.1 RBS 结构分析相关的
-%   2.2 网络流（最大流）相关（但因为问题不同，无法使用，提一句穷举）
-% 3. 介绍修改，逐点列出我们的贡献：state research contribution and achievements as bullet points at the end of the Introduction section
-
-% 按 SST 修改意见修改 0902 【14号前交给润色机构】
-% 1. 摘要修改，量化我们的成果：explain the most important achievements of the proposed method quantitatively
-% 2. 介绍修改，相关文献：
-%   2.1 RBS 结构分析相关的
-%   2.2 网络流（最大流）相关（但因为问题不同，无法使用，提一句穷举）
-% 3. 介绍修改，逐点列出我们的贡献：state research contribution and achievements as bullet points at the end of the Introduction section
-% 4. 讨论修改，增加算法复杂度，以及和穷举法的比较（该领域尚为空白，没有sota的算法）
-% 5. 讨论修改，增加算法的 limitations（根据复杂度，大规模不好用）
-% 6. 讨论修改，增加结果的准确性介绍（和穷举结果比较）：explain about the accuracy, sufficiency and reliability of their results? How do they verify and validate the results
-% 7. 修改算法的第15步
-
 \documentclass{article}
@@
 \usepackage[defaultcolor=red]{changes}
-% \added{xxx}
-% \deleted{xxxx}
-% \replaced{a}{b} 原文的b替换成a
-% \usepackage[final]{changes}
-
-%%%%%% Bibliography %%%%%%
-% Replace "sample" in the \addbibresource line below with the name of your .bib file.
-% \usepackage[style=nejm, 
-% citestyle=numeric-comp,
-% sorting=none]{biblatex}
-% \addbibresource{main.bib}
-
-%%%%%% Title %%%%%%
-% Full titles can be a maximum of 100 characters, including spaces. 
-% Title Format: Use title case, capitalizing the first letter of each word, except for certain small words, such as articles and short prepositions
-\title{Maximum Allowable Current Determination of RBS By Using a Directed Graph Model and Greedy Algorithm}
-
-%%%%%% Authors %%%%%%
-% Authors should be listed in order of contribution to the paper, by first name, then middle initial (if any), followed by last name.
-% Authors should be listed in the order in which they will appear in the published version if the manuscript is accepted. 
-% Use an asterisk (*) to identify the corresponding author, and be sure to include that person’s e-mail address.
-Use symbols (in this order: †, ‡, §, ||, ¶, #, ††, ‡‡, etc.) for author notes, such as present addresses, “These authors contributed equally to this work” notations, and similar information.
-% You can include group authors, but please include a list of the actual authors (the group members) in the Supplementary Materials.
-\author[1$\dag$]{Binghui Xu}
-\author[1$\dag$]{Guangbin Hua}
-\author[1*]{Cheng Qian}
-\author[1,2]{Quan Xia}
-\author[1]{Bo Sun}
-\author[1]{Yi Ren}
-\author[1]{Zili Wang}
-
-%%%%%% Affiliations %%%%%%
-\affil[1]{School of Reliability and Systems Engineering, Beihang University, Beijing, 100191, China}
-\affil[2]{School of Aeronautic Science and Engineering at Beihang University, Beijing, China}
-\affil[*]{Address correspondence to: cqian@buaa.edu.cn}
-\affil[$\dag$]{These authors contributed equally to this work.}
-
-%%%%%% Date %%%%%%
-% Date is optional
-\date{}
-
-%%%%%% Spacing %%%%%%
-% Use paragraph spacing of 1.5 or 2 (for double spacing, use command \doublespacing)
-\onehalfspacing
-
-\begin{document}
-
-\maketitle
 
@@
     \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{stru-V-origin.png}
-        \caption{}
-        \label{fig:stru-Visairo}
-    \end{subfigure}
-    \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{stru-V-serial.png}
-        \caption{}
-        \label{fig:stru-Visairo-serial}
-    \end{subfigure}
-    \\
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{stru-V-parallel.png}
-        \caption{}
-        \label{fig:stru-Visairo-parallel}
-    \end{subfigure}
-    \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{stru-V-isolate.png}
-        \caption{}
-        \label{fig:stru-Visairo-isolate}
-    \end{subfigure}
     \caption{
@@
 Therefore, it provides a benchmark for RBS output current, protecting individual batteries and identifying overall system output limits during operation. 
-Despite its importance, no method currently exists for automatically evaluating MAC for RBSs.
+\deleted{Despite its importance, no method currently exists for automatically evaluating MAC for RBSs.
 In particular, when one or more random cells are isolated, there is still no method to determine the MAC of the remaining RBS in time to assist the system in adjusting the control strategy timely. 
-A \replaced{automatical and universal}{universal and automatical} method for calculating RBS MAC is \deleted{urgently} needed for practical applications. 
-In this study, a directed graph model and greedy algorithm are employed to determine the MAC of RBS and the corresponding control strategy, effectively calculating the MAC for RBSs with arbitrary structures, including scenarios with isolated batteries.
+A universal and automatical method for calculating RBS MAC is urgently needed for practical applications.}
+
+\added{To calculate the MAC of a given RBS, an analysis of the RBS's topology is required, and the voltage, internal resistance, and maximum allowable current of the battery should be taken into account meanwhile.
+Currently, the RBS's topology analysis is mainly dependent on methods and algorithms from graph theory.
+For instance, Chen et al.
+\cite{chenSneakCircuitTheory2021} proposed a systematic approach based on the sneak circuit theory is proposed to fundamentally avoid the short-circuit problem of reconfigurable battery systems.
+This research traverses and analyzes all paths between the positive and negative terminals of each battery in the RBS, and identifies paths that only contain switches as short-circuit paths to form a short-circuit path table for pre-check and before system reconfiguration.
+The maximum flow problem (MFP) in graph theory has a similar formulation to the problem on MAC. 
+MFP is defined as finding the path with the maximum flow in a network flow with a single source node and a single sink node.
+In the RBS, the system positive and negative terminals can be taken as the source and sink nodes respectively, and the current can be regarded as the flow of the graph. 
+However, the Kirchhoff's laws that describe the current in circuit , and the function of switches to control the circuit on-off should be translated into constraints in the MFP, resulting in a special maximum flow problem.
+Despite mature algorithms for the MFP, such as the Edmonds-Karp algorithm and Dinic's blocking flow algorithm, these algorithms cannot be directly applied to solve the MAC due to the speciality of the problem.
+Moreover, these algorithms need to traverse all switch states to calculate the MAC comprehensively, which means high computational complexity and not suitable for large-scale RBS.}
+
+\added{The main contributions of the paper can be summarized as follows:}
+\deleted{In this study, a directed graph model and greedy algorithm are employed to determine the MAC of RBS and the corresponding control strategy, effectively calculating the MAC for RBSs with arbitrary structures, including scenarios with isolated batteries.}
+\begin{itemize}
+  \item \added{Application of the greedy algorithm to solving the MAC of a given RBS for the first time.}
+  \item \added{Presenting a improved directed graph model that considers the voltage, internal resistance, and maximum allowable current of the battery, and the external load.}
+  \item \added{Proposing a new RBS structure and analysing three RBS structures' MAC with random battery isolation.}
+\end{itemize}
 
@@
     \centering
-    \begin{subfigure}[b]{0.8\textwidth}
-        \includegraphics[width=\textwidth]{main.png}
-    \end{subfigure}
+
     \caption{ 
@@
     \centering
-    \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{direct-graph-he.png}
-        \caption{}
-        \label{fig:direct-graph-he}
-    \end{subfigure}
-    \hspace{0.02\textwidth}
-    \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{direct-graph-xu.png}
-        \caption{}
-        \label{fig:direct-graph-xu}
-    \end{subfigure}
-    \hspace{0.02\textwidth}
-    \begin{subfigure}[b]{0.24\textwidth}
-        \includegraphics[width=\textwidth]{direct-graph-my.png}
-        \caption{}
-        \label{fig:direct-graph-my}
-    \end{subfigure}
-    \\
-    \begin{subfigure}[b]{0.8\textwidth}
-        \includegraphics[width=\textwidth]{battery_simple.png}
-        \caption{}
-        \label{fig:battery_simple}
-    \end{subfigure}
+
     \caption{ 
@@
 
-\tikzset{
-  meta box/.style={draw, black, very thick, text centered, },
-  punkt/.style={meta box, rectangle, rounded corners, inner sep=.25em, minimum height=2em, minimum width=4em, align=center, text width=10em },
-  round/.style={meta box, circle, minimum size=0, inner sep=0pt, outer sep=0pt },
-  every fit/.style={draw, thick, dashed, gray, inner xsep=.5em, inner ysep=.75em }
-}
 \begin{figure}
-\begin{tikzpicture}[font=\small, node font=\small, node distance=1.5em]
-    \node[punkt]     (input) {Input: RBS structure};
-    \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Equations \ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
-    \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Equation \ref{eq:A}};
-    \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{set}=N_b$ };
-    \node[punkt, below=0.3of get_Nset] (get_cb) {get $c_b$s by combinating $N_{set}$ batteries from $N_b$};
-    \node[draw, diamond, aspect=2, below=0.3of get_cb] (is_check_all_cb) {are all $c_b$s checked?};
-    \node[draw, diamond, aspect=2, right=1of is_check_all_cb] (is_Nset_converged) {is $N_{set}$ converged?};
-    \node[punkt, above=of is_Nset_converged] (reset_Nset) {reset $N_{set}$ by dichotomy};
-    \node[punkt, text width=15em, below=0.3of is_check_all_cb] (get_Xs) {
-        select an unchecked $c_b$, and get its $\bm{X}_m$ by \\ 
-        if switch $j$ $\in \bigcup_{i\in c_b}SP_i$:\\
-        $\bm{X}[j]=1$ else $0$};
-    \node[punkt, below=0.3of get_Xs] (get_Yn) {get $\bm{Y}_n$ by Equation \ref{eq:Yn}};
-    \node[draw, diamond, aspect=2, below=0.3of get_Yn] (is_Yn_invertible) {is $\bm{Y}_n$ invertible?};
-    \node[punkt, right=1.3of is_Yn_invertible] (construct) {construct an effective solution};
-    \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Equations \ref{eq:I_o} and \ref{eq:I_b}};
-    \node[draw, diamond, aspect=2, below=0.3of get_I] (is_leq_Im) {is $\max \bm{I}_b \leq I_m$?};
-    \node[punkt, right=1.3of is_leq_Im] (drop_eta) {drop this $\eta$};
-    \node[punkt, below=0.3of is_leq_Im] (get_eta) {get $\eta$ by Equation \ref{eq:eta}};
-    \node[punkt, below=0.3of get_eta] (update_max_eta) {update $\max \eta$};
-    \node[punkt, right=1of is_Nset_converged] (output) {Output: $\max \eta$};
-    \node[round,left=1.5of update_max_eta](point1){};
 
-    \graph{
-      (input) -> (get_SP) -> (get_A) -> (get_Nset) -> (get_cb) -> (is_check_all_cb) ->["No"] (get_Xs) -> (get_Yn) -> (is_Yn_invertible) ->["Yes"] (get_I) -> (is_leq_Im) ->["Yes"] (get_eta) -> (update_max_eta);
-      (is_check_all_cb) ->["Yes"] (is_Nset_converged) ->["No"] (reset_Nset) -> (get_cb);
-      (is_Yn_invertible) ->["No"] (construct) ->[to path={|- (\tikztotarget)}] (get_I);
-      (is_leq_Im) ->["No"] (drop_eta) ->[to path={|- (\tikztotarget)}] (update_max_eta);
-      (is_Nset_converged) ->["Yes"] (output);
-      (update_max_eta) -- (point1) ->[to path={|- (\tikztotarget)}] (is_check_all_cb);
-    };
-\end{tikzpicture}
 \caption{The computational flowchart of the MAC for a given RBS.}\label{fig:flowchart}
@@
     \centering
-    \begin{subfigure}[b]{0.2\textwidth}
-        \includegraphics[width=\textwidth]{stru-L-origin.png}
-        \caption{}
-        \label{fig:study-stru-Lawson}
-    \end{subfigure}
-    \hspace{0.02\textwidth}
-    \begin{subfigure}[b]{0.4\textwidth}
-        \includegraphics[width=\textwidth]{stru-V-origin.png}
-        \caption{}
-        \label{fig:study-stru-Visairo}
-    \end{subfigure}
-    \hspace{0.02\textwidth}
-    \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{stru-my-origin.png}
-        \caption{}
-        \label{fig:study-stru-my}
-    \end{subfigure}
+
     \caption{The 4-battery RBS structures proposed by (a)Lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b)Visairo\cite{visairoReconfigurableBatteryPack2008} and (c)this paper.}
@@
     \centering
-    \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{ef-topo.png}
-        \caption{}
-        \label{fig:study-dirgraph-my}
-    \end{subfigure}
-    \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{ef-sp1.png}
-        \caption{}
-        \label{fig:sp1}
-    \end{subfigure}
-    \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{ef-sp2.png}
-        \caption{}
-        \label{fig:sp2}
-    \end{subfigure}
-    \\
-    \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{ef-sp3.png}
-        \caption{}
-        \label{fig:sp3}
-    \end{subfigure}
-    \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{ef-sp4.png}
-        \caption{}
-        \label{fig:sp4}
-    \end{subfigure}
-    \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{ef-mac.png}
-        \caption{}
-        \label{fig:study-results-my}
-    \end{subfigure}
+
     \caption{
@@
     $\bm{I}_b$ & $[u_b/(2R_o+r_b),u_b/(2R_o+r_b),0,0]$ \\
-    $\eta$     & 2 \\
+    \added{$\max$}$\eta$     & 2 \\
     \bottomrule
@@
 Similarly, the MAC calculation results of the structures in Figures \ref{fig:study-stru-Lawson} and \ref{fig:study-stru-Visairo} are shown as Table \ref{tab:study-results-Lawson} and Table \ref{tab:study-results-Visairo}, respectively.
+\added{
+In order to verify and compare the results from the greedy algorithm, we also utilized an algorithm that iterates through all possible switch states to calculate the MAC of the same three RBS. 
+For a given RBS structure with $N_s$ switches, the final $\max$ $\eta$ is the maximum of $\eta$s from all $2^{N_s}$ reconfigured structures.
+The obtained results are the same as the results shown in Tables \ref{tab:study-results-my}-\ref{tab:study-results-Visairo}.
+}
 
@@
     $\bm{I}_b$ & $[u_b/(R_o+r_b),0,0,0]$ \\
-    $\eta$     & 1 \\
+    \added{$\max$}$\eta$     & 1 \\
     \bottomrule
@@
     $\bm{I}_b$ & $[u_b/(4R_o+r_b),u_b/(4R_o+r_b),u_b/(4R_o+r_b),u_b/(4R_o+r_b)]$ \\
-    $\eta$     & 4 \\
+    \added{$\max$}$\eta$     & 4 \\
     \bottomrule
@@
       \centering
-      \begin{subfigure}[b]{0.31\textwidth}
-          \includegraphics[width=\textwidth]{my-isolated-1.png}
-          \caption{}
-          \label{fig:my-isolated-1}
-      \end{subfigure}
-      \hspace{0.02\textwidth}
-      \begin{subfigure}[b]{0.31\textwidth}
-          \includegraphics[width=\textwidth]{my-isolated-2b.png}
-          \caption{}
-          \label{fig:my-isolated-2b}
-      \end{subfigure}
-      \\
-      \begin{subfigure}[b]{0.31\textwidth}
-          \includegraphics[width=\textwidth]{my-isolated-2w.png}
-          \caption{}
-          \label{fig:my-isolated-2w}
-      \end{subfigure}
-      \hspace{0.02\textwidth}
-      \begin{subfigure}[b]{0.31\textwidth}
-          \includegraphics[width=\textwidth]{my-isolated-3.png}
-          \caption{}
-          \label{fig:my-isolated-3}
-      \end{subfigure}
+
       \caption{
@@
 
-\deleted{In this subsection, we firstly discuss the correctness of the results presented in Figure \ref{fig:all-results-my} and Table \ref{tab:study-results-my}.} 
+\replaced{As shown in Figure \ref{fig:all-results-my} and Table \ref{tab:study-results-my}}{In this subsection, we firstly discuss the correctness of the results presented in Figure \ref{fig:all-results-my} and Table \ref{tab:study-results-my}}.
 When $B_1$ and $B_2$ or $B_3$ and $B_4$ are connected in parallel, the RBS can output the maximum current, which is $\eta=2$, i.e., twice the current output of a single battery in RBS. 
@@
 Therefore, the switches state given in Table \ref{tab:study-results-my} can make the RBS output current reach the maximum.
+\added{
+The results of MAC obtained by traversing all reconfigured structures is identical to the one by the greedy algorithm. 
+This further validates the algorithm we proposed.
+From the literature search we have conducted, no formal report on the algorithm for MAC in RBS has been found yet.
+Therefore, the time complexity of the proposed algorithm is analyzed and compared with the algorithm that traverses all reconfigured structures to demonstrate the advantage of this algorithm.
+Assuming that a RBS has $N_b$ batteries and $N_s$ switches, and the corresponding directed graph has $N$ nodes, it requires $2^{N_s}$ iterations to traverse all reconfigured structures.
+The calculation for each reconfigured structure by Equations \ref{eq:I_o}-\ref{eq:eta} requires matrix inversion and matrix multiplication, with a time complexity of $O(N^3+2N^2N_b+N^2N_s+NN^2_b)$.
+Therefore, the time complexity of the algorithm that traverses all reconfigured structures is $O(2^{N_s}(N^3+2N^2N_b+N^2N_s+NN^2_b))$.
+The greedy algorithm proposed in this paper requires find the SP for each battery, which requires $N_b$ iterations.
+Each SP can be obtained by two Dijkstra algorithms.
+Therefore, the total time complexity of calculating all SPs is $O(2N_b(N_b+2N_s)\log N)$.
+According to the Appendix \ref{alg:greedy}, $C^{N_{set}}_{N_b}$ structures can be reconfigured by selecting $N_{set}$ batteries from $N_b$ batteries, which is $\sum^{N_b}_{N_{set}=1}C^{N_{set}}_{N_b}/N_b \approx 2^{N_b}/N_b$ on average.
+Hence, with bisection method, the time complexity of the greedy algorithm is $O(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log N_b+2N_b(N_b+2N_s)\log N)$, i.e., $O(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log N_b)$.
+Based on currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the number of batteries $N_b$, switches $N_s$, and nodes $N$ have the following quantitative relationships: $N_s \approx (3\sim 5)N_b$, $N \approx N_s$.
+After simplifying, the time complexity of the greedy algorithm is $O(2^{N_b}N_s^2\log N_b)$, while the time complexity for traversing all reconstruction structures is $O(2^{N_s}N_s^3)$.
+Therefore, it is reasonable to believe that as the size of the RBS increases, the greedy algorithm will have an advantage over the algorithm that traverses all reconstruction structures.
+However, the greedy algorithm proposed in this paper still contains exponential terms, which means it may not be able to handle extremely large-scale RBS structures.
+}
 
@@
 This paper proposes a pervasive and automatical method for computing the MAC of \replaced{a}{the} given RBS.
-The method is  implemented by a greedy algorithm combined with a directed graph model, \replaced{and}{whose effectiveness is tested on a novel and complex RBS structure.
-The method} remains effective for the application scenario of \replaced{the RBS system with a complex structure and isolated batteries}{RBS battery isolation and demonstrates that the novel structure has the advantage on flexible output current and convenient battery isolation}.
+The method is implemented by a greedy algorithm combined with a directed graph model \deleted{, whose effectiveness is tested on a novel and complex RBS structure}.
+\deleted{The method remains effective for the application scenario of RBS battery isolation and demonstrates that the novel structure has the advantage on flexible output current and convenient battery isolation.}
 \deleted{Future research could focus on developing new indictors to evaluate the performance of the RBS with the currents and voltages obtained by the method, as well as modifying the equivalent model of the battery to allow for more accurate simulations of the RBS, including transient analysis.}
@@
 
-\section{Appendix}
+\end{document}
 
-\begin{algorithm}
-    \caption{Get the max available currents of a certain RBS}\label{alg:greedy}
-    \KwData{Directed graph model $G(V,E)$ of the RBS}
-    \KwResult{$\max \eta$}
-    \For{$i \in E_b$}{
-        $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
-        $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
-    }
-    get $\bm{A}$ by Equation \ref{eq:A}\;
-    \While{not yet determine $\max \eta$ }
-    {
-        $N_{set} \leftarrow \text{number of setected $SP$s calculated by dichotomy}$\;
-        $C_b    \leftarrow \text{set of all combinations of $N_{set} $~batteries from $N_b$}$\;
-        \For{$c_b \in C_b$}{
-            $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
-            $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
-            get $\bm{Y}_n$ by Equation \ref{eq:Yn}\;
-            \eIf{$\bm{Y}_n$ is invertible}{
-            }{construct an effective solution}
-            get $I_o$ by Equation \ref{eq:I_o}\;
-            get $\bm{I}_b$ by Equation \ref{eq:I_b}\;
-            \eIf{$\max(\bm{I}_b)\leq I_m$}{
-                $\eta \leftarrow I_o/\max(\bm{I}_b)$\;
-            }{break}
-        }
-    }
-\end{algorithm}
+Abstract:
+Reconfigurable Battery Systems (RBSs) present a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structure.
+In this paper, we propose a novel method for calculating the Maximum Allowable Current (MAC) of RBSs.
+Our method utilizes a directed graph model and a greedy algorithm to determine the MAC and the corresponding control strategy.
+We validate the effectiveness of our method using a complex RBS structure and demonstrate its potential in facilitating next-generation RBS designs and applications, including battery isolation.
 
-\section*{Acknowledgments}
-
-\subsection*{Author Contributions}
-
-B. Xu conceived the main idea, formulated the overarching research goals and aims, designed the algorithm, and reviewed and revised the manuscript.
-G. Hua developed and analyzed the model, implemented the code and supporting algorithms, and wrote the initial draft.
-C. Qian provided critical review, commentary, and revisions.
-Q. Xia contributed to shaping the research, analysis, and manuscript.
-B. Sun conducted the research and investigation process.
-Y. Ren secured the funding and supervised the project.
-Z. Wang verified the results and provided necessary resources.
-
-\subsection*{Funding}
-
-This work was supported by the National Natural Science Foundation of China (NSFC, No.52075028).
-
-\subsection*{Conflicts of Interest}
-
-The authors declare that there is no conflict of interest regarding the publication of this article.
-
-\subsection*{Data Availability}
-
-This work does not require any data to be declared or publicly disclosed.
-
-\begin{thebibliography}{99}
-
-\bibitem{desiqueiraControlStrategySmooth2021}
-Luanna Maria~Silva {de Siqueira} and Wei Peng.
-\newblock Control strategy to smooth wind power output using battery energy
-  storage system: {{A}} review.
-\newblock {\em Journal of Energy Storage}, 35:102252, March 2021.
-
-\bibitem{yangBatteryEnergyStorage2018}
-Yuqing Yang, Stephen Bremner, Chris Menictas, and Merlinde Kay.
-\newblock Battery energy storage system size determination in renewable energy
-  systems: {{A}} review.
-\newblock {\em Renewable and Sustainable Energy Reviews}, 91:109--125, August
-  2018.
-
-\bibitem{choCommercialResearchBattery2015}
-Jaephil Cho, Sookyung Jeong, and Youngsik Kim.
-\newblock Commercial and research battery technologies for electrical energy
-  storage applications.
-\newblock {\em Progress in Energy and Combustion Science}, 48:84--101, June
-  2015.
-
-\bibitem{zhangDevelopmentProspectChinese2021}
-Lihua Zhang.
-\newblock Development and {{Prospect}} of {{Chinese Lunar Relay Communication
-  Satellite}}.
-\newblock {\em Space: Science \& Technology}, 2021, January 2021.
-
-\bibitem{schwanbeckInternationalSpaceStation2019}
-Eugene Schwanbeck and Penni Dalton.
-\newblock International {{Space Station Lithium-ion Batteries}} for {{Primary
-  Electric Power System}}.
-\newblock In {\em 2019 {{European Space Power Conference}} ({{ESPC}})}, pages
-  1--1. {IEEE}, September 2019.
-
-\bibitem{yangUnbalancedDischargingAging2016}
-Naixing Yang, Xiongwen Zhang, BinBin Shang, and Guojun Li.
-\newblock Unbalanced discharging and aging due to temperature differences among
-  the cells in a lithium-ion battery pack with parallel combination.
-\newblock {\em Journal of Power Sources}, 306:733--741, February 2016.
-
-\bibitem{fengPropagationMechanismsDiagnosis2019}
-Fei Feng, Xiaosong Hu, Lin Hu, Fengling Hu, Yang Li, and Lei Zhang.
-\newblock Propagation mechanisms and diagnosis of parameter inconsistency
-  within {{Li-Ion}} battery packs.
-\newblock {\em Renewable and Sustainable Energy Reviews}, 112:102--113,
-  September 2019.
-
-\bibitem{jeevarajanBatterySafetyQualifications2012}
-J.~A. Jeevarajan and C.~Winchester.
-\newblock Battery {{Safety Qualifications}} for {{Human Ratings}}.
-\newblock {\em Interface magazine}, 21(2):51--55, January 2012.
-
-\bibitem{pomboHybridPowerSystem2021}
-Daniel~V{\'a}zquez Pombo.
-\newblock A {{Hybrid Power System}} for a {{Permanent Colony}} on {{Mars}}.
-\newblock {\em Space: Science \& Technology}, 2021, January 2021.
-
-\bibitem{hanNextGenerationBatteryManagement2020a}
-Weiji Han, Torsten Wik, Anton Kersten, Guangzhong Dong, and Changfu Zou.
-\newblock Next-{{Generation Battery Management Systems}}: {{Dynamic
-  Reconfiguration}}.
-\newblock {\em IEEE Industrial Electronics Magazine}, 14(4):20--31, December
-  2020.
-
-\bibitem{visairoReconfigurableBatteryPack2008}
-H.~Visairo and P.~Kumar.
-\newblock A reconfigurable battery pack for improving power conversion
-  efficiency in portable devices.
-\newblock In {\em 2008 7th {{International Caribbean Conference}} on
-  {{Devices}}, {{Circuits}} and {{Systems}}}, pages 1--6. {IEEE}, April 2008.
-
-\bibitem{heExploringAdaptiveReconfiguration2013}
-Liang He, Lipeng Gu, Linghe Kong, Yu~Gu, Cong Liu, and Tian He.
-\newblock Exploring {{Adaptive Reconfiguration}} to {{Optimize Energy
-  Efficiency}} in {{Large-Scale Battery Systems}}.
-\newblock In {\em 2013 {{IEEE}} 34th {{Real-Time Systems Symposium}}}, pages
-  118--127, December 2013.
-
-\bibitem{hongwenheStateofChargeEstimationLithiumIon2011}
-Hongwen He, Rui Xiong, Xiaowei Zhang, Fengchun Sun, and JinXin Fan.
-\newblock State-of-{{Charge Estimation}} of the {{Lithium-Ion Battery Using}}
-  an {{Adaptive Extended Kalman Filter Based}} on an {{Improved Thevenin
-  Model}}.
-\newblock {\em IEEE Transactions on Vehicular Technology}, 60(4):1461--1469,
-  May 2011.
-
-\bibitem{mousavig.VariousBatteryModels2014}
-S.M. Mousavi~G. and M.~Nikdel.
-\newblock Various battery models for various simulation studies and
-  applications.
-\newblock {\em Renewable and Sustainable Energy Reviews}, 32:477--485, April
-  2014.
-
-\bibitem{lawsonSoftwareConfigurableBattery2012}
-Barrie Lawson.
-\newblock A {{Software Configurable Battery}}.
-\newblock {\em EVS26 International Battery, Hybrid and Fuel Cell Electric
-  Vehicle Symposium}, 2012.
-
-\bibitem{ciNovelDesignAdaptive2007}
-Song Ci, Jiucai Zhang, Hamid Sharif, and Mahmoud Alahmad.
-\newblock A {{Novel Design}} of {{Adaptive Reconfigurable Multicell Battery}}
-  for {{Power-Aware Embedded Networked Sensing Systems}}.
-\newblock In {\em {{IEEE GLOBECOM}} 2007-2007 {{IEEE Global Telecommunications
-  Conference}}}, pages 1043--1047, November 2007.
-
-\bibitem{alahmadBatterySwitchArray2008}
-Mahmoud Alahmad, Herb Hess, Mohammad Mojarradi, William West, and Jay Whitacre.
-\newblock Battery switch array system with application for {{JPL}}'s
-  rechargeable micro-scale batteries.
-\newblock {\em Journal of Power Sources}, 177(2):566--578, March 2008.
-
-\bibitem{kimDependableEfficientScalable2010b}
-Hahnsang Kim and Kang~G. Shin.
-\newblock Dependable, efficient, scalable architecture for management of
-  large-scale batteries.
-\newblock In {\em Proceedings of the 1st {{ACM}}/{{IEEE International
-  Conference}} on {{Cyber-Physical Systems}}}, {{ICCPS}} '10, pages 178--187,
-  {New York, NY, USA}, April 2010. {Association for Computing Machinery}.
-
-\bibitem{kimBalancedReconfigurationStorage2011a}
-Younghyun Kim, Sangyoung Park, Yanzhi Wang, Qing Xie, Naehyuck Chang, Massimo
-  Poncino, and Massoud Pedram.
-\newblock Balanced reconfiguration of storage banks in a hybrid electrical
-  energy storage system.
-\newblock In {\em 2011 {{IEEE}}/{{ACM International Conference}} on
-  {{Computer-Aided Design}} ({{ICCAD}})}, pages 624--631, November 2011.
-
-\bibitem{taesickimSeriesconnectedSelfreconfigurableMulticell2012a}
-Taesic Kim, Wei Qiao, and Liyan Qu.
-\newblock A series-connected self-reconfigurable multicell battery capable of
-  safe and effective charging/discharging and balancing operations.
-\newblock In {\em 2012 {{Twenty-Seventh Annual IEEE Applied Power Electronics
-  Conference}} and {{Exposition}} ({{APEC}})}, pages 2259--2264, February 2012.
-
-\bibitem{6843711}
-Liang He, Linghe Kong, Siyu Lin, Shaodong Ying, Yu~Gu, Tian He, and Cong Liu.
-\newblock Reconfiguration-assisted charging in large-scale {{Lithium-ion}}
-  battery systems.
-\newblock In {\em 2014 {{ACM}}/{{IEEE International Conference}} on
-  {{Cyber-Physical Systems}} ({{ICCPS}})}, pages 60--71, April 2014.
-
-\end{thebibliography}
-
-\end{document}
+Conclusion:
+In this paper, we have presented a pervasive and automatical method for calculating the MAC of Reconfigurable Battery Systems (RBSs).
+Our method utilizes a directed graph model and a greedy algorithm to determine the MAC and the corresponding control strategy.
+The main advantage of our method is its ability to calculate the MAC of RBSs with arbitrary structures, including scenarios with isolated batteries.
+This is achieved by considering the voltage, internal resistance, and maximum allowable current of the batteries, as well as the external load.
+Our method has been validated using a novel and complex RBS structure, and the results demonstrate its effectiveness and potential in facilitating next-generation RBS designs and applications, including battery isolation.
+By providing a comprehensive analysis of the RBS structure and considering various factors, our method enables accurate and efficient calculation of the MAC, ensuring the safety and reliability of the RBS.

### 2023-09-11 paper/SST/SST_main.tex
统一使用 brute force algorithm 这一名称

@@
-% 【done】 按 Q 修改意见修改 0901 【优先】
-
 % 【done】 
-% 2. 介绍修改，相关文献：
-%   2.1 RBS 结构分析相关的
-%   2.2 网络流（最大流）相关（但因为问题不同，无法使用，提一句穷举）
-% 3. 介绍修改，逐点列出我们的贡献：state research contribution and achievements as bullet points at the end of the Introduction section
-
-% 按 SST 修改意见修改 0902 【14号前交给润色机构】
+% 按 Q 修改意见修改 0901 【优先】
 % 1. 摘要修改，量化我们的成果：explain the most important achievements of the proposed method quantitatively
@@
 % 7. 修改算法的第15步
+% 8. 重写总结
+%
+
+% 【doing】
+% 添加文献
+
+% 【todo】
+% 按 SST 修改意见修改 0902 【14号前交给润色机构】
 
@@
 % Replace "sample" in the \addbibresource line below with the name of your .bib file.
-% \usepackage[style=nejm, 
-% citestyle=numeric-comp,
-% sorting=none]{biblatex}
-% \addbibresource{main.bib}
+% \usepackage[style=nejm, citestyle=numeric-comp, sorting=none]{biblatex}
+% \addbibresource{SST_main.bib}
 
@@
 Reconfigurable Battery Systems (RBSs) present a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structure subjected to battery charging and discharging strategies.
-During the operation of the RBS, the Maximum Allowable Current (MAC) of system that ensures each battery’s current remains within a safe range, is a critical indicator to guide the system’s reconfiguring control, ensuring its safety and reliability.
+During the operation of the RBS, the Maximum Allowable Current (MAC) of system that ensures each battery's current remains within a safe range, is a critical indicator to guide the system's reconfiguring control, ensuring its safety and reliability.
 In this paper, we firstly propose a calculation method for the MAC of arbitrary RBS using a greedy algorithm in conjunction with a directed graph model of the RBS.
+\added{
+By introducing the shortest path of the battery, the greedy algorithm reconfigures the structure that can output MAC more efficiently, compared to the complete brute force algorithm method.
+The directed graph model is based on the equivalent circuit and provides a specific method for calculating the MAC of a given structure.
+This method has been validated on two published 4-battery-RBSs and one with more complex structure.
+It obtaining the same results as the brute force algorithm method, while achieves significantly improved computational efficiency (3000 to 75000 times, primarily depending on the number of switches).
+The main advantage of this method is its ability to calculate the MAC of RBSs with arbitrary structures, even in the scenarios with random isolated batteries.
+}
+\deleted{
 In this method, a new directed graph model is developed to model the structure of RBS, and a greedy algorithm is designed to find the possible circuit that enable MAC.
@@
 The results show that this method is capable to calculated the MAC of RBSs with different structures or different battery sizes efficiently, which proves the correctness of this method and its potential in facilitating next-generation RBS designs and applications, including battery isolation.
+}
 \end{abstract}
@@
 Therefore, it provides a benchmark for RBS output current, protecting individual batteries and identifying overall system output limits during operation. 
-Despite its importance, no method currently exists for automatically evaluating MAC for RBSs.
+\deleted{Despite its importance, no method currently exists for automatically evaluating MAC for RBSs.
 In particular, when one or more random cells are isolated, there is still no method to determine the MAC of the remaining RBS in time to assist the system in adjusting the control strategy timely. 
-A \replaced{automatical and universal}{universal and automatical} method for calculating RBS MAC is \deleted{urgently} needed for practical applications. 
-In this study, a directed graph model and greedy algorithm are employed to determine the MAC of RBS and the corresponding control strategy, effectively calculating the MAC for RBSs with arbitrary structures, including scenarios with isolated batteries.
+A universal and automatical method for calculating RBS MAC is urgently needed for practical applications.}
+
+\added{To calculate the MAC of a given RBS, an analysis of the RBS's topology is required, and the voltage, internal resistance, and maximum allowable current of the battery should be taken into account meanwhile.
+Currently, the RBS's topology analysis is mainly dependent on methods and algorithms from graph theory.
+For instance, Chen et al.
+\cite{chenSneakCircuitTheory2021} proposed a systematic approach based on the sneak circuit theory is proposed to fundamentally avoid the short-circuit problem of reconfigurable battery systems.
+This research goes through and analyzes all paths between the positive and negative terminals of each battery in the RBS, and identifies paths that only contain switches as short-circuit paths to form a short-circuit path table for pre-check and before system reconfiguration.
+The maximum flow problem (MFP) in graph theory has a similar formulation to the problem on MAC. 
+MFP is defined as finding the path with the maximum flow in a network flow with a single source node and a single sink node.
+In the RBS, the system positive and negative terminals can be taken as the source and sink nodes respectively, and the current can be regarded as the flow of the graph. 
+However, the Kirchhoff's laws that describe the current in circuit , and the function of switches to control the circuit on-off should be translated into constraints in the MFP, resulting in a special maximum flow problem.
+Despite mature algorithms for the MFP, such as the Edmonds-Karp algorithm \cite{10.1145/321694.321699} and Dinic's blocking flow algorithm \cite{doi:10.1137/0204043}, these algorithms cannot be directly applied to solve the MAC due to the speciality of the problem.
+Moreover, these algorithms need to traverse all switch states to calculate the MAC comprehensively, which means high computational complexity and not suitable for large-scale RBS.}
+
+\added{The main contributions of the paper can be summarized as follows:}
+\deleted{In this study, a directed graph model and greedy algorithm are employed to determine the MAC of RBS and the corresponding control strategy, effectively calculating the MAC for RBSs with arbitrary structures, including scenarios with isolated batteries.}
+\begin{itemize}
+  \item \added{Application of the greedy algorithm to solving the MAC of a given RBS for the first time.}
+  \item \added{Presenting a improved directed graph model that considers the voltage, internal resistance, and maximum allowable current of the battery, and the external load.}
+  \item \added{Proposing a new RBS structure and analysing three RBS structures' MAC with random battery isolation.}
+\end{itemize}
 
@@
 Similarly, the MAC calculation results of the structures in Figures \ref{fig:study-stru-Lawson} and \ref{fig:study-stru-Visairo} are shown as Table \ref{tab:study-results-Lawson} and Table \ref{tab:study-results-Visairo}, respectively.
+\added{
+In order to verify and compare the results from the greedy algorithm, we also utilized a brute force algorithm that go through all possible switch states to calculate the MAC of the same three RBS. 
+For a given RBS structure with $N_s$ switches, the final $\max$ $\eta$ is the maximum of $\eta$s from all $2^{N_s}$ reconfigured structures.
+The final results are the same as the results shown in Tables \ref{tab:study-results-my}-\ref{tab:study-results-Visairo}.
+It is worth noting that the method used the greedy algorithm only calculated 7, 11, and 1 reconfigured structures for the RBS structure in Figures \ref{fig:study-stru-my}, \ref{fig:study-stru-Lawson}, \ref{fig:study-stru-Visairo}, respectively.
+While for the same RBS, the method counted all possible switch states computed $2^{19}$, $2^{15}$, and $2^{13}$ structures, respectively.
+}
 
@@
 Therefore, the switches state given in Table \ref{tab:study-results-my} can make the RBS output current reach the maximum.
+\added{The results of MAC obtained by going through all reconfigured structures is identical to the one by the greedy algorithm. 
+This further validates the algorithm we proposed.}
+
+\added{
+From the literature search we have conducted, no formal report on the algorithm for MAC in RBS has been found yet.
+Therefore, the time complexity of the proposed algorithm is analyzed and compared with the algorithm that goes through all reconfigured structures to demonstrate the advantage of this algorithm.
+Assuming that a RBS has $N_b$ batteries and $N_s$ switches, and the corresponding directed graph has $N$ nodes, it requires $2^{N_s}$ iterations to traverse all reconfigured structures.
+The calculation for each reconfigured structure by Equations \ref{eq:I_o}-\ref{eq:eta} requires matrix inversion and matrix multiplication, with a time complexity of $O(N^3+2N^2N_b+N^2N_s+NN^2_b)$.
+Therefore, the time complexity of the brute force algorithm is $O(2^{N_s}(N^3+2N^2N_b+N^2N_s+NN^2_b))$.
+The greedy algorithm proposed in this paper requires find the SP for each battery, which requires $N_b$ iterations.
+Each SP can be obtained by couple Dijkstra algorithms.
+Therefore, the total time complexity of calculating all SPs is $O(2N_b(N_b+2N_s)\log N)$.
+According to the Appendix \ref{alg:greedy}, the RBS can reconfigure $C^{N_{set}}_{N_b}$ structures by selecting $N_{set}$ batteries from $N_b$ batteries, which is $\sum^{N_b}_{N_{set}=1}C^{N_{set}}_{N_b}/N_b \approx 2^{N_b}/N_b$ on average.
+Hence, with bisection method, the time complexity of the greedy algorithm is $O(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log N_b+2N_b(N_b+2N_s)\log N)$, i.e., $O(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log N_b)$.
+Based on currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the number of batteries $N_b$, switches $N_s$, and nodes $N$ have the following quantitative relationships: $N_s \approx (3\sim 5)N_b$, $N \approx N_s$.
+After simplifying, the time complexity of the greedy algorithm is $O(2^{N_b}N_s^2\log N_b)$, while it is $O(2^{N_s}N_s^3)$ for brute force algorithm.
+Therefore, it is reasonable to believe that as the size of the RBS increases, especially the number of the swithes, the greedy algorithm will have an advantage over the algorithm that goes through all reconfigured structures.
+This can be comfirmed from the number of structures required for MAC determination in the previous subsection. 
+Compared to the brute force algorithm, the efficiency of the method based on the greedy algorithm has been improved by 3000 to 75000 times.
+Among the three RBS structures, the highest is the RBS structure with 19 switches (Figure \ref{fig:study-stru-my}).
+This benefit from two key points:
+(1) The SPs guide the RBS to reconfigure reasonable structures, rather than blindly going through all possible structures.
+This reduces the factor in complexity from $2^{N_s}$ to $2^{N_b}$, which is the main reason for the improvement in efficiency;
+(2) The bisection method further accelerates this process.
+However, the greedy algorithm proposed in this paper still contains exponential terms in the time complexity, which means it may not be able to handle extremely large-scale RBS structures.
+}
 
@@
 This paper proposes a pervasive and automatical method for computing the MAC of \replaced{a}{the} given RBS.
-The method is  implemented by a greedy algorithm combined with a directed graph model, \replaced{and}{whose effectiveness is tested on a novel and complex RBS structure.
-The method} remains effective for the application scenario of \replaced{the RBS system with a complex structure and isolated batteries}{RBS battery isolation and demonstrates that the novel structure has the advantage on flexible output current and convenient battery isolation}.
-\deleted{Future research could focus on developing new indictors to evaluate the performance of the RBS with the currents and voltages obtained by the method, as well as modifying the equivalent model of the battery to allow for more accurate simulations of the RBS, including transient analysis.}
-% #TODO 补充我们方法的优势和先进之处；强调可以计算随机隔离电池情况下的RBS结构的MAC
+\added{
+The method is implemented by a greedy algorithm combined with a directed graph model which considers the voltage, internal resistance, and maximum allowable current of the batteries, as well as the external load.
+The main advantage of this method is its ability to calculate the MAC of RBSs with arbitrary structures.
+Even in the scenarios with random isolated batteries, the method remains effective.
+Compared with the brute force algorithm, the proposed method has higher computational efficiency under the same calculation results.
+This is achieved by two key points when constructing the greedy algorithm: 
+(1) Calculate the shortest path of each battery by Dijkstra algorithm to obtain the SP of each battery; 
+(2) determine the maximum number of available batteries by bisection method to reduce the computational complexity.
+}
+\deleted{The method is implemented by a greedy algorithm combined with a directed graph model , whose effectiveness is tested on a novel and complex RBS structure.
+The method remains effective for the application scenario of RBS battery isolation and demonstrates that the novel structure has the advantage on flexible output current and convenient battery isolation.
+Future research could focus on developing new indictors to evaluate the performance of the RBS with the currents and voltages obtained by the method, as well as modifying the equivalent model of the battery to allow for more accurate simulations of the RBS, including transient analysis.}
 
@@
             \eIf{$\bm{Y}_n$ is invertible}{
+              \added{pass}
             }{construct an effective solution}
@@
 
+\bibitem{chenSneakCircuitTheory2021}
+Si-Zhe Chen, Yule Wang, Guidong Zhang, Le~Chang, and Yun Zhang.
+\newblock Sneak {{Circuit Theory Based Approach}} to {{Avoiding Short-Circuit
+  Paths}} in {{Reconfigurable Battery Systems}}.
+\newblock 68(12):12353--12363.
+
+\bibitem{10.1145/321694.321699}
+Jack Edmonds and Richard~M. Karp.
+\newblock Theoretical improvements in algorithmic efficiency for network flow
+  problems.
+\newblock {\em J. ACM}, 19(2):248–264, apr 1972.
+
+\bibitem{doi:10.1137/0204043}
+Shimon Even and R.~Endre Tarjan.
+\newblock Network flow and testing graph connectivity.
+\newblock {\em SIAM Journal on Computing}, 4(4):507--518, 1975.
+
 \end{thebibliography}

### 2023-09-12 paper/SST/SST_main.tex
完成了修改 (v1.2)

@@
 % 【done】 
+% =====0909
 % 按 Q 修改意见修改 0901 【优先】
+% =====0910
 % 1. 摘要修改，量化我们的成果：explain the most important achievements of the proposed method quantitatively
@@
 % 8. 重写总结
-%
+% 9. 添加文献
+% =====0911
+% 1. introduction 整体逻辑不流畅，跳跃过大
+% 2. introduction 文献
+% 2. conclusion 结尾，可以加上一两句说说这个方法的应用价值之类的，吹一吹
+% 3. abstract
+%   3.1 删去 75000 倍的效率；
+%   3.2 凝练一点，就是说这个方法把遍历法中的枚举开关状态组合，转换为了对最短路径的组合；
+%   3.3 算法复杂度、效率提升倍数=2^开关数/2^电池数
+%   3.4 调整 discussion 的相关内容
 
 % 【doing】
-% 添加文献
 
 % 【todo】
-% 按 SST 修改意见修改 0902 【14号前交给润色机构】
+% ==【14号前交给润色机构】
 
@@
 
-\usepackage[defaultcolor=red]{changes}
+% \usepackage[defaultcolor=red]{changes}
 % \added{xxx}
@@
 % \replaced{a}{b} 原文的b替换成a
-% \usepackage[final]{changes}
+\usepackage[final]{changes}
+% \usepackage{easyReview} % texstudio 部分
 
@@
 \added{
-By introducing the shortest path of the battery, the greedy algorithm reconfigures the structure that can output MAC more efficiently, compared to the complete brute force algorithm method.
-The directed graph model is based on the equivalent circuit and provides a specific method for calculating the MAC of a given structure.
+By introducing the shortest path of the battery, the greedy algorithm transforms the enumeration of switch states in the brute force algorithm into the combination of the shortest paths, which greatly increases the efficiency of the determination of the MAC.
+The directed graph model, based on the equivalent circuit, provides a specific method for calculating the MAC of a given structure.
 This method has been validated on two published 4-battery-RBSs and one with more complex structure.
-It obtaining the same results as the brute force algorithm method, while achieves significantly improved computational efficiency (3000 to 75000 times, primarily depending on the number of switches).
+It obtaining the same results as the brute force algorithm method, while achieves significantly improved computational efficiency ($N_s 2^{N_s - N_b} \log N_b$ times faster than the brute force algorithm for a RBS with $N_b$ batteries and $N_s$ switches, theoretically).
 The main advantage of this method is its ability to calculate the MAC of RBSs with arbitrary structures, even in the scenarios with random isolated batteries.
@@
 Reconfigurable Battery System (RBS), which can dynamically switch to different circuit topology configurations as required, is expected to solve the above problems\cite{hanNextGenerationBatteryManagement2020a}.
-The ability of switching circuit helps to isolate unhealthy batteries, and thereby improve the safety and reliability of the battery system.
-Figure \ref{fig:stru-Visairo} shows a typical RBS structure developed by Visairo \cite{visairoReconfigurableBatteryPack2008} for dynamically adjusting the output voltage and current.
+The ability of switching circuit helps to isolate unhealthy batteries, \replaced{thereby improving}{and thereby improve} the safety and reliability of the battery system.
+\replaced{In order to illustrate the working principle of RBS, a typical RBS structure developed by Visairo \cite{visairoReconfigurableBatteryPack2008}(Figure \ref{fig:stru-Visairo}) is taken as an example to show the reconfiguration process.}{Figure \ref{fig:stru-Visairo} shows a typical RBS structure developed by Visairo \cite{visairoReconfigurableBatteryPack2008} for dynamically adjusting the output voltage and current.}
 In this structure, the batteries can be connected not only in series when the switches $S_1$, $S_5$, $S_6$, $S_7$, $S_8$, $S_9$, and $S_{13}$ are closed (Figure \ref{fig:stru-Visairo-serial}), but also in parallel when $S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$, and $S_{13}$ are closed (Figure \ref{fig:stru-Visairo-parallel}).
@@
 
+\added{
+% 目前，许多研究人员利用 RBS的灵活地可重构特点，设计多种结构，以实现并改善系统的 performance
+% Ci【139】等人提出的结构能够动态调整电池放电倍率以充分挖掘各电池的可用容量；
+% Jan【149，150】等人针对电动汽车充电时不断变化的电压需求，提出了一种能够动态调整电池串联数的结构。
+% Visairo 【140】等人的结构可以根据负载条件改变系统的输出电压，从而减少供电过程中电压调节器的功率损耗以提升能量利用率；
+% 同样处于提升系统能量效率的目的，Lawson等人\cite{lawsonSoftwareConfigurableBattery2012}和He等人【148】也提出过更为简化的结构。Kim等人【143】则通过向结构引入多端口，提升了系统对电池故障的恢复能力。
+Currently, many researchers utilize the flexibility and reconfigurability of RBS to design various structures in order to meet application requirements and improve system performances. 
+Ci et al. \cite{ci2007novel} proposed a RBS structure that can dynamically adjust the batteries discharge rate to fully exploit the available capacity of each battery. 
+Jan's \cite{9209774,engelhardt2021double} structures had the ability to reconfigure structures with variant batteries in series to reach the voltage requirements during electric vehicle charging, which constantly change.
+The structure proposed by Visairo et al.\cite{visairoReconfigurableBatteryPack2008}, as shown in Figure \ref{fig:stru-Visairo}, can change the system's output voltage based on load conditions, thereby reducing the power loss of the voltage regulator during the power supply process and improving energy utilization efficiency.
+For the same purpose to enhance the energy efficiency of the system, Lawson et al.
+\cite{lawsonSoftwareConfigurableBattery2012} and He et al.
+\cite{he2014reconfiguration} also proposed simplified structures which has less switches than Visairo's design.
+Kim et al. \cite{kim2009dynamic} improved the system's ability to recover from battery failures by introducing multiple ports to the structure. 
+% 这些结构的提出很大程度上依赖研究人员的经验，并且缺少严谨的结构分析方法和客观全面的评价指标。
+% 这可能会导致结构设计不够优化，无法充分发挥RBS的性能优势；甚至存在潜在的安全隐患，无法让RBS投入实际应用。
+% To tackle these issues, some analyses on the RBS structure and performance have been conducted. 
+% For instance, Chen et al.
+\cite{chenSneakCircuitTheory2021} proposed a systematic approach based on the sneak circuit theory is proposed to fundamentally avoid the short-circuit problem of reconfigurable battery systems.
+% This research goes through and analyzes all paths between the positive and negative terminals of each battery in the RBS, and identifies paths that only contain switches as short-circuit paths to form a short-circuit path table for pre-check and before system reconfiguration.
+% Ham【162】等人则针对一种特定的RBS结构，推导出 maximum switch current during battery system reeconfiguration 的解析表达式。
+% 该工作可用于指导RBS的开关选型，为RBS的硬件设计提供支撑。
+The design of these structures mainly relies on the experience of researchers and lacks rigorous structural analysis methods and quantitative evaluation criteria. 
+This may result in suboptimal structures, inability to fully leverage the performance advantages of RBS, and even potential safety hazards that prevent practical applications of RBS. 
+To tackle these issues, some analyses on the RBS structure and performance have been conducted. 
+For instance, Chen et al.\cite{chenSneakCircuitTheory2021} proposed a systematic approach based on the sneak circuit theory to fundamentally avoid the short-circuit problem of reconfigurable battery systems.
+This research thoroughly analyzes all paths between the positive and negative terminals of each battery in the RBS and identifies paths that only contain switches as short-circuit paths, forming a short-circuit path table for pre-checking before system reconfiguration.
+Han et al.\cite{han2021analysis} derived an analytical expression for the maximum switch current during battery system reconfiguration for a specific RBS structure. 
+This helps guide the selection of switches and provide support for the hardware design of RBS.
+}
+
+\added{
+% 当前，对于RBS许用电流的分析仍是空白。
+% 电池具有合适的工作电流范围，过大的电流会导致电池的性能下降和衰退，甚至损坏电池。【文献】
+% 通过有限数量的电池组成的RBS也同样存在系统输出电流的上限，即 maximum allowable current (MAC)。
+% 超过该阈值会导系统内部部分电池的电流过载。
+% 因此，需要一种能够确定系统 MAC 的 RBS结构的电流分析方法和求解算法
+There is still a blank of analysis the allowable current of RBS.
+The battery has an appropriate range of operating currents, and excessive current can lead to a decrease and degradation in battery performance, or even damage\cite{lotfi2017li}.
+For RBS composed of finite batteries, there is also an upper limit on the system's output current, known as the maximum allowable current (MAC). 
+Exceeding this threshold can result in current overload on certain batteries of the system. 
+Therefore, there is a requirement for analysis method on RBS current and solving algorithm that can determine the system's MAC.
+The maximum flow problem (MFP) in graph theory has a similar formulation to the RBS MAC determination.
+MFP is defined as finding the path with the maximum flow in a network flow with a single source node and a single sink node.
+In the RBS, the system positive and negative terminals can be taken as the source and sink nodes respectively, and the current can be regarded as the flow of the graph. 
+Meanwhile, the Kirchhoff's laws that describe the current in circuit, and the function of switches to control the circuit on-off should be appropriately translated into constraints in the MFP.
+This strongly increases the complexity and makes it a special maximum flow problem that never been studied before.
+Despite mature algorithms for the MFP, such as the Edmonds-Karp algorithm \cite{10.1145/321694.321699} and Dinic's blocking flow algorithm \cite{doi:10.1137/0204043}, these algorithms cannot be directly applied to solve the MAC due to the speciality of the problem.
+Moreover, these MFP algorithms need to comprehensively compute all possible reconfigured structures to obtain the MAC, which means highly inefficience and not suitable for large-scale RBS.
+}
+
+\deleted{
 The complex connection structure between batteries and switches in the RBS provides flexibility but also introduces challenges in design and operational control. 
-Unlike traditional BESSs with fixed outputs, the RBS \replaced{typology}{output} must be dynamically adjusted by controlling switch states to meet external load requirements. 
+Unlike traditional BESSs with fixed outputs, the RBS output must be dynamically adjusted by controlling switch states to meet external load requirements. 
 This necessitates additional, time-consuming output performance analysis during design and corresponding control strategies. 
@@
 Therefore, it provides a benchmark for RBS output current, protecting individual batteries and identifying overall system output limits during operation. 
-\deleted{Despite its importance, no method currently exists for automatically evaluating MAC for RBSs.
+Despite its importance, no method currently exists for automatically evaluating MAC for RBSs.
 In particular, when one or more random cells are isolated, there is still no method to determine the MAC of the remaining RBS in time to assist the system in adjusting the control strategy timely. 
-A universal and automatical method for calculating RBS MAC is urgently needed for practical applications.}
-
-\added{To calculate the MAC of a given RBS, an analysis of the RBS's topology is required, and the voltage, internal resistance, and maximum allowable current of the battery should be taken into account meanwhile.
-Currently, the RBS's topology analysis is mainly dependent on methods and algorithms from graph theory.
-For instance, Chen et al.
-\cite{chenSneakCircuitTheory2021} proposed a systematic approach based on the sneak circuit theory is proposed to fundamentally avoid the short-circuit problem of reconfigurable battery systems.
-This research goes through and analyzes all paths between the positive and negative terminals of each battery in the RBS, and identifies paths that only contain switches as short-circuit paths to form a short-circuit path table for pre-check and before system reconfiguration.
-The maximum flow problem (MFP) in graph theory has a similar formulation to the problem on MAC. 
-MFP is defined as finding the path with the maximum flow in a network flow with a single source node and a single sink node.
-In the RBS, the system positive and negative terminals can be taken as the source and sink nodes respectively, and the current can be regarded as the flow of the graph. 
-However, the Kirchhoff's laws that describe the current in circuit , and the function of switches to control the circuit on-off should be translated into constraints in the MFP, resulting in a special maximum flow problem.
-Despite mature algorithms for the MFP, such as the Edmonds-Karp algorithm \cite{10.1145/321694.321699} and Dinic's blocking flow algorithm \cite{doi:10.1137/0204043}, these algorithms cannot be directly applied to solve the MAC due to the speciality of the problem.
-Moreover, these algorithms need to traverse all switch states to calculate the MAC comprehensively, which means high computational complexity and not suitable for large-scale RBS.}
-
+A universal and automatical method for calculating RBS MAC is urgently needed for practical applications.
+}
+
+\added{
+To effectively solve the switches states of MAC while strongly decreasing the unnecessary reconfigured structures to compute, and still robust in the scenarios with battery isolation, the greedy algorithm is adopted and adapted to solve the MAC problem in this paper.
+Meanwhile, an improved direct graph model, considering the voltage, internal resistance, and maximum allowable current of the battery, and the external load, is porposed and emploied to obtain the accuracy value of MAC.
+The correctness and effectiveness of the method in this paper are verified by two published 4-battery-RBSs and one with more complex structure.
+}
+\deleted{In this study, a directed graph model and greedy algorithm are employed to determine the MAC of RBS and the corresponding control strategy, effectively calculating the MAC for RBSs with arbitrary structures, including scenarios with isolated batteries.}
 \added{The main contributions of the paper can be summarized as follows:}
-\deleted{In this study, a directed graph model and greedy algorithm are employed to determine the MAC of RBS and the corresponding control strategy, effectively calculating the MAC for RBSs with arbitrary structures, including scenarios with isolated batteries.}
 \begin{itemize}
   \item \added{Application of the greedy algorithm to solving the MAC of a given RBS for the first time.}
-  \item \added{Presenting a improved directed graph model that considers the voltage, internal resistance, and maximum allowable current of the battery, and the external load.}
-  \item \added{Proposing a new RBS structure and analysing three RBS structures' MAC with random battery isolation.}
+  \item \added{Presenting a improved directed graph model to analyse the current of RBS, which considers the voltage, internal resistance, and maximum allowable current of the battery, and the external load.}
+  \item \added{Proposing a new RBS structure and comparing it with two proposed RBS structures in the scenario with randomly isolated batteries.}
 \end{itemize}
@@
 Section III demonstrated a case study of using the proposed method to determine the MAC of a novel and complex structure. 
-The calculation results and scenarios such as batteries isolation also are discussed. 
+The calculation results \added{, the algorithm's computational complexity} and scenarios such as batteries isolation also are discussed. 
 Finally, the concluding remarks are drawn in Section IV.
@@
 Subsequently, based on the equivalent circuit, the MAC problem is transformed into specific objective functions and constraints.
-Then, the shortest paths (SPs, where additional batteries and switches on the path are penalized as distance) for the batteries are obtained using the Dijkstra algorithm to guide the batteries in the RBS connect in parallel.
-Finally, a greedy algorithm is employed to organize the switches, allowing the batteries to connect via their SPs while satisfying the constraints, resulting in the MAC of the RBS.
+Then, the shortest paths (\replaced{$SP$}{SP}s, where additional batteries and switches on the path are penalized as distance) for the batteries are obtained using the Dijkstra algorithm to guide the batteries in the RBS connect in parallel.
+Finally, a greedy algorithm is employed to organize the switches, allowing the batteries to connect via their \replaced{$SP$}{SP}s while satisfying the constraints, resulting in the MAC of the RBS.
 
@@
 Therefore, the time complexity of the brute force algorithm is $O(2^{N_s}(N^3+2N^2N_b+N^2N_s+NN^2_b))$.
-The greedy algorithm proposed in this paper requires find the SP for each battery, which requires $N_b$ iterations.
-Each SP can be obtained by couple Dijkstra algorithms.
-Therefore, the total time complexity of calculating all SPs is $O(2N_b(N_b+2N_s)\log N)$.
+The greedy algorithm proposed in this paper requires find the $SP$ for each battery, which requires $N_b$ iterations.
+Each $SP$ can be obtained by couple Dijkstra algorithms.
+Therefore, the total time complexity of calculating all $SP$s is $O(2N_b(N_b+2N_s)\log N)$.
 According to the Appendix \ref{alg:greedy}, the RBS can reconfigure $C^{N_{set}}_{N_b}$ structures by selecting $N_{set}$ batteries from $N_b$ batteries, which is $\sum^{N_b}_{N_{set}=1}C^{N_{set}}_{N_b}/N_b \approx 2^{N_b}/N_b$ on average.
@@
 This can be comfirmed from the number of structures required for MAC determination in the previous subsection. 
-Compared to the brute force algorithm, the efficiency of the method based on the greedy algorithm has been improved by 3000 to 75000 times.
+Compared to the brute force algorithm, the efficiency of the method based on the greedy algorithm has been improved by 3000 to 75000 times, which is theoretically $N_s 2^{N_s - N_b} \log N_b$ times according to the above time complexity analysis.
 Among the three RBS structures, the highest is the RBS structure with 19 switches (Figure \ref{fig:study-stru-my}).
 This benefit from two key points:
-(1) The SPs guide the RBS to reconfigure reasonable structures, rather than blindly going through all possible structures.
+(1) The $SP$s guide the RBS to reconfigure reasonable structures, rather than blindly going through all possible structures.
 This reduces the factor in complexity from $2^{N_s}$ to $2^{N_b}$, which is the main reason for the improvement in efficiency;
@@
 This is achieved by two key points when constructing the greedy algorithm: 
-(1) Calculate the shortest path of each battery by Dijkstra algorithm to obtain the SP of each battery; 
+(1) Calculate the shortest path of each battery by Dijkstra algorithm to obtain the $SP$ of each battery; 
 (2) determine the maximum number of available batteries by bisection method to reduce the computational complexity.
+This method helps to fully tap the current output potential of the RBS, guide the RBS structure design and optimization in the design stage, and assist in evaluating the current overload risk of the system in practical applications.
 }
@@
 This work does not require any data to be declared or publicly disclosed.
-
-\begin{thebibliography}{99}
-
-\bibitem{desiqueiraControlStrategySmooth2021}
-Luanna Maria~Silva {de Siqueira} and Wei Peng.
-\newblock Control strategy to smooth wind power output using battery energy
-  storage system: {{A}} review.
-\newblock {\em Journal of Energy Storage}, 35:102252, March 2021.
-
-\bibitem{yangBatteryEnergyStorage2018}
-Yuqing Yang, Stephen Bremner, Chris Menictas, and Merlinde Kay.
-\newblock Battery energy storage system size determination in renewable energy
-  systems: {{A}} review.
-\newblock {\em Renewable and Sustainable Energy Reviews}, 91:109--125, August
-  2018.
+\begin{thebibliography}{10}
+
+\bibitem{alahmadBatterySwitchArray2008}
+Mahmoud Alahmad, Herb Hess, Mohammad Mojarradi, William West, and Jay Whitacre.
+\newblock Battery switch array system with application for {{JPL}}'s
+  rechargeable micro-scale batteries.
+\newblock {\em Journal of Power Sources}, 177(2):566--578, March 2008.
+
+\bibitem{chenSneakCircuitTheory2021}
+Si-Zhe Chen, Yule Wang, Guidong Zhang, Le~Chang, and Yun Zhang.
+\newblock Sneak {{Circuit Theory Based Approach}} to {{Avoiding Short-Circuit
+  Paths}} in {{Reconfigurable Battery Systems}}.
+\newblock 68(12):12353--12363, 2021.
 
@@
 
-\bibitem{zhangDevelopmentProspectChinese2021}
-Lihua Zhang.
-\newblock Development and {{Prospect}} of {{Chinese Lunar Relay Communication
-  Satellite}}.
-\newblock {\em Space: Science \& Technology}, 2021, January 2021.
-
-\bibitem{schwanbeckInternationalSpaceStation2019}
-Eugene Schwanbeck and Penni Dalton.
-\newblock International {{Space Station Lithium-ion Batteries}} for {{Primary
-  Electric Power System}}.
-\newblock In {\em 2019 {{European Space Power Conference}} ({{ESPC}})}, pages
-  1--1. {IEEE}, September 2019.
-
-\bibitem{yangUnbalancedDischargingAging2016}
-Naixing Yang, Xiongwen Zhang, BinBin Shang, and Guojun Li.
-\newblock Unbalanced discharging and aging due to temperature differences among
-  the cells in a lithium-ion battery pack with parallel combination.
-\newblock {\em Journal of Power Sources}, 306:733--741, February 2016.
+\bibitem{ci2007novel}
+Song Ci, Jiucai Zhang, Hamid Sharif, and Mahmoud Alahmad.
+\newblock A novel design of adaptive reconfigurable multicell battery for
+  power-aware embedded networked sensing systems.
+\newblock In {\em IEEE GLOBECOM 2007-IEEE Global Telecommunications
+  Conference}, pages 1043--1047. IEEE, 2007.
+
+\bibitem{ciNovelDesignAdaptive2007}
+Song Ci, Jiucai Zhang, Hamid Sharif, and Mahmoud Alahmad.
+\newblock A {{Novel Design}} of {{Adaptive Reconfigurable Multicell Battery}}
+  for {{Power-Aware Embedded Networked Sensing Systems}}.
+\newblock In {\em {{IEEE GLOBECOM}} 2007-2007 {{IEEE Global Telecommunications
+  Conference}}}, pages 1043--1047, November 2007.
+
+\bibitem{desiqueiraControlStrategySmooth2021}
+Luanna Maria~Silva {de Siqueira} and Wei Peng.
+\newblock Control strategy to smooth wind power output using battery energy
+  storage system: {{A}} review.
+\newblock {\em Journal of Energy Storage}, 35:102252, March 2021.
+
+\bibitem{10.1145/321694.321699}
+Jack Edmonds and Richard~M. Karp.
+\newblock Theoretical improvements in algorithmic efficiency for network flow
+  problems.
+\newblock {\em J. ACM}, 19(2):248–264, apr 1972.
+
+\bibitem{9209774}
+Jan Engelhardt, Tatiana Gabderakhmanova, Gunnar Rohde, and Mattia Marinelli.
+\newblock Reconfigurable stationary battery with adaptive cell switching for
+  electric vehicle fast-charging.
+\newblock In {\em 2020 55th International Universities Power Engineering
+  Conference (UPEC)}, pages 1--6, 2020.
+
+\bibitem{engelhardt2021double}
+Jan Engelhardt, Jan~Martin Zepter, Tatiana Gabderakhmanova, Gunnar Rohde, and
+  Mattia Marinelli.
+\newblock Double-string battery system with reconfigurable cell topology
+  operated as a fast charging station for electric vehicles.
+\newblock {\em Energies}, 14(9):2414, 2021.
+
+\bibitem{doi:10.1137/0204043}
+Shimon Even and R.~Endre Tarjan.
+\newblock Network flow and testing graph connectivity.
+\newblock {\em SIAM Journal on Computing}, 4(4):507--518, 1975.
 
@@
 
-\bibitem{jeevarajanBatterySafetyQualifications2012}
-J.~A. Jeevarajan and C.~Winchester.
-\newblock Battery {{Safety Qualifications}} for {{Human Ratings}}.
-\newblock {\em Interface magazine}, 21(2):51--55, January 2012.
-
-\bibitem{pomboHybridPowerSystem2021}
-Daniel~V{\'a}zquez Pombo.
-\newblock A {{Hybrid Power System}} for a {{Permanent Colony}} on {{Mars}}.
-\newblock {\em Space: Science \& Technology}, 2021, January 2021.
+\bibitem{han2021analysis}
+Weiji Han, Anton Kersten, Changfu Zou, Torsten Wik, Xiaoliang Huang, and
+  Guangzhong Dong.
+\newblock Analysis and estimation of the maximum switch current during battery
+  system reconfiguration.
+\newblock {\em IEEE Transactions on Industrial Electronics}, 69(6):5931--5941,
+  2021.
 
@@
   2020.
-
-\bibitem{visairoReconfigurableBatteryPack2008}
-H.~Visairo and P.~Kumar.
-\newblock A reconfigurable battery pack for improving power conversion
-  efficiency in portable devices.
-\newblock In {\em 2008 7th {{International Caribbean Conference}} on
-  {{Devices}}, {{Circuits}} and {{Systems}}}, pages 1--6. {IEEE}, April 2008.
-
-\bibitem{heExploringAdaptiveReconfiguration2013}
-Liang He, Lipeng Gu, Linghe Kong, Yu~Gu, Cong Liu, and Tian He.
-\newblock Exploring {{Adaptive Reconfiguration}} to {{Optimize Energy
-  Efficiency}} in {{Large-Scale Battery Systems}}.
-\newblock In {\em 2013 {{IEEE}} 34th {{Real-Time Systems Symposium}}}, pages
-  118--127, December 2013.
 
@@
 
-\bibitem{mousavig.VariousBatteryModels2014}
-S.M. Mousavi~G. and M.~Nikdel.
-\newblock Various battery models for various simulation studies and
-  applications.
-\newblock {\em Renewable and Sustainable Energy Reviews}, 32:477--485, April
-  2014.
-
-\bibitem{lawsonSoftwareConfigurableBattery2012}
-Barrie Lawson.
-\newblock A {{Software Configurable Battery}}.
-\newblock {\em EVS26 International Battery, Hybrid and Fuel Cell Electric
-  Vehicle Symposium}, 2012.
-
-\bibitem{ciNovelDesignAdaptive2007}
-Song Ci, Jiucai Zhang, Hamid Sharif, and Mahmoud Alahmad.
-\newblock A {{Novel Design}} of {{Adaptive Reconfigurable Multicell Battery}}
-  for {{Power-Aware Embedded Networked Sensing Systems}}.
-\newblock In {\em {{IEEE GLOBECOM}} 2007-2007 {{IEEE Global Telecommunications
-  Conference}}}, pages 1043--1047, November 2007.
-
-\bibitem{alahmadBatterySwitchArray2008}
-Mahmoud Alahmad, Herb Hess, Mohammad Mojarradi, William West, and Jay Whitacre.
-\newblock Battery switch array system with application for {{JPL}}'s
-  rechargeable micro-scale batteries.
-\newblock {\em Journal of Power Sources}, 177(2):566--578, March 2008.
+\bibitem{heExploringAdaptiveReconfiguration2013}
+Liang He, Lipeng Gu, Linghe Kong, Yu~Gu, Cong Liu, and Tian He.
+\newblock Exploring {{Adaptive Reconfiguration}} to {{Optimize Energy
+  Efficiency}} in {{Large-Scale Battery Systems}}.
+\newblock In {\em 2013 {{IEEE}} 34th {{Real-Time Systems Symposium}}}, pages
+  118--127, December 2013.
+
+\bibitem{he2014reconfiguration}
+Liang He, Linghe Kong, Siyu Lin, Shaodong Ying, Yu~Gu, Tian He, and Cong Liu.
+\newblock Reconfiguration-assisted charging in large-scale lithium-ion battery
+  systems.
+\newblock In {\em 2014 ACM/IEEE International Conference on Cyber-Physical
+  Systems (ICCPS)}, pages 60--71. IEEE, 2014.
+
+\bibitem{6843711}
+Liang He, Linghe Kong, Siyu Lin, Shaodong Ying, Yu~Gu, Tian He, and Cong Liu.
+\newblock Reconfiguration-assisted charging in large-scale {{Lithium-ion}}
+  battery systems.
+\newblock In {\em 2014 {{ACM}}/{{IEEE International Conference}} on
+  {{Cyber-Physical Systems}} ({{ICCPS}})}, pages 60--71, April 2014.
+
+\bibitem{jeevarajanBatterySafetyQualifications2012}
+J.~A. Jeevarajan and C.~Winchester.
+\newblock Battery {{Safety Qualifications}} for {{Human Ratings}}.
+\newblock {\em Interface magazine}, 21(2):51--55, January 2012.
+
+\bibitem{kim2009dynamic}
+Hahnsang Kim and Kang~G Shin.
+\newblock On dynamic reconfiguration of a large-scale battery system.
+\newblock In {\em 2009 15th IEEE Real-Time and Embedded Technology and
+  Applications Symposium}, pages 87--96. IEEE, 2009.
 
@@
 
+\bibitem{taesickimSeriesconnectedSelfreconfigurableMulticell2012a}
+Taesic Kim, Wei Qiao, and Liyan Qu.
+\newblock A series-connected self-reconfigurable multicell battery capable of
+  safe and effective charging/discharging and balancing operations.
+\newblock In {\em 2012 {{Twenty-Seventh Annual IEEE Applied Power Electronics
+  Conference}} and {{Exposition}} ({{APEC}})}, pages 2259--2264, February 2012.
+
 \bibitem{kimBalancedReconfigurationStorage2011a}
@@
 
-\bibitem{taesickimSeriesconnectedSelfreconfigurableMulticell2012a}
-Taesic Kim, Wei Qiao, and Liyan Qu.
-\newblock A series-connected self-reconfigurable multicell battery capable of
-  safe and effective charging/discharging and balancing operations.
-\newblock In {\em 2012 {{Twenty-Seventh Annual IEEE Applied Power Electronics
-  Conference}} and {{Exposition}} ({{APEC}})}, pages 2259--2264, February 2012.
-
-\bibitem{6843711}
-Liang He, Linghe Kong, Siyu Lin, Shaodong Ying, Yu~Gu, Tian He, and Cong Liu.
-\newblock Reconfiguration-assisted charging in large-scale {{Lithium-ion}}
-  battery systems.
-\newblock In {\em 2014 {{ACM}}/{{IEEE International Conference}} on
-  {{Cyber-Physical Systems}} ({{ICCPS}})}, pages 60--71, April 2014.
-
-\bibitem{chenSneakCircuitTheory2021}
-Si-Zhe Chen, Yule Wang, Guidong Zhang, Le~Chang, and Yun Zhang.
-\newblock Sneak {{Circuit Theory Based Approach}} to {{Avoiding Short-Circuit
-  Paths}} in {{Reconfigurable Battery Systems}}.
-\newblock 68(12):12353--12363.
-
-\bibitem{10.1145/321694.321699}
-Jack Edmonds and Richard~M. Karp.
-\newblock Theoretical improvements in algorithmic efficiency for network flow
-  problems.
-\newblock {\em J. ACM}, 19(2):248–264, apr 1972.
-
-\bibitem{doi:10.1137/0204043}
-Shimon Even and R.~Endre Tarjan.
-\newblock Network flow and testing graph connectivity.
-\newblock {\em SIAM Journal on Computing}, 4(4):507--518, 1975.
+\bibitem{lawsonSoftwareConfigurableBattery2012}
+Barrie Lawson.
+\newblock A {{Software Configurable Battery}}.
+\newblock {\em EVS26 International Battery, Hybrid and Fuel Cell Electric
+  Vehicle Symposium}, 2012.
+
+\bibitem{lotfi2017li}
+Nima Lotfi, Jie Li, Robert~G Landers, and Jonghyun Park.
+\newblock Li-ion battery state of health estimation based on an improved single
+  particle model.
+\newblock In {\em 2017 American Control Conference (ACC)}, pages 86--91. IEEE,
+  2017.
+
+\bibitem{mousavig.VariousBatteryModels2014}
+S.M. Mousavi~G. and M.~Nikdel.
+\newblock Various battery models for various simulation studies and
+  applications.
+\newblock {\em Renewable and Sustainable Energy Reviews}, 32:477--485, April
+  2014.
+
+\bibitem{pomboHybridPowerSystem2021}
+Daniel~V{\'a}zquez Pombo.
+\newblock A {{Hybrid Power System}} for a {{Permanent Colony}} on {{Mars}}.
+\newblock {\em Space: Science \& Technology}, 2021, January 2021.
+
+\bibitem{schwanbeckInternationalSpaceStation2019}
+Eugene Schwanbeck and Penni Dalton.
+\newblock International {{Space Station Lithium-ion Batteries}} for {{Primary
+  Electric Power System}}.
+\newblock In {\em 2019 {{European Space Power Conference}} ({{ESPC}})}, pages
+  1--1. {IEEE}, September 2019.
+
+\bibitem{visairoReconfigurableBatteryPack2008}
+H.~Visairo and P.~Kumar.
+\newblock A reconfigurable battery pack for improving power conversion
+  efficiency in portable devices.
+\newblock In {\em 2008 7th {{International Caribbean Conference}} on
+  {{Devices}}, {{Circuits}} and {{Systems}}}, pages 1--6. {IEEE}, April 2008.
+
+\bibitem{yangUnbalancedDischargingAging2016}
+Naixing Yang, Xiongwen Zhang, BinBin Shang, and Guojun Li.
+\newblock Unbalanced discharging and aging due to temperature differences among
+  the cells in a lithium-ion battery pack with parallel combination.
+\newblock {\em Journal of Power Sources}, 306:733--741, February 2016.
+
+\bibitem{yangBatteryEnergyStorage2018}
+Yuqing Yang, Stephen Bremner, Chris Menictas, and Merlinde Kay.
+\newblock Battery energy storage system size determination in renewable energy
+  systems: {{A}} review.
+\newblock {\em Renewable and Sustainable Energy Reviews}, 91:109--125, August
+  2018.
+
+\bibitem{zhangDevelopmentProspectChinese2021}
+Lihua Zhang.
+\newblock Development and {{Prospect}} of {{Chinese Lunar Relay Communication
+  Satellite}}.
+\newblock {\em Space: Science \& Technology}, 2021, January 2021.
 
@@
 
+% \bibliographystyle{plain}
+% \bibliography{sst_main}
+
 \end{document}

### 2023-09-12 paper/SST/SST_main.tex
完成了 Q 的意见修改：删去最大流，完善相关细节

@@
 %   3.4 调整 discussion 的相关内容
+% 4. 删去 最大流
+% 5. 按 Q 的意见修改
 
@@
 % 【todo】
-% ==【14号前交给润色机构】
+% ==18号润色完再次核对，21或22号提交。
 
@@
 
-% \usepackage[defaultcolor=red]{changes}
+\usepackage[defaultcolor=red]{changes}
 % \added{xxx}
@@
 % \replaced{a}{b} 原文的b替换成a
-\usepackage[final]{changes}
+% \usepackage[final]{changes}
 % \usepackage{easyReview} % texstudio 部分
@@
 \added{
-% 目前，许多研究人员利用 RBS的灵活地可重构特点，设计多种结构，以实现并改善系统的 performance
-% Ci【139】等人提出的结构能够动态调整电池放电倍率以充分挖掘各电池的可用容量；
-% Jan【149，150】等人针对电动汽车充电时不断变化的电压需求，提出了一种能够动态调整电池串联数的结构。
-% Visairo 【140】等人的结构可以根据负载条件改变系统的输出电压，从而减少供电过程中电压调节器的功率损耗以提升能量利用率；
-% 同样处于提升系统能量效率的目的，Lawson等人\cite{lawsonSoftwareConfigurableBattery2012}和He等人【148】也提出过更为简化的结构。Kim等人【143】则通过向结构引入多端口，提升了系统对电池故障的恢复能力。
-Currently, many researchers utilize the flexibility and reconfigurability of RBS to design various structures in order to meet application requirements and improve system performances. 
+Recently, the flexibility and reconfigurability of RBS have been utilized to design various structures in order to meet application requirements and improve system performances. 
 Ci et al. \cite{ci2007novel} proposed a RBS structure that can dynamically adjust the batteries discharge rate to fully exploit the available capacity of each battery. 
@@
 Kim et al. \cite{kim2009dynamic} improved the system's ability to recover from battery failures by introducing multiple ports to the structure. 
-% 这些结构的提出很大程度上依赖研究人员的经验，并且缺少严谨的结构分析方法和客观全面的评价指标。
-% 这可能会导致结构设计不够优化，无法充分发挥RBS的性能优势；甚至存在潜在的安全隐患，无法让RBS投入实际应用。
-% To tackle these issues, some analyses on the RBS structure and performance have been conducted. 
-% For instance, Chen et al.
-\cite{chenSneakCircuitTheory2021} proposed a systematic approach based on the sneak circuit theory is proposed to fundamentally avoid the short-circuit problem of reconfigurable battery systems.
-% This research goes through and analyzes all paths between the positive and negative terminals of each battery in the RBS, and identifies paths that only contain switches as short-circuit paths to form a short-circuit path table for pre-check and before system reconfiguration.
-% Ham【162】等人则针对一种特定的RBS结构，推导出 maximum switch current during battery system reeconfiguration 的解析表达式。
-% 该工作可用于指导RBS的开关选型，为RBS的硬件设计提供支撑。
 The design of these structures mainly relies on the experience of researchers and lacks rigorous structural analysis methods and quantitative evaluation criteria. 
 This may result in suboptimal structures, inability to fully leverage the performance advantages of RBS, and even potential safety hazards that prevent practical applications of RBS. 
-To tackle these issues, some analyses on the RBS structure and performance have been conducted. 
+To tackle these issues, several approaches to analyze the RBS structure and performance have been proposed in the literature.
 For instance, Chen et al.\cite{chenSneakCircuitTheory2021} proposed a systematic approach based on the sneak circuit theory to fundamentally avoid the short-circuit problem of reconfigurable battery systems.
-This research thoroughly analyzes all paths between the positive and negative terminals of each battery in the RBS and identifies paths that only contain switches as short-circuit paths, forming a short-circuit path table for pre-checking before system reconfiguration.
+They thoroughly analyzes all paths between the cathode and anode of each battery in the RBS and identifies paths that only contain switches as short-circuit paths for pre-checking before system reconfiguration.
 Han et al.\cite{han2021analysis} derived an analytical expression for the maximum switch current during battery system reconfiguration for a specific RBS structure. 
@@
 \added{
-% 当前，对于RBS许用电流的分析仍是空白。
-% 电池具有合适的工作电流范围，过大的电流会导致电池的性能下降和衰退，甚至损坏电池。【文献】
-% 通过有限数量的电池组成的RBS也同样存在系统输出电流的上限，即 maximum allowable current (MAC)。
-% 超过该阈值会导系统内部部分电池的电流过载。
-% 因此，需要一种能够确定系统 MAC 的 RBS结构的电流分析方法和求解算法
-There is still a blank of analysis the allowable current of RBS.
 The battery has an appropriate range of operating currents, and excessive current can lead to a decrease and degradation in battery performance, or even damage\cite{lotfi2017li}.
-For RBS composed of finite batteries, there is also an upper limit on the system's output current, known as the maximum allowable current (MAC). 
+likewise, for RBS composed of finite batteries, there is also an upper limit on the system's output current, known as the maximum allowable current (MAC). 
 Exceeding this threshold can result in current overload on certain batteries of the system. 
-Therefore, there is a requirement for analysis method on RBS current and solving algorithm that can determine the system's MAC.
-The maximum flow problem (MFP) in graph theory has a similar formulation to the RBS MAC determination.
-MFP is defined as finding the path with the maximum flow in a network flow with a single source node and a single sink node.
-In the RBS, the system positive and negative terminals can be taken as the source and sink nodes respectively, and the current can be regarded as the flow of the graph. 
-Meanwhile, the Kirchhoff's laws that describe the current in circuit, and the function of switches to control the circuit on-off should be appropriately translated into constraints in the MFP.
-This strongly increases the complexity and makes it a special maximum flow problem that never been studied before.
-Despite mature algorithms for the MFP, such as the Edmonds-Karp algorithm \cite{10.1145/321694.321699} and Dinic's blocking flow algorithm \cite{doi:10.1137/0204043}, these algorithms cannot be directly applied to solve the MAC due to the speciality of the problem.
-Moreover, these MFP algorithms need to comprehensively compute all possible reconfigured structures to obtain the MAC, which means highly inefficience and not suitable for large-scale RBS.
+Unfortunately, few studies on the RBS structure analysis have been conducted to determine the MAC of RBSs.
+A intuitive and straightforward method is to enumerate all possible switch states and calculate the output current of the system under each reconfigurated structure.
+But this method is inefficient and time-consuming, especially for RBSs with a large number of switches.
 }
@@
 \begin{itemize}
-  \item \added{Application of the greedy algorithm to solving the MAC of a given RBS for the first time.}
-  \item \added{Presenting a improved directed graph model to analyse the current of RBS, which considers the voltage, internal resistance, and maximum allowable current of the battery, and the external load.}
-  \item \added{Proposing a new RBS structure and comparing it with two proposed RBS structures in the scenario with randomly isolated batteries.}
+  \item \added{Proposing a effective method to determine the MAC of RBSs with arbitrary structures, including scenarios with isolated batteries, for the first time.}
+  \item \added{Application of the greedy algorithm to solve the MAC problem, whose computational complexity is greatly reduced compared with the brute force algorithm.}
+  \item \added{introducing an improved directed graph model, considering the voltage, internal resistance, and maximum allowable current of the battery, and the external load, to achieve the current analysis of the RBS.}
 \end{itemize}
@@
 As shown in Figure \ref{fig:study-stru-my}, the new RBS structure consists of 4 batteries and 19 switches. 
-The corresponding directed graph is depicted in Figure \ref{fig:study-dirgraph-my}, which is composed of of a total of 18 nodes and 43 edges. 
+The corresponding directed graph is depicted in Figure \ref{fig:study-dirgraph-my}, which is composed of a total of 18 nodes and 43 edges. 
 Batteries $B_1$, $B_2$, $B_3$, and $B_4$ are denoted by green directed edges in the graph, while the 19 switches are represented by gray directed edges with bi-directional arrows. 
@@
 Therefore, the switches state given in Table \ref{tab:study-results-my} can make the RBS output current reach the maximum.
-\added{The results of MAC obtained by going through all reconfigured structures is identical to the one by the greedy algorithm. 
-This further validates the algorithm we proposed.}
+\added{The results of MAC obtained by brute force algorithm method is identical to the one by the greedy algorithm.}
 
 \added{
-From the literature search we have conducted, no formal report on the algorithm for MAC in RBS has been found yet.
-Therefore, the time complexity of the proposed algorithm is analyzed and compared with the algorithm that goes through all reconfigured structures to demonstrate the advantage of this algorithm.
+From the literature research we have conducted, no formal report on the algorithm for MAC in RBS has been found yet.
+The brute force algorithm, which goes through all possible switch states, is the most straightforward way to solve the MAC problem and is used as a benchmark for the proposed greedy algorithm.
 Assuming that a RBS has $N_b$ batteries and $N_s$ switches, and the corresponding directed graph has $N$ nodes, it requires $2^{N_s}$ iterations to traverse all reconfigured structures.

### 2023-09-12 paper/SST/review_response.tex
添加了 review response 的模板，并整理了文件

\documentclass[12pt,american]{scrartcl}
\usepackage{babel}
\usepackage[babel]{microtype}
\usepackage[babel]{csquotes}

\usepackage[journal={Space: Science \& Technology},
			manuscript={SPACE-D-23-00082},
			editor={Dr. Tian}]{reviewresponse}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
%\usepackage{newcent}
%\usepackage[scaled]{beramono}

\usepackage[]{biblatex}
\bibliography{2-SST_review.bib}

\usepackage{hyperref}

\title{Maximum Allowable Current Determination of RBS By Using a Directed Graph Model and Greedy Algorithm}
\author{Dr. Cheng Qian, on behalf of all authors}

\begin{document}
\maketitle

% Cover Letter
\include{2-SST_cover_letter}

% Reviewer 1
\reviewer
% Comment 1
\begin{revcomment}
	The authors should explain the most important achievements of the proposed method quantitatively, in the abstract.
\end{revcomment}
\begin{revresponse}
	We appreciate the reviewer's valuable feedback and have carefully considered their suggestion. In response, we have re-written the relevant content in the abstract to provide a quantitative analysis of the most important achievements of our proposed method.

	The revised abstract now highlights that our method not only achieves the same results as the traversal method but also demonstrates significantly improved computational efficiency. Specifically, our method achieves computational efficiency improvements ranging from 3000 to 75000 times, primarily depending on the number of switches involved. This enhancement in computational efficiency is a key advantage of our method.

	Furthermore, our method stands out for its ability to accurately calculate the MAC of RBSs with arbitrary configurations, even in scenarios with random isolated batteries. This capability expands the applicability of our method to a wider range of scenarios and enhances its practical utility.

	We believe that these quantitative achievements, as described in the revised abstract, effectively demonstrate the effectiveness and superiority of our proposed method.
\end{revresponse}

% Comment 2
\begin{revcomment}
	The literature review in the introduction section is very short, and the related works, especially the works published in recent years, have not been well reviewed and compared, and the conclusions about the existing research gaps have not been presented.
\end{revcomment}
\begin{revresponse}

\end{revresponse}

% Comment 3
\begin{revcomment}
	It is necessary for the authors to clearly state research contribution and achievements as bullet points at the end of the Introduction section.
\end{revcomment}
\begin{revresponse}

\end{revresponse}

% Comment 4
\begin{revcomment}
	The authors need to present the complexity of their proposed method and compare it with some other state-of-the-art or successful classic methods.
\end{revcomment}
\begin{revresponse}

\end{revresponse}

% Comment 5
\begin{revcomment}
	The authors don't discuss the limitations of the study correctly.
\end{revcomment}
\begin{revresponse}

\end{revresponse}

% Comment 6
\begin{revcomment}
	Some typos should be double check.
\end{revcomment}
\begin{revresponse}

\end{revresponse}

% Comment 7
\begin{revcomment}
	The author should explain more why solution quality of their proposed approach is much better than the others?
\end{revcomment}
\begin{revresponse}

\end{revresponse}

% Comment 8
\begin{revcomment}
	Authors should mention some novel works in the field in the introduction, specially refer to this 2023 reference: An efficient lightweight algorithm for scheduling tasks onto dynamically reconfigurable hardware using graph-oriented simulated annealing, which uses graph-based method. Mention and refer to it in the introduction section.
\end{revcomment}
\begin{revresponse}

\end{revresponse}

% Comment 9
\begin{revcomment}
	Authors need to explain about the accuracy, sufficiency and reliability of their results? How do they verify and validate the results?
\end{revcomment}
\begin{revresponse}

\end{revresponse}

% \begin{revcomment}
% 	Everything else is really good.
% \end{revcomment}
% \begin{revresponse}
% 	We totally agree. We also added the following to the new version of the manuscript
% 	\begin{changes}
% 		This really important sentence was added to the paper.
% 	\end{changes}
% \end{revresponse}

\end{document}

### 2023-09-12 paper/SST/2-SST_cover_letter.tex
添加了 review response 的模板，并整理了文件

Dear \editorname,

Please find enclosed the revised version of our previous submission entitled \enquote{\thetitle} with manuscript number \manuscript. We would like to thank you and the reviewers for the valuable comments which help improving the quality of our manuscript.
In this revision, we have carefully addressed the reviewers' comments. A summary of main modifications and a detailed point-by-point response to the comments from Reviewers 1 and 3 (following the reviewers' order in the decision letter) are given below.

\vspace{1.2em}

Sincerely,

\vspace{1.5em}

\theauthor

\vfil
\textbf{Note:} To enhance the legibility of this response letter, all the editor's and reviewers' comments are typeset in boxes. Rephrased or added sentences are typeset in color. The respective parts in the manuscript are highlighted to indicate changes.

**improve the general language expression** during revision progress.

### 2023-09-13 paper/SST/SST_main.tex
完成了 Xu 的意见修改 (v1.4)

@@
+% 【version: SST-1.4】
+
 % 【done】 
@@
 % 5. 按 Q 的意见修改
+% =====0913
+% 1. 按师兄的修改意见修改（0912晚）
+% 2. 调整文献顺序，改用 biber
 
@@
 
+% \usepackage[final]{changes}
 \usepackage[defaultcolor=red]{changes}
@@
 % \replaced{a}{b} 原文的b替换成a
-% \usepackage[final]{changes}
 % \usepackage{easyReview} % texstudio 部分
@@
 % Replace "sample" in the \addbibresource line below with the name of your .bib file.
-% \usepackage[style=nejm, citestyle=numeric-comp, sorting=none]{biblatex}
-% \addbibresource{SST_main.bib}
+\usepackage[style=nejm, citestyle=numeric-comp, sorting=none]{biblatex}
+\addbibresource{SST_main.bib}
 
@@
 \added{
-Recently, the flexibility and reconfigurability of RBS have been utilized to design various structures in order to meet application requirements and improve system performances. 
-Ci et al. \cite{ci2007novel} proposed a RBS structure that can dynamically adjust the batteries discharge rate to fully exploit the available capacity of each battery. 
+Recently, various types of RBS with different flexibility and reconfigurability have been designed to meet application requirements. 
+For example, Ci et al. \cite{ci2007novel} proposed a RBS structure that can dynamically adjust the batteries discharge rate to fully exploit the available capacity of each battery. 
 Jan's \cite{9209774,engelhardt2021double} structures had the ability to reconfigure structures with variant batteries in series to reach the voltage requirements during electric vehicle charging, which constantly change.
@@
 Kim et al. \cite{kim2009dynamic} improved the system's ability to recover from battery failures by introducing multiple ports to the structure. 
-The design of these structures mainly relies on the experience of researchers and lacks rigorous structural analysis methods and quantitative evaluation criteria. 
-This may result in suboptimal structures, inability to fully leverage the performance advantages of RBS, and even potential safety hazards that prevent practical applications of RBS. 
-To tackle these issues, several approaches to analyze the RBS structure and performance have been proposed in the literature.
-For instance, Chen et al.\cite{chenSneakCircuitTheory2021} proposed a systematic approach based on the sneak circuit theory to fundamentally avoid the short-circuit problem of reconfigurable battery systems.
-They thoroughly analyzes all paths between the cathode and anode of each battery in the RBS and identifies paths that only contain switches as short-circuit paths for pre-checking before system reconfiguration.
+The complex structure between batteries and switches enables the flexibility of RBS, but also brings the challenges in design and control of system. 
+Thus, several approaches to analyze the RBS structure and performance have been proposed in the literature to tackle these challenges.
+For instance, 
 Han et al.\cite{han2021analysis} derived an analytical expression for the maximum switch current during battery system reconfiguration for a specific RBS structure. 
 This helps guide the selection of switches and provide support for the hardware design of RBS.
+Chen et al.\cite{chenSneakCircuitTheory2021} proposed a systematic approach based on the sneak circuit theory to fundamentally avoid the short-circuit problem of reconfigurable battery systems. 
+They thoroughly analyzes all paths between the cathode and anode of each battery in the RBS and identifies paths that only contain switches as short-circuit paths for pre-checking before system reconfiguration.
 }
@@
 \added{
-The battery has an appropriate range of operating currents, and excessive current can lead to a decrease and degradation in battery performance, or even damage\cite{lotfi2017li}.
-likewise, for RBS composed of finite batteries, there is also an upper limit on the system's output current, known as the maximum allowable current (MAC). 
-Exceeding this threshold can result in current overload on certain batteries of the system. 
+In spite of maximum switch current mentioned above, the maximum allowable current (MAC), defined as the maximum current allowed by system under the constraints of the battery cell, is another critical indictor of RBS that need to be evaluated during the design or control process of system.
+It helps the designers to assess whether the RBS meets the output current requirements, and contribute to the formulation of appropriate and safe management strategies for the battery management system (BMS).
 Unfortunately, few studies on the RBS structure analysis have been conducted to determine the MAC of RBSs.
@@
 \added{
-To effectively solve the switches states of MAC while strongly decreasing the unnecessary reconfigured structures to compute, and still robust in the scenarios with battery isolation, the greedy algorithm is adopted and adapted to solve the MAC problem in this paper.
-Meanwhile, an improved direct graph model, considering the voltage, internal resistance, and maximum allowable current of the battery, and the external load, is porposed and emploied to obtain the accuracy value of MAC.
-The correctness and effectiveness of the method in this paper are verified by two published 4-battery-RBSs and one with more complex structure.
+To solve this issue, a new method to effectively evaluate the MAC of RBS is proposed in this paper. 
+First, a greedy algorithm is designed to search the possible circuit topology of RBS with MAC effciently.
+Meanwhile, an improved direct graph model, considering the voltage, internal resistance, and maximum allowable current of the battery, and the external load, is porposed to obtain the accurate current value of RBS under specific circuit topology.
+To the best of our knowledge, the present work is the first to develop an efficient calculation method of RBS MAC.
 }
@@
 \begin{itemize}
-  \item \added{Proposing a effective method to determine the MAC of RBSs with arbitrary structures, including scenarios with isolated batteries, for the first time.}
+  \item \added{Proposing a effective method to determine the MAC of RBSs with arbitrary structures, including scenarios with isolated batteries.}
   \item \added{Application of the greedy algorithm to solve the MAC problem, whose computational complexity is greatly reduced compared with the brute force algorithm.}
@@
 After simplifying, the time complexity of the greedy algorithm is $O(2^{N_b}N_s^2\log N_b)$, while it is $O(2^{N_s}N_s^3)$ for brute force algorithm.
-Therefore, it is reasonable to believe that as the size of the RBS increases, especially the number of the swithes, the greedy algorithm will have an advantage over the algorithm that goes through all reconfigured structures.
-This can be comfirmed from the number of structures required for MAC determination in the previous subsection. 
+Therefore, it is reasonable to believe that as the size of the RBS increases, especially the number of the switches, the greedy algorithm will have an advantage over the algorithm that goes through all reconfigured structures.
+This can be confirmed from the number of structures required for MAC determination in the previous subsection. 
 Compared to the brute force algorithm, the efficiency of the method based on the greedy algorithm has been improved by 3000 to 75000 times, which is theoretically $N_s 2^{N_s - N_b} \log N_b$ times according to the above time complexity analysis.
@@
 
-This paper proposes a pervasive and automatical method for computing the MAC of \replaced{a}{the} given RBS.
+This paper proposes a pervasive and automatical method for computing the MAC of \replaced{a}{the} given RBS \added{efficiently}.
 \added{
@@
 This work does not require any data to be declared or publicly disclosed.
-\begin{thebibliography}{10}
 
-\bibitem{alahmadBatterySwitchArray2008}
-Mahmoud Alahmad, Herb Hess, Mohammad Mojarradi, William West, and Jay Whitacre.
-\newblock Battery switch array system with application for {{JPL}}'s
-  rechargeable micro-scale batteries.
-\newblock {\em Journal of Power Sources}, 177(2):566--578, March 2008.
-
-\bibitem{chenSneakCircuitTheory2021}
-Si-Zhe Chen, Yule Wang, Guidong Zhang, Le~Chang, and Yun Zhang.
-\newblock Sneak {{Circuit Theory Based Approach}} to {{Avoiding Short-Circuit
-  Paths}} in {{Reconfigurable Battery Systems}}.
-\newblock 68(12):12353--12363, 2021.
-
-\bibitem{choCommercialResearchBattery2015}
-Jaephil Cho, Sookyung Jeong, and Youngsik Kim.
-\newblock Commercial and research battery technologies for electrical energy
-  storage applications.
-\newblock {\em Progress in Energy and Combustion Science}, 48:84--101, June
-  2015.
-
-\bibitem{ci2007novel}
-Song Ci, Jiucai Zhang, Hamid Sharif, and Mahmoud Alahmad.
-\newblock A novel design of adaptive reconfigurable multicell battery for
-  power-aware embedded networked sensing systems.
-\newblock In {\em IEEE GLOBECOM 2007-IEEE Global Telecommunications
-  Conference}, pages 1043--1047. IEEE, 2007.
-
-\bibitem{ciNovelDesignAdaptive2007}
-Song Ci, Jiucai Zhang, Hamid Sharif, and Mahmoud Alahmad.
-\newblock A {{Novel Design}} of {{Adaptive Reconfigurable Multicell Battery}}
-  for {{Power-Aware Embedded Networked Sensing Systems}}.
-\newblock In {\em {{IEEE GLOBECOM}} 2007-2007 {{IEEE Global Telecommunications
-  Conference}}}, pages 1043--1047, November 2007.
-
-\bibitem{desiqueiraControlStrategySmooth2021}
-Luanna Maria~Silva {de Siqueira} and Wei Peng.
-\newblock Control strategy to smooth wind power output using battery energy
-  storage system: {{A}} review.
-\newblock {\em Journal of Energy Storage}, 35:102252, March 2021.
-
-\bibitem{10.1145/321694.321699}
-Jack Edmonds and Richard~M. Karp.
-\newblock Theoretical improvements in algorithmic efficiency for network flow
-  problems.
-\newblock {\em J. ACM}, 19(2):248–264, apr 1972.
-
-\bibitem{9209774}
-Jan Engelhardt, Tatiana Gabderakhmanova, Gunnar Rohde, and Mattia Marinelli.
-\newblock Reconfigurable stationary battery with adaptive cell switching for
-  electric vehicle fast-charging.
-\newblock In {\em 2020 55th International Universities Power Engineering
-  Conference (UPEC)}, pages 1--6, 2020.
-
-\bibitem{engelhardt2021double}
-Jan Engelhardt, Jan~Martin Zepter, Tatiana Gabderakhmanova, Gunnar Rohde, and
-  Mattia Marinelli.
-\newblock Double-string battery system with reconfigurable cell topology
-  operated as a fast charging station for electric vehicles.
-\newblock {\em Energies}, 14(9):2414, 2021.
-
-\bibitem{doi:10.1137/0204043}
-Shimon Even and R.~Endre Tarjan.
-\newblock Network flow and testing graph connectivity.
-\newblock {\em SIAM Journal on Computing}, 4(4):507--518, 1975.
-
-\bibitem{fengPropagationMechanismsDiagnosis2019}
-Fei Feng, Xiaosong Hu, Lin Hu, Fengling Hu, Yang Li, and Lei Zhang.
-\newblock Propagation mechanisms and diagnosis of parameter inconsistency
-  within {{Li-Ion}} battery packs.
-\newblock {\em Renewable and Sustainable Energy Reviews}, 112:102--113,
-  September 2019.
-
-\bibitem{han2021analysis}
-Weiji Han, Anton Kersten, Changfu Zou, Torsten Wik, Xiaoliang Huang, and
-  Guangzhong Dong.
-\newblock Analysis and estimation of the maximum switch current during battery
-  system reconfiguration.
-\newblock {\em IEEE Transactions on Industrial Electronics}, 69(6):5931--5941,
-  2021.
-
-\bibitem{hanNextGenerationBatteryManagement2020a}
-Weiji Han, Torsten Wik, Anton Kersten, Guangzhong Dong, and Changfu Zou.
-\newblock Next-{{Generation Battery Management Systems}}: {{Dynamic
-  Reconfiguration}}.
-\newblock {\em IEEE Industrial Electronics Magazine}, 14(4):20--31, December
-  2020.
-
-\bibitem{hongwenheStateofChargeEstimationLithiumIon2011}
-Hongwen He, Rui Xiong, Xiaowei Zhang, Fengchun Sun, and JinXin Fan.
-\newblock State-of-{{Charge Estimation}} of the {{Lithium-Ion Battery Using}}
-  an {{Adaptive Extended Kalman Filter Based}} on an {{Improved Thevenin
-  Model}}.
-\newblock {\em IEEE Transactions on Vehicular Technology}, 60(4):1461--1469,
-  May 2011.
-
-\bibitem{heExploringAdaptiveReconfiguration2013}
-Liang He, Lipeng Gu, Linghe Kong, Yu~Gu, Cong Liu, and Tian He.
-\newblock Exploring {{Adaptive Reconfiguration}} to {{Optimize Energy
-  Efficiency}} in {{Large-Scale Battery Systems}}.
-\newblock In {\em 2013 {{IEEE}} 34th {{Real-Time Systems Symposium}}}, pages
-  118--127, December 2013.
-
-\bibitem{he2014reconfiguration}
-Liang He, Linghe Kong, Siyu Lin, Shaodong Ying, Yu~Gu, Tian He, and Cong Liu.
-\newblock Reconfiguration-assisted charging in large-scale lithium-ion battery
-  systems.
-\newblock In {\em 2014 ACM/IEEE International Conference on Cyber-Physical
-  Systems (ICCPS)}, pages 60--71. IEEE, 2014.
-
-\bibitem{6843711}
-Liang He, Linghe Kong, Siyu Lin, Shaodong Ying, Yu~Gu, Tian He, and Cong Liu.
-\newblock Reconfiguration-assisted charging in large-scale {{Lithium-ion}}
-  battery systems.
-\newblock In {\em 2014 {{ACM}}/{{IEEE International Conference}} on
-  {{Cyber-Physical Systems}} ({{ICCPS}})}, pages 60--71, April 2014.
-
-\bibitem{jeevarajanBatterySafetyQualifications2012}
-J.~A. Jeevarajan and C.~Winchester.
-\newblock Battery {{Safety Qualifications}} for {{Human Ratings}}.
-\newblock {\em Interface magazine}, 21(2):51--55, January 2012.
-
-\bibitem{kim2009dynamic}
-Hahnsang Kim and Kang~G Shin.
-\newblock On dynamic reconfiguration of a large-scale battery system.
-\newblock In {\em 2009 15th IEEE Real-Time and Embedded Technology and
-  Applications Symposium}, pages 87--96. IEEE, 2009.
-
-\bibitem{kimDependableEfficientScalable2010b}
-Hahnsang Kim and Kang~G. Shin.
-\newblock Dependable, efficient, scalable architecture for management of
-  large-scale batteries.
-\newblock In {\em Proceedings of the 1st {{ACM}}/{{IEEE International
-  Conference}} on {{Cyber-Physical Systems}}}, {{ICCPS}} '10, pages 178--187,
-  {New York, NY, USA}, April 2010. {Association for Computing Machinery}.
-
-\bibitem{taesickimSeriesconnectedSelfreconfigurableMulticell2012a}
-Taesic Kim, Wei Qiao, and Liyan Qu.
-\newblock A series-connected self-reconfigurable multicell battery capable of
-  safe and effective charging/discharging and balancing operations.
-\newblock In {\em 2012 {{Twenty-Seventh Annual IEEE Applied Power Electronics
-  Conference}} and {{Exposition}} ({{APEC}})}, pages 2259--2264, February 2012.
-
-\bibitem{kimBalancedReconfigurationStorage2011a}
-Younghyun Kim, Sangyoung Park, Yanzhi Wang, Qing Xie, Naehyuck Chang, Massimo
-  Poncino, and Massoud Pedram.
-\newblock Balanced reconfiguration of storage banks in a hybrid electrical
-  energy storage system.
-\newblock In {\em 2011 {{IEEE}}/{{ACM International Conference}} on
-  {{Computer-Aided Design}} ({{ICCAD}})}, pages 624--631, November 2011.
-
-\bibitem{lawsonSoftwareConfigurableBattery2012}
-Barrie Lawson.
-\newblock A {{Software Configurable Battery}}.
-\newblock {\em EVS26 International Battery, Hybrid and Fuel Cell Electric
-  Vehicle Symposium}, 2012.
-
-\bibitem{lotfi2017li}
-Nima Lotfi, Jie Li, Robert~G Landers, and Jonghyun Park.
-\newblock Li-ion battery state of health estimation based on an improved single
-  particle model.
-\newblock In {\em 2017 American Control Conference (ACC)}, pages 86--91. IEEE,
-  2017.
-
-\bibitem{mousavig.VariousBatteryModels2014}
-S.M. Mousavi~G. and M.~Nikdel.
-\newblock Various battery models for various simulation studies and
-  applications.
-\newblock {\em Renewable and Sustainable Energy Reviews}, 32:477--485, April
-  2014.
-
-\bibitem{pomboHybridPowerSystem2021}
-Daniel~V{\'a}zquez Pombo.
-\newblock A {{Hybrid Power System}} for a {{Permanent Colony}} on {{Mars}}.
-\newblock {\em Space: Science \& Technology}, 2021, January 2021.
-
-\bibitem{schwanbeckInternationalSpaceStation2019}
-Eugene Schwanbeck and Penni Dalton.
-\newblock International {{Space Station Lithium-ion Batteries}} for {{Primary
-  Electric Power System}}.
-\newblock In {\em 2019 {{European Space Power Conference}} ({{ESPC}})}, pages
-  1--1. {IEEE}, September 2019.
-
-\bibitem{visairoReconfigurableBatteryPack2008}
-H.~Visairo and P.~Kumar.
-\newblock A reconfigurable battery pack for improving power conversion
-  efficiency in portable devices.
-\newblock In {\em 2008 7th {{International Caribbean Conference}} on
-  {{Devices}}, {{Circuits}} and {{Systems}}}, pages 1--6. {IEEE}, April 2008.
-
-\bibitem{yangUnbalancedDischargingAging2016}
-Naixing Yang, Xiongwen Zhang, BinBin Shang, and Guojun Li.
-\newblock Unbalanced discharging and aging due to temperature differences among
-  the cells in a lithium-ion battery pack with parallel combination.
-\newblock {\em Journal of Power Sources}, 306:733--741, February 2016.
-
-\bibitem{yangBatteryEnergyStorage2018}
-Yuqing Yang, Stephen Bremner, Chris Menictas, and Merlinde Kay.
-\newblock Battery energy storage system size determination in renewable energy
-  systems: {{A}} review.
-\newblock {\em Renewable and Sustainable Energy Reviews}, 91:109--125, August
-  2018.
-
-\bibitem{zhangDevelopmentProspectChinese2021}
-Lihua Zhang.
-\newblock Development and {{Prospect}} of {{Chinese Lunar Relay Communication
-  Satellite}}.
-\newblock {\em Space: Science \& Technology}, 2021, January 2021.
-
-\end{thebibliography}
-
-% \bibliographystyle{plain}
+% \bibliographystyle{nejm}
 % \bibliography{sst_main}
 
+\printbibliography
+
 \end{document}

### 2023-09-13 paper/SST/SST_main.tex
用于学术润色的版本：删除了中文注释
修改到内容低于6k单词，交付润色机构

@@
-% 【version: SST-1.4】
-
-% 【done】 
-% =====0909
-% 按 Q 修改意见修改 0901 【优先】
-% =====0910
-% 1. 摘要修改，量化我们的成果：explain the most important achievements of the proposed method quantitatively
-% 2. 介绍修改，相关文献：
-%   2.1 RBS 结构分析相关的
-%   2.2 网络流（最大流）相关（但因为问题不同，无法使用，提一句穷举）
-% 3. 介绍修改，逐点列出我们的贡献：state research contribution and achievements as bullet points at the end of the Introduction section
-% 4. 讨论修改，增加算法复杂度，以及和穷举法的比较（该领域尚为空白，没有sota的算法）
-% 5. 讨论修改，增加算法的 limitations（根据复杂度，大规模不好用）
-% 6. 讨论修改，增加结果的准确性介绍（和穷举结果比较）：explain about the accuracy, sufficiency and reliability of their results? How do they verify and validate the results
-% 7. 修改算法的第15步
-% 8. 重写总结
-% 9. 添加文献
-% =====0911
-% 1. introduction 整体逻辑不流畅，跳跃过大
-% 2. introduction 文献
-% 2. conclusion 结尾，可以加上一两句说说这个方法的应用价值之类的，吹一吹
-% 3. abstract
-%   3.1 删去 75000 倍的效率；
-%   3.2 凝练一点，就是说这个方法把遍历法中的枚举开关状态组合，转换为了对最短路径的组合；
-%   3.3 算法复杂度、效率提升倍数=2^开关数/2^电池数
-%   3.4 调整 discussion 的相关内容
-% 4. 删去 最大流
-% 5. 按 Q 的意见修改
-% =====0913
-% 1. 按师兄的修改意见修改（0912晚）
-% 2. 调整文献顺序，改用 biber
-
-% 【doing】
-
-% 【todo】
-% ==18号润色完再次核对，21或22号提交。
-
 \documentclass{article}
@@
 \usepackage{lineno}
-\linenumbers
+% \linenumbers
 
@@
 
-% \usepackage[final]{changes}
-\usepackage[defaultcolor=red]{changes}
+\usepackage[final]{changes}
+% \usepackage[defaultcolor=red]{changes}
 % \added{xxx}
 % \deleted{xxxx}
-% \replaced{a}{b} 原文的b替换成a
-% \usepackage{easyReview} % texstudio 部分
+% \replaced{a}{b}
 
@@
 % You can include group authors, but please include a list of the actual authors (the group members) in the Supplementary Materials.
-\author[1$\dag$]{Binghui Xu}
-\author[1$\dag$]{Guangbin Hua}
-\author[1*]{Cheng Qian}
-\author[1,2]{Quan Xia}
-\author[1]{Bo Sun}
-\author[1]{Yi Ren}
-\author[1]{Zili Wang}
+\author[1]{30577}
+% \author[1$\dag$]{Binghui Xu}
+% \author[1$\dag$]{Guangbin Hua}
+% \author[1*]{Cheng Qian}
+% \author[1,2]{Quan Xia}
+% \author[1]{Bo Sun}
+% \author[1]{Yi Ren}
+% \author[1]{Zili Wang}
 
 %%%%%% Affiliations %%%%%%
-\affil[1]{School of Reliability and Systems Engineering, Beihang University, Beijing, 100191, China}
-\affil[2]{School of Aeronautic Science and Engineering at Beihang University, Beijing, China}
-\affil[*]{Address correspondence to: cqian@buaa.edu.cn}
-\affil[$\dag$]{These authors contributed equally to this work.}
+% \affil[1]{School of Reliability and Systems Engineering, Beihang University, Beijing, 100191, China}
+% \affil[2]{School of Aeronautic Science and Engineering at Beihang University, Beijing, China}
+% \affil[*]{Address correspondence to: cqian@buaa.edu.cn}
+% \affil[$\dag$]{These authors contributed equally to this work.}
 
@@
 
-The algorithm, as illustrated in Figure \ref{fig:flowchart}, can be summarized as follows, with the corresponding pseudo-code presented in Algorithm \ref{alg:greedy}.
+The algorithm, as illustrated in Figure \ref{fig:flowchart}, can be summarized as follows, with the corresponding pseudo-code presented in Algorithm 1. % \ref{alg:greedy}.
 First, the shortest paths ($SP$s) are obtained using Equations \ref{eq:weight} and \ref{eq:def_sp} in conjunction with Dijkstra Search. 
@@
 
-\tikzset{
-  meta box/.style={draw, black, very thick, text centered, },
-  punkt/.style={meta box, rectangle, rounded corners, inner sep=.25em, minimum height=2em, minimum width=4em, align=center, text width=10em },
-  round/.style={meta box, circle, minimum size=0, inner sep=0pt, outer sep=0pt },
-  every fit/.style={draw, thick, dashed, gray, inner xsep=.5em, inner ysep=.75em }
-}
-\begin{figure}
-\begin{tikzpicture}[font=\small, node font=\small, node distance=1.5em]
-    \node[punkt]     (input) {Input: RBS structure};
-    \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Equations \ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
-    \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Equation \ref{eq:A}};
-    \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{set}=N_b$ };
-    \node[punkt, below=0.3of get_Nset] (get_cb) {get $c_b$s by combinating $N_{set}$ batteries from $N_b$};
-    \node[draw, diamond, aspect=2, below=0.3of get_cb] (is_check_all_cb) {are all $c_b$s checked?};
-    \node[draw, diamond, aspect=2, right=1of is_check_all_cb] (is_Nset_converged) {is $N_{set}$ converged?};
-    \node[punkt, above=of is_Nset_converged] (reset_Nset) {reset $N_{set}$ by dichotomy};
-    \node[punkt, text width=15em, below=0.3of is_check_all_cb] (get_Xs) {
-        select an unchecked $c_b$, and get its $\bm{X}_m$ by \\ 
-        if switch $j$ $\in \bigcup_{i\in c_b}SP_i$:\\
-        $\bm{X}[j]=1$ else $0$};
-    \node[punkt, below=0.3of get_Xs] (get_Yn) {get $\bm{Y}_n$ by Equation \ref{eq:Yn}};
-    \node[draw, diamond, aspect=2, below=0.3of get_Yn] (is_Yn_invertible) {is $\bm{Y}_n$ invertible?};
-    \node[punkt, right=1.3of is_Yn_invertible] (construct) {construct an effective solution};
-    \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Equations \ref{eq:I_o} and \ref{eq:I_b}};
-    \node[draw, diamond, aspect=2, below=0.3of get_I] (is_leq_Im) {is $\max \bm{I}_b \leq I_m$?};
-    \node[punkt, right=1.3of is_leq_Im] (drop_eta) {drop this $\eta$};
-    \node[punkt, below=0.3of is_leq_Im] (get_eta) {get $\eta$ by Equation \ref{eq:eta}};
-    \node[punkt, below=0.3of get_eta] (update_max_eta) {update $\max \eta$};
-    \node[punkt, right=1of is_Nset_converged] (output) {Output: $\max \eta$};
-    \node[round,left=1.5of update_max_eta](point1){};
+% \tikzset{
+%   meta box/.style={draw, black, very thick, text centered, },
+%   punkt/.style={meta box, rectangle, rounded corners, inner sep=.25em, minimum height=2em, minimum width=4em, align=center, text width=10em },
+%   round/.style={meta box, circle, minimum size=0, inner sep=0pt, outer sep=0pt },
+%   every fit/.style={draw, thick, dashed, gray, inner xsep=.5em, inner ysep=.75em }
+% }
+% \begin{figure}
+% \begin{tikzpicture}[font=\small, node font=\small, node distance=1.5em]
+%     \node[punkt]     (input) {Input: RBS structure};
+%     \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Equations \ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
+%     \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Equation \ref{eq:A}};
+%     \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{set}=N_b$ };
+%     \node[punkt, below=0.3of get_Nset] (get_cb) {get $c_b$s by combinating $N_{set}$ batteries from $N_b$};
+%     \node[draw, diamond, aspect=2, below=0.3of get_cb] (is_check_all_cb) {are all $c_b$s checked?};
+%     \node[draw, diamond, aspect=2, right=1of is_check_all_cb] (is_Nset_converged) {is $N_{set}$ converged?};
+%     \node[punkt, above=of is_Nset_converged] (reset_Nset) {reset $N_{set}$ by dichotomy};
+%     \node[punkt, text width=15em, below=0.3of is_check_all_cb] (get_Xs) {
+%         select an unchecked $c_b$, and get its $\bm{X}_m$ by \\ 
+%         if switch $j$ $\in \bigcup_{i\in c_b}SP_i$:\\
+%         $\bm{X}[j]=1$ else $0$};
+%     \node[punkt, below=0.3of get_Xs] (get_Yn) {get $\bm{Y}_n$ by Equation \ref{eq:Yn}};
+%     \node[draw, diamond, aspect=2, below=0.3of get_Yn] (is_Yn_invertible) {is $\bm{Y}_n$ invertible?};
+%     \node[punkt, right=1.3of is_Yn_invertible] (construct) {construct an effective solution};
+%     \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Equations \ref{eq:I_o} and \ref{eq:I_b}};
+%     \node[draw, diamond, aspect=2, below=0.3of get_I] (is_leq_Im) {is $\max \bm{I}_b \leq I_m$?};
+%     \node[punkt, right=1.3of is_leq_Im] (drop_eta) {drop this $\eta$};
+%     \node[punkt, below=0.3of is_leq_Im] (get_eta) {get $\eta$ by Equation \ref{eq:eta}};
+%     \node[punkt, below=0.3of get_eta] (update_max_eta) {update $\max \eta$};
+%     \node[punkt, right=1of is_Nset_converged] (output) {Output: $\max \eta$};
+%     \node[round,left=1.5of update_max_eta](point1){};
+% 
+%     \graph{
+%       (input) -> (get_SP) -> (get_A) -> (get_Nset) -> (get_cb) -> (is_check_all_cb) ->["No"] (get_Xs) -> (get_Yn) -> (is_Yn_invertible) ->["Yes"] (get_I) -> (is_leq_Im) ->["Yes"] (get_eta) -> (update_max_eta);
+%       (is_check_all_cb) ->["Yes"] (is_Nset_converged) ->["No"] (reset_Nset) -> (get_cb);
+%       (is_Yn_invertible) ->["No"] (construct) ->[to path={|- (\tikztotarget)}] (get_I);
+%       (is_leq_Im) ->["No"] (drop_eta) ->[to path={|- (\tikztotarget)}] (update_max_eta);
+%       (is_Nset_converged) ->["Yes"] (output);
+%       (update_max_eta) -- (point1) ->[to path={|- (\tikztotarget)}] (is_check_all_cb);
+%     };
+% \end{tikzpicture}
+% \caption{The computational flowchart of the MAC for a given RBS.}\label{fig:flowchart}
+% \end{figure}
 
-    \graph{
-      (input) -> (get_SP) -> (get_A) -> (get_Nset) -> (get_cb) -> (is_check_all_cb) ->["No"] (get_Xs) -> (get_Yn) -> (is_Yn_invertible) ->["Yes"] (get_I) -> (is_leq_Im) ->["Yes"] (get_eta) -> (update_max_eta);
-      (is_check_all_cb) ->["Yes"] (is_Nset_converged) ->["No"] (reset_Nset) -> (get_cb);
-      (is_Yn_invertible) ->["No"] (construct) ->[to path={|- (\tikztotarget)}] (get_I);
-      (is_leq_Im) ->["No"] (drop_eta) ->[to path={|- (\tikztotarget)}] (update_max_eta);
-      (is_Nset_converged) ->["Yes"] (output);
-      (update_max_eta) -- (point1) ->[to path={|- (\tikztotarget)}] (is_check_all_cb);
-    };
-\end{tikzpicture}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=\textwidth]{flowchart.jpg}
     \caption{The computational flowchart of the MAC for a given RBS.}\label{fig:flowchart}
@@
 Utilizing Equation \ref{eq:weight} and the Dijkstra algorithm, the $SP$s of the four batteries in the RBS structure of Figure \ref{fig:study-stru-my} are highlighted by red in Figures \ref{fig:sp1}-\ref{fig:sp4}.
-Finally, the MAC calculation results of the structure in Figure \ref{fig:study-stru-my} are shown as Table \ref{tab:study-results-my} and Figure \ref{fig:study-results-my}, obtained by the greedy algorithm \ref{alg:greedy}.
+Finally, the MAC calculation results of the structure in Figure \ref{fig:study-stru-my} are shown as Table \ref{tab:study-results-my} and Figure \ref{fig:study-results-my}, obtained by the greedy algorithm 1.
+% \ref{alg:greedy}.
 Table \ref{tab:study-results-my} contains the switches states, the output current $I_o$, battery current $\bm{I}_b$ and ratio $\eta$ of the RBS structure with all batteries in good health when the RBS output reaches the MAC.
@@
 Therefore, the total time complexity of calculating all $SP$s is $O(2N_b(N_b+2N_s)\log N)$.
-According to the Appendix \ref{alg:greedy}, the RBS can reconfigure $C^{N_{set}}_{N_b}$ structures by selecting $N_{set}$ batteries from $N_b$ batteries, which is $\sum^{N_b}_{N_{set}=1}C^{N_{set}}_{N_b}/N_b \approx 2^{N_b}/N_b$ on average.
+According to the Appendix 1, % \ref{alg:greedy},
+the RBS can reconfigure $C^{N_{set}}_{N_b}$ structures by selecting $N_{set}$ batteries from $N_b$ batteries, which is $\sum^{N_b}_{N_{set}=1}C^{N_{set}}_{N_b}/N_b \approx 2^{N_b}/N_b$ on average.
 Hence, with bisection method, the time complexity of the greedy algorithm is $O(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log N_b+2N_b(N_b+2N_s)\log N)$, i.e., $O(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log N_b)$.
@@
 
-\begin{algorithm}
-    \caption{Get the max available currents of a certain RBS}\label{alg:greedy}
-    \KwData{Directed graph model $G(V,E)$ of the RBS}
-    \KwResult{$\max \eta$}
-    \For{$i \in E_b$}{
-        $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
-        $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
-    }
-    get $\bm{A}$ by Equation \ref{eq:A}\;
-    \While{not yet determine $\max \eta$ }
-    {
-        $N_{set} \leftarrow \text{number of setected $SP$s calculated by dichotomy}$\;
-        $C_b    \leftarrow \text{set of all combinations of $N_{set} $~batteries from $N_b$}$\;
-        \For{$c_b \in C_b$}{
-            $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
-            $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
-            get $\bm{Y}_n$ by Equation \ref{eq:Yn}\;
-            \eIf{$\bm{Y}_n$ is invertible}{
-              \added{pass}
-            }{construct an effective solution}
-            get $I_o$ by Equation \ref{eq:I_o}\;
-            get $\bm{I}_b$ by Equation \ref{eq:I_b}\;
-            \eIf{$\max(\bm{I}_b)\leq I_m$}{
-                $\eta \leftarrow I_o/\max(\bm{I}_b)$\;
-            }{break}
-        }
-    }
-\end{algorithm}
+% \begin{algorithm}
+%     \caption{Get the max available currents of a certain RBS}\label{alg:greedy}
+%     \KwData{Directed graph model $G(V,E)$ of the RBS}
+%     \KwResult{$\max \eta$}
+%     \For{$i \in E_b$}{
+%         $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
+%         $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
+%     }
+%     get $\bm{A}$ by Equation \ref{eq:A}\;
+%     \While{not yet determine $\max \eta$ }
+%     {
+%         $N_{set} \leftarrow \text{number of setected $SP$s calculated by dichotomy}$\;
+%         $C_b    \leftarrow \text{set of all combinations of $N_{set} $~batteries from $N_b$}$\;
+%         \For{$c_b \in C_b$}{
+%             $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
+%             $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
+%             get $\bm{Y}_n$ by Equation \ref{eq:Yn}\;
+%             \eIf{$\bm{Y}_n$ is invertible}{
+%               \added{pass}
+%             }{construct an effective solution}
+%             get $I_o$ by Equation \ref{eq:I_o}\;
+%             get $\bm{I}_b$ by Equation \ref{eq:I_b}\;
+%             \eIf{$\max(\bm{I}_b)\leq I_m$}{
+%                 $\eta \leftarrow I_o/\max(\bm{I}_b)$\;
+%             }{break}
+%         }
+%     }
+% \end{algorithm}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=\textwidth]{algorithm.jpg}
+\end{figure}
 
-\section*{Acknowledgments}
-
-\subsection*{Author Contributions}
-
-B. Xu conceived the main idea, formulated the overarching research goals and aims, designed the algorithm, and reviewed and revised the manuscript.
-G. Hua developed and analyzed the model, implemented the code and supporting algorithms, and wrote the initial draft.
-C. Qian provided critical review, commentary, and revisions.
-Q. Xia contributed to shaping the research, analysis, and manuscript.
-B. Sun conducted the research and investigation process.
-Y. Ren secured the funding and supervised the project.
-Z. Wang verified the results and provided necessary resources.
-
-\subsection*{Funding}
-
-This work was supported by the National Natural Science Foundation of China (NSFC, No.52075028).
-
-\subsection*{Conflicts of Interest}
-
-The authors declare that there is no conflict of interest regarding the publication of this article.
-
-\subsection*{Data Availability}
-
-This work does not require any data to be declared or publicly disclosed.
+% 
+% \section*{Acknowledgments}
+% 
+% \subsection*{Author Contributions} 
+% 
+% B. Xu conceived the main idea, formulated the overarching research goals and aims, designed the algorithm, and reviewed and revised the manuscript.
+% G. Hua developed and analyzed the model, implemented the code and supporting algorithms, and wrote the initial draft.
+% C. Qian provided critical review, commentary, and revisions.
+% Q. Xia contributed to shaping the research, analysis, and manuscript.
+% B. Sun conducted the research and investigation process.
+% Y. Ren secured the funding and supervised the project.
+% Z. Wang verified the results and provided necessary resources.
+% 
+% \subsection*{Funding}
+% 
+% This work was supported by the National Natural Science Foundation of China (NSFC, No.52075028).
+% 
+% \subsection*{Conflicts of Interest}
+% 
+% The authors declare that there is no conflict of interest regarding the publication of this article.
+% 
+% \subsection*{Data Availability}
+% 
+% This work does not require any data to be declared or publicly disclosed.
 
@@
 
-\printbibliography
+% \printbibliography
 

### 2023-09-13 paper/SST/review_response.tex
response review (doing:4/9)

@@
 \begin{revresponse}
-	We appreciate the reviewer's valuable feedback and have carefully considered their suggestion.
-In response, we have re-written the relevant content in the abstract to provide a quantitative analysis of the most important achievements of our proposed method.
 
-	The revised abstract now highlights that our method not only achieves the same results as the traversal method but also demonstrates significantly improved computational efficiency.
-Specifically, our method achieves computational efficiency improvements ranging from 3000 to 75000 times, primarily depending on the number of switches involved.
-This enhancement in computational efficiency is a key advantage of our method.
+Thank you for your valuable feedback. We have carefully considered your suggestion and made the following modifications to address your concern:
 
-	Furthermore, our method stands out for its ability to accurately calculate the MAC of RBSs with arbitrary configurations, even in scenarios with random isolated batteries.
-This capability expands the applicability of our method to a wider range of scenarios and enhances its practical utility.
+By introducing the shortest path($SP$) of the battery, the greedy algorithm transforms the enumeration of switch states in the brute force algorithm into the combination of the $SP$s, which greatly increases the efficiency of determining the maximum allowable current (MAC) of reconfigurable battery systems (RBSs).
+We have also provided a theoretical estimation of the improved efficiency, which is proportional to $N_s 2^{N_s - N_b} \log N_b$, where $N_s$ is the number of switches and $N_b$ is the number of batteries.
 
-	We believe that these quantitative achievements, as described in the revised abstract, effectively demonstrate the effectiveness and superiority of our proposed method.
+Here is the specific modification we made in the abstract:
+\begin{changes}
+  changes in abstract
+\end{changes}
+
+We believe that these modifications provide a more quantitative explanation of the achievements of our proposed method in the abstract. 
+Thank you once again for your valuable input, which has greatly improved the clarity and effectiveness of our paper.
+
 \end{revresponse}
@@
 \begin{revresponse}
+
+Dear Reviewer,
+
+Thank you for your valuable feedback on our manuscript.
+We have carefully considered your comments and made the necessary revisions to address the concerns raised.
+Below, we provide a detailed response to your specific points.
+
+We have expanded the literature review in the introduction section to provide a comprehensive overview of the existing RBS structures and related works on structure analysis. 
+Although many RBS structures have been proposed for different purposes, such as dynamically adjusting the output voltage, increasing energy utilization efficiency, and improving the system's ability to recover from battery failures, they also bring challenges in design and control of the systems.
+Therefore, several works on structure analysis, like the maximum switch current and the short-circuit problem, have been proposed to tackle these challenges recently.
+However, determining the MAC of RBSs remains blank accroding to our literature review.
+A straightforward method is to enumerate all possible switch states, but the complexity of this method increases exponentially with the number of switches, and has too ineffection to apply.
+
+Here is the specific modification we made in the introduction:
+\begin{changes}
+  changes in introduction
+\end{changes}
+
+Thank you once again for your comments, which have greatly improved the quality and comprehensiveness of our manuscript.
+We believe that the revised introduction section now provides a thorough review of the literature and addresses the existing research gaps in the field of RBS structures.
 
@@
 
+We appreciate and accept your suggestion and have added a clear statement of the contributions in the second-to-last paragraph of the Introduction, as shown below:
+\begin{changes}
+  changes in introduction
+\end{changes}
+
+We believe that these additions enhance the clarity of our manuscript.
+
 \end{revresponse}
@@
 
+Thank you for your valuable feedback. We have carefully considered your suggestion regarding the complexity of our proposed method and have made the following explanation to address this concern:
+
+We have derived the average time complexity of our proposed greedy algorithm-based MAC determination method to be approximately $O(2^{N_b}N_s^2\log N_b)$, where $N_b$ and $N_s$ are the number of batteries and switches, respectively.
+
+As mentioned in our response to Comment 2, there was a blank in the literature regarding MAC determination methods.
+Therefore, a brute force method have been used as a benchmark for comparison, whose time complexity is $O(2^{N_s}N_s^3)$.
+
+Since the number of switches in RBS is typically 3 to 5 times the batteries\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the method we proposed is theoretically more efficient than the brute force method.
+It has been validated by the case study in the manuscript.
+
+The detailed derivation and discussion of the above points have been added to the revised manuscript under the "Discussion".
+Here is the specific modification:
+\begin{changes}
+  changes in discussion
+\end{changes}
+
 \end{revresponse}
@@
 \begin{revresponse}
+
+The time complexity of the proposed method is $O(2^{N_b}N_s^2\log N_b)$, which still has a exponential relationship with the number of batteries.
+That means unsufferable time cost will be caused when the number of batteries is large.
 

### 2023-09-15 paper/SST/review_response.tex
更正了对 my structure 计算过程中重构结构数的结果，由7改为11

@@
 
-Thank you for your valuable feedback. We have carefully considered your suggestion and made the following modifications to address your concern:
+Thanks for the reviewer's valuable feedback. We have carefully considered this suggestion and made the following modifications to address the reviewer's concern:
 
@@
 We believe that these modifications provide a more quantitative explanation of the achievements of our proposed method in the abstract.
-Thank you once again for your valuable input, which has greatly improved the clarity and effectiveness of our paper.
 
@@
 Dear Reviewer,
-
-Thank you for your valuable feedback on our manuscript.
-We have carefully considered your comments and made the necessary revisions to address the concerns raised.
-Below, we provide a detailed response to your specific points.
 
@@
 
-Thank you once again for your comments, which have greatly improved the quality and comprehensiveness of our manuscript.
+Thanks once again for the reviewer's comments, which have greatly improved the quality and comprehensiveness of our manuscript.
 We believe that the revised introduction section now provides a thorough review of the literature and addresses the existing research gaps in the field of RBS structures.
@@
 
-Thank you for your valuable feedback. We have carefully considered your suggestion regarding the complexity of our proposed method and have made the following explanation to address this concern:
+Thanks for the reviewer's valuable feedback.
+We have carefully considered the reviewer's suggestion regarding the complexity of our proposed method and have made the following explanation to address this concern:
 
@@
 
-The time complexity of the proposed method is $O(2^{N_b}N_s^2\log N_b)$, which still has a exponential relationship with the number of batteries.
-That means unsufferable time cost will be caused when the number of batteries is large.
+We are sorry for our negligence of the limitations of the study.
+As far as we are concerned, although the method we proposed is strongly efficient than the brute force method, it still has a exponential relationship with the number of batteries, which means unsufferable time cost will be caused for systems with large number of batteries.
+
+Here is the specific content we added in the discussion:
+\begin{changes}
+  changes in discussion
+\end{changes}
 
@@
 
+We are very sorry for our incorrect writing. We have carefully checked the manuscript and corrected the typos. Thanks for the valuable feedback.
+
 \end{revresponse}
@@
 \begin{revresponse}
+
+We understand the reviewer's concern, and we agree that the explanation on the reason why the solution quality of our proposed approach is much better than the others is important to the academic value of the paper.
+However, as metioned in the response to Comment 2,
+we have not found any other works on MAC determination of RBSs, which means there is no other solution to compare with.
 
@@
 \begin{revresponse}
+
+Thanks to the reviewer's suggestion, we have introduced two novel works in the RBS structure analysis field in the introduction, which respectively study the maximum switch current \cite{han2021analysis} and the short-circuit problem \cite{chenSneakCircuitTheory2021} in RBS structures.
+We believe that these works represent the innovation and recent advances in the field of RBS structure analysis.
+
+The reviewer also specially mentioned the work published in 2023: An efficient lightweight algorithm for scheduling tasks onto dynamically reconfigurable hardware using graph-oriented simulated annealing.
+We have carefully read this paper, and after fully discussion, we finally agreed that this paper is not relevant to our research.
+Although this paper also uses a graph-based method, it mainly studies the task scheduling problem in time series, while our research is about the maximum allowable current of RBS structure, which belongs to the field of structure analysis.
+Therefore, we believe that it is not appropriate to include this paper in our introduction and will not cite it.
+
+Thanks again for the valuable feedback from the reviewer.
 
@@
 
-% \begin{revcomment}
-%   Everything else is really good.
-% \end{revcomment}
-% \begin{revresponse}
-%   We totally agree. We also added the following to the new version of the manuscript
-%   \begin{changes}
-%     This really important sentence was added to the paper.
-%   \end{changes}
-% \end{revresponse}
-
 \end{document}

### 2023-09-15 paper/SST/SST_main.tex
更正了对 my structure 计算过程中重构结构数的结果，由7改为11

--- 2023-09-13 paper/SST/SST_main.tex
@@
 % 2. 调整文献顺序，改用 biber
+% =====0915
+% my structure, my method 的计算结构数为 11，而不是 7
 
@@
 The final results are the same as the results shown in Tables \ref{tab:study-results-my}-\ref{tab:study-results-Visairo}.
-It is worth noting that the method used the greedy algorithm only calculated 7, 11, and 1 reconfigured structures for the RBS structure in Figures \ref{fig:study-stru-my}, \ref{fig:study-stru-Lawson}, \ref{fig:study-stru-Visairo}, respectively.
+It is worth noting that the method used the greedy algorithm only calculated 11, 11, and 1 reconfigured structures for the RBS structure in Figures \ref{fig:study-stru-my}, \ref{fig:study-stru-Lawson}, \ref{fig:study-stru-Visairo}, respectively.
 While for the same RBS, the method counted all possible switch states computed $2^{19}$, $2^{15}$, and $2^{13}$ structures, respectively.
@@
 This can be confirmed from the number of structures required for MAC determination in the previous subsection. 
-Compared to the brute force algorithm, the efficiency of the method based on the greedy algorithm has been improved by 3000 to 75000 times, which is theoretically $N_s 2^{N_s - N_b} \log N_b$ times according to the above time complexity analysis.
+Compared to the brute force algorithm, the efficiency of the method based on the greedy algorithm has been improved by 3000 to 48000 times, which is theoretically $N_s 2^{N_s - N_b} \log N_b$ times according to the above time complexity analysis.
 Among the three RBS structures, the highest is the RBS structure with 19 switches (Figure \ref{fig:study-stru-my}).

### 2023-09-15 paper/SST/review_response.tex
responese review (done:9/9)

@@
 %\usepackage[scaled]{beramono}
-
-\usepackage[]{biblatex}
-\bibliography{2-SST_review.bib}
-
-\usepackage{hyperref}
+\usepackage{graphicx}
+\graphicspath{ {../figures/} }
+\usepackage{subcaption}
+\usepackage{amsmath}
+\usepackage{multirow}
+\usepackage{booktabs}
+\usepackage{footnote}
+\usepackage{bm}
+\usepackage[style=nejm, citestyle=numeric-comp, sorting=none]{biblatex}
+\addbibresource{SST_main.bib}
+\usepackage{indentfirst} 
+\setlength{\parindent}{2em}
 
@@
 
-Dear Reviewer,
-
-We have expanded the literature review in the introduction section to provide a comprehensive overview of the existing RBS structures and related works on structure analysis. 
-Although many RBS structures have been proposed for different purposes, such as dynamically adjusting the output voltage, increasing energy utilization efficiency, and improving the system's ability to recover from battery failures, they also bring challenges in design and control of the systems.
+Considering the Reviewer’s suggestion, we have expanded the literature review in the introduction section to provide a comprehensive overview of the existing RBS structures \cite{ci2007novel,9209774,engelhardt2021double,visairoReconfigurableBatteryPack2008,lawsonSoftwareConfigurableBattery2012,he2014reconfiguration,kim2009dynamic} and related works on structure analysis \cite{han2021analysis,chenSneakCircuitTheory2021}.
+Although many RBS structures have been proposed for different purposes, such as dynamically adjusting the output voltage , increasing energy utilization efficiency, and improving the system's ability to recover from battery failures, they also bring challenges in design and control of the systems.
 Therefore, several works on structure analysis, like the maximum switch current and the short-circuit problem, have been proposed to tackle these challenges recently.
@@
 
-Thanks for the reviewer's valuable feedback.
-We have carefully considered the reviewer's suggestion regarding the complexity of our proposed method and have made the following explanation to address this concern:
+It is really true as Reviewer suggested about the complexity of our proposed method and the comparison with other state-of-art methods.
 
 We have derived the average time complexity of our proposed greedy algorithm-based MAC determination method to be approximately $O(2^{N_b}N_s^2\log N_b)$, where $N_b$ and $N_s$ are the number of batteries and switches, respectively.
-
-As mentioned in our response to Comment 2, there was a blank in the literature regarding MAC determination methods.
-Therefore, a brute force method have been used as a benchmark for comparison, whose time complexity is $O(2^{N_s}N_s^3)$.
-
+However, as mentioned in our response to Comment 2, there was a blank in the literature regarding MAC determination methods.
+The brute force method, the most straightforward and intuitive method, was used as a benchmark for comparison, whose time complexity is $O(2^{N_s}N_s^3)$.
 Since the number of switches in RBS is typically 3 to 5 times the batteries\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the method we proposed is theoretically more efficient than the brute force method.
@@
 
-The detailed derivation and discussion of the above points have been added to the revised manuscript under the "Discussion".
+The detailed derivation and discussion of the above points have been added to the revised manuscript under the Discussion subsection.
 Here is the specific modification:
@@
 
-We are very sorry for our incorrect writing. We have carefully checked the manuscript and corrected the typos. Thanks for the valuable feedback.
+We are very sorry for our incorrect writing, and have carefully checked the manuscript and corrected the typos.
 
@@
 
-We understand the reviewer's concern, and we agree that the explanation on the reason why the solution quality of our proposed approach is much better than the others is important to the academic value of the paper.
-However, as metioned in the response to Comment 2,
-we have not found any other works on MAC determination of RBSs, which means there is no other solution to compare with.
+We appreciate the reviewer's concern regarding the explanation of why the solution quality of our proposed approach is better to others. 
+However, after careful literature research, we would like to clarify that there are currently no existing works on the MAC determination of RBSs that we could compare our solution with. 
+Therefore, it is not possible to directly compare the solution quality of our proposed approach with others.
 
@@
 We have carefully read this paper, and after fully discussion, we finally agreed that this paper is not relevant to our research.
-Although this paper also uses a graph-based method, it mainly studies the task scheduling problem in time series, while our research is about the maximum allowable current of RBS structure, which belongs to the field of structure analysis.
+Although this paper uses a graph-based method, whose name is similar to the method described in our paper, it mainly studies the task scheduling problem in time series.
+While our research is about the maximum allowable current of RBS structure, which belongs to the field of structure analysis.
 Therefore, we believe that it is not appropriate to include this paper in our introduction and will not cite it.
-
-Thanks again for the valuable feedback from the reviewer.
 
@@
 
+TODO: explain about the accuracy, sufficiency and reliability of our results with Xu and Qian.
+
+Thanks for the reviewer's valuable feedback. We have carefully considered the reviewer's question.
+In response, we complemented the computation with the brute force method and provided more detailed explanation and discussion.
+
+In the Case Study section of the paper, we investigated the MACs of three RBS structures, two of which are from published literatures \cite{lawsonSoftwareConfigurableBattery2012,visairoReconfigurableBatteryPack2008} and the other is designed by ourselves, as shown in Figure \ref{fig:study-stru-Lawson}, \ref{fig:study-stru-Visairo} and \ref{fig:study-stru-my}, respectively.
+The results of the three RBS structures calculated by our proposed method are shown in Tables \ref{tab:study-results-Lawson-greedy}, \ref{tab:study-results-Visairo-greedy} and \ref{tab:study-results-my-greedy}, respectively.
+The results by brute force method are shown in Tables \ref{tab:study-results-Lawson-brute}, \ref{tab:study-results-Visairo-brute} and \ref{tab:study-results-my-brute}, respectively.
+
+On the one hand, as shown in the Tables \ref{tab:study-results-Lawson-greedy} to \ref{tab:study-results-my-brute}, the reconfigured structure results from our greedy algorithm are consistent with the results from the brute force algorithm, which enumerates all possible reconfigured structures.
+It shows that our algorithm does find the global optimal solution.
+On the other hand, the output current of the system calculated by our directed graph model is consistent with the experience and common sense.
+To illustrate this, the RBS structure shown in Figure \ref{fig:study-stru-my} is taken as an example here.
+The four batteries in this structure can be divided into two groups: $B_1$ and $B_2$, $B_3$ and $B_4$.
+The relationship between the two batteries in each group can be switched between series and parallel by reconfiguration.
+While the two groups can only form a series connection or be disconnected, rather than a parallel connection.
+Therefore, the MAC of this structure is the maximum of the output current of the two groups, which is twice the maximum allowable current of a single battery, consistented with the result $\max \eta = 2$ shown in Table \ref{tab:study-results-my-greedy}.
+
+We hope that our above content can address the reviewer's concerns.
+
+\begin{figure}[htbp]
+    \centering
+    \begin{subfigure}[b]{0.2\textwidth}
+        \includegraphics[width=\textwidth]{stru-L-origin.png}
+        \caption{}
+        \label{fig:study-stru-Lawson}
+    \end{subfigure}
+    \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.4\textwidth}
+        \includegraphics[width=\textwidth]{stru-V-origin.png}
+        \caption{}
+        \label{fig:study-stru-Visairo}
+    \end{subfigure}
+    \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.31\textwidth}
+        \includegraphics[width=\textwidth]{stru-my-origin.png}
+        \caption{}
+        \label{fig:study-stru-my}
+    \end{subfigure}
+    \caption{The 4-battery RBS structures proposed by (a)Lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b)Visairo\cite{visairoReconfigurableBatteryPack2008} and (c)this paper.}
+\end{figure}
+
+\begin{table}[htbp]
+  \centering
+    \caption{MAC Calculating result of the RBS structure in Figure \ref{fig:study-stru-Lawson} with our method.}
+    \begin{tabular}{cc}
+    \toprule
+        Structure & Figure \ref{fig:study-stru-Lawson} with 4 batteries and 15 switches  \\
+    \midrule
+    Switch ON & $S_1$,$S_3$,$S_5$,$S_7$,$S_{10}$,$S_{13}$,$S_{14}$,$S_{15}$ \\
+    $I_o$ & $u_b/(R_o+r_b)$ \\
+    $\bm{I}_b$ & $[u_b/(R_o+r_b),0,0,0]$ \\
+    $\max  \eta$     & 1 \\
+    computed structure count & 11 \\
+    \bottomrule
+    \end{tabular}
+  \label{tab:study-results-Lawson-greedy}
+\end{table}
+
+\begin{table}[htbp]
+  \centering
+    \caption{MAC Calculating result of the RBS structure in Figure \ref{fig:study-stru-Visairo} with our method.}
+    \begin{tabular}{cc}
+    \toprule
+        Structure & Figure \ref{fig:study-stru-Visairo} with 4 batteries and 13 switches  \\
+    \midrule
+    Switch ON & $S_1$,$S_2$,$S_3$,$S_4$,$S_5$,$S_9$,$S_{10}$,$S_{11}$,$S_{12}$,$S_{13}$ \\
+    $I_o$ & $4u_b/(4R_o+r_b)$ \\
+    $\bm{I}_b$ & $[u_b/(4R_o+r_b),u_b/(4R_o+r_b),u_b/(4R_o+r_b),u_b/(4R_o+r_b)]$ \\
+    $\max \eta$     & 4 \\
+    computed structure count & 1 \\
+    \bottomrule
+    \end{tabular}
+  \label{tab:study-results-Visairo-greedy}
+\end{table}
+
+\begin{table}[htbp]
+  \centering
+    \caption{MAC Calculating result of the RBS structure in Figure \ref{fig:study-stru-my} with our method.}
+    \begin{tabular}{cc}
+    \toprule
+        Structure & Figure \ref{fig:study-stru-my} with 4 batteries and 19 switches  \\
+    \midrule
+    Switch ON & $S_1$,$S_3$,$S_5$,$S_6$,$S_8$,$S_9$,$S_{10}$,$S_{12}$,$S_{18}$,$S_{19}$ \\
+    $I_o$ & $2u_b/(2R_o+r_b)$ \\
+    $\bm{I}_b$ & $[u_b/(2R_o+r_b),u_b/(2R_o+r_b),0,0]$ \\
+    $\max  \eta$     & 2 \\
+    computed structure count & 11 \\
+    \bottomrule
+    \end{tabular}
+  \label{tab:study-results-my-greedy}
+\end{table}
+
+\begin{table}[htbp]
+  \centering
+    \caption{MAC Calculating result of the RBS structure in Figure \ref{fig:study-stru-Lawson} with brute force method.}
+    \begin{tabular}{cc}
+    \toprule
+        Structure & Figure \ref{fig:study-stru-Lawson} with 4 batteries and 15 switches  \\
+    \midrule
+    Switch ON & $S_1$,$S_3$,$S_5$,$S_7$,$S_{10}$,$S_{13}$,$S_{14}$,$S_{15}$ \\
+    $I_o$ & $u_b/(R_o+r_b)$ \\
+    $\bm{I}_b$ & $[u_b/(R_o+r_b),0,0,0]$ \\
+    $\max \eta$     & 1 \\
+    computed structure count & 32768 \\
+    \bottomrule
+    \end{tabular}
+  \label{tab:study-results-Lawson-brute}
+\end{table}
+
+\begin{table}[htbp]
+  \centering
+    \caption{MAC Calculating result of the RBS structure in Figure \ref{fig:study-stru-Visairo} with brute force method.}
+    \begin{tabular}{cc}
+    \toprule
+        Structure & Figure \ref{fig:study-stru-Visairo} with 4 batteries and 13 switches  \\
+    \midrule
+    Switch ON & $S_1$,$S_2$,$S_3$,$S_4$,$S_5$,$S_9$,$S_{10}$,$S_{11}$,$S_{12}$,$S_{13}$ \\
+    $I_o$ & $4u_b/(4R_o+r_b)$ \\
+    $\bm{I}_b$ & $[u_b/(4R_o+r_b),u_b/(4R_o+r_b),u_b/(4R_o+r_b),u_b/(4R_o+r_b)]$ \\
+    $\max \eta$     & 4 \\
+    computed structure count & 8192 \\
+    \bottomrule
+    \end{tabular}
+  \label{tab:study-results-Visairo-brute}
+\end{table}
+
+\begin{table}[htbp]
+  \centering
+    \caption{MAC Calculating result of the RBS structure in Figure \ref{fig:study-stru-my} with brute force method.}
+    \begin{tabular}{cc}
+    \toprule
+        Structure & Figure \ref{fig:study-stru-my} with 4 batteries and 19 switches  \\
+    \midrule
+    Switch ON & $S_1$,$S_3$,$S_5$,$S_6$,$S_8$,$S_9$,$S_{10}$,$S_{12}$,$S_{18}$,$S_{19}$ \\
+    $I_o$ & $2u_b/(2R_o+r_b)$ \\
+    $\bm{I}_b$ & $[u_b/(2R_o+r_b),u_b/(2R_o+r_b),0,0]$ \\
+    $\max \eta$     & 2 \\
+    computed structure count & 524288 \\
+    \bottomrule
+    \end{tabular}
+  \label{tab:study-results-my-brute}
+\end{table}
+
 \end{revresponse}
 
+\printbibliography
+
 \end{document}

### 2023-09-15 paper/SST/2-SST_cover_letter.tex
review cover letter (done)

@@
-Dear \editorname,
+\noindent Dear \editorname,
 
-Please find enclosed the revised version of our previous submission entitled \enquote{\thetitle} with manuscript number \manuscript.
-We would like to thank you and the reviewers for the valuable comments which help improving the quality of our manuscript.
-In this revision, we have carefully addressed the reviewers' comments.
-A summary of main modifications and a detailed point-by-point response to the comments from Reviewers 1 and 3 (following the reviewers' order in the decision letter) are given below.
+On behalf of my co-authors, we thank you very much for giving us an opportunity to revise our manuscript, we appreciate editor and reviewer very much for their positive and constructive comments and suggestions on our manuscript entitled \enquote{\thetitle}(ID:\manuscript).
+
+We have studied reviewer's comments carefully and have made revision which marked in red in the paper.
+We have tried our best to revise our manuscript according to the comments.
+Specially, this manuscript has been retouched by the professional organization, to further improve the readability.
+Attached please find the revised version, which we would like to submit for your kind consideration.
+
+We would like to express our great appreciation to you and reviewers for comments on our paper. Looking forward to hearing from you.
+
+Thank you and best regards.
 
@@
 
-Sincerely,
+\noindent Sincerely,
 
@@
 
-\theauthor
-
-\vfil
-\textbf{Note:} To enhance the legibility of this response letter, all the editor's and reviewers' comments are typeset in boxes.
-Rephrased or added sentences are typeset in color.
-The respective parts in the manuscript are highlighted to indicate changes.
-
-**improve the general language expression** during revision progress.
+\noindent \theauthor

### 2023-09-15 paper/SST/2-response_reviewer1.tex
重构：重命名

--- 2023-09-15 paper/SST/review_response.tex
@@
-\documentclass[12pt,american]{scrartcl}
-\usepackage{babel}
-\usepackage[babel]{microtype}
-\usepackage[babel]{csquotes}
-
-\usepackage[journal={Space: Science \& Technology},
-      manuscript={SPACE-D-23-00082},
-      editor={Dr. Tian}]{reviewresponse}
-
-\usepackage[T1]{fontenc}
-\usepackage{lmodern}
-%\usepackage{newcent}
-%\usepackage[scaled]{beramono}
-\usepackage{graphicx}
-\graphicspath{ {../figures/} }
-\usepackage{subcaption}
-\usepackage{amsmath}
-\usepackage{multirow}
-\usepackage{booktabs}
-\usepackage{footnote}
-\usepackage{bm}
-\usepackage[style=nejm, citestyle=numeric-comp, sorting=none]{biblatex}
-\addbibresource{SST_main.bib}
-\usepackage{indentfirst} 
-\setlength{\parindent}{2em}
-
-\title{Maximum Allowable Current Determination of RBS By Using a Directed Graph Model and Greedy Algorithm}
-\author{Dr. Cheng Qian, on behalf of all authors}
-
-\begin{document}
-\maketitle
-
-% Cover Letter
-\include{2-SST_cover_letter}
-
-% Reviewer 1
 \reviewer
@@
 \end{revresponse}
-
-\printbibliography
-
-\end{document}

### 2023-09-15 paper/SST/2-main.tex
重构：重命名

--- 2023-09-15 paper/SST/SST_main.tex
@@
 \usepackage[style=nejm, citestyle=numeric-comp, sorting=none]{biblatex}
-\addbibresource{SST_main.bib}
+\addbibresource{ref.bib}
 
@@
 In this paper, we firstly propose a calculation method for the MAC of arbitrary RBS using a greedy algorithm in conjunction with a directed graph model of the RBS.
-\added{
 By introducing the shortest path of the battery, the greedy algorithm transforms the enumeration of switch states in the brute force algorithm into the combination of the shortest paths, which greatly increases the efficiency of the determination of the MAC.
@@
 The main advantage of this method is its ability to calculate the MAC of RBSs with arbitrary structures, even in the scenarios with random isolated batteries.
-}
 \deleted{

### 2023-09-15 paper/SST/2-main.tex
重构：使用latexdiff

@@
 % \usepackage[final]{changes}
-\usepackage[defaultcolor=red]{changes}
+% \usepackage[defaultcolor=red]{changes}
 % \added{xxx}
@@
 The main advantage of this method is its ability to calculate the MAC of RBSs with arbitrary structures, even in the scenarios with random isolated batteries.
-\deleted{
-In this method, a new directed graph model is developed to model the structure of RBS, and a greedy algorithm is designed to find the possible circuit that enable MAC.
-Then, the MAC is calculated based on the circuit in-cooperate with the equivalent model of batteries and switches. 
-The effectiveness of the proposed method is validated by a novel and complex RBS structure. 
-The results show that this method is capable to calculated the MAC of RBSs with different structures or different battery sizes efficiently, which proves the correctness of this method and its potential in facilitating next-generation RBS designs and applications, including battery isolation.
-}
 \end{abstract}
@@
 However, traditional BESSs, in which the batteries are connected in a fixed topology, exhibit a significant weakness in their worst battery due to the so-called cask effect.
-Moreover, if this worst battery fails \replaced{from}{during} operation, it can exacerbate the degradation of other batteries with a high possibility, leading to reliability and safety issues \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019,jeevarajanBatterySafetyQualifications2012}.
-These problems have become significant technical barriers in the development of new-generation space vehicles \replaced{unfortunately}{and urgently need to be addressed} \cite{pomboHybridPowerSystem2021}.
+Moreover, if this worst battery fails from operation, it can exacerbate the degradation of other batteries with a high possibility, leading to reliability and safety issues \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019,jeevarajanBatterySafetyQualifications2012}.
+These problems have become significant technical barriers in the development of new-generation space vehicles unfortunately \cite{pomboHybridPowerSystem2021}.
 
 Reconfigurable Battery System (RBS), which can dynamically switch to different circuit topology configurations as required, is expected to solve the above problems\cite{hanNextGenerationBatteryManagement2020a}.
-The ability of switching circuit helps to isolate unhealthy batteries, \replaced{thereby improving}{and thereby improve} the safety and reliability of the battery system.
-\replaced{In order to illustrate the working principle of RBS, a typical RBS structure developed by Visairo \cite{visairoReconfigurableBatteryPack2008}(Figure \ref{fig:stru-Visairo}) is taken as an example to show the reconfiguration process.}{Figure \ref{fig:stru-Visairo} shows a typical RBS structure developed by Visairo \cite{visairoReconfigurableBatteryPack2008} for dynamically adjusting the output voltage and current.}
+The ability of switching circuit helps to isolate unhealthy batteries, thereby improving the safety and reliability of the battery system.
+In order to illustrate the working principle of RBS, a typical RBS structure developed by Visairo \cite{visairoReconfigurableBatteryPack2008}(Figure \ref{fig:stru-Visairo}) is taken as an example to show the reconfiguration process.
 In this structure, the batteries can be connected not only in series when the switches $S_1$, $S_5$, $S_6$, $S_7$, $S_8$, $S_9$, and $S_{13}$ are closed (Figure \ref{fig:stru-Visairo-serial}), but also in parallel when $S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$, and $S_{13}$ are closed (Figure \ref{fig:stru-Visairo-parallel}).
@@
 
-\added{
 Recently, various types of RBS with different flexibility and reconfigurability have been designed to meet application requirements. 
@@
 They thoroughly analyzes all paths between the cathode and anode of each battery in the RBS and identifies paths that only contain switches as short-circuit paths for pre-checking before system reconfiguration.
-}
 
-\added{
 In spite of maximum switch current mentioned above, the maximum allowable current (MAC), defined as the maximum current allowed by system under the constraints of the battery cell, is another critical indictor of RBS that need to be evaluated during the design or control process of system.
@@
 But this method is inefficient and time-consuming, especially for RBSs with a large number of switches.
-}
 
-\deleted{
-The complex connection structure between batteries and switches in the RBS provides flexibility but also introduces challenges in design and operational control. 
-Unlike traditional BESSs with fixed outputs, the RBS output must be dynamically adjusted by controlling switch states to meet external load requirements. 
-This necessitates additional, time-consuming output performance analysis during design and corresponding control strategies. 
-An incorrect switch control strategy may cause battery short-circuiting or overload, risking the entire system. 
-The Maximum Allowable Current (MAC), an RBS performance indicator, can guide designers in addressing this issue. 
-MAC is defined as the maximum RBS output current that ensures each battery's current remains within a safe range.
-Therefore, it provides a benchmark for RBS output current, protecting individual batteries and identifying overall system output limits during operation. 
-Despite its importance, no method currently exists for automatically evaluating MAC for RBSs.
-In particular, when one or more random cells are isolated, there is still no method to determine the MAC of the remaining RBS in time to assist the system in adjusting the control strategy timely. 
-A universal and automatical method for calculating RBS MAC is urgently needed for practical applications.
-}
-
-\added{
 To solve this issue, a new method to effectively evaluate the MAC of RBS is proposed in this paper. 
@@
 To the best of our knowledge, the present work is the first to develop an efficient calculation method of RBS MAC.
-}
-\deleted{In this study, a directed graph model and greedy algorithm are employed to determine the MAC of RBS and the corresponding control strategy, effectively calculating the MAC for RBSs with arbitrary structures, including scenarios with isolated batteries.}
-\added{The main contributions of the paper can be summarized as follows:}
+The main contributions of the paper can be summarized as follows:
 \begin{itemize}
-  \item \added{Proposing a effective method to determine the MAC of RBSs with arbitrary structures, including scenarios with isolated batteries.}
-  \item \added{Application of the greedy algorithm to solve the MAC problem, whose computational complexity is greatly reduced compared with the brute force algorithm.}
-  \item \added{introducing an improved directed graph model, considering the voltage, internal resistance, and maximum allowable current of the battery, and the external load, to achieve the current analysis of the RBS.}
+  \item Proposing a effective method to determine the MAC of RBSs with arbitrary structures, including scenarios with isolated batteries.
+  \item Application of the greedy algorithm to solve the MAC problem, whose computational complexity is greatly reduced compared with the brute force algorithm.
+  \item introducing an improved directed graph model, considering the voltage, internal resistance, and maximum allowable current of the battery, and the external load, to achieve the current analysis of the RBS.
 \end{itemize}
@@
 Section III demonstrated a case study of using the proposed method to determine the MAC of a novel and complex structure. 
-The calculation results \added{, the algorithm's computational complexity} and scenarios such as batteries isolation also are discussed. 
+The calculation results, the algorithm's computational complexity and scenarios such as batteries isolation also are discussed. 
 Finally, the concluding remarks are drawn in Section IV.
@@
 To universally and automatically achieve this, the overall process is divided into four steps, as shown in Figure \ref{fig:main}.
-Firstly, a directed graph model is established for subsequent \replaced{computations.}{computing,} \replaced{The model}{, which} not only contains the connected relationships between batteries and switches, but also retains the performance parameters of the batteries.
+Firstly, a directed graph model is established for subsequent computations.
+The model not only contains the connected relationships between batteries and switches, but also retains the performance parameters of the batteries.
 Subsequently, based on the equivalent circuit, the MAC problem is transformed into specific objective functions and constraints.
-Then, the shortest paths (\replaced{$SP$}{SP}s, where additional batteries and switches on the path are penalized as distance) for the batteries are obtained using the Dijkstra algorithm to guide the batteries in the RBS connect in parallel.
-Finally, a greedy algorithm is employed to organize the switches, allowing the batteries to connect via their \replaced{$SP$}{SP}s while satisfying the constraints, resulting in the MAC of the RBS.
+Then, the shortest paths ($SP$s, where additional batteries and switches on the path are penalized as distance) for the batteries are obtained using the Dijkstra algorithm to guide the batteries in the RBS connect in parallel.
+Finally, a greedy algorithm is employed to organize the switches, allowing the batteries to connect via their $SP$s while satisfying the constraints, resulting in the MAC of the RBS.
 
@@
     \caption{ 
-        Directed graph models used in (a) He's work \cite{heExploringAdaptiveReconfiguration2013}, (b) our previous work , and (c) \added{the improved model in} this paper.
+        Directed graph models used in (a) He's work \cite{heExploringAdaptiveReconfiguration2013}, (b) our previous work , and (c) the improved model in this paper.
         (d) The equivalent circuit of a battery in this method.
@@
 \cite{heExploringAdaptiveReconfiguration2013} once proposed an abstracted directed graph model for RBS, where the nodes represented the batteries, the edges represented the configuration flexibility, and the weight of each vertex corresponded to the battery voltage ( Figure \ref{fig:direct-graph-he}).
-The model effectively captured all potential system configurations and offered a direct metric for configuration flexibility, but it did not specify the physical implementation of the connectivity between batteries, meaning one graph might \replaced{correspond to}{have had} multiple RBS structures.
-We previously proposed a novel directed graph model that, \replaced{completely different from}{in contrast to} He's model, used nodes to represent the connections between batteries and switches, and directed edges to represent batteries and switches (Figure \ref{fig:direct-graph-xu}), allowing for a one-to-one correspondence between the RBS structure and the directed graph model.
-This model was able to accurately and comprehensively represent the RBS topological structure but could not be used for quantitative MAC calculations due to the lack of consideration \replaced{on}{for} \replaced{the voltage, internal resistance and maximum allowable current of the battery}{battery and switch performance parameters}.
-To address this, an \replaced{improvement on our previous model is conducted by}{improved directed graph model is used here based on our original model,} adding electromotive force and resistance attributes on the edges based \replaced{on its}{to} equivalent circuits \deleted{(Figure \ref{fig:direct-graph-my})}.
+The model effectively captured all potential system configurations and offered a direct metric for configuration flexibility, but it did not specify the physical implementation of the connectivity between batteries, meaning one graph might correspond to multiple RBS structures.
+We previously proposed a novel directed graph model that, completely different from He's model, used nodes to represent the connections between batteries and switches, and directed edges to represent batteries and switches (Figure \ref{fig:direct-graph-xu}), allowing for a one-to-one correspondence between the RBS structure and the directed graph model.
+This model was able to accurately and comprehensively represent the RBS topological structure but could not be used for quantitative MAC calculations due to the lack of consideration on the voltage, internal resistance and maximum allowable current of the battery.
+To address this, an improvement on our previous model is conducted by adding electromotive force and resistance attributes on the edges based on its equivalent circuits .
 The model also considers the external load as an equivalent resistance and integrate it into the analysis, making it a complete circuit model for later circuit analysis.
-\added{Figure \ref{fig:direct-graph-my} shows the improved directed graph model used in this paper.}
+Figure \ref{fig:direct-graph-my} shows the improved directed graph model used in this paper.
 The following will provide a detailed explanation of the method for equating the components in RBS and constructing the directed graph model.
@@
 In order to use circuit analysis methods to solve the MAC of the RBS, the components in the RBS are equated to ideal circuit elements.
-\added{For instance,} \replaced{a}{A}s shown in Figure \ref{fig:battery_simple}, the battery in the RBS can be represented as a black-box circuit consisting of two resistors (i.e., $r_1$ and $r_2$) and a capacitor (i.e., $C$), known as the Thevenin model\cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
+For instance, as shown in Figure \ref{fig:battery_simple}, the battery in the RBS can be represented as a black-box circuit consisting of two resistors (i.e., $r_1$ and $r_2$) and a capacitor (i.e., $C$), known as the Thevenin model\cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
 With an emphasis on the stable output of the RBS, the capacitor in the Thevenin model can be considered as an open circuit without affecting the steady-state current.
@@
 
-For a given RBS structure, \replaced{its directed graph model $G(V,E)$ is constructed as follows:}{the directed graph model for the RBS is constructed as a directed graph $G(V,E)$ in such a way that:}
+For a given RBS structure, its directed graph model $G(V,E)$ is constructed as follows:
 \begin{enumerate}
@@
 
-\replaced{For a given RBS, determination of its MAC}{Based on the definition of MAC, determining the MAC of RBS} involves maximizing the RBS output current while ensuring that the currents of all batteries do not exceed the batteries' maximum allowable current.
-In this subsection, the constraints and objective function to solve the RBS's MAC will be established through circuit analysis, based on \replaced{its directed graph model provided in the previous subsection}{the previously constructed directed graph model}.
+For a given RBS, determination of its MAC involves maximizing the RBS output current while ensuring that the currents of all batteries do not exceed the batteries' maximum allowable current. 
+In this subsection, the constraints and objective function to solve the RBS's MAC will be established through circuit analysis, based on its directed graph model provided in the previous subsection.
 
-First, the topology in the directed graph model is represented in matrix form $\bm{A}$, known as the incidence matrix , \replaced{defined}{to facilitate circuit analysis.
-The specific definition of the incidence matrix is shown} in Equation \ref{eq:A}.
+First, the topology in the directed graph model is represented in matrix form $\bm{A}$, known as the incidence matrix , defined in Equation \ref{eq:A}.
 \begin{align}\label{eq:A}
@@
 Since each directed edge has one node to leave and one to enter, the sum of the values in every column of $\bm{A}$ is zero.
-Therefore removing \replaced{the last}{any single one} row will not result in a loss of information. 
-\deleted{Without loss of generality, the last row is removed here.}
+Therefore removing the last row will not result in a loss of information. 
 On the other hand, since each switch in the RBS is represented by a pair of directed edges with two-way directions, the two columns corresponding to the switch are mutually opposite.
@@
 while the elements of the array $\bm{U}_s$ are equal to the first attribute of the corresponding edges in the directed graph.
-The $\bm{Y}$ in \added{Equation} \ref{eq:generalized_branches} is the admittance matrix of the circuit, defined as the inverse of the impedance matrix.
-\replaced{The}{That is the} elements \replaced{on}{of} the diagonal \added{of} matrix $\bm{Y}$ are equal to the reciprocal of \added{the resistance, which is} the second attribute of the corresponding edges in the directed graph, and the off-diagonal elements \added{$\bm{Y}$} are 0.
+The $\bm{Y}$ in Equation \ref{eq:generalized_branches} is the admittance matrix of the circuit, defined as the inverse of the impedance matrix.
+The elements on the diagonal of matrix $\bm{Y}$ are equal to the reciprocal of the resistance, which is the second attribute of the corresponding edges in the directed graph, and the off-diagonal elements $\bm{Y}$ are 0.
 The $\bm{X}$ is the state matrix, which describes whether the RBS batteries and switches are allowed to pass current.
@@
 
-However, it is \added{still} computationally difficult to solve \ref{eq:max_eta} because of the $\bm{Y}_n^{-1}$.
-On one hand, due to the introduction of nonlinear terms by $\bm{Y}_n^{-1}$, many effective methods in linear optimization are not suitable for this \replaced{scenario}{problem}.
+However, it is still computationally difficult to solve \ref{eq:max_eta} because of the $\bm{Y}_n^{-1}$.
+On one hand, due to the introduction of nonlinear terms by $\bm{Y}_n^{-1}$, many effective methods in linear optimization are not suitable for this scenario.
 On the other hand, the rank of $Y_{n}$ is proportional to the number of batteries and switches, which can be very large for a large RBS system, leading to significant computational burden.
-Therefore, intelligent algorithms that rely on evolving by iteration may face efficiency \replaced{problem}{issues} when dealing with large RBS system.
+Therefore, intelligent algorithms that rely on evolving by iteration may face efficiency problem when dealing with large RBS system.
 In order to address this issue, the problem should be considered from the perspective of guiding the RBS to reconstruct as many parallel structures as possible.
@@
 \cite{visairoReconfigurableBatteryPack2008} and Lawson et al.
-\cite{lawsonSoftwareConfigurableBattery2012}, both of which have been \replaced{practically used}{applied in practice}.
-The primary goal of Visairo's structure (Figure \ref{fig:study-stru-Visairo}) was to achieve dynamic adjustment of RBS output \added{power}; however, the isolation of unhealthy batteries was not sufficiently addressed \added{in their work}.
-\deleted{When batteries need to be isolated in the RBS of Visairo's structure, the methods for isolating them and the subsequent changes in RBS output warrant further investigation.}
-Lawson et al.
-\replaced{designed the RBS structure shown in Figure \ref{fig:study-stru-Lawson} for the purpose of battery isolation}{conducted research on battery isolation in RBS and specifically designed the structure shown in Figure \ref{fig:study-stru-Lawson}}.
+\cite{lawsonSoftwareConfigurableBattery2012}, both of which have been practically used.
+The primary goal of Visairo's structure (Figure \ref{fig:study-stru-Visairo}) was to achieve dynamic adjustment of RBS output power; however, the isolation of unhealthy batteries was not sufficiently addressed in their work.
+Lawson et al. designed the RBS structure shown in Figure \ref{fig:study-stru-Lawson} for the purpose of battery isolation. 
 This structure has the advantage of easily isolating batteries, but it cannot dynamically adjust the output current of RBS. 
-Based on the structures of Visairo and Lawson, this paper presents a new structure, as shown in Figure \ref{fig:study-stru-my}\deleted{, which combines the advantages of both}.
+Based on the structures of Visairo and Lawson, this paper presents a new structure, as shown in Figure \ref{fig:study-stru-my}.
 By integrating the Visairo RBS structure into the Lawson RBS structure, the new structure not only allows the flexibility to switch the batteries between series, parallel, and mixed series-parallel modes, but also easily enables the isolation of highly degraded batteries from the RBS.
@@
     $\bm{I}_b$ & $[u_b/(2R_o+r_b),u_b/(2R_o+r_b),0,0]$ \\
-    \added{$\max$}$\eta$     & 2 \\
+    $\max$$\eta$     & 2 \\
     \bottomrule
@@
 Similarly, the MAC calculation results of the structures in Figures \ref{fig:study-stru-Lawson} and \ref{fig:study-stru-Visairo} are shown as Table \ref{tab:study-results-Lawson} and Table \ref{tab:study-results-Visairo}, respectively.
-\added{
 In order to verify and compare the results from the greedy algorithm, we also utilized a brute force algorithm that go through all possible switch states to calculate the MAC of the same three RBS. 
@@
 While for the same RBS, the method counted all possible switch states computed $2^{19}$, $2^{15}$, and $2^{13}$ structures, respectively.
-}
 
@@
     $\bm{I}_b$ & $[u_b/(R_o+r_b),0,0,0]$ \\
-    \added{$\max$}$\eta$     & 1 \\
+    $\max \eta$     & 1 \\
     \bottomrule
@@
     $\bm{I}_b$ & $[u_b/(4R_o+r_b),u_b/(4R_o+r_b),u_b/(4R_o+r_b),u_b/(4R_o+r_b)]$ \\
-    \added{$\max$}$\eta$     & 4 \\
+    $\max \eta$     & 4 \\
     \bottomrule
@@
 
-Furthermore, the RBS \replaced{with}{under the scenario of} isolated batteries is taken into consideration and calculated. 
+Furthermore, the RBS with isolated batteries is taken into consideration and calculated. 
 The MAC calculation results for the three structures under study, with varying numbers of isolated batteries, are presented in Table \ref{tab:isolated_mac}. 
 Figures \ref{fig:my-isolated-1}-\ref{fig:my-isolated-3} illustrate the corresponding switch control schemes for the new structure proposed in this paper under different isolated battery conditions.
-\deleted{The characteristics of these three structures in the context of battery isolation will be discussed in the next subsection.}
 
@@
 
-\replaced{As shown in Figure \ref{fig:all-results-my} and Table \ref{tab:study-results-my}}{In this subsection, we firstly discuss the correctness of the results presented in Figure \ref{fig:all-results-my} and Table \ref{tab:study-results-my}}.
+As shown in Figure \ref{fig:all-results-my} and Table \ref{tab:study-results-my}.
 When $B_1$ and $B_2$ or $B_3$ and $B_4$ are connected in parallel, the RBS can output the maximum current, which is $\eta=2$, i.e., twice the current output of a single battery in RBS. 
@@
 Therefore, the switches state given in Table \ref{tab:study-results-my} can make the RBS output current reach the maximum.
-\added{The results of MAC obtained by brute force algorithm method is identical to the one by the greedy algorithm.}
+The results of MAC obtained by brute force algorithm method is identical to the one by the greedy algorithm.
 
-\added{
 From the literature research we have conducted, no formal report on the algorithm for MAC in RBS has been found yet.
@@
 However, the greedy algorithm proposed in this paper still contains exponential terms in the time complexity, which means it may not be able to handle extremely large-scale RBS structures.
-}
 
-It is important to note that \deleted{when solving for MAC,} $\eta$ is used as the objective function instead of $I_o$ \added{in solving MAC}. 
+It is important to note that $\eta$ is used as the objective function instead of $I_o$ in solving MAC. 
 This choice makes the result of MAC more reasonable. 
 As shown in Table \ref{tab:study-results-my}, $I_o$ and $\bm{I}_b$ are functions of $R_o$, $u_b$, and $r_b$. 
-\replaced{However, when}{If} $I_o$ \replaced{was}{were} used as the objective function, even for the same RBS structure, the MAC \replaced{solution}{result} and corresponding switches state could change due to different external electrical appliances.
+However, when $I_o$ was used as the objective function, even for the same RBS structure, the MAC solution and corresponding switches state could change due to different external electrical appliances.
 It would increase the difficulty and uncertainty in RBS structure design. 
-\replaced{In order to eliminate the influences of such a problem, $\eta$, which is the ratio of $I_o$ and $\max\bm{I}_b$, is adopted as the objective function in our research.}{In contrast, by using $\eta$ as the objective function, which is defined as the ratio of $I_o$ and $\max\bm{I}_b$, the influence of these factors on the results can be eliminated.}
+In order to eliminate the influences of such a problem, $\eta$, which is the ratio of $I_o$ and $\max\bm{I}_b$, is adopted as the objective function in our research.
 $\eta$ solely reflects the maximum output current capability of the RBS structure. 
 Assuming that the maximum allowed current of batteries in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by determining the $\eta$ of the structure.
-\deleted{Therefore, compared to $I_o$, $\eta$ is more suitable for structure design.}
 
-The method proposed in this paper is significant for the design of \deleted{next-generation} RBSs in the following aspects.
+The method proposed in this paper is significant for the design of RBSs in the following aspects.
 Most of the currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} exhibit simple topological characteristics, and the calculation of MACs is relatively straightforward, even intuitive.
 However, these simple structures do not always fully satisfy the requirements of complex applications, such as dynamically adapting the circuit to variable and random operating conditions, and actively equalizing differences among the batteries in the RBS.
-Moreover, \replaced{isolation of}{isolating} the batteries disrupts the original regularity and symmetry of the topology, which complicates the otherwise simple structure, and the maximum output current of the system becomes more challenging to obtain.
-\replaced{On the contrary}{Owing to the advantages of pervasiveness and automation}, the proposed method can be employed to calculate the MAC of arbitrary RBS structures, \replaced{especially for these above complex and flexible RBS structures}{which helps to address the aforementioned issues and paves the way for more complex and flexible RBS structure design}.
+Moreover, isolation of the batteries disrupts the original regularity and symmetry of the topology, which complicates the otherwise simple structure, and the maximum output current of the system becomes more challenging to obtain.
+On the contrary, the proposed method can be employed to calculate the MAC of arbitrary RBS structures, especially for these above complex and flexible RBS structures.
 
-To illustrate this point, the MACs of \deleted{the} three RBS structures mentioned above are calculated after \replaced{one and more}{the} batteries are isolated, as shown in Table \ref{tab:isolated_mac}.
-Specifically, for the structure presented in Figure \ref{fig:study-stru-my}, the corresponding circuit states of MACs \replaced{of}{when} isolating \replaced{one to three}{different numbers of} batteries are depicted in Figures \ref{fig:my-isolated-1}-\ref{fig:my-isolated-3}.
+To illustrate this point, the MACs of three RBS structures mentioned above are calculated after one and more batteries are isolated, as shown in Table \ref{tab:isolated_mac}. 
+Specifically, for the structure presented in Figure \ref{fig:study-stru-my}, the corresponding circuit states of MACs of isolating one to three batteries are depicted in Figures \ref{fig:my-isolated-1}-\ref{fig:my-isolated-3}.
 This structure has two cases of isolating two batteries: 
 one is to isolate two batteries within the same substructure (Figure \ref{fig:my-isolated-2b}), in which case $\eta=2$; the other is to isolate one battery in each of the two substructures (Figure \ref{fig:my-isolated-2w}), in which case $\eta=1$.
-From the results \added{shown in Figure \ref{fig:my-isolated-1}-\ref{fig:my-isolated-3}}, it can be observed that the proposed method provides reasonable outcomes for isolating batteries with any number and position.
+From the results shown in Figure \ref{fig:my-isolated-1}-\ref{fig:my-isolated-3}, it can be observed that the proposed method provides reasonable outcomes for isolating batteries with any number and position.
 
-Furthermore, the \deleted{performance of} output current for the three RBS \replaced{with isolated}{when isolating} batteries is also shown in Table \ref{tab:isolated_mac}. 
-For the structure proposed by Lawson et al., the MAC \replaced{is independent on the number of isolated batteries}{remains the same as that without isolated battery cells, i.e., $\eta=1$, when the number of isolated battery cells increases, until all the cells in the RBS are isolated}.
-\added{However,} \replaced{f}{F}or Visairo's structure, the MAC decreases \replaced{with the increasing number of isolated batteries}{as the number of isolated battery cells increases, until $\eta=0$}.
-\replaced{Nevertherless}{In contrast}, the MAC of the structure proposed in this work is positioned between \replaced{these above}{the} two structures. 
-This indicates that the structure proposed in this paper, compared to Lawson's structure, has a larger MAC under the same number of batteries, \replaced{and exhibits}{which means} a wider output current regulation range.
-\deleted{On the other hand, by simply changing the states of $S_2$, $S_4$, $S_{11}$, and $S_{12}$ in the conversion structure, this structure can address the majority of battery isolation scenarios, whereas Visairo's structure requires specific battery targeting and switch control.}
-\deleted{In summary, the structure proposed in this paper has the advantages of both Lawson's and Visairo's structures.}
+Furthermore, the output current for the three RBS with isolated batteries is also shown in Table \ref{tab:isolated_mac}. 
+For the structure proposed by Lawson et al., the MAC is independent on the number of isolated batteries.
+However, for Visairo's structure, the MAC decreases with the increasing number of isolated batteries. 
+Nevertherless, the MAC of the structure proposed in this work is positioned between these above two structures. 
+This indicates that the structure proposed in this paper, compared to Lawson's structure, has a larger MAC under the same number of batteries, and exhibits a wider output current regulation range.
 
@@
 
-This paper proposes a pervasive and automatical method for computing the MAC of \replaced{a}{the} given RBS \added{efficiently}.
-\added{
+This paper proposes a pervasive and automatical method for computing the MAC of a given RBS efficiently.
 The method is implemented by a greedy algorithm combined with a directed graph model which considers the voltage, internal resistance, and maximum allowable current of the batteries, as well as the external load.
@@
 This method helps to fully tap the current output potential of the RBS, guide the RBS structure design and optimization in the design stage, and assist in evaluating the current overload risk of the system in practical applications.
-}
-\deleted{The method is implemented by a greedy algorithm combined with a directed graph model , whose effectiveness is tested on a novel and complex RBS structure.
-The method remains effective for the application scenario of RBS battery isolation and demonstrates that the novel structure has the advantage on flexible output current and convenient battery isolation.
-Future research could focus on developing new indictors to evaluate the performance of the RBS with the currents and voltages obtained by the method, as well as modifying the equivalent model of the battery to allow for more accurate simulations of the RBS, including transient analysis.}
 
@@
             \eIf{$\bm{Y}_n$ is invertible}{
-              \added{pass}
+              pass
             }{construct an effective solution}

### 2023-09-17 paper/SST/SST_main_polished.tex
添加了润色机构返回的版本：SST_main_polished

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{setspace}
\usepackage[margin=1.25in]{geometry}
\usepackage{graphicx}
% \graphicspath{ {./figures/} }
\graphicspath{ {../figures/} }
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{lineno}
% \linenumbers

\usepackage{enumerate}
\DeclareMathOperator{\diag}{diag}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{footnote}
\usepackage{bm}
\usepackage[ruled,linesnumbered]{algorithm2e}
\setcounter{MaxMatrixCols}{20}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, calc, fit, positioning, quotes, graphs, shapes.geometric}
\def\T{\mathrm{T}}

\usepackage[final]{changes}
% \usepackage[defaultcolor=red]{changes}
% \added{xxx}
% \deleted{xxxx}
% \replaced{a}{b}

%%%%%% Bibliography %%%%%%
% Replace "sample" in the \addbibresource line below with the name of your .bib file.
\usepackage[style=nejm, citestyle=numeric-comp, sorting=none]{biblatex}
\addbibresource{SST_main.bib}

%%%%%% Title %%%%%%
% Full titles can be a maximum of 100 characters, including spaces. 
% Title Format: Use title case, capitalizing the first letter of each word, except for certain small words, such as articles and short prepositions
\title{Using a Directed Graph Model and Greedy Algorithm to Determine the Maximum Allowable Current in a Reconfigurable Battery System}

%%%%%% Authors %%%%%%
% Authors should be listed in order of contribution to the paper, by first name, then middle initial (if any), followed by last name.
% Authors should be listed in the order in which they will appear in the published version if the manuscript is accepted. 
% Use an asterisk (*) to identify the corresponding author, and be sure to include that person’s e-mail address. Use symbols (in this order: †, ‡, §, ||, ¶, #, ††, ‡‡, etc.) for author notes, such as present addresses, “These authors contributed equally to this work” notations, and similar information.
% You can include group authors, but please include a list of the actual authors (the group members) in the Supplementary Materials.
\author[1]{30577}
% \author[1$\dag$]{Binghui Xu}
% \author[1$\dag$]{Guangbin Hua}
% \author[1*]{Cheng Qian}
% \author[1,2]{Quan Xia}
% \author[1]{Bo Sun}
% \author[1]{Yi Ren}
% \author[1]{Zili Wang}

%%%%%% Affiliations %%%%%%
% \affil[1]{School of Reliability and Systems Engineering, Beihang University, Beijing, 100191, China}
% \affil[2]{School of Aeronautic Science and Engineering at Beihang University, Beijing, China}
% \affil[*]{Address correspondence to: cqian@buaa.edu.cn}
% \affil[$\dag$]{These authors contributed equally to this work.}

%%%%%% Date %%%%%%
% Date is optional
\date{}

%%%%%% Spacing %%%%%%
% Use paragraph spacing of 1.5 or 2 (for double spacing, use command \doublespacing)
\onehalfspacing

\begin{document}

\maketitle

%%%%%% Abstract %%%%%%
\begin{abstract}
Reconfigurable battery systems (RBSs) present a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structure that can be adapted to different battery charging and discharging strategies.
During RBS operation, the maximum allowable current (MAC) of the system that ensures that each battery's current remains within a safe range is a critical indicator to guide the system's reconfiguration, ensuring its safety and reliability. 
This paper proposes a method to calculate the MAC of arbitrary RBSs using a greedy algorithm in conjunction with a directed graph model of the RBS.
\added{
By introducing the shortest path of the battery, the greedy algorithm transforms the enumeration of switch states in the brute-force algorithm into the combination of the shortest paths, which greatly increases the efficiency with which the MAC is determined.
The directed graph model, based on the equivalent circuit, provides a specific method for calculating the MAC of a given structure.
The proposed method is validated on two published 4-battery-RBSs and one with a more complex structure.
The results are the same as those of the brute-force algorithm, but the proposed method significantly improves the computational efficiency ($N_s 2^{N_s - N_b} \log_{10} N_b$ times faster than the brute force algorithm for a RBS with $N_b$ batteries and $N_s$ switches, theoretically).
The main advantage of the proposed method is its ability to calculate the MAC of RBSs with arbitrary structures, even in scenarios with random isolated batteries.
}
\deleted{
In this method, a new directed graph model is developed to model the structure of RBS, and a greedy algorithm is designed to find the possible circuit that enable MAC.
Then, the MAC is calculated based on the circuit in-cooperate with the equivalent model of batteries and switches. 
The effectiveness of the proposed method is validated by a novel and complex RBS structure. 
The results show that this method is capable to calculated the MAC of RBSs with different structures or different battery sizes efficiently, which proves the correctness of this method and its potential in facilitating next-generation RBS designs and applications, including battery isolation.
}
\end{abstract}

%%%%%% Main Text %%%%%%

\section{Introduction}

Battery energy storage systems (BESSs) are extensively used in various applications, such as wind power plants and space power systems, to store and release high-quality electrical energy \cite{desiqueiraControlStrategySmooth2021,yangBatteryEnergyStorage2018,choCommercialResearchBattery2015,zhangDevelopmentProspectChinese2021,schwanbeckInternationalSpaceStation2019}.
Typically, a BESS consists of numerous batteries interconnected by series-parallel circuitry to provide the required capacity storage.
However, traditional BESSs, in which the batteries are connected in a fixed topology, suffer from a significant weakness in their worst battery due to the so-called cask effect.
Moreover, if the worst battery fails during operation, it is highly likely to exacerbate the degradation of the other batteries, leading to reliability and safety issues \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019,jeevarajanBatterySafetyQualifications2012}.
These problems have become significant technical barriers in the development of new-generation space vehicles and need to be addressed \cite{pomboHybridPowerSystem2021}.

Reconfigurable battery systems (RBSs), which can dynamically switch as required to different circuit topologies, are expected to solve this problem \cite{hanNextGenerationBatteryManagement2020a}.
The switching circuit helps to isolate unhealthy batteries, thereby improving the safety and reliability of the battery system.
\replaced{To illustrate the working principle of an RBS, we consider a typical RBS structure developed by Visairo \cite{visairoReconfigurableBatteryPack2008} (Fig. \ref{fig:stru-Visairo}), which is taken as an example to show the reconfiguration process.} {Figure \ref{fig:stru-Visairo} shows a typical RBS structure developed by Visairo \cite{visairoReconfigurableBatteryPack2008} for dynamically adjusting the output voltage and current.}
In this structure, the batteries can be connected not only in series when the switches $S_1$, $S_5$, $S_6$, $S_7$, $S_8$, $S_9$, and $S_{13}$ are closed (see Fig. \ref{fig:stru-Visairo-serial}) but also in parallel when $S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$, and $S_{13}$ are closed (Fig. \ref{fig:stru-Visairo-parallel}).
Furthermore, when an unhealthy battery, for instance, the orange one $B_3$ in Fig. \ref{fig:stru-Visairo-isolate}, appears in the RBS, it can be isolated by opening its two adjacent switches (i.e., $S_4$ and $S_{11}$), ensuring that the system remains in a reliable working mode.

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figures/stru-V-origin.png}
        \caption{}
        \label{fig:stru-Visairo}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figures/stru-V-serial.png}
        \caption{}
        \label{fig:stru-Visairo-serial}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figures/stru-V-parallel.png}
        \caption{}
        \label{fig:stru-Visairo-parallel}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figures/stru-V-isolate.png}
        \caption{}
        \label{fig:stru-Visairo-isolate}
    \end{subfigure}
    \caption{
        (a) The RBS structure proposed by Visairo\cite{visairoReconfigurableBatteryPack2008}, with
        all batteries in (b) series connection, (c) parallel connection, and
        (d) battery $B_3$ isolated.
        }
    \label{fig:arch}
\end{figure}

Recently, various types of RBSs with different flexibility and reconfigurability have been designed to meet application requirements. 
For example, Ci et al. \cite{ci2007novel} proposed an RBS structure that dynamically adjusts the battery discharge rate to fully exploit the available capacity of each battery. 
Jan's \cite{9209774,engelhardt2021double} structures  reconfigure structures with variant batteries in series to reach the (constantly changing) voltage requirements during electric vehicle charging.
As shown in Fig. \ref{fig:stru-Visairo}, the structure proposed by Visairo et al. \cite{visairoReconfigurableBatteryPack2008}  changes the system's output voltage based on the load conditions, thereby reducing the power loss of the voltage regulator during the power supply process and improving the efficiency of energy use. 
Also, to enhance the energy efficiency of the system, Lawson et al. \cite{lawsonSoftwareConfigurableBattery2012} and He et al. \cite{he2014reconfiguration}  proposed simplified structures that have fewer switches than Visairo's design.
Kim et al. \cite{kim2009dynamic} improved the system's ability to recover from battery failures by introducing multiple ports into the structure.

The complex structure between batteries and switches gives RBSs flexibility but also creates challenges in the design and control of the system. 
Thus, several approaches to analyze the RBS structure and performance have been proposed to tackle these challenges.
For instance, 
Han et al. \cite{han2021analysis} derived an analytical expression for the maximum switch current during battery system reconfiguration for a specific RBS structure. 
This helps guide the selection of switches and supports the design of RBS hardware.
Chen et al. \cite{chenSneakCircuitTheory2021} proposed a systematic approach based on  sneak circuit theory to fundamentally avoid the short-circuit problem of RBSs: 
They thoroughly analyzed all paths between the cathode and anode of each battery in the RBS and identified paths that only contain switches as short-circuit paths for pre-checking before system reconfiguration.

\added{
In spite of the maximum switch current mentioned above, the maximum allowable current (MAC), defined as the maximum allowed current  under the constraints of the battery cell, is another critical indicator of RBSs that needs to be evaluated during the design or control  of the system. 
The MAC helps the designers assess whether the RBS meets the output current requirements and contributes to the formulation of appropriate and safe management strategies for the battery management system.
Unfortunately, few studies have analyzed the RBS structure to determine the RBS MAC.
An intuitive and straightforward method is to enumerate all possible switch states and calculate the output current of the system under each reconfigurated structure.
However, this method is inefficient and time-consuming, especially for RBSs with a large number of switches.
}

\deleted{
The complex connection structure between batteries and switches in the RBS provides flexibility but also introduces challenges in design and operational control. 
Unlike traditional BESSs with fixed outputs, the RBS output must be dynamically adjusted by controlling switch states to meet external load requirements. 
This necessitates additional, time-consuming output performance analysis during design and corresponding control strategies. 
An incorrect switch control strategy may cause battery short-circuiting or overload, risking the entire system. 
The Maximum Allowable Current (MAC), an RBS performance indicator, can guide designers in addressing this issue. 
MAC is defined as the maximum RBS output current that ensures each battery's current remains within a safe range.
Therefore, it provides a benchmark for RBS output current, protecting individual batteries and identifying overall system output limits during operation. 
Despite its importance, no method currently exists for automatically evaluating MAC for RBSs.
In particular, when one or more random cells are isolated, there is still no method to determine the MAC of the remaining RBS in time to assist the system in adjusting the control strategy timely. 
A universal and automatical method for calculating RBS MAC is urgently needed for practical applications.
}

\added{
To solve this issue, this paper proposes an efficient method to evaluate the MAC of RBSs. 
First, a greedy algorithm is designed to efficiently search the possible circuit topology of RBSs with MAC.
Moreover, the method provides an improved direct graph model that considers the voltage, the internal resistance, the MAC of the battery, and the external load. The method obtains the accurate current of the RBS under a specific circuit topology. 
}
\deleted{In this study, a directed graph model and greedy algorithm are employed to determine the MAC of RBS and the corresponding control strategy, effectively calculating the MAC for RBSs with arbitrary structures, including scenarios with isolated batteries.}
\added{The main contributions of this paper can be summarized as follows:}
\begin{itemize}
  \item \added{An efficient method is proposed to determine the MAC of RBSs with arbitrary structures, including scenarios with isolated batteries.}
  \item \added{The greedy algorithm is applied to solve the MAC problem, the computational complexity of which is greatly reduced compared with the brute-force algorithm.}
  \item \added{An improved directed graph model is introduced; it considers the voltage, the internal resistance, the MAC of the battery, and the external load to analyze the current of the RBS.}
\end{itemize}

The remainder of this paper is organized as follows: 
Section II presents the framework and details of the proposed directed graph model and  greedy algorithm. 
Section III discusses a case study that uses the proposed method to determine the MAC of a novel, complex structure. 
The calculation results, the algorithm's computational complexity, and scenarios such as battery isolation are also discussed. 
Finally, the concluding remarks are presented in Sec. IV.

\section{Methodology}

The central principle of this method is to connect the batteries in an RBS in parallel to the extent possible, thereby maximizing the output current of the RBS.
To achieve this universally and automatically, the overall process is divided into the four steps shown in Fig. \ref{fig:main}.
First, a directed graph model is established for subsequent \replaced{computations.}{computing,} \replaced{The model}{, which} not only contains the connected relationships between batteries and switches but also retains the performance parameters of the batteries.
Subsequently, based on the equivalent circuit, the MAC problem is transformed into specific objective functions and constraints.
The shortest paths (\replaced{$SP$}{SP}s, where additional batteries and switches on the path are penalized as distance) for the batteries are then obtained  by using the Dijkstra algorithm to connect the batteries in the RBS in parallel.
Finally, a greedy algorithm is used to organize the switches, allowing the batteries to connect via their \replaced{$SP$}{SP}s while satisfying the constraints, resulting in the MAC of the RBS.

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=\textwidth]{figures/main.png}
    \end{subfigure}
    \caption{ 
        Diagram of this method, which contains four main steps.
    }
    \label{fig:main}
\end{figure}

\subsection{Directed graph model}

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{figures/direct-graph-he.png}
        \caption{}
        \label{fig:direct-graph-he}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{figures/direct-graph-xu.png}
        \caption{}
        \label{fig:direct-graph-xu}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{figures/direct-graph-my.png}
        \caption{}
        \label{fig:direct-graph-my}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=\textwidth]{figures/battery_simple.png}
        \caption{}
        \label{fig:battery_simple}
    \end{subfigure}
    \caption{ 
        Directed graph models used in (a) He's work \cite{heExploringAdaptiveReconfiguration2013}, (b) our previous work, and (c) \added{the improved model in} this paper.
        (d) The equivalent circuit of a battery in this method.
    }
\end{figure}

He et al. \cite{heExploringAdaptiveReconfiguration2013} proposed an abstracted directed graph model for an RBS, where the nodes represent the batteries, the edges represent the configuration flexibility, and the weight of each vertex corresponds to the battery voltage (Fig. \ref{fig:direct-graph-he}). 
The model captures all potential system configurations and offers a direct metric for configuration flexibility, but it does not specify the physical implementation of the connectivity between batteries, meaning that one graph might \replaced{correspond to}{have had} multiple RBS structures.
We previously proposed a directed graph model that \replaced{differs completely from}{in contrast to} He's model by using nodes to represent the connections between batteries and switches and directed edges to represent batteries and switches (Fig. \ref{fig:direct-graph-xu}), allowing for a one-to-one correspondence between the RBS structure and the directed graph model. 
This model accurately and comprehensively represents the RBS topological structure but cannot be used for quantitative MAC calculations because it does not consider  \replaced{the voltage, internal resistance, and MAC of the battery}{battery and switch performance parameters}. 
To address this issue, \replaced{we improve our previous model by}{improved directed graph model is used here based on our original model,} adding electromotive force and resistance attributes on the edges based \replaced{on its}{to} equivalent circuits\deleted{(Fig. \ref{fig:direct-graph-my})}.
The model also considers the external load as an equivalent resistance and integrates it into the analysis, making it a complete circuit model for later circuit analyses.
\added{Fig. \ref{fig:direct-graph-my} shows the improved directed graph model used in this paper.}
The following  provides a detailed explanation of the method for equating components in RBSs and constructing the directed graph model.

To use circuit analysis methods to solve the MAC of the RBS, the components in the RBS are equated to ideal circuit elements.
\added{For instance,} \replaced{a}{A}s shown in Fig. \ref{fig:battery_simple}, the battery in the RBS can be represented as a black-box circuit consisting of two resistors $r_1$ and $r_2$ and a capacitor  $C$, known as the Thevenin model \cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
With an emphasis on the stable output of the RBS, the capacitor in the Thevenin model can be considered as an open circuit without affecting the steady-state current.
Therefore,  battery $i$ in the RBS can be simplified as a series connection between a constant voltage source $u_{i}$ and a resistor $r_{i}$.
Furthermore, the state of switch $j$ in the RBS is represented by a binary variable $x_j$, where 0 is ON and 1 is OFF.
When the switch is closed, the circuit can be regarded as a resistor with a very small resistance $r_{j}$.
Finally, the external load is considered as a resistor with resistance $R_o$.

For a given RBS structure, \replaced{its directed graph model $G(V,E)$ is constructed as follows:}{the directed graph model for the RBS is constructed as a directed graph $G(V,E)$ in such a way that:}
\begin{enumerate}
    \item Nodes:
        The nodes in the directed graph correspond to the connection points of components in the actual RBS. 
        Assuming there are a total of $N$ nodes in the RBS, for the sake of convenience, the anode of the RBS is denoted as $v_1$ and the cathode as $v_N$.
    \item Edges:
        The edges in the directed graph correspond to the batteries, switches, and external electrical loads in the actual RBS.
        Therefore, there are three types of directed edges. 
        For a battery $B_i$, its directed edge $e_i$ is drawn from the cathode to the anode because the battery in operation only allows current to flow in one direction.
        For a switch $S_j$, since it is allowed to work under bi-directional currents, it is represented by a pair of directed edges with two-way directions. 
        Regarding the external electronic load, because it is connected to the anode and cathode of the RBS, a directed edge from $v_N$ to $v_1$  represents it. 
        In conclusion, for a given RBS structure with $N_b$ batteries and $N_s$ switches, the number of directed edges is $N_b+2N_s+1$, where 1 refers to the external electrical load.
    \item Attributes of edges:
        Each edge is assigned two attributes, voltage difference and resistance, based on the equivalent method mentioned above.
        The values for  battery $B_i$, switch $S_j$, and external loads correspond to $(u_i, r_i)$, $(0, r_j)$, and $(0, R_o)$, respectively.
\end{enumerate}

\subsection{Constraints and objective function}

\replaced{For a given RBS, determining its MAC}{Based on the definition of MAC, determining the MAC of RBS} involves maximizing the RBS output current while ensuring that the sum of the currents of all batteries does not exceed the batteries' MAC. 
This subsection establishes the constraints and objective function to determine the RBS's MAC  through circuit analysis based on \replaced{the directed graph model provided in the previous section}{the previously constructed directed graph model}.

First, the topology in the directed graph model is represented in matrix form $\bm{A}$, known as the incidence matrix and \replaced{defined}{to facilitate circuit analysis.
The specific definition of the incidence matrix is shown} as follows:
\begin{align}\label{eq:A}
    a_{kl}=
    \begin{cases}
        1,  & \text{edge $l$ leaves node $k$},\\
        -1, & \text{edge $l$ enters node $k$},\\
        0,  & \text{otherwise}.
    \end{cases}
\end{align}
For a directed graph consisting of $N$ nodes and $N_b+2N_s+1$ directed edges, its incidence matrix $\bm{A}$ is an $N\times(N_b+2N_s+1)$ matrix. 
In this matrix, the rows and columns represent the nodes and edges of the directed graph, respectively.
By distinguishing the components in the RBS corresponding to each column, $\bm{A}$ can be rewritten as
\begin{equation}\label{eq:A_bso}
    \bm{A} =
    \begin{bmatrix}
        \bm{A}_b & \bm{A}_s & \bm{A}_o
    \end{bmatrix},
\end{equation}
where $\bm{A}_b$, $\bm{A}_s$, and $\bm{A}_o$ are the sub-matrices corresponding to the batteries, switches, and external electrical load, respectively.
To reduce the computational complexity, the dimensions of matrix $\bm{A}$ are reduced.
Since each directed edge has one node to leave and one to enter, the values in every column of $\bm{A}$ sum to zero.
Therefore, removing \replaced{the last}{any single one} row will not result in a loss of information. 
\deleted{Without loss of generality, the last row is removed here.}
Conversely, since each switch in the RBS is represented by a pair of directed edges with two-way directions, the two columns corresponding to the switch are mutually opposite.
Thus, for the submatrix $\bm{A}_s$, only one column is retained for each pair of columns representing the same switch.
As a result, $\bm{A}$ can be reduced to an $(N-1)\times(N_b+N_s+1)$ matrix, denoted  $\bm{\tilde{A}}$, for further calculation of current and voltage.
Similar to Eq. (\ref{eq:A_bso}), $\bm{\tilde{A}}$ can be rewritten as
\begin{equation}\label{eq:A_bso_tilde}
    \bm{\tilde{A}} =
    \begin{bmatrix}
        \bm{\tilde{A}}_b & \bm{\tilde{A}}_s & \bm{\tilde{A}}_o
    \end{bmatrix}.
\end{equation}

After obtaining the incidence matrix, the currents of all batteries and output in the RBS are determined by solving the circuit equations.
According to Kirchhoff's law, we have
\begin{align}\label{eq:Kirchhoffs_law}
    \begin{cases}
        \bm{\tilde{A}} \bm{I} = \bm{0}, \\
        \bm{U}        = \bm{\tilde{A}}^\T \bm{U}_n,
    \end{cases}
\end{align}
where $\bm{I}$ and $\bm{U}$ indicate the current and voltage difference arrays of the $N_b+N_s+1$ edges, respectively, and
$\bm{U}_n$ is the voltage array of the $N-1$ nodes.
These directed edges are treated as generalized branches and expressed in matrix form as follows:
\begin{equation}\label{eq:generalized_branches}
    \bm{I} = \bm{Y}\bm{X} \bm{U} - \bm{Y}\bm{X} \bm{U}_s +\bm{I}_s,
\end{equation}
where $\bm{U}_s$ and $\bm{I}_s$ denote the source voltage and source current of the generalized branches, respectively.
Because all batteries have been equivalent to voltage sources rather than current sources in the previous section, all elements of the array $\bm{I}_s$ are zero, 
whereas the elements of the array $\bm{U}_s$ are equal to the first attribute of the corresponding edges in the directed graph.
The matrix $\bm{Y}$ in \added{Eq.} (\ref{eq:generalized_branches}) is the admittance matrix of the circuit and is defined as the inverse of the impedance matrix.
\replaced{The}{That is the} elements \replaced{on}{of} the diagonal \added{of} matrix $\bm{Y}$ are equal to the reciprocal of \added{the resistance, which is} the second attribute of the corresponding edges in the directed graph. The off-diagonal elements of \added{$\bm{Y}$} are zero.
$\bm{X}$ is the state matrix that determines whether the RBS batteries and switches can pass current.
It is defined as
\begin{equation}\label{eq:X}
    \bm{X} = \diag(
    \underbrace{1, 0, \dots, 1}_{N_b~\text{of}~0/1},
    \underbrace{1, 0, \dots, 1}_{N_s~\text{of}~0/1},
    1)
    =\begin{bmatrix}
        \bm{X}_b & & \\
        & \bm{X}_s &\\
        & & 1
    \end{bmatrix},
\end{equation}
where element $x_i$ of matrix $\bm{X}_b$ indicates whether battery $i$ has been removed from the circuit, with $x_i=1$ indicating removal and $x_i=0$ indicating that battery $i$ is still available to supply power. 
When all batteries are healthy and capable of providing current to the external load, $\bm{X}_b$ is the identity matrix. 
The elements $x_j$ of  matrix $\bm{X}_s$ determine whether switch $j$ is closed, with $x_j=1$ indicating a closed switch and $x_j=0$ indicating an open switch, which is consistent with the previous section.

Theoretically, the output current $I_o$ and the currents of each battery $\bm{I}_b$ in the RBS  can be determined by solving Eqs. (\ref{eq:Kirchhoffs_law})--(\ref{eq:X}) under any given state $\bm{X}$.
To obtain specific constraint conditions and objective functions, it is further assumed that all batteries have the same electromotive force and internal resistance, which are denoted $u_b$ and $r_b$, respectively.
This allows us to derive explicit expressions for $I_o$ and $\bm{I}_b$.
After derivation and simplification, the output current $I_o$ and the currents of each battery $\bm{I}_b$ are ultimately represented as Eqs. (\ref{eq:I_o}) and (\ref{eq:I_b}), respectively:
\begin{eqnarray}\label{eq:I_o}
    I_o &=& \frac{1}{R_o r_b} \bm{\tilde{A}}_o^\T \bm{Y}_n^{-1}(\bm{X}) \bm{\tilde{A}}_b \bm{U}_b,
\\\label{eq:I_b}
    \bm{I}_b &=& \frac{1}{r_b^2}[\bm{\tilde{A}}_b^\T \bm{Y}_n^{-1}(\bm{X}) \bm{\tilde{A}}_b\bm{U}_b -r_b \bm{U}_b],
\end{eqnarray}
where $\bm{U}_b$ is an $N_b\times 1$ array with all elements equal to $u_b$,
and $\bm{Y}_n$ is the equivalent admittance matrix of the circuit and is defined as
\begin{equation}\label{eq:Yn}
    \bm{Y}_n (\bm{X}) = \frac{1}{R_o} \bm{\tilde{A}}_o\bm{\tilde{A}}_o^\T + \frac{1}{r_b} \bm{\tilde{A}}_b\bm{X}_b\bm{\tilde{A}}_b^\T + \frac{1}{r_s}\bm{\tilde{A}}_s\bm{X}_s\bm{\tilde{A}}_s^\T.
\end{equation}

To characterize the current output capacity of the RBS structure under different switching states, an indicator $\eta$ is defined by the ratio of $I_o$ to $\max (\bm{I}_b)$:
\begin{equation}\label{eq:eta}
    \eta = \frac{I_o}{\max (\bm{I}_b)}.
\end{equation}
Finally the problem of finding the MAC can be formulated as
\begin{align}
    & \max \eta(\bm{X}_s) \label{eq:max_eta}\\
    \text{s.t. } & \max (\bm{I}_b) \leq I_m, \label{eq:Ib_leq_Im}
\end{align}
where $I_m$ is the MAC of the battery.

However, it remains computationally difficult to solve Eq. (\ref{eq:max_eta}) because of $\bm{Y}_n^{-1}$.
On one hand,  the introduction of nonlinear terms by $\bm{Y}_n^{-1}$ renders many  methods in linear optimization unsuitable for this problem.
On the other hand, the rank of $Y_{n}$ is proportional to the number of batteries and switches, which can be very large for a large RBS, leading to a significant computational burden.
As a result, intelligent algorithms that rely on evolution by iteration may face efficiency problems when dealing with a large RBS.
To address this issue, the problem should be considered from the perspective of guiding the RBS to reconstruct as many parallel structures as possible.
Consequently, a greedy algorithm based on the shortest path is proposed. 
The detailed implementation of this algorithm is presented in the following two sections.

\subsection{Shortest path}

The path $p$ used in this method is defined as the complete route that passes through one battery (or a consecutive series of batteries) and closed switches, connecting the anode $v_1$ to the cathode $v_N$ of the RBS.
By applying a penalty to the series-connected batteries on the path, where additional batteries imply a greater distance, the algorithm encourages the RBS to form parallel structures to the extent possible.
In addition, to reduce the number of switches controlled during the reconstruction process, a penalty is also applied to the total number of switches on the path while ensuring the minimum number of batteries.
Therefore, the distance $\omega$ of path $p$ is  
\begin{equation}\label{eq:weight}
    \omega(p) = N_s  n_b (p) + n_s (p),
\end{equation}
where $N_s$ is the total number of switches in the system, 
and $n_b(p)$ and $n_s(p)$ are number of batteries and switches in path $p$, respectively. 
Moreover, the shortest path $SP_i$ is defined as the path with the minimum $\omega$ for battery $i$:
\begin{equation}\label{eq:def_sp}
    SP_i = \mathop{\arg\min}_{p \in P_i} \omega(p),
\end{equation}
where $P_i$ is the set of all paths from $v_1$ to $v_N$ that pass through directed edge $i$.

$SP_i$ can be solved by the Dijkstra algorithm.
The Dijkstra algorithm is a graph-search method that finds the shortest path between two given nodes in a weighted graph, efficiently solving the single-source shortest-path problem.
Denoting the cathode and anode of battery $i$ as $v_i^-$ and $v_i^+$ respectively, then path $p$ of battery $i$  can be divided into three segments: $v_1 \rightarrow v_i^-$, $v_i^+ \rightarrow v_N$, and $v_i^- \rightarrow v_i^+$. $v_i^- \rightarrow v_i^+$ is the directed edge corresponding to battery $i$. 
With the Dijkstra algorithm, shortest paths for $v_1 \rightarrow v_i^-$ and $v_i^+ \rightarrow v_N$ can be calculated under the weights given in Eq. (\ref{eq:weight}) and denoted $SP(v_i^- \rightarrow v_i^+)$ and $SP(v_i^+ \rightarrow v_N)$, respectively.
Finally, $SP_i$ for battery $i$ is formed by the complete path, which consists of $SP(v_1 \rightarrow v_i^-)$, $v_i^- \rightarrow v_i^+$, and $SP(v_i^+ \rightarrow v_N)$.

\subsection{Greedy algorithm}\label{subsec:greedy_solution}

From the perspective of series vs parallel connections, integrating more batteries into the circuit through their shortest paths ($SP$s) results in more batteries connected in parallel, thereby increasing the total output current of the RBS.
However, conflicts may arise between the $SP$s of different batteries. 
For instance, the $SP$s of two batteries might form a short-circuit RBS structure, which is not allowed. 
To address this issue, a greedy algorithm incorporates as many $SP$s as possible while satisfying the reconstruction requirements.

The algorithm (see pseudo-code in Algorithm 1) is illustrated in Fig. \ref{fig:flowchart} and is summarized as follows:
First, the $SP$s are obtained by using Eqs. (\ref{eq:weight}) and (\ref{eq:def_sp}) in conjunction with the Dijkstra search. 
Next, the matrix $\bm{A}$ is calculated using Eq. (\ref{eq:A}), and the initial $N_{\text{set}}$ is set to $N_b$. 
The algorithm uses a dichotomy method to iteratively check until convergence different combinations of $c_b$ batteries from $N_b$ and updates $N_{\text{set}}$. 
For each combination, the algorithm constructs an effective solution if possible and calculates the currents $I_o$ and $\bm{I}_b$ by using Eqs. (\ref{eq:I_o}) and (\ref{eq:I_b}). 
If the maximum current $\bm{I}_b$ is less than or equal to $I_m$, $\eta$ is calculated by using Eq. (\ref{eq:eta}), and the maximum $\eta$ is updated accordingly. 
Finally, the algorithm outputs the maximum $\eta$ once $N_{\text{set}}$ converges.

% \tikzset{
%   meta box/.style={draw, black, very thick, text centered, },
%   punkt/.style={meta box, rectangle, rounded corners, inner sep=.25em, minimum height=2em, minimum width=4em, align=center, text width=10em },
%   round/.style={meta box, circle, minimum size=0, inner sep=0pt, outer sep=0pt },
%   every fit/.style={draw, thick, dashed, gray, inner xsep=.5em, inner ysep=.75em }
% }
% \begin{figure}
% \begin{tikzpicture}[font=\small, node font=\small, node distance=1.5em]
%     \node[punkt]     (input) {Input: RBS structure};
%     \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Equations \ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
%     \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Equation \ref{eq:A}};
%     \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{\text{set}}=N_b$ };
%     \node[punkt, below=0.3of get_Nset] (get_cb) {get $c_b$s by combinating $N_{\text{set}}$ batteries from $N_b$};
%     \node[draw, diamond, aspect=2, below=0.3of get_cb] (is_check_all_cb) {are all $c_b$s checked?};
%     \node[draw, diamond, aspect=2, right=1of is_check_all_cb] (is_Nset_converged) {is $N_{\text{set}}$ converged?};
%     \node[punkt, above=of is_Nset_converged] (reset_Nset) {reset $N_{\text{set}}$ by dichotomy};
%     \node[punkt, text width=15em, below=0.3of is_check_all_cb] (get_Xs) {
%         select an unchecked $c_b$, and get its $\bm{X}_m$ by \\ 
%         if switch $j$ $\in \bigcup_{i\in c_b}SP_i$:\\
%         $\bm{X}[j]=1$ else $0$};
%     \node[punkt, below=0.3of get_Xs] (get_Yn) {get $\bm{Y}_n$ by Equation \ref{eq:Yn}};
%     \node[draw, diamond, aspect=2, below=0.3of get_Yn] (is_Yn_invertible) {is $\bm{Y}_n$ invertible?};
%     \node[punkt, right=1.3of is_Yn_invertible] (construct) {construct an effective solution};
%     \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Equations \ref{eq:I_o} and \ref{eq:I_b}};
%     \node[draw, diamond, aspect=2, below=0.3of get_I] (is_leq_Im) {is $\max \bm{I}_b \leq I_m$?};
%     \node[punkt, right=1.3of is_leq_Im] (drop_eta) {drop this $\eta$};
%     \node[punkt, below=0.3of is_leq_Im] (get_eta) {get $\eta$ by Equation \ref{eq:eta}};
%     \node[punkt, below=0.3of get_eta] (update_max_eta) {update $\max \eta$};
%     \node[punkt, right=1of is_Nset_converged] (output) {Output: $\max \eta$};
%     \node[round,left=1.5of update_max_eta](point1){};
% 
%     \graph{
%       (input) -> (get_SP) -> (get_A) -> (get_Nset) -> (get_cb) -> (is_check_all_cb) ->["No"] (get_Xs) -> (get_Yn) -> (is_Yn_invertible) ->["Yes"] (get_I) -> (is_leq_Im) ->["Yes"] (get_eta) -> (update_max_eta);
%       (is_check_all_cb) ->["Yes"] (is_Nset_converged) ->["No"] (reset_Nset) -> (get_cb);
%       (is_Yn_invertible) ->["No"] (construct) ->[to path={|- (\tikztotarget)}] (get_I);
%       (is_leq_Im) ->["No"] (drop_eta) ->[to path={|- (\tikztotarget)}] (update_max_eta);
%       (is_Nset_converged) ->["Yes"] (output);
%       (update_max_eta) -- (point1) ->[to path={|- (\tikztotarget)}] (is_check_all_cb);
%     };
% \end{tikzpicture}
% \caption{The computational flowchart of the MAC for a given RBS.}\label{fig:flowchart}
% \end{figure}

\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{figures/flowchart.jpg}
    \caption{Computational flowchart of MAC for a given RBS.}\label{fig:flowchart}
\end{figure}

\section{Case Study}

\subsection{Structures}

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.2\textwidth}
        \includegraphics[width=\textwidth]{figures/stru-L-origin.png}
        \caption{}
        \label{fig:study-stru-Lawson}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/stru-V-origin.png}
        \caption{}
        \label{fig:study-stru-Visairo}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{figures/stru-my-origin.png}
        \caption{}
        \label{fig:study-stru-my}
    \end{subfigure}
    \caption{The four-battery RBS structures proposed by (a) Lawson \cite{lawsonSoftwareConfigurableBattery2012}, (b) Visairo \cite{visairoReconfigurableBatteryPack2008}, and (c) this paper.}
\end{figure}

Currently, two types of RBS structures have been proposed by Visairo et al. \cite{visairoReconfigurableBatteryPack2008} and Lawson et al. \cite{lawsonSoftwareConfigurableBattery2012}, both of which have seen real use. 
The primary goal of Visairo's structure (Fig. \ref{fig:study-stru-Visairo}) is to dynamically adjust the RBS output \added{power}. However, the isolation of unhealthy batteries is not sufficiently addressed \added{in their work}. 
\deleted{When batteries need to be isolated in the RBS of Visairo's structure, the methods for isolating them and the subsequent changes in RBS output warrant further investigation.}
Lawson et al. \replaced{designed the RBS structure shown in Fig. \ref{fig:study-stru-Lawson} to isolate batteries}{conducted research on battery isolation in RBS and specifically designed the structure shown in Fig. \ref{fig:study-stru-Lawson}}. 
Although this structure easily isolates batteries, it cannot dynamically adjust the output current of the RBS. 
Based on the structures of Visairo and Lawson, this paper proposes the structure shown in Fig. \ref{fig:study-stru-my}\deleted{, which combines the advantages of both}.
By integrating the Visairo RBS structure into the Lawson RBS structure, the proposed structure not only has the flexibility to switch the batteries between series, parallel, and mixed series-parallel modes but also allows the isolation of highly degraded batteries from the RBS.
Their variation in output current under battery isolation will be studied.
This RBS structure is used to validate the proposed method for calculating the MAC and is compared with Lawson's and Visairo's structure to demonstrate its advantages for battery isolation.

\subsection{Result}

As shown in Fig. \ref{fig:study-stru-my}, the new RBS structure consists of four batteries and 19 switches. 
Figure \ref{fig:study-dirgraph-my} shows the corresponding directed graph, which is composed of 18 nodes and 43 edges. 
Batteries $B_1$, $B_2$, $B_3$, and $B_4$ are denoted by green directed edges in the graph, and the 19 switches are represented by gray directed edges with bidirectional arrows. 
The external electrical load is treated as a directed edge from the cathode of the RBS (i.e., node 18) to the anode (i.e., node 1), as indicated by the blue directed edge in the graph.
Using Eq. (\ref{eq:weight}) and the Dijkstra algorithm, the $SP$s of the four batteries in the RBS structure of Fig. \ref{fig:study-stru-my} are highlighted in red in Figs. \ref{fig:sp1} and \ref{fig:sp4}.
Finally, the calculated MACs of the structure in Fig. \ref{fig:study-stru-my} are listed in Table \ref{tab:study-results-my} and Fig. \ref{fig:study-results-my}, as obtained by the greedy algorithm 1. % \ref{alg:greedy}.
Table \ref{tab:study-results-my} contains the states of the switches, the output current $I_o$, the battery current $\bm{I}_b$, and the ratio $\eta$ of the RBS structure with all batteries in good health when the RBS output reaches the MAC.
Figure \ref{fig:study-results-my} presents the corresponding circuit, with the red highlight indicating that the current is flowing through the respective branches.

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{figures/ef-topo.png}
        \caption{}
        \label{fig:study-dirgraph-my}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{figures/ef-sp1.png}
        \caption{}
        \label{fig:sp1}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{figures/ef-sp2.png}
        \caption{}
        \label{fig:sp2}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{figures/ef-sp3.png}
        \caption{}
        \label{fig:sp3}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{figures/ef-sp4.png}
        \caption{}
        \label{fig:sp4}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{figures/ef-mac.png}
        \caption{}
        \label{fig:study-results-my}
    \end{subfigure}
    \caption{
        For the RBS structure in Fig. \ref{fig:study-stru-my}, 
        (a) its directed graph 
        and the $SP$s (highlighted in red) of battery (b) $B_1$, (c) $B_2$, (d) $B_3$, and (e) $B_4$.
        (f) Circuit of RBS with its output reaching the MAC.
        }
    \label{fig:all-results-my}
\end{figure}

\begin{table}[htbp]
  \centering
    \caption{Calculated MAC for four-battery RBS structure in Fig. \ref{fig:study-stru-my}.}
    \begin{tabular}{cc}
    \toprule
        Structure & Figure \ref{fig:study-stru-my} with four batteries and 19 switches  \\
    \midrule
    Switch on & $S_1$,$S_3$,$S_5$,$S_6$,$S_8$,$S_9$,$S_{10}$,$S_{12}$,$S_{18}$,$S_{19}$ \\
    $I_o$ & $2u_b/(2R_o+r_b)$ \\
    $\bm{I}_b$ & $[u_b/(2R_o+r_b),u_b/(2R_o+r_b),0,0]$ \\
    \added{$\max$}$\eta$     & 2 \\
    \bottomrule
    \end{tabular}
  \label{tab:study-results-my}
\end{table}

Similarly, the results of the MAC calculation for the structures in Figs. \ref{fig:study-stru-Lawson} and \ref{fig:study-stru-Visairo} are listed in Tables \ref{tab:study-results-Lawson} and  \ref{tab:study-results-Visairo}, respectively.
\added{
To verify and compare the results from the greedy algorithm, we also used a brute-force algorithm that iterates through all possible switch states to calculate the MAC of the same three RBSs. 
For a given RBS structure with $N_s$ switches, the final $\max \eta$ is the maximum $\eta$ from all $2^{N_s}$ reconfigured structures.
The final results are the same as the results shown in Tables \ref{tab:study-results-my}--\ref{tab:study-results-Visairo}.
The method uses the greedy algorithm to calculate 7, 11, and 1 reconfigured structures for the RBS structure in Figs. \ref{fig:study-stru-my}, \ref{fig:study-stru-Lawson}, and \ref{fig:study-stru-Visairo}, respectively. 
For the same RBS, the method counts all possible switch states, which equates to $2^{19}$, $2^{15}$, and $2^{13}$ structures, respectively.
}

\begin{table}[htbp]
  \centering
    \caption{MAC Calculating result of the 4-battery RBS structure in Fig. \ref{fig:study-stru-Lawson}.}
    \begin{tabular}{cc}
    \toprule
        Structure & Figure \ref{fig:study-stru-Lawson} with 4 batteries and 15 switches  \\
    \midrule
    Switch ON & $S_1$,$S_3$,$S_5$,$S_7$,$S_{10}$,$S_{13}$,$S_{14}$,$S_{15}$ \\
    $I_o$ & $u_b/(R_o+r_b)$ \\
    $\bm{I}_b$ & $[u_b/(R_o+r_b),0,0,0]$ \\
    \added{$\max$}$\eta$     & 1 \\
    \bottomrule
    \end{tabular}
  \label{tab:study-results-Lawson}
\end{table}

\begin{table}[htbp]
  \centering
    \caption{MAC Calculating result of the 4-battery RBS structure in Fig. \ref{fig:study-stru-Visairo}.}
    \begin{tabular}{cc}
    \toprule
        Structure & Figure \ref{fig:study-stru-Visairo} with 4 batteries and 13 switches  \\
    \midrule
    Switch ON & $S_1$,$S_2$,$S_3$,$S_4$,$S_5$,$S_9$,$S_{10}$,$S_{11}$,$S_{12}$,$S_{13}$ \\
    $I_o$ & $4u_b/(4R_o+r_b)$ \\
    $\bm{I}_b$ & $[u_b/(4R_o+r_b),u_b/(4R_o+r_b),u_b/(4R_o+r_b),u_b/(4R_o+r_b)]$ \\
    \added{$\max$}$\eta$     & 4 \\
    \bottomrule
    \end{tabular}
  \label{tab:study-results-Visairo}
\end{table}

Furthermore, the RBS \replaced{with}{under the scenario of} isolated batteries is taken into consideration and calculated. 
The MAC calculation results for the three structures under study, with varying numbers of isolated batteries, are presented in Table \ref{tab:isolated_mac}. 
Figures \ref{fig:my-isolated-1}--\ref{fig:my-isolated-3} illustrate the corresponding switch-control schemes for the new structure proposed in this paper under different conditions of isolated batteries.
\deleted{The characteristics of these three structures in the context of battery isolation will be discussed in the next subsection.}

\begin{table}[htbp]
    \centering
    \caption{
      Variation of MAC with the number of isolated batteries for different RBS structures, including the structure proposed by Lawson et al., Visairo et al., and the structure proposed in this paper.
      }
      \label{tab:isolated_mac}
      \begin{tabular}{cccc}
      \toprule
      \multirow{2}[4]{*}{Number of isolated batteries} & \multicolumn{3}{c}{$\eta$ of RBS structure} \\
  \cmidrule{2-4}          & This paper  & Visairo  & Lawson  \\
      \midrule
      0     & 2     & 4     & 1 \\
      1     & 2     & 3     & 1 \\
      2     & 2$^{\mathrm{a}}$ or 1$^{\mathrm{b}}$ & 2     & 1 \\
      3     & 1     & 1     & 1 \\
      \bottomrule
      \end{tabular}
      \\
      \footnotesize{$^{\mathrm{a}}$ Isolate two batteries within the same substructure, as shown in Fig. \ref{fig:my-isolated-2b}.}\\
      \footnotesize{$^{\mathrm{b}}$ Isolate one battery in each of the two substructures, as shown in Fig. \ref{fig:my-isolated-2w}.}
  \end{table}

  \begin{figure}[htbp]
      \centering
      \begin{subfigure}[b]{0.31\textwidth}
          \includegraphics[width=\textwidth]{figures/my-isolated-1.png}
          \caption{}
          \label{fig:my-isolated-1}
      \end{subfigure}
      \hspace{0.02\textwidth}
      \begin{subfigure}[b]{0.31\textwidth}
          \includegraphics[width=\textwidth]{figures/my-isolated-2b.png}
          \caption{}
          \label{fig:my-isolated-2b}
      \end{subfigure}
      \\
      \begin{subfigure}[b]{0.31\textwidth}
          \includegraphics[width=\textwidth]{figures/my-isolated-2w.png}
          \caption{}
          \label{fig:my-isolated-2w}
      \end{subfigure}
      \hspace{0.02\textwidth}
      \begin{subfigure}[b]{0.31\textwidth}
          \includegraphics[width=\textwidth]{figures/my-isolated-3.png}
          \caption{}
          \label{fig:my-isolated-3}
      \end{subfigure}
      \caption{
          Circuit states of MACs when isolating (a) one, (b) two (best case), (c) two (worst case), and (d) three batteries for the structure in Fig. \ref{fig:study-stru-my}.
          }
  \end{figure}

\subsection{Discussion}

\replaced{Consider first the results shown in Fig. \ref{fig:all-results-my} and Table \ref{tab:study-results-my}}{In this subsection, we firstly discuss the correctness of the results presented in Fig. \ref{fig:all-results-my} and Table \ref{tab:study-results-my}}.
When $B_1$ and $B_2$ or $B_3$ and $B_4$ are connected in parallel, the RBS outputs the maximum current, which is $\eta=2$ (i.e., twice the current output of a single battery in the RBS). 
Adding more batteries to the main circuit only forms a series structure and does not improve the MAC. 
Therefore, the state of the switches given in Table \ref{tab:study-results-my} maximizes the RBS output current.
\added{The MAC obtained by the brute-force algorithm is identical to the one obtained by the greedy algorithm.}

The literature contains no report on an algorithm for calculating the MAC of an RBS.
The brute-force algorithm, which goes through all possible switch states, is the most straightforward way to determine the MAC and is used as a benchmark for the proposed greedy algorithm.
If an RBS has $N_b$ batteries and $N_s$ switches and the corresponding directed graph has $N$ nodes,  $2^{N_s}$ iterations are required to traverse all reconfigured structures.
Calculating each reconfigured structure using Eqs. (\ref{eq:I_o})--(\ref{eq:eta}) requires matrix inversion and matrix multiplication, which has a time complexity of $O(N^3+2N^2N_b+N^2N_s+NN^2_b)$.
Therefore, the time complexity of the brute-force algorithm is $O\bm(2^{N_s}(N^3+2N^2N_b+N^2N_s+NN^2_b)\bm)$.
The greedy algorithm proposed in this paper requires  that $SP$ be found for each battery, which requires $N_b$ iterations.
Each $SP$ can be obtained by several applications of Dijkstra's algorithms.
Therefore, the total time complexity for calculating all $SP$s is $O\bm(2N_b(N_b+2N_s)\log_{10} N\bm)$.
According to  Appendix 1, % \ref{alg:greedy},
the RBS can reconfigure $C^{N_{\text{set}}}_{N_b}$ structures by selecting $N_{\text{set}}$ batteries from $N_b$ batteries, which gives $\sum^{N_b}_{N_{\text{set}}=1}C^{N_{\text{set}}}_{N_b}/N_b \approx 2^{N_b}/N_b$ on average.
Thus, with the bisection method, the time complexity of the greedy algorithm is $O\bm(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log_{10} N_b+2N_b(N_b+2N_s)\log_{10} N\bm)$ [i.e., $O\bm(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log_{10} N_b\bm)$].
Based on currently proposed RBS structures \cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the number $N_b$ of batteries, $N_s$ of switches, and $N$ of nodes are quantitatively related as follows: $N_s \approx (3\text{--} 5)N_b$, $N \approx N_s$. 
After simplifying, the time complexity of the greedy algorithm is $O(2^{N_b}N_s^2\log N_b)$, while it is $O(2^{N_s}N_s^3)$ for brute force algorithm.
Therefore, as the RBS grows, especially in the number of switches, the greedy algorithm gains an advantage over the brute-force algorithm.

This is confirmed by the number of structures required to determine the MAC in the previous section. 
Compared with the brute-force algorithm, the method based on the greedy algorithm is 3000 to 75\,000 times more efficient, which is theoretically $N_s 2^{N_s - N_b} \log_{10} N_b$ times according to the above time-complexity analysis.
Of the three RBS structures, the largest is the RBS structure with 19 switches (Fig. \ref{fig:study-stru-my}).
This benefits from two key points:
\begin{enumerate}
\item[(1)] The $SP$s guide the RBS to reconfigure reasonable structures rather than blindly going through all possible structures. This reduces the complexity from $2^{N_s}$ to $2^{N_b}$, which is the main reason for the improvement in efficiency.
\item[(2)] The bisection method further accelerates this process.
However, the greedy algorithm proposed in this paper still contains exponential terms in the time complexity, which means it may not be able to handle extremely large RBS structures. 
\end{enumerate}

Note that \deleted{when solving for MAC,} $\eta$ is used as the objective function instead of $I_o$ \added{in solving for the MAC}. 
This choice makes the resulting MAC more reasonable. 
As shown in Table \ref{tab:study-results-my}, $I_o$ and $\bm{I}_b$ are functions of $R_o$, $u_b$, and $r_b$. 
\replaced{However, when}{If} $I_o$ \replaced{is}{were} used as the objective function, even for the same RBS structure, the MAC \replaced{solution}{result} and corresponding switch states could change due to different external electrical appliances.
This would increase the difficulty and uncertainty of designing the RBS structure. 
\replaced{To eliminate this problem, the ratio $\eta=I_o/\max\bm{I}_b$ is adopted as the objective function in our research.}{In contrast, by using $\eta$ as the objective function, which is defined as the ratio of $I_o$ and $\max\bm{I}_b$, the influence of these factors on the results can be eliminated.}
Recall that $\eta$ reflects only the MAC of the RBS structure. 
Assuming that the MAC of batteries in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by determining the value of $\eta$ for the structure. 
\deleted{Therefore, compared to $I_o$, $\eta$ is more suitable for structure design.}

The method proposed in this paper facilitates the design of \deleted{next-generation} RBSs in the following ways:
Most currently proposed RBS structures \cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} have simple topological characteristics, so calculating the MACs is relatively straightforward, even intuitive.
However, these simple structures do not always fully satisfy the requirements of complex applications, such as dynamically adapting the circuit to variable and random operating conditions or actively equalizing differences between batteries in the RBS.
Moreover, isolating the batteries disrupts the original regularity and symmetry of the topology, which complicates the otherwise simple structure, and the maximum output current of the system becomes more challenging to obtain.
\replaced{In contrast}{Owing to the advantages of pervasiveness and automation}, the proposed method calculates the MAC of arbitrary RBS structures, \replaced{notably the complex and flexible RBS structures}{which helps to address the aforementioned issues and paves the way for more complex and flexible RBS structure design}.

To illustrate this point, the MACs of \deleted{the} three RBS structures mentioned above are calculated after \replaced{isolating one or more}{the} of the batteries, as shown in Table \ref{tab:isolated_mac}. 
Specifically, for the structure presented in Fig. \ref{fig:study-stru-my}, the corresponding circuit states for the MACs when isolating \replaced{one to three}{different numbers of} batteries are depicted in Figs. \ref{fig:my-isolated-1}--\ref{fig:my-isolated-3}. 
This structure has two cases in which two batteries are isolated: 
one is to isolate two batteries within the same substructure (Fig. \ref{fig:my-isolated-2b}), in which case $\eta=2$; the other is to isolate one battery in each of the two substructures (Fig. \ref{fig:my-isolated-2w}), in which case $\eta=1$. 
The results \added{in Figs. \ref{fig:my-isolated-1}--\ref{fig:my-isolated-3}} show that the proposed method provides reasonable outcomes for isolating any number of batteries in any position.

Furthermore, the \deleted{performance of} output current for the three RBSs \replaced{with isolated}{when isolating} batteries is also shown in Table \ref{tab:isolated_mac}. 
For the structure proposed by Lawson et al., the MAC \replaced{is independent of the number of isolated batteries}{remains the same as that without isolated battery cells, i.e., $\eta=1$, when the number of isolated battery cells increases, until all the cells in the RBS are isolated}.
\added{However,} for Visairo's structure, the MAC decreases \replaced{upon increasing the number of isolated batteries}{as the number of isolated battery cells increases, until $\eta=0$}. 
\replaced{Nevertheless}{In contrast}, the MAC of the structure proposed in this work falls between \replaced{the}{the} MACs of these two structures. 
This result indicates that the structure proposed in this paper has a larger MAC than Lawson's for the same number of batteries \replaced{and has}{which means} a wider range of regulation of the output current. 
\deleted{On the other hand, by simply changing the states of $S_2$, $S_4$, $S_{11}$, and $S_{12}$ in the conversion structure, this structure can address the majority of battery isolation scenarios, whereas Visairo's structure requires specific battery targeting and switch control.}
\deleted{In summary, the structure proposed in this paper has the advantages of both Lawson's and Visairo's structures.}

\section{Conclusion}

This paper proposes a pervasive and automated method to efficiently compute the MAC of \replaced{an}{the}  RBS.
The method is implemented by a greedy algorithm combined with a directed graph model that considers the voltage, internal resistance, and MAC of the batteries, as well as the external load.
The main advantage of this method is its ability to calculate the MAC of RBSs with arbitrary structures.
Even in scenarios with random isolated batteries, the proposed method remains effective.
The proposed method is more computationally efficient than the brute-force algorithm for the same calculation results, which is achieved by two key points when constructing the greedy algorithm: 
\begin{enumerate}
\item[(1)] Calculate the shortest path of each battery by using the Dijkstra algorithm to obtain the $SP$ for each battery. 
\item[(2)] Determine the maximum number of available batteries by bisection to reduce the computational complexity.
\end{enumerate}
This method helps to fully tap the current output potential of the RBS, guide the RBS structure design and optimization in the design stage, and assist in evaluating the current-overload risk of the system in practical applications.

\deleted{The method is implemented by a greedy algorithm combined with a directed graph model , whose effectiveness is tested on a novel and complex RBS structure.
The method remains effective for the application scenario of RBS battery isolation and demonstrates that the novel structure has the advantage on flexible output current and convenient battery isolation.
Future research could focus on developing new indictors to evaluate the performance of the RBS with the currents and voltages obtained by the method, as well as modifying the equivalent model of the battery to allow for more accurate simulations of the RBS, including transient analysis.}

\section{Appendix}

% \begin{algorithm}
%     \caption{Get the max available currents of a certain RBS}\label{alg:greedy}
%     \KwData{Directed graph model $G(V,E)$ of the RBS}
%     \KwResult{$\max \eta$}
%     \For{$i \in E_b$}{
%         $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
%         $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
%     }
%     get $\bm{A}$ by Equation \ref{eq:A}\;
%     \While{not yet determine $\max \eta$ }
%     {
%         $N_{\text{set}} \leftarrow \text{number of setected $SP$s calculated by dichotomy}$\;
%         $C_b    \leftarrow \text{set of all combinations of $N_{\text{set}} $~batteries from $N_b$}$\;
%         \For{$c_b \in C_b$}{
%             $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
%             $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
%             get $\bm{Y}_n$ by Equation \ref{eq:Yn}\;
%             \eIf{$\bm{Y}_n$ is invertible}{
%               \added{pass}
%             }{construct an effective solution}
%             get $I_o$ by Equation \ref{eq:I_o}\;
%             get $\bm{I}_b$ by Equation \ref{eq:I_b}\;
%             \eIf{$\max(\bm{I}_b)\leq I_m$}{
%                 $\eta \leftarrow I_o/\max(\bm{I}_b)$\;
%             }{break}
%         }
%     }
% \end{algorithm}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{figures/algorithm.jpg}
\end{figure}

% 
% \section*{Acknowledgments}
% 
% \subsection*{Author Contributions} 
% 
% B. Xu conceived the main idea, formulated the overarching research goals and aims, designed the algorithm, and reviewed and revised the manuscript.
% G. Hua developed and analyzed the model, implemented the code and supporting algorithms, and wrote the initial draft.
% C. Qian provided critical review, commentary, and revisions.
% Q. Xia contributed to shaping the research, analysis, and manuscript.
% B. Sun conducted the research and investigation process.
% Y. Ren secured the funding and supervised the project.
% Z. Wang verified the results and provided necessary resources.
% 
% \subsection*{Funding}
% 
% This work was supported by the National Natural Science Foundation of China (NSFC, No.52075028).
% 
% \subsection*{Conflicts of Interest}
% 
% The authors declare that there is no conflict of interest regarding the publication of this article.
% 
% \subsection*{Data Availability}
% 
% This work does not require any data to be declared or publicly disclosed.

% \bibliographystyle{nejm}
% \bibliography{sst_main}

% \printbibliography

\end{document}

### 2023-09-17 paper/SST/SST_main_polished.tex
将6k版本转换为正常版本

@@
 \author[1]{30577}
-% \author[1$\dag$]{Binghui Xu}
-% \author[1$\dag$]{Guangbin Hua}
-% \author[1*]{Cheng Qian}
-% \author[1,2]{Quan Xia}
-% \author[1]{Bo Sun}
-% \author[1]{Yi Ren}
-% \author[1]{Zili Wang}
+\author[1$\dag$]{Binghui Xu}
+\author[1$\dag$]{Guangbin Hua}
+\author[1*]{Cheng Qian}
+\author[1,2]{Quan Xia}
+\author[1]{Bo Sun}
+\author[1]{Yi Ren}
+\author[1]{Zili Wang}
 
 %%%%%% Affiliations %%%%%%
-% \affil[1]{School of Reliability and Systems Engineering, Beihang University, Beijing, 100191, China}
-% \affil[2]{School of Aeronautic Science and Engineering at Beihang University, Beijing, China}
-% \affil[*]{Address correspondence to: cqian@buaa.edu.cn}
-% \affil[$\dag$]{These authors contributed equally to this work.}
+\affil[1]{School of Reliability and Systems Engineering, Beihang University, Beijing, 100191, China}
+\affil[2]{School of Aeronautic Science and Engineering at Beihang University, Beijing, China}
+\affil[*]{Address correspondence to: cqian@buaa.edu.cn}
+\affil[$\dag$]{These authors contributed equally to this work.}
 
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{figures/stru-V-origin.png}
+        \includegraphics[width=\textwidth]{stru-V-origin.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{figures/stru-V-serial.png}
+        \includegraphics[width=\textwidth]{stru-V-serial.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{figures/stru-V-parallel.png}
+        \includegraphics[width=\textwidth]{stru-V-parallel.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{figures/stru-V-isolate.png}
+        \includegraphics[width=\textwidth]{stru-V-isolate.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.8\textwidth}
-        \includegraphics[width=\textwidth]{figures/main.png}
+        \includegraphics[width=\textwidth]{main.png}
     \end{subfigure}
@@
     \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{figures/direct-graph-he.png}
+        \includegraphics[width=\textwidth]{direct-graph-he.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.23\textwidth}
-        \includegraphics[width=\textwidth]{figures/direct-graph-xu.png}
+        \includegraphics[width=\textwidth]{direct-graph-xu.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.24\textwidth}
-        \includegraphics[width=\textwidth]{figures/direct-graph-my.png}
+        \includegraphics[width=\textwidth]{direct-graph-my.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.8\textwidth}
-        \includegraphics[width=\textwidth]{figures/battery_simple.png}
+        \includegraphics[width=\textwidth]{battery_simple.png}
         \caption{}
@@
 
-% \tikzset{
-%   meta box/.style={draw, black, very thick, text centered, },
-%   punkt/.style={meta box, rectangle, rounded corners, inner sep=.25em, minimum height=2em, minimum width=4em, align=center, text width=10em },
-%   round/.style={meta box, circle, minimum size=0, inner sep=0pt, outer sep=0pt },
-%   every fit/.style={draw, thick, dashed, gray, inner xsep=.5em, inner ysep=.75em }
-% }
-% \begin{figure}
-% \begin{tikzpicture}[font=\small, node font=\small, node distance=1.5em]
-%     \node[punkt]     (input) {Input: RBS structure};
-%     \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Equations \ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
-%     \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Equation \ref{eq:A}};
-%     \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{\text{set}}=N_b$ };
-%     \node[punkt, below=0.3of get_Nset] (get_cb) {get $c_b$s by combinating $N_{\text{set}}$ batteries from $N_b$};
-%     \node[draw, diamond, aspect=2, below=0.3of get_cb] (is_check_all_cb) {are all $c_b$s checked?};
-%     \node[draw, diamond, aspect=2, right=1of is_check_all_cb] (is_Nset_converged) {is $N_{\text{set}}$ converged?};
-%     \node[punkt, above=of is_Nset_converged] (reset_Nset) {reset $N_{\text{set}}$ by dichotomy};
-%     \node[punkt, text width=15em, below=0.3of is_check_all_cb] (get_Xs) {
-%         select an unchecked $c_b$, and get its $\bm{X}_m$ by \\ 
-%         if switch $j$ $\in \bigcup_{i\in c_b}SP_i$:\\
-%         $\bm{X}[j]=1$ else $0$};
-%     \node[punkt, below=0.3of get_Xs] (get_Yn) {get $\bm{Y}_n$ by Equation \ref{eq:Yn}};
-%     \node[draw, diamond, aspect=2, below=0.3of get_Yn] (is_Yn_invertible) {is $\bm{Y}_n$ invertible?};
-%     \node[punkt, right=1.3of is_Yn_invertible] (construct) {construct an effective solution};
-%     \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Equations \ref{eq:I_o} and \ref{eq:I_b}};
-%     \node[draw, diamond, aspect=2, below=0.3of get_I] (is_leq_Im) {is $\max \bm{I}_b \leq I_m$?};
-%     \node[punkt, right=1.3of is_leq_Im] (drop_eta) {drop this $\eta$};
-%     \node[punkt, below=0.3of is_leq_Im] (get_eta) {get $\eta$ by Equation \ref{eq:eta}};
-%     \node[punkt, below=0.3of get_eta] (update_max_eta) {update $\max \eta$};
-%     \node[punkt, right=1of is_Nset_converged] (output) {Output: $\max \eta$};
-%     \node[round,left=1.5of update_max_eta](point1){};
-% 
-%     \graph{
-%       (input) -> (get_SP) -> (get_A) -> (get_Nset) -> (get_cb) -> (is_check_all_cb) ->["No"] (get_Xs) -> (get_Yn) -> (is_Yn_invertible) ->["Yes"] (get_I) -> (is_leq_Im) ->["Yes"] (get_eta) -> (update_max_eta);
-%       (is_check_all_cb) ->["Yes"] (is_Nset_converged) ->["No"] (reset_Nset) -> (get_cb);
-%       (is_Yn_invertible) ->["No"] (construct) ->[to path={|- (\tikztotarget)}] (get_I);
-%       (is_leq_Im) ->["No"] (drop_eta) ->[to path={|- (\tikztotarget)}] (update_max_eta);
-%       (is_Nset_converged) ->["Yes"] (output);
-%       (update_max_eta) -- (point1) ->[to path={|- (\tikztotarget)}] (is_check_all_cb);
-%     };
-% \end{tikzpicture}
-% \caption{The computational flowchart of the MAC for a given RBS.}\label{fig:flowchart}
+\tikzset{
+  meta box/.style={draw, black, very thick, text centered, },
+  punkt/.style={meta box, rectangle, rounded corners, inner sep=.25em, minimum height=2em, minimum width=4em, align=center, text width=10em },
+  round/.style={meta box, circle, minimum size=0, inner sep=0pt, outer sep=0pt },
+  every fit/.style={draw, thick, dashed, gray, inner xsep=.5em, inner ysep=.75em }
+}
+\begin{figure}
+\begin{tikzpicture}[font=\small, node font=\small, node distance=1.5em]
+    \node[punkt]     (input) {Input: RBS structure};
+    \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Equations \ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
+    \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Equation \ref{eq:A}};
+    \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{\text{set}}=N_b$ };
+    \node[punkt, below=0.3of get_Nset] (get_cb) {get $c_b$s by combinating $N_{\text{set}}$ batteries from $N_b$};
+    \node[draw, diamond, aspect=2, below=0.3of get_cb] (is_check_all_cb) {are all $c_b$s checked?};
+    \node[draw, diamond, aspect=2, right=1of is_check_all_cb] (is_Nset_converged) {is $N_{\text{set}}$ converged?};
+    \node[punkt, above=of is_Nset_converged] (reset_Nset) {reset $N_{\text{set}}$ by dichotomy};
+    \node[punkt, text width=15em, below=0.3of is_check_all_cb] (get_Xs) {
+        select an unchecked $c_b$, and get its $\bm{X}_m$ by \\ 
+        if switch $j$ $\in \bigcup_{i\in c_b}SP_i$:\\
+        $\bm{X}[j]=1$ else $0$};
+    \node[punkt, below=0.3of get_Xs] (get_Yn) {get $\bm{Y}_n$ by Equation \ref{eq:Yn}};
+    \node[draw, diamond, aspect=2, below=0.3of get_Yn] (is_Yn_invertible) {is $\bm{Y}_n$ invertible?};
+    \node[punkt, right=1.3of is_Yn_invertible] (construct) {construct an effective solution};
+    \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Equations \ref{eq:I_o} and \ref{eq:I_b}};
+    \node[draw, diamond, aspect=2, below=0.3of get_I] (is_leq_Im) {is $\max \bm{I}_b \leq I_m$?};
+    \node[punkt, right=1.3of is_leq_Im] (drop_eta) {drop this $\eta$};
+    \node[punkt, below=0.3of is_leq_Im] (get_eta) {get $\eta$ by Equation \ref{eq:eta}};
+    \node[punkt, below=0.3of get_eta] (update_max_eta) {update $\max \eta$};
+    \node[punkt, right=1of is_Nset_converged] (output) {Output: $\max \eta$};
+    \node[round,left=1.5of update_max_eta](point1){};
+
+    \graph{
+      (input) -> (get_SP) -> (get_A) -> (get_Nset) -> (get_cb) -> (is_check_all_cb) ->["No"] (get_Xs) -> (get_Yn) -> (is_Yn_invertible) ->["Yes"] (get_I) -> (is_leq_Im) ->["Yes"] (get_eta) -> (update_max_eta);
+      (is_check_all_cb) ->["Yes"] (is_Nset_converged) ->["No"] (reset_Nset) -> (get_cb);
+      (is_Yn_invertible) ->["No"] (construct) ->[to path={|- (\tikztotarget)}] (get_I);
+      (is_leq_Im) ->["No"] (drop_eta) ->[to path={|- (\tikztotarget)}] (update_max_eta);
+      (is_Nset_converged) ->["Yes"] (output);
+      (update_max_eta) -- (point1) ->[to path={|- (\tikztotarget)}] (is_check_all_cb);
+    };
+\end{tikzpicture}
+\caption{The computational flowchart of the MAC for a given RBS.}\label{fig:flowchart}
+\end{figure}
+
+% \begin{figure}[htbp]
+%     \centering
+%     \includegraphics[width=\textwidth]{flowchart.jpg}
+%     \caption{Computational flowchart of MAC for a given RBS.}\label{fig:flowchart}
 % \end{figure}
-
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=\textwidth]{figures/flowchart.jpg}
-    \caption{Computational flowchart of MAC for a given RBS.}\label{fig:flowchart}
-\end{figure}
 
@@
     \begin{subfigure}[b]{0.2\textwidth}
-        \includegraphics[width=\textwidth]{figures/stru-L-origin.png}
+        \includegraphics[width=\textwidth]{stru-L-origin.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.4\textwidth}
-        \includegraphics[width=\textwidth]{figures/stru-V-origin.png}
+        \includegraphics[width=\textwidth]{stru-V-origin.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{figures/stru-my-origin.png}
+        \includegraphics[width=\textwidth]{stru-my-origin.png}
         \caption{}
@@
 \ref{fig:study-stru-my} are listed in Table \ref{tab:study-results-my} and Fig.
-\ref{fig:study-results-my}, as obtained by the greedy algorithm 1.
-% \ref{alg:greedy}.
+\ref{fig:study-results-my}, as obtained by the greedy algorithm \ref{alg:greedy}.
 Table \ref{tab:study-results-my} contains the states of the switches, the output current $I_o$, the battery current $\bm{I}_b$, and the ratio $\eta$ of the RBS structure with all batteries in good health when the RBS output reaches the MAC.
@@
     \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{figures/ef-topo.png}
+        \includegraphics[width=\textwidth]{ef-topo.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{figures/ef-sp1.png}
+        \includegraphics[width=\textwidth]{ef-sp1.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{figures/ef-sp2.png}
+        \includegraphics[width=\textwidth]{ef-sp2.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{figures/ef-sp3.png}
+        \includegraphics[width=\textwidth]{ef-sp3.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{figures/ef-sp4.png}
+        \includegraphics[width=\textwidth]{ef-sp4.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{figures/ef-mac.png}
+        \includegraphics[width=\textwidth]{ef-mac.png}
         \caption{}
@@
       \begin{subfigure}[b]{0.31\textwidth}
-          \includegraphics[width=\textwidth]{figures/my-isolated-1.png}
+          \includegraphics[width=\textwidth]{my-isolated-1.png}
           \caption{}
@@
       \begin{subfigure}[b]{0.31\textwidth}
-          \includegraphics[width=\textwidth]{figures/my-isolated-2b.png}
+          \includegraphics[width=\textwidth]{my-isolated-2b.png}
           \caption{}
@@
       \begin{subfigure}[b]{0.31\textwidth}
-          \includegraphics[width=\textwidth]{figures/my-isolated-2w.png}
+          \includegraphics[width=\textwidth]{my-isolated-2w.png}
           \caption{}
@@
       \begin{subfigure}[b]{0.31\textwidth}
-          \includegraphics[width=\textwidth]{figures/my-isolated-3.png}
+          \includegraphics[width=\textwidth]{my-isolated-3.png}
           \caption{}
@@
 Therefore, the total time complexity for calculating all $SP$s is $O\bm(2N_b(N_b+2N_s)\log_{10} N\bm)$.
-According to  Appendix 1, % \ref{alg:greedy},
-the RBS can reconfigure $C^{N_{\text{set}}}_{N_b}$ structures by selecting $N_{\text{set}}$ batteries from $N_b$ batteries, which gives $\sum^{N_b}_{N_{\text{set}}=1}C^{N_{\text{set}}}_{N_b}/N_b \approx 2^{N_b}/N_b$ on average.
+According to  Appendix \ref{alg:greedy}, the RBS can reconfigure $C^{N_{\text{set}}}_{N_b}$ structures by selecting $N_{\text{set}}$ batteries from $N_b$ batteries, which gives $\sum^{N_b}_{N_{\text{set}}=1}C^{N_{\text{set}}}_{N_b}/N_b \approx 2^{N_b}/N_b$ on average.
 Thus, with the bisection method, the time complexity of the greedy algorithm is $O\bm(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log_{10} N_b+2N_b(N_b+2N_s)\log_{10} N\bm)$ [i.e., $O\bm(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log_{10} N_b\bm)$].
@@
 
-% \begin{algorithm}
-%     \caption{Get the max available currents of a certain RBS}\label{alg:greedy}
-%     \KwData{Directed graph model $G(V,E)$ of the RBS}
-%     \KwResult{$\max \eta$}
-%     \For{$i \in E_b$}{
-%         $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
-%         $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
-%     }
-%     get $\bm{A}$ by Equation \ref{eq:A}\;
-%     \While{not yet determine $\max \eta$ }
-%     {
-%         $N_{\text{set}} \leftarrow \text{number of setected $SP$s calculated by dichotomy}$\;
-%         $C_b    \leftarrow \text{set of all combinations of $N_{\text{set}} $~batteries from $N_b$}$\;
-%         \For{$c_b \in C_b$}{
-%             $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
-%             $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
-%             get $\bm{Y}_n$ by Equation \ref{eq:Yn}\;
-%             \eIf{$\bm{Y}_n$ is invertible}{
-%               \added{pass}
-%             }{construct an effective solution}
-%             get $I_o$ by Equation \ref{eq:I_o}\;
-%             get $\bm{I}_b$ by Equation \ref{eq:I_b}\;
-%             \eIf{$\max(\bm{I}_b)\leq I_m$}{
-%                 $\eta \leftarrow I_o/\max(\bm{I}_b)$\;
-%             }{break}
-%         }
-%     }
-% \end{algorithm}
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=\textwidth]{figures/algorithm.jpg}
-\end{figure}
+\begin{algorithm}
+    \caption{Get the max available currents of a certain RBS}\label{alg:greedy}
+    \KwData{Directed graph model $G(V,E)$ of the RBS}
+    \KwResult{$\max \eta$}
+    \For{$i \in E_b$}{
+        $P_i \leftarrow \{path| \text{starts at $v_1$ and ends at $v_n$} \}$\;
+        $SP_i \leftarrow p_i \text{ which has the minimum}~\omega(p_i)~\text{among all}~p_i \in P_i. $
+    }
+    get $\bm{A}$ by Equation \ref{eq:A}\;
+    \While{not yet determine $\max \eta$ }
+    {
+        $N_{\text{set}} \leftarrow \text{number of setected $SP$s calculated by dichotomy}$\;
+        $C_b    \leftarrow \text{set of all combinations of $N_{\text{set}} $~batteries from $N_b$}$\;
+        \For{$c_b \in C_b$}{
+            $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
+            $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
+            get $\bm{Y}_n$ by Equation \ref{eq:Yn}\;
+            \eIf{$\bm{Y}_n$ is invertible}{
+              \added{pass}
+            }{construct an effective solution}
+            get $I_o$ by Equation \ref{eq:I_o}\;
+            get $\bm{I}_b$ by Equation \ref{eq:I_b}\;
+            \eIf{$\max(\bm{I}_b)\leq I_m$}{
+                $\eta \leftarrow I_o/\max(\bm{I}_b)$\;
+            }{break}
+        }
+    }
+\end{algorithm}
+% \begin{figure}[htbp]
+%     \centering
+%     \includegraphics[width=\textwidth]{algorithm.jpg}
+% \end{figure}
 
-% 
-% \section*{Acknowledgments}
-% 
-% \subsection*{Author Contributions} 
-% 
-% B. Xu conceived the main idea, formulated the overarching research goals and aims, designed the algorithm, and reviewed and revised the manuscript.
-% G. Hua developed and analyzed the model, implemented the code and supporting algorithms, and wrote the initial draft.
-% C. Qian provided critical review, commentary, and revisions.
-% Q. Xia contributed to shaping the research, analysis, and manuscript.
-% B. Sun conducted the research and investigation process.
-% Y. Ren secured the funding and supervised the project.
-% Z. Wang verified the results and provided necessary resources.
-% 
-% \subsection*{Funding}
-% 
-% This work was supported by the National Natural Science Foundation of China (NSFC, No.52075028).
-% 
-% \subsection*{Conflicts of Interest}
-% 
-% The authors declare that there is no conflict of interest regarding the publication of this article.
-% 
-% \subsection*{Data Availability}
-% 
-% This work does not require any data to be declared or publicly disclosed.
+\section*{Acknowledgments}
+
+\subsection*{Author Contributions}
+
+B. Xu conceived the main idea, formulated the overarching research goals and aims, designed the algorithm, and reviewed and revised the manuscript.
+G. Hua developed and analyzed the model, implemented the code and supporting algorithms, and wrote the initial draft.
+C. Qian provided critical review, commentary, and revisions.
+Q. Xia contributed to shaping the research, analysis, and manuscript.
+B. Sun conducted the research and investigation process.
+Y. Ren secured the funding and supervised the project.
+Z. Wang verified the results and provided necessary resources.
+
+\subsection*{Funding}
+
+This work was supported by the National Natural Science Foundation of China (NSFC, No.52075028).
+
+\subsection*{Conflicts of Interest}
+
+The authors declare that there is no conflict of interest regarding the publication of this article.
+
+\subsection*{Data Availability}
+
+This work does not require any data to be declared or publicly disclosed.
 
@@
 
-% \printbibliography
+\printbibliography
 

### 2023-09-17 paper/SST/SST_main_polished.tex

@@
 
-\usepackage[final]{changes}
+% \usepackage[final]{changes}
 % \usepackage[defaultcolor=red]{changes}
@@
 This paper proposes a method to calculate the MAC of arbitrary RBSs using a greedy algorithm in conjunction with a directed graph model of the RBS.
-\added{
 By introducing the shortest path of the battery, the greedy algorithm transforms the enumeration of switch states in the brute-force algorithm into the combination of the shortest paths, which greatly increases the efficiency with which the MAC is determined.
@@
 The main advantage of the proposed method is its ability to calculate the MAC of RBSs with arbitrary structures, even in scenarios with random isolated batteries.
-}
-\deleted{
-In this method, a new directed graph model is developed to model the structure of RBS, and a greedy algorithm is designed to find the possible circuit that enable MAC.
-Then, the MAC is calculated based on the circuit in-cooperate with the equivalent model of batteries and switches. 
-The effectiveness of the proposed method is validated by a novel and complex RBS structure. 
-The results show that this method is capable to calculated the MAC of RBSs with different structures or different battery sizes efficiently, which proves the correctness of this method and its potential in facilitating next-generation RBS designs and applications, including battery isolation.
-}
 \end{abstract}
@@
 The switching circuit helps to isolate unhealthy batteries, thereby improving the safety and reliability of the battery system.
-\replaced{To illustrate the working principle of an RBS, we consider a typical RBS structure developed by Visairo \cite{visairoReconfigurableBatteryPack2008} (Fig.
-\ref{fig:stru-Visairo}), which is taken as an example to show the reconfiguration process.} {Figure \ref{fig:stru-Visairo} shows a typical RBS structure developed by Visairo \cite{visairoReconfigurableBatteryPack2008} for dynamically adjusting the output voltage and current.}
+To illustrate the working principle of an RBS, we consider a typical RBS structure developed by Visairo \cite{visairoReconfigurableBatteryPack2008} (Fig.
+\ref{fig:stru-Visairo}), which is taken as an example to show the reconfiguration process.
 In this structure, the batteries can be connected not only in series when the switches $S_1$, $S_5$, $S_6$, $S_7$, $S_8$, $S_9$, and $S_{13}$ are closed (see Fig.
@@
 
-\added{
 In spite of the maximum switch current mentioned above, the maximum allowable current (MAC), defined as the maximum allowed current  under the constraints of the battery cell, is another critical indicator of RBSs that needs to be evaluated during the design or control  of the system.
@@
 However, this method is inefficient and time-consuming, especially for RBSs with a large number of switches.
-}
 
-\deleted{
-The complex connection structure between batteries and switches in the RBS provides flexibility but also introduces challenges in design and operational control. 
-Unlike traditional BESSs with fixed outputs, the RBS output must be dynamically adjusted by controlling switch states to meet external load requirements. 
-This necessitates additional, time-consuming output performance analysis during design and corresponding control strategies. 
-An incorrect switch control strategy may cause battery short-circuiting or overload, risking the entire system. 
-The Maximum Allowable Current (MAC), an RBS performance indicator, can guide designers in addressing this issue. 
-MAC is defined as the maximum RBS output current that ensures each battery's current remains within a safe range.
-Therefore, it provides a benchmark for RBS output current, protecting individual batteries and identifying overall system output limits during operation. 
-Despite its importance, no method currently exists for automatically evaluating MAC for RBSs.
-In particular, when one or more random cells are isolated, there is still no method to determine the MAC of the remaining RBS in time to assist the system in adjusting the control strategy timely. 
-A universal and automatical method for calculating RBS MAC is urgently needed for practical applications.
-}
-
-\added{
 To solve this issue, this paper proposes an efficient method to evaluate the MAC of RBSs. 
@@
 The method obtains the accurate current of the RBS under a specific circuit topology.
-}
-\deleted{In this study, a directed graph model and greedy algorithm are employed to determine the MAC of RBS and the corresponding control strategy, effectively calculating the MAC for RBSs with arbitrary structures, including scenarios with isolated batteries.}
-\added{The main contributions of this paper can be summarized as follows:}
+The main contributions of this paper can be summarized as follows:
 \begin{itemize}
-  \item \added{An efficient method is proposed to determine the MAC of RBSs with arbitrary structures, including scenarios with isolated batteries.}
-  \item \added{The greedy algorithm is applied to solve the MAC problem, the computational complexity of which is greatly reduced compared with the brute-force algorithm.}
-  \item \added{An improved directed graph model is introduced; it considers the voltage, the internal resistance, the MAC of the battery, and the external load to analyze the current of the RBS.}
+  \item An efficient method is proposed to determine the MAC of RBSs with arbitrary structures, including scenarios with isolated batteries.
+  \item The greedy algorithm is applied to solve the MAC problem, the computational complexity of which is greatly reduced compared with the brute-force algorithm.
+  \item An improved directed graph model is introduced; it considers the voltage, the internal resistance, the MAC of the battery, and the external load to analyze the current of the RBS.
 \end{itemize}
@@
 To achieve this universally and automatically, the overall process is divided into the four steps shown in Fig. \ref{fig:main}.
-First, a directed graph model is established for subsequent \replaced{computations.}{computing,} \replaced{The model}{, which} not only contains the connected relationships between batteries and switches but also retains the performance parameters of the batteries.
+First, a directed graph model is established for subsequent computations.
+The model not only contains the connected relationships between batteries and switches but also retains the performance parameters of the batteries.
 Subsequently, based on the equivalent circuit, the MAC problem is transformed into specific objective functions and constraints.
-The shortest paths (\replaced{$SP$}{SP}s, where additional batteries and switches on the path are penalized as distance) for the batteries are then obtained  by using the Dijkstra algorithm to connect the batteries in the RBS in parallel.
-Finally, a greedy algorithm is used to organize the switches, allowing the batteries to connect via their \replaced{$SP$}{SP}s while satisfying the constraints, resulting in the MAC of the RBS.
+The shortest paths ($SP$s, where additional batteries and switches on the path are penalized as distance) for the batteries are then obtained  by using the Dijkstra algorithm to connect the batteries in the RBS in parallel.
+Finally, a greedy algorithm is used to organize the switches, allowing the batteries to connect via their $SP$s while satisfying the constraints, resulting in the MAC of the RBS.
 
@@
     \caption{ 
-        Directed graph models used in (a) He's work \cite{heExploringAdaptiveReconfiguration2013}, (b) our previous work, and (c) \added{the improved model in} this paper.
+        Directed graph models used in (a) He's work \cite{heExploringAdaptiveReconfiguration2013}, (b) our previous work, and (c) the improved model in this paper.
         (d) The equivalent circuit of a battery in this method.
@@
 \ref{fig:direct-graph-he}).
-The model captures all potential system configurations and offers a direct metric for configuration flexibility, but it does not specify the physical implementation of the connectivity between batteries, meaning that one graph might \replaced{correspond to}{have had} multiple RBS structures.
-We previously proposed a directed graph model that \replaced{differs completely from}{in contrast to} He's model by using nodes to represent the connections between batteries and switches and directed edges to represent batteries and switches (Fig.
+The model captures all potential system configurations and offers a direct metric for configuration flexibility, but it does not specify the physical implementation of the connectivity between batteries, meaning that one graph might correspond to multiple RBS structures.
+We previously proposed a directed graph model that differs completely from He's model by using nodes to represent the connections between batteries and switches and directed edges to represent batteries and switches (Fig.
 \ref{fig:direct-graph-xu}), allowing for a one-to-one correspondence between the RBS structure and the directed graph model.
-This model accurately and comprehensively represents the RBS topological structure but cannot be used for quantitative MAC calculations because it does not consider  \replaced{the voltage, internal resistance, and MAC of the battery}{battery and switch performance parameters}.
-To address this issue, \replaced{we improve our previous model by}{improved directed graph model is used here based on our original model,} adding electromotive force and resistance attributes on the edges based \replaced{on its}{to} equivalent circuits\deleted{(Fig.
-\ref{fig:direct-graph-my})}.
+This model accurately and comprehensively represents the RBS topological structure but cannot be used for quantitative MAC calculations because it does not consider  the voltage, internal resistance, and MAC of the battery.
+To address this issue, we improve our previous model by adding electromotive force and resistance attributes on the edges based on its equivalent circuits.
 The model also considers the external load as an equivalent resistance and integrates it into the analysis, making it a complete circuit model for later circuit analyses.
-\added{Fig. \ref{fig:direct-graph-my} shows the improved directed graph model used in this paper.}
+Fig. \ref{fig:direct-graph-my} shows the improved directed graph model used in this paper.
 The following  provides a detailed explanation of the method for equating components in RBSs and constructing the directed graph model.
@@
 To use circuit analysis methods to solve the MAC of the RBS, the components in the RBS are equated to ideal circuit elements.
-\added{For instance,} \replaced{a}{A}s shown in Fig.
+For instance, as shown in Fig.
 \ref{fig:battery_simple}, the battery in the RBS can be represented as a black-box circuit consisting of two resistors $r_1$ and $r_2$ and a capacitor  $C$, known as the Thevenin model \cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
@@
 
-\replaced{For a given RBS, determining its MAC}{Based on the definition of MAC, determining the MAC of RBS} involves maximizing the RBS output current while ensuring that the sum of the currents of all batteries does not exceed the batteries' MAC.
-This subsection establishes the constraints and objective function to determine the RBS's MAC  through circuit analysis based on \replaced{the directed graph model provided in the previous section}{the previously constructed directed graph model}.
+For a given RBS, determining its MAC involves maximizing the RBS output current while ensuring that the sum of the currents of all batteries does not exceed the batteries' MAC. 
+This subsection establishes the constraints and objective function to determine the RBS's MAC  through circuit analysis based on the directed graph model provided in the previous section.
 
-First, the topology in the directed graph model is represented in matrix form $\bm{A}$, known as the incidence matrix and \replaced{defined}{to facilitate circuit analysis.
-The specific definition of the incidence matrix is shown} as follows:
+First, the topology in the directed graph model is represented in matrix form $\bm{A}$, known as the incidence matrix and defined as follows:
 \begin{align}\label{eq:A}
@@
 Since each directed edge has one node to leave and one to enter, the values in every column of $\bm{A}$ sum to zero.
-Therefore, removing \replaced{the last}{any single one} row will not result in a loss of information. 
-\deleted{Without loss of generality, the last row is removed here.}
+Therefore, removing the last row will not result in a loss of information. 
 Conversely, since each switch in the RBS is represented by a pair of directed edges with two-way directions, the two columns corresponding to the switch are mutually opposite.
@@
 whereas the elements of the array $\bm{U}_s$ are equal to the first attribute of the corresponding edges in the directed graph.
-The matrix $\bm{Y}$ in \added{Eq.} (\ref{eq:generalized_branches}) is the admittance matrix of the circuit and is defined as the inverse of the impedance matrix.
-\replaced{The}{That is the} elements \replaced{on}{of} the diagonal \added{of} matrix $\bm{Y}$ are equal to the reciprocal of \added{the resistance, which is} the second attribute of the corresponding edges in the directed graph.
-The off-diagonal elements of \added{$\bm{Y}$} are zero.
+The matrix $\bm{Y}$ in Eq. (\ref{eq:generalized_branches}) is the admittance matrix of the circuit and is defined as the inverse of the impedance matrix.
+The elements on the diagonal of matrix $\bm{Y}$ are equal to the reciprocal of the resistance, which is the second attribute of the corresponding edges in the directed graph.
+The off-diagonal elements of $\bm{Y}$ are zero.
 $\bm{X}$ is the state matrix that determines whether the RBS batteries and switches can pass current.
@@
 The primary goal of Visairo's structure (Fig.
-\ref{fig:study-stru-Visairo}) is to dynamically adjust the RBS output \added{power}.
-However, the isolation of unhealthy batteries is not sufficiently addressed \added{in their work}.
-\deleted{When batteries need to be isolated in the RBS of Visairo's structure, the methods for isolating them and the subsequent changes in RBS output warrant further investigation.}
-Lawson et al.
-\replaced{designed the RBS structure shown in Fig.
-\ref{fig:study-stru-Lawson} to isolate batteries}{conducted research on battery isolation in RBS and specifically designed the structure shown in Fig.
-\ref{fig:study-stru-Lawson}}.
+\ref{fig:study-stru-Visairo}) is to dynamically adjust the RBS output power.
+However, the isolation of unhealthy batteries is not sufficiently addressed in their work.
+Lawson et al. designed the RBS structure shown in Fig. \ref{fig:study-stru-Lawson} to isolate batteries. 
 Although this structure easily isolates batteries, it cannot dynamically adjust the output current of the RBS. 
-Based on the structures of Visairo and Lawson, this paper proposes the structure shown in Fig. \ref{fig:study-stru-my}\deleted{, which combines the advantages of both}.
+Based on the structures of Visairo and Lawson, this paper proposes the structure shown in Fig. \ref{fig:study-stru-my}.
 By integrating the Visairo RBS structure into the Lawson RBS structure, the proposed structure not only has the flexibility to switch the batteries between series, parallel, and mixed series-parallel modes but also allows the isolation of highly degraded batteries from the RBS.
@@
     $\bm{I}_b$ & $[u_b/(2R_o+r_b),u_b/(2R_o+r_b),0,0]$ \\
-    \added{$\max$}$\eta$     & 2 \\
+    $\max \eta$     & 2 \\
     \bottomrule
@@
 \ref{fig:study-stru-Lawson} and \ref{fig:study-stru-Visairo} are listed in Tables \ref{tab:study-results-Lawson} and  \ref{tab:study-results-Visairo}, respectively.
-\added{
 To verify and compare the results from the greedy algorithm, we also used a brute-force algorithm that iterates through all possible switch states to calculate the MAC of the same three RBSs. 
@@
 For the same RBS, the method counts all possible switch states, which equates to $2^{19}$, $2^{15}$, and $2^{13}$ structures, respectively.
-}
 
@@
 
-Furthermore, the RBS \replaced{with}{under the scenario of} isolated batteries is taken into consideration and calculated. 
+Furthermore, the RBS with isolated batteries is taken into consideration and calculated. 
 The MAC calculation results for the three structures under study, with varying numbers of isolated batteries, are presented in Table \ref{tab:isolated_mac}. 
 Figures \ref{fig:my-isolated-1}--\ref{fig:my-isolated-3} illustrate the corresponding switch-control schemes for the new structure proposed in this paper under different conditions of isolated batteries.
-\deleted{The characteristics of these three structures in the context of battery isolation will be discussed in the next subsection.}
 
@@
 
-\replaced{Consider first the results shown in Fig.
-\ref{fig:all-results-my} and Table \ref{tab:study-results-my}}{In this subsection, we firstly discuss the correctness of the results presented in Fig.
-\ref{fig:all-results-my} and Table \ref{tab:study-results-my}}.
+Consider first the results shown in Fig. \ref{fig:all-results-my} and Table \ref{tab:study-results-my}.
 When $B_1$ and $B_2$ or $B_3$ and $B_4$ are connected in parallel, the RBS outputs the maximum current, which is $\eta=2$ (i.e., twice the current output of a single battery in the RBS). 
@@
 Therefore, the state of the switches given in Table \ref{tab:study-results-my} maximizes the RBS output current.
-\added{The MAC obtained by the brute-force algorithm is identical to the one obtained by the greedy algorithm.}
+The MAC obtained by the brute-force algorithm is identical to the one obtained by the greedy algorithm.
 
@@
 
-Note that \deleted{when solving for MAC,} $\eta$ is used as the objective function instead of $I_o$ \added{in solving for the MAC}. 
+Note that $\eta$ is used as the objective function instead of $I_o$ in solving for the MAC. 
 This choice makes the resulting MAC more reasonable. 
 As shown in Table \ref{tab:study-results-my}, $I_o$ and $\bm{I}_b$ are functions of $R_o$, $u_b$, and $r_b$. 
-\replaced{However, when}{If} $I_o$ \replaced{is}{were} used as the objective function, even for the same RBS structure, the MAC \replaced{solution}{result} and corresponding switch states could change due to different external electrical appliances.
+However, when $I_o$ is used as the objective function, even for the same RBS structure, the MAC solution and corresponding switch states could change due to different external electrical appliances.
 This would increase the difficulty and uncertainty of designing the RBS structure. 
-\replaced{To eliminate this problem, the ratio $\eta=I_o/\max\bm{I}_b$ is adopted as the objective function in our research.}{In contrast, by using $\eta$ as the objective function, which is defined as the ratio of $I_o$ and $\max\bm{I}_b$, the influence of these factors on the results can be eliminated.}
+To eliminate this problem, the ratio $\eta=I_o/\max\bm{I}_b$ is adopted as the objective function in our research.
 Recall that $\eta$ reflects only the MAC of the RBS structure. 
 Assuming that the MAC of batteries in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by determining the value of $\eta$ for the structure.
-\deleted{Therefore, compared to $I_o$, $\eta$ is more suitable for structure design.}
 
-The method proposed in this paper facilitates the design of \deleted{next-generation} RBSs in the following ways:
+The method proposed in this paper facilitates the design of RBSs in the following ways:
 Most currently proposed RBS structures \cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} have simple topological characteristics, so calculating the MACs is relatively straightforward, even intuitive.
@@
 Moreover, isolating the batteries disrupts the original regularity and symmetry of the topology, which complicates the otherwise simple structure, and the maximum output current of the system becomes more challenging to obtain.
-\replaced{In contrast}{Owing to the advantages of pervasiveness and automation}, the proposed method calculates the MAC of arbitrary RBS structures, \replaced{notably the complex and flexible RBS structures}{which helps to address the aforementioned issues and paves the way for more complex and flexible RBS structure design}.
+In contrast, the proposed method calculates the MAC of arbitrary RBS structures, notably the complex and flexible RBS structures.
 
-To illustrate this point, the MACs of \deleted{the} three RBS structures mentioned above are calculated after \replaced{isolating one or more}{the} of the batteries, as shown in Table \ref{tab:isolated_mac}.
+To illustrate this point, the MACs of three RBS structures mentioned above are calculated after isolating one or more of the batteries, as shown in Table \ref{tab:isolated_mac}. 
 Specifically, for the structure presented in Fig.
-\ref{fig:study-stru-my}, the corresponding circuit states for the MACs when isolating \replaced{one to three}{different numbers of} batteries are depicted in Figs.
+\ref{fig:study-stru-my}, the corresponding circuit states for the MACs when isolating one to three batteries are depicted in Figs.
 \ref{fig:my-isolated-1}--\ref{fig:my-isolated-3}.
@@
 \ref{fig:my-isolated-2w}), in which case $\eta=1$.
-The results \added{in Figs. \ref{fig:my-isolated-1}--\ref{fig:my-isolated-3}} show that the proposed method provides reasonable outcomes for isolating any number of batteries in any position.
+The results in Figs. \ref{fig:my-isolated-1}--\ref{fig:my-isolated-3} show that the proposed method provides reasonable outcomes for isolating any number of batteries in any position.
 
-Furthermore, the \deleted{performance of} output current for the three RBSs \replaced{with isolated}{when isolating} batteries is also shown in Table \ref{tab:isolated_mac}. 
-For the structure proposed by Lawson et al., the MAC \replaced{is independent of the number of isolated batteries}{remains the same as that without isolated battery cells, i.e., $\eta=1$, when the number of isolated battery cells increases, until all the cells in the RBS are isolated}.
-\added{However,} for Visairo's structure, the MAC decreases \replaced{upon increasing the number of isolated batteries}{as the number of isolated battery cells increases, until $\eta=0$}. 
-\replaced{Nevertheless}{In contrast}, the MAC of the structure proposed in this work falls between \replaced{the}{the} MACs of these two structures. 
-This result indicates that the structure proposed in this paper has a larger MAC than Lawson's for the same number of batteries \replaced{and has}{which means} a wider range of regulation of the output current.
-\deleted{On the other hand, by simply changing the states of $S_2$, $S_4$, $S_{11}$, and $S_{12}$ in the conversion structure, this structure can address the majority of battery isolation scenarios, whereas Visairo's structure requires specific battery targeting and switch control.}
-\deleted{In summary, the structure proposed in this paper has the advantages of both Lawson's and Visairo's structures.}
+Furthermore, the output current for the three RBSs with isolated batteries is also shown in Table \ref{tab:isolated_mac}. 
+For the structure proposed by Lawson et al., the MAC is independent of the number of isolated batteries.
+However, for Visairo's structure, the MAC decreases upon increasing the number of isolated batteries. 
+Nevertheless, the MAC of the structure proposed in this work falls between the MACs of these two structures. 
+This result indicates that the structure proposed in this paper has a larger MAC than Lawson's for the same number of batteries and has a wider range of regulation of the output current.
 
@@
 
-This paper proposes a pervasive and automated method to efficiently compute the MAC of \replaced{an}{the}  RBS.
+This paper proposes a pervasive and automated method to efficiently compute the MAC of a RBS.
 The method is implemented by a greedy algorithm combined with a directed graph model that considers the voltage, internal resistance, and MAC of the batteries, as well as the external load.
@@
 This method helps to fully tap the current output potential of the RBS, guide the RBS structure design and optimization in the design stage, and assist in evaluating the current-overload risk of the system in practical applications.
-
-\deleted{The method is implemented by a greedy algorithm combined with a directed graph model , whose effectiveness is tested on a novel and complex RBS structure.
-The method remains effective for the application scenario of RBS battery isolation and demonstrates that the novel structure has the advantage on flexible output current and convenient battery isolation.
-Future research could focus on developing new indictors to evaluate the performance of the RBS with the currents and voltages obtained by the method, as well as modifying the equivalent model of the battery to allow for more accurate simulations of the RBS, including transient analysis.}
 
@@
     {
-        $N_{\text{set}} \leftarrow \text{number of setected $SP$s calculated by dichotomy}$\;
-        $C_b    \leftarrow \text{set of all combinations of $N_{\text{set}} $~batteries from $N_b$}$\;
+        $N_{\text{set}} \leftarrow$ number of setected $SP$s calculated by dichotomy\;
+        $C_b    \leftarrow$ set of all combinations of $N_{\text{set}} $~batteries from $N_b$\;
         \For{$c_b \in C_b$}{

### 2023-09-17 paper/SST/2-main.tex
使用latexdiff生成了1-2-diff；处理了合并后的杂项

@@
-% 【version: SST-1.4】
-
-% 【done】 
-% =====0909
-% 按 Q 修改意见修改 0901 【优先】
-% =====0910
-% 1. 摘要修改，量化我们的成果：explain the most important achievements of the proposed method quantitatively
-% 2. 介绍修改，相关文献：
-%   2.1 RBS 结构分析相关的
-%   2.2 网络流（最大流）相关（但因为问题不同，无法使用，提一句穷举）
-% 3. 介绍修改，逐点列出我们的贡献：state research contribution and achievements as bullet points at the end of the Introduction section
-% 4. 讨论修改，增加算法复杂度，以及和穷举法的比较（该领域尚为空白，没有sota的算法）
-% 5. 讨论修改，增加算法的 limitations（根据复杂度，大规模不好用）
-% 6. 讨论修改，增加结果的准确性介绍（和穷举结果比较）：explain about the accuracy, sufficiency and reliability of their results? How do they verify and validate the results
-% 7. 修改算法的第15步
-% 8. 重写总结
-% 9. 添加文献
-% =====0911
-% 1. introduction 整体逻辑不流畅，跳跃过大
-% 2. introduction 文献
-% 2. conclusion 结尾，可以加上一两句说说这个方法的应用价值之类的，吹一吹
-% 3. abstract
-%   3.1 删去 75000 倍的效率；
-%   3.2 凝练一点，就是说这个方法把遍历法中的枚举开关状态组合，转换为了对最短路径的组合；
-%   3.3 算法复杂度、效率提升倍数=2^开关数/2^电池数
-%   3.4 调整 discussion 的相关内容
-% 4. 删去 最大流
-% 5. 按 Q 的意见修改
-% =====0913
-% 1. 按师兄的修改意见修改（0912晚）
-% 2. 调整文献顺序，改用 biber
-% =====0915
-% my structure, my method 的计算结构数为 11，而不是 7
-
-% 【doing】
-
-% 【todo】
-% ==18号润色完再次核对，21或22号提交。
-
 \documentclass{article}
@@
 % \deleted{xxxx}
-% \replaced{a}{b} 原文的b替换成a
-% \usepackage{easyReview} % texstudio 部分
+% \replaced{a}{b}
 
@@
 % Title Format: Use title case, capitalizing the first letter of each word, except for certain small words, such as articles and short prepositions
-\title{Maximum Allowable Current Determination of RBS By Using a Directed Graph Model and Greedy Algorithm}
+\title{Using a Directed Graph Model and Greedy Algorithm to Determine the Maximum Allowable Current in a Reconfigurable Battery System}
 
@@
 \begin{abstract}
-Reconfigurable Battery Systems (RBSs) present a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structure subjected to battery charging and discharging strategies.
-During the operation of the RBS, the Maximum Allowable Current (MAC) of system that ensures each battery's current remains within a safe range, is a critical indicator to guide the system's reconfiguring control, ensuring its safety and reliability.
-In this paper, we firstly propose a calculation method for the MAC of arbitrary RBS using a greedy algorithm in conjunction with a directed graph model of the RBS.
-By introducing the shortest path of the battery, the greedy algorithm transforms the enumeration of switch states in the brute force algorithm into the combination of the shortest paths, which greatly increases the efficiency of the determination of the MAC.
+Reconfigurable battery systems (RBSs) present a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structure that can be adapted to different battery charging and discharging strategies.
+During RBS operation, the maximum allowable current (MAC) of the system that ensures that each battery's current remains within a safe range is a critical indicator to guide the system's reconfiguration, ensuring its safety and reliability.
+This paper proposes a method to calculate the MAC of arbitrary RBSs using a greedy algorithm in conjunction with a directed graph model of the RBS.
+By introducing the shortest path of the battery, the greedy algorithm transforms the enumeration of switch states in the brute-force algorithm into the combination of the shortest paths, which greatly increases the efficiency with which the MAC is determined.
 The directed graph model, based on the equivalent circuit, provides a specific method for calculating the MAC of a given structure.
-This method has been validated on two published 4-battery-RBSs and one with more complex structure.
-It obtaining the same results as the brute force algorithm method, while achieves significantly improved computational efficiency ($N_s 2^{N_s - N_b} \log N_b$ times faster than the brute force algorithm for a RBS with $N_b$ batteries and $N_s$ switches, theoretically).
-The main advantage of this method is its ability to calculate the MAC of RBSs with arbitrary structures, even in the scenarios with random isolated batteries.
+The proposed method is validated on two published 4-battery-RBSs and one with a more complex structure.
+The results are the same as those of the brute-force algorithm, but the proposed method significantly improves the computational efficiency ($N_s 2^{N_s - N_b} \log_{10} N_b$ times faster than the brute force algorithm for a RBS with $N_b$ batteries and $N_s$ switches, theoretically).
+The main advantage of the proposed method is its ability to calculate the MAC of RBSs with arbitrary structures, even in scenarios with random isolated batteries.
 \end{abstract}
@@
 
-Battery Energy Storage Systems (BESSs) are extensively employed in various applications, such as wind power plants and space power systems, to store and release high-quality electrical energy \cite{desiqueiraControlStrategySmooth2021,yangBatteryEnergyStorage2018,choCommercialResearchBattery2015,zhangDevelopmentProspectChinese2021,schwanbeckInternationalSpaceStation2019}.
+Battery energy storage systems (BESSs) are extensively used in various applications, such as wind power plants and space power systems, to store and release high-quality electrical energy \cite{desiqueiraControlStrategySmooth2021,yangBatteryEnergyStorage2018,choCommercialResearchBattery2015,zhangDevelopmentProspectChinese2021,schwanbeckInternationalSpaceStation2019}.
 Typically, a BESS consists of numerous batteries interconnected by series-parallel circuitry to provide the required capacity storage.
-However, traditional BESSs, in which the batteries are connected in a fixed topology, exhibit a significant weakness in their worst battery due to the so-called cask effect.
-Moreover, if this worst battery fails from operation, it can exacerbate the degradation of other batteries with a high possibility, leading to reliability and safety issues \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019,jeevarajanBatterySafetyQualifications2012}.
-These problems have become significant technical barriers in the development of new-generation space vehicles unfortunately \cite{pomboHybridPowerSystem2021}.
+However, traditional BESSs, in which the batteries are connected in a fixed topology, suffer from a significant weakness in their worst battery due to the so-called cask effect.
+Moreover, if the worst battery fails during operation, it is highly likely to exacerbate the degradation of the other batteries, leading to reliability and safety issues \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019,jeevarajanBatterySafetyQualifications2012}.
+These problems have become significant technical barriers in the development of new-generation space vehicles and need to be addressed \cite{pomboHybridPowerSystem2021}.
 
-Reconfigurable Battery System (RBS), which can dynamically switch to different circuit topology configurations as required, is expected to solve the above problems\cite{hanNextGenerationBatteryManagement2020a}.
-The ability of switching circuit helps to isolate unhealthy batteries, thereby improving the safety and reliability of the battery system.
-In order to illustrate the working principle of RBS, a typical RBS structure developed by Visairo \cite{visairoReconfigurableBatteryPack2008}(Figure \ref{fig:stru-Visairo}) is taken as an example to show the reconfiguration process.
-In this structure, the batteries can be connected not only in series when the switches $S_1$, $S_5$, $S_6$, $S_7$, $S_8$, $S_9$, and $S_{13}$ are closed (Figure \ref{fig:stru-Visairo-serial}), but also in parallel when $S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$, and $S_{13}$ are closed (Figure \ref{fig:stru-Visairo-parallel}).
-Furthermore, when an unhealthy battery, for instance the orange one $B_3$ in Figure \ref{fig:stru-Visairo-isolate}, appears in the RBS, it can be isolated by opening its two adjacent switches (i.e.
-$S_4$ and $S_{11}$), ensuring the system still remains a reliable working mode.
+Reconfigurable battery systems (RBSs), which can dynamically switch as required to different circuit topologies, are expected to solve this problem \cite{hanNextGenerationBatteryManagement2020a}.
+The switching circuit helps to isolate unhealthy batteries, thereby improving the safety and reliability of the battery system.
+To illustrate the working principle of an RBS, we consider a typical RBS structure developed by Visairo \cite{visairoReconfigurableBatteryPack2008} (Fig.
+\ref{fig:stru-Visairo}), which is taken as an example to show the reconfiguration process.
+In this structure, the batteries can be connected not only in series when the switches $S_1$, $S_5$, $S_6$, $S_7$, $S_8$, $S_9$, and $S_{13}$ are closed (see Fig.
+\ref{fig:stru-Visairo-serial}) but also in parallel when $S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$, and $S_{13}$ are closed (Fig.
+\ref{fig:stru-Visairo-parallel}).
+Furthermore, when an unhealthy battery, for instance, the orange one $B_3$ in Fig.
+\ref{fig:stru-Visairo-isolate}, appears in the RBS, it can be isolated by opening its two adjacent switches (i.e., $S_4$ and $S_{11}$), ensuring that the system remains in a reliable working mode.
 
@@
 
-Recently, various types of RBS with different flexibility and reconfigurability have been designed to meet application requirements. 
-For example, Ci et al. \cite{ci2007novel} proposed a RBS structure that can dynamically adjust the batteries discharge rate to fully exploit the available capacity of each battery. 
-Jan's \cite{9209774,engelhardt2021double} structures had the ability to reconfigure structures with variant batteries in series to reach the voltage requirements during electric vehicle charging, which constantly change.
-The structure proposed by Visairo et al.\cite{visairoReconfigurableBatteryPack2008}, as shown in Figure \ref{fig:stru-Visairo}, can change the system's output voltage based on load conditions, thereby reducing the power loss of the voltage regulator during the power supply process and improving energy utilization efficiency.
-For the same purpose to enhance the energy efficiency of the system, Lawson et al.
+Recently, various types of RBSs with different flexibility and reconfigurability have been designed to meet application requirements. 
+For example, Ci et al. \cite{ci2007novel} proposed an RBS structure that dynamically adjusts the battery discharge rate to fully exploit the available capacity of each battery. 
+Jan's \cite{9209774,engelhardt2021double} structures  reconfigure structures with variant batteries in series to reach the (constantly changing) voltage requirements during electric vehicle charging.
+As shown in Fig.
+\ref{fig:stru-Visairo}, the structure proposed by Visairo et al.
+\cite{visairoReconfigurableBatteryPack2008}  changes the system's output voltage based on the load conditions, thereby reducing the power loss of the voltage regulator during the power supply process and improving the efficiency of energy use.
+Also, to enhance the energy efficiency of the system, Lawson et al.
 \cite{lawsonSoftwareConfigurableBattery2012} and He et al.
-\cite{he2014reconfiguration} also proposed simplified structures which has less switches than Visairo's design.
-Kim et al. \cite{kim2009dynamic} improved the system's ability to recover from battery failures by introducing multiple ports to the structure. 
-The complex structure between batteries and switches enables the flexibility of RBS, but also brings the challenges in design and control of system. 
-Thus, several approaches to analyze the RBS structure and performance have been proposed in the literature to tackle these challenges.
+\cite{he2014reconfiguration}  proposed simplified structures that have fewer switches than Visairo's design.
+Kim et al. \cite{kim2009dynamic} improved the system's ability to recover from battery failures by introducing multiple ports into the structure.
+
+The complex structure between batteries and switches gives RBSs flexibility but also creates challenges in the design and control of the system. 
+Thus, several approaches to analyze the RBS structure and performance have been proposed to tackle these challenges.
 For instance, 
-Han et al.\cite{han2021analysis} derived an analytical expression for the maximum switch current during battery system reconfiguration for a specific RBS structure. 
-This helps guide the selection of switches and provide support for the hardware design of RBS.
-Chen et al.\cite{chenSneakCircuitTheory2021} proposed a systematic approach based on the sneak circuit theory to fundamentally avoid the short-circuit problem of reconfigurable battery systems. 
-They thoroughly analyzes all paths between the cathode and anode of each battery in the RBS and identifies paths that only contain switches as short-circuit paths for pre-checking before system reconfiguration.
+Han et al. \cite{han2021analysis} derived an analytical expression for the maximum switch current during battery system reconfiguration for a specific RBS structure. 
+This helps guide the selection of switches and supports the design of RBS hardware.
+Chen et al. \cite{chenSneakCircuitTheory2021} proposed a systematic approach based on  sneak circuit theory to fundamentally avoid the short-circuit problem of RBSs: 
+They thoroughly analyzed all paths between the cathode and anode of each battery in the RBS and identified paths that only contain switches as short-circuit paths for pre-checking before system reconfiguration.
 
-In spite of maximum switch current mentioned above, the maximum allowable current (MAC), defined as the maximum current allowed by system under the constraints of the battery cell, is another critical indictor of RBS that need to be evaluated during the design or control process of system.
-It helps the designers to assess whether the RBS meets the output current requirements, and contribute to the formulation of appropriate and safe management strategies for the battery management system (BMS).
-Unfortunately, few studies on the RBS structure analysis have been conducted to determine the MAC of RBSs.
-A intuitive and straightforward method is to enumerate all possible switch states and calculate the output current of the system under each reconfigurated structure.
-But this method is inefficient and time-consuming, especially for RBSs with a large number of switches.
+In spite of the maximum switch current mentioned above, the maximum allowable current (MAC), defined as the maximum allowed current  under the constraints of the battery cell, is another critical indicator of RBSs that needs to be evaluated during the design or control  of the system.
+The MAC helps the designers assess whether the RBS meets the output current requirements and contributes to the formulation of appropriate and safe management strategies for the battery management system.
+Unfortunately, few studies have analyzed the RBS structure to determine the RBS MAC.
+An intuitive and straightforward method is to enumerate all possible switch states and calculate the output current of the system under each reconfigurated structure.
+However, this method is inefficient and time-consuming, especially for RBSs with a large number of switches.
 
-To solve this issue, a new method to effectively evaluate the MAC of RBS is proposed in this paper. 
-First, a greedy algorithm is designed to search the possible circuit topology of RBS with MAC effciently.
-Meanwhile, an improved direct graph model, considering the voltage, internal resistance, and maximum allowable current of the battery, and the external load, is porposed to obtain the accurate current value of RBS under specific circuit topology.
-To the best of our knowledge, the present work is the first to develop an efficient calculation method of RBS MAC.
-The main contributions of the paper can be summarized as follows:
+To solve this issue, this paper proposes an efficient method to evaluate the MAC of RBSs. 
+First, a greedy algorithm is designed to efficiently search the possible circuit topology of RBSs with MAC.
+Moreover, the method provides an improved direct graph model that considers the voltage, the internal resistance, the MAC of the battery, and the external load.
+The method obtains the accurate current of the RBS under a specific circuit topology.
+The main contributions of this paper can be summarized as follows:
 \begin{itemize}
-  \item Proposing a effective method to determine the MAC of RBSs with arbitrary structures, including scenarios with isolated batteries.
-  \item Application of the greedy algorithm to solve the MAC problem, whose computational complexity is greatly reduced compared with the brute force algorithm.
-  \item introducing an improved directed graph model, considering the voltage, internal resistance, and maximum allowable current of the battery, and the external load, to achieve the current analysis of the RBS.
+  \item An efficient method is proposed to determine the MAC of RBSs with arbitrary structures, including scenarios with isolated batteries.
+  \item The greedy algorithm is applied to solve the MAC problem, the computational complexity of which is greatly reduced compared with the brute-force algorithm.
+  \item An improved directed graph model is introduced; it considers the voltage, the internal resistance, the MAC of the battery, and the external load to analyze the current of the RBS.
 \end{itemize}
@@
 The remainder of this paper is organized as follows: 
-Section II presents the framework and details of the proposed directed graph model and the greedy algorithm. 
-Section III demonstrated a case study of using the proposed method to determine the MAC of a novel and complex structure. 
-The calculation results, the algorithm's computational complexity and scenarios such as batteries isolation also are discussed. 
-Finally, the concluding remarks are drawn in Section IV.
+Section II presents the framework and details of the proposed directed graph model and  greedy algorithm. 
+Section III discusses a case study that uses the proposed method to determine the MAC of a novel, complex structure. 
+The calculation results, the algorithm's computational complexity, and scenarios such as battery isolation are also discussed. 
+Finally, the concluding remarks are presented in Sec. IV.
 
@@
 
-The central principle of this method is to make the batteries in RBS connected in parallel as much as possible, thereby maximizing the output current of the RBS.
-To universally and automatically achieve this, the overall process is divided into four steps, as shown in Figure \ref{fig:main}.
-Firstly, a directed graph model is established for subsequent computations.
-The model not only contains the connected relationships between batteries and switches, but also retains the performance parameters of the batteries.
+The central principle of this method is to connect the batteries in an RBS in parallel to the extent possible, thereby maximizing the output current of the RBS.
+To achieve this universally and automatically, the overall process is divided into the four steps shown in Fig. \ref{fig:main}.
+First, a directed graph model is established for subsequent computations.
+The model not only contains the connected relationships between batteries and switches but also retains the performance parameters of the batteries.
 Subsequently, based on the equivalent circuit, the MAC problem is transformed into specific objective functions and constraints.
-Then, the shortest paths ($SP$s, where additional batteries and switches on the path are penalized as distance) for the batteries are obtained using the Dijkstra algorithm to guide the batteries in the RBS connect in parallel.
-Finally, a greedy algorithm is employed to organize the switches, allowing the batteries to connect via their $SP$s while satisfying the constraints, resulting in the MAC of the RBS.
+The shortest paths ($SP$s, where additional batteries and switches on the path are penalized as distance) for the batteries are then obtained  by using the Dijkstra algorithm to connect the batteries in the RBS in parallel.
+Finally, a greedy algorithm is used to organize the switches, allowing the batteries to connect via their $SP$s while satisfying the constraints, resulting in the MAC of the RBS.
 
@@
 
-\subsection{Directed graph Model}
+\subsection{Directed graph model}
 
@@
     \caption{ 
-        Directed graph models used in (a) He's work \cite{heExploringAdaptiveReconfiguration2013}, (b) our previous work , and (c) the improved model in this paper.
+        Directed graph models used in (a) He's work \cite{heExploringAdaptiveReconfiguration2013}, (b) our previous work, and (c) the improved model in this paper.
         (d) The equivalent circuit of a battery in this method.
@@
 He et al.
-\cite{heExploringAdaptiveReconfiguration2013} once proposed an abstracted directed graph model for RBS, where the nodes represented the batteries, the edges represented the configuration flexibility, and the weight of each vertex corresponded to the battery voltage ( Figure \ref{fig:direct-graph-he}).
-The model effectively captured all potential system configurations and offered a direct metric for configuration flexibility, but it did not specify the physical implementation of the connectivity between batteries, meaning one graph might correspond to multiple RBS structures.
-We previously proposed a novel directed graph model that, completely different from He's model, used nodes to represent the connections between batteries and switches, and directed edges to represent batteries and switches (Figure \ref{fig:direct-graph-xu}), allowing for a one-to-one correspondence between the RBS structure and the directed graph model.
-This model was able to accurately and comprehensively represent the RBS topological structure but could not be used for quantitative MAC calculations due to the lack of consideration on the voltage, internal resistance and maximum allowable current of the battery.
-To address this, an improvement on our previous model is conducted by adding electromotive force and resistance attributes on the edges based on its equivalent circuits .
-The model also considers the external load as an equivalent resistance and integrate it into the analysis, making it a complete circuit model for later circuit analysis.
-Figure \ref{fig:direct-graph-my} shows the improved directed graph model used in this paper.
-The following will provide a detailed explanation of the method for equating the components in RBS and constructing the directed graph model.
+\cite{heExploringAdaptiveReconfiguration2013} proposed an abstracted directed graph model for an RBS, where the nodes represent the batteries, the edges represent the configuration flexibility, and the weight of each vertex corresponds to the battery voltage (Fig.
+\ref{fig:direct-graph-he}).
+The model captures all potential system configurations and offers a direct metric for configuration flexibility, but it does not specify the physical implementation of the connectivity between batteries, meaning that one graph might correspond to multiple RBS structures.
+We previously proposed a directed graph model that differs completely from He's model by using nodes to represent the connections between batteries and switches and directed edges to represent batteries and switches (Fig.
+\ref{fig:direct-graph-xu}), allowing for a one-to-one correspondence between the RBS structure and the directed graph model.
+This model accurately and comprehensively represents the RBS topological structure but cannot be used for quantitative MAC calculations because it does not consider  the voltage, internal resistance, and MAC of the battery.
+To address this issue, we improve our previous model by adding electromotive force and resistance attributes on the edges based on its equivalent circuits.
+The model also considers the external load as an equivalent resistance and integrates it into the analysis, making it a complete circuit model for later circuit analyses.
+Fig. \ref{fig:direct-graph-my} shows the improved directed graph model used in this paper.
+The following  provides a detailed explanation of the method for equating components in RBSs and constructing the directed graph model.
 
-In order to use circuit analysis methods to solve the MAC of the RBS, the components in the RBS are equated to ideal circuit elements.
-For instance, as shown in Figure \ref{fig:battery_simple}, the battery in the RBS can be represented as a black-box circuit consisting of two resistors (i.e., $r_1$ and $r_2$) and a capacitor (i.e., $C$), known as the Thevenin model\cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
+To use circuit analysis methods to solve the MAC of the RBS, the components in the RBS are equated to ideal circuit elements.
+For instance, as shown in Fig.
+\ref{fig:battery_simple}, the battery in the RBS can be represented as a black-box circuit consisting of two resistors $r_1$ and $r_2$ and a capacitor  $C$, known as the Thevenin model \cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
 With an emphasis on the stable output of the RBS, the capacitor in the Thevenin model can be considered as an open circuit without affecting the steady-state current.
-Therefore, the battery $i$ in the RBS can be simplified as the series connection between a constant voltage source $u_{i}$ and a resistor $r_{i}$.
-Furthermore, the state of switch $j$ in the RBS is represented by a binary variable $x_j$, where 0 is for ON and 1 is for OFF, respectively.
-When the switch is closed, it can be regarded as a resistor with a very small resistance value $r_{j}$.
-Lastly, the external load is considered as a resistor with a value of $R_o$.
+Therefore,  battery $i$ in the RBS can be simplified as a series connection between a constant voltage source $u_{i}$ and a resistor $r_{i}$.
+Furthermore, the state of switch $j$ in the RBS is represented by a binary variable $x_j$, where 0 is ON and 1 is OFF.
+When the switch is closed, the circuit can be regarded as a resistor with a very small resistance $r_{j}$.
+Finally, the external load is considered as a resistor with resistance $R_o$.
 
@@
         Therefore, there are three types of directed edges. 
-        For a battery $B_i$, its directed edge $e_i$ is drawn from the cathode to the anode, as the battery only allows current to flow in one direction when in operation.
+        For a battery $B_i$, its directed edge $e_i$ is drawn from the cathode to the anode because the battery in operation only allows current to flow in one direction.
         For a switch $S_j$, since it is allowed to work under bi-directional currents, it is represented by a pair of directed edges with two-way directions. 
-        Regarding the external electronic load, as it is connected to the anode and cathode of the RBS, a directed edge from $v_N$ to $v_1$ is used to represent it. 
-        In conclusion, for a given RBS structure with $N_b$ batteries and $N_s$ switches, the total number of directed edges is $N_b+2N_s+1$, where 1 refers to the external electrical load.
-    \item Edges' attributes:
+        Regarding the external electronic load, because it is connected to the anode and cathode of the RBS, a directed edge from $v_N$ to $v_1$  represents it. 
+        In conclusion, for a given RBS structure with $N_b$ batteries and $N_s$ switches, the number of directed edges is $N_b+2N_s+1$, where 1 refers to the external electrical load.
+    \item Attributes of edges:
         Each edge is assigned two attributes, voltage difference and resistance, based on the equivalent method mentioned above.
-        The values for the battery $B_i$, switch $S_j$, and external loads correspond to $(u_i, r_i)$, $(0, r_j)$, and $(0, R_o)$, respectively.
+        The values for  battery $B_i$, switch $S_j$, and external loads correspond to $(u_i, r_i)$, $(0, r_j)$, and $(0, R_o)$, respectively.
 \end{enumerate}
 
-\subsection{Constraints and Objective Function}
+\subsection{Constraints and objective function}
 
-For a given RBS, determination of its MAC involves maximizing the RBS output current while ensuring that the currents of all batteries do not exceed the batteries' maximum allowable current. 
-In this subsection, the constraints and objective function to solve the RBS's MAC will be established through circuit analysis, based on its directed graph model provided in the previous subsection.
+For a given RBS, determining its MAC involves maximizing the RBS output current while ensuring that the sum of the currents of all batteries does not exceed the batteries' MAC. 
+This subsection establishes the constraints and objective function to determine the RBS's MAC  through circuit analysis based on the directed graph model provided in the previous section.
 
-First, the topology in the directed graph model is represented in matrix form $\bm{A}$, known as the incidence matrix , defined in Equation \ref{eq:A}.
+First, the topology in the directed graph model is represented in matrix form $\bm{A}$, known as the incidence matrix and defined as follows:
 \begin{align}\label{eq:A}
@@
 In this matrix, the rows and columns represent the nodes and edges of the directed graph, respectively.
-By distinguishing the components in the RBS corresponding to each column , $\bm{A}$ can be rewritten as:
+By distinguishing the components in the RBS corresponding to each column, $\bm{A}$ can be rewritten as
 \begin{equation}\label{eq:A_bso}
@@
 \end{equation}
-where $\bm{A}_b$, $\bm{A}_s$ and $\bm{A}_o$ are the sub-matrices corresponding to the batteries, switches and external electrical load, respectively.
-To alleviate computational complexity, matrix $\bm{A}$ undergoes dimensionality reduction.
-Since each directed edge has one node to leave and one to enter, the sum of the values in every column of $\bm{A}$ is zero.
-Therefore removing the last row will not result in a loss of information. 
-On the other hand, since each switch in the RBS is represented by a pair of directed edges with two-way directions, the two columns corresponding to the switch are mutually opposite.
-Thus, for the sub-matrix $\bm{A}_s$, only one column is retained for each pair of columns representing the same switch.
-As a result, $\bm{A}$ can be reduced to a $(N-1)\times(N_b+N_s+1)$ matrix, denoted as $\bm{\tilde{A}}$, for further calculation of current and voltage.
-Similar to Equation \ref{eq:A_bso}, $\bm{\tilde{A}}$ can be rewritten as:
+where $\bm{A}_b$, $\bm{A}_s$, and $\bm{A}_o$ are the sub-matrices corresponding to the batteries, switches, and external electrical load, respectively.
+To reduce the computational complexity, the dimensions of matrix $\bm{A}$ are reduced.
+Since each directed edge has one node to leave and one to enter, the values in every column of $\bm{A}$ sum to zero.
+Therefore, removing the last row will not result in a loss of information. 
+Conversely, since each switch in the RBS is represented by a pair of directed edges with two-way directions, the two columns corresponding to the switch are mutually opposite.
+Thus, for the submatrix $\bm{A}_s$, only one column is retained for each pair of columns representing the same switch.
+As a result, $\bm{A}$ can be reduced to an $(N-1)\times(N_b+N_s+1)$ matrix, denoted  $\bm{\tilde{A}}$, for further calculation of current and voltage.
+Similar to Eq. (\ref{eq:A_bso}), $\bm{\tilde{A}}$ can be rewritten as
 \begin{equation}\label{eq:A_bso_tilde}
@@
 
-After obtaining the incidence matrix, the currents of all batteries and output in RBS are determined by solving the circuit equations.
-According to Kirchhoffs law, we have
+After obtaining the incidence matrix, the currents of all batteries and output in the RBS are determined by solving the circuit equations.
+According to Kirchhoff's law, we have
 \begin{align}\label{eq:Kirchhoffs_law}
@@
 \end{align}
-where $\bm{I}$ and $\bm{U}$ indicate the current and voltage difference arrays of the $N_b+N_s+1$ edges, respectively;
+where $\bm{I}$ and $\bm{U}$ indicate the current and voltage difference arrays of the $N_b+N_s+1$ edges, respectively, and
 $\bm{U}_n$ is the voltage array of the $N-1$ nodes.
-These directed edges are treated as generalized branches and expressed in matrix form as follows
+These directed edges are treated as generalized branches and expressed in matrix form as follows:
 \begin{equation}\label{eq:generalized_branches}
@@
 where $\bm{U}_s$ and $\bm{I}_s$ denote the source voltage and source current of the generalized branches, respectively.
-Because all batteries have been equivalent to voltage sources rather than current sources in the previous subsection, all elements of the array $\bm{I}_s$ are 0, 
-while the elements of the array $\bm{U}_s$ are equal to the first attribute of the corresponding edges in the directed graph.
-The $\bm{Y}$ in Equation \ref{eq:generalized_branches} is the admittance matrix of the circuit, defined as the inverse of the impedance matrix.
-The elements on the diagonal of matrix $\bm{Y}$ are equal to the reciprocal of the resistance, which is the second attribute of the corresponding edges in the directed graph, and the off-diagonal elements $\bm{Y}$ are 0.
-The $\bm{X}$ is the state matrix, which describes whether the RBS batteries and switches are allowed to pass current.
+Because all batteries have been equivalent to voltage sources rather than current sources in the previous section, all elements of the array $\bm{I}_s$ are zero, 
+whereas the elements of the array $\bm{U}_s$ are equal to the first attribute of the corresponding edges in the directed graph.
+The matrix $\bm{Y}$ in Eq. (\ref{eq:generalized_branches}) is the admittance matrix of the circuit and is defined as the inverse of the impedance matrix.
+The elements on the diagonal of matrix $\bm{Y}$ are equal to the reciprocal of the resistance, which is the second attribute of the corresponding edges in the directed graph.
+The off-diagonal elements of $\bm{Y}$ are zero.
+$\bm{X}$ is the state matrix that determines whether the RBS batteries and switches can pass current.
 It is defined as
@@
     \bm{X} = \diag(
-    \underbrace{1, 0 \cdots, 1}_{N_b~\text{of}~0/1},
-    \underbrace{1, 0 \cdots, 1}_{N_s~\text{of}~0/1},
+    \underbrace{1, 0, \dots, 1}_{N_b~\text{of}~0/1},
+    \underbrace{1, 0, \dots, 1}_{N_s~\text{of}~0/1},
     1)
@@
         & & 1
-    \end{bmatrix}.
+    \end{bmatrix},
 \end{equation}
-Where the elements $x_i$ of the matrix $\bm{X}_b$ represent whether the battery $i$ has been removed from the circuit, with $x_i=1$ indicating removal and $x_i=0$ indicating that it is still available to supply power.
-When all batteries are health and capable of providing current to the external load, $\bm{X}_b$ is an identity matrix. 
-The elements $x_j$ of the matrix $\bm{X}_s$ represent whether the switch $j$ is closed, with $x_j=1$ indicating closure and $x_j=0$ indicating disconnection, which is consistent with the previous subsection.
+where element $x_i$ of matrix $\bm{X}_b$ indicates whether battery $i$ has been removed from the circuit, with $x_i=1$ indicating removal and $x_i=0$ indicating that battery $i$ is still available to supply power.
+When all batteries are healthy and capable of providing current to the external load, $\bm{X}_b$ is the identity matrix. 
+The elements $x_j$ of  matrix $\bm{X}_s$ determine whether switch $j$ is closed, with $x_j=1$ indicating a closed switch and $x_j=0$ indicating an open switch, which is consistent with the previous section.
 
-Theoretically, the output current $I_o$ and the currents of each battery $\bm{I}_b$ in the RBS  can be determined by solving Equations \ref{eq:Kirchhoffs_law}, \ref{eq:generalized_branches}, and \ref{eq:X} under any given state $\bm{X}$.
-In order to obtain specific constraint conditions and objective functions, it is further assumed that all batteries have the same electromotive force and internal resistance, denoted as $u_b$ and $r_b$, respectively.
-This allows for the derivation of explicit expressions for $I_o$ and $\bm{I}_b$.
-After derivation and simplification, the output current $I_o$ and the currents of each battery $\bm{I}_b$ are ultimately represented as Equations \ref{eq:I_o} and \ref{eq:I_b}, respectively.
+Theoretically, the output current $I_o$ and the currents of each battery $\bm{I}_b$ in the RBS  can be determined by solving Eqs.
+(\ref{eq:Kirchhoffs_law})--(\ref{eq:X}) under any given state $\bm{X}$.
+To obtain specific constraint conditions and objective functions, it is further assumed that all batteries have the same electromotive force and internal resistance, which are denoted $u_b$ and $r_b$, respectively.
+This allows us to derive explicit expressions for $I_o$ and $\bm{I}_b$.
+After derivation and simplification, the output current $I_o$ and the currents of each battery $\bm{I}_b$ are ultimately represented as Eqs. (\ref{eq:I_o}) and (\ref{eq:I_b}), respectively:
 \begin{equation}\label{eq:I_o}
@@
 \end{equation}
-where $\bm{U}_b$ is a $N_b\times 1$ array with all elements equaling to $u_b$;
-$\bm{Y}_n$ is the equivalent admittance matrix of the circuit, defined as
+where $\bm{U}_b$ is an $N_b\times 1$ array with all elements equal to $u_b$,
+and $\bm{Y}_n$ is the equivalent admittance matrix of the circuit and is defined as
 \begin{equation}\label{eq:Yn}
@@
 
-To characterize the current output capacity of the RBS structure under different switching states, an indicator $\eta$ is defined by the ratio of $I_o$ and $\max (\bm{I}_b)$ shown in Equation \ref{eq:eta}:
+To characterize the current output capacity of the RBS structure under different switching states, an indicator $\eta$ is defined by the ratio of $I_o$ to $\max (\bm{I}_b)$:
 \begin{equation}\label{eq:eta}
@@
 \end{equation}
-Finally the problem of solving MAC can be formulated as
+Finally the problem of finding the MAC can be formulated as
 \begin{align}
     & \max \eta(\bm{X}_s) \label{eq:max_eta}\\
-    \text{s.t.} & \max (\bm{I}_b) \leq I_m, \label{eq:Ib_leq_Im}
+    \text{s.t. } & \max (\bm{I}_b) \leq I_m, \label{eq:Ib_leq_Im}
 \end{align}
-where $I_m$ is the maximum allowable current of the battery.
+where $I_m$ is the MAC of the battery.
 
-However, it is still computationally difficult to solve \ref{eq:max_eta} because of the $\bm{Y}_n^{-1}$.
-On one hand, due to the introduction of nonlinear terms by $\bm{Y}_n^{-1}$, many effective methods in linear optimization are not suitable for this scenario.
-On the other hand, the rank of $Y_{n}$ is proportional to the number of batteries and switches, which can be very large for a large RBS system, leading to significant computational burden.
-Therefore, intelligent algorithms that rely on evolving by iteration may face efficiency problem when dealing with large RBS system.
-In order to address this issue, the problem should be considered from the perspective of guiding the RBS to reconstruct as many parallel structures as possible.
+However, it remains computationally difficult to solve Eq. (\ref{eq:max_eta}) because of $\bm{Y}_n^{-1}$.
+On one hand,  the introduction of nonlinear terms by $\bm{Y}_n^{-1}$ renders many  methods in linear optimization unsuitable for this problem.
+On the other hand, the rank of $Y_{n}$ is proportional to the number of batteries and switches, which can be very large for a large RBS, leading to a significant computational burden.
+As a result, intelligent algorithms that rely on evolution by iteration may face efficiency problems when dealing with a large RBS.
+To address this issue, the problem should be considered from the perspective of guiding the RBS to reconstruct as many parallel structures as possible.
 Consequently, a greedy algorithm based on the shortest path is proposed. 
-The detailed implementation process is presented in the following two subsections.
+The detailed implementation of this algorithm is presented in the following two sections.
 
-\subsection{Shortest Path}
+\subsection{Shortest path}
 
 The path $p$ used in this method is defined as the complete route that passes through one battery (or a consecutive series of batteries) and closed switches, connecting the anode $v_1$ to the cathode $v_N$ of the RBS.
-By applying a penalty to the series-connected batteries on the path, where additional batteries imply a longer distance, the algorithm encourages the RBS to form parallel structures as much as possible.
-Meanwhile, to reduce the number of switches controlled during the reconstruction process, a penalty is also applied to the total number of switches on the path, while ensuring the minimum number of batteries.
-Therefore, the distance $\omega$ of the path $p$ is defined by the following equation: 
+By applying a penalty to the series-connected batteries on the path, where additional batteries imply a greater distance, the algorithm encourages the RBS to form parallel structures to the extent possible.
+In addition, to reduce the number of switches controlled during the reconstruction process, a penalty is also applied to the total number of switches on the path while ensuring the minimum number of batteries.
+Therefore, the distance $\omega$ of path $p$ is  
 \begin{equation}\label{eq:weight}
-    \omega(p) = N_s \cdot n_b (p) + n_s (p),
+    \omega(p) = N_s  n_b (p) + n_s (p),
 \end{equation}
-where $N_s$ is the total number of switches in the system; 
-$n_b(p)$ and $n_s(p)$ are number of batteries and switches in the path $p$ respectively. 
-Moreover, the shortest path $SP_i$ is defined as the path with the minimum $\omega$ for battery $i$, as shown in the following equation:
+where $N_s$ is the total number of switches in the system, 
+and $n_b(p)$ and $n_s(p)$ are number of batteries and switches in path $p$, respectively. 
+Moreover, the shortest path $SP_i$ is defined as the path with the minimum $\omega$ for battery $i$:
 \begin{equation}\label{eq:def_sp}
@@
 \end{equation}
-where $P_i$ is the set of all paths from $v_1$ to $v_N$ which pass through the directed edge $i$.
+where $P_i$ is the set of all paths from $v_1$ to $v_N$ that pass through directed edge $i$.
 
-The $SP_i$ can be solved by the Dijkstra algorithm.
-The Dijkstra algorithm is a graph search method that finds the shortest path between two given nodes in a weighted graph, efficiently solving the single-source shortest path problem.
-Assuming that the cathode and anode of battery $i$ are denoted as $v_i^-$ and $v_i^+$ respectively, the path $p$ of battery $i$  can be divided into three segments : $v_1 \rightarrow v_i^-$, $v_i^+ \rightarrow v_N$, and $v_i^- \rightarrow v_i^+$.
-The $v_i^- \rightarrow v_i^+$ is the directed edge corresponding to battery $i$. 
-With the Dijkstra algorithm, shortest paths for the $v_1 \rightarrow v_i^-$ and $v_i^+ \rightarrow v_N$ can be calculated under the weights given in Equation \ref{eq:weight}, denoted as $SP(v_i^- \rightarrow v_i^+)$ and $SP(v_i^+ \rightarrow v_N)$, respectively.
-Finally, the $SP_i$ for battery $i$ is formed by the complete path with $SP(v_1 \rightarrow v_i^-)$, $v_i^- \rightarrow v_i^+$, and $SP(v_i^+ \rightarrow v_N)$.
+$SP_i$ can be solved by the Dijkstra algorithm.
+The Dijkstra algorithm is a graph-search method that finds the shortest path between two given nodes in a weighted graph, efficiently solving the single-source shortest-path problem.
+Denoting the cathode and anode of battery $i$ as $v_i^-$ and $v_i^+$ respectively, then path $p$ of battery $i$  can be divided into three segments: $v_1 \rightarrow v_i^-$, $v_i^+ \rightarrow v_N$, and $v_i^- \rightarrow v_i^+$.
+$v_i^- \rightarrow v_i^+$ is the directed edge corresponding to battery $i$.
+With the Dijkstra algorithm, shortest paths for $v_1 \rightarrow v_i^-$ and $v_i^+ \rightarrow v_N$ can be calculated under the weights given in Eq.
+(\ref{eq:weight}) and denoted $SP(v_i^- \rightarrow v_i^+)$ and $SP(v_i^+ \rightarrow v_N)$, respectively.
+Finally, $SP_i$ for battery $i$ is formed by the complete path, which consists of $SP(v_1 \rightarrow v_i^-)$, $v_i^- \rightarrow v_i^+$, and $SP(v_i^+ \rightarrow v_N)$.
 
-\subsection{Greedy Algorithm}\label{subsec:greedy_solution}
+\subsection{Greedy algorithm}\label{subsec:greedy_solution}
 
-From the perspective of series/parallel connections, integrating more batteries into the circuit through their shortest paths ($SP$s) results in a larger number of batteries connected in parallel, thereby increasing the total output current of the RBS.
+From the perspective of series vs parallel connections, integrating more batteries into the circuit through their shortest paths ($SP$s) results in more batteries connected in parallel, thereby increasing the total output current of the RBS.
 However, conflicts may arise between the $SP$s of different batteries. 
-For instance, the $SP$s of two batteries might form a short-circuited RBS structure, which is not allowed. 
-To address this issue, a greedy algorithm is employed to incorporate as many $SP$s as possible while satisfying the reconstruction requirements.
+For instance, the $SP$s of two batteries might form a short-circuit RBS structure, which is not allowed. 
+To address this issue, a greedy algorithm incorporates as many $SP$s as possible while satisfying the reconstruction requirements.
 
-The algorithm, as illustrated in Figure \ref{fig:flowchart}, can be summarized as follows, with the corresponding pseudo-code presented in Algorithm \ref{alg:greedy}.
-First, the shortest paths ($SP$s) are obtained using Equations \ref{eq:weight} and \ref{eq:def_sp} in conjunction with Dijkstra Search. 
-Next, the matrix $\bm{A}$ is calculated using Equation \ref{eq:A}, and the initial $N_{set}$ is set to $N_b$. 
-The algorithm iteratively checks different combinations of $c_b$ batteries from $N_b$ and updates $N_{set}$ using a dichotomy method until convergence is reached. 
-For each combination, the algorithm constructs an effective solution if possible, and calculates the currents $I_o$ and $\bm{I}_b$ using Equations \ref{eq:I_o} and \ref{eq:I_b}. 
-If the maximum current $\bm{I}_b$ is less than or equal to $I_m$, the $\eta$ is calculated using Equation \ref{eq:eta}, and the maximum $\eta$ is updated accordingly. 
-Finally, the algorithm outputs the maximum $\eta$ once $N_{set}$ converges.
+The algorithm (see pseudo-code in Algorithm 1) is illustrated in Fig. \ref{fig:flowchart} and is summarized as follows:
+First, the $SP$s are obtained by using Eqs. (\ref{eq:weight}) and (\ref{eq:def_sp}) in conjunction with the Dijkstra search. 
+Next, the matrix $\bm{A}$ is calculated using Eq. (\ref{eq:A}), and the initial $N_{\text{set}}$ is set to $N_b$. 
+The algorithm uses a dichotomy method to iteratively check until convergence different combinations of $c_b$ batteries from $N_b$ and updates $N_{\text{set}}$. 
+For each combination, the algorithm constructs an effective solution if possible and calculates the currents $I_o$ and $\bm{I}_b$ by using Eqs. (\ref{eq:I_o}) and (\ref{eq:I_b}). 
+If the maximum current $\bm{I}_b$ is less than or equal to $I_m$, $\eta$ is calculated by using Eq. (\ref{eq:eta}), and the maximum $\eta$ is updated accordingly. 
+Finally, the algorithm outputs the maximum $\eta$ once $N_{\text{set}}$ converges.
 
@@
     \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Equation \ref{eq:A}};
-    \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{set}=N_b$ };
-    \node[punkt, below=0.3of get_Nset] (get_cb) {get $c_b$s by combinating $N_{set}$ batteries from $N_b$};
+    \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{\text{set}}=N_b$ };
+    \node[punkt, below=0.3of get_Nset] (get_cb) {get $c_b$s by combinating $N_{\text{set}}$ batteries from $N_b$};
     \node[draw, diamond, aspect=2, below=0.3of get_cb] (is_check_all_cb) {are all $c_b$s checked?};
-    \node[draw, diamond, aspect=2, right=1of is_check_all_cb] (is_Nset_converged) {is $N_{set}$ converged?};
-    \node[punkt, above=of is_Nset_converged] (reset_Nset) {reset $N_{set}$ by dichotomy};
+    \node[draw, diamond, aspect=2, right=1of is_check_all_cb] (is_Nset_converged) {is $N_{\text{set}}$ converged?};
+    \node[punkt, above=of is_Nset_converged] (reset_Nset) {reset $N_{\text{set}}$ by dichotomy};
     \node[punkt, text width=15em, below=0.3of is_check_all_cb] (get_Xs) {
@@
 
+% \begin{figure}[htbp]
+%     \centering
+%     \includegraphics[width=\textwidth]{flowchart.jpg}
+%     \caption{Computational flowchart of MAC for a given RBS.}\label{fig:flowchart}
+% \end{figure}
+
 \section{Case Study}
@@
     \end{subfigure}
-    \caption{The 4-battery RBS structures proposed by (a)Lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b)Visairo\cite{visairoReconfigurableBatteryPack2008} and (c)this paper.}
+    \caption{The four-battery RBS structures proposed by (a) Lawson \cite{lawsonSoftwareConfigurableBattery2012}, (b) Visairo \cite{visairoReconfigurableBatteryPack2008}, and (c) this paper.}
 \end{figure}
@@
 \cite{visairoReconfigurableBatteryPack2008} and Lawson et al.
-\cite{lawsonSoftwareConfigurableBattery2012}, both of which have been practically used.
-The primary goal of Visairo's structure (Figure \ref{fig:study-stru-Visairo}) was to achieve dynamic adjustment of RBS output power; however, the isolation of unhealthy batteries was not sufficiently addressed in their work.
-Lawson et al. designed the RBS structure shown in Figure \ref{fig:study-stru-Lawson} for the purpose of battery isolation. 
-This structure has the advantage of easily isolating batteries, but it cannot dynamically adjust the output current of RBS. 
-Based on the structures of Visairo and Lawson, this paper presents a new structure, as shown in Figure \ref{fig:study-stru-my}.
-By integrating the Visairo RBS structure into the Lawson RBS structure, the new structure not only allows the flexibility to switch the batteries between series, parallel, and mixed series-parallel modes, but also easily enables the isolation of highly degraded batteries from the RBS.
-And their variations in output current under battery isolation conditions will be studied.
-This RBS structure will be used to validate the effectiveness of the proposed method for calculating the MAC, and be compared with the Lawson's and Visairo's structure to illustrate its advantage on battery isolation.
+\cite{lawsonSoftwareConfigurableBattery2012}, both of which have seen real use.
+The primary goal of Visairo's structure (Fig.
+\ref{fig:study-stru-Visairo}) is to dynamically adjust the RBS output power.
+However, the isolation of unhealthy batteries is not sufficiently addressed in their work.
+Lawson et al. designed the RBS structure shown in Fig. \ref{fig:study-stru-Lawson} to isolate batteries. 
+Although this structure easily isolates batteries, it cannot dynamically adjust the output current of the RBS. 
+Based on the structures of Visairo and Lawson, this paper proposes the structure shown in Fig. \ref{fig:study-stru-my}.
+By integrating the Visairo RBS structure into the Lawson RBS structure, the proposed structure not only has the flexibility to switch the batteries between series, parallel, and mixed series-parallel modes but also allows the isolation of highly degraded batteries from the RBS.
+Their variation in output current under battery isolation will be studied.
+This RBS structure is used to validate the proposed method for calculating the MAC and is compared with Lawson's and Visairo's structure to demonstrate its advantages for battery isolation.
 
@@
 
-As shown in Figure \ref{fig:study-stru-my}, the new RBS structure consists of 4 batteries and 19 switches. 
-The corresponding directed graph is depicted in Figure \ref{fig:study-dirgraph-my}, which is composed of a total of 18 nodes and 43 edges. 
-Batteries $B_1$, $B_2$, $B_3$, and $B_4$ are denoted by green directed edges in the graph, while the 19 switches are represented by gray directed edges with bi-directional arrows. 
+As shown in Fig. \ref{fig:study-stru-my}, the new RBS structure consists of four batteries and 19 switches. 
+Figure \ref{fig:study-dirgraph-my} shows the corresponding directed graph, which is composed of 18 nodes and 43 edges. 
+Batteries $B_1$, $B_2$, $B_3$, and $B_4$ are denoted by green directed edges in the graph, and the 19 switches are represented by gray directed edges with bidirectional arrows. 
 The external electrical load is treated as a directed edge from the cathode of the RBS (i.e., node 18) to the anode (i.e., node 1), as indicated by the blue directed edge in the graph.
-Utilizing Equation \ref{eq:weight} and the Dijkstra algorithm, the $SP$s of the four batteries in the RBS structure of Figure \ref{fig:study-stru-my} are highlighted by red in Figures \ref{fig:sp1}-\ref{fig:sp4}.
-Finally, the MAC calculation results of the structure in Figure \ref{fig:study-stru-my} are shown as Table \ref{tab:study-results-my} and Figure \ref{fig:study-results-my}, obtained by the greedy algorithm \ref{alg:greedy}.
-Table \ref{tab:study-results-my} contains the switches states, the output current $I_o$, battery current $\bm{I}_b$ and ratio $\eta$ of the RBS structure with all batteries in good health when the RBS output reaches the MAC.
-Figure \ref{fig:study-results-my} presents the corresponding circuit, with the red highlight indicating that current is flowing through the respective branches.
+Using Eq.
+(\ref{eq:weight}) and the Dijkstra algorithm, the $SP$s of the four batteries in the RBS structure of Fig.
+\ref{fig:study-stru-my} are highlighted in red in Figs.
+\ref{fig:sp1} and \ref{fig:sp4}.
+Finally, the calculated MACs of the structure in Fig.
+\ref{fig:study-stru-my} are listed in Table \ref{tab:study-results-my} and Fig.
+\ref{fig:study-results-my}, as obtained by the greedy algorithm \ref{alg:greedy}.
+Table \ref{tab:study-results-my} contains the states of the switches, the output current $I_o$, the battery current $\bm{I}_b$, and the ratio $\eta$ of the RBS structure with all batteries in good health when the RBS output reaches the MAC.
+Figure \ref{fig:study-results-my} presents the corresponding circuit, with the red highlight indicating that the current is flowing through the respective branches.
 
@@
     \caption{
-        For the RBS structure in Figure \ref{fig:study-stru-my}, 
-        (a)its directed graph 
-        and the $SP$s (highlighted in red) of battery (b)$B_1$, (c)$B_2$, (d)$B_3$, (e)$B_4$.
-        (f)The circuit of the RBS with its output reaching the MAC.
+        For the RBS structure in Fig. \ref{fig:study-stru-my}, 
+        (a) its directed graph 
+        and the $SP$s (highlighted in red) of battery (b) $B_1$, (c) $B_2$, (d) $B_3$, and (e) $B_4$.
+        (f) Circuit of RBS with its output reaching the MAC.
         }
@@
   \centering
-    \caption{MAC Calculating result of the 4-battery RBS structure in Figure \ref{fig:study-stru-my}.}
+    \caption{Calculated MAC for four-battery RBS structure in Fig. \ref{fig:study-stru-my}.}
     \begin{tabular}{cc}
     \toprule
-        Structure & Figure \ref{fig:study-stru-my} with 4 batteries and 19 switches  \\
+        Structure & Figure \ref{fig:study-stru-my} with four batteries and 19 switches  \\
     \midrule
-    Switch ON & $S_1$,$S_3$,$S_5$,$S_6$,$S_8$,$S_9$,$S_{10}$,$S_{12}$,$S_{18}$,$S_{19}$ \\
+    Switch on & $S_1$,$S_3$,$S_5$,$S_6$,$S_8$,$S_9$,$S_{10}$,$S_{12}$,$S_{18}$,$S_{19}$ \\
     $I_o$ & $2u_b/(2R_o+r_b)$ \\
     $\bm{I}_b$ & $[u_b/(2R_o+r_b),u_b/(2R_o+r_b),0,0]$ \\
-    $\max$$\eta$     & 2 \\
+    $\max \eta$     & 2 \\
     \bottomrule
@@
 
-Similarly, the MAC calculation results of the structures in Figures \ref{fig:study-stru-Lawson} and \ref{fig:study-stru-Visairo} are shown as Table \ref{tab:study-results-Lawson} and Table \ref{tab:study-results-Visairo}, respectively.
-In order to verify and compare the results from the greedy algorithm, we also utilized a brute force algorithm that go through all possible switch states to calculate the MAC of the same three RBS. 
-For a given RBS structure with $N_s$ switches, the final $\max$ $\eta$ is the maximum of $\eta$s from all $2^{N_s}$ reconfigured structures.
-The final results are the same as the results shown in Tables \ref{tab:study-results-my}-\ref{tab:study-results-Visairo}.
-It is worth noting that the method used the greedy algorithm only calculated 11, 11, and 1 reconfigured structures for the RBS structure in Figures \ref{fig:study-stru-my}, \ref{fig:study-stru-Lawson}, \ref{fig:study-stru-Visairo}, respectively.
-While for the same RBS, the method counted all possible switch states computed $2^{19}$, $2^{15}$, and $2^{13}$ structures, respectively.
+Similarly, the results of the MAC calculation for the structures in Figs.
+\ref{fig:study-stru-Lawson} and \ref{fig:study-stru-Visairo} are listed in Tables \ref{tab:study-results-Lawson} and  \ref{tab:study-results-Visairo}, respectively.
+To verify and compare the results from the greedy algorithm, we also used a brute-force algorithm that iterates through all possible switch states to calculate the MAC of the same three RBSs. 
+For a given RBS structure with $N_s$ switches, the final $\max \eta$ is the maximum $\eta$ from all $2^{N_s}$ reconfigured structures.
+The final results are the same as the results shown in Tables \ref{tab:study-results-my}--\ref{tab:study-results-Visairo}.
+The method uses the greedy algorithm to calculate 11, 11, and 1 reconfigured structures for the RBS structure in Figs.
+\ref{fig:study-stru-my}, \ref{fig:study-stru-Lawson}, and \ref{fig:study-stru-Visairo}, respectively.
+For the same RBS, the method counts all possible switch states, which equates to $2^{19}$, $2^{15}$, and $2^{13}$ structures, respectively.
 
@@
   \centering
-    \caption{MAC Calculating result of the 4-battery RBS structure in Figure \ref{fig:study-stru-Lawson}.}
+    \caption{MAC Calculating result of the 4-battery RBS structure in Fig. \ref{fig:study-stru-Lawson}.}
     \begin{tabular}{cc}
@@
   \centering
-    \caption{MAC Calculating result of the 4-battery RBS structure in Figure \ref{fig:study-stru-Visairo}.}
+    \caption{MAC Calculating result of the 4-battery RBS structure in Fig. \ref{fig:study-stru-Visairo}.}
     \begin{tabular}{cc}
@@
 The MAC calculation results for the three structures under study, with varying numbers of isolated batteries, are presented in Table \ref{tab:isolated_mac}. 
-Figures \ref{fig:my-isolated-1}-\ref{fig:my-isolated-3} illustrate the corresponding switch control schemes for the new structure proposed in this paper under different isolated battery conditions.
+Figures \ref{fig:my-isolated-1}--\ref{fig:my-isolated-3} illustrate the corresponding switch-control schemes for the new structure proposed in this paper under different conditions of isolated batteries.
 
@@
     \caption{
-      The variation of MAC with the number of isolated batteries for different RBS structures, including the structure proposed by Lawson et al., Visairo et al.
-, and the structure proposed in this paper.
+      Variation of MAC with the number of isolated batteries for different RBS structures, including the structure proposed by Lawson et al., Visairo et al., and the structure proposed in this paper.
       }
@@
       \toprule
-      \multirow{2}[4]{*}{number of isolated batteries} & \multicolumn{3}{c}{$\eta$ of RBS structure} \\
-  \cmidrule{2-4}          & our  & Visairo's  & Lawson's  \\
+      \multirow{2}[4]{*}{Number of isolated batteries} & \multicolumn{3}{c}{$\eta$ of RBS structure} \\
+  \cmidrule{2-4}          & This paper  & Visairo  & Lawson  \\
       \midrule
@@
       \\
-      \footnotesize{$^{\mathrm{a}}$ isolate two batteries within the same substructure, as shown in Figure \ref{fig:my-isolated-2b}}\\
-      \footnotesize{$^{\mathrm{b}}$ isolate one battery in each of the two substructures, as shown in Figure \ref{fig:my-isolated-2w}}
+      \footnotesize{$^{\mathrm{a}}$ Isolate two batteries within the same substructure, as shown in Fig. \ref{fig:my-isolated-2b}.}\\
+      \footnotesize{$^{\mathrm{b}}$ Isolate one battery in each of the two substructures, as shown in Fig. \ref{fig:my-isolated-2w}.}
   \end{table}
@@
       \caption{
-          The circuit states of MACs when isolating (a)one, (b)two(best case), (c)two(worst case) and (d)three batteries for the structure in Figure \ref{fig:study-stru-my}.
+          Circuit states of MACs when isolating (a) one, (b) two (best case), (c) two (worst case), and (d) three batteries for the structure in Fig. \ref{fig:study-stru-my}.
           }
@@
 
-As shown in Figure \ref{fig:all-results-my} and Table \ref{tab:study-results-my}.
-When $B_1$ and $B_2$ or $B_3$ and $B_4$ are connected in parallel, the RBS can output the maximum current, which is $\eta=2$, i.e., twice the current output of a single battery in RBS. 
-Adding more batteries to the main circuit can only form a series structure and will not improve the MAC. 
-Therefore, the switches state given in Table \ref{tab:study-results-my} can make the RBS output current reach the maximum.
-The results of MAC obtained by brute force algorithm method is identical to the one by the greedy algorithm.
+Consider first the results shown in Fig. \ref{fig:all-results-my} and Table \ref{tab:study-results-my}.
+When $B_1$ and $B_2$ or $B_3$ and $B_4$ are connected in parallel, the RBS outputs the maximum current, which is $\eta=2$ (i.e., twice the current output of a single battery in the RBS). 
+Adding more batteries to the main circuit only forms a series structure and does not improve the MAC. 
+Therefore, the state of the switches given in Table \ref{tab:study-results-my} maximizes the RBS output current.
+The MAC obtained by the brute-force algorithm is identical to the one obtained by the greedy algorithm.
 
-From the literature research we have conducted, no formal report on the algorithm for MAC in RBS has been found yet.
-The brute force algorithm, which goes through all possible switch states, is the most straightforward way to solve the MAC problem and is used as a benchmark for the proposed greedy algorithm.
-Assuming that a RBS has $N_b$ batteries and $N_s$ switches, and the corresponding directed graph has $N$ nodes, it requires $2^{N_s}$ iterations to traverse all reconfigured structures.
-The calculation for each reconfigured structure by Equations \ref{eq:I_o}-\ref{eq:eta} requires matrix inversion and matrix multiplication, with a time complexity of $O(N^3+2N^2N_b+N^2N_s+NN^2_b)$.
-Therefore, the time complexity of the brute force algorithm is $O(2^{N_s}(N^3+2N^2N_b+N^2N_s+NN^2_b))$.
-The greedy algorithm proposed in this paper requires find the $SP$ for each battery, which requires $N_b$ iterations.
-Each $SP$ can be obtained by couple Dijkstra algorithms.
-Therefore, the total time complexity of calculating all $SP$s is $O(2N_b(N_b+2N_s)\log N)$.
-According to the Appendix \ref{alg:greedy}, the RBS can reconfigure $C^{N_{set}}_{N_b}$ structures by selecting $N_{set}$ batteries from $N_b$ batteries, which is $\sum^{N_b}_{N_{set}=1}C^{N_{set}}_{N_b}/N_b \approx 2^{N_b}/N_b$ on average.
-Hence, with bisection method, the time complexity of the greedy algorithm is $O(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log N_b+2N_b(N_b+2N_s)\log N)$, i.e., $O(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log N_b)$.
-Based on currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the number of batteries $N_b$, switches $N_s$, and nodes $N$ have the following quantitative relationships: $N_s \approx (3\sim 5)N_b$, $N \approx N_s$.
+The literature contains no report on an algorithm for calculating the MAC of an RBS.
+The brute-force algorithm, which goes through all possible switch states, is the most straightforward way to determine the MAC and is used as a benchmark for the proposed greedy algorithm.
+If an RBS has $N_b$ batteries and $N_s$ switches and the corresponding directed graph has $N$ nodes,  $2^{N_s}$ iterations are required to traverse all reconfigured structures.
+Calculating each reconfigured structure using Eqs. (\ref{eq:I_o})--(\ref{eq:eta}) requires matrix inversion and matrix multiplication, which has a time complexity of $O(N^3+2N^2N_b+N^2N_s+NN^2_b)$.
+Therefore, the time complexity of the brute-force algorithm is $O\bm(2^{N_s}(N^3+2N^2N_b+N^2N_s+NN^2_b)\bm)$.
+The greedy algorithm proposed in this paper requires  that $SP$ be found for each battery, which requires $N_b$ iterations.
+Each $SP$ can be obtained by several applications of Dijkstra's algorithms.
+Therefore, the total time complexity for calculating all $SP$s is $O\bm(2N_b(N_b+2N_s)\log_{10} N\bm)$.
+According to  Appendix \ref{alg:greedy}, the RBS can reconfigure $C^{N_{\text{set}}}_{N_b}$ structures by selecting $N_{\text{set}}$ batteries from $N_b$ batteries, which gives $\sum^{N_b}_{N_{\text{set}}=1}C^{N_{\text{set}}}_{N_b}/N_b \approx 2^{N_b}/N_b$ on average.
+Thus, with the bisection method, the time complexity of the greedy algorithm is $O\bm(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log_{10} N_b+2N_b(N_b+2N_s)\log_{10} N\bm)$ [i.e., $O\bm(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log_{10} N_b\bm)$].
+Based on currently proposed RBS structures \cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the number $N_b$ of batteries, $N_s$ of switches, and $N$ of nodes are quantitatively related as follows: $N_s \approx (3\text{--} 5)N_b$, $N \approx N_s$.
 After simplifying, the time complexity of the greedy algorithm is $O(2^{N_b}N_s^2\log N_b)$, while it is $O(2^{N_s}N_s^3)$ for brute force algorithm.
-Therefore, it is reasonable to believe that as the size of the RBS increases, especially the number of the switches, the greedy algorithm will have an advantage over the algorithm that goes through all reconfigured structures.
-This can be confirmed from the number of structures required for MAC determination in the previous subsection. 
-Compared to the brute force algorithm, the efficiency of the method based on the greedy algorithm has been improved by 3000 to 48000 times, which is theoretically $N_s 2^{N_s - N_b} \log N_b$ times according to the above time complexity analysis.
-Among the three RBS structures, the highest is the RBS structure with 19 switches (Figure \ref{fig:study-stru-my}).
-This benefit from two key points:
-(1) The $SP$s guide the RBS to reconfigure reasonable structures, rather than blindly going through all possible structures.
-This reduces the factor in complexity from $2^{N_s}$ to $2^{N_b}$, which is the main reason for the improvement in efficiency;
-(2) The bisection method further accelerates this process.
-However, the greedy algorithm proposed in this paper still contains exponential terms in the time complexity, which means it may not be able to handle extremely large-scale RBS structures.
+Therefore, as the RBS grows, especially in the number of switches, the greedy algorithm gains an advantage over the brute-force algorithm.
 
-It is important to note that $\eta$ is used as the objective function instead of $I_o$ in solving MAC. 
-This choice makes the result of MAC more reasonable. 
+This is confirmed by the number of structures required to determine the MAC in the previous section. 
+Compared with the brute-force algorithm, the method based on the greedy algorithm is 3\,000 to 48\,000 times more efficient, which is theoretically $N_s 2^{N_s - N_b} \log_{10} N_b$ times according to the above time-complexity analysis.
+Of the three RBS structures, the largest is the RBS structure with 19 switches (Fig. \ref{fig:study-stru-my}).
+This benefits from two key points:
+\begin{enumerate}
+\item[(1)] The $SP$s guide the RBS to reconfigure reasonable structures rather than blindly going through all possible structures.
+This reduces the complexity from $2^{N_s}$ to $2^{N_b}$, which is the main reason for the improvement in efficiency.
+\item[(2)] The bisection method further accelerates this process.
+However, the greedy algorithm proposed in this paper still contains exponential terms in the time complexity, which means it may not be able to handle extremely large RBS structures. 
+\end{enumerate}
+
+Note that $\eta$ is used as the objective function instead of $I_o$ in solving for the MAC. 
+This choice makes the resulting MAC more reasonable. 
 As shown in Table \ref{tab:study-results-my}, $I_o$ and $\bm{I}_b$ are functions of $R_o$, $u_b$, and $r_b$. 
-However, when $I_o$ was used as the objective function, even for the same RBS structure, the MAC solution and corresponding switches state could change due to different external electrical appliances.
-It would increase the difficulty and uncertainty in RBS structure design. 
-In order to eliminate the influences of such a problem, $\eta$, which is the ratio of $I_o$ and $\max\bm{I}_b$, is adopted as the objective function in our research.
-$\eta$ solely reflects the maximum output current capability of the RBS structure. 
-Assuming that the maximum allowed current of batteries in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by determining the $\eta$ of the structure.
+However, when $I_o$ is used as the objective function, even for the same RBS structure, the MAC solution and corresponding switch states could change due to different external electrical appliances.
+This would increase the difficulty and uncertainty of designing the RBS structure. 
+To eliminate this problem, the ratio $\eta=I_o/\max\bm{I}_b$ is adopted as the objective function in our research.
+Recall that $\eta$ reflects only the MAC of the RBS structure. 
+Assuming that the MAC of batteries in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by determining the value of $\eta$ for the structure.
 
-The method proposed in this paper is significant for the design of RBSs in the following aspects.
-Most of the currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} exhibit simple topological characteristics, and the calculation of MACs is relatively straightforward, even intuitive.
-However, these simple structures do not always fully satisfy the requirements of complex applications, such as dynamically adapting the circuit to variable and random operating conditions, and actively equalizing differences among the batteries in the RBS.
-Moreover, isolation of the batteries disrupts the original regularity and symmetry of the topology, which complicates the otherwise simple structure, and the maximum output current of the system becomes more challenging to obtain.
-On the contrary, the proposed method can be employed to calculate the MAC of arbitrary RBS structures, especially for these above complex and flexible RBS structures.
+The method proposed in this paper facilitates the design of RBSs in the following ways:
+Most currently proposed RBS structures \cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} have simple topological characteristics, so calculating the MACs is relatively straightforward, even intuitive.
+However, these simple structures do not always fully satisfy the requirements of complex applications, such as dynamically adapting the circuit to variable and random operating conditions or actively equalizing differences between batteries in the RBS.
+Moreover, isolating the batteries disrupts the original regularity and symmetry of the topology, which complicates the otherwise simple structure, and the maximum output current of the system becomes more challenging to obtain.
+In contrast, the proposed method calculates the MAC of arbitrary RBS structures, notably the complex and flexible RBS structures.
 
-To illustrate this point, the MACs of three RBS structures mentioned above are calculated after one and more batteries are isolated, as shown in Table \ref{tab:isolated_mac}. 
-Specifically, for the structure presented in Figure \ref{fig:study-stru-my}, the corresponding circuit states of MACs of isolating one to three batteries are depicted in Figures \ref{fig:my-isolated-1}-\ref{fig:my-isolated-3}.
-This structure has two cases of isolating two batteries: 
-one is to isolate two batteries within the same substructure (Figure \ref{fig:my-isolated-2b}), in which case $\eta=2$; the other is to isolate one battery in each of the two substructures (Figure \ref{fig:my-isolated-2w}), in which case $\eta=1$.
-From the results shown in Figure \ref{fig:my-isolated-1}-\ref{fig:my-isolated-3}, it can be observed that the proposed method provides reasonable outcomes for isolating batteries with any number and position.
+To illustrate this point, the MACs of three RBS structures mentioned above are calculated after isolating one or more of the batteries, as shown in Table \ref{tab:isolated_mac}. 
+Specifically, for the structure presented in Fig.
+\ref{fig:study-stru-my}, the corresponding circuit states for the MACs when isolating one to three batteries are depicted in Figs.
+\ref{fig:my-isolated-1}--\ref{fig:my-isolated-3}.
+This structure has two cases in which two batteries are isolated: 
+one is to isolate two batteries within the same substructure (Fig.
+\ref{fig:my-isolated-2b}), in which case $\eta=2$; the other is to isolate one battery in each of the two substructures (Fig.
+\ref{fig:my-isolated-2w}), in which case $\eta=1$.
+The results in Figs. \ref{fig:my-isolated-1}--\ref{fig:my-isolated-3} show that the proposed method provides reasonable outcomes for isolating any number of batteries in any position.
 
-Furthermore, the output current for the three RBS with isolated batteries is also shown in Table \ref{tab:isolated_mac}. 
-For the structure proposed by Lawson et al., the MAC is independent on the number of isolated batteries.
-However, for Visairo's structure, the MAC decreases with the increasing number of isolated batteries. 
-Nevertherless, the MAC of the structure proposed in this work is positioned between these above two structures. 
-This indicates that the structure proposed in this paper, compared to Lawson's structure, has a larger MAC under the same number of batteries, and exhibits a wider output current regulation range.
+Furthermore, the output current for the three RBSs with isolated batteries is also shown in Table \ref{tab:isolated_mac}. 
+For the structure proposed by Lawson et al., the MAC is independent of the number of isolated batteries.
+However, for Visairo's structure, the MAC decreases upon increasing the number of isolated batteries. 
+Nevertheless, the MAC of the structure proposed in this work falls between the MACs of these two structures. 
+This result indicates that the structure proposed in this paper has a larger MAC than Lawson's for the same number of batteries and has a wider range of regulation of the output current.
 
@@
 
-This paper proposes a pervasive and automatical method for computing the MAC of a given RBS efficiently.
-The method is implemented by a greedy algorithm combined with a directed graph model which considers the voltage, internal resistance, and maximum allowable current of the batteries, as well as the external load.
+This paper proposes a pervasive and automated method to efficiently compute the MAC of a RBS.
+The method is implemented by a greedy algorithm combined with a directed graph model that considers the voltage, internal resistance, and MAC of the batteries, as well as the external load.
 The main advantage of this method is its ability to calculate the MAC of RBSs with arbitrary structures.
-Even in the scenarios with random isolated batteries, the method remains effective.
-Compared with the brute force algorithm, the proposed method has higher computational efficiency under the same calculation results.
-This is achieved by two key points when constructing the greedy algorithm: 
-(1) Calculate the shortest path of each battery by Dijkstra algorithm to obtain the $SP$ of each battery; 
-(2) determine the maximum number of available batteries by bisection method to reduce the computational complexity.
-This method helps to fully tap the current output potential of the RBS, guide the RBS structure design and optimization in the design stage, and assist in evaluating the current overload risk of the system in practical applications.
+Even in scenarios with random isolated batteries, the proposed method remains effective.
+The proposed method is more computationally efficient than the brute-force algorithm for the same calculation results, which is achieved by two key points when constructing the greedy algorithm: 
+\begin{enumerate}
+\item[(1)] Calculate the shortest path of each battery by using the Dijkstra algorithm to obtain the $SP$ for each battery. 
+\item[(2)] Determine the maximum number of available batteries by bisection to reduce the computational complexity.
+\end{enumerate}
+This method helps to fully tap the current output potential of the RBS, guide the RBS structure design and optimization in the design stage, and assist in evaluating the current-overload risk of the system in practical applications.
 
@@
     {
-        $N_{set} \leftarrow \text{number of setected $SP$s calculated by dichotomy}$\;
-        $C_b    \leftarrow \text{set of all combinations of $N_{set} $~batteries from $N_b$}$\;
+        $N_{\text{set}} \leftarrow$ number of setected $SP$s calculated by dichotomy\;
+        $C_b    \leftarrow$ set of all combinations of $N_{\text{set}} $~batteries from $N_b$\;
         \For{$c_b \in C_b$}{
@@
 \end{algorithm}
+% \begin{figure}[htbp]
+%     \centering
+%     \includegraphics[width=\textwidth]{algorithm.jpg}
+% \end{figure}
 

### 2023-09-17 paper/SST/2-response_reviewer1.tex
形成完整的 letter 和 response

@@
 By introducing the shortest path($SP$) of the battery, the greedy algorithm transforms the enumeration of switch states in the brute force algorithm into the combination of the $SP$s, which greatly increases the efficiency of determining the maximum allowable current (MAC) of reconfigurable battery systems (RBSs).
-We have also provided a theoretical estimation of the improved efficiency, which is proportional to $N_s 2^{N_s - N_b} \log N_b$, where $N_s$ is the number of switches and $N_b$ is the number of batteries.
+We have also provided a theoretical estimation of the improved efficiency, which is proportional to $N_s 2^{N_s - N_b} \log_{10} N_b$, where $N_s$ is the number of switches and $N_b$ is the number of batteries.
 
@@
 \begin{changes}
-  changes in abstract
+
+This paper proposes a method to calculate the MAC of arbitrary RBSs using a greedy algorithm in conjunction with a directed graph model of the RBS.
+By introducing the shortest path of the battery, the greedy algorithm transforms the enumeration of switch states in the brute-force algorithm into the combination of the shortest paths, which greatly increases the efficiency with which the MAC is determined.
+The directed graph model, based on the equivalent circuit, provides a specific method for calculating the MAC of a given structure.
+The proposed method is validated on two published 4-battery-RBSs and one with a more complex structure.
+The results are the same as those of the brute-force algorithm, but the proposed method significantly improves the computational efficiency ($N_s 2^{N_s - N_b} \log_{10} N_b$ times faster than the brute force algorithm for a RBS with $N_b$ batteries and $N_s$ switches, theoretically).
+The main advantage of the proposed method is its ability to calculate the MAC of RBSs with arbitrary structures, even in scenarios with random isolated batteries.
 \end{changes}
@@
 
-Considering the Reviewer’s suggestion, we have expanded the literature review in the introduction section to provide a comprehensive overview of the existing RBS structures \cite{ci2007novel,9209774,engelhardt2021double,visairoReconfigurableBatteryPack2008,lawsonSoftwareConfigurableBattery2012,he2014reconfiguration,kim2009dynamic} and related works on structure analysis \cite{han2021analysis,chenSneakCircuitTheory2021}.
+Considering the Reviewer's suggestion, we have expanded the literature review in the introduction section to provide a comprehensive overview of the existing RBS structures \cite{ci2007novel,9209774,engelhardt2021double,visairoReconfigurableBatteryPack2008,lawsonSoftwareConfigurableBattery2012,he2014reconfiguration,kim2009dynamic} and related works on structure analysis \cite{han2021analysis,chenSneakCircuitTheory2021}.
 Although many RBS structures have been proposed for different purposes, such as dynamically adjusting the output voltage , increasing energy utilization efficiency, and improving the system's ability to recover from battery failures, they also bring challenges in design and control of the systems.
@@
 \begin{changes}
-  changes in introduction
+Recently, various types of RBSs with different flexibility and reconfigurability have been designed to meet application requirements. 
+For example, Ci et al. \cite{ci2007novel} proposed an RBS structure that dynamically adjusts the battery discharge rate to fully exploit the available capacity of each battery. 
+Jan's \cite{9209774,engelhardt2021double} structures  reconfigure structures with variant batteries in series to reach the (constantly changing) voltage requirements during electric vehicle charging.
+As shown in Fig.
+\ref{fig:stru-Visairo}, the structure proposed by Visairo et al.
+\cite{visairoReconfigurableBatteryPack2008}  changes the system's output voltage based on the load conditions, thereby reducing the power loss of the voltage regulator during the power supply process and improving the efficiency of energy use.
+Also, to enhance the energy efficiency of the system, Lawson et al.
+\cite{lawsonSoftwareConfigurableBattery2012} and He et al.
+\cite{he2014reconfiguration}  proposed simplified structures that have fewer switches than Visairo's design.
+Kim et al. \cite{kim2009dynamic} improved the system's ability to recover from battery failures by introducing multiple ports into the structure.
+
+The complex structure between batteries and switches gives RBSs flexibility but also creates challenges in the design and control of the system. 
+Thus, several approaches to analyze the RBS structure and performance have been proposed to tackle these challenges.
+For instance, 
+Han et al. \cite{han2021analysis} derived an analytical expression for the maximum switch current during battery system reconfiguration for a specific RBS structure. 
+This helps guide the selection of switches and supports the design of RBS hardware.
+Chen et al. \cite{chenSneakCircuitTheory2021} proposed a systematic approach based on  sneak circuit theory to fundamentally avoid the short-circuit problem of RBSs: 
+They thoroughly analyzed all paths between the cathode and anode of each battery in the RBS and identified paths that only contain switches as short-circuit paths for pre-checking before system reconfiguration.
 \end{changes}
@@
 \begin{changes}
-  changes in introduction
+The main contributions of this paper can be summarized as follows:
+\begin{itemize}
+  \item An efficient method is proposed to determine the MAC of RBSs with arbitrary structures, including scenarios with isolated batteries.
+  \item The greedy algorithm is applied to solve the MAC problem, the computational complexity of which is greatly reduced compared with the brute-force algorithm.
+  \item An improved directed graph model is introduced; it considers the voltage, the internal resistance, the MAC of the battery, and the external load to analyze the current of the RBS.
+\end{itemize}
 \end{changes}
@@
 
-We have derived the average time complexity of our proposed greedy algorithm-based MAC determination method to be approximately $O(2^{N_b}N_s^2\log N_b)$, where $N_b$ and $N_s$ are the number of batteries and switches, respectively.
+We have derived the average time complexity of our proposed greedy algorithm-based MAC determination method to be approximately $O(2^{N_b}N_s^2\log_{10} N_b)$, where $N_b$ and $N_s$ are the number of batteries and switches, respectively.
 However, as mentioned in our response to Comment 2, there was a blank in the literature regarding MAC determination methods.
@@
 \begin{changes}
-  changes in discussion
+The literature contains no report on an algorithm for calculating the MAC of an RBS.
+The brute-force algorithm, which goes through all possible switch states, is the most straightforward way to determine the MAC and is used as a benchmark for the proposed greedy algorithm.
+If an RBS has $N_b$ batteries and $N_s$ switches and the corresponding directed graph has $N$ nodes,  $2^{N_s}$ iterations are required to traverse all reconfigured structures.
+Calculating each reconfigured structure using Eqs. (\ref{eq:I_o})--(\ref{eq:eta}) requires matrix inversion and matrix multiplication, which has a time complexity of $O(N^3+2N^2N_b+N^2N_s+NN^2_b)$.
+Therefore, the time complexity of the brute-force algorithm is $O\bm(2^{N_s}(N^3+2N^2N_b+N^2N_s+NN^2_b)\bm)$.
+The greedy algorithm proposed in this paper requires  that $SP$ be found for each battery, which requires $N_b$ iterations.
+Each $SP$ can be obtained by several applications of Dijkstra's algorithms.
+Therefore, the total time complexity for calculating all $SP$s is $O\bm(2N_b(N_b+2N_s)\log_{10} N\bm)$.
+According to  Appendix \ref{alg:greedy}, the RBS can reconfigure $C^{N_{\text{set}}}_{N_b}$ structures by selecting $N_{\text{set}}$ batteries from $N_b$ batteries, which gives $\sum^{N_b}_{N_{\text{set}}=1}C^{N_{\text{set}}}_{N_b}/N_b \approx 2^{N_b}/N_b$ on average.
+Thus, with the bisection method, the time complexity of the greedy algorithm is $O\bm(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log_{10} N_b+2N_b(N_b+2N_s)\log_{10} N\bm)$ [i.e., $O\bm(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log_{10} N_b\bm)$].
+Based on currently proposed RBS structures \cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the number $N_b$ of batteries, $N_s$ of switches, and $N$ of nodes are quantitatively related as follows: $N_s \approx (3\text{--} 5)N_b$, $N \approx N_s$.
+After simplifying, the time complexity of the greedy algorithm is $O(2^{N_b}N_s^2\log_{10} N_b)$, while it is $O(2^{N_s}N_s^3)$ for brute force algorithm.
+Therefore, as the RBS grows, especially in the number of switches, the greedy algorithm gains an advantage over the brute-force algorithm.
+
+This is confirmed by the number of structures required to determine the MAC in the previous section. 
+Compared with the brute-force algorithm, the method based on the greedy algorithm is 3\,000 to 48\,000 times more efficient, which is theoretically $N_s 2^{N_s - N_b} \log_{10} N_b$ times according to the above time-complexity analysis.
+Of the three RBS structures, the largest is the RBS structure with 19 switches (Fig. \ref{fig:study-stru-my}).
+This benefits from two key points:
+\begin{enumerate}
+\item[(1)] The $SP$s guide the RBS to reconfigure reasonable structures rather than blindly going through all possible structures.
+This reduces the complexity from $2^{N_s}$ to $2^{N_b}$, which is the main reason for the improvement in efficiency.
+\item[(2)] The bisection method further accelerates this process.
+\end{enumerate}
 \end{changes}
@@
 \begin{changes}
-  changes in discussion
+However, the greedy algorithm proposed in this paper still contains exponential terms in the time complexity, which means it may not be able to handle extremely large RBS structures. 
 \end{changes}
@@
 
-TODO: explain about the accuracy, sufficiency and reliability of our results with Xu and Qian.
+TODO: discuss with Qian and Xu
 
@@
 
-\begin{figure}[htbp]
-    \centering
-    \begin{subfigure}[b]{0.2\textwidth}
-        \includegraphics[width=\textwidth]{stru-L-origin.png}
-        \caption{}
-        \label{fig:study-stru-Lawson}
-    \end{subfigure}
-    \hspace{0.02\textwidth}
-    \begin{subfigure}[b]{0.4\textwidth}
-        \includegraphics[width=\textwidth]{stru-V-origin.png}
-        \caption{}
-        \label{fig:study-stru-Visairo}
-    \end{subfigure}
-    \hspace{0.02\textwidth}
-    \begin{subfigure}[b]{0.31\textwidth}
-        \includegraphics[width=\textwidth]{stru-my-origin.png}
-        \caption{}
-        \label{fig:study-stru-my}
-    \end{subfigure}
-    \caption{The 4-battery RBS structures proposed by (a)Lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b)Visairo\cite{visairoReconfigurableBatteryPack2008} and (c)this paper.}
-\end{figure}
+% \begin{figure}[htbp]
+%     \centering
+%     \begin{subfigure}[b]{0.2\textwidth}
+%         \includegraphics[width=\textwidth]{stru-L-origin.png}
+%         \caption{}
+%         \label{fig:study-stru-Lawson}
+%     \end{subfigure}
+%     \hspace{0.02\textwidth}
+%     \begin{subfigure}[b]{0.4\textwidth}
+%         \includegraphics[width=\textwidth]{stru-V-origin.png}
+%         \caption{}
+%         \label{fig:study-stru-Visairo}
+%     \end{subfigure}
+%     \hspace{0.02\textwidth}
+%     \begin{subfigure}[b]{0.31\textwidth}
+%         \includegraphics[width=\textwidth]{stru-my-origin.png}
+%         \caption{}
+%         \label{fig:study-stru-my}
+%     \end{subfigure}
+%     \caption{The 4-battery RBS structures proposed by (a)Lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b)Visairo\cite{visairoReconfigurableBatteryPack2008} and (c)this paper.}
+% \end{figure}
 

### 2023-09-17 paper/SST/2-main.tex
形成检查后的 main

@@
 
-% \usepackage[final]{changes}
-% \usepackage[defaultcolor=red]{changes}
-% \added{xxx}
-% \deleted{xxxx}
-% \replaced{a}{b}
-
 %%%%%% Bibliography %%%%%%
 % Replace "sample" in the \addbibresource line below with the name of your .bib file.
-\usepackage[style=nejm, citestyle=numeric-comp, sorting=none]{biblatex}
+\usepackage[style=nejm, 
+citestyle=numeric-comp, 
+sorting=none]{biblatex}
 \addbibresource{ref.bib}
@@
 % Title Format: Use title case, capitalizing the first letter of each word, except for certain small words, such as articles and short prepositions
-\title{Using a Directed Graph Model and Greedy Algorithm to Determine the Maximum Allowable Current in a Reconfigurable Battery System}
+% \title{Using a Directed Graph Model and Greedy Algorithm to Determine the Maximum Allowable Current in a Reconfigurable Battery System}
+\title{Maximum Allowable Current Determination of RBS By Using a Directed Graph Model and Greedy Algorithm}
 
@@
 The directed graph model, based on the equivalent circuit, provides a specific method for calculating the MAC of a given structure.
-The proposed method is validated on two published 4-battery-RBSs and one with a more complex structure.
-The results are the same as those of the brute-force algorithm, but the proposed method significantly improves the computational efficiency ($N_s 2^{N_s - N_b} \log_{10} N_b$ times faster than the brute force algorithm for a RBS with $N_b$ batteries and $N_s$ switches, theoretically).
+The proposed method is validated on two published four-battery-RBSs and one with a more complex structure.
+The results are the same as those of the brute-force algorithm, but the proposed method significantly improves the computational efficiency ($N_s 2^{N_s - N_b} \log_{10} N_b$ times faster than the brute force algorithm for an RBS with $N_b$ batteries and $N_s$ switches, theoretically).
 The main advantage of the proposed method is its ability to calculate the MAC of RBSs with arbitrary structures, even in scenarios with random isolated batteries.
@@
 Moreover, the method provides an improved direct graph model that considers the voltage, the internal resistance, the MAC of the battery, and the external load.
-The method obtains the accurate current of the RBS under a specific circuit topology.
+The model obtains the accurate current of the RBS under a specific circuit topology.
 The main contributions of this paper can be summarized as follows:
@@
 Section II presents the framework and details of the proposed directed graph model and  greedy algorithm. 
-Section III discusses a case study that uses the proposed method to determine the MAC of a novel, complex structure. 
-The calculation results, the algorithm's computational complexity, and scenarios such as battery isolation are also discussed. 
-Finally, the concluding remarks are presented in Sec. IV.
+Section III discusses a case study that uses the proposed method to determine the MACs of two published four-battery RBSs and one with a more complex structure. 
+The calculation results, the algorithm's computational complexity, and scenarios such as battery random isolation are also discussed. 
+Finally, the concluding remarks are presented in Section IV.
 
@@
 Subsequently, based on the equivalent circuit, the MAC problem is transformed into specific objective functions and constraints.
-The shortest paths ($SP$s, where additional batteries and switches on the path are penalized as distance) for the batteries are then obtained  by using the Dijkstra algorithm to connect the batteries in the RBS in parallel.
-Finally, a greedy algorithm is used to organize the switches, allowing the batteries to connect via their $SP$s while satisfying the constraints, resulting in the MAC of the RBS.
+The shortest paths (SPs, where additional batteries and switches on the path are penalized as distance) for the batteries are then obtained  by using the Dijkstra algorithm to connect the batteries in the RBS in parallel.
+Finally, a greedy algorithm is used to organize the switches, allowing the batteries to connect via their SPs while satisfying the constraints, resulting in the MAC of the RBS.
 
@@
 For instance, as shown in Fig.
-\ref{fig:battery_simple}, the battery in the RBS can be represented as a black-box circuit consisting of two resistors $r_1$ and $r_2$ and a capacitor  $C$, known as the Thevenin model \cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
+\ref{fig:battery_simple}, the battery in the RBS is represented as a black-box circuit consisting of two resistors $r_1$ and $r_2$ and a capacitor  $C$, known as the Thevenin model \cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
 With an emphasis on the stable output of the RBS, the capacitor in the Thevenin model can be considered as an open circuit without affecting the steady-state current.
@@
         Therefore, there are three types of directed edges. 
-        For a battery $B_i$, its directed edge $e_i$ is drawn from the cathode to the anode because the battery in operation only allows current to flow in one direction.
-        For a switch $S_j$, since it is allowed to work under bi-directional currents, it is represented by a pair of directed edges with two-way directions. 
+        For battery $B_i$, its directed edge $e_i$ is drawn from the cathode to the anode because the battery in operation only allows current to flow in one direction.
+        For switch $S_j$, since it is allowed to work under bidirectional currents, it is represented by a pair of directed edges with two-way directions. 
         Regarding the external electronic load, because it is connected to the anode and cathode of the RBS, a directed edge from $v_N$ to $v_1$  represents it. 
@@
 
-For a given RBS, determining its MAC involves maximizing the RBS output current while ensuring that the sum of the currents of all batteries does not exceed the batteries' MAC. 
+For a given RBS, determining its MAC involves maximizing the RBS output current while ensuring that all battery currents do not exceed the batteries' MAC. 
 This subsection establishes the constraints and objective function to determine the RBS's MAC through circuit analysis based on the directed graph model provided in the previous section.
@@
 \end{equation}
-where $\bm{A}_b$, $\bm{A}_s$, and $\bm{A}_o$ are the sub-matrices corresponding to the batteries, switches, and external electrical load, respectively.
+where $\bm{A}_b$, $\bm{A}_s$, and $\bm{A}_o$ are the submatrices corresponding to the batteries, switches, and external electrical load, respectively.
 To reduce the computational complexity, the dimensions of matrix $\bm{A}$ are reduced.
@@
 After obtaining the incidence matrix, the currents of all batteries and output in the RBS are determined by solving the circuit equations.
-According to Kirchhoff's law, we have
+According to Kirchhoff's laws, we have
 \begin{align}\label{eq:Kirchhoffs_law}
@@
 where $\bm{U}_s$ and $\bm{I}_s$ denote the source voltage and source current of the generalized branches, respectively.
-Because all batteries have been equivalent to voltage sources rather than current sources in the previous section, all elements of the array $\bm{I}_s$ are zero, 
+Because all batteries have been equivalent to voltage sources rather than current sources in the previous subsection, all elements of the array $\bm{I}_s$ are zero, 
 whereas the elements of the array $\bm{U}_s$ are equal to the first attribute of the corresponding edges in the directed graph.
@@
 \end{equation}
-where element $x_i$ of matrix $\bm{X}_b$ indicates whether battery $i$ has been removed from the circuit, with $x_i=1$ indicating removal and $x_i=0$ indicating that battery $i$ is still available to supply power.
+where element $x_i$ of matrix $\bm{X}_b$ indicates whether battery $B_i$ has been removed from the circuit, with $x_i=1$ indicating removal and $x_i=0$ indicating that battery $B_i$ is still available to supply power.
 When all batteries are healthy and capable of providing current to the external load, $\bm{X}_b$ is the identity matrix. 
-The elements $x_j$ of  matrix $\bm{X}_s$ determine whether switch $j$ is closed, with $x_j=1$ indicating a closed switch and $x_j=0$ indicating an open switch, which is consistent with the previous section.
+The elements $x_j$ of  matrix $\bm{X}_s$ determine whether switch $S_j$ is closed, with $x_j=1$ indicating a closed switch and $x_j=0$ indicating an open switch, which is consistent with the previous subsection.
 
@@
 (\ref{eq:Kirchhoffs_law})--(\ref{eq:X}) under any given state $\bm{X}$.
-To obtain specific constraint conditions and objective functions, it is further assumed that all batteries have the same electromotive force and internal resistance, which are denoted $u_b$ and $r_b$, respectively.
+To further simplify the problem, it is assumed that all batteries have the same electromotive force and internal resistance, which are denoted $u_b$ and $r_b$, respectively.
 This allows us to derive explicit expressions for $I_o$ and $\bm{I}_b$.
@@
 Consequently, a greedy algorithm based on the shortest path is proposed. 
-The detailed implementation of this algorithm is presented in the following two sections.
+The detailed implementation of this algorithm is presented in the following two subsections.
 
@@
 and $n_b(p)$ and $n_s(p)$ are number of batteries and switches in path $p$, respectively. 
-Moreover, the shortest path $SP_i$ is defined as the path with the minimum $\omega$ for battery $i$:
+Moreover, the shortest path $SP_i$ is defined as the path with the minimum $\omega$ for battery $B_i$:
 \begin{equation}\label{eq:def_sp}
@@
 The Dijkstra algorithm is a graph-search method that finds the shortest path between two given nodes in a weighted graph, efficiently solving the single-source shortest-path problem.
-Denoting the cathode and anode of battery $i$ as $v_i^-$ and $v_i^+$ respectively, then path $p$ of battery $i$  can be divided into three segments: $v_1 \rightarrow v_i^-$, $v_i^+ \rightarrow v_N$, and $v_i^- \rightarrow v_i^+$.
-$v_i^- \rightarrow v_i^+$ is the directed edge corresponding to battery $i$.
+Denoting the cathode and anode of battery $B_i$ as $v_i^-$ and $v_i^+$ respectively, then path $p$ of battery $B_i$  can be divided into three segments: $v_1 \rightarrow v_i^-$, $v_i^+ \rightarrow v_N$, and $v_i^- \rightarrow v_i^+$.
+$v_i^- \rightarrow v_i^+$ is the directed edge corresponding to battery $B_i$.
 With the Dijkstra algorithm, shortest paths for $v_1 \rightarrow v_i^-$ and $v_i^+ \rightarrow v_N$ can be calculated under the weights given in Eq.
 (\ref{eq:weight}) and denoted $SP(v_i^- \rightarrow v_i^+)$ and $SP(v_i^+ \rightarrow v_N)$, respectively.
-Finally, $SP_i$ for battery $i$ is formed by the complete path, which consists of $SP(v_1 \rightarrow v_i^-)$, $v_i^- \rightarrow v_i^+$, and $SP(v_i^+ \rightarrow v_N)$.
+Finally, $SP_i$ for battery $B_i$ is formed by the complete path, which consists of $SP(v_1 \rightarrow v_i^-)$, $v_i^- \rightarrow v_i^+$, and $SP(v_i^+ \rightarrow v_N)$.
 
@@
 
-From the perspective of series vs parallel connections, integrating more batteries into the circuit through their shortest paths ($SP$s) results in more batteries connected in parallel, thereby increasing the total output current of the RBS.
-However, conflicts may arise between the $SP$s of different batteries. 
-For instance, the $SP$s of two batteries might form a short-circuit RBS structure, which is not allowed. 
-To address this issue, a greedy algorithm incorporates as many $SP$s as possible while satisfying the reconstruction requirements.
+From the perspective of series vs parallel connections, integrating more batteries into the circuit through their shortest paths (SPs) results in more batteries connected in parallel, thereby increasing the total output current of the RBS.
+However, conflicts may arise between the SPs of different batteries. 
+For instance, the SPs of two batteries might form a short-circuit RBS structure, which is not allowed. 
+To address this issue, a greedy algorithm incorporates as many SPs as possible while satisfying the reconstruction requirements.
 
 The algorithm (see pseudo-code in Algorithm 1) is illustrated in Fig. \ref{fig:flowchart} and is summarized as follows:
-First, the $SP$s are obtained by using Eqs. (\ref{eq:weight}) and (\ref{eq:def_sp}) in conjunction with the Dijkstra search. 
+First, the SPs are obtained by using Eqs. (\ref{eq:weight}) and (\ref{eq:def_sp}) in conjunction with the Dijkstra search. 
 Next, the matrix $\bm{A}$ is calculated using Eq. (\ref{eq:A}), and the initial $N_{\text{set}}$ is set to $N_b$. 
@@
     \node[punkt]     (input) {Input: RBS structure};
-    \node[punkt, below=0.3of input] (get_SP) {get $SP$s by Equations \ref{eq:weight} and \ref{eq:def_sp} and Dijkstra Search};
+    \node[punkt, below=0.3of input] (get_SP) {get SPs by Eqs. (\ref{eq:weight}) and (\ref{eq:def_sp}) and Dijkstra Search};
     \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Equation \ref{eq:A}};
@@
         $\bm{X}[j]=1$ else $0$};
-    \node[punkt, below=0.3of get_Xs] (get_Yn) {get $\bm{Y}_n$ by Equation \ref{eq:Yn}};
+    \node[punkt, below=0.3of get_Xs] (get_Yn) {get $\bm{Y}_n$ by Eq. (\ref{eq:Yn})};
     \node[draw, diamond, aspect=2, below=0.3of get_Yn] (is_Yn_invertible) {is $\bm{Y}_n$ invertible?};
     \node[punkt, right=1.3of is_Yn_invertible] (construct) {construct an effective solution};
-    \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Equations \ref{eq:I_o} and \ref{eq:I_b}};
+    \node[punkt, below=0.3of is_Yn_invertible] (get_I) {get $I_o$ and $\bm{I}_b$ by Eqs. (\ref{eq:I_o}) and (\ref{eq:I_b})};
     \node[draw, diamond, aspect=2, below=0.3of get_I] (is_leq_Im) {is $\max \bm{I}_b \leq I_m$?};
     \node[punkt, right=1.3of is_leq_Im] (drop_eta) {drop this $\eta$};
-    \node[punkt, below=0.3of is_leq_Im] (get_eta) {get $\eta$ by Equation \ref{eq:eta}};
+    \node[punkt, below=0.3of is_leq_Im] (get_eta) {get $\eta$ by Eq. (\ref{eq:eta})};
     \node[punkt, below=0.3of get_eta] (update_max_eta) {update $\max \eta$};
@@
 By integrating the Visairo RBS structure into the Lawson RBS structure, the proposed structure not only has the flexibility to switch the batteries between series, parallel, and mixed series-parallel modes but also allows the isolation of highly degraded batteries from the RBS.
-Their variation in output current under battery isolation will be studied.
-This RBS structure is used to validate the proposed method for calculating the MAC and is compared with Lawson's and Visairo's structure to demonstrate its advantages for battery isolation.
+These four-battery RBS structures are investigated in the case study, including the scenarios with random isolated batteries.
 
@@
 Using Eq.
-(\ref{eq:weight}) and the Dijkstra algorithm, the $SP$s of the four batteries in the RBS structure of Fig.
+(\ref{eq:weight}) and the Dijkstra algorithm, the SPs of the four batteries in the RBS structure of Fig.
 \ref{fig:study-stru-my} are highlighted in red in Figs.
@@
 Finally, the calculated MACs of the structure in Fig.
-\ref{fig:study-stru-my} are listed in Table \ref{tab:study-results-my} and Fig.
+\ref{fig:study-stru-my} are listed in Tab.
+\ref{tab:study-results-my} and shown in Fig.
 \ref{fig:study-results-my}, as obtained by the greedy algorithm \ref{alg:greedy}.
-Table \ref{tab:study-results-my} contains the states of the switches, the output current $I_o$, the battery current $\bm{I}_b$, and the ratio $\eta$ of the RBS structure with all batteries in good health when the RBS output reaches the MAC.
-Figure \ref{fig:study-results-my} presents the corresponding circuit, with the red highlight indicating that the current is flowing through the respective branches.
+Tab.
+\ref{tab:study-results-my} contains the states of the switches, the output current $I_o$, the battery current $\bm{I}_b$, and the ratio $\eta$ of the RBS structure with all batteries in good health when the RBS output reaches the MAC.
+Fig. \ref{fig:study-results-my} presents the corresponding circuit, with the red highlight indicating that the current is flowing through the respective branches.
 
@@
         (a) its directed graph 
-        and the $SP$s (highlighted in red) of battery (b) $B_1$, (c) $B_2$, (d) $B_3$, and (e) $B_4$.
+        and the SPs (highlighted in red) of battery (b) $B_1$, (c) $B_2$, (d) $B_3$, and (e) $B_4$.
         (f) Circuit of RBS with its output reaching the MAC.
@@
 Similarly, the results of the MAC calculation for the structures in Figs.
-\ref{fig:study-stru-Lawson} and \ref{fig:study-stru-Visairo} are listed in Tables \ref{tab:study-results-Lawson} and  \ref{tab:study-results-Visairo}, respectively.
+\ref{fig:study-stru-Lawson} and \ref{fig:study-stru-Visairo} are listed in Tabs.
+\ref{tab:study-results-Lawson} and  \ref{tab:study-results-Visairo}, respectively.
+
 To verify and compare the results from the greedy algorithm, we also used a brute-force algorithm that iterates through all possible switch states to calculate the MAC of the same three RBSs. 
-For a given RBS structure with $N_s$ switches, the final $\max \eta$ is the maximum $\eta$ from all $2^{N_s}$ reconfigured structures.
-The final results are the same as the results shown in Tables \ref{tab:study-results-my}--\ref{tab:study-results-Visairo}.
+The final results are the same as the results shown in Tabs. \ref{tab:study-results-my}--\ref{tab:study-results-Visairo}.
 The method uses the greedy algorithm to calculate 11, 11, and 1 reconfigured structures for the RBS structure in Figs.
@@
   \centering
-    \caption{MAC Calculating result of the 4-battery RBS structure in Fig. \ref{fig:study-stru-Lawson}.}
+    \caption{MAC Calculating result of the four-battery RBS structure in Fig. \ref{fig:study-stru-Lawson}.}
     \begin{tabular}{cc}
@@
   \centering
-    \caption{MAC Calculating result of the 4-battery RBS structure in Fig. \ref{fig:study-stru-Visairo}.}
+    \caption{MAC Calculating result of the four-battery RBS structure in Fig. \ref{fig:study-stru-Visairo}.}
     \begin{tabular}{cc}
@@
 Furthermore, the RBS with isolated batteries is taken into consideration and calculated. 
-The MAC calculation results for the three structures under study, with varying numbers of isolated batteries, are presented in Table \ref{tab:isolated_mac}. 
-Figures \ref{fig:my-isolated-1}--\ref{fig:my-isolated-3} illustrate the corresponding switch-control schemes for the new structure proposed in this paper under different conditions of isolated batteries.
+The MAC calculation results for the three structures under study, with varying numbers of isolated batteries, are presented in Tab. \ref{tab:isolated_mac}. 
+Figs.
+\ref{fig:my-isolated-1}--\ref{fig:my-isolated-3} illustrate the corresponding switch-control schemes for the new structure proposed in this paper under different conditions of isolated batteries.
 
@@
 
-Consider first the results shown in Fig. \ref{fig:all-results-my} and Table \ref{tab:study-results-my}.
+Consider first the results shown in Fig. \ref{fig:study-results-my} and listed in Tab. \ref{tab:study-results-my}.
 When $B_1$ and $B_2$ or $B_3$ and $B_4$ are connected in parallel, the RBS outputs the maximum current, which is $\eta=2$ (i.e., twice the current output of a single battery in the RBS). 
 Adding more batteries to the main circuit only forms a series structure and does not improve the MAC. 
-Therefore, the state of the switches given in Table \ref{tab:study-results-my} maximizes the RBS output current.
-The MAC obtained by the brute-force algorithm is identical to the one obtained by the greedy algorithm.
+Therefore, the state of the switches given in Tab. \ref{tab:study-results-my} maximizes the RBS output current.
+The brute-force method, which go through all possible switch states, also gives the same result.
 
@@
 Calculating each reconfigured structure using Eqs. (\ref{eq:I_o})--(\ref{eq:eta}) requires matrix inversion and matrix multiplication, which has a time complexity of $O(N^3+2N^2N_b+N^2N_s+NN^2_b)$.
-Therefore, the time complexity of the brute-force algorithm is $O\bm(2^{N_s}(N^3+2N^2N_b+N^2N_s+NN^2_b)\bm)$.
-The greedy algorithm proposed in this paper requires  that $SP$ be found for each battery, which requires $N_b$ iterations.
-Each $SP$ can be obtained by several applications of Dijkstra's algorithms.
-Therefore, the total time complexity for calculating all $SP$s is $O\bm(2N_b(N_b+2N_s)\log_{10} N\bm)$.
-According to  Appendix \ref{alg:greedy}, the RBS can reconfigure $C^{N_{\text{set}}}_{N_b}$ structures by selecting $N_{\text{set}}$ batteries from $N_b$ batteries, which gives $\sum^{N_b}_{N_{\text{set}}=1}C^{N_{\text{set}}}_{N_b}/N_b \approx 2^{N_b}/N_b$ on average.
-Thus, with the bisection method, the time complexity of the greedy algorithm is $O\bm(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log_{10} N_b+2N_b(N_b+2N_s)\log_{10} N\bm)$ [i.e., $O\bm(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log_{10} N_b\bm)$].
+Therefore, the time complexity of the brute-force algorithm is $O\bm((N^3+2N^2N_b+N^2N_s+NN^2_b)2^{N_s}\bm)$.
+The greedy algorithm proposed in this paper requires  that SP be found for each battery, which requires $N_b$ iterations.
+Each SP can be obtained by several applications of Dijkstra's algorithms.
+Therefore, the total time complexity for calculating all SPs is $O\bm(N_b(N_b+2N_s)\log_{10} N\bm)$.
+According to  Appendix \ref{alg:greedy}, the RBS can reconfigure $C^{N_{\text{set}}}_{N_b}$ structures by selecting $N_{\text{set}}$ batteries from $N_b$ batteries, which gives $\sum^{N_b}_{N_{\text{set}}=1}C^{N_{\text{set}}}_{N_b}/N_b \approx 2^{N_b} N_b^{-1}$ on average.
+Thus, with the bisection method, the time complexity of the greedy algorithm is $O\bm((N^3+2N^2N_b+N^2N_s+NN^2_b) 2^{N_b} N_b^{-1} \log_{10} N_b+N_b(N_b+2N_s)\log_{10} N\bm)$.
 Based on currently proposed RBS structures \cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the number $N_b$ of batteries, $N_s$ of switches, and $N$ of nodes are quantitatively related as follows: $N_s \approx (3\text{--} 5)N_b$, $N \approx N_s$.
-After simplifying, the time complexity of the greedy algorithm is $O(2^{N_b}N_s^2\log N_b)$, while it is $O(2^{N_s}N_s^3)$ for brute force algorithm.
+After simplifying, the time complexity of the method with greedy algorithm is $O(2^{N_b}N_s^2\log_{10} N_b)$, while it is $O(2^{N_s}N_s^3)$ for the method with brute force algorithm.
 Therefore, as the RBS grows, especially in the number of switches, the greedy algorithm gains an advantage over the brute-force algorithm.
-
 This is confirmed by the number of structures required to determine the MAC in the previous section. 
 Compared with the brute-force algorithm, the method based on the greedy algorithm is 3\,000 to 48\,000 times more efficient, which is theoretically $N_s 2^{N_s - N_b} \log_{10} N_b$ times according to the above time-complexity analysis.
-Of the three RBS structures, the largest is the RBS structure with 19 switches (Fig. \ref{fig:study-stru-my}).
 This benefits from two key points:
 \begin{enumerate}
-\item[(1)] The $SP$s guide the RBS to reconfigure reasonable structures rather than blindly going through all possible structures.
+\item[(1)] The SPs guide the RBS to reconfigure reasonable structures rather than blindly going through all possible structures.
 This reduces the complexity from $2^{N_s}$ to $2^{N_b}$, which is the main reason for the improvement in efficiency.
-\item[(2)] The bisection method further accelerates this process.
-However, the greedy algorithm proposed in this paper still contains exponential terms in the time complexity, which means it may not be able to handle extremely large RBS structures. 
+\item[(2)] The bisection method further accelerates this process, reducing the complexity from $2^{N_b}$ to $2^{N_b} N_B^{-1} \log_{10} N_b$.
 \end{enumerate}
+However, the greedy algorithm proposed in this paper still contains exponential terms in the time complexity, which means it may not be able to handle extremely large RBS structures having large $N_b$.
 
@@
 This choice makes the resulting MAC more reasonable. 
-As shown in Table \ref{tab:study-results-my}, $I_o$ and $\bm{I}_b$ are functions of $R_o$, $u_b$, and $r_b$. 
+As shown in Tab. \ref{tab:study-results-my}, $I_o$ and $\bm{I}_b$ are functions of $R_o$, $u_b$, and $r_b$. 
 However, when $I_o$ is used as the objective function, even for the same RBS structure, the MAC solution and corresponding switch states could change due to different external electrical appliances.
@@
 To eliminate this problem, the ratio $\eta=I_o/\max\bm{I}_b$ is adopted as the objective function in our research.
-Recall that $\eta$ reflects only the MAC of the RBS structure. 
+Recall that $\eta$ reflects only the structure's ability to output current, rather than the actual current outputing by the battery system.
 Assuming that the MAC of batteries in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by determining the value of $\eta$ for the structure.
@@
 
-To illustrate this point, the MACs of three RBS structures mentioned above are calculated after isolating one or more of the batteries, as shown in Table \ref{tab:isolated_mac}. 
+To illustrate this point, the MACs of three RBS structures mentioned above are calculated after isolating one or more of the batteries, as shown in Tab. \ref{tab:isolated_mac}. 
 Specifically, for the structure presented in Fig.
@@
 The results in Figs. \ref{fig:my-isolated-1}--\ref{fig:my-isolated-3} show that the proposed method provides reasonable outcomes for isolating any number of batteries in any position.
-
-Furthermore, the output current for the three RBSs with isolated batteries is also shown in Table \ref{tab:isolated_mac}. 
+Furthermore, the output current for the three RBSs with isolated batteries is also shown in Tab. \ref{tab:isolated_mac}. 
 For the structure proposed by Lawson et al., the MAC is independent of the number of isolated batteries.
@@
 
-This paper proposes a pervasive and automated method to efficiently compute the MAC of a RBS.
-The method is implemented by a greedy algorithm combined with a directed graph model that considers the voltage, internal resistance, and MAC of the batteries, as well as the external load.
+This paper proposes a pervasive and automated method to efficiently compute the MAC of an RBS.
+The method is implemented by a greedy algorithm combined with an improved directed graph model.
 The main advantage of this method is its ability to calculate the MAC of RBSs with arbitrary structures.
 Even in scenarios with random isolated batteries, the proposed method remains effective.
-The proposed method is more computationally efficient than the brute-force algorithm for the same calculation results, which is achieved by two key points when constructing the greedy algorithm: 
-\begin{enumerate}
-\item[(1)] Calculate the shortest path of each battery by using the Dijkstra algorithm to obtain the $SP$ for each battery. 
-\item[(2)] Determine the maximum number of available batteries by bisection to reduce the computational complexity.
-\end{enumerate}
+The proposed method is more computationally efficient than the brute-force algorithm for the same calculation results, which is mainly because of using the batteries' SPs to guide the RBS to reconfigure reasonable structures rather than blindly going through all possible structures.
 This method helps to fully tap the current output potential of the RBS, guide the RBS structure design and optimization in the design stage, and assist in evaluating the current-overload risk of the system in practical applications.
@@
     }
-    get $\bm{A}$ by Equation \ref{eq:A}\;
+    get $\bm{A}$ by Eq. \ref{eq:A}\;
     \While{not yet determine $\max \eta$ }
     {
-        $N_{\text{set}} \leftarrow$ number of setected $SP$s calculated by dichotomy\;
+        $N_{\text{set}} \leftarrow$ number of setected SPs calculated by dichotomy\;
         $C_b    \leftarrow$ set of all combinations of $N_{\text{set}} $~batteries from $N_b$\;
@@
             $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;
-            get $\bm{Y}_n$ by Equation \ref{eq:Yn}\;
+            get $\bm{Y}_n$ by Eq. \ref{eq:Yn}\;
             \eIf{$\bm{Y}_n$ is invertible}{
@@
             }{construct an effective solution}
-            get $I_o$ by Equation \ref{eq:I_o}\;
-            get $\bm{I}_b$ by Equation \ref{eq:I_b}\;
+            get $I_o$ by Eq. \ref{eq:I_o}\;
+            get $\bm{I}_b$ by Eq. \ref{eq:I_b}\;
             \eIf{$\max(\bm{I}_b)\leq I_m$}{

### 2023-09-17 paper/SST/2-response_reviewer1.tex
修正了 response 的细节

@@
 
-By introducing the shortest path($SP$) of the battery, the greedy algorithm transforms the enumeration of switch states in the brute force algorithm into the combination of the $SP$s, which greatly increases the efficiency of determining the maximum allowable current (MAC) of reconfigurable battery systems (RBSs).
-We have also provided a theoretical estimation of the improved efficiency, which is proportional to $N_s 2^{N_s - N_b} \log_{10} N_b$, where $N_s$ is the number of switches and $N_b$ is the number of batteries.
+By introducing the shortest path (SP) of the battery, the greedy algorithm transforms the enumeration of switch states in the brute force algorithm into the combination of the SPs, resulting in more efficient computation of the maximum allowable current (MAC).
+We have also provided a theoretical estimation of the improvement, which is proportional to $2^{N_s - N_b} N_s \log_{10} N_b$ for an RBS with $N_b$ batteries and $N_s$ switches.
 
-Here is the specific modification we made in the abstract:
+Here is the specific content we added in the abstract:
 \begin{changes}
-
 This paper proposes a method to calculate the MAC of arbitrary RBSs using a greedy algorithm in conjunction with a directed graph model of the RBS.
@@
 
-We believe that these modifications provide a more quantitative explanation of the achievements of our proposed method in the abstract.
+We hope the above content provide a more quantitative explanation of the achievements of our proposed method in the abstract.
 
@@
 
-Considering the Reviewer's suggestion, we have expanded the literature review in the introduction section to provide a comprehensive overview of the existing RBS structures \cite{ci2007novel,9209774,engelhardt2021double,visairoReconfigurableBatteryPack2008,lawsonSoftwareConfigurableBattery2012,he2014reconfiguration,kim2009dynamic} and related works on structure analysis \cite{han2021analysis,chenSneakCircuitTheory2021}.
-Although many RBS structures have been proposed for different purposes, such as dynamically adjusting the output voltage , increasing energy utilization efficiency, and improving the system's ability to recover from battery failures, they also bring challenges in design and control of the systems.
-Therefore, several works on structure analysis, like the maximum switch current and the short-circuit problem, have been proposed to tackle these challenges recently.
+Considering the Reviewer's suggestion, we have expanded the literature review in the introduction section to provide a comprehensive overview of the existing RBS structures \cite{ci2007novel,9209774,engelhardt2021double,visairoReconfigurableBatteryPack2008,lawsonSoftwareConfigurableBattery2012,he2014reconfiguration,kim2009dynamic} and related works on structure analyses \cite{han2021analysis,chenSneakCircuitTheory2021}.
+Although many RBS structures have been proposed for different purposes, such as dynamically adjusting the output voltage , increasing energy utilization efficiency, and improving the system's ability to recover from battery failures, these structures also bring challenges in design and control of the systems.
+Therefore, several works on structure analyses, like the maximum switch current and the short-circuit problem, have been proposed to tackle these challenges recently.
 However, determining the MAC of RBSs remains blank accroding to our literature review.
-A straightforward method is to enumerate all possible switch states, but the complexity of this method increases exponentially with the number of switches, and has too ineffection to apply.
+A straightforward method is to enumerate all possible switch states.
+But this method has exponentially increasing computational complexity with the number of switches, and is too ineffection to apply.
 
@@
 They thoroughly analyzed all paths between the cathode and anode of each battery in the RBS and identified paths that only contain switches as short-circuit paths for pre-checking before system reconfiguration.
+
+In spite of the maximum switch current mentioned above, the maximum allowable current (MAC), defined as the maximum allowed current  under the constraints of the battery cell, is another critical indicator of RBSs that needs to be evaluated during the design or control  of the system.
+The MAC helps the designers assess whether the RBS meets the output current requirements and contributes to the formulation of appropriate and safe management strategies for the battery management system.
+Unfortunately, few studies have analyzed the RBS structure to determine the RBS MAC.
+An intuitive and straightforward method is to enumerate all possible switch states and calculate the output current of the system under each reconfigurated structure.
+However, this method is inefficient and time-consuming, especially for RBSs with a large number of switches.
 \end{changes}
 
-Thanks once again for the reviewer's comments, which have greatly improved the quality and comprehensiveness of our manuscript.
-We believe that the revised introduction section now provides a thorough review of the literature and addresses the existing research gaps in the field of RBS structures.
+Thanks again for the reviewer's comments, which have greatly improved the quality and comprehensiveness of our manuscript.
 
@@
 
-We believe that these additions enhance the clarity of our manuscript.
-
 \end{revresponse}
@@
 
-It is really true as Reviewer suggested about the complexity of our proposed method and the comparison with other state-of-art methods.
+We totally agree with the reviewer's suggestion.
+It is indeed necessary to analyze the complexity of the proposed method and compare it with other existing methods.
 
 We have derived the average time complexity of our proposed greedy algorithm-based MAC determination method to be approximately $O(2^{N_b}N_s^2\log_{10} N_b)$, where $N_b$ and $N_s$ are the number of batteries and switches, respectively.
-However, as mentioned in our response to Comment 2, there was a blank in the literature regarding MAC determination methods.
-The brute force method, the most straightforward and intuitive method, was used as a benchmark for comparison, whose time complexity is $O(2^{N_s}N_s^3)$.
+However, as mentioned in our response to Comment 2, there is a blank in the literature regarding MAC determination methods.
+The brute force method, the most straightforward and intuitive method, is used as a benchmark for comparison, the time complexity of which is $O(2^{N_s}N_s^3)$.
 Since the number of switches in RBS is typically 3 to 5 times the batteries\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the method we proposed is theoretically more efficient than the brute force method.
@@
 The detailed derivation and discussion of the above points have been added to the revised manuscript under the Discussion subsection.
-Here is the specific modification:
+Here is the specific content:
 \begin{changes}
@@
 Calculating each reconfigured structure using Eqs. (\ref{eq:I_o})--(\ref{eq:eta}) requires matrix inversion and matrix multiplication, which has a time complexity of $O(N^3+2N^2N_b+N^2N_s+NN^2_b)$.
-Therefore, the time complexity of the brute-force algorithm is $O\bm(2^{N_s}(N^3+2N^2N_b+N^2N_s+NN^2_b)\bm)$.
-The greedy algorithm proposed in this paper requires  that $SP$ be found for each battery, which requires $N_b$ iterations.
-Each $SP$ can be obtained by several applications of Dijkstra's algorithms.
-Therefore, the total time complexity for calculating all $SP$s is $O\bm(2N_b(N_b+2N_s)\log_{10} N\bm)$.
-According to  Appendix \ref{alg:greedy}, the RBS can reconfigure $C^{N_{\text{set}}}_{N_b}$ structures by selecting $N_{\text{set}}$ batteries from $N_b$ batteries, which gives $\sum^{N_b}_{N_{\text{set}}=1}C^{N_{\text{set}}}_{N_b}/N_b \approx 2^{N_b}/N_b$ on average.
-Thus, with the bisection method, the time complexity of the greedy algorithm is $O\bm(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log_{10} N_b+2N_b(N_b+2N_s)\log_{10} N\bm)$ [i.e., $O\bm(2^{N_b}/N_b(N^3+2N^2N_b+N^2N_s+NN^2_b)\log_{10} N_b\bm)$].
+Therefore, the time complexity of the brute-force algorithm is $O\bm((N^3+2N^2N_b+N^2N_s+NN^2_b)2^{N_s}\bm)$.
+The greedy algorithm proposed in this paper requires  that SP be found for each battery, which requires $N_b$ iterations.
+Each SP can be obtained by several applications of Dijkstra's algorithms.
+Therefore, the total time complexity for calculating all SPs is $O\bm(N_b(N_b+2N_s)\log_{10} N\bm)$.
+According to  Appendix \ref{alg:greedy}, the RBS can reconfigure $C^{N_{\text{set}}}_{N_b}$ structures by selecting $N_{\text{set}}$ batteries from $N_b$ batteries, which gives $\sum^{N_b}_{N_{\text{set}}=1}C^{N_{\text{set}}}_{N_b}/N_b \approx 2^{N_b} N_b^{-1}$ on average.
+Thus, with the bisection method, the time complexity of the greedy algorithm is $O\bm((N^3+2N^2N_b+N^2N_s+NN^2_b) 2^{N_b} N_b^{-1} \log_{10} N_b+N_b(N_b+2N_s)\log_{10} N\bm)$.
 Based on currently proposed RBS structures \cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the number $N_b$ of batteries, $N_s$ of switches, and $N$ of nodes are quantitatively related as follows: $N_s \approx (3\text{--} 5)N_b$, $N \approx N_s$.
-After simplifying, the time complexity of the greedy algorithm is $O(2^{N_b}N_s^2\log_{10} N_b)$, while it is $O(2^{N_s}N_s^3)$ for brute force algorithm.
+After simplifying, the time complexity of the method with greedy algorithm is $O(2^{N_b}N_s^2\log_{10} N_b)$, while it is $O(2^{N_s}N_s^3)$ for the method with brute force algorithm.
 Therefore, as the RBS grows, especially in the number of switches, the greedy algorithm gains an advantage over the brute-force algorithm.
-
 This is confirmed by the number of structures required to determine the MAC in the previous section. 
 Compared with the brute-force algorithm, the method based on the greedy algorithm is 3\,000 to 48\,000 times more efficient, which is theoretically $N_s 2^{N_s - N_b} \log_{10} N_b$ times according to the above time-complexity analysis.
-Of the three RBS structures, the largest is the RBS structure with 19 switches (Fig. \ref{fig:study-stru-my}).
 This benefits from two key points:
 \begin{enumerate}
-\item[(1)] The $SP$s guide the RBS to reconfigure reasonable structures rather than blindly going through all possible structures.
+\item[(1)] The SPs guide the RBS to reconfigure reasonable structures rather than blindly going through all possible structures.
 This reduces the complexity from $2^{N_s}$ to $2^{N_b}$, which is the main reason for the improvement in efficiency.
-\item[(2)] The bisection method further accelerates this process.
+\item[(2)] The bisection method further accelerates this process, reducing the complexity from $2^{N_b}$ to $2^{N_b} N_B^{-1} \log_{10} N_b$.
 \end{enumerate}
@@
 We are sorry for our negligence of the limitations of the study. 
-As far as we are concerned, although the method we proposed is strongly efficient than the brute force method, it still has a exponential relationship with the number of batteries, which means unsufferable time cost will be caused for systems with large number of batteries.
+As far as we are concerned, although the method we proposed is strongly efficient than the brute force method, it still has a exponential relationship with the number of batteries.
+That means unsufferable time will be costed for systems with large number of batteries.
 
@@
 \begin{changes}
-However, the greedy algorithm proposed in this paper still contains exponential terms in the time complexity, which means it may not be able to handle extremely large RBS structures. 
+However, the greedy algorithm proposed in this paper still contains exponential terms in the time complexity, which means it may not be able to handle extremely large RBS structures having large $N_b$.
 \end{changes}
@@
 
-Thanks to the reviewer's suggestion, we have introduced two novel works in the RBS structure analysis field in the introduction, which respectively study the maximum switch current \cite{han2021analysis} and the short-circuit problem \cite{chenSneakCircuitTheory2021} in RBS structures.
+Thanks to the reviewer's suggestion, we have introduced two novel works in the RBS structure analysis field in the introduction, which respectively study the maximum switch current \cite{han2021analysis} and the short-circuit problem \cite{chenSneakCircuitTheory2021}.
 We believe that these works represent the innovation and recent advances in the field of RBS structure analysis.
 
-The reviewer also specially mentioned the work published in 2023: An efficient lightweight algorithm for scheduling tasks onto dynamically reconfigurable hardware using graph-oriented simulated annealing.
-We have carefully read this paper, and after fully discussion, we finally agreed that this paper is not relevant to our research.
+The reviewer also mentioned the work \enquote{An efficient lightweight algorithm for scheduling tasks onto dynamically reconfigurable hardware using graph-oriented simulated annealing}, sepcially.
+After carefully reading and fully discussion, we reached a conclusion that this paper is not relevant to our research.
 Although this paper uses a graph-based method, whose name is similar to the method described in our paper, it mainly studies the task scheduling problem in time series.
 While our research is about the maximum allowable current of RBS structure, which belongs to the field of structure analysis.
-Therefore, we believe that it is not appropriate to include this paper in our introduction and will not cite it.
+Therefore, we think it is not appropriate to include this paper in our introduction and will not cite it.
 
@@
 
-TODO: discuss with Qian and Xu
+Thanks for the reviewer's valuable feedback. 
+We have carefully considered the reviewer's question.
+In response, we complemented the computation and validation with the brute force method and provided more detailed explanation and discussion.
 
-Thanks for the reviewer's valuable feedback. We have carefully considered the reviewer's question.
-In response, we complemented the computation with the brute force method and provided more detailed explanation and discussion.
+In the Case study section of the paper, we investigated three RBS structures, two of which are from published literatures \cite{lawsonSoftwareConfigurableBattery2012,visairoReconfigurableBatteryPack2008} and the other is designed by ourselves, as shown in Figs.
+\ref{fig:study-stru-Lawson-comment}, \ref{fig:study-stru-Visairo-comment}, and \ref{fig:study-stru-my-comment}, respectively.
+The results of the three RBS structures calculated by our proposed method are shown in Tabs.
+\ref{tab:study-results-Lawson-greedy}, \ref{tab:study-results-Visairo-greedy} and \ref{tab:study-results-my-greedy}, respectively.
+The results by brute force method are shown in Tabs. \ref{tab:study-results-Lawson-brute}, \ref{tab:study-results-Visairo-brute} and \ref{tab:study-results-my-brute}, respectively.
 
-In the Case Study section of the paper, we investigated the MACs of three RBS structures, two of which are from published literatures \cite{lawsonSoftwareConfigurableBattery2012,visairoReconfigurableBatteryPack2008} and the other is designed by ourselves, as shown in Figure \ref{fig:study-stru-Lawson}, \ref{fig:study-stru-Visairo} and \ref{fig:study-stru-my}, respectively.
-The results of the three RBS structures calculated by our proposed method are shown in Tables \ref{tab:study-results-Lawson-greedy}, \ref{tab:study-results-Visairo-greedy} and \ref{tab:study-results-my-greedy}, respectively.
-The results by brute force method are shown in Tables \ref{tab:study-results-Lawson-brute}, \ref{tab:study-results-Visairo-brute} and \ref{tab:study-results-my-brute}, respectively.
+On the one hand, as shown in the Tabs.
+\ref{tab:study-results-Lawson-greedy} -- \ref{tab:study-results-my-brute}, the reconfigured structure results from greedy algorithm are consistent with the results from the brute force algorithm.
+Since the brute force algorithm enumerates all possible reconfigured structures, it ensures that we obtain the global optimal solution.
+On the other hand, the output current of the system calculated by our directed graph model is consistent with the experience and common sense.
+To illustrate this, the RBS in Fig. \ref{fig:study-stru-my-comment} is taken as an example here.
+The four batteries in this system can be divided into two groups: gourp $g_A$ has $B_1$ and $B_2$; group $g_B$ has $B_3$ and $B_4$.
+The relationship between the two batteries in each group can be switched between series and parallel by reconfigurating the structure.
+While the two groups can only connect in series or disconnect.
+Therefore, this system's MAC is the maximum of the MAC of the two groups (i.e., $\max[\text{MAC}(g_A),\text{MAC}(g_B)]$).
+Both $g_A$ and $g_B$ are the two-battery and degenerated structure of the RBS in Fig. \ref{fig:study-stru-Visairo-comment}, and have the same MAC (i.e., 2).
+Therefore, the MAC of the RBS in Fig. \ref{fig:study-stru-my-comment} is 2, consistent with the result shown in Tab. \ref{tab:study-results-my-greedy}.
 
-On the one hand, as shown in the Tables \ref{tab:study-results-Lawson-greedy} to \ref{tab:study-results-my-brute}, the reconfigured structure results from our greedy algorithm are consistent with the results from the brute force algorithm, which enumerates all possible reconfigured structures.
-It shows that our algorithm does find the global optimal solution.
-On the other hand, the output current of the system calculated by our directed graph model is consistent with the experience and common sense.
-To illustrate this, the RBS structure shown in Figure \ref{fig:study-stru-my} is taken as an example here.
-The four batteries in this structure can be divided into two groups: $B_1$ and $B_2$, $B_3$ and $B_4$.
-The relationship between the two batteries in each group can be switched between series and parallel by reconfiguration.
-While the two groups can only form a series connection or be disconnected, rather than a parallel connection.
-Therefore, the MAC of this structure is the maximum of the output current of the two groups, which is twice the maximum allowable current of a single battery, consistented with the result $\max \eta = 2$ shown in Table \ref{tab:study-results-my-greedy}.
+We hope the above content can address the reviewer's concerns.
 
-We hope that our above content can address the reviewer's concerns.
-
-% \begin{figure}[htbp]
-%     \centering
-%     \begin{subfigure}[b]{0.2\textwidth}
-%         \includegraphics[width=\textwidth]{stru-L-origin.png}
-%         \caption{}
-%         \label{fig:study-stru-Lawson}
-%     \end{subfigure}
-%     \hspace{0.02\textwidth}
-%     \begin{subfigure}[b]{0.4\textwidth}
-%         \includegraphics[width=\textwidth]{stru-V-origin.png}
-%         \caption{}
-%         \label{fig:study-stru-Visairo}
-%     \end{subfigure}
-%     \hspace{0.02\textwidth}
-%     \begin{subfigure}[b]{0.31\textwidth}
-%         \includegraphics[width=\textwidth]{stru-my-origin.png}
-%         \caption{}
-%         \label{fig:study-stru-my}
-%     \end{subfigure}
-%     \caption{The 4-battery RBS structures proposed by (a)Lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b)Visairo\cite{visairoReconfigurableBatteryPack2008} and (c)this paper.}
-% \end{figure}
+\begin{figure}[htbp]
+    \centering
+    \begin{subfigure}[b]{0.2\textwidth}
+        \includegraphics[width=\textwidth]{stru-L-origin.png}
+        \caption{}
+        \label{fig:study-stru-Lawson-comment}
+    \end{subfigure}
+    \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.4\textwidth}
+        \includegraphics[width=\textwidth]{stru-V-origin.png}
+        \caption{}
+        \label{fig:study-stru-Visairo-comment}
+    \end{subfigure}
+    \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.31\textwidth}
+        \includegraphics[width=\textwidth]{stru-my-origin.png}
+        \caption{}
+        \label{fig:study-stru-my-comment}
+    \end{subfigure}
+    \caption{The four-battery RBS structures proposed by (a)Lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b)Visairo\cite{visairoReconfigurableBatteryPack2008} and (c)this paper.}
+\end{figure}
 

### 2023-09-17 paper/SST/2-main.tex
修正了 main 的细节

@@
 With an emphasis on the stable output of the RBS, the capacitor in the Thevenin model can be considered as an open circuit without affecting the steady-state current.
-Therefore,  battery $i$ in the RBS can be simplified as a series connection between a constant voltage source $u_{i}$ and a resistor $r_{i}$.
-Furthermore, the state of switch $j$ in the RBS is represented by a binary variable $x_j$, where 0 is ON and 1 is OFF.
+Therefore,  battery $B_i$ in the RBS can be simplified as a series connection between a constant voltage source $u_{i}$ and a resistor $r_{i}$.
+Furthermore, the state of switch $S_j$ in the RBS is represented by a binary variable $x_j$, where 0 is ON and 1 is OFF.
 When the switch is closed, the circuit can be regarded as a resistor with a very small resistance $r_{j}$.
@@
     \node[punkt, below=0.3of input] (get_SP) {get SPs by Eqs. (\ref{eq:weight}) and (\ref{eq:def_sp}) and Dijkstra Search};
-    \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Equation \ref{eq:A}};
+    \node[punkt, below=0.3of get_SP] (get_A) {get $\bm{A}$ from Eq. (\ref{eq:A})};
     \node[punkt, below=0.3of get_A] (get_Nset) {init $N_{\text{set}}=N_b$ };
@@
     \node[draw, diamond, aspect=2, right=1of is_check_all_cb] (is_Nset_converged) {is $N_{\text{set}}$ converged?};
-    \node[punkt, above=of is_Nset_converged] (reset_Nset) {reset $N_{\text{set}}$ by dichotomy};
+    \node[punkt, above=0.3of is_Nset_converged] (reset_Nset) {reset $N_{\text{set}}$ by dichotomy};
     \node[punkt, text width=15em, below=0.3of is_check_all_cb] (get_Xs) {

### 2023-09-18 paper/SST/2-response_reviewer1.tex
修正了 response 的细节

@@
 The results of the three RBS structures calculated by our proposed method are shown in Tabs.
-\ref{tab:study-results-Lawson-greedy}, \ref{tab:study-results-Visairo-greedy} and \ref{tab:study-results-my-greedy}, respectively.
-The results by brute force method are shown in Tabs. \ref{tab:study-results-Lawson-brute}, \ref{tab:study-results-Visairo-brute} and \ref{tab:study-results-my-brute}, respectively.
+\ref{tab:study-results-Lawson-greedy}, \ref{tab:study-results-Visairo-greedy}, and \ref{tab:study-results-my-greedy}, respectively.
+The results by brute force method are shown in Tabs. \ref{tab:study-results-Lawson-brute}, \ref{tab:study-results-Visairo-brute}, and \ref{tab:study-results-my-brute}, respectively.
 

### 2023-09-20 paper/SST/2-main.tex
添加了 Xu 的修改意见
完成了Xu的意见修改

@@
 Reconfigurable battery systems (RBSs) present a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structure that can be adapted to different battery charging and discharging strategies.
-During RBS operation, the maximum allowable current (MAC) of the system that ensures that each battery's current remains within a safe range is a critical indicator to guide the system's reconfiguration, ensuring its safety and reliability.
+During RBS operation, a critical system parameter known as the maximum allowable current (MAC) become pivotal.
+This parameter is instrumental in maintaining the current of each individual battery within a safe range and serves as a guiding indicator for the system's reconfiguration, thereby ensuring its safety and reliability.
 This paper proposes a method to calculate the MAC of arbitrary RBSs using a greedy algorithm in conjunction with a directed graph model of the RBS.
@@
 
-Battery energy storage systems (BESSs) are extensively used in various applications, such as wind power plants and space power systems, to store and release high-quality electrical energy \cite{desiqueiraControlStrategySmooth2021,yangBatteryEnergyStorage2018,choCommercialResearchBattery2015,zhangDevelopmentProspectChinese2021,schwanbeckInternationalSpaceStation2019}.
+Battery energy storage systems (BESSs) are extensively used in various applications \cite{yangBatteryEnergyStorage2018}, such as wind power plants \cite{desiqueiraControlStrategySmooth2021} and space power systems \cite{schwanbeckInternationalSpaceStation2019,zhangDevelopmentProspectChinese2021}, to store and release high-quality electrical energy \cite{choCommercialResearchBattery2015}.
 Typically, a BESS consists of numerous batteries interconnected by series-parallel circuitry to provide the required capacity storage.
@@
 Moreover, if the worst battery fails during operation, it is highly likely to exacerbate the degradation of the other batteries, leading to reliability and safety issues \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019,jeevarajanBatterySafetyQualifications2012}.
-These problems have become significant technical barriers in the development of new-generation space vehicles and need to be addressed \cite{pomboHybridPowerSystem2021}.
+These problems have become significant technical barriers in many engineering projects requiring high reliability, such as developing new-generation space vehicles \cite{pomboHybridPowerSystem2021}.
 
@@
 To solve this issue, this paper proposes an efficient method to evaluate the MAC of RBSs. 
-First, a greedy algorithm is designed to efficiently search the possible circuit topology of RBSs with MAC.
-Moreover, the method provides an improved direct graph model that considers the voltage, the internal resistance, the MAC of the battery, and the external load.
-The model obtains the accurate current of the RBS under a specific circuit topology.
+In this method, a greedy algorithm is designed to efficiently search the possible circuit topology of RBSs with MAC.
+This algorithm transforms the enumeration of switch states in the brute-force algorithm into the combination of the batteries' shortest paths.
+An improved direct graph model that considers the voltage, the internal resistance, the MAC of the battery, and the external load is also introduced to analyze the current of the RBS.
 The main contributions of this paper can be summarized as follows:
@@
   \item An efficient method is proposed to determine the MAC of RBSs with arbitrary structures, including scenarios with isolated batteries.
-  \item The greedy algorithm is applied to solve the MAC problem, the computational complexity of which is greatly reduced compared with the brute-force algorithm.
-  \item An improved directed graph model is introduced; it considers the voltage, the internal resistance, the MAC of the battery, and the external load to analyze the current of the RBS.
+  \item A greedy algorithm is applied to solve the MAC problem, the computational complexity of which is greatly reduced compared with the brute-force algorithm.
+  \item An improved directed graph model is introduced to provide a specific method for calculating the MAC of a given structure.
 \end{itemize}
@@
 The method is implemented by a greedy algorithm combined with an improved directed graph model.
+Not only does the method provides the same global MAC calculation results as the brute force method, but it also improves the calculation efficiency by 3\,000 to 48\,000 times for three RBS structures in the case study.
+Theoretically, for an RBS with $N_s$ switches and $N_b$ batteries, the efficiency of the proposed method is $N_s 2^{N_s - N_b} \log_{10} N_b$ times that of the brute-force method, which is mainly because of using the batteries' SPs to guide the RBS to reconfigure reasonable structures rather than blindly going through all possible structures.
 The main advantage of this method is its ability to calculate the MAC of RBSs with arbitrary structures.
 Even in scenarios with random isolated batteries, the proposed method remains effective.
-The proposed method is more computationally efficient than the brute-force algorithm for the same calculation results, which is mainly because of using the batteries' SPs to guide the RBS to reconfigure reasonable structures rather than blindly going through all possible structures.
 This method helps to fully tap the current output potential of the RBS, guide the RBS structure design and optimization in the design stage, and assist in evaluating the current-overload risk of the system in practical applications.

### 2023-09-20 paper/SST/2-response_reviewer1.tex
添加了 Xu 的修改意见
形成最终的提交版本（SST）；将参考文献的引用方式由biber改为bibtex

@@
 \begin{changes}
-This paper proposes a method to calculate the MAC of arbitrary RBSs using a greedy algorithm in conjunction with a directed graph model of the RBS.
-By introducing the shortest path of the battery, the greedy algorithm transforms the enumeration of switch states in the brute-force algorithm into the combination of the shortest paths, which greatly increases the efficiency with which the MAC is determined.
-The directed graph model, based on the equivalent circuit, provides a specific method for calculating the MAC of a given structure.
-The proposed method is validated on two published four-battery-RBSs and one with a more complex structure.
-The results are the same as those of the brute-force algorithm, but the proposed method significantly improves the computational efficiency ($N_s 2^{N_s - N_b} \log_{10} N_b$ times faster than the brute force algorithm for an RBS with $N_b$ batteries and $N_s$ switches, theoretically).
-The main advantage of the proposed method is its ability to calculate the MAC of RBSs with arbitrary structures, even in scenarios with random isolated batteries.
+  \ExecuteMetaData[2-main]{reviewer1-comment1}
 \end{changes}
@@
 
-Considering the Reviewer's suggestion, we have expanded the literature review in the introduction section to provide a comprehensive overview of the existing RBS structures \cite{ci2007novel,9209774,engelhardt2021double,visairoReconfigurableBatteryPack2008,lawsonSoftwareConfigurableBattery2012,he2014reconfiguration,kim2009dynamic} and related works on structure analyses \cite{han2021analysis,chenSneakCircuitTheory2021}.
+Considering the Reviewer's suggestion, we have expanded the literature review in the introduction section to provide a comprehensive overview of the existing RBS structures (cited as \cite{ci2007novel,9209774,engelhardt2021double,visairoReconfigurableBatteryPack2008,lawsonSoftwareConfigurableBattery2012,he2014reconfiguration,kim2009dynamic} in revised manuscript) and related works on structure analyses (cited as \cite{han2021analysis,chenSneakCircuitTheory2021} in revised manuscript).
 Although many RBS structures have been proposed for different purposes, such as dynamically adjusting the output voltage , increasing energy utilization efficiency, and improving the system's ability to recover from battery failures, these structures also bring challenges in design and control of the systems.
@@
 \begin{changes}
-Recently, various types of RBSs with different flexibility and reconfigurability have been designed to meet application requirements. 
-For example, Ci et al. \cite{ci2007novel} proposed an RBS structure that dynamically adjusts the battery discharge rate to fully exploit the available capacity of each battery. 
-Jan's \cite{9209774,engelhardt2021double} structures  reconfigure structures with variant batteries in series to reach the (constantly changing) voltage requirements during electric vehicle charging.
-As shown in Fig.
-\ref{fig:stru-Visairo}, the structure proposed by Visairo et al.
-\cite{visairoReconfigurableBatteryPack2008}  changes the system's output voltage based on the load conditions, thereby reducing the power loss of the voltage regulator during the power supply process and improving the efficiency of energy use.
-Also, to enhance the energy efficiency of the system, Lawson et al.
-\cite{lawsonSoftwareConfigurableBattery2012} and He et al.
-\cite{he2014reconfiguration}  proposed simplified structures that have fewer switches than Visairo's design.
-Kim et al. \cite{kim2009dynamic} improved the system's ability to recover from battery failures by introducing multiple ports into the structure.
-
-The complex structure between batteries and switches gives RBSs flexibility but also creates challenges in the design and control of the system. 
-Thus, several approaches to analyze the RBS structure and performance have been proposed to tackle these challenges.
-For instance, 
-Han et al. \cite{han2021analysis} derived an analytical expression for the maximum switch current during battery system reconfiguration for a specific RBS structure. 
-This helps guide the selection of switches and supports the design of RBS hardware.
-Chen et al. \cite{chenSneakCircuitTheory2021} proposed a systematic approach based on  sneak circuit theory to fundamentally avoid the short-circuit problem of RBSs: 
-They thoroughly analyzed all paths between the cathode and anode of each battery in the RBS and identified paths that only contain switches as short-circuit paths for pre-checking before system reconfiguration.
-
-In spite of the maximum switch current mentioned above, the maximum allowable current (MAC), defined as the maximum allowed current  under the constraints of the battery cell, is another critical indicator of RBSs that needs to be evaluated during the design or control  of the system.
-The MAC helps the designers assess whether the RBS meets the output current requirements and contributes to the formulation of appropriate and safe management strategies for the battery management system.
-Unfortunately, few studies have analyzed the RBS structure to determine the RBS MAC.
-An intuitive and straightforward method is to enumerate all possible switch states and calculate the output current of the system under each reconfigurated structure.
-However, this method is inefficient and time-consuming, especially for RBSs with a large number of switches.
+  \ExecuteMetaData[2-main]{reviewer1-comment2}
 \end{changes}
@@
 \begin{changes}
-The main contributions of this paper can be summarized as follows:
-\begin{itemize}
-  \item An efficient method is proposed to determine the MAC of RBSs with arbitrary structures, including scenarios with isolated batteries.
-  \item The greedy algorithm is applied to solve the MAC problem, the computational complexity of which is greatly reduced compared with the brute-force algorithm.
-  \item An improved directed graph model is introduced; it considers the voltage, the internal resistance, the MAC of the battery, and the external load to analyze the current of the RBS.
-\end{itemize}
+  \ExecuteMetaData[2-main]{reviewer1-comment3}
 \end{changes}
@@
 The brute force method, the most straightforward and intuitive method, is used as a benchmark for comparison, the time complexity of which is $O(2^{N_s}N_s^3)$.
-Since the number of switches in RBS is typically 3 to 5 times the batteries\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the method we proposed is theoretically more efficient than the brute force method.
+Since the number of switches in RBS is typically 3 to 5 times the batteries, the method we proposed is theoretically more efficient than the brute force method.
 It has been validated by the case study in the manuscript.
@@
 \begin{changes}
-The literature contains no report on an algorithm for calculating the MAC of an RBS.
-The brute-force algorithm, which goes through all possible switch states, is the most straightforward way to determine the MAC and is used as a benchmark for the proposed greedy algorithm.
-If an RBS has $N_b$ batteries and $N_s$ switches and the corresponding directed graph has $N$ nodes,  $2^{N_s}$ iterations are required to traverse all reconfigured structures.
-Calculating each reconfigured structure using Eqs. (\ref{eq:I_o})--(\ref{eq:eta}) requires matrix inversion and matrix multiplication, which has a time complexity of $O(N^3+2N^2N_b+N^2N_s+NN^2_b)$.
-Therefore, the time complexity of the brute-force algorithm is $O\bm((N^3+2N^2N_b+N^2N_s+NN^2_b)2^{N_s}\bm)$.
-The greedy algorithm proposed in this paper requires  that SP be found for each battery, which requires $N_b$ iterations.
-Each SP can be obtained by several applications of Dijkstra's algorithms.
-Therefore, the total time complexity for calculating all SPs is $O\bm(N_b(N_b+2N_s)\log_{10} N\bm)$.
-According to  Appendix \ref{alg:greedy}, the RBS can reconfigure $C^{N_{\text{set}}}_{N_b}$ structures by selecting $N_{\text{set}}$ batteries from $N_b$ batteries, which gives $\sum^{N_b}_{N_{\text{set}}=1}C^{N_{\text{set}}}_{N_b}/N_b \approx 2^{N_b} N_b^{-1}$ on average.
-Thus, with the bisection method, the time complexity of the greedy algorithm is $O\bm((N^3+2N^2N_b+N^2N_s+NN^2_b) 2^{N_b} N_b^{-1} \log_{10} N_b+N_b(N_b+2N_s)\log_{10} N\bm)$.
-Based on currently proposed RBS structures \cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the number $N_b$ of batteries, $N_s$ of switches, and $N$ of nodes are quantitatively related as follows: $N_s \approx (3\text{--} 5)N_b$, $N \approx N_s$.
-After simplifying, the time complexity of the method with greedy algorithm is $O(2^{N_b}N_s^2\log_{10} N_b)$, while it is $O(2^{N_s}N_s^3)$ for the method with brute force algorithm.
-Therefore, as the RBS grows, especially in the number of switches, the greedy algorithm gains an advantage over the brute-force algorithm.
-This is confirmed by the number of structures required to determine the MAC in the previous section. 
-Compared with the brute-force algorithm, the method based on the greedy algorithm is 3\,000 to 48\,000 times more efficient, which is theoretically $N_s 2^{N_s - N_b} \log_{10} N_b$ times according to the above time-complexity analysis.
-This benefits from two key points:
-\begin{enumerate}
-\item[(1)] The SPs guide the RBS to reconfigure reasonable structures rather than blindly going through all possible structures.
-This reduces the complexity from $2^{N_s}$ to $2^{N_b}$, which is the main reason for the improvement in efficiency.
-\item[(2)] The bisection method further accelerates this process, reducing the complexity from $2^{N_b}$ to $2^{N_b} N_B^{-1} \log_{10} N_b$.
-\end{enumerate}
+  \ExecuteMetaData[2-main]{reviewer1-comment4}
 \end{changes}
@@
 \begin{changes}
-However, the greedy algorithm proposed in this paper still contains exponential terms in the time complexity, which means it may not be able to handle extremely large RBS structures having large $N_b$.
+  \ExecuteMetaData[2-main]{reviewer1-comment5}
 \end{changes}
@@
 
-Thanks to the reviewer's suggestion, we have introduced two novel works in the RBS structure analysis field in the introduction, which respectively study the maximum switch current \cite{han2021analysis} and the short-circuit problem \cite{chenSneakCircuitTheory2021}.
-We believe that these works represent the innovation and recent advances in the field of RBS structure analysis.
+Thanks to the reviewer's suggestion, we have introduced two novel works in the RBS structure analysis field in the introduction, which respectively study the maximum switch current and the short-circuit problem.
+Here is the specific content we added in the introduction:
+\begin{changes}
+  \ExecuteMetaData[2-main]{reviewer1-comment8}
+\end{changes}
 
@@
 
-In the Case study section of the paper, we investigated three RBS structures, two of which are from published literatures \cite{lawsonSoftwareConfigurableBattery2012,visairoReconfigurableBatteryPack2008} and the other is designed by ourselves, as shown in Figs.
+In the Case study section of the paper, we investigated three RBS structures, two of which are from published literatures (see references \cite{lawsonSoftwareConfigurableBattery2012,visairoReconfigurableBatteryPack2008} in revised manuscript) and the other is designed by ourselves, as shown in Figs.
 \ref{fig:study-stru-Lawson-comment}, \ref{fig:study-stru-Visairo-comment}, and \ref{fig:study-stru-my-comment}, respectively.
@@
 We hope the above content can address the reviewer's concerns.
+The above content corresponds to lines 276 to 283, and lines 289 to 294 of our revised manuscript without changes marked.
 
@@
   \centering
-    \caption{MAC Calculating result of the RBS structure in Figure \ref{fig:study-stru-Lawson} with our method.}
+    \caption{MAC Calculating result of the RBS structure in Figure \ref{fig:study-stru-Lawson-comment} with our method.}
     \begin{tabular}{cc}
     \toprule
-        Structure & Figure \ref{fig:study-stru-Lawson} with 4 batteries and 15 switches  \\
+        Structure & Figure \ref{fig:study-stru-Lawson-comment} with 4 batteries and 15 switches  \\
     \midrule
@@
   \centering
-    \caption{MAC Calculating result of the RBS structure in Figure \ref{fig:study-stru-Visairo} with our method.}
+    \caption{MAC Calculating result of the RBS structure in Figure \ref{fig:study-stru-Visairo-comment} with our method.}
     \begin{tabular}{cc}
     \toprule
-        Structure & Figure \ref{fig:study-stru-Visairo} with 4 batteries and 13 switches  \\
+        Structure & Figure \ref{fig:study-stru-Visairo-comment} with 4 batteries and 13 switches  \\
     \midrule
@@
   \centering
-    \caption{MAC Calculating result of the RBS structure in Figure \ref{fig:study-stru-my} with our method.}
+    \caption{MAC Calculating result of the RBS structure in Figure \ref{fig:study-stru-my-comment} with our method.}
     \begin{tabular}{cc}
     \toprule
-        Structure & Figure \ref{fig:study-stru-my} with 4 batteries and 19 switches  \\
+        Structure & Figure \ref{fig:study-stru-my-comment} with 4 batteries and 19 switches  \\
     \midrule
@@
   \centering
-    \caption{MAC Calculating result of the RBS structure in Figure \ref{fig:study-stru-Lawson} with brute force method.}
+    \caption{MAC Calculating result of the RBS structure in Figure \ref{fig:study-stru-Lawson-comment} with brute force method.}
     \begin{tabular}{cc}
     \toprule
-        Structure & Figure \ref{fig:study-stru-Lawson} with 4 batteries and 15 switches  \\
+        Structure & Figure \ref{fig:study-stru-Lawson-comment} with 4 batteries and 15 switches  \\
     \midrule
@@
   \centering
-    \caption{MAC Calculating result of the RBS structure in Figure \ref{fig:study-stru-Visairo} with brute force method.}
+    \caption{MAC Calculating result of the RBS structure in Figure \ref{fig:study-stru-Visairo-comment} with brute force method.}
     \begin{tabular}{cc}
     \toprule
-        Structure & Figure \ref{fig:study-stru-Visairo} with 4 batteries and 13 switches  \\
+        Structure & Figure \ref{fig:study-stru-Visairo-comment} with 4 batteries and 13 switches  \\
     \midrule
@@
   \centering
-    \caption{MAC Calculating result of the RBS structure in Figure \ref{fig:study-stru-my} with brute force method.}
+    \caption{MAC Calculating result of the RBS structure in Figure \ref{fig:study-stru-my-comment} with brute force method.}
     \begin{tabular}{cc}
     \toprule
-        Structure & Figure \ref{fig:study-stru-my} with 4 batteries and 19 switches  \\
+        Structure & Figure \ref{fig:study-stru-my-comment} with 4 batteries and 19 switches  \\
     \midrule

### 2023-09-20 paper/SST/2-main.tex
形成最终的提交版本（SST）；将参考文献的引用方式由biber改为bibtex

@@
 % Replace "sample" in the \addbibresource line below with the name of your .bib file.
-\usepackage[style=nejm, 
-citestyle=numeric-comp, 
-sorting=none]{biblatex}
-\addbibresource{ref.bib}
+% \usepackage[style=nejm, 
+% citestyle=numeric-comp, 
+% sorting=none]{biblatex}
+% \addbibresource{ref.bib}
 
@@
 This parameter is instrumental in maintaining the current of each individual battery within a safe range and serves as a guiding indicator for the system's reconfiguration, thereby ensuring its safety and reliability.
+%<*reviewer1-comment1>
 This paper proposes a method to calculate the MAC of arbitrary RBSs using a greedy algorithm in conjunction with a directed graph model of the RBS.
@@
 The main advantage of the proposed method is its ability to calculate the MAC of RBSs with arbitrary structures, even in scenarios with random isolated batteries.
+%</reviewer1-comment1>
 \end{abstract}
@@
 
+%<*reviewer1-comment2>
 Recently, various types of RBSs with different flexibility and reconfigurability have been designed to meet application requirements. 
@@
 
+%<*reviewer1-comment8>
 The complex structure between batteries and switches gives RBSs flexibility but also creates challenges in the design and control of the system. 
@@
 They thoroughly analyzed all paths between the cathode and anode of each battery in the RBS and identified paths that only contain switches as short-circuit paths for pre-checking before system reconfiguration.
+%</reviewer1-comment8>
 
@@
 However, this method is inefficient and time-consuming, especially for RBSs with a large number of switches.
+%</reviewer1-comment2>
 
@@
 An improved direct graph model that considers the voltage, the internal resistance, the MAC of the battery, and the external load is also introduced to analyze the current of the RBS.
+%<*reviewer1-comment3>
 The main contributions of this paper can be summarized as follows:
@@
 \end{itemize}
+%</reviewer1-comment3>
 
@@
 
+%<*reviewer1-comment4>
 The literature contains no report on an algorithm for calculating the MAC of an RBS.
@@
 \end{enumerate}
+%</reviewer1-comment4>
+%<*reviewer1-comment5>
 However, the greedy algorithm proposed in this paper still contains exponential terms in the time complexity, which means it may not be able to handle extremely large RBS structures having large $N_b$.
+%</reviewer1-comment5>
 
@@
 
-% \bibliographystyle{nejm}
-% \bibliography{sst_main}
+\bibliographystyle{unsrt}
+\bibliography{ref}
 
-\printbibliography
+% \begin{thebibliography}{10}
+% 
+% \bibitem{yangBatteryEnergyStorage2018}
+% Yuqing Yang, Stephen Bremner, Chris Menictas, and Merlinde Kay.
+% \newblock Battery energy storage system size determination in renewable energy systems: {{A}} review.
+% \newblock {\em Renewable and Sustainable Energy Reviews}, 91:109--125, August 2018.
+% 
+% \bibitem{desiqueiraControlStrategySmooth2021}
+% Luanna Maria~Silva {de Siqueira} and Wei Peng.
+% \newblock Control strategy to smooth wind power output using battery energy storage system: {{A}} review.
+% \newblock {\em Journal of Energy Storage}, 35:102252, March 2021.
+% 
+% \bibitem{schwanbeckInternationalSpaceStation2019}
+% Eugene Schwanbeck and Penni Dalton.
+% \newblock International {{Space Station Lithium-ion Batteries}} for {{Primary Electric Power System}}.
+% \newblock In {\em 2019 {{European Space Power Conference}} ({{ESPC}})}, pages 1--1. {IEEE}, September 2019.
+% 
+% \bibitem{zhangDevelopmentProspectChinese2021}
+% Lihua Zhang.
+% \newblock Development and {{Prospect}} of {{Chinese Lunar Relay Communication Satellite}}.
+% \newblock {\em Space: Science \& Technology}, 2021, January 2021.
+% 
+% \bibitem{choCommercialResearchBattery2015}
+% Jaephil Cho, Sookyung Jeong, and Youngsik Kim.
+% \newblock Commercial and research battery technologies for electrical energy storage applications.
+% \newblock {\em Progress in Energy and Combustion Science}, 48:84--101, June 2015.
+% 
+% \bibitem{yangUnbalancedDischargingAging2016}
+% Naixing Yang, Xiongwen Zhang, BinBin Shang, and Guojun Li.
+% \newblock Unbalanced discharging and aging due to temperature differences among the cells in a lithium-ion battery pack with parallel combination.
+% \newblock {\em Journal of Power Sources}, 306:733--741, February 2016.
+% 
+% \bibitem{fengPropagationMechanismsDiagnosis2019}
+% Fei Feng, Xiaosong Hu, Lin Hu, Fengling Hu, Yang Li, and Lei Zhang.
+% \newblock Propagation mechanisms and diagnosis of parameter inconsistency within {{Li-Ion}} battery packs.
+% \newblock {\em Renewable and Sustainable Energy Reviews}, 112:102--113, September 2019.
+% 
+% \bibitem{jeevarajanBatterySafetyQualifications2012}
+% J.~A. Jeevarajan and C.~Winchester.
+% \newblock Battery {{Safety Qualifications}} for {{Human Ratings}}.
+% \newblock {\em Interface magazine}, 21(2):51--55, January 2012.
+% 
+% \bibitem{pomboHybridPowerSystem2021}
+% Daniel~V{\'a}zquez Pombo.
+% \newblock A {{Hybrid Power System}} for a {{Permanent Colony}} on {{Mars}}.
+% \newblock {\em Space: Science \& Technology}, 2021, January 2021.
+% 
+% \bibitem{hanNextGenerationBatteryManagement2020a}
+% Weiji Han, Torsten Wik, Anton Kersten, Guangzhong Dong, and Changfu Zou.
+% \newblock Next-{{Generation Battery Management Systems}}: {{Dynamic Reconfiguration}}.
+% \newblock {\em IEEE Industrial Electronics Magazine}, 14(4):20--31, December 2020.
+% 
+% \bibitem{visairoReconfigurableBatteryPack2008}
+% H.~Visairo and P.~Kumar.
+% \newblock A reconfigurable battery pack for improving power conversion efficiency in portable devices.
+% \newblock In {\em 2008 7th {{International Caribbean Conference}} on {{Devices}}, {{Circuits}} and {{Systems}}}, pages 1--6. {IEEE}, April 2008.
+% 
+% \bibitem{ci2007novel}
+% Song Ci, Jiucai Zhang, Hamid Sharif, and Mahmoud Alahmad.
+% \newblock A novel design of adaptive reconfigurable multicell battery for power-aware embedded networked sensing systems.
+% \newblock In {\em IEEE GLOBECOM 2007-IEEE Global Telecommunications Conference}, pages 1043--1047. IEEE, 2007.
+% 
+% \bibitem{9209774}
+% Jan Engelhardt, Tatiana Gabderakhmanova, Gunnar Rohde, and Mattia Marinelli.
+% \newblock Reconfigurable stationary battery with adaptive cell switching for electric vehicle fast-charging.
+% \newblock In {\em 2020 55th International Universities Power Engineering Conference (UPEC)}, pages 1--6, 2020.
+% 
+% \bibitem{engelhardt2021double}
+% Jan Engelhardt, Jan~Martin Zepter, Tatiana Gabderakhmanova, Gunnar Rohde, and Mattia Marinelli.
+% \newblock Double-string battery system with reconfigurable cell topology operated as a fast charging station for electric vehicles.
+% \newblock {\em Energies}, 14(9):2414, 2021.
+% 
+% \bibitem{lawsonSoftwareConfigurableBattery2012}
+% Barrie Lawson.
+% \newblock A {{Software Configurable Battery}}.
+% \newblock {\em EVS26 International Battery, Hybrid and Fuel Cell Electric Vehicle Symposium}, 2012.
+% 
+% \bibitem{he2014reconfiguration}
+% Liang He, Linghe Kong, Siyu Lin, Shaodong Ying, Yu~Gu, Tian He, and Cong Liu.
+% \newblock Reconfiguration-assisted charging in large-scale lithium-ion battery systems.
+% \newblock In {\em 2014 ACM/IEEE International Conference on Cyber-Physical Systems (ICCPS)}, pages 60--71. IEEE, 2014.
+% 
+% \bibitem{kim2009dynamic}
+% Hahnsang Kim and Kang~G Shin.
+% \newblock On dynamic reconfiguration of a large-scale battery system.
+% \newblock In {\em 2009 15th IEEE Real-Time and Embedded Technology and Applications Symposium}, pages 87--96. IEEE, 2009.
+% 
+% \bibitem{han2021analysis}
+% Weiji Han, Anton Kersten, Changfu Zou, Torsten Wik, Xiaoliang Huang, and Guangzhong Dong.
+% \newblock Analysis and estimation of the maximum switch current during battery system reconfiguration.
+% \newblock {\em IEEE Transactions on Industrial Electronics}, 69(6):5931--5941, 2021.
+% 
+% \bibitem{chenSneakCircuitTheory2021}
+% Si-Zhe Chen, Yule Wang, Guidong Zhang, Le~Chang, and Yun Zhang.
+% \newblock Sneak {{Circuit Theory Based Approach}} to {{Avoiding Short-Circuit Paths}} in {{Reconfigurable Battery Systems}}.
+% \newblock {\em IEEE Transactions on Industrial Electronics}, 68(12):12353--12363, 2021.
+% 
+% \bibitem{heExploringAdaptiveReconfiguration2013}
+% Liang He, Lipeng Gu, Linghe Kong, Yu~Gu, Cong Liu, and Tian He.
+% \newblock Exploring {{Adaptive Reconfiguration}} to {{Optimize Energy Efficiency}} in {{Large-Scale Battery Systems}}.
+% \newblock In {\em 2013 {{IEEE}} 34th {{Real-Time Systems Symposium}}}, pages 118--127, December 2013.
+% 
+% \bibitem{hongwenheStateofChargeEstimationLithiumIon2011}
+% Hongwen He, Rui Xiong, Xiaowei Zhang, Fengchun Sun, and JinXin Fan.
+% \newblock State-of-{{Charge Estimation}} of the {{Lithium-Ion Battery Using}} an {{Adaptive Extended Kalman Filter Based}} on an {{Improved Thevenin Model}}.
+% \newblock {\em IEEE Transactions on Vehicular Technology}, 60(4):1461--1469, May 2011.
+% 
+% \bibitem{mousavig.VariousBatteryModels2014}
+% S.M. Mousavi~G. and M.~Nikdel.
+% \newblock Various battery models for various simulation studies and applications.
+% \newblock {\em Renewable and Sustainable Energy Reviews}, 32:477--485, April 2014.
+% 
+% \bibitem{ciNovelDesignAdaptive2007}
+% Song Ci, Jiucai Zhang, Hamid Sharif, and Mahmoud Alahmad.
+% \newblock A {{Novel Design}} of {{Adaptive Reconfigurable Multicell Battery}} for {{Power-Aware Embedded Networked Sensing Systems}}.
+% \newblock In {\em {{IEEE GLOBECOM}} 2007-2007 {{IEEE Global Telecommunications Conference}}}, pages 1043--1047, November 2007.
+% 
+% \bibitem{alahmadBatterySwitchArray2008}
+% Mahmoud Alahmad, Herb Hess, Mohammad Mojarradi, William West, and Jay Whitacre.
+% \newblock Battery switch array system with application for {{JPL}}'s rechargeable micro-scale batteries.
+% \newblock {\em Journal of Power Sources}, 177(2):566--578, March 2008.
+% 
+% \bibitem{kimDependableEfficientScalable2010b}
+% Hahnsang Kim and Kang~G. Shin.
+% \newblock Dependable, efficient, scalable architecture for management of large-scale batteries.
+% \newblock In {\em Proceedings of the 1st {{ACM}}/{{IEEE International Conference}} on {{Cyber-Physical Systems}}}, {{ICCPS}} '10, pages 178--187, {New York, NY, USA}, April 2010.
+{Association for Computing Machinery}.
+% 
+% \bibitem{kimBalancedReconfigurationStorage2011a}
+% Younghyun Kim, Sangyoung Park, Yanzhi Wang, Qing Xie, Naehyuck Chang, Massimo Poncino, and Massoud Pedram.
+% \newblock Balanced reconfiguration of storage banks in a hybrid electrical energy storage system.
+% \newblock In {\em 2011 {{IEEE}}/{{ACM International Conference}} on {{Computer-Aided Design}} ({{ICCAD}})}, pages 624--631, November 2011.
+% 
+% \bibitem{taesickimSeriesconnectedSelfreconfigurableMulticell2012a}
+% Taesic Kim, Wei Qiao, and Liyan Qu.
+% \newblock A series-connected self-reconfigurable multicell battery capable of safe and effective charging/discharging and balancing operations.
+% \newblock In {\em 2012 {{Twenty-Seventh Annual IEEE Applied Power Electronics Conference}} and {{Exposition}} ({{APEC}})}, pages 2259--2264, February 2012.
+% 
+% \bibitem{6843711}
+% Liang He, Linghe Kong, Siyu Lin, Shaodong Ying, Yu~Gu, Tian He, and Cong Liu.
+% \newblock Reconfiguration-assisted charging in large-scale {{Lithium-ion}} battery systems.
+% \newblock In {\em 2014 {{ACM}}/{{IEEE International Conference}} on {{Cyber-Physical Systems}} ({{ICCPS}})}, pages 60--71, April 2014.
+% 
+% \end{thebibliography}
+
+% \printbibliography
 

### 2023-11-05 code/RBSClass.m
添加了 SA、GA 的算法；添加了e2f1、e2f3 的结构

@@ -150,6 +150,7 @@ classdef RBSClass
         end
         function [out_current_ideal, ...
                 isnot_short_circuit, ...
+                isnot_charge_battery, ...
                 Io_ideal,Ib_ideal]=get_current(rbs,x_s)
 
             Us=[0,-rbs.ub*ones(1,rbs.num_b),zeros(1,rbs.num_s)]';
@@ -164,12 +165,14 @@ classdef RBSClass
             Ib=simplify(I(2:rbs.num_b+1));
             Io_ideal=subs(Io,rbs.rs,0);
             Ib_ideal=subs(Ib,rbs.rs,0);
-            % whether battery short circuit
-            isnot_short_circuit=1;
-            for ib_ideal = Ib_ideal
-                if ib_ideal == rbs.ub/rbs.rb
-                    isnot_short_circuit=0;
-                end
+            % whether battery short circuit or has charge
+            isnot_short_circuit=1;            
+            isnot_charge_battery=1;
+            for i = 1:rbs.num_b
+                isnot_short_circuit = isnot_short_circuit ...
+                    *isAlways(Ib_ideal(i)<rbs.ub/rbs.rb);
+                isnot_charge_battery = isnot_charge_battery ...
+                    *isAlways(Ib_ideal(i)>=0);
             end
             % out current
             if my_max(Ib) == 0
@@ -177,34 +180,45 @@ classdef RBSClass
             else
                 out_current=simplify(Io_ideal/my_max(Ib));
             end
-            out_current_ideal=subs(out_current,rbs.rs,0);
+            out_current_ideal=simplify(subs(out_current,rbs.rs,0));
         end
-        function [mac_under_b,xs_mac] = get_mac_under_b(rbs, under_b)
+        function [mac_under_b,xs_mac,num_iter,all_mac] = get_mac_under_b(rbs, under_b)
             % count mac with given numbers(under_b) batteries
+            num_iter = 0;
             all_choose = nchoosek(1:rbs.num_b, under_b);
             all_out_current_ideal = zeros(1,size(all_choose,1));
             all_isnot_short_circuit = ones(1,size(all_choose,1));
+            all_isnot_charge_battery = ones(1,size(all_choose,1));
             for i = 1:size(all_choose,1)
                 choose = all_choose(i,:);
                 x_s = rbs.get_x_s(choose);
                 [all_out_current_ideal(i), ...
                     all_isnot_short_circuit(i), ...
+                    all_isnot_charge_battery(i), ...
[…]

### 2023-11-05 code/RBSClass_e2f1.m

@@ -1,28 +1,28 @@
-classdef RBSClass_e2f2 < RBSClass
+classdef RBSClass_e2f1 < RBSClass
     properties
     end
     methods
-        function rbs = RBSClass_e2f2()
-            rbs = rbs@RBSClass(4);
-            num_b = 4;
+        function rbs = RBSClass_e2f1()
+            rbs = rbs@RBSClass(2);
+            num_b = 2;
             rbs.num_b = num_b;
-            rbs.num_s = 19;
-            rbs.num_n = 18;
+            rbs.num_s = 13;
+            rbs.num_n = 14;
             % node: positon
-            rbs.node_pos_x = [0,2,4,2,1,3,1,3,2,4,2,1,3,1,3,2,4,0];
-            rbs.node_pos_y = [0,0,0,1,2,2,3,3,4,4,5,6,6,7,7,8,8,8];
+            rbs.node_pos_x = [0,1,2,1,1,1,1,2,1,1,1,1,2,0];
+            rbs.node_pos_y = [0,0,0,1,2,3,4,4,5,6,7,8,8,8];
   
             % edge: out
             rbs.s_o = rbs.num_n;
             rbs.t_o = 1;
             rbs.weight_o= 1+num_b*rbs.num_s+rbs.num_s;
             % edge: battery
-            rbs.s_b = [5,6,12,13];
-            rbs.t_b = [7,8,14,15];
+            rbs.s_b = [5,10];
+            rbs.t_b = [6,11];
             rbs.weight_b = rbs.num_s*ones(1,num_b);
             % edge: switch 
-            rbs.s_s = [1,2,2,3,4,4,5,7,8,9,9,10,11,11,12,14,15,16,16];
-            rbs.t_s = [2,3,4,10,5,6,8,9,9,10,11,17,12,13,15,16,16,17,18];
+            rbs.s_s = [1,2,2,3,4,6,7,7,8,9,11,12,12];
+            rbs.t_s = [2,3,4,8,5,7,8,9,13,10,12,13,14];
             rbs.weight_s = ones(1,rbs.num_s);
             % G for graph
             rbs.G_total = rbs.get_G_total();

### 2023-11-05 code/RBSClass_e2f3.m

@@ -1,28 +1,28 @@
-classdef RBSClass_e2f2 < RBSClass
+classdef RBSClass_e2f3 < RBSClass
     properties
     end
     methods
-        function rbs = RBSClass_e2f2()
-            rbs = rbs@RBSClass(4);
-            num_b = 4;
+        function rbs = RBSClass_e2f3()
+            rbs = rbs@RBSClass(6);
+            num_b = 6;
             rbs.num_b = num_b;
-            rbs.num_s = 19;
-            rbs.num_n = 18;
+            rbs.num_s = 25;
+            rbs.num_n = 22;
             % node: positon
-            rbs.node_pos_x = [0,2,4,2,1,3,1,3,2,4,2,1,3,1,3,2,4,0];
-            rbs.node_pos_y = [0,0,0,1,2,2,3,3,4,4,5,6,6,7,7,8,8,8];
+            rbs.node_pos_x = [0,2,4,2,1,2,3,1,2,3,2,4,2,1,2,3,1,2,3,2,4,0];
+            rbs.node_pos_y = [0,0,0,1,2,2,2,3,3,3,4,4,5,6,6,6,7,7,7,8,8,8];
   
             % edge: out
             rbs.s_o = rbs.num_n;
             rbs.t_o = 1;
             rbs.weight_o= 1+num_b*rbs.num_s+rbs.num_s;
             % edge: battery
-            rbs.s_b = [5,6,12,13];
-            rbs.t_b = [7,8,14,15];
+            rbs.s_b = [5,6,7,14,15,16];
+            rbs.t_b = [8,9,10,17,18,19];
             rbs.weight_b = rbs.num_s*ones(1,num_b);
             % edge: switch 
-            rbs.s_s = [1,2,2,3,4,4,5,7,8,9,9,10,11,11,12,14,15,16,16];
-            rbs.t_s = [2,3,4,10,5,6,8,9,9,10,11,17,12,13,15,16,16,17,18];
+            rbs.s_s = [1,2,2,3,4,4,4,5,6,8,9,10,11,11,12,13,13,13,14,15,17,18,19,20,20];
+            rbs.t_s = [2,3,4,12,5,6,7,9,10,11,11,11,12,13,21,14,15,16,18,19,20,20,20,21,22];
             rbs.weight_s = ones(1,rbs.num_s);
             % G for graph
             rbs.G_total = rbs.get_G_total();

### 2023-11-05 code/main.m

@@ -1,78 +1,65 @@
-delete main.out
-diary('main.out');
-%% RBS-f
-for i = [2,4,6]
-    % 创建RBSClass_f对象
-    rbs_f = RBSClass_f(i);
-    % 绘制并保存对象结构
-    path_file = sprintf('.\\attachments\\f-dege-%d.png',i);
-    rbs_f.save_plot(rbs_f.plot_G_dege(),path_file)
-    % 获取MAC和x_s并打印相关信息
-    [mac, x_s] = rbs_f.get_mac();
-    fprintf('MAC of RBS_f(%d): %.2f\n', i, mac)
-    [~,~,Io_ideal,Ib_ideal] = rbs_f.get_current(x_s);
-    fprintf('Io_ideal: %s\n', Io_ideal)
-    for battery=1:i
-        fprintf('Ib_ideal(%d): %s\n',battery, Ib_ideal(battery))
-    end
-    fprintf('those switches are close: ')
-    for j = 1:length(x_s)
-        if (x_s(j)==1)
-            fprintf('%d ',j)
+clear;clc;
+outfile_path = sprintf('.\\main.out');
+delete(outfile_path);
+diary(outfile_path);
+
+struct_list = {'f','e','e2f'};
+num_b_list = [2,4,6];
+method_list = {'Greedy','SA','GA'};
+
+for i = 1:length(struct_list)
+    id = struct_list{i};
+    for j = 1:length(num_b_list)
+        num_b = num_b_list(j);
+        % create RBS
+        if strcmp(id, 'f')
+            rbs = RBSClass_f(num_b);
+            str_id = [id,num2str(num_b)];
+        elseif strcmp(id, 'e')
+            rbs = RBSClass_e(num_b);
+            str_id = [id,num2str(num_b)];
+        elseif strcmp(id, 'e2f') && num_b == 2
+            rbs = RBSClass_e2f1();
+            str_id = 'e2f1';
+        elseif strcmp(id, 'e2f') && num_b == 4
+            rbs = RBSClass_e2f2();
+            str_id = 'e2f2';
+        elseif strcmp(id, 'e2f') && num_b == 6
+            rbs = RBSClass_e2f3();
+            str_id = 'e2f3';
+        else
+            continue
+        end
+        for k = 1:length(method_list)
+            method = method_list{k}; 
+            fprintf('Solve %s by %s\n',str_id, method)
[…]

### 2023-11-05 code/main_par.m

@@ -1,0 +1,68 @@
+clear;clc;
+outfile_path = sprintf('.\\main.out');
+delete(outfile_path);
+diary(outfile_path);
+
+conditions = {'f',2,'Greedy'; 'f',2,'SA'; 'f',2,'GA';
+    'f',4,'Greedy'; 'f',4,'SA'; 'f',4,'GA';
+    'f',6,'Greedy'; 'f',6,'SA'; 'f',6,'GA';
+    'e',2,'Greedy'; 'e',2,'SA'; 'e',2,'GA';
+    'e',4,'Greedy'; 'e',4,'SA'; 'e',4,'GA';
+    'e',6,'Greedy'; 'e',6,'SA'; 'e',6,'GA';
+    'e2f',2,'Greedy'; 'e2f',2,'SA'; 'e2f',2,'GA';
+    'e2f',4,'Greedy'; 'e2f',4,'SA'; 'e2f',4,'GA';
+    'e2f',6,'Greedy'; 'e2f',6,'SA'; 'e2f',6,'GA'};
+
+parfor i = 1:size(conditions,1)
+    id = conditions{i,1};
+    num_b = conditions{i,2};
+    method = conditions{i,3};
+    % create RBS
+    % create RBS
+    if strcmp(id, 'f')
+        rbs = RBSClass_f(num_b);
+        str_id = [id,num2str(num_b)];
+    elseif strcmp(id, 'e')
+        rbs = RBSClass_e(num_b);
+        str_id = [id,num2str(num_b)];
+    elseif strcmp(id, 'e2f') && num_b == 2
+        rbs = RBSClass_e2f1();
+        str_id = 'e2f1';
+    elseif strcmp(id, 'e2f') && num_b == 4
+        rbs = RBSClass_e2f2();
+        str_id = 'e2f2';
+    elseif strcmp(id, 'e2f') && num_b == 6
+        rbs = RBSClass_e2f3();
+        str_id = 'e2f3';
+    else
+        continue
+    end
+    fprintf('Solve %s by %s\n',str_id, method)
+    % solve RBS
+    if strcmp(method, 'Greedy')
+        [mac, x_s, num_iter, all_mac] = rbs.get_mac();
+    elseif strcmp(method, 'SA')
+        [mac, x_s, num_iter, all_mac] = rbs.get_mac_SA();
+    elseif strcmp(method, 'GA')
+        [mac, x_s, num_iter, all_mac] = rbs.get_mac_GA();
+    end
+    % print result
[…]

### 2023-11-06 code/temp.m
添加了三种算法的计算结果

@@ -1,0 +1,2 @@
+rbs23 = RBSClass_e2f3();
+rbs23.plot_G_dege

### 2023-11-06 paper/SST/3-main.tex
新建第三版SST投稿，添加了修改意见(v2.0)
Update RBS research literature review

--- 2023-09-20 paper/SST/2-main.tex
@@
+% =====2-review outline======
+% 1. intro 文献综述部分：重写、补充，引用c8的文献；对RBS性能的分析
+%   1.1 任务分配：如果从电流分配的角度考虑，这是一个 NP-hard 问题，求解这类问题的开销一般很大，通过针对性地改进传统算法来解决计算开销，例如 Mollajafari 提出了 a meta-heuristic method named Graph-Oriented Simulated Annealing (GOSA) )(结合 gammoudiEnergyEfficientSchedulingRealTime2020 这篇可重构任务调度的文章)
+%   1.2 对RBS性能的分析
+%   1.3 多说一点启发式算法
+% 2. case study 增加实验 模拟退火、遗传算法；增加b结构的2，6数量的电池
+%   2.1 structures and details
+%       2.1.1 4-battery 不同结构（3个tab：our method；1个图）
+%       2.1.2 2/4/6-battery 结构b
+%       2.1.3 4-battery 不同结构 isolated battery
+%   2.2 result: 删去table4和前面一段话；添加文字，描述figure7；使用子图子表格
+%       2.1.1 c结构的计算细节：1组fig（有向图、SP、最终结果）
+%       2.1.2 4-battery 不同结构的计算结果：1组tab（各结构计算结果）、2组fig（各结构MAC正确闭合方案+算法迭代过程中的MAC折线图）
+%       2.1.3 2/4/6-battery 结构c（1,2,3 *2）的计算结果：1组tab（各结构计算结果）、2组fig（各结构MAC正确闭合方案+算法迭代过程中的MAC折线图）
+%       2.1.4 4-battery 不同结构 isolated battery 的计算结果：1组fig（不同电池数的开关闭合方案）
+%   2.3 discussion:
+%       2.3.1 结果正确性和准确性：a. 电路分析；b. 与 force-brute 结果的验证
+%       2.3.2 算法的有效性和优劣：a. 复杂度；b. 与 SA、GA 的比较(启发式算法仅找到局部最优；收敛时间)；c. 本算法的优劣和原因
+%       2.3.3 this work 的意义和应用：a. 说明 eta 的意义、应用方法；b. 结合 isolated battery 说明应用场景
+% 3. conclusion 相关内容修改
+% 4. abstract 相关内容修改
+
 \documentclass{article}
@@
 %<*reviewer1-comment2>
-Recently, various types of RBSs with different flexibility and reconfigurability have been designed to meet application requirements. 
+The early research on RBSs focused on the design of the structure with different flexibility and reconfigurability to meet application requirements.
 For example, Ci et al. \cite{ci2007novel} proposed an RBS structure that dynamically adjusts the battery discharge rate to fully exploit the available capacity of each battery. 
@@
 Kim et al. \cite{kim2009dynamic} improved the system's ability to recover from battery failures by introducing multiple ports into the structure. 
-
-%<*reviewer1-comment8>
-The complex structure between batteries and switches gives RBSs flexibility but also creates challenges in the design and control of the system. 
-Thus, several approaches to analyze the RBS structure and performance have been proposed to tackle these challenges.
-For instance, 
-Han et al. \cite{han2021analysis} derived an analytical expression for the maximum switch current during battery system reconfiguration for a specific RBS structure. 
+Those complex structures between batteries and switches give RBSs flexibility but also creates the challenge in the design of the hardware. 
+The variation of current occurs during the system reconfigurating.
+Specifically, when the system connect is swithed from series to parallel, circulating current between parallel cells can be triggered due to their voltage imbalance \cite{hanAnalysisEstimationMaximum2020}.
+It will bring damage to the batteries, switches, and wires if not fully considered during the design of the RBSs.
+For instance, Engelhardt et al.
+\cite{engelhardtDoubleStringBatterySystem2021} applied the RBS to a fast-charging scenario with adaptive cell switching, which can balance cell states while following the voltage request, but the switching of batteries leads to untolerant current variations.
+To solve this problem, Han et al. \cite{han2021analysis} derived an analytical expression for the maximum switch current during battery system reconfiguration. 
 This helps guide the selection of switches and supports the design of RBS hardware.
-Chen et al. \cite{chenSneakCircuitTheory2021} proposed a systematic approach based on  sneak circuit theory to fundamentally avoid the short-circuit problem of RBSs: 
+
+Recently, more attention has been paid to the system state estimation and control of RBSs, and several approaches to optimize the system's performance have been proposed.
+The state estimation, one of the essential technologies of the traditional battery management system, is the premise of the system control, and shows great potential in the RBSs \cite{komsiyskaCriticalReviewIntelligent2021}.
+Couto et al.
+\cite{coutoPartitionbasedUnscentedKalman2018a} proposed a partition-based unscented Kalman filter to estimate the state of a given large-scale RBS, using an enhanced reduced-order electrochemical model.
+Kersten et al.
+\cite{kerstenOnlineOnBoardBattery2020a} used the balancing current of neighboring cells in parallel operation to determine the battery impedances, yielding state of health and power capability.
+Schmid et al.
+\cite{schmidActiveModelBasedFault2021a} further token advantage of the system's reconfigured characteristic to actively diagnose fault, whose algorithm changes the structure of the system in order to improve the fault isolability.
+To develop the effective control strategies of RBSs to achieve the optimal performance, such as better stability \cite{kacetlDesignAnalysisModular2023b} and efficiency \cite{yangAdaptiveControlFramework2022}, is another hot research topic.
+Han et al. \cite{hanNearFastestBatteryBalancing2019a} proposed a near-fastest battery balancing algorithm to minimize the battery charge equalization time.
+Liu et al. \cite{liuFlexiblePathPlanningbased2023a} also proposed a maximum capacity utilization scheme based on a path planning algorithm to improve the battery consistency in the system.
+To break through the bootleneck of the potential short-circuit paths increase exponentially with the RBS's scale, Chen et al.
+\cite{chenSneakCircuitTheory2021} proposed a systematic approach based on sneak circuit theory.
 They thoroughly analyzed all paths between the cathode and anode of each battery in the RBS and identified paths that only contain switches as short-circuit paths for pre-checking before system reconfiguration.
+Furthermore, AI-based management is also used in the system \cite{liuLongLifetimeBattery2022a}.
+The effectiveness of deep reinforcement learning method has been validated on the real-world RBSs \cite{yangAdaptiveControlFramework2022}.
 %</reviewer1-comment8>
 
-In spite of the maximum switch current mentioned above, the maximum allowable current (MAC), defined as the maximum allowed current  under the constraints of the battery cell, is another critical indicator of RBSs that needs to be evaluated during the design or control  of the system.
+The maximum allowable current (MAC), defined as the maximum allowed current under the constraints of the battery cell, is a critical indicator of RBSs that needs to be evaluated during the design and control of the system.
 The MAC helps the designers assess whether the RBS meets the output current requirements and contributes to the formulation of appropriate and safe management strategies for the battery management system.
-Unfortunately, few studies have analyzed the RBS structure to determine the RBS MAC.
+Unfortunately, few studies have been proposed to determine the RBS MAC.
+% scheduling tasks onto dynamically reconfigurable hardware 的方法可以考虑资源有限和任务依存的问题，但是难以处理 RBS 的结构特征和电路方程。
+% 从 RBS 结构分析的角度分析，求解 MAC 的问题转化为在 RBS 的所有可能重构出的结构中寻找最大输出电流。
+% 但是这可能会是一个 NP-hard 问题 pinterReviewControlAlgorithms2021a 
 An intuitive and straightforward method is to enumerate all possible switch states and calculate the output current of the system under each reconfigurated structure.
 However, this method is inefficient and time-consuming, especially for RBSs with a large number of switches.
+% 启发式算法，如SA和GA，也可以用于求解该问题，但是不能完全保证获得最优解，而且收敛时间较长。z
+% 这些方法都不能满足设计和控制时，对 MAC 的快速求解需求。
 %</reviewer1-comment2>

### 2023-11-07 paper/SST/3-main.tex
完成了对 intro 文献综述部分的修改。

@@
 The proposed method is validated on two published four-battery-RBSs and one with a more complex structure.
-The results are the same as those of the brute-force algorithm, but the proposed method significantly improves the computational efficiency ($N_s 2^{N_s - N_b} \log_{10} N_b$ times faster than the brute force algorithm for an RBS with $N_b$ batteries and $N_s$ switches, theoretically).
+The results are the same as those of the brute-force algorithm, but the proposed method significantly improves the computational efficiency ($N_s 2^{N_s - N_b} \log_{10} N_b$ times faster than the brute-force algorithm for an RBS with $N_b$ batteries and $N_s$ switches, theoretically).
 The main advantage of the proposed method is its ability to calculate the MAC of RBSs with arbitrary structures, even in scenarios with random isolated batteries.
@@
 %<*reviewer1-comment2>
-The early research on RBSs focused on the design of the structure with different flexibility and reconfigurability to meet application requirements.
+The early research on RBSs mainly focused on the topological design of the structure with different flexibility and reconfigurability to meet application requirements.
 For example, Ci et al. \cite{ci2007novel} proposed an RBS structure that dynamically adjusts the battery discharge rate to fully exploit the available capacity of each battery. 
-Jan's \cite{9209774,engelhardt2021double} structures  reconfigure structures with variant batteries in series to reach the (constantly changing) voltage requirements during electric vehicle charging.
+Jan's \cite{9209774,engelhardt2021double} structures reconfigure circuits with variant batteries in series to reach the constantly changing voltage requirements during electric vehicle charging.
 As shown in Fig.
@@
 Kim et al. \cite{kim2009dynamic} improved the system's ability to recover from battery failures by introducing multiple ports into the structure. 
-Those complex structures between batteries and switches give RBSs flexibility but also creates the challenge in the design of the hardware. 
-The variation of current occurs during the system reconfigurating.
+Those complex structures between batteries and switches give RBSs flexibility but also create the challenge in the design of the hardware. 
+Current deviation and fluctuation occur when the system is reconfigurating.
 Specifically, when the system connect is swithed from series to parallel, circulating current between parallel cells can be triggered due to their voltage imbalance \cite{hanAnalysisEstimationMaximum2020}.
@@
 \cite{schmidActiveModelBasedFault2021a} further token advantage of the system's reconfigured characteristic to actively diagnose fault, whose algorithm changes the structure of the system in order to improve the fault isolability.
-To develop the effective control strategies of RBSs to achieve the optimal performance, such as better stability \cite{kacetlDesignAnalysisModular2023b} and efficiency \cite{yangAdaptiveControlFramework2022}, is another hot research topic.
+Developing the effective control strategies of RBSs to achieve the optimal performance, such as better stability \cite{kacetlDesignAnalysisModular2023b} and efficiency \cite{yangAdaptiveControlFramework2022}, is another hot research topic.
 Han et al. \cite{hanNearFastestBatteryBalancing2019a} proposed a near-fastest battery balancing algorithm to minimize the battery charge equalization time.
-Liu et al. \cite{liuFlexiblePathPlanningbased2023a} also proposed a maximum capacity utilization scheme based on a path planning algorithm to improve the battery consistency in the system.
+Liu et al. \cite{liuFlexiblePathPlanningbased2023a} also proposed a maximum capacity utilization scheme based on a path planning algorithm to improve the battery consistency within the system.
 To break through the bootleneck of the potential short-circuit paths increase exponentially with the RBS's scale, Chen et al.
@@
 They thoroughly analyzed all paths between the cathode and anode of each battery in the RBS and identified paths that only contain switches as short-circuit paths for pre-checking before system reconfiguration.
-Furthermore, AI-based management is also used in the system \cite{liuLongLifetimeBattery2022a}.
+Furthermore, Artificial Intelligence also appears in the RBS management \cite{liuLongLifetimeBattery2022a}.
 The effectiveness of deep reinforcement learning method has been validated on the real-world RBSs \cite{yangAdaptiveControlFramework2022}.
@@
 The MAC helps the designers assess whether the RBS meets the output current requirements and contributes to the formulation of appropriate and safe management strategies for the battery management system.
-Unfortunately, few studies have been proposed to determine the RBS MAC.
-% scheduling tasks onto dynamically reconfigurable hardware 的方法可以考虑资源有限和任务依存的问题，但是难以处理 RBS 的结构特征和电路方程。
-% 从 RBS 结构分析的角度分析，求解 MAC 的问题转化为在 RBS 的所有可能重构出的结构中寻找最大输出电流。
-% 但是这可能会是一个 NP-hard 问题 pinterReviewControlAlgorithms2021a 
-An intuitive and straightforward method is to enumerate all possible switch states and calculate the output current of the system under each reconfigurated structure.
-However, this method is inefficient and time-consuming, especially for RBSs with a large number of switches.
-% 启发式算法，如SA和GA，也可以用于求解该问题，但是不能完全保证获得最优解，而且收敛时间较长。z
-% 这些方法都不能满足设计和控制时，对 MAC 的快速求解需求。
+Unfortunately, few studies have been proposed to determine the RBS MAC directly, owing to the complexity from reconfiguration. 
+The computer science has the problem of scheduling tasks on dynamically reconfigurable hardware under the condition of limited resources and task interdependencies, similar to the MAC determination, and corresponding solution has been proposed \cite{mollajafariEfficientLightweightAlgorithm2023,heReconfigurationassistedChargingLargescale2014}.
+But it is hard to deal with the RBS's structural characteristics and circuit equations. 
+From the perspective of RBS structure analysis, the MAC problem can be transformed into finding the maximum output current in all possible reconfigurations of the RBS. 
+However, this may be an NP-hard problem \cite{pinterReviewControlAlgorithms2021a}. 
+Common methods, such as brute-force algorithm, simulated annealing (SA) algorithm and genetic algorithm (GA), have the disadvantages of inefficient, time-consuming, and cannot guarantee to obtain the global optimal solution.
 %</reviewer1-comment2>
@@
 In this method, a greedy algorithm is designed to efficiently search the possible circuit topology of RBSs with MAC.
-This algorithm transforms the enumeration of switch states in the brute-force algorithm into the combination of the batteries' shortest paths.
+This algorithm transforms the inefficiently searching reconfigurations into the proactively combining of the shortest paths of batteries.
 An improved direct graph model that considers the voltage, the internal resistance, the MAC of the battery, and the external load is also introduced to analyze the current of the RBS.

### 2023-11-07 paper/SST/3-main.tex
remove review-comment ref in 3-main

@@
 This parameter is instrumental in maintaining the current of each individual battery within a safe range and serves as a guiding indicator for the system's reconfiguration, thereby ensuring its safety and reliability.
-%<*reviewer1-comment1>
 This paper proposes a method to calculate the MAC of arbitrary RBSs using a greedy algorithm in conjunction with a directed graph model of the RBS.
@@
 The main advantage of the proposed method is its ability to calculate the MAC of RBSs with arbitrary structures, even in scenarios with random isolated batteries.
-%</reviewer1-comment1>
 \end{abstract}
@@
 
-%<*reviewer1-comment2>
 The early research on RBSs mainly focused on the topological design of the structure with different flexibility and reconfigurability to meet application requirements.
@@
 The effectiveness of deep reinforcement learning method has been validated on the real-world RBSs \cite{yangAdaptiveControlFramework2022}.
-%</reviewer1-comment8>
 
@@
 Common methods, such as brute-force algorithm, simulated annealing (SA) algorithm and genetic algorithm (GA), have the disadvantages of inefficient, time-consuming, and cannot guarantee to obtain the global optimal solution.
-%</reviewer1-comment2>
 
@@
 An improved direct graph model that considers the voltage, the internal resistance, the MAC of the battery, and the external load is also introduced to analyze the current of the RBS.
-%<*reviewer1-comment3>
 The main contributions of this paper can be summarized as follows:
@@
 \end{itemize}
-%</reviewer1-comment3>
 
@@
 
-%<*reviewer1-comment4>
 The literature contains no report on an algorithm for calculating the MAC of an RBS.
@@
 \end{enumerate}
-%</reviewer1-comment4>
-%<*reviewer1-comment5>
 However, the greedy algorithm proposed in this paper still contains exponential terms in the time complexity, which means it may not be able to handle extremely large RBS structures having large $N_b$.
-%</reviewer1-comment5>
 

### 2023-11-07 paper/SST/3-main.tex
rm Funding in 3-main
规划了图片和表格；finish structures and details

@@
 %       2.1.1 4-battery 不同结构（3个tab：our method；1个图）
-%       2.1.2 2/4/6-battery 结构b
+%       2.1.2 2/4/6-battery 结构c
 %       2.1.3 4-battery 不同结构 isolated battery
+%       2.1.4 四种计算方法
 %   2.2 result: 删去table4和前面一段话；添加文字，描述figure7；使用子图子表格
@@
 %       2.1.3 2/4/6-battery 结构c（1,2,3 *2）的计算结果：1组tab（各结构计算结果）、2组fig（各结构MAC正确闭合方案+算法迭代过程中的MAC折线图）
-%       2.1.4 4-battery 不同结构 isolated battery 的计算结果：1组fig（不同电池数的开关闭合方案）
+%       2.1.4 4-battery c 不同 isolated battery 的计算结果：1组fig（不同电池数的开关闭合方案）
 %   2.3 discussion:
@@
 % 4. abstract 相关内容修改
+
+% ! NOTE
+% 1. red mark -> blue mark
+% 2. check ref
+% 3. rewrite the last two paragraphs of the introduction if time permits
 
@@
 These problems have become significant technical barriers in many engineering projects requiring high reliability, such as developing new-generation space vehicles \cite{pomboHybridPowerSystem2021}.  
-
-Reconfigurable battery systems (RBSs), which can dynamically switch as required to different circuit topologies, are expected to solve this problem \cite{hanNextGenerationBatteryManagement2020a}.
+Reconfigurable battery systems (RBSs), which can dynamically switch as required to different circuit topologies, are expected to solve those problem \cite{hanNextGenerationBatteryManagement2020a}.
+% TODO : rewrite
 The switching circuit helps to isolate unhealthy batteries, thereby improving the safety and reliability of the battery system.
-To illustrate the working principle of an RBS, we consider a typical RBS structure developed by Visairo \cite{visairoReconfigurableBatteryPack2008} (Fig.
+% To illustrate the working principle of an RBS, we consider a typical RBS structure developed by Visairo \cite{visairoReconfigurableBatteryPack2008} (Fig.
 \ref{fig:stru-Visairo}), which is taken as an example to show the reconfiguration process.
-In this structure, the batteries can be connected not only in series when the switches $S_1$, $S_5$, $S_6$, $S_7$, $S_8$, $S_9$, and $S_{13}$ are closed (see Fig.
+% In this structure, the batteries can be connected not only in series when the switches $S_1$, $S_5$, $S_6$, $S_7$, $S_8$, $S_9$, and $S_{13}$ are closed (see Fig.
 \ref{fig:stru-Visairo-serial}) but also in parallel when $S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$, and $S_{13}$ are closed (Fig.
 \ref{fig:stru-Visairo-parallel}).
-Furthermore, when an unhealthy battery, for instance, the orange one $B_3$ in Fig.
+% Furthermore, when an unhealthy battery, for instance, the orange one $B_3$ in Fig.
 \ref{fig:stru-Visairo-isolate}, appears in the RBS, it can be isolated by opening its two adjacent switches (i.e., $S_4$ and $S_{11}$), ensuring that the system remains in a reliable working mode.
-
-\begin{figure}[htbp]
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{stru-V-origin.png}
-        \caption{}
-        \label{fig:stru-Visairo}
-    \end{subfigure}
-    \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{stru-V-serial.png}
-        \caption{}
-        \label{fig:stru-Visairo-serial}
-    \end{subfigure}
-    \\
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{stru-V-parallel.png}
-        \caption{}
-        \label{fig:stru-Visairo-parallel}
-    \end{subfigure}
-    \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{stru-V-isolate.png}
-        \caption{}
-        \label{fig:stru-Visairo-isolate}
-    \end{subfigure}
-    \caption{
-        (a) The RBS structure proposed by Visairo\cite{visairoReconfigurableBatteryPack2008}, with
-        all batteries in (b) series connection, (c) parallel connection, and
-        (d) battery $B_3$ isolated.
-        }
-    \label{fig:arch}
-\end{figure}
+% 
+% \begin{figure}[htbp]
+%     \centering
+%     \begin{subfigure}[b]{0.45\textwidth}
+%         \includegraphics[width=\textwidth]{stru-V-origin.png}
+%         \caption{}
+%         \label{fig:stru-Visairo}
+%     \end{subfigure}
+%     \hspace{0.05\textwidth}
+%     \begin{subfigure}[b]{0.45\textwidth}
+%         \includegraphics[width=\textwidth]{stru-V-serial.png}
+%         \caption{}
+%         \label{fig:stru-Visairo-serial}
+%     \end{subfigure}
+%     \\
+%     \begin{subfigure}[b]{0.45\textwidth}
+%         \includegraphics[width=\textwidth]{stru-V-parallel.png}
+%         \caption{}
+%         \label{fig:stru-Visairo-parallel}
+%     \end{subfigure}
+%     \hspace{0.05\textwidth}
+%     \begin{subfigure}[b]{0.45\textwidth}
+%         \includegraphics[width=\textwidth]{stru-V-isolate.png}
+%         \caption{}
+%         \label{fig:stru-Visairo-isolate}
+%     \end{subfigure}
+%     \caption{
+%         (a) The RBS structure proposed by Visairo\cite{visairoReconfigurableBatteryPack2008}, with
+%         all batteries in (b) series connection, (c) parallel connection, and
+%         (d) battery $B_3$ isolated.
+%         }
+%     \label{fig:arch}
+% \end{figure}
 
@@
 
-\subsection{Structures}
+\subsection{Structures and details}
 
@@
 By integrating the Visairo RBS structure into the Lawson RBS structure, the proposed structure not only has the flexibility to switch the batteries between series, parallel, and mixed series-parallel modes but also allows the isolation of highly degraded batteries from the RBS.
-These four-battery RBS structures are investigated in the case study, including the scenarios with random isolated batteries.
+
+In the case study, these RBS systems are investigated and compared: (a) three different structures (Figs.
+\ref{fig:study-stru-Visairo}-\ref{fig:study-stru-my}) with the same four batteries; (b) the same structure in Figs.
+\ref{fig:study-stru-my} with two/four/six batteries; and (c) the four-battery structure in Figs.
+\ref{fig:study-stru-my} with random isolated batteries.
+The greedy algorithm proposed in this work is also compared with the brute-force algorithm, SA, and GA to validate its effectiveness and efficiency.
+In order to adapt the two heuristic algorithms to the system's structure and scale, the number of the state neighbours of SA and the population size of GA are both set to $N_b \cdot N_s$, which increase with the number of batteries and switches in the system.
+The other algorithms' parameters are set as shown in Tab. \ref{tab:algorithm-parameter}.
+
+\begin{table}[htbp]
+  \centering
+  \caption{Algorithms parameters of SA and GA.}
+    \begin{tabular}{lr}
+    \toprule
+    algorithm/paramter & \multicolumn{1}{l}{value} \\
+    \midrule
+    SA/initial temperature & 100 \\
+    SA/final temperature & 1 \\
+    SA/cooling rate & 0.95 \\
+    GA/total generations & 100 \\
+    GA/crossover probability & 0.8 \\
+    GA/mutation probability & 0.02 \\
+    \bottomrule
+    \end{tabular}
+  \label{tab:algorithm-parameter}
+\end{table}
 
 \subsection{Result}
+
+% SP 结果：三种结构 4battery
+% 重新画图，在实际电路图中表示
+% e4-sp f4-sp e2f2-sp
 
@@
 
+% 4-battery 结构结果，不同算法
+% tab：三种结构greedy的结果细节 3个子表
+% fig：三种结构的闭合方案 3并列子图
+% tab：三种结构不同算法的 eta 计算值 1个tab
+% fig：不同算法的迭代 MAC 值 3并列子图
+
 To verify and compare the results from the greedy algorithm, we also used a brute-force algorithm that iterates through all possible switch states to calculate the MAC of the same three RBSs. 
@@
 \end{table}
+
+% c:2/4/6-battery 结构结果，不同算法
+% fig：两种结构的闭合方案 2并列子图
+% tab：两种结构不同算法的 eta 计算值 1个tab
+% fig：不同算法的迭代 MAC 值 2并列子图
+
+% 4-battery 结构，随机隔离
+% fig：四种情况的闭合方案 4个子图
+% 文字描述 4个图的 eta
 
@@
 
-\subsection*{Funding}
-
-This work was supported by the National Natural Science Foundation of China (NSFC, No.52075028).
+% \subsection*{Funding}
+% 
+% This work was supported by the National Natural Science Foundation of China (NSFC, No.52075028).
 

### 2023-11-08 paper/SST/3-main.tex
完成了对 3-main 图片部分的修改；修改了 case study的 results 部分；修改了 intro 中 RBS 的介绍。

@@
 % \graphicspath{ {./figures/} }
-\graphicspath{ {../figures/} }
+% \graphicspath{ {../figures/} }
+\graphicspath{ {../../attachments} }
 \usepackage{subcaption}
@@
 However, traditional BESSs, in which the batteries are connected in a fixed topology, suffer from a significant weakness in their worst battery due to the so-called cask effect.
-Moreover, if the worst battery fails during operation, it is highly likely to exacerbate the degradation of the other batteries, leading to reliability and safety issues \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019,jeevarajanBatterySafetyQualifications2012}.
+Moreover, if the worst battery fails during operation, it is highly likely to exacerbate the degradation of the other batteries, leading to system-level reliability and safety issues \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019,jeevarajanBatterySafetyQualifications2012}.
 These problems have become significant technical barriers in many engineering projects requiring high reliability, such as developing new-generation space vehicles \cite{pomboHybridPowerSystem2021}.  
 Reconfigurable battery systems (RBSs), which can dynamically switch as required to different circuit topologies, are expected to solve those problem \cite{hanNextGenerationBatteryManagement2020a}.
-% TODO : rewrite
-The switching circuit helps to isolate unhealthy batteries, thereby improving the safety and reliability of the battery system.
-% To illustrate the working principle of an RBS, we consider a typical RBS structure developed by Visairo \cite{visairoReconfigurableBatteryPack2008} (Fig.
-\ref{fig:stru-Visairo}), which is taken as an example to show the reconfiguration process.
-% In this structure, the batteries can be connected not only in series when the switches $S_1$, $S_5$, $S_6$, $S_7$, $S_8$, $S_9$, and $S_{13}$ are closed (see Fig.
-\ref{fig:stru-Visairo-serial}) but also in parallel when $S_1$, $S_2$, $S_3$, $S_4$, $S_5$, $S_9$, $S_{10}$, $S_{11}$, $S_{12}$, and $S_{13}$ are closed (Fig.
-\ref{fig:stru-Visairo-parallel}).
-% Furthermore, when an unhealthy battery, for instance, the orange one $B_3$ in Fig.
-\ref{fig:stru-Visairo-isolate}, appears in the RBS, it can be isolated by opening its two adjacent switches (i.e., $S_4$ and $S_{11}$), ensuring that the system remains in a reliable working mode.
-% 
-% \begin{figure}[htbp]
-%     \centering
-%     \begin{subfigure}[b]{0.45\textwidth}
-%         \includegraphics[width=\textwidth]{stru-V-origin.png}
-%         \caption{}
-%         \label{fig:stru-Visairo}
-%     \end{subfigure}
-%     \hspace{0.05\textwidth}
-%     \begin{subfigure}[b]{0.45\textwidth}
-%         \includegraphics[width=\textwidth]{stru-V-serial.png}
-%         \caption{}
-%         \label{fig:stru-Visairo-serial}
-%     \end{subfigure}
-%     \\
-%     \begin{subfigure}[b]{0.45\textwidth}
-%         \includegraphics[width=\textwidth]{stru-V-parallel.png}
-%         \caption{}
-%         \label{fig:stru-Visairo-parallel}
-%     \end{subfigure}
-%     \hspace{0.05\textwidth}
-%     \begin{subfigure}[b]{0.45\textwidth}
-%         \includegraphics[width=\textwidth]{stru-V-isolate.png}
-%         \caption{}
-%         \label{fig:stru-Visairo-isolate}
-%     \end{subfigure}
-%     \caption{
-%         (a) The RBS structure proposed by Visairo\cite{visairoReconfigurableBatteryPack2008}, with
-%         all batteries in (b) series connection, (c) parallel connection, and
-%         (d) battery $B_3$ isolated.
-%         }
-%     \label{fig:arch}
-% \end{figure}
+In a typical RBS, the extra switches are added between the batteries to form a reconfigurable network, where the circuit's topology can be changed by opening or closing the switches. 
+The unhealthy batteries can be isolated from the system by opening the switches adjacent to them, thereby ensuring that the system remains in a reliable working mode \cite{ci2016reconfigurable}. 
+Furthermore, the RBS can be reconfigured to adapt to different charging and discharging strategies, thereby improving the system's efficiency and extending the battery's life \cite{bouchhima2018lifetime}.
+Those advantages make RBSs a promising alternative to traditional BESSs.
 
@@
 Jan's \cite{9209774,engelhardt2021double} structures reconfigure circuits with variant batteries in series to reach the constantly changing voltage requirements during electric vehicle charging.
-As shown in Fig.
-\ref{fig:stru-Visairo}, the structure proposed by Visairo et al.
+The structure proposed by Visairo et al.
 \cite{visairoReconfigurableBatteryPack2008} changes the system's output voltage based on the load conditions, thereby reducing the power loss of the voltage regulator during the power supply process and improving the efficiency of energy use.
@@
 
-% \begin{figure}[htbp]
-%     \centering
-%     \includegraphics[width=\textwidth]{flowchart.jpg}
-%     \caption{Computational flowchart of MAC for a given RBS.}\label{fig:flowchart}
-% \end{figure}
-
 \section{Case Study}
@@
 
-% SP 结果：三种结构 4battery
-% 重新画图，在实际电路图中表示
-% e4-sp f4-sp e2f2-sp
-
-As shown in Fig. \ref{fig:study-stru-my}, the new RBS structure consists of four batteries and 19 switches. 
-Figure \ref{fig:study-dirgraph-my} shows the corresponding directed graph, which is composed of 18 nodes and 43 edges. 
-Batteries $B_1$, $B_2$, $B_3$, and $B_4$ are denoted by green directed edges in the graph, and the 19 switches are represented by gray directed edges with bidirectional arrows. 
-The external electrical load is treated as a directed edge from the cathode of the RBS (i.e., node 18) to the anode (i.e., node 1), as indicated by the blue directed edge in the graph.
+\subsubsection{the shortest path}
+
 Using Eq.
-(\ref{eq:weight}) and the Dijkstra algorithm, the SPs of the four batteries in the RBS structure of Fig.
-\ref{fig:study-stru-my} are highlighted in red in Figs.
-\ref{fig:sp1} and \ref{fig:sp4}.
-Finally, the calculated MACs of the structure in Fig.
-\ref{fig:study-stru-my} are listed in Tab.
-\ref{tab:study-results-my} and shown in Fig.
-\ref{fig:study-results-my}, as obtained by the greedy algorithm \ref{alg:greedy}.
-Tab.
-\ref{tab:study-results-my} contains the states of the switches, the output current $I_o$, the battery current $\bm{I}_b$, and the ratio $\eta$ of the RBS structure with all batteries in good health when the RBS output reaches the MAC.
-Fig. \ref{fig:study-results-my} presents the corresponding circuit, with the red highlight indicating that the current is flowing through the respective branches.
+(\ref{eq:weight}) and the Dijkstra algorithm, the SPs of the four batteries in the RBS structures of Figs.
+\ref{fig:study-stru-Lawson}, \ref{fig:study-stru-Visairo}, and \ref{fig:study-stru-my} are calculated and highlighted with difference colors in Figs.
+\ref{fig:e4-sp}, \ref{fig:f4-sp}, and \ref{fig:e2f2-sp}, respectively.
 
@@
     \centering
-    \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{ef-topo.png}
-        \caption{}
-        \label{fig:study-dirgraph-my}
-    \end{subfigure}
-    \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{ef-sp1.png}
-        \caption{}
-        \label{fig:sp1}
-    \end{subfigure}
-    \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{ef-sp2.png}
-        \caption{}
-        \label{fig:sp2}
-    \end{subfigure}
-    \\
-    \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{ef-sp3.png}
-        \caption{}
-        \label{fig:sp3}
-    \end{subfigure}
-    \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{ef-sp4.png}
-        \caption{}
-        \label{fig:sp4}
-    \end{subfigure}
-    \hspace{0.05\textwidth}
-    \begin{subfigure}[b]{0.28\textwidth}
-        \includegraphics[width=\textwidth]{ef-mac.png}
-        \caption{}
-        \label{fig:study-results-my}
-    \end{subfigure}
-    \caption{
-        For the RBS structure in Fig. \ref{fig:study-stru-my}, 
-        (a) its directed graph 
-        and the SPs (highlighted in red) of battery (b) $B_1$, (c) $B_2$, (d) $B_3$, and (e) $B_4$.
-        (f) Circuit of RBS with its output reaching the MAC.
-        }
-    \label{fig:all-results-my}
+    \begin{subfigure}[b]{0.2\textwidth}
+        \includegraphics[width=\textwidth]{e4-sp.png}
+        \caption{}
+        \label{fig:e4-sp}
+    \end{subfigure}
+    \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.4\textwidth}
+        \includegraphics[width=\textwidth]{f4-sp.png}
+        \caption{}
+        \label{fig:f4-sp}
+    \end{subfigure}
+    \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.31\textwidth}
+        \includegraphics[width=\textwidth]{e2f2-sp.png}
+        \caption{}
+        \label{fig:e2f2-sp}
+    \end{subfigure}
+    \caption{The SPs of the four batteries in the RBS structures of (a) Fig. \ref{fig:study-stru-Lawson}, (b) Fig. \ref{fig:study-stru-Visairo}, and (c) Fig. \ref{fig:study-stru-my}.}
 \end{figure}
+
+\subsubsection{three structures with four batteries}
+
+After obtaining the SPs, the MACs of the three RBS structures with four batteries are calculated using the proposed greedy algorithm, and the results are shown in Tabs.
+\ref{tab:study-results-Lawson}, \ref{tab:study-results-Visairo}, and \ref{tab:study-results-my}, each of which contains the states of the switches, the output current $I_o$, the battery current $\bm{I}_b$, and the ratio $\eta$ when the system output reaches the MAC.
+The correspond switch-control schemes are shown as blue-highlighted electric current in Figs. \ref{fig:e4-mac}, \ref{fig:f4-mac}, and \ref{fig:e2f2-mac}, respectively.
+To verify and compare the proposed greedy algorithm, we also used the brute-force algorithm, which iterates through all possible switch states, and heuristic algorithms (SA and GA) to calculate the MAC of the same three RBSs.
+The final results of the brute-force algorithm are the same as the ones of the greedy algorithm, which are shown in Tabs.
+\ref{tab:study-results-Lawson}, \ref{tab:study-results-Visairo}, and \ref{tab:study-results-my}.
+But, the brute-force algorithm counts all possible switch states, which equates to $2^{15}$, $2^{13}$, and $2^{19}$ structures, respectively.
+The two heuristic algorithms' temporal variation of the objective values during the iteration process are shown in Figs.
+\ref{fig:e4-alg}, \ref{fig:f4-alg}, and \ref{fig:e2f2-alg}, respectively, compared with the greedy algorithm.
+
+\begin{table}[htbp]
+  \centering
+    \caption{MAC Calculating result of the four-battery RBS structure in Fig. \ref{fig:study-stru-Lawson}.}
+    \begin{tabular}{cc}
+    \toprule
+        Structure & Figure \ref{fig:study-stru-Lawson} with 4 batteries and 15 switches  \\
+    \midrule
+    Switch ON & $S_1$,$S_3$,$S_5$,$S_7$,$S_{10}$,$S_{13}$,$S_{14}$,$S_{15}$ \\
+    $I_o$ & $u_b/(R_o+r_b)$ \\
+    $\bm{I}_b$ & $[u_b/(R_o+r_b),0,0,0]$ \\
+    $\max \eta$     & 1 \\
+    \bottomrule
+    \end{tabular}
+  \label{tab:study-results-Lawson}
+\end{table}
+
+\begin{table}[htbp]
+  \centering
+    \caption{MAC Calculating result of the four-battery RBS structure in Fig. \ref{fig:study-stru-Visairo}.}
+    \begin{tabular}{cc}
+    \toprule
+        Structure & Figure \ref{fig:study-stru-Visairo} with 4 batteries and 13 switches  \\
+    \midrule
+    Switch ON & $S_1$,$S_2$,$S_3$,$S_4$,$S_5$,$S_9$,$S_{10}$,$S_{11}$,$S_{12}$,$S_{13}$ \\
+    $I_o$ & $4u_b/(4R_o+r_b)$ \\
+    $\bm{I}_b$ & $[u_b/(4R_o+r_b),u_b/(4R_o+r_b),u_b/(4R_o+r_b),u_b/(4R_o+r_b)]$ \\
+    $\max \eta$     & 4 \\
+    \bottomrule
+    \end{tabular}
+  \label{tab:study-results-Visairo}
+\end{table}
 
@@
 
-Similarly, the results of the MAC calculation for the structures in Figs.
-\ref{fig:study-stru-Lawson} and \ref{fig:study-stru-Visairo} are listed in Tabs.
-\ref{tab:study-results-Lawson} and  \ref{tab:study-results-Visairo}, respectively.
-
-% 4-battery 结构结果，不同算法
-% tab：三种结构greedy的结果细节 3个子表
-% fig：三种结构的闭合方案 3并列子图
-% tab：三种结构不同算法的 eta 计算值 1个tab
-% fig：不同算法的迭代 MAC 值 3并列子图
-
-To verify and compare the results from the greedy algorithm, we also used a brute-force algorithm that iterates through all possible switch states to calculate the MAC of the same three RBSs. 
-The final results are the same as the results shown in Tabs. \ref{tab:study-results-my}--\ref{tab:study-results-Visairo}.
-The method uses the greedy algorithm to calculate 11, 11, and 1 reconfigured structures for the RBS structure in Figs.
-\ref{fig:study-stru-my}, \ref{fig:study-stru-Lawson}, and \ref{fig:study-stru-Visairo}, respectively.
-For the same RBS, the method counts all possible switch states, which equates to $2^{19}$, $2^{15}$, and $2^{13}$ structures, respectively.
-
-\begin{table}[htbp]
-  \centering
-    \caption{MAC Calculating result of the four-battery RBS structure in Fig. \ref{fig:study-stru-Lawson}.}
-    \begin{tabular}{cc}
-    \toprule
-        Structure & Figure \ref{fig:study-stru-Lawson} with 4 batteries and 15 switches  \\
-    \midrule
-    Switch ON & $S_1$,$S_3$,$S_5$,$S_7$,$S_{10}$,$S_{13}$,$S_{14}$,$S_{15}$ \\
-    $I_o$ & $u_b/(R_o+r_b)$ \\
-    $\bm{I}_b$ & $[u_b/(R_o+r_b),0,0,0]$ \\
-    $\max \eta$     & 1 \\
-    \bottomrule
-    \end{tabular}
-  \label{tab:study-results-Lawson}
-\end{table}
-
-\begin{table}[htbp]
-  \centering
-    \caption{MAC Calculating result of the four-battery RBS structure in Fig. \ref{fig:study-stru-Visairo}.}
-    \begin{tabular}{cc}
-    \toprule
-        Structure & Figure \ref{fig:study-stru-Visairo} with 4 batteries and 13 switches  \\
-    \midrule
-    Switch ON & $S_1$,$S_2$,$S_3$,$S_4$,$S_5$,$S_9$,$S_{10}$,$S_{11}$,$S_{12}$,$S_{13}$ \\
-    $I_o$ & $4u_b/(4R_o+r_b)$ \\
-    $\bm{I}_b$ & $[u_b/(4R_o+r_b),u_b/(4R_o+r_b),u_b/(4R_o+r_b),u_b/(4R_o+r_b)]$ \\
-    $\max \eta$     & 4 \\
-    \bottomrule
-    \end{tabular}
-  \label{tab:study-results-Visairo}
-\end{table}
-
-% c:2/4/6-battery 结构结果，不同算法
-% fig：两种结构的闭合方案 2并列子图
-% tab：两种结构不同算法的 eta 计算值 1个tab
-% fig：不同算法的迭代 MAC 值 2并列子图
-
-% 4-battery 结构，随机隔离
-% fig：四种情况的闭合方案 4个子图
-% 文字描述 4个图的 eta
-
-Furthermore, the RBS with isolated batteries is taken into consideration and calculated. 
-The MAC calculation results for the three structures under study, with varying numbers of isolated batteries, are presented in Tab. \ref{tab:isolated_mac}. 
-Figs.
-\ref{fig:my-isolated-1}--\ref{fig:my-isolated-3} illustrate the corresponding switch-control schemes for the new structure proposed in this paper under different conditions of isolated batteries.
-
-\begin{table}[htbp]
-    \centering
-    \caption{
-      Variation of MAC with the number of isolated batteries for different RBS structures, including the structure proposed by Lawson et al., Visairo et al., and the structure proposed in this paper.
-      }
-      \label{tab:isolated_mac}
-      \begin{tabular}{cccc}
-      \toprule
-      \multirow{2}[4]{*}{Number of isolated batteries} & \multicolumn{3}{c}{$\eta$ of RBS structure} \\
-  \cmidrule{2-4}          & This paper  & Visairo  & Lawson  \\
-      \midrule
-      0     & 2     & 4     & 1 \\
-      1     & 2     & 3     & 1 \\
-      2     & 2$^{\mathrm{a}}$ or 1$^{\mathrm{b}}$ & 2     & 1 \\
-      3     & 1     & 1     & 1 \\
-      \bottomrule
-      \end{tabular}
-      \\
-      \footnotesize{$^{\mathrm{a}}$ Isolate two batteries within the same substructure, as shown in Fig. \ref{fig:my-isolated-2b}.}\\
-      \footnotesize{$^{\mathrm{b}}$ Isolate one battery in each of the two substructures, as shown in Fig. \ref{fig:my-isolated-2w}.}
-  \end{table}
-
 \begin{figure}[htbp]
     \centering
+    \begin{subfigure}[b]{0.2\textwidth}
+        \includegraphics[width=\textwidth]{e4-mac.png}
+        \caption{}
+        \label{fig:e4-mac}
+    \end{subfigure}
+    \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.4\textwidth}
+        \includegraphics[width=\textwidth]{f4-mac.png}
+        \caption{}
+        \label{fig:f4-mac}
+    \end{subfigure}
+    \hspace{0.02\textwidth}
     \begin{subfigure}[b]{0.31\textwidth}
-          \includegraphics[width=\textwidth]{my-isolated-1.png}
+        \includegraphics[width=\textwidth]{e2f2-mac.png}
+        \caption{}
+        \label{fig:e2f2-mac}
+    \end{subfigure}
+    \caption{The RBSs' switch-control schemes with the output reaching the MAC.}
+\end{figure}
+
+\begin{figure}[htbp]
+    \centering
+    \begin{subfigure}[b]{0.32\textwidth}
+        \includegraphics[width=\textwidth]{e4-alg.png}
+        \caption{}
+        \label{fig:e4-alg}
+    \end{subfigure}
+    % \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \includegraphics[width=\textwidth]{f4-alg}
+        \caption{}
+        \label{fig:f4-alg}
+    \end{subfigure}
+    % \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \includegraphics[width=\textwidth]{e2f2-alg}
+        \caption{}
+        \label{fig:e2f2-alg}
+    \end{subfigure}
+    \caption{The temporal variation of the objective values during the iteration process of calculating the RBS structures in (a) Fig.
+\ref{fig:study-stru-Lawson}, (b) Fig.
+\ref{fig:study-stru-Visairo}, and (c) Fig.
+\ref{fig:study-stru-my}}
+\end{figure}
+
+\subsubsection{structures with different numbers of batteries}
+
+We next consider the RBS structure in Fig. \ref{fig:study-stru-my} with two, four, and six batteries.
+The result of four-battery structure has been shown in Tab. \ref{tab:study-results-my}, Fig. \ref{fig:e2f2-mac}, and Fig. \ref{fig:e2f2-alg}. 
+The structures and final switch-control schemes of the others are shown in Figs. \ref{fig:e2f1-mac} and \ref{fig:e2f3-mac}, respectively. 
+And the temporal variation of the objective values during the iteration process are shown in Figs. \ref{fig:e2f1-alg} and \ref{fig:e2f3-alg}, respectively.
+
+\begin{figure}[htbp]
+    \centering
+    \begin{subfigure}[b]{0.27\textwidth}
+        \includegraphics[width=\textwidth]{e2f1-mac.png}
+        \caption{}
+        \label{fig:e2f1-mac}
+    \end{subfigure}
+    \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.31\textwidth}
+        \includegraphics[width=\textwidth]{e2f3-mac.png}
+        \caption{}
+        \label{fig:e2f3-mac}
+    \end{subfigure}
+    \caption{The (a) two-battery and (b) six-battery RBSs' switch-control schemes with the output reaching the MAC.}
+\end{figure}
+
+\begin{figure}[htbp]
+    \centering
+    \begin{subfigure}[b]{0.34\textwidth}
+        \includegraphics[width=\textwidth]{e2f1-alg.png}
+        \caption{}
+        \label{fig:e2f1-alg}
+    \end{subfigure}
+    \hspace{0.02\textwidth}
+    \begin{subfigure}[b]{0.33\textwidth}
+        \includegraphics[width=\textwidth]{e2f3-alg.png}
+        \caption{}
+        \label{fig:e2f3-alg}
+    \end{subfigure}
+    \caption{The temporal variation of the objective values during the iteration process of calculating the RBS structures in (a) Fig. \ref{fig:e2f1-mac} and (b) Fig. \ref{fig:e2f3-mac}.}
+\end{figure}
+
+\subsubsection{random isolated batteries}
+
+To validate the proposed algorithm's effectiveness in the scenario of unhealthy batteries, the RBS with isolated batteries is also taken into consideration and calculated. 
+For the four-battery RBS structure shown in Fig.
+\ref{fig:study-stru-my}, there are four possible cases of isolated batteries: (a) only one unhealthy battery, (b) two unhealthy batteries which are separated in the two subsections, (c) two batteries located in the same subsection, and (d) three batteries.
+The final calculated MAC($\eta$)s of these four cases are 2, 2, 1, and 1, respectively.
+And the corresponding switch-control schemes of these four cases are shown in Figs. \ref{fig:my-isolated-1}--\ref{fig:my-isolated-3}.
+
+\begin{figure}[htbp]
+    \centering
+    \begin{subfigure}[b]{0.31\textwidth}
+        \includegraphics[width=\textwidth]{e2f2-isolate-1.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.31\textwidth}
-          \includegraphics[width=\textwidth]{my-isolated-2b.png}
+        \includegraphics[width=\textwidth]{e2f2-isolate-2b.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.31\textwidth}
-          \includegraphics[width=\textwidth]{my-isolated-2w.png}
+        \includegraphics[width=\textwidth]{e2f2-isolate-2w.png}
         \caption{}
@@
     \begin{subfigure}[b]{0.31\textwidth}
-          \includegraphics[width=\textwidth]{my-isolated-3.png}
+        \includegraphics[width=\textwidth]{e2f2-isolate-3.png}
         \caption{}
@@
     \caption{
-          Circuit states of MACs when isolating (a) one, (b) two (best case), (c) two (worst case), and (d) three batteries for the structure in Fig. \ref{fig:study-stru-my}.
+        Circuit states of MACs when isolating (a) one, (b) two (in different substructures), (c) two (in the same substructure), and (d) three batteries for the structure in Fig.
+\ref{fig:study-stru-my}.
         }

### 2023-11-09 paper/SST/3-main.tex
修改了 case study 部分；增加了学术润色的 prompt

@@
 Schmid et al.
-\cite{schmidActiveModelBasedFault2021a} further token advantage of the system's reconfigured characteristic to actively diagnose fault, whose algorithm changes the structure of the system in order to improve the fault isolability.
+\cite{schmidActiveModelBasedFault2021a} further taken advantage of the system's reconfigured characteristic to actively diagnose fault, whose algorithm changes the structure of the system in order to improve the fault isolability.
 Developing the effective control strategies of RBSs to achieve the optimal performance, such as better stability \cite{kacetlDesignAnalysisModular2023b} and efficiency \cite{yangAdaptiveControlFramework2022}, is another hot research topic.
@@
 In the case study, these RBS systems are investigated and compared: (a) three different structures (Figs.
-\ref{fig:study-stru-Visairo}-\ref{fig:study-stru-my}) with the same four batteries; (b) the same structure in Figs.
+\ref{fig:study-stru-Lawson}--\ref{fig:study-stru-my}) with the same four batteries; (b) the same structure in Figs.
 \ref{fig:study-stru-my} with two/four/six batteries; and (c) the four-battery structure in Figs.
@@
 In order to adapt the two heuristic algorithms to the system's structure and scale, the number of the state neighbours of SA and the population size of GA are both set to $N_b \cdot N_s$, which increase with the number of batteries and switches in the system.
-The other algorithms' parameters are set as shown in Tab. \ref{tab:algorithm-parameter}.
+The other algorithms' parameters are shown in Tab. \ref{tab:algorithm-parameter}.
 
@@
     \toprule
-    algorithm/paramter & \multicolumn{1}{l}{value} \\
+    Algorithm/paramter & \multicolumn{1}{l}{Value} \\
     \midrule
@@
 The correspond switch-control schemes are shown as blue-highlighted electric current in Figs. \ref{fig:e4-mac}, \ref{fig:f4-mac}, and \ref{fig:e2f2-mac}, respectively.
-To verify and compare the proposed greedy algorithm, we also used the brute-force algorithm, which iterates through all possible switch states, and heuristic algorithms (SA and GA) to calculate the MAC of the same three RBSs.
+To verify and compare the proposed greedy algorithm, we also used the brute-force algorithm, which iterates through all possible switch states, and the heuristic algorithms (SA and GA) to calculate the MAC of the same RBSs.
 The final results of the brute-force algorithm are the same as the ones of the greedy algorithm, which are shown in Tabs.
@@
 But, the brute-force algorithm counts all possible switch states, which equates to $2^{15}$, $2^{13}$, and $2^{19}$ structures, respectively.
-The two heuristic algorithms' temporal variation of the objective values during the iteration process are shown in Figs.
-\ref{fig:e4-alg}, \ref{fig:f4-alg}, and \ref{fig:e2f2-alg}, respectively, compared with the greedy algorithm.
+The two heuristic algorithms' temporal evaluation of the objective values during the iteration process are shown in Figs.
+\ref{fig:e4-alg}, \ref{fig:f4-alg}, and \ref{fig:e2f2-alg}, respectively, compared with the proposed greedy algorithm.
 
@@
     \end{subfigure}
-    \caption{The temporal variation of the objective values during the iteration process of calculating the RBS structures in (a) Fig.
+    \caption{The temporal evolution of the objective values during the iteration process of calculating the RBS structures in (a) Fig.
 \ref{fig:study-stru-Lawson}, (b) Fig.
@@
 We next consider the RBS structure in Fig. \ref{fig:study-stru-my} with two, four, and six batteries.
-The result of four-battery structure has been shown in Tab. \ref{tab:study-results-my}, Fig. \ref{fig:e2f2-mac}, and Fig. \ref{fig:e2f2-alg}. 
-The structures and final switch-control schemes of the others are shown in Figs. \ref{fig:e2f1-mac} and \ref{fig:e2f3-mac}, respectively. 
-And the temporal variation of the objective values during the iteration process are shown in Figs. \ref{fig:e2f1-alg} and \ref{fig:e2f3-alg}, respectively.
+The result of four-battery structure has been shown in Tab. \ref{tab:study-results-my}, Figs. \ref{fig:e2f2-mac}, and \ref{fig:e2f2-alg}. 
+The structures and final switch-control schemes of the remaining two-battery and six-battery systems are illustrated in Figs. \ref{fig:e2f1-mac} and \ref{fig:e2f3-mac}, respectively. 
+And the temporal evolution of the objective values throughout the iteration process are shown in Figs. \ref{fig:e2f1-alg} and \ref{fig:e2f3-alg}, respectively.
 
@@
 
-To validate the proposed algorithm's effectiveness in the scenario of unhealthy batteries, the RBS with isolated batteries is also taken into consideration and calculated. 
-For the four-battery RBS structure shown in Fig.
-\ref{fig:study-stru-my}, there are four possible cases of isolated batteries: (a) only one unhealthy battery, (b) two unhealthy batteries which are separated in the two subsections, (c) two batteries located in the same subsection, and (d) three batteries.
-The final calculated MAC($\eta$)s of these four cases are 2, 2, 1, and 1, respectively.
-And the corresponding switch-control schemes of these four cases are shown in Figs. \ref{fig:my-isolated-1}--\ref{fig:my-isolated-3}.
+To assess the effectiveness of the proposed algorithm in the scenario of unhealthy batteries, the RBS with random isolated batteries is also taken into account and computed. 
+In the case of the four-battery RBS structure depicted in Fig.
+\ref{fig:study-stru-my}, there are four possible scenarios of isolated batteries: (a) only one unhealthy battery, (b) two unhealthy batteries that are separated in the two substructure, (c) two batteries located in the same substructure, and (d) three batteries.
+The resulting MAC ($\eta$) values for these four scenarios are 2, 2, 1, and 1, respectively.
+Furthermore, the corresponding switch-control schemes for these four scenarios are illustrated in Figs \ref{fig:my-isolated-1}--\ref{fig:my-isolated-3}.
 
@@
 
-Consider first the results shown in Fig. \ref{fig:study-results-my} and listed in Tab. \ref{tab:study-results-my}.
-When $B_1$ and $B_2$ or $B_3$ and $B_4$ are connected in parallel, the RBS outputs the maximum current, which is $\eta=2$ (i.e., twice the current output of a single battery in the RBS). 
-Adding more batteries to the main circuit only forms a series structure and does not improve the MAC. 
-Therefore, the state of the switches given in Tab. \ref{tab:study-results-my} maximizes the RBS output current.
-The brute-force method, which go through all possible switch states, also gives the same result.
-
-The literature contains no report on an algorithm for calculating the MAC of an RBS.
-The brute-force algorithm, which goes through all possible switch states, is the most straightforward way to determine the MAC and is used as a benchmark for the proposed greedy algorithm.
+\subsubsection{correctness of the results}
+
+The correctness of the outcomes provided by the proposed greedy algorithm will be discussed from two perspectives: circuit analysis and validation against the brute-force algorithm. 
+Let's take the four-battery RBS structure shown in Fig. \ref{fig:study-stru-my} as an example.
+When $B_1$ and $B_2$ or $B_3$ and $B_4$ are connected in parallel, the RBS produces the maximum current, which is $\eta=2$ (i.e., twice the current output of a single battery in the RBS). 
+Adding more batteries to the main circuit only creates a series structure and does not improve the MAC. 
+Therefore, the switch-control scheme provided in Tab. \ref{tab:study-results-my} maximizes the RBS output current.
+On the other hand, the brute-force method, which examines all possible switch states, also yields the same $\eta$.
+This indicates that the proposed greedy algorithm successfully identifies the MAC among all the potential reconfigured structures.
+
+\subsubsection{advantages and disadvantages of our method}
+
+The proposed greedy algorithm possesses a significant advantage in terms of its effectiveness and efficiency. 
+In this paper, it is compared with the brute-force algorithm, SA, and GA. 
+While the brute-force algorithm ensures the correctness of the results by exploring all possible switch states, it comes at a high computational cost. 
+The SA and GA are commonly used heuristic algorithms for addressing NP-hard problems. 
+They selectively generate solutions for the switching states to maximize the objective value $\eta$.
+However, neither of these two algorithms can determine whether the current $\eta$ represents the final MAC or if they should continue searching for better solutions. 
+Moreover, as depicted in Figs.
+\ref{fig:e4-alg}--\ref{fig:e2f2-alg} and Figs.
+\ref{fig:e2f1-alg}--\ref{fig:e2f3-alg}, the SA and GA algorithms require more iterations to converge to the final solution compared to the proposed greedy algorithm.
+In contrast, the proposed greedy algorithm can identify the correct MAC in a shorter number of steps.
+
+To further elaborate on the efficiency of our algorithm, we analyze the time complexity of both the brute-force algorithm and the greedy algorithm.
 If an RBS has $N_b$ batteries and $N_s$ switches and the corresponding directed graph has $N$ nodes,  $2^{N_s}$ iterations are required to traverse all reconfigured structures.
@@
 \end{enumerate}
-However, the greedy algorithm proposed in this paper still contains exponential terms in the time complexity, which means it may not be able to handle extremely large RBS structures having large $N_b$.
+
+Furthermore, this approach has the capability to handle RBSs with arbitrary structures, which is another significant advantage of it. 
+It is able to correctly calculate the MACs of RBSs with arbitrary structures, even when they have different variant batteries, or even random isolated batteries. 
+These results have been validate in the previous subsection.
+
+However, the suggested greedy algorithm still includes exponential terms in its time complexity, indicating that it struggles to perform at scale. 
+Additionally, all batteries are assumed to be identical for the sake of simplification in the derivation.
+However, there may exist a small balancing current, which could introduce a minor bias to the MAC, due to variations in open-circuit voltage $u_b$ and internal resistance $r_b$ in reality.
+Nevertheless, the proposed greedy algorithm remains a viable choice for the RBS design and optimization in the early stage, and the issue of balancing current bias can be addressed by considering the variations in batteries and replacing the internal resistance with impedance when constructing the directed graph model.
+
+\subsubsection{application scenarios}
 
 Note that $\eta$ is used as the objective function instead of $I_o$ in solving for the MAC. 
-This choice makes the resulting MAC more reasonable. 
+This choice makes the resulting MAC more reasonable and applicable in practical scenarios. 
 As shown in Tab. \ref{tab:study-results-my}, $I_o$ and $\bm{I}_b$ are functions of $R_o$, $u_b$, and $r_b$. 
@@
 This would increase the difficulty and uncertainty of designing the RBS structure. 
-To eliminate this problem, the ratio $\eta=I_o/\max\bm{I}_b$ is adopted as the objective function in our research.
+To eliminate this problem, the ratio $\eta=I_o/\max(\bm{I}_b)$ is adopted as the objective function in our research.
 Recall that $\eta$ reflects only the structure's ability to output current, rather than the actual current outputing by the battery system.
@@
 The method proposed in this paper facilitates the design of RBSs in the following ways:
-Most currently proposed RBS structures \cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} have simple topological characteristics, so calculating the MACs is relatively straightforward, even intuitive.
+most currently proposed RBS structures \cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} have simple topological characteristics, so calculating the MACs is relatively straightforward, even intuitive.
 However, these simple structures do not always fully satisfy the requirements of complex applications, such as dynamically adapting the circuit to variable and random operating conditions or actively equalizing differences between batteries in the RBS.
@@
 
-To illustrate this point, the MACs of three RBS structures mentioned above are calculated after isolating one or more of the batteries, as shown in Tab. \ref{tab:isolated_mac}. 
-Specifically, for the structure presented in Fig.
-\ref{fig:study-stru-my}, the corresponding circuit states for the MACs when isolating one to three batteries are depicted in Figs.
+To illustrate this point, the MACs of the RBS structure in Fig.
+\ref{fig:study-stru-my} are calculated after isolating one or more of the batteries, as shown in Figs.
 \ref{fig:my-isolated-1}--\ref{fig:my-isolated-3}.
-This structure has two cases in which two batteries are isolated: 
-one is to isolate two batteries within the same substructure (Fig.
-\ref{fig:my-isolated-2b}), in which case $\eta=2$; the other is to isolate one battery in each of the two substructures (Fig.
-\ref{fig:my-isolated-2w}), in which case $\eta=1$.
-The results in Figs. \ref{fig:my-isolated-1}--\ref{fig:my-isolated-3} show that the proposed method provides reasonable outcomes for isolating any number of batteries in any position.
-Furthermore, the output current for the three RBSs with isolated batteries is also shown in Tab. \ref{tab:isolated_mac}. 
-For the structure proposed by Lawson et al., the MAC is independent of the number of isolated batteries.
-However, for Visairo's structure, the MAC decreases upon increasing the number of isolated batteries. 
-Nevertheless, the MAC of the structure proposed in this work falls between the MACs of these two structures. 
-This result indicates that the structure proposed in this paper has a larger MAC than Lawson's for the same number of batteries and has a wider range of regulation of the output current.
+When a single battery is isolated, the RBS is still capable of outputting the maximum current, denoted as $\eta=2$.
+When two batteries are isolated, there are two scenarios: 
+one is isolating two batteries within the same substructure (Figure \ref{fig:my-isolated-2b}), resulting in $\eta=2$; the other is isolating one battery in each of the two substructures (Figure \ref{fig:my-isolated-2w}), resulting in $\eta=1$.
+If three batteries are isolated, the RBS can only output the current of a single battery, which is $\eta=1$.
+Therefore, the battery management system can adjust the output current and control the RBS to reconfigure the corresponding structure based on the isolated batteries.
 

### 2023-11-09 paper/SST/3-main.tex
完成了对 3-main 的全文润色（methodology 部分除外）

@@
 % ! NOTE
+% [DONE]
 % 1. red mark -> blue mark
@@
 This paper proposes a method to calculate the MAC of arbitrary RBSs using a greedy algorithm in conjunction with a directed graph model of the RBS.
-By introducing the shortest path of the battery, the greedy algorithm transforms the enumeration of switch states in the brute-force algorithm into the combination of the shortest paths, which greatly increases the efficiency with which the MAC is determined.
+By introducing the shortest path (SP) of the battery, the greedy algorithm transforms the enumeration of switch states in the brute-force algorithm or variable search without utilizing structures in the heuristic algorithms (simulated annealing and genetic algorithm) into the combination of the shortest paths.
+This significantly enhances the efficiency with which the MAC is determined.
 The directed graph model, based on the equivalent circuit, provides a specific method for calculating the MAC of a given structure.
-The proposed method is validated on two published four-battery-RBSs and one with a more complex structure.
+The proposed method is validated on two published RBS structures and one with a more complex structure.
 The results are the same as those of the brute-force algorithm, but the proposed method significantly improves the computational efficiency ($N_s 2^{N_s - N_b} \log_{10} N_b$ times faster than the brute-force algorithm for an RBS with $N_b$ batteries and $N_s$ switches, theoretically).
-The main advantage of the proposed method is its ability to calculate the MAC of RBSs with arbitrary structures, even in scenarios with random isolated batteries.
+Another advantage of the proposed method is its ability to calculate the MAC of RBSs with arbitrary structures and variable battries, even in scenarios with random isolated batteries.
 \end{abstract}
 
-%%%%%% Main Text %%%%%%
-
 \section{Introduction}
 
-Battery energy storage systems (BESSs) are extensively used in various applications \cite{yangBatteryEnergyStorage2018}, such as wind power plants \cite{desiqueiraControlStrategySmooth2021} and space power systems \cite{schwanbeckInternationalSpaceStation2019,zhangDevelopmentProspectChinese2021}, to store and release high-quality electrical energy \cite{choCommercialResearchBattery2015}.
-Typically, a BESS consists of numerous batteries interconnected by series-parallel circuitry to provide the required capacity storage.
-However, traditional BESSs, in which the batteries are connected in a fixed topology, suffer from a significant weakness in their worst battery due to the so-called cask effect.
-Moreover, if the worst battery fails during operation, it is highly likely to exacerbate the degradation of the other batteries, leading to system-level reliability and safety issues \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019,jeevarajanBatterySafetyQualifications2012}.
-These problems have become significant technical barriers in many engineering projects requiring high reliability, such as developing new-generation space vehicles \cite{pomboHybridPowerSystem2021}.  
-Reconfigurable battery systems (RBSs), which can dynamically switch as required to different circuit topologies, are expected to solve those problem \cite{hanNextGenerationBatteryManagement2020a}.
-In a typical RBS, the extra switches are added between the batteries to form a reconfigurable network, where the circuit's topology can be changed by opening or closing the switches. 
-The unhealthy batteries can be isolated from the system by opening the switches adjacent to them, thereby ensuring that the system remains in a reliable working mode \cite{ci2016reconfigurable}. 
-Furthermore, the RBS can be reconfigured to adapt to different charging and discharging strategies, thereby improving the system's efficiency and extending the battery's life \cite{bouchhima2018lifetime}.
-Those advantages make RBSs a promising alternative to traditional BESSs.
-
-The early research on RBSs mainly focused on the topological design of the structure with different flexibility and reconfigurability to meet application requirements.
+Battery energy storage systems (BESSs) are widely utilized in various applications \cite{yangBatteryEnergyStorage2018}, such as wind power plants \cite{desiqueiraControlStrategySmooth2021} and space power systems \cite{schwanbeckInternationalSpaceStation2019,zhangDevelopmentProspectChinese2021}, for the purpose of storing and releasing high-quality electrical energy \cite{choCommercialResearchBattery2015}.
+Typically, a BESS consists of numerous batteries interconnected by series-parallel circuitry to provide the required storage capacity.
+However, conventional BESSs, in which the batteries are connected in a fixed topology, suffer from a significant weakness in their worst battery due to the so-called cask effect.
+Furthermore, if the worst battery fails during operation, it is highly likely to accelerate the degradation of the other batteries, resulting in reliability and safety issues at the system level \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019,jeevarajanBatterySafetyQualifications2012}.
+These challenges have become major technical obstacles in many engineering projects that demand high reliability, such as the development of next-generation space vehicles \cite{pomboHybridPowerSystem2021}.
+Reconfigurable battery systems (RBSs), which can dynamically switch between different circuit topologies as needed, are expected to address these issues \cite{hanNextGenerationBatteryManagement2020a}.
+In a typical RBS, additional switches are introduced between the batteries to form a reconfigurable network, where the circuit's topology can be altered by opening or closing the switches.
+By opening the switches adjacent to the unhealthy batteries, they can be isolated from the system, ensuring that the system remains in a reliable operational state \cite{ci2016reconfigurable}.
+Furthermore, the RBS can be reconfigured to adapt to different charging and discharging strategies, thereby enhancing the system's efficiency and prolonging the battery's lifespan \cite{bouchhima2018lifetime}.
+These advantages make RBSs a promising alternative to traditional BESSs.
+
+The early research on RBSs mainly focused on the topological design of the structure, incorporating different levels of flexibility and reconfigurability to meet application requirements.
 For example, Ci et al. \cite{ci2007novel} proposed an RBS structure that dynamically adjusts the battery discharge rate to fully exploit the available capacity of each battery. 
-Jan's \cite{9209774,engelhardt2021double} structures reconfigure circuits with variant batteries in series to reach the constantly changing voltage requirements during electric vehicle charging.
+Jan's \cite{9209774,engelhardt2021double} structures reconfigure circuits with variant batteries in series to accommodate the constantly changing voltage requirements during electric vehicle charging.
 The structure proposed by Visairo et al.
-\cite{visairoReconfigurableBatteryPack2008} changes the system's output voltage based on the load conditions, thereby reducing the power loss of the voltage regulator during the power supply process and improving the efficiency of energy use.
+\cite{visairoReconfigurableBatteryPack2008} alters the system's output voltage based on the load conditions, thereby reducing power loss in the voltage regulator during the power supply process and enhancing energy efficiency.
 Also, to enhance the energy efficiency of the system, Lawson et al.
@@
 Kim et al. \cite{kim2009dynamic} improved the system's ability to recover from battery failures by introducing multiple ports into the structure. 
-Those complex structures between batteries and switches give RBSs flexibility but also create the challenge in the design of the hardware. 
-Current deviation and fluctuation occur when the system is reconfigurating.
-Specifically, when the system connect is swithed from series to parallel, circulating current between parallel cells can be triggered due to their voltage imbalance \cite{hanAnalysisEstimationMaximum2020}.
-It will bring damage to the batteries, switches, and wires if not fully considered during the design of the RBSs.
-For instance, Engelhardt et al.
-\cite{engelhardtDoubleStringBatterySystem2021} applied the RBS to a fast-charging scenario with adaptive cell switching, which can balance cell states while following the voltage request, but the switching of batteries leads to untolerant current variations.
-To solve this problem, Han et al. \cite{han2021analysis} derived an analytical expression for the maximum switch current during battery system reconfiguration. 
-This helps guide the selection of switches and supports the design of RBS hardware.
-
-Recently, more attention has been paid to the system state estimation and control of RBSs, and several approaches to optimize the system's performance have been proposed.
-The state estimation, one of the essential technologies of the traditional battery management system, is the premise of the system control, and shows great potential in the RBSs \cite{komsiyskaCriticalReviewIntelligent2021}.
+However, these complex structures between batteries and switches provide flexibility to RBSs while also posing challenges in hardware design. 
+During the reconfiguration process, current deviation and fluctuation may occur.
+Specifically, when the system switches from series to parallel connection, circulating current between parallel cells can be triggered due to voltage imbalance \cite{hanAnalysisEstimationMaximum2020}.
+Failure to fully consider this issue during the design of RBSs can result in damage to the batteries, switches, and wires.
+For example, Engelhardt et al.
+\cite{engelhardtDoubleStringBatterySystem2021} applied RBS to a fast-charging scenario with adaptive cell switching, which can balance cell states while adhering to voltage requests.
+However, the switching of batteries leads to intolerable current variations.
+To address this problem, Han et al.
+\cite{han2021analysis} derived an analytical expression for the maximum switch current during battery system reconfiguration.
+This analytical expression aids in the selection of switches and supports the hardware design of RBSs.
+
+Recently, there has been increasing attention given to the estimation and control of the system state of RBSs, and several approaches have been proposed to optimize the performance of the system. 
+State estimation, which is an essential technology in traditional battery management systems, serves as the foundation for system control and holds great potential in the context of RBSs \cite{komsiyskaCriticalReviewIntelligent2021}.
 Couto et al.
-\cite{coutoPartitionbasedUnscentedKalman2018a} proposed a partition-based unscented Kalman filter to estimate the state of a given large-scale RBS, using an enhanced reduced-order electrochemical model.
+\cite{coutoPartitionbasedUnscentedKalman2018a} introduced a partition-based unscented Kalman filter to estimate the state of a large-scale RBS, utilizing an enhanced reduced-order electrochemical model.
 Kersten et al.
-\cite{kerstenOnlineOnBoardBattery2020a} used the balancing current of neighboring cells in parallel operation to determine the battery impedances, yielding state of health and power capability.
+\cite{kerstenOnlineOnBoardBattery2020a} utilized the balancing current of neighboring cells in parallel operation to determine battery impedances, thereby obtaining information about the state of health and power capability.
 Schmid et al.
-\cite{schmidActiveModelBasedFault2021a} further taken advantage of the system's reconfigured characteristic to actively diagnose fault, whose algorithm changes the structure of the system in order to improve the fault isolability.
-Developing the effective control strategies of RBSs to achieve the optimal performance, such as better stability \cite{kacetlDesignAnalysisModular2023b} and efficiency \cite{yangAdaptiveControlFramework2022}, is another hot research topic.
-Han et al. \cite{hanNearFastestBatteryBalancing2019a} proposed a near-fastest battery balancing algorithm to minimize the battery charge equalization time.
-Liu et al. \cite{liuFlexiblePathPlanningbased2023a} also proposed a maximum capacity utilization scheme based on a path planning algorithm to improve the battery consistency within the system.
+\cite{schmidActiveModelBasedFault2021a} further leveraged the reconfigurable nature of the system to actively diagnose faults, employing an algorithm that changes the system structure to enhance fault isolability.
+Another active research topic is the development of effective control strategies for RBSs to achieve optimal performance, including improved stability \cite{kacetlDesignAnalysisModular2023b} and efficiency \cite{yangAdaptiveControlFramework2022}.
+Han et al. \cite{hanNearFastestBatteryBalancing2019a} proposed a near-fastest battery balancing algorithm to minimize the time required for battery charge equalization.
+Liu et al.
+\cite{liuFlexiblePathPlanningbased2023a} also proposed a scheme for maximizing capacity utilization based on a path planning algorithm, aiming to enhance battery consistency within the system.
 To break through the bootleneck of the potential short-circuit paths increase exponentially with the RBS's scale, Chen et al.
 \cite{chenSneakCircuitTheory2021} proposed a systematic approach based on sneak circuit theory.
-They thoroughly analyzed all paths between the cathode and anode of each battery in the RBS and identified paths that only contain switches as short-circuit paths for pre-checking before system reconfiguration.
+They conducted a comprehensive analysis of all paths between the cathode and anode of each battery in the RBS, identifying paths that only consist of switches as short-circuit paths for pre-checking before system reconfiguration.
 Furthermore, Artificial Intelligence also appears in the RBS management \cite{liuLongLifetimeBattery2022a}.
-The effectiveness of deep reinforcement learning method has been validated on the real-world RBSs \cite{yangAdaptiveControlFramework2022}.
-
-The maximum allowable current (MAC), defined as the maximum allowed current under the constraints of the battery cell, is a critical indicator of RBSs that needs to be evaluated during the design and control of the system.
-The MAC helps the designers assess whether the RBS meets the output current requirements and contributes to the formulation of appropriate and safe management strategies for the battery management system.
-Unfortunately, few studies have been proposed to determine the RBS MAC directly, owing to the complexity from reconfiguration. 
-The computer science has the problem of scheduling tasks on dynamically reconfigurable hardware under the condition of limited resources and task interdependencies, similar to the MAC determination, and corresponding solution has been proposed \cite{mollajafariEfficientLightweightAlgorithm2023,heReconfigurationassistedChargingLargescale2014}.
-But it is hard to deal with the RBS's structural characteristics and circuit equations. 
-From the perspective of RBS structure analysis, the MAC problem can be transformed into finding the maximum output current in all possible reconfigurations of the RBS. 
+The effectiveness of deep reinforcement learning method has been validated in real-world RBSs \cite{yangAdaptiveControlFramework2022}.
+
+The maximum allowable current (MAC), which is defined as the maximum current allowed within the constraints of the battery cell, is a crucial indicator of RBSs that needs to be evaluated during the design and control of the system.
+The MAC assists designers in assessing whether the RBS meets the requirements for output current and contributes to the development of appropriate and safe management strategies for the battery management system.
+Unfortunately, there have been few studies proposed to directly determine the MAC of RBSs, primarily due to the complexity arising from reconfiguration. 
+In the field of computer science, there is a similar problem of scheduling tasks on dynamically reconfigurable hardware with limited resources and task interdependencies, which is analogous to the determination of MAC.
+A corresponding method has been proposed \cite{mollajafariEfficientLightweightAlgorithm2023,heReconfigurationassistedChargingLargescale2014}. 
+However, dealing with the structural characteristics and circuit equations of RBSs is challenging for this method.  
+From the perspective of RBS structure analysis, the MAC problem can be transformed into finding the maximum output current among all possible reconfigurations of the RBS. 
 However, this may be an NP-hard problem \cite{pinterReviewControlAlgorithms2021a}. 
-Common methods, such as brute-force algorithm, simulated annealing (SA) algorithm and genetic algorithm (GA), have the disadvantages of inefficient, time-consuming, and cannot guarantee to obtain the global optimal solution.
+Common methods such as brute-force algorithms, simulated annealing (SA) algorithms, and genetic algorithms (GA) have the drawbacks of inefficiency, time consumption, and inability to guarantee the globally optimal solution.
 
@@
 This algorithm transforms the inefficiently searching reconfigurations into the proactively combining of the shortest paths of batteries.
-An improved direct graph model that considers the voltage, the internal resistance, the MAC of the battery, and the external load is also introduced to analyze the current of the RBS.
-The main contributions of this paper can be summarized as follows:
+Furthermore, an improved directed graph model is introduced to analyze the current of the RBS, taking into account factors such as voltage, internal resistance, MAC of the battery, and external load. 
+The main contributions of this study can be summarized as follows:
 \begin{itemize}
@@
 Section II presents the framework and details of the proposed directed graph model and greedy algorithm. 
-Section III discusses a case study that uses the proposed method to determine the MACs of two published four-battery RBSs and one with a more complex structure. 
-The calculation results, the algorithm's computational complexity, and scenarios such as battery random isolation are also discussed. 
+Section III examines a case study that applies the proposed method to determine the MACs of two published RBS structures and one with a more complex structure. 
+The calculation results, the computational complexity of the algorithm, and scenarios such as battery random isolation are also discussed. 
 Finally, the concluding remarks are presented in Section IV.
@@
 Based on currently proposed RBS structures \cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the number $N_b$ of batteries, $N_s$ of switches, and $N$ of nodes are quantitatively related as follows: $N_s \approx (3\text{--} 5)N_b$, $N \approx N_s$.
-After simplifying, the time complexity of the method with greedy algorithm is $O(2^{N_b}N_s^2\log_{10} N_b)$, while it is $O(2^{N_s}N_s^3)$ for the method with brute force algorithm.
+After simplifying, the time complexity of the method with greedy algorithm is $O(2^{N_b}N_s^2\log_{10} N_b)$, while it is $O(2^{N_s}N_s^3)$ for the method with brute-force algorithm.
 Therefore, as the RBS grows, especially in the number of switches, the greedy algorithm gains an advantage over the brute-force algorithm.
@@
 It is able to correctly calculate the MACs of RBSs with arbitrary structures, even when they have different variant batteries, or even random isolated batteries. 
-These results have been validate in the previous subsection.
+Theoretically, each RBS structure can be transformed into the unique directed graph model using the methodology described in the Section II, and the MAC can subsequently be calculated using the proposed greedy algorithm.
+This finding has been supported in the previous subsection.
 
@@
 The method is implemented by a greedy algorithm combined with an improved directed graph model.
-Not only does the method provides the same global MAC calculation results as the brute force method, but it also improves the calculation efficiency by 3\,000 to 48\,000 times for three RBS structures in the case study.
-Theoretically, for an RBS with $N_s$ switches and $N_b$ batteries, the efficiency of the proposed method is $N_s 2^{N_s - N_b} \log_{10} N_b$ times that of the brute-force method, which is mainly because of using the batteries' SPs to guide the RBS to reconfigure reasonable structures rather than blindly going through all possible structures.
-The main advantage of this method is its ability to calculate the MAC of RBSs with arbitrary structures.
+Not only does the method provides the same global MAC calculation results as the brute-force method, but it also demonstrates superior computational efficiency compared to both the brute-force algorithm and the heuristic algorithms (SA and GA).
+Theoretically, for an RBS with $N_s$ switches and $N_b$ batteries, the efficiency of the proposed method is $N_s 2^{N_s - N_b} \log_{10} N_b$ times that of the brute-force method. 
+This is primarily due to the utilization of the batteries' SPs to guide the RBS to reconfigure reasonable structures rather than blindly going through all possible structures.
+Another advantage of this method is its capability to calculate the MAC of RBSs with arbitrary structures and variant batteries. 
 Even in scenarios with random isolated batteries, the proposed method remains effective.
-This method helps to fully tap the current output potential of the RBS, guide the RBS structure design and optimization in the design stage, and assist in evaluating the current-overload risk of the system in practical applications.
+This method facilitates the full utilization of the RBS's current output potential, guides the design and optimization of the RBS structure during the design stage, and assists in evaluating the risk of current overload in practical applications.
 

### 2023-11-09 paper/SST/3-main.tex
Update graphics path and remove isolated_mac.png.
modify results in case study

@@
 % \graphicspath{ {./figures/} }
-% \graphicspath{ {../figures/} }
-\graphicspath{ {../../attachments} }
+\graphicspath{ {../figures/} }
+% \graphicspath{ {../../attachments} }
 \usepackage{subcaption}
@@
 \ref{fig:e4-alg}, \ref{fig:f4-alg}, and \ref{fig:e2f2-alg}, respectively, compared with the proposed greedy algorithm.
+Comparing to the SA and GA, the proposed greedy algorithm solves the correct results with fewer iteration steps.
 
@@
 
-We next consider the RBS structure in Fig. \ref{fig:study-stru-my} with two, four, and six batteries.
-The result of four-battery structure has been shown in Tab. \ref{tab:study-results-my}, Figs. \ref{fig:e2f2-mac}, and \ref{fig:e2f2-alg}. 
-The structures and final switch-control schemes of the remaining two-battery and six-battery systems are illustrated in Figs. \ref{fig:e2f1-mac} and \ref{fig:e2f3-mac}, respectively. 
-And the temporal evolution of the objective values throughout the iteration process are shown in Figs. \ref{fig:e2f1-alg} and \ref{fig:e2f3-alg}, respectively.
+We next examine the RBS configuration depicted in Fig. \ref{fig:study-stru-my}, which consists of two, four, and six batteries.
+The results for the four-battery configuration are presented in Tab. \ref{tab:study-results-my}, Figs. \ref{fig:e2f2-mac}, and \ref{fig:e2f2-alg}.
+The structures and final switch-control schemes for the two-battery and six-battery systems are illustrated in Figs. \ref{fig:e2f1-mac} and \ref{fig:e2f3-mac}, respectively.
+Furthermore, the temporal evolutions of the objective values throughout the iteration process are shown in Figs. \ref{fig:e2f1-alg} and \ref{fig:e2f3-alg}, respectively.
+The proposed greedy algorithm is still the one that converges the fastest and achieves the correct MAC. 
+And the SA algorithm fails to obstain the correct MAC within the given iteration steps in the case of six-battery RBS structure.
 

### 2023-11-09 paper/SST/3-main.tex
fix grammatical and spelling errors

@@
 The results are the same as those of the brute-force algorithm, but the proposed method significantly improves the computational efficiency ($N_s 2^{N_s - N_b} \log_{10} N_b$ times faster than the brute-force algorithm for an RBS with $N_b$ batteries and $N_s$ switches, theoretically).
-Another advantage of the proposed method is its ability to calculate the MAC of RBSs with arbitrary structures and variable battries, even in scenarios with random isolated batteries.
+Another advantage of the proposed method is its ability to calculate the MAC of RBSs with arbitrary structures and variable batteries, even in scenarios with random isolated batteries.
 \end{abstract}
@@
 Kersten et al.
-\cite{kerstenOnlineOnBoardBattery2020a} utilized the balancing current of neighboring cells in parallel operation to determine battery impedances, thereby obtaining information about the state of health and power capability.
+\cite{kerstenOnlineOnBoardBattery2020a} utilized the balancing current of neighboring cells in parallel operation to determine battery impedance, thereby obtaining information about the state of health and power capability.
 Schmid et al.
@@
 \cite{liuFlexiblePathPlanningbased2023a} also proposed a scheme for maximizing capacity utilization based on a path planning algorithm, aiming to enhance battery consistency within the system.
-To break through the bootleneck of the potential short-circuit paths increase exponentially with the RBS's scale, Chen et al.
+To break through the bottleneck of the potential short-circuit paths increase exponentially with the RBS's scale, Chen et al.
 \cite{chenSneakCircuitTheory2021} proposed a systematic approach based on sneak circuit theory.
@@
 To address this issue, we improve our previous model by adding electromotive force and resistance attributes on the edges based on its equivalent circuits.
-The model also considers the external load as an equivalent resistance and integrates it into the analysis, making it a complete circuit model for later circuit analyses.
+The model also considers the external load as an equivalent resistance and integrates it into the analysis, making it a complete circuit model for later circuit analyzes.
 Fig. \ref{fig:direct-graph-my} shows the improved directed graph model used in this paper.
@@
 Thus, for the submatrix $\bm{A}_s$, only one column is retained for each pair of columns representing the same switch.
-As a result, $\bm{A}$ can be reduced to an $(N-1)\times(N_b+N_s+1)$ matrix, denoted  $\bm{\tilde{A}}$, for further calculation of current and voltage.
+As a result, $\bm{A}$ can be reduced to a $(N-1)\times(N_b+N_s+1)$ matrix, denoted $\bm{\tilde{A}}$, for further calculation of current and voltage.
 Similar to Eq. (\ref{eq:A_bso}), $\bm{\tilde{A}}$ can be rewritten as
@@
 \end{equation}
-Finally the problem of finding the MAC can be formulated as
+Finally, the problem of finding the MAC can be formulated as
 \begin{align}
@@
 where $N_s$ is the total number of switches in the system, 
-and $n_b(p)$ and $n_s(p)$ are number of batteries and switches in path $p$, respectively. 
+and $n_b(p)$ and $n_s(p)$ are the number of batteries and switches in path $p$, respectively. 
 Moreover, the shortest path $SP_i$ is defined as the path with the minimum $\omega$ for battery $B_i$:
@@
 $v_i^- \rightarrow v_i^+$ is the directed edge corresponding to battery $B_i$.
-With the Dijkstra algorithm, shortest paths for $v_1 \rightarrow v_i^-$ and $v_i^+ \rightarrow v_N$ can be calculated under the weights given in Eq.
+With the Dijkstra algorithm, the shortest paths for $v_1 \rightarrow v_i^-$ and $v_i^+ \rightarrow v_N$ can be calculated under the weights given in Eq.
 (\ref{eq:weight}) and denoted $SP(v_i^- \rightarrow v_i^+)$ and $SP(v_i^+ \rightarrow v_N)$, respectively.
@@
 
-The algorithm (see pseudo-code in Algorithm 1) is illustrated in Fig. \ref{fig:flowchart} and is summarized as follows:
+The algorithm (see pseudocode in Algorithm 1) is illustrated in Fig. \ref{fig:flowchart} and is summarized as follows:
 First, the SPs are obtained by using Eqs. (\ref{eq:weight}) and (\ref{eq:def_sp}) in conjunction with the Dijkstra search. 
@@
 The greedy algorithm proposed in this work is also compared with the brute-force algorithm, SA, and GA to validate its effectiveness and efficiency.
-In order to adapt the two heuristic algorithms to the system's structure and scale, the number of the state neighbours of SA and the population size of GA are both set to $N_b \cdot N_s$, which increase with the number of batteries and switches in the system.
+In order to adapt the two heuristic algorithms to the system's structure and scale, the number of the state neighbors of SA and the population size of GA are both set to $N_b \cdot N_s$, which increase with the number of batteries and switches in the system.
 The other algorithms' parameters are shown in Tab. \ref{tab:algorithm-parameter}.
@@
     \toprule
-    Algorithm/paramter & \multicolumn{1}{l}{Value} \\
+    Algorithm/parameter & \multicolumn{1}{l}{Value} \\
     \midrule
@@
 
-\subsubsection{the shortest path}
+\subsubsection{The shortest path}
 
@@
 
-\subsubsection{three structures with four batteries}
+\subsubsection{Three structures with four batteries}
 
@@
 \ref{tab:study-results-Lawson}, \ref{tab:study-results-Visairo}, and \ref{tab:study-results-my}, each of which contains the states of the switches, the output current $I_o$, the battery current $\bm{I}_b$, and the ratio $\eta$ when the system output reaches the MAC.
-The correspond switch-control schemes are shown as blue-highlighted electric current in Figs. \ref{fig:e4-mac}, \ref{fig:f4-mac}, and \ref{fig:e2f2-mac}, respectively.
+The corresponding switch-control schemes are shown as blue-highlighted electric current in Figs. \ref{fig:e4-mac}, \ref{fig:f4-mac}, and \ref{fig:e2f2-mac}, respectively.
 To verify and compare the proposed greedy algorithm, we also used the brute-force algorithm, which iterates through all possible switch states, and the heuristic algorithms (SA and GA) to calculate the MAC of the same RBSs.
@@
 
-\subsubsection{structures with different numbers of batteries}
+\subsubsection{Structures with different numbers of batteries}
 
@@
 The proposed greedy algorithm is still the one that converges the fastest and achieves the correct MAC. 
-And the SA algorithm fails to obstain the correct MAC within the given iteration steps in the case of six-battery RBS structure.
+And the SA algorithm fails to obtain the correct MAC within the given iteration steps in the case of six-battery RBS structure.
 
@@
 
-\subsubsection{random isolated batteries}
+\subsubsection{Random isolated batteries}
 
@@
 
-\subsubsection{correctness of the results}
+\subsubsection{Correctness of the results}
 
@@
 
-\subsubsection{advantages and disadvantages of our method}
+\subsubsection{Advantages and disadvantages of our method}
 
@@
 
-\subsubsection{application scenarios}
+\subsubsection{Application scenarios}
 
@@
 To eliminate this problem, the ratio $\eta=I_o/\max(\bm{I}_b)$ is adopted as the objective function in our research.
-Recall that $\eta$ reflects only the structure's ability to output current, rather than the actual current outputing by the battery system.
+Recall that $\eta$ reflects only the structure's ability to output current, rather than the actual current outputting by the battery system.
 Assuming that the MAC of batteries in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by determining the value of $\eta$ for the structure.
@@
 The method is implemented by a greedy algorithm combined with an improved directed graph model.
-Not only does the method provides the same global MAC calculation results as the brute-force method, but it also demonstrates superior computational efficiency compared to both the brute-force algorithm and the heuristic algorithms (SA and GA).
+Not only does the method provide the same global MAC calculation results as the brute-force method, but it also demonstrates superior computational efficiency compared to both the brute-force algorithm and the heuristic algorithms (SA and GA).
 Theoretically, for an RBS with $N_s$ switches and $N_b$ batteries, the efficiency of the proposed method is $N_s 2^{N_s - N_b} \log_{10} N_b$ times that of the brute-force method. 
@@
     }
-    get $\bm{A}$ by Eq. \ref{eq:A}\;
+    Get $\bm{A}$ by Eq. \ref{eq:A}\;
     \While{not yet determine $\max \eta$ }
     {
-        $N_{\text{set}} \leftarrow$ number of setected SPs calculated by dichotomy\;
+        $N_{\text{set}} \leftarrow$ number of selected SPs calculated by dichotomy\;
         $C_b    \leftarrow$ set of all combinations of $N_{\text{set}} $~batteries from $N_b$\;
@@
             get $\bm{Y}_n$ by Eq. \ref{eq:Yn}\;
-            \eIf{$\bm{Y}_n$ is invertible}{
-              pass
-            }{construct an effective solution}
+            \eIf{$\bm{Y}_n$ is invertible}{pass}{construct an effective solution}
             get $I_o$ by Eq. \ref{eq:I_o}\;
             get $\bm{I}_b$ by Eq. \ref{eq:I_b}\;
-            \eIf{$\max(\bm{I}_b)\leq I_m$}{
-                $\eta \leftarrow I_o/\max(\bm{I}_b)$\;
-            }{break}
+            \eIf{$\max(\bm{I}_b)\leq I_m$}{$\eta \leftarrow I_o/\max(\bm{I}_b)$\;}{break}
         }

### 2023-11-09 paper/SST/3-response_reviewer1.tex
Add revised manuscript and response to reviewer comments

% Reviewer 1
\reviewer
% Comment 1
\begin{revcomment}
  Grammatical and spelling errors are still observed. Please check and fix carefully.
\end{revcomment}
\begin{revresponse}

We are sorry for our negligence of the grammatical and spelling errors, and have carefully checked the manuscript and corrected them.

\end{revresponse}

% Comment 2
\begin{revcomment}
  Since authors stated that there is no existing works on the MAC determination of RBSs that they could compare their solution with. So how the authors validate their works and their results.
\end{revcomment}
\begin{revresponse}

We infer that the reviewer may desire to convey: since the authors stated that there are no existing works on the MAC determination of RBSs that they could compare their solution with, it is important to meticulously and comprehensively elucidate how the authors validate their works and the results.

To address the concern raised by the reviewer, we have incorporated a comprehensive discussion in the Case study section, specifically titled "Correctness of the results". 
In this part, we thoroughly examine the correctness of the results obtained through the proposed greedy algorithm from two distinct perspectives: circuit analysis and validation against the brute-force algorithm. 
Additionally, we have included a comparison between the proposed greedy algorithm and two heuristic algorithms, namely simulated annealing and genetic algorithm, in the revised manuscript. 
There is a reference ([35] in the manuscript) claiming that the path selection problem under consideration may be NP-hard.
Therefore, it is reasonable to compare the performance of the proposed greedy algorithm with these heuristic approaches, which are commonly employed to tackle NP-hard problems.
Remarkably, our results demonstrate that the proposed greedy algorithm consistently achieves the same or superior outcomes compared to the heuristic algorithms.

Here is the specific modification we made in the Discussion:
\begin{changes}
  \ExecuteMetaData[3-main]{reviewer1-comment2}
\end{changes}
And here is the comparison between the proposed greedy algorithm and the heuristic algorithms in the "Result":
\begin{changes}
  \ExecuteMetaData[3-main]{reviewer1-comment2a}
  \ExecuteMetaData[3-main]{reviewer1-comment2b}
\end{changes}

\end{revresponse}

% Comment 3
\begin{revcomment}
  Refer to the mentioned article as previously stated in comment 8 of the first revision.
\end{revcomment}
\begin{revresponse}

We have reconsidered and modified the corresponding content about the analysis on MAC problem in the introduction. 
The mentioned article becomes important to this paper, therefore, we have cited it in the introduction and accept the reviewer's suggestion.

We have reevaluated and revised the relevant content regarding the analysis of the MAC problem in the introduction. The mentioned article holds significance in this paper, hence we have referenced it in the introduction and acknowledged the suggestion made by the reviewer.

Here is the specific modification we made in the introduction:
\begin{changes}
  \ExecuteMetaData[3-main]{reviewer1-comment3}
\end{changes}

\end{revresponse}

### 2023-11-09 paper/SST/3-response_reviewer2.tex
Add revised manuscript and response to reviewer comments

% Reviewer 2
\reviewer
% Comment 1
\begin{revcomment}
  The latest related works need to be reviewed carlfully please, expecicially the works published in recent year 2022,2023.
\end{revcomment}
\begin{revresponse}

We concur with the reviewer's assertion that it is important for our paper to undergo a thorough review of the most recent relevant literature. 
We have carefully scrutinized the pertinent works from the past five years and made appropriate revisions to the manuscript.
In the "Introduction" section, we provide an overview of the challenges posed by the complex RBS structures in hardware design. 
Furthermore, the estimation and control of the system state of RBSs have been receiving increasing attention in recent time.
Consequently, we have chosen several corresponding methodologies aimed at optimizing the system's performance.

Here is the specific modification in the introduction:
\begin{changes}
  \ExecuteMetaData[3-main]{reviewer2-comment1}
\end{changes}

\end{revresponse}

% Comment 2
\begin{revcomment}
  The greedy algorithm and the brute force algorithm are compared in this paper, but the advantages and disadvantages of this algorithm compared with other algorithms cannot be determined.
\end{revcomment}
\begin{revresponse}

Thanks to the suggestion of the reviewer! 
We have revised the "Discussion" subsection and included a specific part to analyze the advantages and disadvantages of the proposed greedy algorithm in comparison to other algorithms. 
Based on our discussion and comparison, the proposed greedy algorithm demonstrates a significant advantage in terms of its effectiveness and efficiency.
It is also capable of handling RBSs with diverse structures. 
However, this algorithm may encounter challenges when dealing with large-scale problems due to its exponential time complexity.
Furthermore, the simplification of the derivation by assuming that all batteries are identical may introduce a slight bias to the MAC due to variations in open-circuit voltage $u_b$ and internal resistance $r_b$ in reality.
We have also provided a solution to address this issue.

The relevant content has been added to the "Advantages and disadvantages of our method" part within the "Discussion" subsection. 
Once again, we appreciate this constructive comment from the reviewer.

\end{revresponse}

% Comment 3
\begin{revcomment}
  This paper mainly applies to the four-battery system, but the usability of other structures of RBS should also be discussed.
\end{revcomment}
\begin{revresponse}

Thanks for the valuable feedback. 
We have thoroughly considered the comment made by the reviewer.
In response, we have supplemented the case study with a series of experiments on RBSs with variant batteries. 
Overall, the proposed greedy algorithm has been applied to RBSs with three different structures, variant batteries, and scenarios involving random isolated batteries. 
The correctness and efficiency of the proposed greedy algorithm have been verified through the comparison with other algorithms.

The relevant content has been added to the "Case study" section. 
We hope it can address the reviewer's concerns.

\end{revresponse}

### 2023-11-09 paper/SST/3-cover_letter.tex
Add revised manuscript and response to reviewer comments

\noindent Dear \editorname \, and the anonymous reviewers,

On behalf of my co-authors, we express our sincere gratitude for providing us with the opportunity to revise our manuscript. We highly value the reviewers' insightful and constructive comments and suggestions on our manuscript titled "\thetitle" (ID:\manuscript).

We have thoroughly examined the reviewers' comments and have made revisions, which are indicated in red within the paper. We have made every effort to address the comments and improve our manuscript accordingly. Please find attached the revised version, which we kindly request you to consider.

We would like to extend our great appreciation to you and the reviewers for their valuable feedback on our paper. We eagerly await your response.

Thank you and best regards.
\begin{flushright}
\theauthor

Beihang University

2023.11.10
\end{flushright}

### 2023-11-10 paper/SST/3-response_reviewer1.tex
fix and modify cover letter and response

@@
 Additionally, we have included a comparison between the proposed greedy algorithm and two heuristic algorithms, namely simulated annealing and genetic algorithm, in the revised manuscript. 
-There is a reference ([35] in the manuscript) claiming that the path selection problem under consideration may be NP-hard.
+There is a reference (No. 35 in the manuscript) claiming that the path selection problem under consideration may be NP-hard.
 Therefore, it is reasonable to compare the performance of the proposed greedy algorithm with these heuristic approaches, which are commonly employed to tackle NP-hard problems.
@@
 
-Here is the specific modification we made in the Discussion:
+Here is the specific modification we made in the "Discussion":
 \begin{changes}
@@
 \end{changes}
-And here is the comparison between the proposed greedy algorithm and the heuristic algorithms in the "Result":
+And here is one of the comparisons between the proposed greedy algorithm and the heuristic algorithms in the "Result" section:
 \begin{changes}
   \ExecuteMetaData[3-main]{reviewer1-comment2a}
-  \ExecuteMetaData[3-main]{reviewer1-comment2b}
 \end{changes}
+For more information on the other compared results and details, please refer to the revised "Case Study" section.
 
+We hope that the reviewer is satisfied with the modifications made to the manuscript.
 \end{revresponse}

### 2023-11-10 paper/SST/3-cover_letter.tex
fix and modify cover letter and response

@@
 
-We have thoroughly examined the reviewers' comments and have made revisions, which are indicated in red within the paper.
-We have made every effort to address the comments and improve our manuscript accordingly.
+We have thoroughly examined the reviewers' comments and have made revisions, which are indicated in red and blue within the paper.
 Please find attached the revised version, which we kindly request you to consider.

### 2023-11-10 paper/SST/3-response_reviewer1.tex
按 Q 的意见修改

@@
 
-We infer that the reviewer may desire to convey: since the authors stated that there are no existing works on the MAC determination of RBSs that they could compare their solution with, it is important to meticulously and comprehensively elucidate how the authors validate their works and the results.
+% We infer that the reviewer may desire to convey: since the authors stated that there are no existing works on the MAC determination of RBSs that they could compare their solution with, it is important to meticulously and comprehensively elucidate how the authors validate their works and the results.
 
-To address the concern raised by the reviewer, we have incorporated a comprehensive discussion in the Case study section, specifically titled "Correctness of the results". 
+To address the concern raised by the reviewer, we have incorporated a comprehensive discussion in the Case study section, specifically titled "Result validation". 
 In this part, we thoroughly examine the correctness of the results obtained through the proposed greedy algorithm from two distinct perspectives: circuit analysis and validation against the brute-force algorithm.

### 2023-11-15 paper/SST/3-main.tex
Add revised manuscript and response to reviewer comments
fix and modify cover letter and response
按 Q 的意见修改
polished 3-main from professional organization

@@
-% =====2-review outline======
-% 1. intro 文献综述部分：重写、补充，引用c8的文献；对RBS性能的分析
-%   1.1 任务分配：如果从电流分配的角度考虑，这是一个 NP-hard 问题，求解这类问题的开销一般很大，通过针对性地改进传统算法来解决计算开销，例如 Mollajafari 提出了 a meta-heuristic method named Graph-Oriented Simulated Annealing (GOSA) )(结合 gammoudiEnergyEfficientSchedulingRealTime2020 这篇可重构任务调度的文章)
-%   1.2 对RBS性能的分析
-%   1.3 多说一点启发式算法
-% 2. case study 增加实验 模拟退火、遗传算法；增加b结构的2，6数量的电池
-%   2.1 structures and details
-%       2.1.1 4-battery 不同结构（3个tab：our method；1个图）
-%       2.1.2 2/4/6-battery 结构c
-%       2.1.3 4-battery 不同结构 isolated battery
-%       2.1.4 四种计算方法
-%   2.2 result: 删去table4和前面一段话；添加文字，描述figure7；使用子图子表格
-%       2.1.1 c结构的计算细节：1组fig（有向图、SP、最终结果）
-%       2.1.2 4-battery 不同结构的计算结果：1组tab（各结构计算结果）、2组fig（各结构MAC正确闭合方案+算法迭代过程中的MAC折线图）
-%       2.1.3 2/4/6-battery 结构c（1,2,3 *2）的计算结果：1组tab（各结构计算结果）、2组fig（各结构MAC正确闭合方案+算法迭代过程中的MAC折线图）
-%       2.1.4 4-battery c 不同 isolated battery 的计算结果：1组fig（不同电池数的开关闭合方案）
-%   2.3 discussion:
-%       2.3.1 结果正确性和准确性：a. 电路分析；b. 与 force-brute 结果的验证
-%       2.3.2 算法的有效性和优劣：a. 复杂度；b. 与 SA、GA 的比较(启发式算法仅找到局部最优；收敛时间)；c. 本算法的优劣和原因
-%       2.3.3 this work 的意义和应用：a. 说明 eta 的意义、应用方法；b. 结合 isolated battery 说明应用场景
-% 3. conclusion 相关内容修改
-% 4. abstract 相关内容修改
-
-% ! NOTE
-% [DONE]
-% 1. red mark -> blue mark
-% 2. check ref
-% 3. rewrite the last two paragraphs of the introduction if time permits
-
 \documentclass{article}
@@
 % \title{Using a Directed Graph Model and Greedy Algorithm to Determine the Maximum Allowable Current in a Reconfigurable Battery System}
-\title{Maximum Allowable Current Determination of RBS By Using a Directed Graph Model and Greedy Algorithm}
+\title{Determining the Maximum Allowable Current of an RBS using a Directed Graph Model and Greedy Algorithm}
 
@@
 \begin{abstract}
-Reconfigurable battery systems (RBSs) present a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structure that can be adapted to different battery charging and discharging strategies.
-During RBS operation, a critical system parameter known as the maximum allowable current (MAC) become pivotal.
-This parameter is instrumental in maintaining the current of each individual battery within a safe range and serves as a guiding indicator for the system's reconfiguration, thereby ensuring its safety and reliability.
-This paper proposes a method to calculate the MAC of arbitrary RBSs using a greedy algorithm in conjunction with a directed graph model of the RBS.
-By introducing the shortest path (SP) of the battery, the greedy algorithm transforms the enumeration of switch states in the brute-force algorithm or variable search without utilizing structures in the heuristic algorithms (simulated annealing and genetic algorithm) into the combination of the shortest paths.
+Reconfigurable battery systems (RBSs) provide a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structures that can be adapted to different battery charging and discharging strategies.
+A critical system parameter known as the maximum allowable current (MAC) is pivotal to RBS operation.
+This parameter is instrumental in maintaining the current of each individual battery within a safe range and serves as a guiding indicator for the system's reconfiguration, ensuring its safety and reliability.
+In this paper, a method is proposed for calculating the MAC of an arbitrary RBS using a greedy algorithm in conjunction with a directed graph model of the RBS.
+Using the shortest path (SP) of the battery, the greedy algorithm transforms the exhaustion of the switch states in the brute-force algorithm or variable search without utilizing structures in the heuristic algorithms (simulated annealing and genetic algorithms) in the combination of the shortest paths.
 This significantly enhances the efficiency with which the MAC is determined.
-The directed graph model, based on the equivalent circuit, provides a specific method for calculating the MAC of a given structure.
-The proposed method is validated on two published RBS structures and one with a more complex structure.
-The results are the same as those of the brute-force algorithm, but the proposed method significantly improves the computational efficiency ($N_s 2^{N_s - N_b} \log_{10} N_b$ times faster than the brute-force algorithm for an RBS with $N_b$ batteries and $N_s$ switches, theoretically).
+The directed graph model, based on an equivalent circuit, provides a specific method for calculating the MAC of a given structure.
+The proposed method is validated using two previously published RBS structures and an additional one with a more complex structure.
+The results are the same as those from the brute-force algorithm, but the proposed method significantly improves the computational efficiency, being theoretically $N_s 2^{N_s - N_b} \log_{10} N_b$ times faster than the brute-force algorithm for an RBS with $N_b$ batteries and $N_s$ switches.
 Another advantage of the proposed method is its ability to calculate the MAC of RBSs with arbitrary structures and variable batteries, even in scenarios with random isolated batteries.
@@
 Typically, a BESS consists of numerous batteries interconnected by series-parallel circuitry to provide the required storage capacity.
-However, conventional BESSs, in which the batteries are connected in a fixed topology, suffer from a significant weakness in their worst battery due to the so-called cask effect.
+However, conventional BESSs, in which the batteries are connected in a fixed topology, suffer from a significant weakness in their worst batteries due to the so-called cask effect.
 Furthermore, if the worst battery fails during operation, it is highly likely to accelerate the degradation of the other batteries, resulting in reliability and safety issues at the system level \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019,jeevarajanBatterySafetyQualifications2012}.
 These challenges have become major technical obstacles in many engineering projects that demand high reliability, such as the development of next-generation space vehicles \cite{pomboHybridPowerSystem2021}.
-Reconfigurable battery systems (RBSs), which can dynamically switch between different circuit topologies as needed, are expected to address these issues \cite{hanNextGenerationBatteryManagement2020a}.
+Reconfigurable battery systems (RBSs), which can dynamically switch between different circuit topologies as needed, are expected to be able to address these issues \cite{hanNextGenerationBatteryManagement2020a}.
 In a typical RBS, additional switches are introduced between the batteries to form a reconfigurable network, where the circuit's topology can be altered by opening or closing the switches.
 By opening the switches adjacent to the unhealthy batteries, they can be isolated from the system, ensuring that the system remains in a reliable operational state \cite{ci2016reconfigurable}.
-Furthermore, the RBS can be reconfigured to adapt to different charging and discharging strategies, thereby enhancing the system's efficiency and prolonging the battery's lifespan \cite{bouchhima2018lifetime}.
+Furthermore, an RBS can be reconfigured to adapt to different charging and discharging strategies, thereby enhancing the system's efficiency and prolonging the battery's lifespan \cite{bouchhima2018lifetime}.
 These advantages make RBSs a promising alternative to traditional BESSs.
 
-The early research on RBSs mainly focused on the topological design of the structure, incorporating different levels of flexibility and reconfigurability to meet application requirements.
+The early research on RBSs mainly focused on the topological design of their structures, incorporating different levels of flexibility and reconfigurability to meet application requirements.
 For example, Ci et al. \cite{ci2007novel} proposed an RBS structure that dynamically adjusts the battery discharge rate to fully exploit the available capacity of each battery. 
-Jan's \cite{9209774,engelhardt2021double} structures reconfigure circuits with variant batteries in series to accommodate the constantly changing voltage requirements during electric vehicle charging.
-The structure proposed by Visairo et al.
-\cite{visairoReconfigurableBatteryPack2008} alters the system's output voltage based on the load conditions, thereby reducing power loss in the voltage regulator during the power supply process and enhancing energy efficiency.
-Also, to enhance the energy efficiency of the system, Lawson et al.
-\cite{lawsonSoftwareConfigurableBattery2012} and He et al.
-\cite{he2014reconfiguration}  proposed simplified structures that have fewer switches than Visairo's design.
-Kim et al. \cite{kim2009dynamic} improved the system's ability to recover from battery failures by introducing multiple ports into the structure. 
-However, these complex structures between batteries and switches provide flexibility to RBSs while also posing challenges in hardware design. 
+Jan et al.
+\cite{9209774,engelhardt2021double} designed structures that reconfigure circuits with variant batteries in series to accommodate the constantly changing voltage requirements during electric vehicle charging.
+A structure proposed by Visairo and Kumar \cite{visairoReconfigurableBatteryPack2008} alters the system's output voltage based on the load conditions, thereby reducing power loss in the voltage regulator during the power supply process and enhancing energy efficiency.
+Lawson \cite{lawsonSoftwareConfigurableBattery2012} and He et al.
+\cite{he2014reconfiguration} also focused on enhancing energy efficiency, and proposed simplified structures that have fewer switches than the design of Visairo and Kumar.
+Kim et al. \cite{kim2009dynamic} improved the ability of an RBS structure to recover from battery failures by introducing multiple ports. 
+%<*reviewer2-comment1>
+These complex structures between batteries and switches provide flexibility to RBSs but also pose challenges in hardware design. 
 During the reconfiguration process, current deviation and fluctuation may occur.
-Specifically, when the system switches from series to parallel connection, circulating current between parallel cells can be triggered due to voltage imbalance \cite{hanAnalysisEstimationMaximum2020}.
+Specifically, when the system switches from series to parallel connection, a circulating current between parallel cells can be triggered due to a voltage imbalance \cite{hanAnalysisEstimationMaximum2020}.
 Failure to fully consider this issue during the design of RBSs can result in damage to the batteries, switches, and wires.
 For example, Engelhardt et al.
-\cite{engelhardtDoubleStringBatterySystem2021} applied RBS to a fast-charging scenario with adaptive cell switching, which can balance cell states while adhering to voltage requests.
+\cite{engelhardtDoubleStringBatterySystem2021} applied an RBS to a fast-charging scenario with adaptive cell switching to balance cell states while adhering to voltage requests.
 However, the switching of batteries leads to intolerable current variations.
@@
 \cite{han2021analysis} derived an analytical expression for the maximum switch current during battery system reconfiguration.
-This analytical expression aids in the selection of switches and supports the hardware design of RBSs.
-
-Recently, there has been increasing attention given to the estimation and control of the system state of RBSs, and several approaches have been proposed to optimize the performance of the system. 
+This analytical expression aids in the selection of switches and supports general hardware design.
+
+Recently, increasing attention has been paid to the estimation and control of RBS system states, and several approaches have been proposed to optimize the performance of these systems. 
 State estimation, which is an essential technology in traditional battery management systems, serves as the foundation for system control and holds great potential in the context of RBSs \cite{komsiyskaCriticalReviewIntelligent2021}.
@@
 Kersten et al.
-\cite{kerstenOnlineOnBoardBattery2020a} utilized the balancing current of neighboring cells in parallel operation to determine battery impedance, thereby obtaining information about the state of health and power capability.
+\cite{kerstenOnlineOnBoardBattery2020a} utilized the balancing current of neighboring cells in parallel operation to determine the battery impedance, thereby obtaining information about the state of health and power capability of the RBS.
 Schmid et al.
-\cite{schmidActiveModelBasedFault2021a} further leveraged the reconfigurable nature of the system to actively diagnose faults, employing an algorithm that changes the system structure to enhance fault isolability.
-Another active research topic is the development of effective control strategies for RBSs to achieve optimal performance, including improved stability \cite{kacetlDesignAnalysisModular2023b} and efficiency \cite{yangAdaptiveControlFramework2022}.
+\cite{schmidActiveModelBasedFault2021a} further leveraged the reconfigurable nature of the system to actively diagnose faults, employing an algorithm that changes the system structure to enhance the fault isolability.
+Another active research area is the development of effective control strategies for RBSs to achieve optimal performance, including improved stability \cite{kacetlDesignAnalysisModular2023b} and efficiency \cite{yangAdaptiveControlFramework2022}.
 Han et al. \cite{hanNearFastestBatteryBalancing2019a} proposed a near-fastest battery balancing algorithm to minimize the time required for battery charge equalization.
 Liu et al.
-\cite{liuFlexiblePathPlanningbased2023a} also proposed a scheme for maximizing capacity utilization based on a path planning algorithm, aiming to enhance battery consistency within the system.
-To break through the bottleneck of the potential short-circuit paths increase exponentially with the RBS's scale, Chen et al.
+\cite{liuFlexiblePathPlanningbased2023a} also proposed a scheme for maximizing capacity utilization based on a path planning algorithm, aiming to enhance the battery consistency within the system.
+To break through the bottleneck of the potential short-circuit paths increasing exponentially with the RBS scale, Chen et al.
 \cite{chenSneakCircuitTheory2021} proposed a systematic approach based on sneak circuit theory.
-They conducted a comprehensive analysis of all paths between the cathode and anode of each battery in the RBS, identifying paths that only consist of switches as short-circuit paths for pre-checking before system reconfiguration.
-Furthermore, Artificial Intelligence also appears in the RBS management \cite{liuLongLifetimeBattery2022a}.
-The effectiveness of deep reinforcement learning method has been validated in real-world RBSs \cite{yangAdaptiveControlFramework2022}.
-
-The maximum allowable current (MAC), which is defined as the maximum current allowed within the constraints of the battery cell, is a crucial indicator of RBSs that needs to be evaluated during the design and control of the system.
-The MAC assists designers in assessing whether the RBS meets the requirements for output current and contributes to the development of appropriate and safe management strategies for the battery management system.
-Unfortunately, there have been few studies proposed to directly determine the MAC of RBSs, primarily due to the complexity arising from reconfiguration. 
-In the field of computer science, there is a similar problem of scheduling tasks on dynamically reconfigurable hardware with limited resources and task interdependencies, which is analogous to the determination of MAC.
-A corresponding method has been proposed \cite{mollajafariEfficientLightweightAlgorithm2023,heReconfigurationassistedChargingLargescale2014}. 
+They conducted a comprehensive analysis of all paths between the cathode and anode of each battery in the RBS, identifying paths that consist only of switches as short-circuit paths for pre-checking before system reconfiguration.
+Artificial intelligence has also appeared in RBS management \cite{liuLongLifetimeBattery2022a}.
+The effectiveness of the deep reinforcement learning method has been validated in real-world RBSs \cite{yangAdaptiveControlFramework2022}.
+%</reviewer2-comment1>
+
+The maximum allowable current (MAC), which is defined as the maximum current allowed within the constraints of a battery cell, is a crucial indicator of RBSs that need to be evaluated during the design and control of the system.
+The MAC assists designers in assessing whether the RBS meets output current requirements and contributes to the development of appropriate and safe strategies for the battery management system. 
+%<*reviewer1-comment3>
+However, few studies have directly determined the MACs of RBSs, primarily due to the complexity arising from reconfiguration. 
+In the field of computer science, there is a similar problem with scheduling tasks on dynamically reconfigurable hardware with limited resources and task interdependencies.
+This problem is analogous to the determination of the MAC and a corresponding solution has been proposed \cite{mollajafariEfficientLightweightAlgorithm2023,heReconfigurationassistedChargingLargescale2014}.
 However, dealing with the structural characteristics and circuit equations of RBSs is challenging for this method. 
-From the perspective of RBS structure analysis, the MAC problem can be transformed into finding the maximum output current among all possible reconfigurations of the RBS. 
+%</reviewer1-comment3>
+From the perspective of RBS structure analysis, the MAC problem can be transformed into a problem of finding the maximum output current among all possible reconfigurations of the RBS. 
 However, this may be an NP-hard problem \cite{pinterReviewControlAlgorithms2021a}. 
-Common methods such as brute-force algorithms, simulated annealing (SA) algorithms, and genetic algorithms (GA) have the drawbacks of inefficiency, time consumption, and inability to guarantee the globally optimal solution.
-
-To solve this issue, this paper proposes an efficient method to evaluate the MAC of RBSs. 
-In this method, a greedy algorithm is designed to efficiently search the possible circuit topology of RBSs with MAC.
-This algorithm transforms the inefficiently searching reconfigurations into the proactively combining of the shortest paths of batteries.
-Furthermore, an improved directed graph model is introduced to analyze the current of the RBS, taking into account factors such as voltage, internal resistance, MAC of the battery, and external load. 
+Common methods such as brute-force algorithms, simulated annealing (SA) algorithms, and genetic algorithms (GA) have the drawbacks of inefficiency, excessive time consumption, and an inability to guarantee the globally optimal solution.
+
+To solve this issue, this paper proposes an efficient method to evaluate the MACs of RBSs. 
+In this method, a greedy algorithm is designed to efficiently search the possible circuit topologies of RBSs.
+This algorithm transforms the inefficient search for reconfigurations into a proactive combining of the shortest paths of the batteries.
+Furthermore, an improved directed graph model is introduced to analyze the current of the RBS, taking into account factors such as the voltage, internal resistance, MAC of the battery, and external load.
 The main contributions of this study can be summarized as follows:
 \begin{itemize}
-  \item An efficient method is proposed to determine the MAC of RBSs with arbitrary structures, including scenarios with isolated batteries.
+  \item An efficient method is proposed to determine the MACs of RBSs with arbitrary structures, including scenarios with isolated batteries.
   \item A greedy algorithm is applied to solve the MAC problem, the computational complexity of which is greatly reduced compared with the brute-force algorithm.
@@
 The remainder of this paper is organized as follows: 
-Section II presents the framework and details of the proposed directed graph model and greedy algorithm. 
-Section III examines a case study that applies the proposed method to determine the MACs of two published RBS structures and one with a more complex structure. 
+Section II presents the framework and details of the proposed directed graph model and the greedy algorithm. 
+Section III applies the proposed method to determine the MACs of two published RBS structures and a new one with a more complex structure. 
 The calculation results, the computational complexity of the algorithm, and scenarios such as battery random isolation are also discussed. 
@@
 
-The central principle of this method is to connect the batteries in an RBS in parallel to the extent possible, thereby maximizing the output current of the RBS.
+The central principle of the proposed method is to connect the batteries in an RBS in parallel to the maximum possible extent, thereby maximizing the output current.
 To achieve this universally and automatically, the overall process is divided into the four steps shown in Fig. \ref{fig:main}.
-First, a directed graph model is established for subsequent computations.
+First, a directed graph model is established for the subsequent computations.
 The model not only contains the connected relationships between batteries and switches but also retains the performance parameters of the batteries.
 Subsequently, based on the equivalent circuit, the MAC problem is transformed into specific objective functions and constraints.
-The shortest paths (SPs, where additional batteries and switches on the path are penalized as distance) for the batteries are then obtained  by using the Dijkstra algorithm to connect the batteries in the RBS in parallel.
+The shortest paths (SPs, where additional batteries and switches on the path are penalized for distance) of the batteries are then obtained using the Dijkstra algorithm to connect the batteries in the RBS in parallel.
 Finally, a greedy algorithm is used to organize the switches, allowing the batteries to connect via their SPs while satisfying the constraints, resulting in the MAC of the RBS.
@@
     \caption{ 
-        Diagram of this method, which contains four main steps.
+        A diagram of the proposed method, which contains four main steps.
     }
@@
     \caption{ 
-        Directed graph models used in (a) He's work \cite{heExploringAdaptiveReconfiguration2013}, (b) our previous work, and (c) the improved model in this paper.
+        The directed graph models used in (a) the work of He et al. \cite{heExploringAdaptiveReconfiguration2013}, (b) our previous work, and (c) the improved model in this paper.
         (d) The equivalent circuit of a battery in this method.
@@
 The model captures all potential system configurations and offers a direct metric for configuration flexibility, but it does not specify the physical implementation of the connectivity between batteries, meaning that one graph might correspond to multiple RBS structures.
-We previously proposed a directed graph model that differs completely from He's model by using nodes to represent the connections between batteries and switches and directed edges to represent batteries and switches (Fig.
-\ref{fig:direct-graph-xu}), allowing for a one-to-one correspondence between the RBS structure and the directed graph model.
-This model accurately and comprehensively represents the RBS topological structure but cannot be used for quantitative MAC calculations because it does not consider  the voltage, internal resistance, and MAC of the battery.
-To address this issue, we improve our previous model by adding electromotive force and resistance attributes on the edges based on its equivalent circuits.
-The model also considers the external load as an equivalent resistance and integrates it into the analysis, making it a complete circuit model for later circuit analyzes.
+We previously proposed a directed graph model that differs significantly from He et al.'s model by using nodes to represent the connections between batteries and switches and directed edges to represent batteries and switches (Fig.
+\ref{fig:direct-graph-xu}), allowing for a one-to-one correspondence between an RBS structure and its directed graph model.
+This model accurately and comprehensively represents the RBS topological structure but cannot be used for quantitative MAC calculations because it does not consider the voltage, internal resistance, or MAC of the battery.
+To address this issue, we improve our previous model by adding electromotive force and resistance attributes on the edges based on the corresponding equivalent circuits.
+The model also considers the external load as an equivalent resistance and integrates it into the analysis, making it a complete circuit model for later circuit analysis.
 Fig. \ref{fig:direct-graph-my} shows the improved directed graph model used in this paper.
-The following  provides a detailed explanation of the method for equating components in RBSs and constructing the directed graph model.
+The following provides a detailed explanation of the method used for equating components in RBSs and constructing the directed graph model.
 
@@
 For instance, as shown in Fig.
-\ref{fig:battery_simple}, the battery in the RBS is represented as a black-box circuit consisting of two resistors $r_1$ and $r_2$ and a capacitor $C$, known as the Thevenin model \cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
+\ref{fig:battery_simple}, the battery in the RBS is represented as a black-box circuit consisting of two resistors $r_1$ and $r_2$ and a capacitor $C$, in what is known as the Thevenin model \cite{hongwenheStateofChargeEstimationLithiumIon2011,mousavig.VariousBatteryModels2014}.
 With an emphasis on the stable output of the RBS, the capacitor in the Thevenin model can be considered as an open circuit without affecting the steady-state current.
 Therefore, battery $B_i$ in the RBS can be simplified as a series connection between a constant voltage source $u_{i}$ and a resistor $r_{i}$.
-Furthermore, the state of switch $S_j$ in the RBS is represented by a binary variable $x_j$, where 0 is ON and 1 is OFF.
+Furthermore, the state of the switch $S_j$ in the RBS is represented by a binary variable $x_j$, where 0 is ON and 1 is OFF.
 When the switch is closed, the circuit can be regarded as a resistor with a very small resistance $r_{j}$.
@@
         For switch $S_j$, since it is allowed to work under bidirectional currents, it is represented by a pair of directed edges with two-way directions. 
-        Regarding the external electronic load, because it is connected to the anode and cathode of the RBS, a directed edge from $v_N$ to $v_1$  represents it. 
-        In conclusion, for a given RBS structure with $N_b$ batteries and $N_s$ switches, the number of directed edges is $N_b+2N_s+1$, where 1 refers to the external electrical load.
+        For the external electrical load, because it is connected to the anode and cathode of the RBS, a directed edge from $v_N$ to $v_1$ is used to represent it. 
+        In conclusion, for a given RBS structure with $N_b$ batteries and $N_s$ switches, the number of directed edges is $N_b+2N_s+1$, where 1 represents the external electrical load.
     \item Attributes of edges:
-        Each edge is assigned two attributes, voltage difference and resistance, based on the equivalent method mentioned above.
-        The values for  battery $B_i$, switch $S_j$, and external loads correspond to $(u_i, r_i)$, $(0, r_j)$, and $(0, R_o)$, respectively.
+        Each edge is assigned two attributes, a voltage difference and a resistance, based on the equivalent method mentioned above.
+        The values for battery $B_i$, switch $S_j$, and the external loads correspond to $(u_i, r_i)$, $(0, r_j)$, and $(0, R_o)$, respectively.
 \end{enumerate}
@@
 
-For a given RBS, determining its MAC involves maximizing the RBS output current while ensuring that all battery currents do not exceed the batteries' MAC. 
-This subsection establishes the constraints and objective function to determine the RBS's MAC through circuit analysis based on the directed graph model provided in the previous section.
-
-First, the topology in the directed graph model is represented in matrix form $\bm{A}$, known as the incidence matrix and defined as follows:
+For a given RBS, determining the MAC involves maximizing the RBS output current while ensuring that all battery currents do not exceed the batteries' MAC. 
+This subsection establishes the constraints and objective function used to determine the MAC through circuit analysis based on the directed graph model provided in the previous section.
+
+First, the topology in the directed graph model is represented in the form of a matrix $\bm{A}$, which is known as the incidence matrix and is defined as follows:
 \begin{align}\label{eq:A}
@@
 \end{align}
-For a directed graph consisting of $N$ nodes and $N_b+2N_s+1$ directed edges, its incidence matrix $\bm{A}$ is an $N\times(N_b+2N_s+1)$ matrix. 
+For a directed graph consisting of $N$ nodes and $N_b+2N_s+1$ directed edges, the incidence matrix $\bm{A}$ is an $N\times(N_b+2N_s+1)$ matrix. 
 In this matrix, the rows and columns represent the nodes and edges of the directed graph, respectively.
@@
 Thus, for the submatrix $\bm{A}_s$, only one column is retained for each pair of columns representing the same switch.
-As a result, $\bm{A}$ can be reduced to a $(N-1)\times(N_b+N_s+1)$ matrix, denoted $\bm{\tilde{A}}$, for further calculation of current and voltage.
+As a result, $\bm{A}$ can be reduced to an $(N-1)\times(N_b+N_s+1)$ matrix, denoted $\bm{\tilde{A}}$, for further calculation of the current and voltage.
 Similar to Eq. (\ref{eq:A_bso}), $\bm{\tilde{A}}$ can be rewritten as
@@
 where $\bm{U}_s$ and $\bm{I}_s$ denote the source voltage and source current of the generalized branches, respectively.
-Because all batteries have been equivalent to voltage sources rather than current sources in the previous subsection, all elements of the array $\bm{I}_s$ are zero, 
+Because all batteries have been made equivalent to voltage sources rather than current sources in the previous subsection, all elements of the array $\bm{I}_s$ are zero, 
 whereas the elements of the array $\bm{U}_s$ are equal to the first attribute of the corresponding edges in the directed graph.
@@
 When all batteries are healthy and capable of providing current to the external load, $\bm{X}_b$ is the identity matrix. 
-The elements $x_j$ of  matrix $\bm{X}_s$ determine whether switch $S_j$ is closed, with $x_j=1$ indicating a closed switch and $x_j=0$ indicating an open switch, which is consistent with the previous subsection.
-
-Theoretically, the output current $I_o$ and the currents of each battery $\bm{I}_b$ in the RBS  can be determined by solving Eqs.
-(\ref{eq:Kirchhoffs_law})--(\ref{eq:X}) under any given state $\bm{X}$.
+The elements $x_j$ of matrix $\bm{X}_s$ determine whether switch $S_j$ is closed, with $x_j=1$ indicating a closed switch and $x_j=0$ indicating an open switch, consistently with the previous subsection.
+
+Theoretically, the output current $I_o$ and the currents of each battery $\bm{I}_b$ in the RBS can be determined by solving Eqs. (\ref{eq:Kirchhoffs_law})--(\ref{eq:X}) under any given state $\bm{X}$.
 To further simplify the problem, it is assumed that all batteries have the same electromotive force and internal resistance, which are denoted $u_b$ and $r_b$, respectively.
 This allows us to derive explicit expressions for $I_o$ and $\bm{I}_b$.
-After derivation and simplification, the output current $I_o$ and the currents of each battery $\bm{I}_b$ are ultimately represented as Eqs. (\ref{eq:I_o}) and (\ref{eq:I_b}), respectively:
+After derivation and simplification, the output current $I_o$ and the currents of each battery $\bm{I}_b$ are ultimately represented as in Eqs. (\ref{eq:I_o}) and (\ref{eq:I_b}), respectively:
 \begin{equation}\label{eq:I_o}
@@
 However, it remains computationally difficult to solve Eq. (\ref{eq:max_eta}) because of $\bm{Y}_n^{-1}$.
-On one hand,  the introduction of nonlinear terms by $\bm{Y}_n^{-1}$ renders many  methods in linear optimization unsuitable for this problem.
-On the other hand, the rank of $Y_{n}$ is proportional to the number of batteries and switches, which can be very large for a large RBS, leading to a significant computational burden.
+Firstly, the introduction of nonlinear terms through $\bm{Y}_n^{-1}$ renders many methods in linear optimization unsuitable for this problem.
+Secondly, the rank of $Y_{n}$ is proportional to the number of batteries and switches, which can be very large for a large RBS, leading to a significant computational burden.
 As a result, intelligent algorithms that rely on evolution by iteration may face efficiency problems when dealing with a large RBS.
@@
 The path $p$ used in this method is defined as the complete route that passes through one battery (or a consecutive series of batteries) and closed switches, connecting the anode $v_1$ to the cathode $v_N$ of the RBS.
-By applying a penalty to the series-connected batteries on the path, where additional batteries imply a greater distance, the algorithm encourages the RBS to form parallel structures to the extent possible.
+By applying a penalty to the series-connected batteries on the path, where additional batteries imply a greater distance, the algorithm encourages the RBS to form parallel structures to the maximum extent possible.
 In addition, to reduce the number of switches controlled during the reconstruction process, a penalty is also applied to the total number of switches on the path while ensuring the minimum number of batteries.
@@
 where $N_s$ is the total number of switches in the system, 
-and $n_b(p)$ and $n_s(p)$ are the number of batteries and switches in path $p$, respectively. 
+and $n_b(p)$ and $n_s(p)$ are the number of batteries and switches along path $p$, respectively. 
 Moreover, the shortest path $SP_i$ is defined as the path with the minimum $\omega$ for battery $B_i$:
@@
 
-$SP_i$ can be solved by the Dijkstra algorithm.
+$SP_i$ can be solved using the Dijkstra algorithm.
 The Dijkstra algorithm is a graph-search method that finds the shortest path between two given nodes in a weighted graph, efficiently solving the single-source shortest-path problem.
-Denoting the cathode and anode of battery $B_i$ as $v_i^-$ and $v_i^+$ respectively, then path $p$ of battery $B_i$  can be divided into three segments: $v_1 \rightarrow v_i^-$, $v_i^+ \rightarrow v_N$, and $v_i^- \rightarrow v_i^+$.
+Denoting the cathode and anode of battery $B_i$ as $v_i^-$ and $v_i^+$ respectively, path $p$ of battery $B_i$ can be divided into three segments: $v_1 \rightarrow v_i^-$, $v_i^+ \rightarrow v_N$, and $v_i^- \rightarrow v_i^+$.
 $v_i^- \rightarrow v_i^+$ is the directed edge corresponding to battery $B_i$.
@@
 
-From the perspective of series vs parallel connections, integrating more batteries into the circuit through their shortest paths (SPs) results in more batteries connected in parallel, thereby increasing the total output current of the RBS.
+From the perspective of series vs.
+parallel connections, integrating more batteries into the circuit through their shortest paths (SPs) results in more batteries connected in parallel, thereby increasing the total output current of the RBS.
 However, conflicts may arise between the SPs of different batteries. 
@@
 
-The algorithm (see pseudocode in Algorithm 1) is illustrated in Fig. \ref{fig:flowchart} and is summarized as follows:
+The algorithm (see the pseudocode in Algorithm 1) is illustrated in Fig. \ref{fig:flowchart} and is summarized as follows:
 First, the SPs are obtained by using Eqs. (\ref{eq:weight}) and (\ref{eq:def_sp}) in conjunction with the Dijkstra search. 
@@
 The algorithm uses a dichotomy method to iteratively check until convergence different combinations of $c_b$ batteries from $N_b$ and updates $N_{\text{set}}$. 
-For each combination, the algorithm constructs an effective solution if possible and calculates the currents $I_o$ and $\bm{I}_b$ by using Eqs. (\ref{eq:I_o}) and (\ref{eq:I_b}). 
-If the maximum current $\bm{I}_b$ is less than or equal to $I_m$, $\eta$ is calculated by using Eq. (\ref{eq:eta}), and the maximum $\eta$ is updated accordingly. 
+For each combination, the algorithm constructs an effective solution if possible, and calculates the currents $I_o$ and $\bm{I}_b$ using Eqs. (\ref{eq:I_o}) and (\ref{eq:I_b}). 
+If the maximum current $\bm{I}_b$ is less than or equal to $I_m$, $\eta$ is calculated using Eq. (\ref{eq:eta}), and the maximum $\eta$ is updated accordingly. 
 Finally, the algorithm outputs the maximum $\eta$ once $N_{\text{set}}$ converges.
@@
     \end{subfigure}
-    \caption{The four-battery RBS structures proposed by (a) Lawson \cite{lawsonSoftwareConfigurableBattery2012}, (b) Visairo \cite{visairoReconfigurableBatteryPack2008}, and (c) this paper.}
+    \caption{The four-battery RBS structures proposed by (a) Lawson \cite{lawsonSoftwareConfigurableBattery2012}, (b) Visairo and Kumar \cite{visairoReconfigurableBatteryPack2008}, and (c) this paper.}
 \end{figure}
 
-Currently, two types of RBS structures have been proposed by Visairo et al.
-\cite{visairoReconfigurableBatteryPack2008} and Lawson et al.
-\cite{lawsonSoftwareConfigurableBattery2012}, both of which have seen real use.
-The primary goal of Visairo's structure (Fig.
+Currently, there are two types of RBS structures in the existing literature --- those of Visairo and Kumar \cite{visairoReconfigurableBatteryPack2008} and Lawson \cite{lawsonSoftwareConfigurableBattery2012}, both of which have seen real use.
+The primary goal of Visairo and Kumar's structure (Fig.
 \ref{fig:study-stru-Visairo}) is to dynamically adjust the RBS output power.
 However, the isolation of unhealthy batteries is not sufficiently addressed in their work.
-Lawson et al. designed the RBS structure shown in Fig. \ref{fig:study-stru-Lawson} to isolate batteries. 
+Lawson designed the RBS structure shown in Fig. \ref{fig:study-stru-Lawson} to isolate batteries. 
 Although this structure easily isolates batteries, it cannot dynamically adjust the output current of the RBS. 
-Based on the structures of Visairo and Lawson, this paper proposes the structure shown in Fig. \ref{fig:study-stru-my}.
-By integrating the Visairo RBS structure into the Lawson RBS structure, the proposed structure not only has the flexibility to switch the batteries between series, parallel, and mixed series-parallel modes but also allows the isolation of highly degraded batteries from the RBS.
-
-In the case study, these RBS systems are investigated and compared: (a) three different structures (Figs.
-\ref{fig:study-stru-Lawson}--\ref{fig:study-stru-my}) with the same four batteries; (b) the same structure in Figs.
-\ref{fig:study-stru-my} with two/four/six batteries; and (c) the four-battery structure in Figs.
+Based on the structure of Visairo and Kumar and that of Lawson, this paper proposes the structure shown in Fig. \ref{fig:study-stru-my}.
+By integrating the Visairo and Kumar RBS structure into the Lawson RBS structure, the proposed structure not only has the flexibility to switch the batteries between series, parallel, and mixed series-parallel modes, but also allows the isolation of highly degraded batteries from the RBS.
+
+In the case study, the following RBS systems are investigated and compared: (a) three different structures (Figs.
+\ref{fig:study-stru-Lawson}--\ref{fig:study-stru-my}) with the same four batteries; (b) the same structure as in Fig.
+\ref{fig:study-stru-my} with two/four/six batteries; and (c) the four-battery structure in Fig.
 \ref{fig:study-stru-my} with random isolated batteries.
 The greedy algorithm proposed in this work is also compared with the brute-force algorithm, SA, and GA to validate its effectiveness and efficiency.
-In order to adapt the two heuristic algorithms to the system's structure and scale, the number of the state neighbors of SA and the population size of GA are both set to $N_b \cdot N_s$, which increase with the number of batteries and switches in the system.
-The other algorithms' parameters are shown in Tab. \ref{tab:algorithm-parameter}.
+In order to adapt the two heuristic algorithms to the system's structure and scale, the number of state neighbors of SA and the population size of GA are both set to $N_b \cdot N_s$, which increases with the number of batteries and switches in the system.
+The parameters of the other algorithms are shown in Tab. \ref{tab:algorithm-parameter}.
 
@@
   \centering
-  \caption{Algorithms parameters of SA and GA.}
+  \caption{The SA and GA algorithm parameters.}
     \begin{tabular}{lr}
@@
 (\ref{eq:weight}) and the Dijkstra algorithm, the SPs of the four batteries in the RBS structures of Figs.
-\ref{fig:study-stru-Lawson}, \ref{fig:study-stru-Visairo}, and \ref{fig:study-stru-my} are calculated and highlighted with difference colors in Figs.
+\ref{fig:study-stru-Lawson}, \ref{fig:study-stru-Visairo}, and \ref{fig:study-stru-my} are calculated and highlighted with different colors in Figs.
 \ref{fig:e4-sp}, \ref{fig:f4-sp}, and \ref{fig:e2f2-sp}, respectively.
@@
 \ref{tab:study-results-Lawson}, \ref{tab:study-results-Visairo}, and \ref{tab:study-results-my}, each of which contains the states of the switches, the output current $I_o$, the battery current $\bm{I}_b$, and the ratio $\eta$ when the system output reaches the MAC.
-The corresponding switch-control schemes are shown as blue-highlighted electric current in Figs. \ref{fig:e4-mac}, \ref{fig:f4-mac}, and \ref{fig:e2f2-mac}, respectively.
-To verify and compare the proposed greedy algorithm, we also used the brute-force algorithm, which iterates through all possible switch states, and the heuristic algorithms (SA and GA) to calculate the MAC of the same RBSs.
-The final results of the brute-force algorithm are the same as the ones of the greedy algorithm, which are shown in Tabs.
+The corresponding switch-control schemes are shown as blue-highlighted electric currents in Figs. \ref{fig:e4-mac}, \ref{fig:f4-mac}, and \ref{fig:e2f2-mac}, respectively.
+%<*reviewer1-comment2a>
+To verify and compare the proposed greedy algorithm, we also used the brute-force algorithm, which iterates through all possible switch states, and the heuristic algorithms (SA and GA) to calculate the MACs of the same RBSs.
+The final results of the brute-force algorithm are the same as those of the greedy algorithm and are shown in Tabs.
 \ref{tab:study-results-Lawson}, \ref{tab:study-results-Visairo}, and \ref{tab:study-results-my}.
-But, the brute-force algorithm counts all possible switch states, which equates to $2^{15}$, $2^{13}$, and $2^{19}$ structures, respectively.
-The two heuristic algorithms' temporal evaluation of the objective values during the iteration process are shown in Figs.
-\ref{fig:e4-alg}, \ref{fig:f4-alg}, and \ref{fig:e2f2-alg}, respectively, compared with the proposed greedy algorithm.
-Comparing to the SA and GA, the proposed greedy algorithm solves the correct results with fewer iteration steps.
+However, the brute-force algorithm counts all possible switch states, which equates to $2^{15}$, $2^{13}$, and $2^{19}$ structures, respectively.
+The temporal evolutions of the objective values of the two heuristic algorithms during the iteration process are shown in Figs.
+\ref{fig:e4-alg}, \ref{fig:f4-alg}, and \ref{fig:e2f2-alg}, respectively, and compared with the proposed greedy algorithm.
+Compared with the SA and GA, the proposed greedy algorithm identifies the correct results within fewer iteration steps. 
+%</reviewer1-comment2a>
 
@@
   \centering
-    \caption{MAC Calculating result of the four-battery RBS structure in Fig. \ref{fig:study-stru-Lawson}.}
+    \caption{The calculated MAC of the four-battery RBS structure in Fig. \ref{fig:study-stru-Lawson}.}
     \begin{tabular}{cc}
     \toprule
-        Structure & Figure \ref{fig:study-stru-Lawson} with 4 batteries and 15 switches  \\
+        Structure & Figure \ref{fig:study-stru-Lawson} with four batteries and 15 switches  \\
     \midrule
@@
   \centering
-    \caption{MAC Calculating result of the four-battery RBS structure in Fig. \ref{fig:study-stru-Visairo}.}
+    \caption{The calculated MAC of the four-battery RBS structure in Fig. \ref{fig:study-stru-Visairo}.}
     \begin{tabular}{cc}
     \toprule
-        Structure & Figure \ref{fig:study-stru-Visairo} with 4 batteries and 13 switches  \\
+        Structure & Figure \ref{fig:study-stru-Visairo} with four batteries and 13 switches  \\
     \midrule
@@
   \centering
-    \caption{Calculated MAC for four-battery RBS structure in Fig. \ref{fig:study-stru-my}.}
+    \caption{The calculated MAC of the four-battery RBS structure in Fig. \ref{fig:study-stru-my}.}
     \begin{tabular}{cc}
@@
     \midrule
-    Switch on & $S_1$,$S_3$,$S_5$,$S_6$,$S_8$,$S_9$,$S_{10}$,$S_{12}$,$S_{18}$,$S_{19}$ \\
+    Switch ON & $S_1$,$S_3$,$S_5$,$S_6$,$S_8$,$S_9$,$S_{10}$,$S_{12}$,$S_{18}$,$S_{19}$ \\
     $I_o$ & $2u_b/(2R_o+r_b)$ \\
@@
     \end{subfigure}
-    \caption{The RBSs' switch-control schemes with the output reaching the MAC.}
+    \caption{The RBS switch-control schemes with the output reaching the MAC.}
 \end{figure}
@@
 
-We next examine the RBS configuration depicted in Fig. \ref{fig:study-stru-my}, which consists of two, four, and six batteries.
-The results for the four-battery configuration are presented in Tab. \ref{tab:study-results-my}, Figs. \ref{fig:e2f2-mac}, and \ref{fig:e2f2-alg}.
+We next examine the RBS configurations depicted in Fig. \ref{fig:study-stru-my}, which consist of two, four, and six batteries.
+The results for the four-battery configuration are presented in Tab. \ref{tab:study-results-my} and Figs. \ref{fig:e2f2-mac} and \ref{fig:e2f2-alg}.
 The structures and final switch-control schemes for the two-battery and six-battery systems are illustrated in Figs. \ref{fig:e2f1-mac} and \ref{fig:e2f3-mac}, respectively.
 Furthermore, the temporal evolutions of the objective values throughout the iteration process are shown in Figs. \ref{fig:e2f1-alg} and \ref{fig:e2f3-alg}, respectively.
-The proposed greedy algorithm is still the one that converges the fastest and achieves the correct MAC. 
-And the SA algorithm fails to obtain the correct MAC within the given iteration steps in the case of six-battery RBS structure.
+The proposed greedy algorithm still converges the fastest and achieves the correct MAC. 
+The SA algorithm fails to obtain the correct MAC within the given number of iteration steps in the case of the six-battery RBS structure.
 
@@
     \end{subfigure}
-    \caption{The (a) two-battery and (b) six-battery RBSs' switch-control schemes with the output reaching the MAC.}
+    \caption{The (a) two-battery and (b) six-battery RBS switch-control schemes with the output reaching the MAC.}
 \end{figure}
@@
 
-To assess the effectiveness of the proposed algorithm in the scenario of unhealthy batteries, the RBS with random isolated batteries is also taken into account and computed. 
+To assess the effectiveness of the proposed algorithm in the case of unhealthy batteries, the RBS with random isolated batteries is also taken into account and computed. 
 In the case of the four-battery RBS structure depicted in Fig.
-\ref{fig:study-stru-my}, there are four possible scenarios of isolated batteries: (a) only one unhealthy battery, (b) two unhealthy batteries that are separated in the two substructure, (c) two batteries located in the same substructure, and (d) three batteries.
+\ref{fig:study-stru-my}, there are four possible scenarios for isolated batteries: (a) a single unhealthy battery, (b) two unhealthy batteries located in different substructures, (c) two unhealthy batteries located in the same substructure, and (d) three unhealthy batteries.
 The resulting MAC ($\eta$) values for these four scenarios are 2, 2, 1, and 1, respectively.
-Furthermore, the corresponding switch-control schemes for these four scenarios are illustrated in Figs \ref{fig:my-isolated-1}--\ref{fig:my-isolated-3}.
+Furthermore, the corresponding switch-control schemes for the four scenarios are illustrated in Figs \ref{fig:my-isolated-1}--\ref{fig:my-isolated-3}.
 
@@
     \caption{
-        Circuit states of MACs when isolating (a) one, (b) two (in different substructures), (c) two (in the same substructure), and (d) three batteries for the structure in Fig.
+        The circuit states of MACs when isolating (a) one, (b) two (in different substructures), (c) two (in the same substructure), and (d) three batteries for the structure in Fig.
 \ref{fig:study-stru-my}.
@@
 
-\subsubsection{Correctness of the results}
-
-The correctness of the outcomes provided by the proposed greedy algorithm will be discussed from two perspectives: circuit analysis and validation against the brute-force algorithm. 
-Let's take the four-battery RBS structure shown in Fig. \ref{fig:study-stru-my} as an example.
+\subsubsection{Result validation}
+
+%<*reviewer1-comment2>
+The correctness of the outcomes provided by the proposed greedy algorithm will now be discussed from two perspectives: circuit analysis and validation against the brute-force algorithm. 
+The result of the four-battery RBS structure shown in Fig. \ref{fig:study-stru-my} is determined as an example.
 When $B_1$ and $B_2$ or $B_3$ and $B_4$ are connected in parallel, the RBS produces the maximum current, which is $\eta=2$ (i.e., twice the current output of a single battery in the RBS). 
@@
 Therefore, the switch-control scheme provided in Tab. \ref{tab:study-results-my} maximizes the RBS output current.
-On the other hand, the brute-force method, which examines all possible switch states, also yields the same $\eta$.
+The brute-force method, which examines all possible switch states, yields the same $\eta$.
 This indicates that the proposed greedy algorithm successfully identifies the MAC among all the potential reconfigured structures.
-
-\subsubsection{Advantages and disadvantages of our method}
+%</reviewer1-comment2>
+
+\subsubsection{Pros and cons analysis}
 
@@
 They selectively generate solutions for the switching states to maximize the objective value $\eta$.
-However, neither of these two algorithms can determine whether the current $\eta$ represents the final MAC or if they should continue searching for better solutions. 
+However, neither of these two algorithms can determine whether the current $\eta$ represents the final MAC or if there are better solutions. 
 Moreover, as depicted in Figs.
 \ref{fig:e4-alg}--\ref{fig:e2f2-alg} and Figs.
-\ref{fig:e2f1-alg}--\ref{fig:e2f3-alg}, the SA and GA algorithms require more iterations to converge to the final solution compared to the proposed greedy algorithm.
-In contrast, the proposed greedy algorithm can identify the correct MAC in a shorter number of steps.
+\ref{fig:e2f1-alg}--\ref{fig:e2f3-alg}, the SA and GA algorithms require more iterations to converge to the final solution than the proposed greedy algorithm.
 
 To further elaborate on the efficiency of our algorithm, we analyze the time complexity of both the brute-force algorithm and the greedy algorithm.
-If an RBS has $N_b$ batteries and $N_s$ switches and the corresponding directed graph has $N$ nodes,  $2^{N_s}$ iterations are required to traverse all reconfigured structures.
-Calculating each reconfigured structure using Eqs. (\ref{eq:I_o})--(\ref{eq:eta}) requires matrix inversion and matrix multiplication, which has a time complexity of $O(N^3+2N^2N_b+N^2N_s+NN^2_b)$.
+If an RBS has $N_b$ batteries and $N_s$ switches and the corresponding directed graph has $N$ nodes, $2^{N_s}$ iterations are required to traverse all possible structures.
+Calculating each reconfigured structure using Eqs.
+(\ref{eq:I_o})--(\ref{eq:eta}) requires matrix inversion and matrix multiplication, which results in a time complexity of $O(N^3+2N^2N_b+N^2N_s+NN^2_b)$.
 Therefore, the time complexity of the brute-force algorithm is $O\bm((N^3+2N^2N_b+N^2N_s+NN^2_b)2^{N_s}\bm)$.
-The greedy algorithm proposed in this paper requires  that SP be found for each battery, which requires $N_b$ iterations.
-Each SP can be obtained by several applications of Dijkstra's algorithms.
+The greedy algorithm proposed in this paper requires that the SP be found for each battery, which requires $N_b$ iterations.
+Each SP can be obtained through several applications of Dijkstra's algorithms.
 Therefore, the total time complexity for calculating all SPs is $O\bm(N_b(N_b+2N_s)\log_{10} N\bm)$.
@@
 Thus, with the bisection method, the time complexity of the greedy algorithm is $O\bm((N^3+2N^2N_b+N^2N_s+NN^2_b) 2^{N_b} N_b^{-1} \log_{10} N_b+N_b(N_b+2N_s)\log_{10} N\bm)$.
-Based on currently proposed RBS structures \cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the number $N_b$ of batteries, $N_s$ of switches, and $N$ of nodes are quantitatively related as follows: $N_s \approx (3\text{--} 5)N_b$, $N \approx N_s$.
-After simplifying, the time complexity of the method with greedy algorithm is $O(2^{N_b}N_s^2\log_{10} N_b)$, while it is $O(2^{N_s}N_s^3)$ for the method with brute-force algorithm.
-Therefore, as the RBS grows, especially in the number of switches, the greedy algorithm gains an advantage over the brute-force algorithm.
+For the existing RBS structures in the literature \cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the number of batteries $N_b$, the number of switches $N_s$, and the number of nodes $N$ are quantitatively related as follows: $N_s \approx (3\text{--} 5)N_b$, $N \approx N_s$.
+After simplifying, the time complexity of the method with the greedy algorithm is $O(2^{N_b}N_s^2\log_{10} N_b)$, while that of the method with the brute-force algorithm is $O(2^{N_s}N_s^3)$.
+Therefore, as the RBS grows, especially in terms of the number of switches, the greedy algorithm gains an advantage over the brute-force algorithm.
 This is confirmed by the number of structures required to determine the MAC in the previous section. 
 Compared with the brute-force algorithm, the method based on the greedy algorithm is 3\,000 to 48\,000 times more efficient, which is theoretically $N_s 2^{N_s - N_b} \log_{10} N_b$ times according to the above time-complexity analysis.
-This benefits from two key points:
+This is the result of two key factors:
 \begin{enumerate}
@@
 
-Furthermore, this approach has the capability to handle RBSs with arbitrary structures, which is another significant advantage of it. 
-It is able to correctly calculate the MACs of RBSs with arbitrary structures, even when they have different variant batteries, or even random isolated batteries. 
-Theoretically, each RBS structure can be transformed into the unique directed graph model using the methodology described in the Section II, and the MAC can subsequently be calculated using the proposed greedy algorithm.
-This finding has been supported in the previous subsection.
+Furthermore, this approach can handle RBSs with arbitrary structures, which is another significant advantage. 
+It can even do this when they have different battery variations or even random isolated batteries. 
+Theoretically, each RBS structure can be transformed into a unique directed graph model using the methodology described in Section II, and the MAC can subsequently be calculated using the proposed greedy algorithm.
+This finding is supported by the findings in the previous subsection.
 
@@
 Additionally, all batteries are assumed to be identical for the sake of simplification in the derivation.
-However, there may exist a small balancing current, which could introduce a minor bias to the MAC, due to variations in open-circuit voltage $u_b$ and internal resistance $r_b$ in reality.
-Nevertheless, the proposed greedy algorithm remains a viable choice for the RBS design and optimization in the early stage, and the issue of balancing current bias can be addressed by considering the variations in batteries and replacing the internal resistance with impedance when constructing the directed graph model.
+However, in reality, there may exist a small balancing current that could introduce a minor bias in the MAC due to variations in the open-circuit voltage $u_b$ and the internal resistance $r_b$.
+Nevertheless, the proposed greedy algorithm remains a viable choice for RBS design and optimization in the early stage, and the issue of balancing current bias can be addressed by considering the inconsistency between batteries and replacing the internal resistance with impedance when constructing the directed graph model.
 
@@
 Note that $\eta$ is used as the objective function instead of $I_o$ in solving for the MAC. 
-This choice makes the resulting MAC more reasonable and applicable in practical scenarios. 
+This choice makes the resulting MAC more reasonable and applicable to practical scenarios. 
 As shown in Tab. \ref{tab:study-results-my}, $I_o$ and $\bm{I}_b$ are functions of $R_o$, $u_b$, and $r_b$. 
-However, when $I_o$ is used as the objective function, even for the same RBS structure, the MAC solution and corresponding switch states could change due to different external electrical appliances.
-This would increase the difficulty and uncertainty of designing the RBS structure. 
+However, when $I_o$ is used as the objective function, even for the same RBS structure, the MAC solution and corresponding switch states can change due to different external electrical appliances.
+This increases the difficulty and uncertainty involved in designing the RBS structure. 
 To eliminate this problem, the ratio $\eta=I_o/\max(\bm{I}_b)$ is adopted as the objective function in our research.
-Recall that $\eta$ reflects only the structure's ability to output current, rather than the actual current outputting by the battery system.
-Assuming that the MAC of batteries in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by determining the value of $\eta$ for the structure.
-
-The method proposed in this paper facilitates the design of RBSs in the following ways:
-most currently proposed RBS structures \cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} have simple topological characteristics, so calculating the MACs is relatively straightforward, even intuitive.
+Recall that $\eta$ reflects only the structure's ability to output current, rather than the actual current output by the battery system.
+Assuming that the MAC of the batteries in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by determining the value of $\eta$ for the structure.
+
+The method proposed in this paper facilitates the design of RBSs in the following ways.
+Most of the existing RBS structures \cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} have simple topological characteristics, so calculating their MACs is relatively straightforward or even intuitive.
 However, these simple structures do not always fully satisfy the requirements of complex applications, such as dynamically adapting the circuit to variable and random operating conditions or actively equalizing differences between batteries in the RBS.
 Moreover, isolating the batteries disrupts the original regularity and symmetry of the topology, which complicates the otherwise simple structure, and the maximum output current of the system becomes more challenging to obtain.
-In contrast, the proposed method calculates the MAC of arbitrary RBS structures, notably the complex and flexible RBS structures.
+In contrast, the proposed method calculates the MAC of arbitrary RBS structures, most notably complex and flexible RBS structures.
 
@@
 When two batteries are isolated, there are two scenarios: 
-one is isolating two batteries within the same substructure (Figure \ref{fig:my-isolated-2b}), resulting in $\eta=2$; the other is isolating one battery in each of the two substructures (Figure \ref{fig:my-isolated-2w}), resulting in $\eta=1$.
+one is isolating two batteries within the same substructure (Fig.
+\ref{fig:my-isolated-2b}), resulting in $\eta=2$; the other is isolating one battery in each of the two substructures (Fig.
+\ref{fig:my-isolated-2w}), resulting in $\eta=1$.
 If three batteries are isolated, the RBS can only output the current of a single battery, which is $\eta=1$.
@@
 
-This paper proposes a pervasive and automated method to efficiently compute the MAC of an RBS.
-The method is implemented by a greedy algorithm combined with an improved directed graph model.
-Not only does the method provide the same global MAC calculation results as the brute-force method, but it also demonstrates superior computational efficiency compared to both the brute-force algorithm and the heuristic algorithms (SA and GA).
+This paper has proposed a reliable and automated method to efficiently compute the MAC of an RBS.
+The method is implemented using a greedy algorithm combined with an improved directed graph model.
+Not only does the method provide the same global MAC calculation results as the brute-force method, but it also demonstrates superior computational efficiency to both the brute-force algorithm and the heuristic algorithms (SA and GA).
 Theoretically, for an RBS with $N_s$ switches and $N_b$ batteries, the efficiency of the proposed method is $N_s 2^{N_s - N_b} \log_{10} N_b$ times that of the brute-force method. 
-This is primarily due to the utilization of the batteries' SPs to guide the RBS to reconfigure reasonable structures rather than blindly going through all possible structures.
-Another advantage of this method is its capability to calculate the MAC of RBSs with arbitrary structures and variant batteries. 
+This is primarily due to the utilization of the batteries' SPs guiding the RBS to reconfigure reasonable structures rather than blindly going through all possible structures.
+Another advantage of this method is its capability to calculate the MACs of RBSs with arbitrary structures and varying batteries. 
 Even in scenarios with random isolated batteries, the proposed method remains effective.
-This method facilitates the full utilization of the RBS's current output potential, guides the design and optimization of the RBS structure during the design stage, and assists in evaluating the risk of current overload in practical applications.
+This method can facilitate the full utilization of the RBS's current output potential, guide the design and optimization of the RBS structure, and assist in evaluating the risk of current overload in practical applications.
 
@@
 \begin{algorithm}
-    \caption{Get the max available currents of a certain RBS}\label{alg:greedy}
+    \caption{Obtain the maximum available current (MAC) of a given RBS}\label{alg:greedy}
     \KwData{Directed graph model $G(V,E)$ of the RBS}
@@
     Get $\bm{A}$ by Eq. \ref{eq:A}\;
-    \While{not yet determine $\max \eta$ }
+    \While{not yet determined $\max \eta$ }
     {
@@
         \For{$c_b \in C_b$}{
-            $\bm{x}_s \leftarrow \text{list of all switches' state: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
+            $\bm{x}_s \leftarrow \text{list of all switches' states: $x_s[j]=1$ if $ j \in \bigcup_{i\in c_b}SP_i $ else 0}$\;
             $\bm{X} \leftarrow diag[1,1,\cdots,1,\bm{x}_s] $\;

### 2023-11-15 paper/SST/3-response_reviewer1.tex
modify 3-letter-and-response

@@
 
-We are sorry for our negligence of the grammatical and spelling errors, and have carefully checked the manuscript and corrected them.
+We apologize for our oversight regarding the grammatical and spelling errors, and we have thoroughly reviewed the manuscript and rectified them.
+Additionally, the manuscript has undergone revisions by a professional organization to ensure the accuracy of grammar and spelling.
 

### 2023-11-15 paper/SST/3-main.tex
根据 SST 提交要求简化了题目和摘要

@@
 % \title{Using a Directed Graph Model and Greedy Algorithm to Determine the Maximum Allowable Current in a Reconfigurable Battery System}
-\title{Determining the Maximum Allowable Current of an RBS using a Directed Graph Model and Greedy Algorithm}
+\title{Determining Maximum Allowable Current of an RBS using a Directed Graph Model and Greedy Algorithm}
 
@@
 \begin{abstract}
-Reconfigurable battery systems (RBSs) provide a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structures that can be adapted to different battery charging and discharging strategies.
+Reconfigurable battery systems provide a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structures that can be adapted to different battery charging and discharging strategies.
 A critical system parameter known as the maximum allowable current (MAC) is pivotal to RBS operation.
 This parameter is instrumental in maintaining the current of each individual battery within a safe range and serves as a guiding indicator for the system's reconfiguration, ensuring its safety and reliability.
-In this paper, a method is proposed for calculating the MAC of an arbitrary RBS using a greedy algorithm in conjunction with a directed graph model of the RBS.
-Using the shortest path (SP) of the battery, the greedy algorithm transforms the exhaustion of the switch states in the brute-force algorithm or variable search without utilizing structures in the heuristic algorithms (simulated annealing and genetic algorithms) in the combination of the shortest paths.
-This significantly enhances the efficiency with which the MAC is determined.
+This paper proposes a method for calculating the MAC of an arbitrary RBS using a greedy algorithm in conjunction with a directed graph model of the RBS.
+Using the shortest path of the battery, the greedy algorithm transforms the exhaustion of the switch states in the brute-force algorithm or variable search without utilizing structures in the heuristic algorithms in the combination of the shortest paths.
 The directed graph model, based on an equivalent circuit, provides a specific method for calculating the MAC of a given structure.
 The proposed method is validated using two previously published RBS structures and an additional one with a more complex structure.
-The results are the same as those from the brute-force algorithm, but the proposed method significantly improves the computational efficiency, being theoretically $N_s 2^{N_s - N_b} \log_{10} N_b$ times faster than the brute-force algorithm for an RBS with $N_b$ batteries and $N_s$ switches.
+The results are the same as those from the brute-force algorithm, but the proposed method significantly improves the computational efficiency, being theoretically $N_s2^{N_s-N_b}\log_{10}N_b$ times faster than the brute-force algorithm for an RBS with $N_b$ batteries and $N_s$ switches.
 Another advantage of the proposed method is its ability to calculate the MAC of RBSs with arbitrary structures and variable batteries, even in scenarios with random isolated batteries. 

### 2024-02-11 paper/SST/3-main.tex
删除了main.tex中不必要的细节；删除了ref.bib中未引用文献
Add new files and update file modes

@@
 \graphicspath{ {../figures/} }
-% \graphicspath{ {../../attachments} }
 \usepackage{subcaption} 
@@
 % Title Format: Use title case, capitalizing the first letter of each word, except for certain small words, such as articles and short prepositions
-% \title{Using a Directed Graph Model and Greedy Algorithm to Determine the Maximum Allowable Current in a Reconfigurable Battery System}
 \title{Determining Maximum Allowable Current of an RBS using a Directed Graph Model and Greedy Algorithm}
@@
 Even in scenarios with random isolated batteries, the proposed method remains effective.
-This method can facilitate the full utilization of the RBS's current output potential, guide the design and optimization of the RBS structure, and assist in evaluating the risk of current overload in practical applications.
+Accordingly, this proposed method can facilitate the full utilization of the RBS's current output potential, guide the design and optimization of the RBS structure, and assist in evaluating the risk of current overload in practical applications.
+Its further application potentially focuses on the future explorations in battery energy management of the space power system in a spacecraft, to open new avenues for enhancing its efficiency and reliability.
 
@@
 \end{algorithm}
-% \begin{figure}[htbp]
-%     \centering
-%     \includegraphics[width=\textwidth]{algorithm.jpg}
-% \end{figure}
 
@@
 
-% \subsection*{Funding}
-% 
-% This work was supported by the National Natural Science Foundation of China (NSFC, No.52075028).
-
 \subsection*{Conflicts of Interest}
@@
 
-% \begin{thebibliography}{10}
-% 
-% \bibitem{yangBatteryEnergyStorage2018}
-% Yuqing Yang, Stephen Bremner, Chris Menictas, and Merlinde Kay.
-% \newblock Battery energy storage system size determination in renewable energy systems: {{A}} review.
-% \newblock {\em Renewable and Sustainable Energy Reviews}, 91:109--125, August 2018.
-% 
-% \bibitem{desiqueiraControlStrategySmooth2021}
-% Luanna Maria~Silva {de Siqueira} and Wei Peng.
-% \newblock Control strategy to smooth wind power output using battery energy storage system: {{A}} review.
-% \newblock {\em Journal of Energy Storage}, 35:102252, March 2021.
-% 
-% \bibitem{schwanbeckInternationalSpaceStation2019}
-% Eugene Schwanbeck and Penni Dalton.
-% \newblock International {{Space Station Lithium-ion Batteries}} for {{Primary Electric Power System}}.
-% \newblock In {\em 2019 {{European Space Power Conference}} ({{ESPC}})}, pages 1--1. {IEEE}, September 2019.
-% 
-% \bibitem{zhangDevelopmentProspectChinese2021}
-% Lihua Zhang.
-% \newblock Development and {{Prospect}} of {{Chinese Lunar Relay Communication Satellite}}.
-% \newblock {\em Space: Science \& Technology}, 2021, January 2021.
-% 
-% \bibitem{choCommercialResearchBattery2015}
-% Jaephil Cho, Sookyung Jeong, and Youngsik Kim.
-% \newblock Commercial and research battery technologies for electrical energy storage applications.
-% \newblock {\em Progress in Energy and Combustion Science}, 48:84--101, June 2015.
-% 
-% \bibitem{yangUnbalancedDischargingAging2016}
-% Naixing Yang, Xiongwen Zhang, BinBin Shang, and Guojun Li.
-% \newblock Unbalanced discharging and aging due to temperature differences among the cells in a lithium-ion battery pack with parallel combination.
-% \newblock {\em Journal of Power Sources}, 306:733--741, February 2016.
-% 
-% \bibitem{fengPropagationMechanismsDiagnosis2019}
-% Fei Feng, Xiaosong Hu, Lin Hu, Fengling Hu, Yang Li, and Lei Zhang.
-% \newblock Propagation mechanisms and diagnosis of parameter inconsistency within {{Li-Ion}} battery packs.
-% \newblock {\em Renewable and Sustainable Energy Reviews}, 112:102--113, September 2019.
-% 
-% \bibitem{jeevarajanBatterySafetyQualifications2012}
-% J.~A. Jeevarajan and C.~Winchester.
-% \newblock Battery {{Safety Qualifications}} for {{Human Ratings}}.
-% \newblock {\em Interface magazine}, 21(2):51--55, January 2012.
-% 
-% \bibitem{pomboHybridPowerSystem2021}
-% Daniel~V{\'a}zquez Pombo.
-% \newblock A {{Hybrid Power System}} for a {{Permanent Colony}} on {{Mars}}.
-% \newblock {\em Space: Science \& Technology}, 2021, January 2021.
-% 
-% \bibitem{hanNextGenerationBatteryManagement2020a}
-% Weiji Han, Torsten Wik, Anton Kersten, Guangzhong Dong, and Changfu Zou.
-% \newblock Next-{{Generation Battery Management Systems}}: {{Dynamic Reconfiguration}}.
-% \newblock {\em IEEE Industrial Electronics Magazine}, 14(4):20--31, December 2020.
-% 
-% \bibitem{visairoReconfigurableBatteryPack2008}
-% H.~Visairo and P.~Kumar.
-% \newblock A reconfigurable battery pack for improving power conversion efficiency in portable devices.
-% \newblock In {\em 2008 7th {{International Caribbean Conference}} on {{Devices}}, {{Circuits}} and {{Systems}}}, pages 1--6. {IEEE}, April 2008.
-% 
-% \bibitem{ci2007novel}
-% Song Ci, Jiucai Zhang, Hamid Sharif, and Mahmoud Alahmad.
-% \newblock A novel design of adaptive reconfigurable multicell battery for power-aware embedded networked sensing systems.
-% \newblock In {\em IEEE GLOBECOM 2007-IEEE Global Telecommunications Conference}, pages 1043--1047. IEEE, 2007.
-% 
-% \bibitem{9209774}
-% Jan Engelhardt, Tatiana Gabderakhmanova, Gunnar Rohde, and Mattia Marinelli.
-% \newblock Reconfigurable stationary battery with adaptive cell switching for electric vehicle fast-charging.
-% \newblock In {\em 2020 55th International Universities Power Engineering Conference (UPEC)}, pages 1--6, 2020.
-% 
-% \bibitem{engelhardt2021double}
-% Jan Engelhardt, Jan~Martin Zepter, Tatiana Gabderakhmanova, Gunnar Rohde, and Mattia Marinelli.
-% \newblock Double-string battery system with reconfigurable cell topology operated as a fast charging station for electric vehicles.
-% \newblock {\em Energies}, 14(9):2414, 2021.
-% 
-% \bibitem{lawsonSoftwareConfigurableBattery2012}
-% Barrie Lawson.
-% \newblock A {{Software Configurable Battery}}.
-% \newblock {\em EVS26 International Battery, Hybrid and Fuel Cell Electric Vehicle Symposium}, 2012.
-% 
-% \bibitem{he2014reconfiguration}
-% Liang He, Linghe Kong, Siyu Lin, Shaodong Ying, Yu~Gu, Tian He, and Cong Liu.
-% \newblock Reconfiguration-assisted charging in large-scale lithium-ion battery systems.
-% \newblock In {\em 2014 ACM/IEEE International Conference on Cyber-Physical Systems (ICCPS)}, pages 60--71. IEEE, 2014.
-% 
-% \bibitem{kim2009dynamic}
-% Hahnsang Kim and Kang~G Shin.
-% \newblock On dynamic reconfiguration of a large-scale battery system.
-% \newblock In {\em 2009 15th IEEE Real-Time and Embedded Technology and Applications Symposium}, pages 87--96. IEEE, 2009.
-% 
-% \bibitem{han2021analysis}
-% Weiji Han, Anton Kersten, Changfu Zou, Torsten Wik, Xiaoliang Huang, and Guangzhong Dong.
-% \newblock Analysis and estimation of the maximum switch current during battery system reconfiguration.
-% \newblock {\em IEEE Transactions on Industrial Electronics}, 69(6):5931--5941, 2021.
-% 
-% \bibitem{chenSneakCircuitTheory2021}
-% Si-Zhe Chen, Yule Wang, Guidong Zhang, Le~Chang, and Yun Zhang.
-% \newblock Sneak {{Circuit Theory Based Approach}} to {{Avoiding Short-Circuit Paths}} in {{Reconfigurable Battery Systems}}.
-% \newblock {\em IEEE Transactions on Industrial Electronics}, 68(12):12353--12363, 2021.
-% 
-% \bibitem{heExploringAdaptiveReconfiguration2013}
-% Liang He, Lipeng Gu, Linghe Kong, Yu~Gu, Cong Liu, and Tian He.
-% \newblock Exploring {{Adaptive Reconfiguration}} to {{Optimize Energy Efficiency}} in {{Large-Scale Battery Systems}}.
-% \newblock In {\em 2013 {{IEEE}} 34th {{Real-Time Systems Symposium}}}, pages 118--127, December 2013.
-% 
-% \bibitem{hongwenheStateofChargeEstimationLithiumIon2011}
-% Hongwen He, Rui Xiong, Xiaowei Zhang, Fengchun Sun, and JinXin Fan.
-% \newblock State-of-{{Charge Estimation}} of the {{Lithium-Ion Battery Using}} an {{Adaptive Extended Kalman Filter Based}} on an {{Improved Thevenin Model}}.
-% \newblock {\em IEEE Transactions on Vehicular Technology}, 60(4):1461--1469, May 2011.
-% 
-% \bibitem{mousavig.VariousBatteryModels2014}
-% S.M. Mousavi~G. and M.~Nikdel.
-% \newblock Various battery models for various simulation studies and applications.
-% \newblock {\em Renewable and Sustainable Energy Reviews}, 32:477--485, April 2014.
-% 
-% \bibitem{ciNovelDesignAdaptive2007}
-% Song Ci, Jiucai Zhang, Hamid Sharif, and Mahmoud Alahmad.
-% \newblock A {{Novel Design}} of {{Adaptive Reconfigurable Multicell Battery}} for {{Power-Aware Embedded Networked Sensing Systems}}.
-% \newblock In {\em {{IEEE GLOBECOM}} 2007-2007 {{IEEE Global Telecommunications Conference}}}, pages 1043--1047, November 2007.
-% 
-% \bibitem{alahmadBatterySwitchArray2008}
-% Mahmoud Alahmad, Herb Hess, Mohammad Mojarradi, William West, and Jay Whitacre.
-% \newblock Battery switch array system with application for {{JPL}}'s rechargeable micro-scale batteries.
-% \newblock {\em Journal of Power Sources}, 177(2):566--578, March 2008.
-% 
-% \bibitem{kimDependableEfficientScalable2010b}
-% Hahnsang Kim and Kang~G. Shin.
-% \newblock Dependable, efficient, scalable architecture for management of large-scale batteries.
-% \newblock In {\em Proceedings of the 1st {{ACM}}/{{IEEE International Conference}} on {{Cyber-Physical Systems}}}, {{ICCPS}} '10, pages 178--187, {New York, NY, USA}, April 2010.
-{Association for Computing Machinery}.
-% 
-% \bibitem{kimBalancedReconfigurationStorage2011a}
-% Younghyun Kim, Sangyoung Park, Yanzhi Wang, Qing Xie, Naehyuck Chang, Massimo Poncino, and Massoud Pedram.
-% \newblock Balanced reconfiguration of storage banks in a hybrid electrical energy storage system.
-% \newblock In {\em 2011 {{IEEE}}/{{ACM International Conference}} on {{Computer-Aided Design}} ({{ICCAD}})}, pages 624--631, November 2011.
-% 
-% \bibitem{taesickimSeriesconnectedSelfreconfigurableMulticell2012a}
-% Taesic Kim, Wei Qiao, and Liyan Qu.
-% \newblock A series-connected self-reconfigurable multicell battery capable of safe and effective charging/discharging and balancing operations.
-% \newblock In {\em 2012 {{Twenty-Seventh Annual IEEE Applied Power Electronics Conference}} and {{Exposition}} ({{APEC}})}, pages 2259--2264, February 2012.
-% 
-% \bibitem{6843711}
-% Liang He, Linghe Kong, Siyu Lin, Shaodong Ying, Yu~Gu, Tian He, and Cong Liu.
-% \newblock Reconfiguration-assisted charging in large-scale {{Lithium-ion}} battery systems.
-% \newblock In {\em 2014 {{ACM}}/{{IEEE International Conference}} on {{Cyber-Physical Systems}} ({{ICCPS}})}, pages 60--71, April 2014.
-% 
-% \end{thebibliography}
-
-% \printbibliography
-
 \end{document}
